### 2011-09-12 shortRange.inhomo/writeDown/main.tex
update

\documentclass[aps,pre,preprint]{revtex4}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\renewcommand{\v}[1]{\textbf{\textit{#1}}}
\renewcommand{\d}[1]{\textsf{#1}}

\begin{document}

\title{The Error Estimate of Force Calculation in Heterogeneous and Correlated Molecular Systems}
\author{Han Wang}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}
\author{Pingwen Zhang}
% \email{pzhang@pku.edu.cn}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}

\begin{abstract}
\end{abstract}

\maketitle

\section{Theoretical background}
\subsection{Error estimate in a heterogeneous system}

If a particle with cut-off radius $r_c$ is located at position $\v r$,
we denote the computed force (or cut-offed force) by $\tilde{\v F}(\v
r)$. The difference between the exact force and the computed force,
namely the error force, is denoted by $\Delta\v F(\v r) = \v F(\v r) -
\tilde{\v F}(\v r)$. The error force can be expressed by
\begin{align}
  \Delta\v F(\v r) = \sum_{j}\, \v f^c(\v r - \v r_j)
\end{align}
where $\v f^c$ is the complementary pairwise short-range force defined
by
\begin{align}
  \v f^c(\v r) =
  \left\{
  \begin{array}{ll}
    0, & \vert\v r\vert\leq r_c; \\
    \v f(\v r), & \vert\v r\vert > r_c.
  \end{array}
  \right.
\end{align}
In a homogeneous system with periodic boundary condition applied, the
surounding of any particle is isotropic, so the mean of the error
force vanishes. However, in a heterogenous system, the mean of the
error force is not necessarily zero, but
\begin{align} \label{eqn:tmp3} %\nonumber
  \langle\Delta\v F(\v r)\rangle
  &=
  \big\langle
  \sum_{j}\, \v f^c(\v r - \v r_j)
  \big\rangle 
  =
  \int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r'
\end{align}
Where $\rho(\v r)$ is the particle number density at the position $\v
r$. And notice the error force implicitly depends on the cut-off
radius used for the particle.

The widely accepted definition of the force error is the root mean
square (RMS) error, namely the square root of the second moment of the
error force is $\mathcal E(\v r) = \sqrt{\langle\vert\Delta\v F(\v
  r)\vert^2\rangle}$, which can be calculate by
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  =\,&
  \big\langle\sum_{j,k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \big\langle\sum_j\vert\v f^c(\v r - \v r_j)\vert^2\big\rangle +
  \big\langle\sum_{j\neq k}\v f^c(\v r - \v r_j)\cdot\v f^c(\v r - \v r_k)\big\rangle \\ \nonumber
  =\,&
  \int_{\mathbb R^3}\vert\v F^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r'
  + \\\label{eqn:tmp4}
  \,&
  \int_{\mathbb R^3\times\mathbb R^3}\v F^c(\v r - \v r')\cdot\v F^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r'',
\end{align}
The density $\rho(\v r')$ and the pair density $\rho(\v r', \v r'')$
are related to the probability density $p(\v r')$ and pair probability
density $p(\v r', \v r'')$ by
\begin{align}
  \rho(\v r') &= N\,p(\v r') \\
  \rho(\v r', \v r'') &= N(N-1)\,p(\v r', \v r'')
\end{align}
The densities are periodically extented to the whole space $\mathbb
R^3$.
% The problem now this how to discretize the integrals in
% \eqref{eqn:tmp4}. With the piecewise constant numerical integration
% formulus, we have:
Now, let
\begin{align} \nonumber
  \rho(\v r', \v r'')
  & = N (N-1) \,p(\v r', \v r'') \\\nonumber
  & = N (N-1) \big\{ p(\v r')p(\v r'') + [\,p(\v r', \v r'') -  p(\v r')p(\v r'')\,]\big\} \\\nonumber
  &= \frac{N-1}N \rho(\v r')\rho(\v r'') + C (\v r', \v r'')\\ \label{eqn:tmp7}
  &\approx \rho(\v r')\rho(\v r'') + C (\v r', \v r'')
\end{align}
the function
\begin{align}
C (\v r', \v r'') = N (N-1) [\,p(\v r', \v r'') -  p(\v r')p(\v r'')\,]
\end{align}
denotes the correlation between
position $\v r'$ and $\v r''$. Therefore, \eqref{eqn:tmp4} becomes
\begin{align} \nonumber
  \langle\vert\Delta\v F(\v r)\vert^2\rangle
  = &\,
  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r' \,+ \\\nonumber
  &\,
  \bigg[\int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r'\,\bigg]^2 + \\\nonumber
  &\,
  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\,C(\v r', \v r'')\,\d d\v r'\d d\v r'' \\\label{eqn:tmp5}
  = &\,
  \mathcal E_{\textrm{homo}}(\v r) +
%  \langle\Delta\v F(\v r)\,\rangle^2 +
  \mathcal E_{\textrm{hetero}}(\v r) +
  \mathcal E_{\textrm{correlation}}(\v r)
\end{align}
If the system is homogeneous and the correlation between particles is
neglected, then only the first term, which is called the homogeneity
error, is left in \eqref{eqn:tmp5}. This term is originated from the
flucuation of the error force $\Delta\v F(\v r)$. The second term is
called the heterogeneity error, because it only exists when the system
is heterogenous. It is worth poining out that the heterogeneity error
is the squared mean of the error force, namely $\mathcal
E_{\textrm{hetero}}(\v r) = \langle\Delta\v F(\v r)\,\rangle^2$.  The
last term in \eqref{eqn:tmp5} originates from the correlation between
the particles, so it is called the correlation error.  The correlation
error involves a double integrals, which implies that this term
requires more compuational cost than the homogeneity and heterogeneity
errors. The rest of this paper assumes the system is far from the
critical point, therefore the correlation error does not dominate in the
system, and can be savely neglected.

\subsection{The ways to reduce force error in a heterogenous system}

In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
standard Lennard-Jone particles is set up in a tube with periodic
boundary condition. The liquid droplet (in the middle of the tube) is
in equilibrium with the surrounding vapor environment. The red line in
the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
of this heterogeneous system. The green square denotes the real RMS
force error distribution. It is clear that the error form two peaks in
the interfacial region, which is much higher than the relative
constant error of the bulk liquid and the bulk vapor. The dashed and
the dotted blue line are the estimated homogeneity and heterogeneity
errors, and the solid blue line is the sum. In the bulk region, the
homogeneity error dominates while in the interfacial region, the
heterogeneity error dominates. The esitmated error matches perfactly
with the real error at the interfacial region, but presents
overestimation in the bulk regions. The overestimation probably stems
from the neglection of the correlation error in \eqref{eqn:tmp5}.

Traditionally, a very large cutoff radius is used to reach precise
simulation results. Since heterogeneity error dominate the force error
of the system, such a big cutoff radius is a waste in the bulk liquid
and vapor regions. One possible way is to use adapt cut-off radius
according to the error distribution, so that larger cut-off radii are
used in the interfacial region while smaller cut-off radii are used in
the bulk regions.  More precisely, the aim of the adaptive cut-off
method is to equivalently distributed the force error over the
simulation region.

The other way is to screen out the heterogeneity error by a applying a
correction force.  Starting from equation \eqref{eqn:tmp5}, the
variation of the error force can be calculated by
\begin{align} \nonumber
  \textrm{Var}[\Delta\v F(\v r)]
  & =
  \big\langle\,
  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
  \big\rangle \\\nonumber
  & =
  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
  \langle\Delta\v F(\v r)\,\rangle^2 \\
  & =
  \mathcal E_{\textrm{homo}}(\v r) +
  \mathcal E_{\textrm{corr}}(\v r)  
\end{align}
This means if we correct the computed force by the mean of the error
force, namely applying to each particle $\tilde{\v F}^c(\v r) =
\tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle$ instead of
$\tilde{\v F}(\v r)$. The error of this corrected force is reduced to
$\mathcal E_{\textrm{homo}}(\v r) + \mathcal E_{\textrm{corr}}(\v r)$
and contains no heterogeneous contribution.  These two possibilities
will be addressed and tested later in this paper.

% This
% means the force error is a combination of a homogeneous contribution,
% a heterogeneous contribution and a correlational contribution. The
% heterogeneous force can be applied as a correction to the error:
% \begin{align}\label{eqn:tmp7}
%   \v F_{\textrm{hetero}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
% \end{align}

\subsection{The fast calculation of the error estimate}\label{sec:tmp1.3}

The fast calculation of the convolutions in \eqref{eqn:tmp5} relies on
the fast Fourier transform. We assume the simulation box is uniformly
divided in to small bins.  The positions of these bins are
\begin{align}
  \v r_{i_1, i_2, i_3} & =
  \frac{i_1}{K_1}\v a_1 + 
  \frac{i_2}{K_2}\v a_2 + 
  \frac{i_3}{K_3}\v a_3,\qquad 0\leq i_\alpha< K_\alpha
\end{align}
where $\v a_\alpha$ are box vectors, and $K_\alpha$ is the number of
division on each direction. In the reciprocal space, a corresponding
lettice is set up:
\begin{align}
  \v k_{k_1, k_2, k_3} & =
  k_1\v a_1^\ast +
  k_2\v a_2^\ast +
  k_3\v a_3^\ast, \qquad 0\leq k_\alpha<K_\alpha
\end{align}
where $\v a_\alpha^\ast$ are reciprocal box vectors defined by $\v
a_\alpha\cdot\v a_\beta^\ast = \delta_{\alpha\beta}$.  In each bin the
error and the particles number density are assumed to be constant,
therefore,
\begin{align}\nonumber
  \mathcal E_{\textrm{homo}}(\v r_{i_1,i_2,i_3})
  & \approx
  \frac1V\sum_{k_1=-\infty}^\infty\sum_{k_2=-\infty}^\infty\sum_{k_3=-\infty}^\infty
  \hat{\mathcal E}_{\textrm{homo}}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg] \\\label{eqn:tmp13}
  & \approx
  \frac1V\sum_{k_1=0}^{K_1}\sum_{k_2=0}^{K_2}\sum_{k_3=0}^{K_3}
  \hat{K}_{\textrm{homo}}(\v k'_{k_1,k_2,k_3})\:
  \hat{\rho}(\v k_{k_1,k_2,k_3})
  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
  \exp\bigg[
  2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg]   
\end{align}
here we denote the convolution kernel $\vert\v f^c(\v r)\vert^2$ by
$K_{\textrm{homo}}(\v r)$.  Equation \eqref{eqn:tmp13} simply utilizes
the identity: the Fourier transform of the convolution
$K_{\textrm{homo}}\ast\rho$ is equal to the multiply of
$\hat{K}_{\textrm{homo}}$ and $\hat\rho$.  The prime on $\v
k_{k_1,k_2,k_3}$ means that we should use the periodic image $k_\alpha
- K_\alpha$ instead of $k_\alpha$ when $k_\alpha \geq K_\alpha/2$. By
definition, the Fourier transform of the density is
\begin{align}
  \hat\rho(\v k_{k_1,k_2,k_3})
  & \approx
  \frac{V}{K_1K_2K_3}
  \sum_{i_1=0}^{K_1}\sum_{i_2=0}^{K_2}\sum_{i_2=0}^{K_2}
  \rho(\v r_{i_1,i_2,i_3})
  \exp\bigg[
  -2\pi i\bigg(
  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
  \bigg)
  \bigg]
\end{align}
The Fourier transform of the homogeneity kernel is 
\begin{align}
  \hat K_{\textrm{homo}}(\v k)
  &=
  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r
\end{align}
Most of the short-range interactions are isotropic, therefore,
$K_{\textrm{homo}}(\v r) = K_{\textrm{homo}}(r)$, and
\begin{align}
  \hat{K}_{\textrm{homo}}(\v k)
  =
  \int_{\mathbb R^3}K_{\textrm{homo}}(r)e^{-2\pi i\v k\cdot\v r}\d d\v r
  =
  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr
\end{align}

Similarly, by \eqref{eqn:tmp3}, the Fourier mode of the the mean of
the error force is
\begin{align}
  \langle\Delta\v F\rangle^\wedge(\v k) =
  \hat{\v f}^c(\v k)\,
  \hat\rho(\v k)
\end{align}
where 
\begin{align}\label{eqn:tmp18}
  \hat{\v f}^c(\v k) 
  & = 
  2\pi\frac{\v k}k\, i\,
  \bigg\{
  r_c^2\,u(r_c)
  \bigg[\,
  \frac{2\cos(2\pi kr)}{2\pi kr}
  -\frac{2\sin(2\pi kr)}{(2\pi kr)^2}
  \,\bigg] 
  -
  \int_{r_c}^\infty 2r\,u(r)\sin(2\pi kr)\d d\v r
  \bigg\}
\end{align}

\subsection{Pressure corrections}
By cut-off method, the system lost the  pressure
contribution from the particles outside the cut-off radius.  In the
homogeneous systems, the distribution of particles is assumed to be
uniform and the energy and pressure corrections are calculated by
integral corresponding pair functions from the cut-off to infinity.

In the heterogeneous systems, the previous idea does not
work. Instead, the pressure correction of the
system are:
\begin{align}
  \v P^c &= \frac1{V} \bigg\langle \sum_{i\neq j}\,\frac12\, (\v r_i - \v r_j) \otimes \v f^c(\v r_i - \v r_j) \bigg\rangle
\end{align}
For simplicity, let us consider the general form the the corrections:
\begin{align}
  Q = \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle
\end{align}
For the pressure correction, $K$ is replaced by $\frac{1}{2V}\v
r\otimes\v f^c$.  By using \eqref{eqn:tmp7}, we have
\begin{align}\nonumber
  Q
  &= \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle\\\nonumber
  & = \int K(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
  & = \int K(\v r' - \v r'')
  \big[
  \rho(\v r') \rho(\v r'') + C(\v r', \v r'')
  \big]
  \d d\v r'\d d\v r''
\end{align}
Assuming the correlation $C(\v r', \v r'')$ vanishes, then
\begin{align} \nonumber
  Q 
  & = \int K(\v r' - \v r'')
  \rho(\v r') \rho(\v r'') 
  \d d\v r'\d d\v r'' \\
  & = \int
  \Big[
  \int K(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
  \Big]
  \rho(\v r')\,\d d\v r'
\end{align}

The Fourier transform of the convolution $\int K(\v r' - \v r'')
\rho(\v r'')\,\d d\v r''$ is identical to the product $\hat K(\v
k)\,\hat \rho(\v k)$. In the case of pressure correction, the Fourier
transform of $\frac{1}{2V}\v r\otimes\v f^c$ requires more efforts.
For the isotropic short-range interactions, the $\alpha\beta$
component of the pressure correction kernel can be written as
\begin{align}
  \frac1{2V}\{\v r\otimes\v f^c\}_{\alpha\beta} =
  r_\alpha r_\beta \,G^c(r) \qquad \alpha, \beta = 1, 2, 3
\end{align}
where $G^c(r)$ is independent with the direction of $\v r$.  We list
here without proving the Fourier transform of the pressure correction
kernel:
\begin{align}
  [\,r_1r_1\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi +
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big] \\
  [\,r_2 r_2\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi -
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big]   \\
  [\,r_3 r_3\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\: \,r^4 G(r)\,\pi\,
  \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23 J_{\frac12}(2\pi kr) +
  \big(\,
  \frac23 - 2\cos^2\Phi
  \big)
  J_{\frac52}(2\pi kr)
  \,\Big]\\
  [\,r_1 r_2\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin^2\Phi\sin 2\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_1 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\cos\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_2 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\sin\Theta\,J_{\frac52}(2\pi kr)
\end{align}
Where $(k, \Phi, \Theta)$ are the spherical coordinates of reciprocal
variable $\v k$, and $J_\nu(x)$ is the Bessel function of the first
kind.

\subsection{Details on implementing the adaptive cut-off radius
  method}

The adaptive cut-off radius method should be able to choose a proper
cut-off radius for each particle so that the force error is below a
predetermined target precision $\mathcal E^\ast$. The computational
cost of this operation is at least $\mathcal O(N^2\log N)$.  Becasue
to determine the cut-off radius, we should estimate the force error at
least once for each particle, and the computational cost of the force
error estimate \eqref{eqn:tmp5} is $\mathcal O(N \log N)$.

To reduce the computational cost, we assume
\begin{enumerate}
\item The space is divided in to small bins, the size of which is the
  same as those mentioned in the section \ref{sec:tmp1.3}. The cut-off
  radius is assumed to be constant within a bin, no matter the
  position of the partile.
\item The cut-off radius can only be set to a series of increasing
  discrete values between a maximum cut-off radius
  $r_c^{\textrm{max}}$ and a minimum cut-off radius
  $r_c^{\textrm{min}}$, namely $\{\,r_c^{\textrm{min}} = r_c^0 <
  r_c^1 < \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$. For
  convenience but not necessarily, the interval between two neighboring
  cut-off radius in uniform, which means
  \begin{align}
    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M
  \end{align}
  For example in some
  simulation cases, we set $r_c^{\textrm{max}} = 10.0\sigma$ and
  $r_c^{\textrm{min}} = 2.5\sigma$. In between the cut-off radius is
  adapted at a step of $0.5\sigma$, namely can only use values such as
  $2.5\,\sigma,\ 3.0\,\sigma,\ 3.5\,\sigma,\ 4.0\,\sigma,\ \cdots,\
  10.0\,\sigma$. 
\end{enumerate}

For each cut-off radius, the force error distribution $\mathcal E(\v
r)$, which is also defined on the lattice, is calculated by estimate
\eqref{eqn:tmp5}. Then a satisfactory cut-off radius of a bin is
choosen such that it is the smallest one that satisfying the precision
constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal E^\ast$. The
computational cost of this algorithm is $\mathcal O(MN\log N)$.  The
idea of this algorithm is based on the observation that the cut-off
radius may not be calculated at a high precision, a slightly (and at
most $r_c^{\textrm{step}}$) larger cut-off radius will not waste too
much computational cost.

\section{Results and discussions}

\subsection{Liquid-vapor coexistence simulation of the Lennard-Jones fluid}\label{sec:tmp2.1}

The liquid-vapor coexistence simulation is a very typical
heterogeneous molecular system, which is widely used to study the
phase coexistence properties, for example, the equilibrium liquid and
vapor density, and the surface tension. The system contains 16,000
standard Lennard-Jones particles that saperated into liquid phase in
the center of the box and vapor phase surrounded. The size of the
simulation box is $L_x^\ast \times \L_y^\ast \times L_z^\ast =
150\times 21\times 21$. This simulation box permit a maximum cut-off
radius of $r_c^\ast = 10$, and eliminate the finite scale effect
discussed in literatures \recheck {give citations here}. In all
simulations, the maximum cut-off radius considered is $10$, but the
reference (precise value) results are given by a simulation carried
out in a 24,000 particles system with simulation box $L_x^\ast \times
\L_y^\ast \times L_z^\ast = 150\times 27\times 27$, and a uniform
cut-off radius of $r_c^\ast = 13$.

Figure \ref{fig:tmp2} presents the real RMS force error (in green
square) in a system using a uniform cut-off raidus of $r_c^\ast =
7.5$. The number density distribution along $x$ direction that is
shown by the solid red line for reference.  The error is comparatively
constant at the bulk liquid and gas region and two paaks, which are
more than one order of maganitude higher than the bulk force errors,
form at the interfacial region.  The estimated RMS force error is
presented in solid blue line.  The estimate follows the real error
very well at the interfacial region, but slightly over estimate the
error in the bulk regions.  Two component of interest, namely the
homogeneous error and heterogeneous error are presented in
Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
the bulk regions, the dashed blue line overlaps with the solid blue
line, that means the homogeneous error dominates.  In the interfacial
region, in the contrary, the heterogeneous error dominate, because the
dotted blue line overlaps with the solid one.

The Fig. \ref{fig:tmp2} inspire us to develop the adaptive cut-off
method: in the bulk regions, the error is much smaller, therefore, it
is a waste to use the same cut-off radius in the bulk as the
interfacial region. The key idea is to use small cut-off radius in the
bulk regions, so that the RMS force error is uniformly distributed
over the simulation region. In Fig. \ref{fig:tmp3}, we present the
adapted cut-off radius in a solid red line and all errors in the same
notation as the Fig. \ref{fig:tmp2}. The control error $\mathcal
E^\ast = 0.0045$ is the same as the maximum error in the uniform
cut-off simulation. In the interfacial region, the cut-off radius used
is the same as in Fig. \ref{fig:tmp2}, namely $7.5$.  Whereas, in the
liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
respective, which is notably reduced. Considering the computational
cost grows with $r_c^3$, the adaptive simulation save 75 \% and 90 \%
computational cost in the liquid and vapor regions, respectively.  The
error is uniformly distributed, except that in the liquid region, the
real error is lower because the error estimate is not sharp here. In
constrast with the uniform cut-off case, i.e. Fig. \ref{fig:tmp2}, the
error estimate for the vapor region is very sharp. The same phenominon
is observed: the homogeneous error dominates in the bulk regions,
while the heterogeneous error dominates in the interfacial region.

In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
component) in the red solid line. On the left interface, the
correction force is along the positive direction of $x$ axis, namely
poiting right.  On the right interface, the correction force is of the
same maganitude but poiting left. From Fig. \ref{fig:tmp5}, the liquid
density should be higher and the vapor density should be lower than
the uniform and adaptive cut-off simulation.  The real error (in green
square) and the homogeneous error (in blue solid line) are all
presented in Fig. \ref{fig:tmp4}. The contribution of the
heterogeneous error is successfully removed, The estimate of
homogeneous error follows the real error perfectly in the vapor and
interfacial regions.  in the bulk liquid region, it slightly
overestimate the error, which is the same as the uniform and adaptive
cut-off simulations.

% As mentioned before, form Fig. \ref{fig:tmp2}, the error dominates at
% the interfacial regions. The error estimate is sharp in these
% regions. While in the bulk regions, the error estimate is not sharp,
% but still acceptable. By the adapt cut-off radius MD, the resulting
% distribution (averaged on $y$ and $z$ directions) of cut-off radius is
% given in Fig. \ref{fig:tmp3}. In the interfacial regions, the cut-off
% radius is adapted to $r_c^\ast = 7.5$. In the bulk liquid and vapor
% regions, the cut-off radii are approximatly $5.0$ and $3.5$.  The
% resulting error distribution is ploted in FIg. \ref{fig:tmp4}. It is
% clear that the error is comparatively uniformly distributed in the
% space. The estimate heterogeneous error is also dominant at the
% interfacial region, while the homogeneous error dominants in the bulk
% regions.  Since the computational cost is proportional to $r_c^3$,
% comparing with a simulation using uniform cut-off radius $7.5$, the
% adaptive cut-off simulation saves 3.4 times and 9.8 times
% computational cost, respectively. In total, the adaptive cut-off
% radius method save 50\% of the computational cost.

We test the uniform and adaptive cut-off methods as well as the
correction force method in the mentioned liquid vapor equilibrium
system. The temperatures are controlled to $T^\ast = 0.70,\ 0.85,\
1.10,\ 1.20$ by a Nos\`e-Hoover thermostat. The interested properties are
the liquid-vapor equilibrium density and the surface tension defined
by
\begin{align}
  \gamma = \frac12 \int_{L_x}
  \bigg[\,
  p_x(x) - \frac{p_y(x) + p_z(x)}{2}
  \,\bigg]
  \,\d dx
\end{align}
where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
pressure. The convergence of the properties of interest with respect
to the cut-off radius is considered.  For the adaptive cut-off
simulation, the ``cut-off radius'' means the largest cut-off radius
used in the simulation region.

In the Fig. \ref{fig:tmp5}, the convergence of the equilibrium density
is investigated. The red, green and blue points presents the results
of uniform, adaptive and force correction simulations, respectively.
The vapor densities are connected by the solid lines, and the liquid
densities are connected by the dashed lines for clarity. All data are
substracted by the reference results, which are calculated by uniform
cut-off simulations with a cut-off radius 13. We can see that the
results of the uniform and the adaptive cut-off simulations are
basically the same, which means using larger cut-off radius or
introducing large homogeneous error in the bulk regions will not
change the simulations result. For the uniform and adaptive cut-off
simulations, the results satisfactorily converge only when the cut-off
10 is used. In contrast, the force correction simulations present a
perfect convergence when the cut-off radius is equal to 5, although
result at cut-off 3.5 is acceptable. This reduction of cut-off radius
will impressively save the computational cost by 8 times with respect
to the uniform cut-off simulations, and 4 times with respect to
adaptive cut-off simulations. The liquid densities of the force
correction simulation seem systematically higher, but the deviation is
smaller than the statistical uncertainty.

The surface tension with respect to the cut-off radius is shown in the
Fig. \ref{fig:tmp6}. The color is the same as Fig. \ref{fig:tmp5}.
Surface tensions measured with and without pressure correction are
connected by solid and dashed lines, respectively.  The reference
surface tension is presented by the black solid lines. Although the
force correction is a little better, no substential difference between
the different simulation methods is observed. However, the
heterogeneous pressure correction improve the surface tention
measurement greatly. With the pressure correction, the result is
acceptable at cut-off 5.0 and satisfactorily converged at cut-off 7.5.

% The equilibrium liquid and vapor densities with respect to
% the cut-off radius are presented in Fig. \ref{fig:tmp5}. For the
% adaptive cut-off simulation, the data points represent the largest
% cut-off radius used in the simulations. All the results are
% substracted by the reference results, which are calculated at uniform
% cut-off radius of 13, for a clear comparison. Solid and dashed lines
% are added to the data points of vapor and liquid densities
% respectively. For the uniform and adaptive cut-off simulations, the
% cut-off radii 5, 7.5 and 10 are considered. For the force correction,
% the cut-off 3.5 is investigated in addition. We perform simulations at
% different temperature: that are denoted in the plots.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{fig/t0.85-n16000-rc07.5uni/confout.eps}
  \caption{The snapshot of the 16000 Lennard-Jones particle system at
    $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast = 7.5$.}
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
  \includegraphics[]{fig/t0.85-n16000-rc07.5uni/error.uniform.eps}
  \caption{The error distribution of the 16000 Lennard-Jones particle
    system at $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast
    = 7.5$.}
  \label{fig:tmp2}
\end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.adapt.eps}
%   \caption{The adapted cut-off radius of the 16000 Lennard-Jones
%     particle system at $T^\ast=0.85$.}
%   \label{fig:tmp3}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/error.adapt.eps}
%   \caption{The error distribution of the adaptive-cut-off 16000
%     Lennard-Jones particle system at $T^\ast=0.85$.}
%   \label{fig:tmp4}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.eps}
%   \caption{The correction force simulation of the 16000 Lennard-Jones
%     particle system at $T^\ast=0.85$.}
%   \label{fig:tmp3}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/error.fcorr.eps}
%   \caption{The correction force simulation of the adaptive-cut-off 16000
%     Lennard-Jones particle system at $T^\ast=0.85$.}
%   \label{fig:tmp4}
% \end{figure}

\begin{figure}
  \centering
  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
  \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.and.error.eps}
  \caption{The correction force simulation of the 16000 Lennard-Jones
    particle system at $T^\ast=0.85$.}
  \label{fig:tmp3}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
  \caption{The correction force simulation of the 16000 Lennard-Jones
    particle system at $T^\ast=0.85$.}
  \label{fig:tmp4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
  \caption{normal words}
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
  \caption{normal words}
  \label{fig:tmp6}
\end{figure}

\subsection{Collision of nanoscale Lennard-Jones clusters}
\label{sec:tmp2.2}

In this section, we test how the adaptive cut-off method and the force
correction method work in a dynamical problem: collision of nanoscale
Lennard-Jones clusters. Two initial Lennard-Jones clusters, denoted by
$A$ and $B$, are setup in the simulation box, each of which contains
the same number of particles $N_A = N_B = 10792$, with a diameter of
$d^\ast\approx 27$. The initial velocity of the clusters are $\v u_A =
\frac12(u, 0, 0)$ and $\v u_B = -\frac12(u, 0, 0)$, see
Fig. \ref{fig:tmp7}. The impact parameter $D$ is defined by the $z$
corrdinate difference between the center of mass (COM) of the
clusters. The unitless impact factor defined by
\begin{align}
  x = \frac D d
\end{align}
is used to measure how far off-center the collision happens. If $x =
0$ the collision is head-on, while $x=1$ the collision is avoided.
Ref. \cite{kalweit2006collision} investigated a board range
combination of velocity $u$ and impact factor $x$, and identified
three major collision modes: the coalescence, the streching seperation
and the shattering. The major modes were further classified into a
series submodes. In this paper, we want to study the how the collision
properties of interests are affected by the force calculation
precision, therefore, we will NOT investigate a broad range of
parameters, but focus on one special case: $u^\ast = 2.2$ and $x =
0.6$, where poor precision of force calculation will lead to wrong
major collision modes.

In the top two plots of Fig. \ref{fig:tmp9}, we present the trajectory
of cluster $A$ and COM distance between the two clusters.  Three
different cut-off radii of uniform cut-off simulation are considered.
In this case the two clusters collide and form one rotating cluster.
It is obvious that the trajectory of $r_c^\ast = 2.5$ is completely
wrong: two clusters finally seperate. The $r_c^\ast = 5.0$ trajectory
is reasonably good, but the COM distance converges only when $r_c^\ast
= 7.5$. This means the precision of force calculation is crucial in
the study of collision dynamics.

The RMS force error of $r_c^\ast = 5.0$ uniform cut-off simulation,
the distribution of adaptive cut-off simulation and the magnitude of
the correction force are plotted in Fig. \ref{tmp:fig8}.  The
configuration of the two clusters (colored in gray and yellow) are
presented on the top for reference. The same as the liquid-vapor
equilibrium simulation, the error of the force located at the
interfacial region, namely the boundary of the clusters. Inside and
outside the clusters, the force error is much lower.  The maximum
cut-off used in the adaptive cut-off simulation is 5.0, which follows
the maximum RMS force error perfectly. The maximum cut-off region is
much border than the maximum error region, because it is refined by
twice to keep track of the possible moving of the clusters.  The
cut-off radius in the force correction simulation is 2.5, although
using such a small cut-off radius, the collision is in the right mode,
see also Fig. \ref{tmp:fig9}. The maximum of the correction force also
following the boundary of the colliding clusters, wheras in the interial
region of the clusters, the correction force is neglectable.

The angular velocity is presented in the left plot of
Fig. \ref{tmp:fig10}. The force correction result is not as precise as
other simulations excluding uniform $r_c = 2.5$ simulation. This
because the correction force is not precise because it is calculated
every \recheck{aaa} steps. In the right plot of Fig. \ref{tmp:fig10},
the angular moment, which should be preserved is presented. All
uniform simulations preserved the angular moment perfectly. The
angular moment of the adaptive cut-off simulation, which does not
precisly preserve the Newton's third law, shows deviation but is still
around the correct value. However, the angular moment of the force
correction simulation flies away from the the correct value by 1 \% at
$t^\ast = 130$.

\begin{figure}
  \centering
  \includegraphics[]{fig/collision-init/init.2.eps}
  \caption{normal words}
  \label{fig:tmp7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/trajs.eps}
  \includegraphics[width=0.49\textwidth]{fig/dists.eps}
  \caption{normal words}
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.90\textwidth]{fig/error-rcut-ball.eps} 
  \includegraphics[width=0.90\textwidth]{fig/error-rcut.eps}
  \caption{normal words}
  \label{fig:tmp8}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/wy.eps}
  \includegraphics[width=0.49\textwidth]{fig/ly.eps}
  \caption{normal words}
  \label{fig:tmp10}
\end{figure}

% \newpage

% \bibliography{ref}{}
% \bibliographystyle{unsrt}

\end{document}

### 2011-09-27 shortRange.inhomo/writeDown/main.tex
back up, finished intro

@@
 \documentclass[aps,pre,preprint]{revtex4}
+% \documentclass[aps,pre,twocolumn]{revtex4}
 % \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
@@
 
-\title{The Error Estimate of Force Calculation in Heterogeneous and Correlated Molecular Systems}
+\title{The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems}
 \author{Han Wang}
@@
 
+\section{Introduction}
+Non-bonded short-range interaction is encountered in nearly every
+molecular simulation.  A naive idea to calculate short-range
+interactions is to explicitly calculate all pairwise
+interactions. This results in a computational cost scaling $\mathcal
+O(N^2)$ per time step, which rapidly becomes inefficient as the number
+of particles $N$ grows large. A better way is to introduce a cut-off
+radius, outside of which all pairwise interactions are simply
+neglected. In combination with the cell list and the neighbor list
+algorithms \cite{frenkel02b}, the total computational cost of the
+short-range interactions can be reduced to an acceptable level of
+$\mathcal O(N)$. The cut-off radius is only a user provided
+algorithmetic parameter, so it should have no effect on the
+physical/chemical properties of the system.  Therefore, it is very
+important to test the convergence of the simulation results with
+respect to the used cut-off radius before collecting data and deriving
+conclusions. Fortunately, in most homogeneous systems, a satisfactory
+convergence can be achieved even with a very small cut-off value, for
+example, $2.5$ -- $4.0\sigma$.  Moreover, it is possible to correct
+the systematic error of the potential energy, the pressure and the
+free energy by applying the standard long range correction
+(LRC)~\cite{allen87a}, which assumes the uniformity outside the
+cut-off and integrates the contribution of the mentioned properties to
+infinity.  However,
+% The spacial inhomogenety of the system in terms of particle density,
+% particle type and change distribution is very common in natrual
+% system.
+the direct molecular simulation of a inhomogeneous system will
+encounter non-trival difficulty that does not exist in the homogeneous
+bulk simulations.  The measured properties are found to depend on the
+cut-off radius even at a very large value~\cite{duque2004some}. Also
+the contiuity at the cut-off and the long-range correction involved
+may have foundamental effect on the simulation
+results~\cite{trokhymchuk1999computer, shen2007comparative,
+  guo1997long, mecke1997molecular, janecek2006long, goujon2004monte}.
+Therefore, it is necessary to systemetically study the precision of
+short-range interaction calculation, and to develop methods screening
+out the aforementioned cut-off artifect in the inhomogeneous systems.
+
+% In this paper, we focus on the systems in which
+% atoms/particles are interacting via short-range interactions, because
+% it is a good starting point of the study of more complex systems, for
+% example, the systems with long-range electrostatic interactions.  The
+% simulation results in the inhomogeneous systems are found to depend on
+% a number of factors of treating the short-range interaction in the
+% simulation. For example, the way of calculating the short-range
+% interaction (simple cut-off method or Ewald
+% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
+%   lopez2006liquid, shi2006molecular, ismail2007application}, the
+% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
+%   shen2007comparative}, the way of long-range
+% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
+%   goujon2004monte} and the size and shape of the simulation
+% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
+% It should be noticed that the physical properties are the nature of
+% the system, and should NOT depend on the details of the interaction
+% calculation.
+
+A promising way to quantitatively analyze the undesirable cut-off
+effects is to express these artifacts in terms of the difference
+between the cut-offed interaction and the exact interaction, namely
+the error. In homogeneous systems, the error analysis of the
+short-range interaction has been well established,
+see~\cite{kolafa1992cutoff} for example. Also the error
+estimates~\cite{hummer1995numerical, kolafa1992cutoff,
+  petersen1995accuracy, deserno1998mue2, wang2010optimizing} for
+long-range Ewald family methods~\cite{ewald1921die,
+  hockney1988computer, deserno1998mue1, darden1993pme, essmann1995spm}
+have provided a profound view of the precision of force calculation,
+and introduced parameter tuning algorithms~\cite{limbach06a,
+  wang2010optimizing} that boost the efficiency of the computation
+with a good control of the error. However, in inhomogeneous systems
+the error study is still scarce, even for the simplest short-range
+interaction.
+
+In this work, we develop the error estimate of the short-range force
+in inhomogeneous systems. The force error can be split into the
+homogeneous and inhomogeneous part regardless the correlation in the
+system. The inhomogeneous error that can be more than one order of
+maganitude larger than the homogeneous error plays a dominant role in
+the interfacial region. An adaptive cut-off method is hereby proposed
+to equally distribte the error according to the error estimate, so
+that a substantial computational effort can be saved while the
+precision of simulation is preserved. We also proposed a long-range
+force correction method based on the error estimate to screen out the
+contribution of the inhomogeneous error, which can tremendously
+improve the precision of simulation. To show the effectiveness of the
+error estimate and the proposed methods, two systems are tested: the
+liquid-vapor equilibrium for equilibrium properties, and the colliding
+nanoscale clusters for dynamical properties. Finally, a conclusion is
+given in section \ref{sec:conclusion}.
+
+% The error estimate of long-range algorithms, for example the Ewald
+% family method~\cite{ewald1921die, hockney1988computer,
+%   deserno1998mue1, darden1993pme, essmann1995spm} and the fast
+% multipole method~\cite{greengard1987fast}, has been well developped in
+% the past 20 years ~\cite{hummer1995numerical, kolafa1992cutoff,
+%   petersen1995accuracy, deserno1998mue2, wang2010optimizing,
+%   dachsel2009error}.
+
 \section{Theoretical background}
@@
 
-If a particle with cut-off radius $r_c$ is located at position $\v r$,
-we denote the computed force (or cut-offed force) by $\tilde{\v F}(\v
-r)$. The difference between the exact force and the computed force,
-namely the error force, is denoted by $\Delta\v F(\v r) = \v F(\v r) -
-\tilde{\v F}(\v r)$. The error force can be expressed by
-\begin{align}
-  \Delta\v F(\v r) = \sum_{j}\, \v f^c(\v r - \v r_j)
-\end{align}
-where $\v f^c$ is the complementary pairwise short-range force defined
-by
+Suppose the system is composed by $N$ identical particles located at
+$\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
+Since the error estimate developed for the one-component system can be
+directly extended to multi-component system without substantial
+difficulty, the discussion in this paper will focus on one-component
+system for symplicity.  These particles are interacting via a
+short-range pairwise interaction denoted by $u(\v r)$ and correspond
+force denoted by $\v f(\v r)$, with a cut-off radius $r_c > 0$.  This
+means the interaction between any pair of particles falling out of the
+cut-off radius is neglected.  An infinite cut-off radius will lead to
+a precise calculation of interaction, but it is impractical.  The
+error of computing interaction is mainly introduced by a finit value
+of the cut-off radius. For convenience, the complementary of the
+cut-offed short-range force is defined by
 \begin{align}
@@
 \end{align}
-In a homogeneous system with periodic boundary condition applied, the
-surounding of any particle is isotropic, so the mean of the error
-force vanishes. However, in a heterogenous system, the mean of the
-error force is not necessarily zero, but
+To measure the error of force computing, we add a testing particle at
+position $\v r$. The exact force and the computed force (or cut-offed
+force) exerted by the system on the testing particle are denoted by
+${\v F}(\v r)$ and $\tilde{\v F}(\v r)$, respectively.  The difference
+between them, namely the \emph{error force}, is denoted by $\Delta\v
+F(\v r) = \v F(\v r) - \tilde{\v F}(\v r)$, which can be expressed by
+\begin{align}
+  \Delta\v F(\v r) = \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n).
+\end{align}
+Where $\v n$ is simulation box vector, so the summation over $\v n$
+indicates that all periodic images are consider in the force
+calculation. In a homogeneous system with periodic boundary condition
+applied, the surounding of any particle is isotropic, so the
+\emph{mean error force} vanishes, namely $\langle\Delta\v F(\v
+r)\rangle = 0$. However, in a heterogenous system, the mean error
+force is not necessarily zero but
 \begin{align} \label{eqn:tmp3} %\nonumber
@@
   \big\langle
-  \sum_{j}\, \v f^c(\v r - \v r_j)
+  \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n)
   \big\rangle 
@@
 \end{align}
-Where $\rho(\v r)$ is the particle number density at the position $\v
-r$. And notice the error force implicitly depends on the cut-off
-radius used for the particle.
+Where $\rho(\v r)$ denotes the particle number density at the position
+$\v r$, and is periodically extended to $\mathbb R^3$. And notice the
+error force implicitly depends on the cut-off radius used for the
+interaction.
 
-The widely accepted definition of the force error is the root mean
-square (RMS) error, namely the square root of the second moment of the
+The widely accepted definition of the force error is the \emph{root mean
+square} (RMS) \emph{error}, namely the square root of the second moment of the
 error force is $\mathcal E(\v r) = \sqrt{\langle\vert\Delta\v F(\v
@@
 \end{align}
-The densities are periodically extented to the whole space $\mathbb
+The pair density is also periodically extented to the whole space $\mathbb
 R^3$.
@@
 flucuation of the error force $\Delta\v F(\v r)$. The second term is
-called the heterogeneity error, because it only exists when the system
-is heterogenous. It is worth poining out that the heterogeneity error
-is the squared mean of the error force, namely $\mathcal
-E_{\textrm{hetero}}(\v r) = \langle\Delta\v F(\v r)\,\rangle^2$.  The
-last term in \eqref{eqn:tmp5} originates from the correlation between
-the particles, so it is called the correlation error.  The correlation
-error involves a double integrals, which implies that this term
-requires more compuational cost than the homogeneity and heterogeneity
-errors. The rest of this paper assumes the system is far from the
-critical point, therefore the correlation error does not dominate in the
-system, and can be savely neglected.
-
-\subsection{The ways to reduce force error in a heterogenous system}
-
-In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
-standard Lennard-Jone particles is set up in a tube with periodic
-boundary condition. The liquid droplet (in the middle of the tube) is
-in equilibrium with the surrounding vapor environment. The red line in
-the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
-of this heterogeneous system. The green square denotes the real RMS
-force error distribution. It is clear that the error form two peaks in
-the interfacial region, which is much higher than the relative
-constant error of the bulk liquid and the bulk vapor. The dashed and
-the dotted blue line are the estimated homogeneity and heterogeneity
-errors, and the solid blue line is the sum. In the bulk region, the
-homogeneity error dominates while in the interfacial region, the
-heterogeneity error dominates. The esitmated error matches perfactly
-with the real error at the interfacial region, but presents
-overestimation in the bulk regions. The overestimation probably stems
-from the neglection of the correlation error in \eqref{eqn:tmp5}.
-
-Traditionally, a very large cutoff radius is used to reach precise
-simulation results. Since heterogeneity error dominate the force error
-of the system, such a big cutoff radius is a waste in the bulk liquid
-and vapor regions. One possible way is to use adapt cut-off radius
-according to the error distribution, so that larger cut-off radii are
-used in the interfacial region while smaller cut-off radii are used in
-the bulk regions.  More precisely, the aim of the adaptive cut-off
-method is to equivalently distributed the force error over the
-simulation region.
-
-The other way is to screen out the heterogeneity error by a applying a
-correction force.  Starting from equation \eqref{eqn:tmp5}, the
-variation of the error force can be calculated by
-\begin{align} \nonumber
-  \textrm{Var}[\Delta\v F(\v r)]
-  & =
-  \big\langle\,
-  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
-  \big\rangle \\\nonumber
-  & =
-  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
-  \langle\Delta\v F(\v r)\,\rangle^2 \\
-  & =
-  \mathcal E_{\textrm{homo}}(\v r) +
-  \mathcal E_{\textrm{corr}}(\v r)  
-\end{align}
-This means if we correct the computed force by the mean of the error
-force, namely applying to each particle $\tilde{\v F}^c(\v r) =
-\tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle$ instead of
-$\tilde{\v F}(\v r)$. The error of this corrected force is reduced to
-$\mathcal E_{\textrm{homo}}(\v r) + \mathcal E_{\textrm{corr}}(\v r)$
-and contains no heterogeneous contribution.  These two possibilities
-will be addressed and tested later in this paper.
-
-% This
-% means the force error is a combination of a homogeneous contribution,
-% a heterogeneous contribution and a correlational contribution. The
-% heterogeneous force can be applied as a correction to the error:
-% \begin{align}\label{eqn:tmp7}
-%   \v F_{\textrm{hetero}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
-% \end{align}
+called the heterogeneity error, because it generates due to the
+density heterogeneity of the system. It is worth poining out that the
+heterogeneity error is the nothing but the squared mean error force,
+namely $\mathcal E_{\textrm{hetero}}(\v r) = \langle\Delta\v F(\v
+r)\,\rangle^2$.  The last term in \eqref{eqn:tmp5} originates from the
+correlation between the particles, so it is called the correlation
+error.  The correlation error involves a double integral, which
+implies that calculating this term requires more compuational cost
+than the homogeneity and heterogeneity errors. The rest of this paper
+assumes the system is far from the critical point, therefore the
+correlation error does not dominate in the system, and can be savely
+neglected.
 
@@
 
-The fast calculation of the convolutions in \eqref{eqn:tmp5} relies on
-the fast Fourier transform. We assume the simulation box is uniformly
-divided in to small bins.  The positions of these bins are
+The naive calculation of the error estimate \eqref{eqn:tmp5} requires
+the compuational cost of $\mathcal O(N^2)$. To apply the error
+estimate on-the-fly with simulation, the compuational cost should be
+reduced to at least $\mathcal O(N\log N)$.  This is achieved by
+calculating the convolutions in \eqref{eqn:tmp5} with the fast Fourier
+transform. We assume the simulation box is uniformly divided in to
+small bins.  The positions of these bins are
 \begin{align}
@@
 
-Similarly, by \eqref{eqn:tmp3}, the Fourier mode of the the mean of
-the error force is
-\begin{align}
+Similarly, by \eqref{eqn:tmp3}, the Fourier mode of the the mean error
+force is
+\begin{align}\label{eqn:tmp17}
   \langle\Delta\v F\rangle^\wedge(\v k) =
@@
   -
-  \int_{r_c}^\infty 2r\,u(r)\sin(2\pi kr)\d d\v r
+  \int_{r_c}^\infty 2r\,u(r)\sin(2\pi kr)\,\d d\v r
   \bigg\}
@@
 
-\subsection{Pressure corrections}
-By cut-off method, the system lost the  pressure
-contribution from the particles outside the cut-off radius.  In the
-homogeneous systems, the distribution of particles is assumed to be
-uniform and the energy and pressure corrections are calculated by
-integral corresponding pair functions from the cut-off to infinity.
+\subsection{The adaptive cut-off radius method}
+
+% In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
+% standard Lennard-Jone particles is set up in a tube with periodic
+% boundary condition. The liquid droplet (in the middle of the tube) is
+% in equilibrium with the surrounding vapor environment. The red line in
+% the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
+% of this heterogeneous system. The green square denotes the real RMS
+% force error distribution. It is clear that the error form two peaks in
+% the interfacial region, which is much higher than the relative
+% constant error of the bulk liquid and the bulk vapor. The dashed and
+% the dotted blue line are the estimated homogeneity and heterogeneity
+% errors, and the solid blue line is the sum. In the bulk region, the
+% homogeneity error dominates while in the interfacial region, the
+% heterogeneity error dominates. The esitmated error matches perfactly
+% with the real error at the interfacial region, but presents
+% overestimation in the bulk regions. The overestimation probably stems
+% from the neglection of the correlation error in \eqref{eqn:tmp5}.
+
+A basic observation in a heterogeneous system is that the RMS force
+error is not uniformly distributed. The difference between the maximum
+and minimum error can be as large as two orders of maganitude, see
+Fig. \ref{fig:tmp2}. Traditionally, a very large cut-off radius is
+used to reduce the maximum error to an acceptable level and to reach
+convergent simulation results. However, a huge amount of compuational
+effort is wasted in the low-error region. The idea of the adaptive
+cut-off radius simulation is to use larger cut-off radius for
+particles in the high-error region to control the force error, while
+to use smaller cut-off radius for particles in the low-error region to
+save compuational cost.  The vaidity of this method relies on a
+diliberated cut-off choice for each particle so that the force error
+is uniformly distributed across the simulation region.  Unfortunately,
+the compuational expense of a naive implementation of this method is
+at least $\mathcal O(N^2\log N)$.  Becasue to determine the cut-off
+radius, we should estimate the RMS force error at least once for each
+particle, and the computational cost of each force error estimate is
+$\mathcal O(N \log N)$.
+
+% Since heterogeneity error dominate the
+% force error of the system, such a big cutoff radius is a waste in the
+% bulk liquid and vapor regions. One possible way is to use adapt
+% cut-off radius according to the error distribution, so that larger
+% cut-off radii are used in the interfacial region while smaller cut-off
+% radii are used in the bulk regions.  More precisely, the aim of the
+% adaptive cut-off method is to equivalently distributed the force error
+% over the simulation region.
+
+To make the adaptive cut-off method feasible,
+\begin{enumerate}
+\item The space is divided in to small bins, the size of which is the
+  same as those mentioned in the section \ref{sec:tmp1.3}.  The
+  particles falling in the same bin are assigned by the same cut-off
+  radius.
+  % The cut-off
+  % radius is assumed to be constant within a bin, no matter the
+  % position of the partile.
+\item The cut-off radius can only be chosen from a discrete series of
+  increasing values between a maximum cut-off radius
+  $r_c^{\textrm{max}}$ and a minimum cut-off radius
+  $r_c^{\textrm{min}}$: $\{\,r_c^{\textrm{min}} = r_c^0 < r_c^1 <
+  \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$.  We call it the
+  \emph{candidate set} of cut-off radii.  For convenience but not
+  necessarily, the interval between two neighboring cut-off radius in
+  uniform, which means
+  \begin{align}
+    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M
+  \end{align}
+  For example, a possible candidate set is $\{2.5\,\sigma,\
+  3.0\,\sigma,\ 3.5\,\sigma,\ 4.0\,\sigma,\ \cdots,\ 10.0\,\sigma\}$,
+  with $r_c^{\textrm{max}} = 10.0\sigma$, $r_c^{\textrm{min}} =
+  2.5\sigma$ and $r_c^{\textrm{step}} = 0.5 \sigma$.
+\end{enumerate}
+For each cut-off radius in the candidate set, the force error
+distribution $\mathcal E(\v r)$ is calculated by estimate
+\eqref{eqn:tmp5}. Notice the error is calculated on-the-fly by the
+fast algorithm described in section \ref{sec:tmp1.3}, therefore it is
+defined on the bins.  For a predetermined error control level
+$\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius of a bin is
+choosen such that it is the smallest one that satisfying the precision
+constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
+E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
+O(MN\log N)$.  The idea of this algorithm is based on the observation
+that the cut-off radius may not be calculated at a very high
+precision, a slightly (and at most $r_c^{\textrm{step}}$) larger
+cut-off radius will not waste too much computational cost.  Due to the
+thermodynamic flucuation of the system density, the resulting cut-off
+distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of lattice
+position) needs to be refined by the following scheme:
+\begin{align}\label{eqn:rc-refine}
+  r^{(1)}_c(\v r_{i_1,i_2,i_3}) = \max_{j_\alpha\in I}\,r_c(\v r_{i_1+j_1,i_2+j_2,i_3+j_3}),
+  \quad I = \{-1, 0, 1\},
+\end{align}
+to catch the fluctuating interfacial region.
+
+% This
+% means the force error is a combination of a homogeneous contribution,
+% a heterogeneous contribution and a correlational contribution. The
+% heterogeneous force can be applied as a correction to the error:
+% \begin{align}\label{eqn:tmp7}
+%   \v F_{\textrm{hetero}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
+% \end{align}
+
+\subsection{Force correction by the mean error force}
+
+In a spacial heterogeneous system, the heterogeneity error may play a
+dominate role in the simulation, (see examples in section
+\ref{sec:tmp2}).  Since the mean error force can be calculated
+by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
+heterogeneity error is to correct the computed force by the mean error
+force, namely
+\begin{align}\label{eqn:define-fcorr}
+  \v F_{\textrm{corr}}(\v r) = \tilde{\v F}(\v r) + \langle\Delta\v F(\v r)\rangle.
+\end{align}
+The mean of the corrected error force vanishes:
+\begin{align}\label{eqn:mean-fcorr}
+  \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
+   =
+  \big\langle\,
+  \v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,
+  \big\rangle = 0.
+\end{align}
+The mean square error is therefore given by
+\begin{align} \nonumber
+  \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
+  & =
+  \big\langle\,
+  [\,\v F(\v r) - \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
+  \big\rangle \\\nonumber
+  & =
+  \big\langle\,
+  [\,\Delta\v F(\v r) - \langle\Delta\v F(\v r)\rangle\,]^2
+  \big\rangle \\\nonumber
+  & =
+  \langle\vert\Delta\v F(\v r)\vert^2\rangle -
+  \langle\Delta\v F(\v r)\,\rangle^2 \\
+  & =
+  \mathcal E_{\textrm{homo}}(\v r) +
+  \mathcal E_{\textrm{correlation}}(\v r).
+\end{align}
+It worth noticing that the mean square error of the corrected force is
+nothing but the variance of the uncorrected  error force:
+$\langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle =
+\textrm{Var}[\Delta\v F(\v r)]$, which contains no heterogeneous
+contribution.
+
+% \textrm{Var}[\Delta\v F_{\textrm{corr}}(\v r)] =
+
+% This means if we correct the computed force by the mean of the error
+% force, namely applying to each particle $\tilde{\v F}^c(\v r) =
+% \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle$ instead of
+% $\tilde{\v F}(\v r)$.
+
+\subsection{Heterogeneous pressure corrections}
+By the cut-off method, the system lost the pressure contribution from
+the particles outside the cut-off radius.  In the homogeneous systems,
+the distribution of particles is assumed to be uniform outside the
+cut-off radius, and the pressure correction is calculated by
+integrating the virial from the cut-off to infinity.
 
 In the heterogeneous systems, the previous idea does not
-work. Instead, the pressure correction of the
-system are:
+work. Instead, the pressure correction of the system are:
 \begin{align}
@@
 For the isotropic short-range interactions, the $\alpha\beta$
-component of the pressure correction kernel can be written as
+component of the kernel $\frac{1}{2V}\v r\otimes\v f^c$ can be written
+as
 \begin{align}
@@
 where $G^c(r)$ is independent with the direction of $\v r$.  We list
-here without proving the Fourier transform of the pressure correction
-kernel:
+here without proving the Fourier transform of these terms:
 \begin{align}
@@
 
-\subsection{Details on implementing the adaptive cut-off radius
-  method}
-
-The adaptive cut-off radius method should be able to choose a proper
-cut-off radius for each particle so that the force error is below a
-predetermined target precision $\mathcal E^\ast$. The computational
-cost of this operation is at least $\mathcal O(N^2\log N)$.  Becasue
-to determine the cut-off radius, we should estimate the force error at
-least once for each particle, and the computational cost of the force
-error estimate \eqref{eqn:tmp5} is $\mathcal O(N \log N)$.
-
-To reduce the computational cost, we assume
-\begin{enumerate}
-\item The space is divided in to small bins, the size of which is the
-  same as those mentioned in the section \ref{sec:tmp1.3}. The cut-off
-  radius is assumed to be constant within a bin, no matter the
-  position of the partile.
-\item The cut-off radius can only be set to a series of increasing
-  discrete values between a maximum cut-off radius
-  $r_c^{\textrm{max}}$ and a minimum cut-off radius
-  $r_c^{\textrm{min}}$, namely $\{\,r_c^{\textrm{min}} = r_c^0 <
-  r_c^1 < \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$. For
-  convenience but not necessarily, the interval between two neighboring
-  cut-off radius in uniform, which means
-  \begin{align}
-    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M
-  \end{align}
-  For example in some
-  simulation cases, we set $r_c^{\textrm{max}} = 10.0\sigma$ and
-  $r_c^{\textrm{min}} = 2.5\sigma$. In between the cut-off radius is
-  adapted at a step of $0.5\sigma$, namely can only use values such as
-  $2.5\,\sigma,\ 3.0\,\sigma,\ 3.5\,\sigma,\ 4.0\,\sigma,\ \cdots,\
-  10.0\,\sigma$. 
-\end{enumerate}
-
-For each cut-off radius, the force error distribution $\mathcal E(\v
-r)$, which is also defined on the lattice, is calculated by estimate
-\eqref{eqn:tmp5}. Then a satisfactory cut-off radius of a bin is
-choosen such that it is the smallest one that satisfying the precision
-constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal E^\ast$. The
-computational cost of this algorithm is $\mathcal O(MN\log N)$.  The
-idea of this algorithm is based on the observation that the cut-off
-radius may not be calculated at a high precision, a slightly (and at
-most $r_c^{\textrm{step}}$) larger cut-off radius will not waste too
-much computational cost.
-
-\section{Results and discussions}
+\section{Results and discussions}\label{sec:tmp2}
 
@@
 standard Lennard-Jones particles that saperated into liquid phase in
-the center of the box and vapor phase surrounded. The size of the
-simulation box is $L_x^\ast \times \L_y^\ast \times L_z^\ast =
-150\times 21\times 21$. This simulation box permit a maximum cut-off
+the center of the box and vapor phase surrounded.  The conventional
+dimensionless unit system is employed: the unit of length, energy,
+mass and time are denoted by $\epsilon$, $\sigma$, $m$ and $\tau$
+($\tau = \sigma\sqrt{m/\varepsilon}$), respectively.  All quantities
+are written in the unitless form by adding the superscript ``$\ast$''.
+For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$ and
+$P^\ast = P \sigma^3 / \epsilon$.  The MD time step {is} $\Delta
+t^\ast = 0.005$. The simulations last for $3\times 10^6$ time
+steps. The first $1\times 10^6$ steps are discarded. The quantities of
+interest are sampled every 100 time steps. The commonly used blocking
+average method~\cite{flyvbjerg1989error} is applied to estimate the
+statistical uncertainty of the autocorrelated data. The NVT ensemble
+is generated by the Nos\`e-Hoover thermostat~\cite{nose1984molecular,
+  hoover1985canonical}.  The size of the simulation box is $L_x^\ast
+\times L_y^\ast \times L_z^\ast = 150\times 21\times 21$, as shown in
+Fig. \ref{fig:tmp1}. This simulation box permit a maximum cut-off
 radius of $r_c^\ast = 10$, and eliminate the finite scale effect
-discussed in literatures \recheck {give citations here}. In all
-simulations, the maximum cut-off radius considered is $10$, but the
-reference (precise value) results are given by a simulation carried
-out in a 24,000 particles system with simulation box $L_x^\ast \times
-\L_y^\ast \times L_z^\ast = 150\times 27\times 27$, and a uniform
-cut-off radius of $r_c^\ast = 13$.
+discussed in literatures \cite{orea2005oscillatory,
+  biscay2009calculation}. In all simulations, the maximum cut-off
+radius considered is $10$, but the reference (precise value) results
+are given by a simulation carried out in a 24,000 particles system
+with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
+150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
+13$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{fig/t0.85-n16000-rc07.5uni/confout.eps}
+  \caption{The snapshot of the 16000 Lennard-Jones particle system at
+    $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast = 7.5$.}
+  \label{fig:tmp1}
+\end{figure}
 
@@
 square) in a system using a uniform cut-off raidus of $r_c^\ast =
-7.5$. The number density distribution along $x$ direction that is
-shown by the solid red line for reference.  The error is comparatively
-constant at the bulk liquid and gas region and two paaks, which are
-more than one order of maganitude higher than the bulk force errors,
-form at the interfacial region.  The estimated RMS force error is
-presented in solid blue line.  The estimate follows the real error
-very well at the interfacial region, but slightly over estimate the
-error in the bulk regions.  Two component of interest, namely the
-homogeneous error and heterogeneous error are presented in
+7.5$. The number density distribution along $x$ direction is shown by
+the solid red line for reference.  The error is comparatively constant
+at the bulk liquid and gas region. In contrast, two paaks, which are
+more than one order of maganitude larger than the force errors in bulk
+regions, form at the interfacial region.  The estimated RMS force
+error is presented in solid blue line.  The estimate follows the real
+error very well at the interfacial region, but slightly over estimate
+the error in the bulk regions.  Two components of the force error,
+namely the homogeneity error and heterogeneity error are presented in
 Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
 the bulk regions, the dashed blue line overlaps with the solid blue
-line, that means the homogeneous error dominates.  In the interfacial
-region, in the contrary, the heterogeneous error dominate, because the
+line, that means the homogeneity error dominates.  In the interfacial
+region, in the contrary, the heterogeneity error dominate, because the
 dotted blue line overlaps with the solid one.
 
-The Fig. \ref{fig:tmp2} inspire us to develop the adaptive cut-off
+\begin{figure}
+  \centering
+  % \includegraphics[]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
+  \includegraphics[]{fig/t0.85-n16000-rc07.5uni/error.uniform.eps}
+  \caption{The RMS force error distribution of the 16000 Lennard-Jones
+    particle system at $T^\ast=0.85$ with a uniform cut-off radius of
+    $r_c^\ast = 7.5$. The green squares present the real error. The
+    solid blue line is the error estimate by \eqref{eqn:tmp5}. The
+    dashed blue line is the homogeneity error contribution, while the
+    dotted blue line is the heterogeneity error contribution. The
+    density distribution of the system is presented by red solid line
+    for reference.  All properties are properly averaged on the $y$
+    and $z$ direction, therefore, the profiles are plotted along the
+    $x$ direction.  }
+  \label{fig:tmp2}
+\end{figure}
+
+The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
 method: in the bulk regions, the error is much smaller, therefore, it
-is a waste to use the same cut-off radius in the bulk as the
-interfacial region. The key idea is to use small cut-off radius in the
-bulk regions, so that the RMS force error is uniformly distributed
-over the simulation region. In Fig. \ref{fig:tmp3}, we present the
-adapted cut-off radius in a solid red line and all errors in the same
-notation as the Fig. \ref{fig:tmp2}. The control error $\mathcal
-E^\ast = 0.0045$ is the same as the maximum error in the uniform
-cut-off simulation. In the interfacial region, the cut-off radius used
-is the same as in Fig. \ref{fig:tmp2}, namely $7.5$.  Whereas, in the
-liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
-respective, which is notably reduced. Considering the computational
-cost grows with $r_c^3$, the adaptive simulation save 75 \% and 90 \%
-computational cost in the liquid and vapor regions, respectively.  The
-error is uniformly distributed, except that in the liquid region, the
-real error is lower because the error estimate is not sharp here. In
-constrast with the uniform cut-off case, i.e. Fig. \ref{fig:tmp2}, the
-error estimate for the vapor region is very sharp. The same phenominon
-is observed: the homogeneous error dominates in the bulk regions,
-while the heterogeneous error dominates in the interfacial region.
+is a waste to use the same cut-off radius as the interfacial
+regions. As mentioned before, the key idea is to use small cut-off
+radius in the bulk regions, so that the RMS force error is uniformly
+distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
+present the adapted cut-off radius in a solid red line and all errors
+in the same notation as the Fig. \ref{fig:tmp2}. The control error
+$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is the same as the maximum
+error in the uniform cut-off simulation with $r_c^\ast=7.5$. The
+cut-off distribution is refined for twice by \eqref{eqn:rc-refine}. In
+the interfacial region, the same cut-off radius as the uniform cut-off
+simulation, namely $7.5$, is reproduced.  Whereas, in the liquid and
+vapor regions, the cut-off radii are $4.75$ and $3.5$, respective,
+which is notably reduced. Considering the computational cost grows
+with $\mathcal O(r_c^3)$, the adaptive cut-off saves 75 \% and 90 \%
+computational cost in the liquid and vapor bulk regions, respectively.
+The error is uniformly distributed, except that in the liquid region,
+the real error is somewhat lower because the error estimate is not
+sharp here. In constrast with the uniform cut-off case,
+i.e. Fig. \ref{fig:tmp2}, the error estimate for the vapor region is
+very sharp. The same phenominon is observed: the homogeneity error
+dominates in the bulk regions, while the heterogeneity error dominates
+in the interfacial region.
 
-In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
-component) in the red solid line. On the left interface, the
-correction force is along the positive direction of $x$ axis, namely
-poiting right.  On the right interface, the correction force is of the
-same maganitude but poiting left. From Fig. \ref{fig:tmp5}, the liquid
-density should be higher and the vapor density should be lower than
-the uniform and adaptive cut-off simulation.  The real error (in green
-square) and the homogeneous error (in blue solid line) are all
-presented in Fig. \ref{fig:tmp4}. The contribution of the
-heterogeneous error is successfully removed, The estimate of
-homogeneous error follows the real error perfectly in the vapor and
-interfacial regions.  in the bulk liquid region, it slightly
-overestimate the error, which is the same as the uniform and adaptive
-cut-off simulations.
+\begin{figure}
+  \centering
+  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
+  \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.and.error.eps}
+  \caption{ The RMS force error distribution of the 16000
+    Lennard-Jones particle system at $T^\ast=0.85$ with adaptive
+    cut-off radius. The control error $\mathcal E^\ast_{\textrm{C}}$
+    is the same as the maximum error in the uniform cut-off simulation
+    with $r_c^\ast=7.5$.  The resulting cut-off radius distribution is
+    presented by the red line. All other notations are the same as
+    Fig.~\ref{fig:tmp2}.}
+  \label{fig:tmp3}
+\end{figure}
+
+In Fig. \ref{fig:tmp4}, we present the mean error force (only $x$
+component) by the red solid line. The $y$ and $z$ components of the
+mean error force is not shown because their magnitudes are negligible.
+On the left interface, the mean error force is along the positive
+direction of $x$ axis, namely poiting right.  On the right interface,
+the mean error force is of the same maganitude but poiting
+left. Therefore, the liquid density should be higher and the vapor
+density should be lower than the uniform and adaptive cut-off
+simulations.  The real error (in green square) and the homogeneity
+error (in blue solid line) are all presented in
+Fig. \ref{fig:tmp4}. Clearly the contribution of the heterogeneity
+error is successfully removed, because the estimate of homogeneity
+error follows the real error perfectly in the interfacial regions.  In
+the bulk liquid region, the homogeneity error is slightly
+overestimated, which is the same as the uniform and adaptive cut-off
+simulations.
+
+\begin{figure}
+  \centering
+  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
+  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
+  \caption{ The RMS force error distribution of the 16000
+    Lennard-Jones particle system at $T^\ast=0.85$ with force
+    corrected by the mean error force,
+    i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off radius is $r^\ast_c =
+    7.5$. The $x$ component of the mean error force is presented by
+    the solid red line. The green squares present the real error. The
+    solid blue line presents the homogeneity error. }
+  \label{fig:tmp4}
+\end{figure}
 
@@
 % clear that the error is comparatively uniformly distributed in the
-% space. The estimate heterogeneous error is also dominant at the
+% space. The estimate heterogeneity error is also dominant at the
 % interfacial region, while the homogeneous error dominants in the bulk
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
+  \caption{The convergence of the equilibrium gas and liquid density
+    with respect to the cut-off radius. All densities are substracted
+    by the reference value, namely, the liquid and vapor density
+    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
+    presents the results of three methods, namely the uniform cut-off
+    (URC), the adaptive cut-off (ARC) and the force correction (FC)
+    method. }
+  \label{fig:tmp5}
+\end{figure}
+
 In the Fig. \ref{fig:tmp5}, the convergence of the equilibrium density
@@
 of uniform, adaptive and force correction simulations, respectively.
-The vapor densities are connected by the solid lines, and the liquid
+The gas densities are connected by the solid lines, and the liquid
 densities are connected by the dashed lines for clarity. All data are
 substracted by the reference results, which are calculated by uniform
-cut-off simulations with a cut-off radius 13. We can see that the
-results of the uniform and the adaptive cut-off simulations are
-basically the same, which means using larger cut-off radius or
-introducing large homogeneous error in the bulk regions will not
-change the simulations result. For the uniform and adaptive cut-off
-simulations, the results satisfactorily converge only when the cut-off
-10 is used. In contrast, the force correction simulations present a
-perfect convergence when the cut-off radius is equal to 5, although
-result at cut-off 3.5 is acceptable. This reduction of cut-off radius
-will impressively save the computational cost by 8 times with respect
-to the uniform cut-off simulations, and 4 times with respect to
-adaptive cut-off simulations. The liquid densities of the force
-correction simulation seem systematically higher, but the deviation is
-smaller than the statistical uncertainty.
+cut-off simulations with a cut-off radius $r_c^\ast=13$.  In the
+higher temperature cases, the thermodynamic flucuation of the system
+is stronger. Therefore, the meansurement of densities are less
+accurate in higher temperature cases than in lower temperature cases.
+At $T^\ast = 0.70$, the gas density is more accurate than the liquid
+density, while at $T^\ast = 1.20$, the gas and liquid densities are of
+the same accuracy.
 
-The surface tension with respect to the cut-off radius is shown in the
-Fig. \ref{fig:tmp6}. The color is the same as Fig. \ref{fig:tmp5}.
-Surface tensions measured with and without pressure correction are
-connected by solid and dashed lines, respectively.  The reference
-surface tension is presented by the black solid lines. Although the
-force correction is a little better, no substential difference between
-the different simulation methods is observed. However, the
-heterogeneous pressure correction improve the surface tention
-measurement greatly. With the pressure correction, the result is
-acceptable at cut-off 5.0 and satisfactorily converged at cut-off 7.5.
+The liquid and gas densities of the uniform and the adaptive cut-off
+methods are almost identical using the same cut-off radius. This
+observation is also true for the surface tension, see
+Fig. \ref{fig:tmp6}. This indicates that controlling the maximum of
+force error (see Tab. \ref{tab:tmp1}) and introducing larger
+homogeneous force error in the bulk liquid/gas regions will not
+disturb the accuracy of equilibrium densities and surface tension.
+The adaptive cut-off method roughly saves one half of the
+computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
+adaptive cut-off depends on the system geometry: if the work load
+mainly concentrates on the bulk phase region, the adaptive cut-off
+will save a lot computational expense. On the other hand, if the
+interfacial region is computationally intensive, the adaptive will not
+improve the efficency greatly.
+
+The force correction method presents a perfect convergence when the
+cut-off radius is equal to or larger than 5, and the result at a
+cut-off as small as 3.5 is acceptable. Comparing the results of force
+correction method at $r_c^\ast = 3.5$ and uniform cut-off radius
+method at $r_c = 7.5$, the maximum force error of the former method is
+3--5 times larger than the later (see Tab. \ref{tab:tmp1}), however,
+the measure of equilibrium densities and surface tension are
+comparable to and sometimes even better than the later (see
+Fig. \ref{fig:tmp5} and \ref{fig:tmp6}). In the force correction
+simulation, the heterogeneity error is screened out and the force
+error term is dominated by the homogeneity error. And in the uniform
+cut-off simulation the force error is dominated by the heterogeneity
+error in the interfacial regions. Therefore, the homogeneity error and
+heterogeneity error play different roles in the simulations.  The
+heterogeneity error stems from the non-vanishing value of the mean
+error force, which is alway pointing at one certain direction (the
+same direction as the low-to-high density jump), see
+Fig. \ref{fig:tmp4} for example. The homogeneity error is actually the
+variation of the corrected error force that may be cancelled by itself
+in a long time. The reason is the corrected error force has a
+varnished mean value (see eqn. \eqref{eqn:mean-fcorr}), so it may
+point to any direction with the same possibility.  With the same
+cut-off radius, the computational cost of the force correction and
+uniform cut-off methods are nearly the same, see
+Tab. \ref{tab:tmp1}. However, the maximum force error of the force
+correction method is about one order of maganitude more precise,
+comparing with the uniform cut-off simulations.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
+  \caption{The convergence of the surface tension with respect to the
+    cut-off radius.  This figure presents the results of three
+    methods, namely the uniform cut-off (URC), the adaptive cut-off
+    (ARC) and the force correction (FC) method.  The results with and
+    without heterogeneous pressure correction (HPC) are shown together
+    for comparison. The reference surface tensions, shown by solid
+    black lines, are measured by the uniform cut-off method with
+    $r_c^\ast=13$ using HPC.}
+  \label{fig:tmp6}
+\end{figure}
+
+The convergence of the surface tension with respect to the cut-off
+radius is shown in the Fig. \ref{fig:tmp6}. The color notation is the
+same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
+without heterogeneous pressure correction are connected by solid and
+dashed lines, respectively.  The reference surface tension is
+presented by the black solid lines. The heterogeneous pressure
+correction improve the surface tention measurement greatly. The
+discrepancy between the corrected and uncorrected pressure is the
+value of the correction, which decreases with increasing cut-off
+radius. However, even at $r_c^\ast=10$, the correction is not
+negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
+temperature, the statistical uncertainty gets larger, and better
+convergence is achieved at small cut-off radius.
+
+% Although the force correction is a
+% little better, no substential difference between the different
+% simulation methods is observed. However, the With the
+% pressure correction, the result is acceptable at cut-off 5.0 and
+% satisfactorily converged at cut-off 7.5.
+
+\begin{table}
+  \centering
+  \caption{
+    The maximum RMS force error and computational cost of 
+    of three methods, namely the uniform cut-off
+    (URC), the adaptive cut-off (ARC) and the force correction (FC) method.
+    The computational cost is the number of pairwise interaction 
+    measurements performed by the program, which should be mashine-independent.
+  }\label{tab:tmp1}
+  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
+    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
+    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
+    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
+    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
+0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
+    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
+    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
+    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
+    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
+    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
+    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
+    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
+    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
+    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
+0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
+    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
+    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
+    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
+    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
+  \end{tabular*}
+  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
+    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
+    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
+    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
+    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
+1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
+    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
+    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
+    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
+    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
+    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
+    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
+    & 5.0 &\textrm{ARC} & $9.2\times 10^{-3}$ & 2.9 \\
+    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
+    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
+1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
+    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
+    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
+    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
+    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
+  \end{tabular*}
+\end{table}
 
@@
 % different temperature: that are denoted in the plots.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\textwidth]{fig/t0.85-n16000-rc07.5uni/confout.eps}
-  \caption{The snapshot of the 16000 Lennard-Jones particle system at
-    $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast = 7.5$.}
-  \label{fig:tmp1}
-\end{figure}
-
-\begin{figure}
-  \centering
-  % \includegraphics[]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-rc07.5uni/error.uniform.eps}
-  \caption{The error distribution of the 16000 Lennard-Jones particle
-    system at $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast
-    = 7.5$.}
-  \label{fig:tmp2}
-\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.and.error.eps}
-  \caption{The correction force simulation of the 16000 Lennard-Jones
-    particle system at $T^\ast=0.85$.}
-  \label{fig:tmp3}
-\end{figure}
-
-\begin{figure}
-  \centering
-  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
-  \caption{The correction force simulation of the 16000 Lennard-Jones
-    particle system at $T^\ast=0.85$.}
-  \label{fig:tmp4}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
-  \caption{normal words}
-  \label{fig:tmp5}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
-  \caption{normal words}
-  \label{fig:tmp6}
-\end{figure}
-
 \subsection{Collision of nanoscale Lennard-Jones clusters}
@@
 
-In this section, we test how the adaptive cut-off method and the force
-correction method work in a dynamical problem: collision of nanoscale
+In this section, we test the adaptive cut-off method and the force
+correction method in a dynamical problem: collision of nanoscale
 Lennard-Jones clusters. Two initial Lennard-Jones clusters, denoted by
@@
 
-In the top two plots of Fig. \ref{fig:tmp9}, we present the trajectory
-of cluster $A$ and COM distance between the two clusters.  Three
-different cut-off radii of uniform cut-off simulation are considered.
-In this case the two clusters collide and form one rotating cluster.
-It is obvious that the trajectory of $r_c^\ast = 2.5$ is completely
-wrong: two clusters finally seperate. The $r_c^\ast = 5.0$ trajectory
-is reasonably good, but the COM distance converges only when $r_c^\ast
-= 7.5$. This means the precision of force calculation is crucial in
-the study of collision dynamics.
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/collision-init/init.2.eps}
+  \caption{The initial setup of cluster $A$ and $B$. The initial
+    velocity are equal in maganitude but on opposite direction.}
+  \label{fig:tmp7}
+\end{figure}
 
-The RMS force error of $r_c^\ast = 5.0$ uniform cut-off simulation,
-the distribution of adaptive cut-off simulation and the magnitude of
-the correction force are plotted in Fig. \ref{tmp:fig8}.  The
-configuration of the two clusters (colored in gray and yellow) are
-presented on the top for reference. The same as the liquid-vapor
-equilibrium simulation, the error of the force located at the
-interfacial region, namely the boundary of the clusters. Inside and
-outside the clusters, the force error is much lower.  The maximum
-cut-off used in the adaptive cut-off simulation is 5.0, which follows
-the maximum RMS force error perfectly. The maximum cut-off region is
-much border than the maximum error region, because it is refined by
-twice to keep track of the possible moving of the clusters.  The
-cut-off radius in the force correction simulation is 2.5, although
-using such a small cut-off radius, the collision is in the right mode,
-see also Fig. \ref{tmp:fig9}. The maximum of the correction force also
-following the boundary of the colliding clusters, wheras in the interial
-region of the clusters, the correction force is neglectable.
-
-The angular velocity is presented in the left plot of
-Fig. \ref{tmp:fig10}. The force correction result is not as precise as
-other simulations excluding uniform $r_c = 2.5$ simulation. This
-because the correction force is not precise because it is calculated
-every \recheck{aaa} steps. In the right plot of Fig. \ref{tmp:fig10},
-the angular moment, which should be preserved is presented. All
-uniform simulations preserved the angular moment perfectly. The
-angular moment of the adaptive cut-off simulation, which does not
-precisly preserve the Newton's third law, shows deviation but is still
-around the correct value. However, the angular moment of the force
-correction simulation flies away from the the correct value by 1 \% at
-$t^\ast = 130$.
+In Fig. \ref{fig:tmp8} and \ref{fig:tmp9}, we present the trajectory
+of cluster $A$ and COM distance between the two clusters,
+respectively. Three different cut-off radii of uniform cut-off
+simulation are considered. In this case the two clusters collide and
+form one rotating cluster. It is obvious that the trajectory of
+$r_c^\ast = 2.5$ is completely wrong: two clusters seperate after
+collision. The $r_c^\ast = 5.0$ trajectory is reasonably good, but the
+COM distance converges only when $r_c^\ast = 7.5$. This means the
+precision of force calculation is crucial in the study of collision
+dynamics. Althougth the precision of the adaptive cut-off method of
+$r_c^\ast = 5$ is the as uniform cut-off $r_c^\ast = 5$, the former
+produce better trajectory than the later. The force correction method
+that get rid of the heterogeneity error produces correct trajectory,
+but the motion along the trajectory is somewhat faster than other
+methods (see also the angular velocity in Fig. \ref{fig:tmp11}).
 
@@
   \centering
-  \includegraphics[]{fig/collision-init/init.2.eps}
-  \caption{normal words}
-  \label{fig:tmp7}
+  \includegraphics[]{fig/trajs.eps}
+  \caption{The center of mass trajectory of cluster A. Uniform cut-off
+    $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off $r_c = 5.0$ and
+    force correction of $r^\ast_c = 2.5$ are investigated.  The time
+    interval between two neighboring squares on the trajectory is 4.
+  }
+  \label{fig:tmp8}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/trajs.eps}
   \includegraphics[width=0.49\textwidth]{fig/dists.eps}
-  \caption{normal words}
+  \caption{The distance between the center of mass of cluster $A$ and
+    cluster $B$ as a function of time.}
   \label{fig:tmp9}
 \end{figure}
+
+The RMS force error of $r_c^\ast = 5.0$ uniform cut-off simulation,
+the cut-off distribution of adaptive cut-off method and the magnitude
+of the mean error force are plotted in Fig. \ref{fig:tmp8}.  The
+configuration of the two clusters (colored in gray and yellow) are
+presented on the top for reference. The same as the liquid-vapor
+equilibrium simulation, the force error located at the interfacial
+region, namely the boundary of the clusters. Inside and outside the
+clusters, the error is much lower.  The maximum cut-off used in the
+adaptive cut-off simulation is 5.0, which follows the large error
+region perfectly. The large cut-off region is much border than the
+large error region, because it is refined by twice to keep track of
+the possible moving of the clusters.  The mean error force also
+follows the boundary of the colliding clusters. In the bulk region
+of the clusters, the correction force is neglectable.
 
@@
   \caption{normal words}
-  \label{fig:tmp8}
+  \label{fig:tmp10}
+\end{figure}
+
+The angular velocity is presented in Fig. \ref{fig:tmp11}. The force
+correction result is not as precise as other simulations excluding
+uniform $r_c = 2.5$ simulation.  The value of the mean error force is
+updated every \recheck{aaa} time steps, so considering the moving of the clusters,
+it is not the up-to-date value.
+% This because the correction force is
+% not precise because it is calculated every \recheck{aaa} steps.
+In the Fig. \ref{fig:tmp12}, the angular moment, which should be
+preserved is presented. All uniform simulations preserved the angular
+moment perfectly. The angular moment of the adaptive cut-off
+simulation, which does not precisly preserve the Newton's third law,
+shows deviation but is still around the correct value. However, the
+angular moment of the force correction simulation flies away from the
+the correct value by 1 \% at $t^\ast = 130$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/wy.eps}
+  \caption{normal words}
+  \label{fig:tmp11}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/wy.eps}
   \includegraphics[width=0.49\textwidth]{fig/ly.eps}
   \caption{normal words}
-  \label{fig:tmp10}
+  \label{fig:tmp12}
 \end{figure}
+
+\section{Conclusion}\label{sec:conclusion}
 
@@
 
-% \bibliography{ref}{}
-% \bibliographystyle{unsrt}
+\bibliography{ref}{}
+\bibliographystyle{unsrt}
 

### 2011-09-27 shortRange.inhomo/writeDown/main.tex
finish intro

@@
 in inhomogeneous systems. The force error can be split into the
-homogeneous and inhomogeneous part regardless the correlation in the
-system. The inhomogeneous error that can be more than one order of
-maganitude larger than the homogeneous error plays a dominant role in
-the interfacial region. An adaptive cut-off method is hereby proposed
-to equally distribte the error according to the error estimate, so
-that a substantial computational effort can be saved while the
-precision of simulation is preserved. We also proposed a long-range
-force correction method based on the error estimate to screen out the
-contribution of the inhomogeneous error, which can tremendously
-improve the precision of simulation. To show the effectiveness of the
-error estimate and the proposed methods, two systems are tested: the
-liquid-vapor equilibrium for equilibrium properties, and the colliding
-nanoscale clusters for dynamical properties. Finally, a conclusion is
-given in section \ref{sec:conclusion}.
+homogeneous and inhomogeneous part regardless the particle-particle
+correlation outside the cut-off radius. The inhomogeneous error that
+can be more than one order of maganitude larger than the homogeneous
+error plays a dominant role in the interfacial region. An adaptive
+cut-off method is hereby proposed to equally distribte the error
+according to the error estimate, so that a substantial computational
+effort can be saved while the precision of simulation is preserved. We
+also proposed a long-range force correction method based on the error
+estimate to screen out the contribution of the inhomogeneous error,
+which can tremendously improve the precision of simulation. To show
+the effectiveness of the error estimate and the proposed methods, two
+systems are tested: the liquid-vapor equilibrium for equilibrium
+properties, and the colliding nanoscale clusters for dynamical
+properties. Finally, conclusions are given in section
+\ref{sec:conclusion}.
 
@@
     &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
-    & 5.0 &\textrm{ARC} & $9.2\times 10^{-3}$ & 2.9 \\
+    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
     &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
@@
 
-\section{Conclusion}\label{sec:conclusion}
+\section{Conclusions}\label{sec:conclusion}
 

### 2011-09-28 shortRange.inhomo/writeDown/main.tex
revising, backup

@@
 short-range interactions can be reduced to an acceptable level of
-$\mathcal O(N)$. The cut-off radius is only a user provided
-algorithmetic parameter, so it should have no effect on the
-physical/chemical properties of the system.  Therefore, it is very
-important to test the convergence of the simulation results with
-respect to the used cut-off radius before collecting data and deriving
-conclusions. Fortunately, in most homogeneous systems, a satisfactory
-convergence can be achieved even with a very small cut-off value, for
-example, $2.5$ -- $4.0\sigma$.  Moreover, it is possible to correct
-the systematic error of the potential energy, the pressure and the
-free energy by applying the standard long range correction
-(LRC)~\cite{allen87a}, which assumes the uniformity outside the
-cut-off and integrates the contribution of the mentioned properties to
-infinity.  However,
-% The spacial inhomogenety of the system in terms of particle density,
+$\mathcal O(N)$. The cut-off radius is a user provided algorithmetic
+parameter, so it should have NO effect on the simulation result of
+physical/chemical properties.  Therefore, it is very important to test
+the convergence of the simulation results with respect to the cut-off
+radius before collecting data and deriving conclusions. Fortunately,
+in most homogeneous systems, a satisfactory convergence can be
+achieved even with a very small cut-off value, for example,
+$2.5\sigma$.  Moreover, it is possible to correct the systematic error
+of the potential energy, the pressure and the free energy by applying
+the standard long range correction (LRC)~\cite{allen87a}, which
+assumes the uniformity outside the cut-off radius and integrates the
+contribution of the mentioned properties to infinity. 
+% The spacial heterogenety of the system in terms of particle density,
 % particle type and change distribution is very common in natrual
 % system.
-the direct molecular simulation of a inhomogeneous system will
-encounter non-trival difficulty that does not exist in the homogeneous
-bulk simulations.  The measured properties are found to depend on the
-cut-off radius even at a very large value~\cite{duque2004some}. Also
-the contiuity at the cut-off and the long-range correction involved
-may have foundamental effect on the simulation
-results~\cite{trokhymchuk1999computer, shen2007comparative,
+
+Heterogeneous systems, in which density (or atom type) changes within
+the length scale of several molecules, are more universal than
+homogeneous systems in nature. However, the direct molecular
+simulation of heterogeneous systems by the cut-off method will
+encounter non-trival difficulties that do not exist in the homogeneous
+system simulations.  The simulation results are found to converge only
+at a very large cut-off radius value~\cite{duque2004some,
+  ismail2007application}, also denpend on the energy/force continuity
+at the cut-off and the way of applying the long-range
+correction~\cite{trokhymchuk1999computer, shen2007comparative,
   guo1997long, mecke1997molecular, janecek2006long, goujon2004monte}.
 Therefore, it is necessary to systemetically study the precision of
-short-range interaction calculation, and to develop methods screening
-out the aforementioned cut-off artifect in the inhomogeneous systems.
+the short-range interaction calculation, and to develop methods
+screening out the aforementioned cut-off artifect in the heterogeneous
+systems.
 
@@
 % example, the systems with long-range electrostatic interactions.  The
-% simulation results in the inhomogeneous systems are found to depend on
+% simulation results in the heterogeneous systems are found to depend on
 % a number of factors of treating the short-range interaction in the
@@
 between the cut-offed interaction and the exact interaction, namely
-the error. In homogeneous systems, the error analysis of the
-short-range interaction has been well established,
-see~\cite{kolafa1992cutoff} for example. Also the error
-estimates~\cite{hummer1995numerical, kolafa1992cutoff,
-  petersen1995accuracy, deserno1998mue2, wang2010optimizing} for
-long-range Ewald family methods~\cite{ewald1921die,
-  hockney1988computer, deserno1998mue1, darden1993pme, essmann1995spm}
-have provided a profound view of the precision of force calculation,
-and introduced parameter tuning algorithms~\cite{limbach06a,
-  wang2010optimizing} that boost the efficiency of the computation
-with a good control of the error. However, in inhomogeneous systems
-the error study is still scarce, even for the simplest short-range
-interaction.
+the error. In homogeneous systems, the error analysis of the cut-off
+method has been well established, see~\cite{kolafa1992cutoff} for
+example. Also the error estimates~\cite{hummer1995numerical,
+  kolafa1992cutoff, petersen1995accuracy, deserno1998mue2,
+  wang2010optimizing} for long-range Ewald family
+methods~\cite{ewald1921die, hockney1988computer, deserno1998mue1,
+  darden1993pme, essmann1995spm} have provided a profound
+understanding of the accuracy of force calculation, and introduced
+parameter tuning algorithms~\cite{limbach06a, wang2010optimizing} that
+boost the efficiency of the computation with a good control of the
+error. However, in heterogeneous systems the error study is still
+scarce, even for the simplest cut-off method.
 
 In this work, we develop the error estimate of the short-range force
-in inhomogeneous systems. The force error can be split into the
-homogeneous and inhomogeneous part regardless the particle-particle
-correlation outside the cut-off radius. The inhomogeneous error that
-can be more than one order of maganitude larger than the homogeneous
-error plays a dominant role in the interfacial region. An adaptive
-cut-off method is hereby proposed to equally distribte the error
-according to the error estimate, so that a substantial computational
-effort can be saved while the precision of simulation is preserved. We
-also proposed a long-range force correction method based on the error
-estimate to screen out the contribution of the inhomogeneous error,
-which can tremendously improve the precision of simulation. To show
-the effectiveness of the error estimate and the proposed methods, two
+in heterogeneous systems. We prove that the 
+force error is comprised of a homogeneity error and a heterogeneity
+error, regardless the particle-particle correlation outside the
+cut-off radius.  In a heterogeneous system composed by several bulk
+regions, an important observation is that the heterogeneity error can
+be more than one order of maganitude larger than the homogeneity
+error, and plays a dominant role in the interfacial region. An
+adaptive cut-off method is hereby proposed to equally distribute the
+error across the simulation region, so that a substantial
+computational effort can be saved while the precision of simulation is
+preserved. We also proposed a long-range force correction (LFC) method
+based on the error estimate to screen out the contribution of the
+heterogeneity error, which can tremendously improve the precision of
+simulation without much extra computational load. To show the
+effectiveness of the error estimate and the proposed methods, two
 systems are tested: the liquid-vapor equilibrium for equilibrium
@@
 
+In this paper, we only consider the single-component system. Because
+this assumption simplifies the discussion, and the error estimates for
+the single-component system can be straightforwardly extended to the
+multi-component system without substantial difficulty.  The only the
+force error is estimated in the present paper, because the
+applications are based on molecular dynamics simulation.
+% Since the error estimate developed for the one-component system can be
+% directly extended to multi-component system without substantial
+% difficulty, the discussion in this paper will focus on one-component
+% system for symplicity. 
 Suppose the system is composed by $N$ identical particles located at
 $\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
-Since the error estimate developed for the one-component system can be
-directly extended to multi-component system without substantial
-difficulty, the discussion in this paper will focus on one-component
-system for symplicity.  These particles are interacting via a
+ These particles are interacting via a
 short-range pairwise interaction denoted by $u(\v r)$ and correspond
@@
 means the interaction between any pair of particles falling out of the
-cut-off radius is neglected.  An infinite cut-off radius will lead to
-a precise calculation of interaction, but it is impractical.  The
-error of computing interaction is mainly introduced by a finit value
-of the cut-off radius. For convenience, the complementary of the
-cut-offed short-range force is defined by
+cut-off radius is neglected.
+% An infinite cut-off radius will lead to
+% a precise calculation of interaction, but it is impractical.
+% The error of computing interaction is mainly introduced by a finit
+% value of the cut-off radius.
+The force error mainly stems from the neglected interaction outside
+the cut-off radius, so it is convenient to consider the complementary
+of the cut-offed force that is defined by
 \begin{align}
@@
 \end{align}
-To measure the error of force computing, we add a testing particle at
-position $\v r$. The exact force and the computed force (or cut-offed
-force) exerted by the system on the testing particle are denoted by
-${\v F}(\v r)$ and $\tilde{\v F}(\v r)$, respectively.  The difference
+We measure the force error at an arbitary position in the system,
+saying $\v r$, by adding a testing particle to that position.  We
+assume all particles in the system exert forces on the testng
+particle, whereas the testing particle do NOT exert any force on the
+system.  The exact force and the computed force (or cut-offed force)
+exerted by the system on the testing particle are denoted by ${\v
+  F}(\v r)$ and $\tilde{\v F}(\v r)$, respectively.  The difference
 between them, namely the \emph{error force}, is denoted by $\Delta\v
@@
 \end{align}
-Where $\v n$ is simulation box vector, so the summation over $\v n$
-indicates that all periodic images are consider in the force
-calculation. In a homogeneous system with periodic boundary condition
-applied, the surounding of any particle is isotropic, so the
-\emph{mean error force} vanishes, namely $\langle\Delta\v F(\v
-r)\rangle = 0$. However, in a heterogenous system, the mean error
-force is not necessarily zero but
+Where $\v n$ is the box vector, so the summation over $\v n$ indicates
+that all periodic images of the system are considered. In a
+homogeneous system, the surounding of any particle is isotropic, so
+the \emph{mean error force} vanishes: $\langle\Delta\v F(\v r)\rangle
+= 0$. In contrast, the mean error force is not necessarily zero in a
+heterogeneous system:
 \begin{align} \label{eqn:tmp3} %\nonumber
@@
   =
-  \int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r'
-\end{align}
-Where $\rho(\v r)$ denotes the particle number density at the position
+  \int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r',
+\end{align}
+where $\rho(\v r)$ denotes the particle number density at the position
 $\v r$, and is periodically extended to $\mathbb R^3$. And notice the
 error force implicitly depends on the cut-off radius used for the
-interaction.
-
-The widely accepted definition of the force error is the \emph{root mean
-square} (RMS) \emph{error}, namely the square root of the second moment of the
-error force is $\mathcal E(\v r) = \sqrt{\langle\vert\Delta\v F(\v
-  r)\vert^2\rangle}$, which can be calculate by
+interaction calculation.
+
+The widely accepted definition of the force error is the \emph{root
+  mean square} (RMS) \emph{error}, which the square root of the second
+moment of the error force $\mathcal E(\v r) =
+\sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$. It can be
+calculate by
 \begin{align} \nonumber
@@
   \,&
-  \int_{\mathbb R^3\times\mathbb R^3}\v F^c(\v r - \v r')\cdot\v F^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r'',
+  \int_{\mathbb R^3\times\mathbb R^3}\v F^c(\v r - \v r')\cdot\v F^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
 \end{align}
 The density $\rho(\v r')$ and the pair density $\rho(\v r', \v r'')$
-are related to the probability density $p(\v r')$ and pair probability
-density $p(\v r', \v r'')$ by
+(also extended to $\mathbb R^3$) are related to the probability
+density $p(\v r')$ and pair probability density $p(\v r', \v r'')$ by
 \begin{align}
@@
 \end{align}
-The pair density is also periodically extented to the whole space $\mathbb
-R^3$.
 % The problem now this how to discretize the integrals in
@@
 % formulus, we have:
-Now, let
+Notice
 \begin{align} \nonumber
@@
   &= \frac{N-1}N \rho(\v r')\rho(\v r'') + C (\v r', \v r'')\\ \label{eqn:tmp7}
-  &\approx \rho(\v r')\rho(\v r'') + C (\v r', \v r'')
-\end{align}
-the function
+  &\approx \rho(\v r')\rho(\v r'') + C (\v r', \v r''),
+\end{align}
+where 
 \begin{align}
@@
 \end{align}
-denotes the correlation between
-position $\v r'$ and $\v r''$. Therefore, \eqref{eqn:tmp4} becomes
+denotes the density correlation between position $\v r'$ and $\v
+r''$. Eqn. \eqref{eqn:tmp4} becomes
 \begin{align} \nonumber
@@
   = &\,
-  \mathcal E_{\textrm{homo}}(\v r) +
+  \mathcal E^2_{\textrm{homo}}(\v r) +
 %  \langle\Delta\v F(\v r)\,\rangle^2 +
-  \mathcal E_{\textrm{hetero}}(\v r) +
-  \mathcal E_{\textrm{correlation}}(\v r)
-\end{align}
-If the system is homogeneous and the correlation between particles is
-neglected, then only the first term, which is called the homogeneity
-error, is left in \eqref{eqn:tmp5}. This term is originated from the
+  \mathcal E^2_{\textrm{hetero}}(\v r) +
+  \mathcal E^2_{\textrm{correlation}}(\v r).
+\end{align}
+If the system is homogeneous and the particle-particle correlation is
+neglected, then only the first term is left in \eqref{eqn:tmp5}, so it
+is called the homogeneity error.  This term originates from the
 flucuation of the error force $\Delta\v F(\v r)$.  The second term is
-called the heterogeneity error, because it generates due to the
-density heterogeneity of the system. It is worth poining out that the
-heterogeneity error is the nothing but the squared mean error force,
-namely $\mathcal E_{\textrm{hetero}}(\v r) = \langle\Delta\v F(\v
-r)\,\rangle^2$.  The last term in \eqref{eqn:tmp5} originates from the
+called the heterogeneity error, because it stems from the density
+heterogeneity of the system. It is worth poining out that the
+heterogeneity error is the nothing but the maganitude of the mean error force,
+namely $\mathcal E_{\textrm{hetero}}(\v r) = \vert\langle\Delta\v F(\v
+r)\,\rangle\vert$.  The last term in \eqref{eqn:tmp5} originates from the
 correlation between the particles, so it is called the correlation
-error.  The correlation error involves a double integral, which
-implies that calculating this term requires more compuational cost
-than the homogeneity and heterogeneity errors. The rest of this paper
+error.
+% The correlation error involves a double integral, which
+% implies that calculating this term requires more compuational cost
+% than the homogeneity and heterogeneity errors.
+The rest of this paper
 assumes the system is far from the critical point, therefore the
@@
 
-\subsection{The fast calculation of the error estimate}\label{sec:tmp1.3}
+\subsection{Fast calculation of the error estimate}\label{sec:tmp1.3}
 
 The naive calculation of the error estimate \eqref{eqn:tmp5} requires
-the compuational cost of $\mathcal O(N^2)$. To apply the error
-estimate on-the-fly with simulation, the compuational cost should be
-reduced to at least $\mathcal O(N\log N)$.  This is achieved by
-calculating the convolutions in \eqref{eqn:tmp5} with the fast Fourier
-transform. We assume the simulation box is uniformly divided in to
-small bins.  The positions of these bins are
+a compuational cost of $\mathcal O(N^2)$. To estimate the force error
+on the fly, the compuational cost of the estimate should be reduced to
+at least $\mathcal O(N\log N)$.  This is achieved by calculating the
+convolutions in \eqref{eqn:tmp5} by the fast Fourier transform. We
+assume the simulation box is uniformly divided in to small bins.  The
+positions of these bins are
 \begin{align}
@@
 division on each direction. In the reciprocal space, a corresponding
-lettice is set up:
+lattice is set up:
 \begin{align}
@@
 error and the particles number density are assumed to be constant,
-therefore,
+then, a Fourier expansion can be obtained:
 \begin{align}\nonumber
-  \mathcal E_{\textrm{homo}}(\v r_{i_1,i_2,i_3})
-  & \approx
+  \mathcal E^2_{\textrm{homo}}(\v r_{i_1,i_2,i_3})
+  & =
   \frac1V\sum_{k_1=-\infty}^\infty\sum_{k_2=-\infty}^\infty\sum_{k_3=-\infty}^\infty
-  \hat{\mathcal E}_{\textrm{homo}}(\v k_{k_1,k_2,k_3})
+  [{\mathcal E}^2_{\textrm{homo}}]^{\wedge}(\v k_{k_1,k_2,k_3})
   % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
@@
   \bigg] \\\label{eqn:tmp13}
-  & \approx
+  & =
   \frac1V\sum_{k_1=0}^{K_1}\sum_{k_2=0}^{K_2}\sum_{k_3=0}^{K_3}
@@
   \bigg)
-  \bigg]   
-\end{align}
-here we denote the convolution kernel $\vert\v f^c(\v r)\vert^2$ by
-$K_{\textrm{homo}}(\v r)$.  Equation \eqref{eqn:tmp13} simply utilizes
-the identity: the Fourier transform of the convolution
-$K_{\textrm{homo}}\ast\rho$ is equal to the multiply of
+  \bigg].
+\end{align}
+Here we denote the convolution kernel $\vert\v f^c(\v r)\vert^2$ by
+$K_{\textrm{homo}}(\v r)$.  The second equation in \eqref{eqn:tmp13}
+holds due to the fact: the Fourier transform of the convolution
+$K_{\textrm{homo}}\ast\rho$ is equal to the multiplication of
 $\hat{K}_{\textrm{homo}}$ and $\hat\rho$.  The prime on $\v
@@
   \hat\rho(\v k_{k_1,k_2,k_3})
-  & \approx
+  & =
   \frac{V}{K_1K_2K_3}
@@
   \bigg)
-  \bigg]
+  \bigg].
 \end{align}
@@
   &=
-  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r
-\end{align}
-Most of the short-range interactions are isotropic, therefore,
+  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r.
+\end{align}
+Most of the short-range interactions are isotropic, therefore
 $K_{\textrm{homo}}(\v r) = K_{\textrm{homo}}(r)$, and
-\begin{align}
+\begin{align}\label{eqn:kernel-inte}
   \hat{K}_{\textrm{homo}}(\v k)
@@
   =
-  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr
-\end{align}
+  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr.
+\end{align}
+The last one-dimentional integral can be calculated by numerical
+integration from $r_c$ to a large upper bound, saying $R_c$. Perfact
+convergence can be achieve by using $R_c = 30\sigma$ throughout the
+paper. Since integral \eqref{eqn:kernel-inte} is independent with the
+density of the system, it can be calculated for only once and stored
+for reference.
 
@@
   \hat{\v f}^c(\v k)\,
-  \hat\rho(\v k)
-\end{align}
-where 
+  \hat\rho(\v k),
+\end{align}
+where the Fourier transform of the complementary force is given by
 \begin{align}\label{eqn:tmp18}
@@
   \int_{r_c}^\infty 2r\,u(r)\sin(2\pi kr)\,\d d\v r
-  \bigg\}
-\end{align}
-
-\subsection{The adaptive cut-off radius method}
+  \bigg\}.
+\end{align}
+
+\subsection{Adaptive cut-off radius method}
 
@@
 error is not uniformly distributed. The difference between the maximum
-and minimum error can be as large as two orders of maganitude, see
+and minimum error can be as large as more than one order of
+maganitude, in one of the cases we studied, see
 Fig. \ref{fig:tmp2}. Traditionally, a very large cut-off radius is
-used to reduce the maximum error to an acceptable level and to reach
-convergent simulation results. However, a huge amount of compuational
-effort is wasted in the low-error region. The idea of the adaptive
-cut-off radius simulation is to use larger cut-off radius for
-particles in the high-error region to control the force error, while
-to use smaller cut-off radius for particles in the low-error region to
-save compuational cost.  The vaidity of this method relies on a
+used to reduce the maximum error in the system to reach convergent
+simulation results. Therefore, a huge amount of compuational effort is
+wasted in the low-error region. The idea of the adaptive cut-off
+radius simulation is to use larger cut-off radius for particles in the
+high-error region to control the force error, while to use smaller
+cut-off radius for particles in the low-error region to save
+compuational cost.  The effectiveness of this method relies on a
 diliberated cut-off choice for each particle so that the force error
@@
 
-To make the adaptive cut-off method feasible,
+To make the adaptive cut-off method feasible, we assume
 \begin{enumerate}
@@
   particles falling in the same bin are assigned by the same cut-off
-  radius.
+  radius. In other words, the cut-off radius is chosen for each bin
+  rather than each particles.
   % The cut-off
@@
 \item The cut-off radius can only be chosen from a discrete series of
-  increasing values between a maximum cut-off radius
-  $r_c^{\textrm{max}}$ and a minimum cut-off radius
+  monotonically increasing values between a maximum 
+  $r_c^{\textrm{max}}$ and a minimum 
   $r_c^{\textrm{min}}$: $\{\,r_c^{\textrm{min}} = r_c^0 < r_c^1 <
   \cdots < r_c^{M-1} <r_c^M = r_c^{\textrm{max}}\}$.  We call it the
-  \emph{candidate set} of cut-off radii.  For convenience but not
-  necessarily, the interval between two neighboring cut-off radius in
-  uniform, which means
-  \begin{align}
-    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M
+  \emph{candidate set} of the cut-off radius.  For convenience but not
+  necessarily, the cut-off radii in the candidate set is uniformly increasing, i.e.
+  \begin{align}
+    r_c^m = r_c^0 + r_c^{\textrm{step}} m, \quad 0 \leq m \leq M.
   \end{align}
@@
 For each cut-off radius in the candidate set, the force error
-distribution $\mathcal E(\v r)$ is calculated by estimate
-\eqref{eqn:tmp5}. Notice the error is calculated on-the-fly by the
-fast algorithm described in section \ref{sec:tmp1.3}, therefore it is
+$\mathcal E(\v r)$ is calculated by estimate
+\eqref{eqn:tmp5}. Notice the error is calculated by the
+fast algorithm described in section \ref{sec:tmp1.3}, so it is
 defined on the bins.  For a predetermined error control level
 $\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius of a bin is
-choosen such that it is the smallest one that satisfying the precision
+choosen such that it is the smallest one satisfying the precision
 constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
@@
 that the cut-off radius may not be calculated at a very high
-precision, a slightly (and at most $r_c^{\textrm{step}}$) larger
+precision, a slightly (at most $r_c^{\textrm{step}}$) larger
 cut-off radius will not waste too much computational cost.  Due to the
 thermodynamic flucuation of the system density, the resulting cut-off
-distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of lattice
-position) needs to be refined by the following scheme:
+distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of bin
+position) needs to be refined for several times by the following scheme:
 \begin{align}\label{eqn:rc-refine}
@@
 \end{align}
-to catch the fluctuating interfacial region.
+so that the fluctuating large-error regions are savely covered by bins
+with large cut-off radius.
 
@@
 
-\subsection{Force correction by the mean error force}
+\subsection{Long-range Force correction}
 
@@
 \end{align}
-The mean of the corrected error force vanishes:
+This long-range correction works because it takes into the force
+contribution outside the cut-off radius. The mean of the corrected
+error force vanishes:
 \begin{align}\label{eqn:mean-fcorr}
@@
   & =
-  \mathcal E_{\textrm{homo}}(\v r) +
-  \mathcal E_{\textrm{correlation}}(\v r).
-\end{align}
-It worth noticing that the mean square error of the corrected force is
-nothing but the variance of the uncorrected  error force:
-$\langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle =
-\textrm{Var}[\Delta\v F(\v r)]$, which contains no heterogeneous
-contribution.
+  \mathcal E^2_{\textrm{homo}}(\v r) +
+  \mathcal E^2_{\textrm{correlation}}(\v r),
+\end{align}
+containing no heterogeneity error.  It worth noticing that the mean
+square error of the corrected force is nothing but the variance of the
+uncorrected error force: $\langle\vert\Delta\v F_{\textrm{corr}}(\v
+r)\vert^2\rangle = \textrm{Var}[\Delta\v F(\v r)]$, which contains no
+heterogeneous contribution.
+
+The idea of the long-range force correction is very similar to those
+proposed in earlier works~\cite{guo1997long, mecke1997molecular,
+  janecek2006long, shen2007comparative}. In these works, the density
+profile is assume to varying on only one direction, and the system is
+subdivided into slabs perpendicular to that direction to calculate the
+energy/force correction. The advantange of the our force correction is
+that it has no geometric restriction on the density profile of the
+system, so can be used in a wider range of heterogeneous simulations.
 
@@
 
-\subsection{Heterogeneous pressure corrections}
-By the cut-off method, the system lost the pressure contribution from
-the particles outside the cut-off radius.  In the homogeneous systems,
-the distribution of particles is assumed to be uniform outside the
-cut-off radius, and the pressure correction is calculated by
-integrating the virial from the cut-off to infinity.
-
-In the heterogeneous systems, the previous idea does not
-work. Instead, the pressure correction of the system are:
+\subsection{Long-range pressure corrections}
+% By the cut-off method, the system lost the pressure contribution from
+% the particles outside the cut-off radius.  In the homogeneous systems,
+% the distribution of particles is assumed to be uniform outside the
+% cut-off radius, and the pressure correction is calculated by
+% integrating the virial from the cut-off to infinity.
+
+% In the heterogeneous systems, the previous idea does not
+% work. Instead, the pressure correction of the system are:
+
+The pressure contribution outside the cut-off radius can be expressed
+by:
 \begin{align}
@@
 \end{align}
-For simplicity, let us consider the general form the the corrections:
-\begin{align}
-  Q = \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle
-\end{align}
-For the pressure correction, $K$ is replaced by $\frac{1}{2V}\v
-r\otimes\v f^c$.  By using \eqref{eqn:tmp7}, we have
+For simplicity, we denote $\frac{1}{2V}\v r\otimes\v f^c$ by $\v
+K_{\textrm{P}}$, therefore,
+% For simplicity, let us consider the general form the the corrections:
+% \begin{align}
+%   Q = \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle
+% \end{align}
+% For the pressure correction, $K$ is replaced by $\frac{1}{2V}\v
+% r\otimes\v f^c$.  By using \eqref{eqn:tmp7}, we have
 \begin{align}\nonumber
-  Q
-  &= \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle\\\nonumber
-  & = \int K(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
-  & = \int K(\v r' - \v r'')
+  \v P^c
+  &= \bigg\langle \sum_{i\neq j} \v K_{\textrm{P}}(\v r_i - \v r_j) \bigg\rangle\\\nonumber
+  & = \int \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
+  & = \int \v K_{\textrm{P}}(\v r' - \v r'')
   \big[
@@
 \end{align}
-Assuming the correlation $C(\v r', \v r'')$ vanishes, then
+Assuming the correlation term $C(\v r', \v r'')$ vanishes, then
 \begin{align} \nonumber
-  Q 
-  & = \int K(\v r' - \v r'')
+  \v P^c
+  & = \int \v K_{\textrm{P}}(\v r' - \v r'')
   \rho(\v r') \rho(\v r'') 
@@
   \Big[
-  \int K(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
+  \int \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
   \Big]
@@
 \end{align}
-
-The Fourier transform of the convolution $\int K(\v r' - \v r'')
-\rho(\v r'')\,\d d\v r''$ is identical to the product $\hat K(\v
-k)\,\hat \rho(\v k)$. In the case of pressure correction, the Fourier
-transform of $\frac{1}{2V}\v r\otimes\v f^c$ requires more efforts.
-For the isotropic short-range interactions, the $\alpha\beta$
-component of the kernel $\frac{1}{2V}\v r\otimes\v f^c$ can be written
-as
-\begin{align}
-  \frac1{2V}\{\v r\otimes\v f^c\}_{\alpha\beta} =
-  r_\alpha r_\beta \,G^c(r) \qquad \alpha, \beta = 1, 2, 3
-\end{align}
-where $G^c(r)$ is independent with the direction of $\v r$.  We list
+The Fourier transform of the convolution $\int \v K_{\textrm{P}}(\v r'
+- \v r'') \rho(\v r'')\,\d d\v r''$ is identical to the product $\hat
+{\v K}_{\textrm{P}}(\v k)\,\hat \rho(\v k)$. The Fourier transform of
+${\v K}_{\textrm{P}}$ requires more efforts, because unlike
+the convolution kernel of the homogeneity error, this kernel is 
+anisotropic.  Assuming the isotropicity of the short-range interaction,
+the $\alpha\beta$ component of this kernel can be written as
+\begin{align}
+  \{\v K_{\textrm{P}}\}_{\alpha\beta}
+  = \frac1{2V}\{\v r\otimes\v f^c\}_{\alpha\beta}
+  = \frac1{2V} r_\alpha r_\beta \,G^c(r)
+  \qquad \alpha, \beta = 1, 2, 3,
+\end{align}
+where $G^c(r) = [u^c(r)]'/r$ is isotropic.  We list
 here without proving the Fourier transform of these terms:
@@
 
-\section{Results and discussions}\label{sec:tmp2}
-
-\subsection{Liquid-vapor coexistence simulation of the Lennard-Jones fluid}\label{sec:tmp2.1}
-
-The liquid-vapor coexistence simulation is a very typical
-heterogeneous molecular system, which is widely used to study the
-phase coexistence properties, for example, the equilibrium liquid and
-vapor density, and the surface tension. The system contains 16,000
-standard Lennard-Jones particles that saperated into liquid phase in
-the center of the box and vapor phase surrounded.  The conventional
-dimensionless unit system is employed: the unit of length, energy,
-mass and time are denoted by $\epsilon$, $\sigma$, $m$ and $\tau$
-($\tau = \sigma\sqrt{m/\varepsilon}$), respectively.  All quantities
-are written in the unitless form by adding the superscript ``$\ast$''.
-For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$ and
-$P^\ast = P \sigma^3 / \epsilon$.  The MD time step {is} $\Delta
-t^\ast = 0.005$. The simulations last for $3\times 10^6$ time
-steps. The first $1\times 10^6$ steps are discarded. The quantities of
-interest are sampled every 100 time steps. The commonly used blocking
-average method~\cite{flyvbjerg1989error} is applied to estimate the
+\section{Simulation results and discussions}\label{sec:tmp2}
+
+\subsection{Liquid-vapor equilibrium}\label{sec:tmp2.1}
+
+The direct simulation of the liquid-vapor equilibrium is a very
+typical heterogeneous system, which is widely used to study the phase
+coexistence properties, for example, the equilibrium liquid and vapor
+density, and the surface tension. The system studied in the present
+paper contains 16,000 standard Lennard-Jones particles that are
+saperated into liquid phase in the center of the box and vapor phase
+surrounded, see Fig.~\ref{fig:tmp1}.  The conventional dimensionless
+unit system is employed: the unit of length, energy, mass and time are
+denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
+\sigma\sqrt{m/\varepsilon}$), respectively.  All quantities are
+written in the unitless form by adding the superscript ``$\ast$''.
+For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
+$P^\ast = P\cdot \sigma^3 / \epsilon$ and $\mathcal E^\ast = \mathcal
+E\cdot\sigma/\varepsilon$.  The MD time step {is} $\Delta t^\ast =
+0.005$. The simulations last for $3\times 10^6$ time steps. The first
+$1\times 10^6$ steps are discarded. The quantities of interest are
+sampled every 100 time steps. The blocking average
+method~\cite{flyvbjerg1989error} is applied to estimate the
 statistical uncertainty of the autocorrelated data. The NVT ensemble
@@
 \times L_y^\ast \times L_z^\ast = 150\times 21\times 21$, as shown in
-Fig. \ref{fig:tmp1}. This simulation box permit a maximum cut-off
-radius of $r_c^\ast = 10$, and eliminate the finite scale effect
-discussed in literatures \cite{orea2005oscillatory,
+Fig. \ref{fig:tmp1}. This simulation box permits a maximum cut-off
+radius of $r_c^\ast = 10$, and eliminates the finite size effect
+reported in literatures \cite{chen1995area, orea2005oscillatory,
   biscay2009calculation}. In all simulations, the maximum cut-off
-radius considered is $10$, but the reference (precise value) results
-are given by a simulation carried out in a 24,000 particles system
+radius considered is $10$, but the reference results for comparison
+are obtained by simulations carried out in a 24,000 particles system
 with simulation box $L_x^\ast \times L_y^\ast \times L_z^\ast =
@@
   \includegraphics[width=0.9\textwidth]{fig/t0.85-n16000-rc07.5uni/confout.eps}
-  \caption{The snapshot of the 16000 Lennard-Jones particle system at
-    $T^\ast=0.85$ with a uniform cut-off radius of $r_c^\ast = 7.5$.}
+  \caption{The snapshot of the 16000 Lennard-Jones particle system in
+    liquid-vapor equilibrium at $T^\ast=0.85$ with a uniform cut-off
+    radius of $r_c^\ast = 7.5$.}
   \label{fig:tmp1}
@@
 Figure \ref{fig:tmp2} presents the real RMS force error (in green
-square) in a system using a uniform cut-off raidus of $r_c^\ast =
+square and log-scaled) in a system using a uniform cut-off raidus of $r_c^\ast =
 7.5$. The number density distribution along $x$ direction is shown by
@@
 regions, form at the interfacial region.  The estimated RMS force
-error is presented in solid blue line.  The estimate follows the real
+error is presented by solid blue line.  The estimate follows the real
 error very well at the interfacial region, but slightly over estimate
@@
 is a waste to use the same cut-off radius as the interfacial
-regions. As mentioned before, the key idea is to use small cut-off
+regions. As mentioned before, the key idea is to use smaller cut-off
 radius in the bulk regions, so that the RMS force error is uniformly
 distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
-present the adapted cut-off radius in a solid red line and all errors
-in the same notation as the Fig. \ref{fig:tmp2}. The control error
+present the adapted cut-off radius by a solid red line and all errors
+by the same notations as in the Fig. \ref{fig:tmp2}. The control error
 $\mathcal E^\ast_{\textrm{C}} = 0.0045$ is the same as the maximum
 error in the uniform cut-off simulation with $r_c^\ast=7.5$. The
-cut-off distribution is refined for twice by \eqref{eqn:rc-refine}. In
-the interfacial region, the same cut-off radius as the uniform cut-off
-simulation, namely $7.5$, is reproduced.  Whereas, in the liquid and
-vapor regions, the cut-off radii are $4.75$ and $3.5$, respective,
-which is notably reduced. Considering the computational cost grows
-with $\mathcal O(r_c^3)$, the adaptive cut-off saves 75 \% and 90 \%
-computational cost in the liquid and vapor bulk regions, respectively.
-The error is uniformly distributed, except that in the liquid region,
-the real error is somewhat lower because the error estimate is not
-sharp here. In constrast with the uniform cut-off case,
-i.e. Fig. \ref{fig:tmp2}, the error estimate for the vapor region is
-very sharp. The same phenominon is observed: the homogeneity error
-dominates in the bulk regions, while the heterogeneity error dominates
-in the interfacial region.
+cut-off distribution is calculated every 20,000 time steps, and is
+refined for twice by \eqref{eqn:rc-refine}. In the interfacial
+regions, the same cut-off radius as the uniform cut-off simulation,
+namely $7.5$, is chosen from the candidate set as expected.  In the
+liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
+respective, which is notably reduced. Since the computational cost
+grows with $\mathcal O(r_c^3)$, the adaptive cut-off saves 75 \% and
+90 \% computational cost in the liquid and vapor bulk regions,
+respectively.  The error is uniformly distributed, except that in the
+liquid region, the real error is somewhat lower because the error
+estimate overestimate the real error. In constrast with the uniform
+cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
+vapor region is very sharp. The similar phenominon is observed by
+Ref.~\cite{wang2011}. The same as the uniform cut-off simuation, the
+homogeneity error dominates in the bulk regions, while the
+heterogeneity error dominates in the interfacial region.
 
@@
 In Fig. \ref{fig:tmp4}, we present the mean error force (only $x$
-component) by the red solid line. The $y$ and $z$ components of the
-mean error force is not shown because their magnitudes are negligible.
-On the left interface, the mean error force is along the positive
-direction of $x$ axis, namely poiting right.  On the right interface,
-the mean error force is of the same maganitude but poiting
-left. Therefore, the liquid density should be higher and the vapor
-density should be lower than the uniform and adaptive cut-off
-simulations.  The real error (in green square) and the homogeneity
-error (in blue solid line) are all presented in
-Fig. \ref{fig:tmp4}. Clearly the contribution of the heterogeneity
-error is successfully removed, because the estimate of homogeneity
-error follows the real error perfectly in the interfacial regions.  In
-the bulk liquid region, the homogeneity error is slightly
-overestimated, which is the same as the uniform and adaptive cut-off
-simulations.
+component) by the red solid line. The $y$ and $z$ components are not
+shown because their magnitudes are negligible.  On the left interface,
+the mean error force is along the positive direction of $x$ axis,
+namely poiting right.  On the right interface, the mean error force is
+of the same maganitude but poiting left. Therefore, the liquid density
+should be higher and the vapor density should be lower than the
+corresponding uniform cut-off simulation.  The real error (in green
+square) and the homogeneity error (in blue solid line) are all
+presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows the
+homogeneity error estimate, which implies the contribution of the
+heterogeneity error is successfully removed. In the bulk liquid
+region, the homogeneity error is slightly overestimated, which is the
+same as the uniform and adaptive cut-off simulations.
+
+% Clearly the contribution of the heterogeneity
+% error is successfully removed, because the estimate of homogeneity
+% error follows the real error perfectly in the interfacial regions.  In
+% the bulk liquid region, the homogeneity error is slightly
+% overestimated, which is the same as the uniform and adaptive cut-off
+% simulations.
 
@@
 
-We test the uniform and adaptive cut-off methods as well as the
-correction force method in the mentioned liquid vapor equilibrium
-system. The temperatures are controlled to $T^\ast = 0.70,\ 0.85,\
-1.10,\ 1.20$ by a Nos\`e-Hoover thermostat. The interested properties are
-the liquid-vapor equilibrium density and the surface tension defined
-by
+% We test the uniform and adaptive cut-off methods as well as the
+% correction force method in the mentioned liquid vapor equilibrium
+% system.
+
+To extensively test the effectiveness of the proposed adaptive cut-off
+and long-range force correction methods, we perform simulations at
+$T^\ast = 0.70,\ 0.85,\ 1.10,\ 1.20$.  We test the liquid-vapor
+equilibrium density and the surface tension defined by
 \begin{align}
@@
   \,\bigg]
-  \,\d dx
-\end{align}
-where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
+  \,\d dx.
+\end{align}
+Where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
 pressure. The convergence of the properties of interest with respect
@@
 \end{figure}
-
-In the Fig. \ref{fig:tmp5}, the convergence of the equilibrium density
-is investigated. The red, green and blue points presents the results
-of uniform, adaptive and force correction simulations, respectively.
-The gas densities are connected by the solid lines, and the liquid
-densities are connected by the dashed lines for clarity. All data are
-substracted by the reference results, which are calculated by uniform
-cut-off simulations with a cut-off radius $r_c^\ast=13$.  In the
-higher temperature cases, the thermodynamic flucuation of the system
-is stronger. Therefore, the meansurement of densities are less
-accurate in higher temperature cases than in lower temperature cases.
-At $T^\ast = 0.70$, the gas density is more accurate than the liquid
-density, while at $T^\ast = 1.20$, the gas and liquid densities are of
-the same accuracy.
-
-The liquid and gas densities of the uniform and the adaptive cut-off
-methods are almost identical using the same cut-off radius. This
-observation is also true for the surface tension, see
-Fig. \ref{fig:tmp6}. This indicates that controlling the maximum of
-force error (see Tab. \ref{tab:tmp1}) and introducing larger
-homogeneous force error in the bulk liquid/gas regions will not
-disturb the accuracy of equilibrium densities and surface tension.
-The adaptive cut-off method roughly saves one half of the
-computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
-adaptive cut-off depends on the system geometry: if the work load
-mainly concentrates on the bulk phase region, the adaptive cut-off
-will save a lot computational expense. On the other hand, if the
-interfacial region is computationally intensive, the adaptive will not
-improve the efficency greatly.
-
-The force correction method presents a perfect convergence when the
-cut-off radius is equal to or larger than 5, and the result at a
-cut-off as small as 3.5 is acceptable. Comparing the results of force
-correction method at $r_c^\ast = 3.5$ and uniform cut-off radius
-method at $r_c = 7.5$, the maximum force error of the former method is
-3--5 times larger than the later (see Tab. \ref{tab:tmp1}), however,
-the measure of equilibrium densities and surface tension are
-comparable to and sometimes even better than the later (see
-Fig. \ref{fig:tmp5} and \ref{fig:tmp6}). In the force correction
-simulation, the heterogeneity error is screened out and the force
-error term is dominated by the homogeneity error. And in the uniform
-cut-off simulation the force error is dominated by the heterogeneity
-error in the interfacial regions. Therefore, the homogeneity error and
-heterogeneity error play different roles in the simulations.  The
-heterogeneity error stems from the non-vanishing value of the mean
-error force, which is alway pointing at one certain direction (the
-same direction as the low-to-high density jump), see
-Fig. \ref{fig:tmp4} for example. The homogeneity error is actually the
-variation of the corrected error force that may be cancelled by itself
-in a long time. The reason is the corrected error force has a
-varnished mean value (see eqn. \eqref{eqn:mean-fcorr}), so it may
-point to any direction with the same possibility.  With the same
-cut-off radius, the computational cost of the force correction and
-uniform cut-off methods are nearly the same, see
-Tab. \ref{tab:tmp1}. However, the maximum force error of the force
-correction method is about one order of maganitude more precise,
-comparing with the uniform cut-off simulations.
 
@@
 
-The convergence of the surface tension with respect to the cut-off
-radius is shown in the Fig. \ref{fig:tmp6}. The color notation is the
-same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
-without heterogeneous pressure correction are connected by solid and
-dashed lines, respectively.  The reference surface tension is
-presented by the black solid lines. The heterogeneous pressure
-correction improve the surface tention measurement greatly. The
-discrepancy between the corrected and uncorrected pressure is the
-value of the correction, which decreases with increasing cut-off
-radius. However, even at $r_c^\ast=10$, the correction is not
-negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
-temperature, the statistical uncertainty gets larger, and better
-convergence is achieved at small cut-off radius.
+In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
+the equilibrium liquid/vapor densities and surface tension are
+investigated with respect to increasing cut-off radius. The red, green
+and blue points with error bars denote the results of uniform,
+adaptive and long-range force correction simulations, respectively.
+In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
+value measured by uniform cut-off simulation of $r_c^\ast = 13$.  The
+gas densities are connected by the dashed lines, and the liquid
+densities are connected by the solid lines to guide the eyes.  In
+Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
+points connected by the dashed lines) are presented with pressure
+corrected surface tension (data points connected by solid lines) and
+the reference surface tension measured by uniform cut-off simulations
+at $r_c^\ast = 13$ with pressure correction.
+
+% In the higher
+% temperature cases, the thermodynamic flucuation of the system is
+% stronger. Therefore, the meansurement of densities and surface tension
+% are less accurate.
+% At $T^\ast = 0.70$, the gas
+% density converges much faster than the liquid density, while at
+% $T^\ast = 1.20$, the gas and liquid densities almost converges at the
+% same speed, see Fig. \ref{fig:tmp5}.
+
+For all temperatures studied, the liquid and gas densities of the
+uniform and the adaptive cut-off methods are almost identical at the
+same cut-off radius. This observation is also true for the surface
+tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
+maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
+larger homogeneous force error in the bulk liquid/gas regions will not
+disturb the accuracy of the equilibrium densities and surface tension.
+The adaptive cut-off method roughly saves one half of the
+computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
+adaptive cut-off depends on the property of the system: if the bulk
+regions dominate the system, and the density difference between the
+bulk regions is big enough to produce large error in the interfacial regions,
+then the adaptive cut-off will save a lot of
+computational expense. On the other hand, if the interfacial region is
+computationally intensive, the adaptive cut-off will not improve the efficency
+greatly.
+
+For the liquid/vapor densities, the long-range force correction method
+presents a much better convergence than the uniform and adaptive
+cut-off simulations. The densities perfectly converge when the cut-off
+radius is equal to or larger than 5, and the convergence at a cut-off
+as small as 3.5 is acceptable.  With the same cut-off radius, the
+computational cost of the force correction is nearly the same as the
+uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
+time, the force accuracy is more than one order of maganitude better.
+% However, the maximum
+% force error of the force correction method is reduced by about one
+% order of maganitude.
+
+With long-range pressure correction, the convergence of the surface
+tension of all methods are greatly improved. The discrepancy between
+the corrected and uncorrected pressure is the value of the correction,
+which decreases with increasing cut-off radius. However, even at
+$r_c^\ast=10$, the correction is not negligible for $T^\ast = 0.70$
+and $T^\ast = 0.85$. At higher temperature, the statistical
+uncertainty gets larger, and better convergence is achieved at smaller
+cut-off radius.
+
+Comparing the results of the force correction method at
+$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c = 7.5$, the
+force accuracy of the former method is 3--5 times less than the later
+(see Tab. \ref{tab:tmp1}), however, the former accuracy of the
+equilibrium densities and surface tension are comparable to and
+sometimes even better than the later (see Fig. \ref{fig:tmp5} and
+\ref{fig:tmp6}).
+% In the force correction simulation, the
+% heterogeneity error is screened out and the force error term is
+% dominated by the homogeneity error. And in the uniform cut-off
+% simulation the force error is dominated by the heterogeneity error.
+Since the homogeneity error dominates in the former simulation and the
+heterogeneity error dominates in the later, the homogeneity error and
+heterogeneity error play different roles in the simulations.  The
+homogeneity error is actually the variation of the corrected error
+force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
+implies that the corrected error force may point to any direction with
+the same probability, and may be cancelled by itself in a long time
+average.  The heterogeneity error, in contrast, stems from the
+non-vanishing value of the mean error force, which is alway pointing
+at one certain direction (the same direction as the low-to-high
+density jump), and has no oppotunity to be self-cancelled.
+
+% The reason is the corrected error force has a varnished mean
+% value (, so it may point to any
+% direction with the same possibility.  With the same cut-off radius,
+% the computational cost of the force correction and uniform cut-off
+% methods are nearly the same, see Tab. \ref{tab:tmp1}. However, the
+% maximum force error of the force correction method is about one order
+% of maganitude more precise, comparing with the uniform cut-off
+% simulations.
+
+% The convergence of the surface tension with respect to the cut-off
+% radius is shown in the Fig. \ref{fig:tmp6}. The color notation is the
+% same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
+% without heterogeneous pressure correction are connected by solid and
+% dashed lines, respectively.  The reference surface tension is
+% presented by the black solid lines. The heterogeneous pressure
+% correction improve the surface tention measurement greatly. The
+% discrepancy between the corrected and uncorrected pressure is the
+% value of the correction, which decreases with increasing cut-off
+% radius. However, even at $r_c^\ast=10$, the correction is not
+% negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
+% temperature, the statistical uncertainty gets larger, and better
+% convergence is achieved at small cut-off radius.
 
@@
 
-In this section, we test the adaptive cut-off method and the force
+In this section, we test the adaptive cut-off method and the long-range force
 correction method in a dynamical problem: collision of nanoscale
@@
 properties of interests are affected by the force calculation
-precision, therefore, we will NOT investigate a broad range of
-parameters, but focus on one special case: $u^\ast = 2.2$ and $x =
-0.6$, where poor precision of force calculation will lead to wrong
-major collision modes.
+precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
+$x = 0.6$, where the major collision mode is the coalescence, and a
+poor precision of force calculation may lead to a wrong major
+collision mode.
 
@@
 In Fig. \ref{fig:tmp8} and \ref{fig:tmp9}, we present the trajectory
-of cluster $A$ and COM distance between the two clusters,
+of COM of cluster $A$ and the COM distance between the two clusters,
 respectively. Three different cut-off radii of uniform cut-off
-simulation are considered. In this case the two clusters collide and
-form one rotating cluster. It is obvious that the trajectory of
+simulation are considered. It is obvious that the trajectory of
 $r_c^\ast = 2.5$ is completely wrong: two clusters seperate after
@@
 $r_c^\ast = 5$ is the as uniform cut-off $r_c^\ast = 5$, the former
-produce better trajectory than the later. The force correction method
-that get rid of the heterogeneity error produces correct trajectory,
-but the motion along the trajectory is somewhat faster than other
-methods (see also the angular velocity in Fig. \ref{fig:tmp11}).
+produce better trajectory than the later. The long-range force
+correction method that gets rid of the heterogeneity error produces
+correct trajectory, but the motion along the trajectory is somewhat
+faster than other methods (see also the angular velocity in
+Fig. \ref{fig:tmp11}).
 

### 2011-09-29 shortRange.inhomo/writeDown/main.tex
backup

@@
 \end{align}
-This long-range correction works because it takes into the force
-contribution outside the cut-off radius. The mean of the corrected
-error force vanishes:
+In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
+is also refered as \emph{correction force} in the context of
+long-range force correction. This correction works because it takes
+into the force contribution outside the cut-off radius. The mean of
+the corrected error force vanishes:
 \begin{align}\label{eqn:mean-fcorr}
@@
 \end{align}
-The mean square error is therefore given by
+The mean square error is given by
 \begin{align} \nonumber
@@
 The idea of the long-range force correction is very similar to those
-proposed in earlier works~\cite{guo1997long, mecke1997molecular,
+proposed by earlier works~\cite{guo1997long, mecke1997molecular,
   janecek2006long, shen2007comparative}. In these works, the density
-profile is assume to varying on only one direction, and the system is
+profile is assumed varying on only one direction, and the system is
 subdivided into slabs perpendicular to that direction to calculate the
@@
 
-\subsection{Long-range pressure corrections}
+\subsection{Long-range pressure correction}
 % By the cut-off method, the system lost the pressure contribution from
@@
 
-\section{Simulation results and discussions}\label{sec:tmp2}
+\section{Testing simulations and discussions}\label{sec:tmp2}
 
@@
 typical heterogeneous system, which is widely used to study the phase
-coexistence properties, for example, the equilibrium liquid and vapor
+coexistence properties, for example, the equilibrium liquid/vapor
 density, and the surface tension. The system studied in the present
@@
 method~\cite{flyvbjerg1989error} is applied to estimate the
-statistical uncertainty of the autocorrelated data. The NVT ensemble
-is generated by the Nos\`e-Hoover thermostat~\cite{nose1984molecular,
-  hoover1985canonical}.  The size of the simulation box is $L_x^\ast
-\times L_y^\ast \times L_z^\ast = 150\times 21\times 21$, as shown in
-Fig. \ref{fig:tmp1}. This simulation box permits a maximum cut-off
-radius of $r_c^\ast = 10$, and eliminates the finite size effect
-reported in literatures \cite{chen1995area, orea2005oscillatory,
+statistical uncertainty of the autocorrelated data with 95\%
+confidence level. The NVT ensemble is generated by the Nos\`e-Hoover
+thermostat~\cite{nose1984molecular, hoover1985canonical}.  The size of
+the simulation box is $L_x^\ast \times L_y^\ast \times L_z^\ast =
+150\times 21\times 21$, which permits a maximum cut-off radius of
+$r_c^\ast = 10$, and eliminates the finite size effect reported in
+literatures \cite{chen1995area, orea2005oscillatory,
   biscay2009calculation}. In all simulations, the maximum cut-off
@@
 
-In Fig. \ref{fig:tmp4}, we present the mean error force (only $x$
+In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
 component) by the red solid line. The $y$ and $z$ components are not
 shown because their magnitudes are negligible.  On the left interface,
-the mean error force is along the positive direction of $x$ axis,
-namely poiting right.  On the right interface, the mean error force is
+the correction force is along the positive direction of $x$ axis,
+namely poiting right.  On the right interface, the correction force is
 of the same maganitude but poiting left. Therefore, the liquid density
@@
 corresponding uniform cut-off simulation.  The real error (in green
-square) and the homogeneity error (in blue solid line) are all
-presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows the
-homogeneity error estimate, which implies the contribution of the
-heterogeneity error is successfully removed. In the bulk liquid
-region, the homogeneity error is slightly overestimated, which is the
-same as the uniform and adaptive cut-off simulations.
+square) and the estimated homogeneity error (in blue solid line) are
+all presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows
+the homogeneity error across the simulation region, which implies the
+contribution of the heterogeneity error is successfully removed, or is
+at least negligible. In the bulk liquid region, the homogeneity error
+is slightly overestimated, which is the same as the uniform and
+adaptive cut-off simulations.
 
@@
   \caption{ The RMS force error distribution of the 16000
-    Lennard-Jones particle system at $T^\ast=0.85$ with force
-    corrected by the mean error force,
-    i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off radius is $r^\ast_c =
-    7.5$. The $x$ component of the mean error force is presented by
-    the solid red line. The green squares present the real error. The
-    solid blue line presents the homogeneity error. }
+    Lennard-Jones particle system at $T^\ast=0.85$ with long-range
+    force correction, i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off
+    radius is $r^\ast_c = 7.5$. The $x$ component of the correction
+    force is presented by the solid red line. The green squares
+    present the real error. The solid blue line presents the estimated
+    homogeneity error. }
   \label{fig:tmp4}
@@
     presents the results of three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the force correction (FC)
+    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
     method. }
@@
 and blue points with error bars denote the results of uniform,
-adaptive and long-range force correction simulations, respectively.
+adaptive and long-range force correction, respectively.
 In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
-value measured by uniform cut-off simulation of $r_c^\ast = 13$.  The
+value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
 gas densities are connected by the dashed lines, and the liquid
@@
 presents a much better convergence than the uniform and adaptive
-cut-off simulations. The densities perfectly converge when the cut-off
+cut-off simulations. The properties perfectly converge when the cut-off
 radius is equal to or larger than 5, and the convergence at a cut-off
@@
 
-With long-range pressure correction, the convergence of the surface
-tension of all methods are greatly improved. The discrepancy between
-the corrected and uncorrected pressure is the value of the correction,
-which decreases with increasing cut-off radius. However, even at
-$r_c^\ast=10$, the correction is not negligible for $T^\ast = 0.70$
-and $T^\ast = 0.85$. At higher temperature, the statistical
+With the long-range pressure correction, the convergence of the
+surface tension of all methods are greatly improved. The discrepancy
+between the corrected and uncorrected pressure is the value of the
+correction, which decreases with increasing cut-off radius. However,
+even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
+0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
 uncertainty gets larger, and better convergence is achieved at smaller
@@
 Comparing the results of the force correction method at
-$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c = 7.5$, the
-force accuracy of the former method is 3--5 times less than the later
-(see Tab. \ref{tab:tmp1}), however, the former accuracy of the
-equilibrium densities and surface tension are comparable to and
+$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
+force accuracy of the former method is 3--5 times worse than the later
+(see Tab. \ref{tab:tmp1}), however, the
+density and surface tension accuracies are comparable to and
 sometimes even better than the later (see Fig. \ref{fig:tmp5} and
@@
 Since the homogeneity error dominates in the former simulation and the
-heterogeneity error dominates in the later, the homogeneity error and
-heterogeneity error play different roles in the simulations.  The
-homogeneity error is actually the variation of the corrected error
+heterogeneity error dominates in the later, the above observation
+indicates different errors play different roles in the simulations.
+The homogeneity error is actually the variation of the corrected error
 force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
@@
     The maximum RMS force error and computational cost of 
-    of three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the force correction (FC) method.
+    three methods, namely the uniform cut-off
+    (URC), the adaptive cut-off (ARC) and the long-range
+    force correction (LFC) method.
     The computational cost is the number of pairwise interaction 
-    measurements performed by the program, which should be mashine-independent.
+    measurements, which should be mashine-independent.
   }\label{tab:tmp1}
@@
 Ref. \cite{kalweit2006collision} investigated a board range
-combination of velocity $u$ and impact factor $x$, and identified
+combination of the velocity $u$ and impact factor $x$, and identified
 three major collision modes: the coalescence, the streching seperation
@@
 series submodes. In this paper, we want to study the how the collision
-properties of interests are affected by the force calculation
+properties are affected by the force 
 precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
@@
 precision of force calculation is crucial in the study of collision
-dynamics. Althougth the precision of the adaptive cut-off method of
-$r_c^\ast = 5$ is the as uniform cut-off $r_c^\ast = 5$, the former
-produce better trajectory than the later. The long-range force
-correction method that gets rid of the heterogeneity error produces
+dynamics. Althougth the precision of the adaptive cut-off method with
+$r_c^\ast = 5$ is the same as uniform cut-off $r_c^\ast = 5$, the former
+produces better trajectory. The long-range force
+correction method that gets rid of the heterogeneity error also produces
 correct trajectory, but the motion along the trajectory is somewhat
@@
   \caption{The center of mass trajectory of cluster A. Uniform cut-off
-    $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off $r_c = 5.0$ and
-    force correction of $r^\ast_c = 2.5$ are investigated.  The time
-    interval between two neighboring squares on the trajectory is 4.
-  }
+    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
+    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
+    investigated.  The time interval between two neighboring squares
+    on the trajectory is 4.  }
   \label{fig:tmp8}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/dists.eps}
-  \caption{The distance between the center of mass of cluster $A$ and
-    cluster $B$ as a function of time.}
+  \includegraphics[]{fig/dists.eps}
+  \caption{The COM distance between cluster $A$ and cluster $B$ versus
+    time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
+    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
+    $r^\ast_c = 2.5$ are investigated.  }
   \label{fig:tmp9}
@@
 
-The RMS force error of $r_c^\ast = 5.0$ uniform cut-off simulation,
-the cut-off distribution of adaptive cut-off method and the magnitude
-of the mean error force are plotted in Fig. \ref{fig:tmp8}.  The
-configuration of the two clusters (colored in gray and yellow) are
-presented on the top for reference. The same as the liquid-vapor
-equilibrium simulation, the force error located at the interfacial
-region, namely the boundary of the clusters. Inside and outside the
-clusters, the error is much lower.  The maximum cut-off used in the
-adaptive cut-off simulation is 5.0, which follows the large error
-region perfectly. The large cut-off region is much border than the
-large error region, because it is refined by twice to keep track of
-the possible moving of the clusters.  The mean error force also
-follows the boundary of the colliding clusters. In the bulk region
-of the clusters, the correction force is neglectable.
+The RMS force error of uniform cut-off, the cut-off
+distribution of adaptive cut-off and the magnitude of
+the correction force of long-range force correction method
+are plotted in Fig. \ref{fig:tmp10}.  The configuration of the two
+clusters (colored in gray and yellow) are presented on top of the
+figure for reference. The same as the liquid-vapor equilibrium
+simulation, the force error dominates in the interfacial regions,
+namely the boundaries of the clusters. Inside and outside the
+clusters, the error is much lower. The cut-off distribution of the
+adaptive cut-off method is updated every 200 time steps. The third row
+of Fig. \ref{fig:tmp10} shows that the large cut-off region follows the cluster
+boundaries perfectly. It is much border than the
+large error region, because it is refined by Eqn. \eqref{eqn:rc-refine}
+to keep track of the
+possible moving of the clusters.  The correction force is calculated
+every 10 time steps. From the fourth row 
+of Fig. \ref{fig:tmp10}, it also follows the moving boundaries the colliding
+clusters. In the bulk region of the clusters, the correction force is
+neglectable. It is not efficient to calculate the correction force more
+frequently, because the it takes up 50\% of the
+total computational cost. 
+The FFTs are comparably more expensive than one step of MD simulation.
 
@@
   \includegraphics[width=0.90\textwidth]{fig/error-rcut.eps}
-  \caption{normal words}
+  \caption{The colliding clusters (the first row), the RMS force error
+    distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
+    row), the cut-off distribution of adaptive cut-off with $r_c^\ast
+    = 5.0$ (the third row) and the magenitude of long-range force
+    correction with $r_c^\ast = 2.5$ (the fourth row). The four
+    columes corresponds to snap shots taken at $t^\ast = 12,\ 24,\
+    36,\ 56$, respectively.  }
   \label{fig:tmp10}
@@
 correction result is not as precise as other simulations excluding
-uniform $r_c = 2.5$ simulation.  The value of the mean error force is
-updated every \recheck{aaa} time steps, so considering the moving of the clusters,
-it is not the up-to-date value.
+uniform $r_c = 2.5$ simulation. This probably because the value of the
+correction force is updated every 10 time steps, so considering the
+moving of the clusters, it is not the exactly up-to-date value.
 % This because the correction force is
 % not precise because it is calculated every \recheck{aaa} steps.
-In the Fig. \ref{fig:tmp12}, the angular moment, which should be
-preserved is presented. All uniform simulations preserved the angular
-moment perfectly. The angular moment of the adaptive cut-off
-simulation, which does not precisly preserve the Newton's third law,
-shows deviation but is still around the correct value. However, the
-angular moment of the force correction simulation flies away from the
-the correct value by 1 \% at $t^\ast = 130$.
+In the Fig. \ref{fig:tmp12} presents the angular moment, which should be
+preserved during the simulations. All uniform simulations
+preserve the angular moment perfectly. The angular moment of the
+adaptive cut-off simulation, which does not precisly preserve the
+Newton's third law, shows deviation but is still around the correct
+value. However, the angular moment of the force correction simulation
+deviates away from the the correct value by 1 \% at $t^\ast = 130$.
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/wy.eps}
-  \caption{normal words}
+  \includegraphics[]{fig/wy.eps}
+  \caption{The angular velocity of cluster $A$ versus time. Uniform
+    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
+    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.}
   \label{fig:tmp11}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/ly.eps}
-  \caption{normal words}
+  \includegraphics[]{fig/ly.eps}
+  \caption{The angular moment of cluster $A$ versus time. Uniform
+    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
+    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.}
   \label{fig:tmp12}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/cost.eps}
+  \caption{The computational cost versus time. Uniform
+    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
+    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.}
+  \label{fig:tmp13}
+\end{figure}
+
+The computational cost is given in Fig. \ref{fig:tmp13}, counted by
+the number of calculated pairwise interactions. The relative cost of
+the uniform cut-off method with $r_c^\ast = 2.5,\ 5.0,\ 7.5$ is
+$1:5.6:15.8$. The adaptive cut-off with $r_c^\ast = 5.0$ saves
+about 18\% computational cost comparing with the uniform cut-off
+method with $r_c^\ast = 5.0$. The adaptive cut-off method does not
+saves a lot computational cost, because the radius of the spherical
+cluster is about $13.5$, the interfacial region (with a width of 5.0)
+is roughly 3/4 of the total volume. If larger clusters are studied,
+the performance of the adaptive cut-off method will be better. The
+long-range force correction with $r_c^\ast = 2.5$ calculates the same
+number of interactions as the uniform cut-off $r_c^\ast =
+2.5$. However, as discussed before, 1/2 of the total computational
+effort is spend on calculatng the correction force. This extra expense
+is worthwhile because it improves the simulation results tramendously.
+
 \section{Conclusions}\label{sec:conclusion}

### 2011-10-08 shortRange.inhomo/writeDown/main.tex
backup, add converge.new

@@
-\documentclass[aps,pre,preprint]{revtex4}
-% \documentclass[aps,pre,twocolumn]{revtex4}
+\documentclass[aps,pre,preprint]{revtex4-1}
+% \documentclass[aps,pre,twocolumn]{revtex4-1}
 % \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
@@
 at the cut-off and the way of applying the long-range
-correction~\cite{trokhymchuk1999computer, shen2007comparative,
-  guo1997long, mecke1997molecular, janecek2006long, goujon2004monte}.
-Therefore, it is necessary to systemetically study the precision of
-the short-range interaction calculation, and to develop methods
-screening out the aforementioned cut-off artifect in the heterogeneous
-systems.
+correction~\cite{trokhymchuk1999computer, guo1997long,
+  mecke1997molecular, janecek2006long, goujon2004monte,
+  shen2007comparative}.  Therefore, it is necessary to systemetically
+study the precision of the short-range interaction calculation, and to
+develop methods screening out the aforementioned cut-off artifect in
+the heterogeneous systems.
 
@@
 
-In Fig. \ref{fig:tmp4}, we present the correction force (only $x$
-component) by the red solid line. The $y$ and $z$ components are not
-shown because their magnitudes are negligible.  On the left interface,
-the correction force is along the positive direction of $x$ axis,
-namely poiting right.  On the right interface, the correction force is
-of the same maganitude but poiting left. Therefore, the liquid density
-should be higher and the vapor density should be lower than the
-corresponding uniform cut-off simulation.  The real error (in green
-square) and the estimated homogeneity error (in blue solid line) are
-all presented in Fig. \ref{fig:tmp4}.  Cleary, the real error follows
-the homogeneity error across the simulation region, which implies the
-contribution of the heterogeneity error is successfully removed, or is
-at least negligible. In the bulk liquid region, the homogeneity error
-is slightly overestimated, which is the same as the uniform and
-adaptive cut-off simulations.
+In Fig. \ref{fig:tmp4}, the red solid line presents the $x$ component
+correction force that is calculated every 40 time steps. The $y$ and
+$z$ components are not shown because their magnitudes are negligible.
+On the left interface, the correction force is along the positive
+direction of $x$ axis, namely poiting right.  On the right interface,
+the correction force is of the same maganitude but poiting
+left. Therefore, the liquid density should be higher and the vapor
+density should be lower than the corresponding uniform cut-off
+simulation.  The real error (in green square) and the estimated
+homogeneity error (in blue solid line) are all presented in
+Fig. \ref{fig:tmp4}.  Cleary, the real error follows the homogeneity
+error across the simulation region, which implies the contribution of
+the heterogeneity error is successfully removed, or is at least
+negligible. In the bulk liquid region, the homogeneity error is
+slightly overestimated, which is the same as the uniform and adaptive
+cut-off simulations.
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
-  \caption{The convergence of the equilibrium gas and liquid density
-    with respect to the cut-off radius. All densities are substracted
-    by the reference value, namely, the liquid and vapor density
-    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
-    presents the results of three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
-    method. }
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.gas.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.liquid.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.85.gas.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.85.liquid.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.gas.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.liquid.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.gas.eps} 
+  \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.liquid.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.70.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.10.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.20.eps} 
+  \caption{The convergence of the equilibrium gas and liquid densities
+    with respect to the cut-off radius. All densities are compared
+    with the refence value (black solid line), namely, the liquid and
+    vapor densities meansured with a uniform cut-off radius
+    $r_c^\ast=13$. The gray region denotes the statistcal uncertainty
+    of the reference value.  This figure presents the results of three
+    methods, namely the uniform cut-off (URC), the adaptive cut-off
+    (ARC) and the force correction (LFC) method. }
   \label{fig:tmp5}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.70.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.85.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.10.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.20.eps} 
   \caption{The convergence of the surface tension with respect to the
@@
     methods, namely the uniform cut-off (URC), the adaptive cut-off
-    (ARC) and the force correction (FC) method.  The results with and
-    without heterogeneous pressure correction (HPC) are shown together
-    for comparison. The reference surface tensions, shown by solid
-    black lines, are measured by the uniform cut-off method with
-    $r_c^\ast=13$ using HPC.}
+    (ARC) and the long-range force correction (LFC) method.  The
+    results with and without long-range pressure correction (LPC) are
+    shown together for comparison. The reference surface tensions,
+    shown by solid black lines, are measured by the uniform cut-off
+    method with $r_c^\ast=13$ using LPC.}
   \label{fig:tmp6}
 \end{figure}
+
+\begin{table}
+  \centering
+  \caption{
+    The maximum RMS force error and computational cost of 
+    three methods, namely the uniform cut-off
+    (URC), the adaptive cut-off (ARC) and the long-range
+    force correction (LFC) method.
+    The computational cost is the number of pairwise interaction 
+    measurements, which should be mashine-independent.
+  }\label{tab:tmp1}
+  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+    & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
+    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
+    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
+    &     &\textrm{LFC} & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
+    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
+0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
+    &     &\textrm{LFC} & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
+    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
+    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
+    &     &\textrm{LFC} & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
+    & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
+    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
+    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
+    &     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
+    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
+0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
+    &     &\textrm{LFC} & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
+    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
+    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
+    &     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
+  \end{tabular*}
+  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+    & 3.5 &\textrm{LFC} & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
+    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
+    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
+    &     &\textrm{LFC} & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
+    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
+1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
+    &     &\textrm{LFC} & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
+    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
+    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
+    &     &\textrm{LFC} & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
+    & 3.5 &\textrm{LFC} & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
+    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
+    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
+    &     &\textrm{LFC} & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
+    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
+1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
+    &     &\textrm{LFC} & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
+    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
+    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
+    &     &\textrm{LFC} & $3.3\times 10^{-5}$ & 31 \\\hline\hline
+  \end{tabular*}
+\end{table}
 
@@
 and blue points with error bars denote the results of uniform,
-adaptive and long-range force correction, respectively.
-In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
-value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
-gas densities are connected by the dashed lines, and the liquid
-densities are connected by the solid lines to guide the eyes.  In
+adaptive and long-range force correction, respectively.  In
+Fig. \ref{fig:tmp5}, all densities are compared with the reference
+value measured by uniform cut-off simulations of $r_c^\ast = 13$, with
+the statistcal uncertainty denoted by the gray region. The densities
+are connected by the the solid lines to guide the eyes.  In
 Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
 points connected by the dashed lines) are presented with pressure
-corrected surface tension (data points connected by solid lines) and
-the reference surface tension measured by uniform cut-off simulations
-at $r_c^\ast = 13$ with pressure correction.
+corrected surface tension (data points connected by solid lines).  The
+reference surface tension is measured by uniform cut-off simulations
+at $r_c^\ast = 13$ with long-range pressure correction.
 
@@
 uniform and the adaptive cut-off methods are almost identical at the
-same cut-off radius. This observation is also true for the surface
-tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
-maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
-larger homogeneous force error in the bulk liquid/gas regions will not
-disturb the accuracy of the equilibrium densities and surface tension.
-The adaptive cut-off method roughly saves one half of the
-computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
-adaptive cut-off depends on the property of the system: if the bulk
-regions dominate the system, and the density difference between the
-bulk regions is big enough to produce large error in the interfacial regions,
-then the adaptive cut-off will save a lot of
+same cut-off radius, see Fig. \ref{fig:tmp5}. This observation is also
+true for the surface tension, see Fig. \ref{fig:tmp6}. This indicates
+that controlling the maximum of force error (see Tab. \ref{tab:tmp1})
+and introducing larger homogeneous force error in the bulk liquid/gas
+regions will not disturb the accuracy of the equilibrium densities and
+surface tension.  The adaptive cut-off method roughly saves one half
+of the computational cost (see Tab. \ref{tab:tmp1}). The benefit of
+the adaptive cut-off depends on the property of the system: if the
+bulk regions dominate the system, and the density difference between
+the bulk regions is big enough to produce large error in the
+interfacial regions, then the adaptive cut-off will save a lot of
 computational expense. On the other hand, if the interfacial region is
-computationally intensive, the adaptive cut-off will not improve the efficency
-greatly.
+computationally intensive, the adaptive cut-off will not improve the
+efficency greatly.
 
@@
 presents a much better convergence than the uniform and adaptive
-cut-off simulations. The properties perfectly converge when the cut-off
-radius is equal to or larger than 5, and the convergence at a cut-off
-as small as 3.5 is acceptable.  With the same cut-off radius, the
-computational cost of the force correction is nearly the same as the
-uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
-time, the force accuracy is more than one order of maganitude better.
+cut-off simulations. The properties converge when the cut-off radius is
+only 3.5.  With the same cut-off radius, the computational cost of the
+force correction is nearly the same as the uniform cut-off methods,
+see Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is
+more than one order of maganitude better.
 % However, the maximum
@@
 % order of maganitude.
-
-With the long-range pressure correction, the convergence of the
-surface tension of all methods are greatly improved. The discrepancy
-between the corrected and uncorrected pressure is the value of the
-correction, which decreases with increasing cut-off radius. However,
-even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
-0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
-uncertainty gets larger, and better convergence is achieved at smaller
-cut-off radius.
+We also observe that the liquid densities are systemetically higher
+than the reference results. This fact will be discussed later by
+comparing with literature results.
+
+The surface tension result of the force correction without pressure
+correction is slightly better than the uniform and adaptive cut-off
+methods with out pressure correction, see Fig. \ref{fig:tmp6}.  With
+the help of the long-range pressure correction, the convergence of the
+surface tension of all methods are greatly improved.  The force
+correction method converges at $r_c^\ast = 3.5$, and the
+uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0$ ($T^\ast
+= 0.70$) and at $r_c^\ast = 7.5$ ($T^\ast = 0.85,\ 1.10,\ 1.20$).  The
+discrepancy between the corrected and uncorrected tension is the
+amount of the correction, which decreases with increasing cut-off
+radius. However, even at $r_c^\ast=10$, the correction is not
+negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
+temperature, amount of correction is sometimes smaller than the
+statistcal uncertainty.
+
+We list in Tab. \ref{tab:comparison} a wide range of results reported
+by literature~\cite{janecek2006long, lotfi1992vapour,
+  errington2003evaluating, ismail2007application}, as well as our
+uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
+results for comparison. The abbreviations in the table are explained
+in the caption. The MC/LEC, MD/Ewald and our methods are direct
+simulation of the heterogeneous system. The MD/Npt+test particle and
+MC/GC-TMMC methods are simulation of homogeneous systems that do not
+have the difficulties of heterogeneity, and are believed to be more
+precise than direct simulations~\cite{shen2007comparative}.
+\begin{table}
+  \centering
+  \caption{Equilibrium densities and surface tension comparision 
+    with various literature results: Monte Carlo with long-range
+    energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
+    particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
+    grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
+    molecular dynamics with dispersion term calculated by the Ewald
+    summation (MD/Ewald)~\cite{ismail2007application}
+    and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
+    proposed by this work. The surface tensions of this work are
+    corrected by the long-range pressure correction.
+    The cut-off radius of the Ewald summation is for the real space.
+  }
+  \label{tab:comparison}
+  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
+  % \begin{tabular}{cccc|cccc}\hline\hline
+    $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
+    0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
+    0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
+    0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
+    0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
+    0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
+    0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
+    0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
+    0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
+    0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
+    0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
+    0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
+    1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
+    1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
+    1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
+    1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
+    1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
+    1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
+    1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
+    1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
+    1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
+    1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(06) & this work\\
+    1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
+    \hline\hline
+  % \end{tabular}
+  \end{tabular*}
+\end{table}
 
@@
 non-vanishing value of the mean error force, which is alway pointing
-at one certain direction (the same direction as the low-to-high
-density jump), and has no oppotunity to be self-cancelled.
+at one certain direction (the opposite direction of the density
+gradient), and has no oppotunity to be self-cancelled.
 
@@
 % satisfactorily converged at cut-off 7.5.
-
-\begin{table}
-  \centering
-  \caption{
-    The maximum RMS force error and computational cost of 
-    three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the long-range
-    force correction (LFC) method.
-    The computational cost is the number of pairwise interaction 
-    measurements, which should be mashine-independent.
-  }\label{tab:tmp1}
-  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
-    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
-    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
-    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
-    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
-0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
-    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
-    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
-    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
-    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
-    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
-    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
-    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
-    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
-    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
-0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
-    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
-    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
-    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
-    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
-  \end{tabular*}
-  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
-    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
-    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
-    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
-    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
-1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
-    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
-    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
-    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
-    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
-    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
-    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
-    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
-    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
-    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
-1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
-    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
-    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
-    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
-    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
-  \end{tabular*}
-\end{table}
 
@@
 
+In this paper, we developed the force error estimate for non-bonded
+short-range interaction in the heterogeneous system.
+
 % \newpage

### 2011-10-17 shortRange.inhomo/writeDown/main.tex
remove result of T=0.7, 1.1, 1.2

--- 2011-09-29 shortRange.inhomo/writeDown/main.tex
@@
 square error of the corrected force is nothing but the variance of the
-uncorrected error force: $\langle\vert\Delta\v F_{\textrm{corr}}(\v
-r)\vert^2\rangle = \textrm{Var}[\Delta\v F(\v r)]$, which contains no
-heterogeneous contribution.
+corrected/uncorrected error force: $\langle\vert\Delta\v
+F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
+F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$, which
+contains no heterogeneous contribution.
 
@@
   janecek2006long, shen2007comparative}. In these works, the density
-profile is assumed varying on only one direction, and the system is
-subdivided into slabs perpendicular to that direction to calculate the
-energy/force correction. The advantange of the our force correction is
-that it has no geometric restriction on the density profile of the
-system, so can be used in a wider range of heterogeneous simulations.
+profile is assumed to be heterogeneous on only one direction, and the
+system is subdivided into slabs perpendicular to that direction to
+calculate the energy/force correction. The advantange of the our force
+correction is that it has no geometric restriction on the density
+profile of the system, so can be used in a wider range of
+heterogeneous simulations.
 
@@
 
-To extensively test the effectiveness of the proposed adaptive cut-off
-and long-range force correction methods, we perform simulations at
-$T^\ast = 0.70,\ 0.85,\ 1.10,\ 1.20$.  We test the liquid-vapor
+To test the effectiveness of the proposed adaptive cut-off and
+long-range force correction methods, we measure the liquid-vapor
 equilibrium density and the surface tension defined by
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/t1.20.eps} 
-  \caption{The convergence of the equilibrium gas and liquid density
-    with respect to the cut-off radius. All densities are substracted
-    by the reference value, namely, the liquid and vapor density
-    meansured with a uniform cut-off radius $r_c^\ast=13$. This figure
-    presents the results of three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the force correction (LFC)
-    method. }
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.gas.eps} 
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.liquid.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.gas.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.liquid.eps} 
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.gas.eps} 
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.liquid.eps} 
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.gas.eps} 
+  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.liquid.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.70.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.10.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.20.eps} 
+  \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
+    liquid densities with respect to the cut-off radius. All densities
+    are compared with the refence value (black solid line), namely,
+    the liquid and vapor densities meansured with a uniform cut-off
+    radius $r_c^\ast=13$. The gray region denotes the statistcal
+    uncertainty of the reference value.  This figure presents the
+    results of three methods, namely the uniform cut-off (URC), the
+    adaptive cut-off (ARC) and the force correction (LFC) method. }
   \label{fig:tmp5}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t0.85.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.10.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge/tension.t1.20.eps} 
-  \caption{The convergence of the surface tension with respect to the
-    cut-off radius.  This figure presents the results of three
-    methods, namely the uniform cut-off (URC), the adaptive cut-off
-    (ARC) and the force correction (FC) method.  The results with and
-    without heterogeneous pressure correction (HPC) are shown together
-    for comparison. The reference surface tensions, shown by solid
-    black lines, are measured by the uniform cut-off method with
-    $r_c^\ast=13$ using HPC.}
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.70.eps} 
+  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.85.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.10.eps} 
+  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.20.eps} 
+  \caption{$T^\ast = 0.85$. The convergence of the surface tension
+    with respect to the cut-off radius.  This figure presents the
+    results of three methods, namely the uniform cut-off (URC), the
+    adaptive cut-off (ARC) and the long-range force correction (LFC)
+    method.  The results with and without long-range pressure
+    correction (LPC) are shown together for comparison. The reference
+    surface tensions, shown by solid black lines, are measured by the
+    uniform cut-off method with $r_c^\ast=13$ using LPC.}
   \label{fig:tmp6}
@@
 
+\begin{table}
+  \centering
+  \caption{
+    $T^\ast = 0.85$. The maximum RMS force error and computational cost of 
+    three methods, namely the uniform cut-off
+    (URC), the adaptive cut-off (ARC) and the long-range
+    force correction (LFC) method.
+    The computational cost is the number of pairwise interaction 
+    measurements, which should be mashine-independent.
+  }\label{tab:tmp1}
+  \begin{tabular*}{0.50\textwidth}{c|@{\extracolsep{\fill}}ccc}\hline\hline
+    $r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+     &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
+ 3.5 &\textrm{ARC} & $8.6\times 10^{-2}$ & 1.9 \\
+     &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{1-4}
+     &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
+ 5.0 &\textrm{ARC} & $2.2\times 10^{-2}$ & 4.5 \\
+     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{1-4}
+     &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
+ 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
+     &\textrm{LFC} & $2.3\times 10^{-4}$ & 24 \\\cline{1-4}
+     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
+10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
+     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
+  \end{tabular*}
+\end{table}
+
+% \begin{table}
+%   \centering
+%   \caption{
+%     The maximum RMS force error and computational cost of 
+%     three methods, namely the uniform cut-off
+%     (URC), the adaptive cut-off (ARC) and the long-range
+%     force correction (LFC) method.
+%     The computational cost is the number of pairwise interaction 
+%     measurements, which should be mashine-independent.
+%   }\label{tab:tmp1}
+%   \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+%     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+% %     & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
+% %     &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
+% %     & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
+% %     &     &\textrm{LFC} & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
+% %     &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
+% % 0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
+% %     &     &\textrm{LFC} & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
+% %     &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
+% %     &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
+% %     &     &\textrm{LFC} & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
+%     &     &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
+%     & 3.5 &\textrm{ARC} & $6.7\times 10^{-2}$ & 2.1 \\
+%     &     &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
+%     &     &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
+%     & 5.0 &\textrm{ARC} & $1.9\times 10^{-2}$ & 4.6 \\
+%     &     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
+%     &     &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
+% 0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
+%     &     &\textrm{LFC} & $2.3\times 10^{-4}$ & 24 \\\cline{2-5}
+%     &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
+%     &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
+%     &     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
+%   \end{tabular*}
+% %   \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
+% %     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
+% %     & 3.5 &\textrm{LFC} & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
+% %     &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
+% %     & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
+% %     &     &\textrm{LFC} & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
+% %     &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
+% % 1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
+% %     &     &\textrm{LFC} & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
+% %     &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
+% %     &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
+% %     &     &\textrm{LFC} & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
+% % %     & 3.5 &\textrm{LFC} & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
+% % %     &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
+% % %     & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
+% % %     &     &\textrm{LFC} & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
+% % %     &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
+% % % 1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
+% % %     &     &\textrm{LFC} & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
+% % %     &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
+% % %     &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
+% % %     &     &\textrm{LFC} & $3.3\times 10^{-5}$ & 31 \\\hline\hline
+% %   \end{tabular*}
+% \end{table}
+
 In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
 the equilibrium liquid/vapor densities and surface tension are
-investigated with respect to increasing cut-off radius. The red, green
-and blue points with error bars denote the results of uniform,
-adaptive and long-range force correction, respectively.
-In Fig. \ref{fig:tmp5}, all densities are substracted by the reference
-value measured by uniform cut-off simulations of $r_c^\ast = 13$.  The
-gas densities are connected by the dashed lines, and the liquid
-densities are connected by the solid lines to guide the eyes.  In
-Fig. \ref{fig:tmp6}, the direct measures of surface tension (data
-points connected by the dashed lines) are presented with pressure
-corrected surface tension (data points connected by solid lines) and
-the reference surface tension measured by uniform cut-off simulations
-at $r_c^\ast = 13$ with pressure correction.
+investigated with respect to the increasing cut-off radius. The red,
+green and blue points with error bars denote the results of uniform,
+adaptive cut-off methods and the long-range force correction,
+respectively.  In Fig. \ref{fig:tmp5}, all densities are compared with
+the reference value measured by the uniform cut-off simulation of
+$r_c^\ast = 13$, with the statistcal uncertainty denoted by the gray
+region. The densities are connected by the the solid lines to guide
+the eyes.  In Fig. \ref{fig:tmp6}, the direct measures of surface
+tension (data points connected by the dashed lines) are presented with
+pressure corrected surface tension (data points connected by solid
+lines).  The same as the reference densities, the reference surface
+tension is measured by uniform cut-off simulations at $r_c^\ast = 13$
+with long-range pressure correction.  Table \ref{tab:tmp1} presents
+the maximum RMS force error and the computational expense of the the
+mentioned methods at different cut-off radii. The computational cost
+is given by the average number of pairwise interactions calculated by
+the program, which is platform independent and serves as a good bench
+mark.
 
@@
 
-For all temperatures studied, the liquid and gas densities of the
-uniform and the adaptive cut-off methods are almost identical at the
-same cut-off radius. This observation is also true for the surface
+The liquid and gas densities of the uniform and the adaptive cut-off
+methods are almost identical at the same cut-off radius, see
+Fig. \ref{fig:tmp5}. This observation is also true for the surface
 tension, see Fig. \ref{fig:tmp6}. This indicates that controlling the
@@
 disturb the accuracy of the equilibrium densities and surface tension.
-The adaptive cut-off method roughly saves one half of the
-computational cost (see Tab. \ref{tab:tmp1}). The benefit of the
-adaptive cut-off depends on the property of the system: if the bulk
-regions dominate the system, and the density difference between the
-bulk regions is big enough to produce large error in the interfacial regions,
-then the adaptive cut-off will save a lot of
+The adaptive cut-off method roughly saves 1/3 -- 1/2 of the
+computational cost (see Tab. \ref{tab:tmp1}). The efficiency benefit
+of the adaptive cut-off depends on the property of the system: if the
+bulk regions dominate the system, and the heterogeneity produces large
+interfacial force error, then the adaptive cut-off will save a lot of
 computational expense. On the other hand, if the interfacial region is
-computationally intensive, the adaptive cut-off will not improve the efficency
-greatly.
-
-For the liquid/vapor densities, the long-range force correction method
-presents a much better convergence than the uniform and adaptive
-cut-off simulations. The properties perfectly converge when the cut-off
-radius is equal to or larger than 5, and the convergence at a cut-off
-as small as 3.5 is acceptable.  With the same cut-off radius, the
-computational cost of the force correction is nearly the same as the
-uniform cut-off methods, see Tab. \ref{tab:tmp1}, and at the same
-time, the force accuracy is more than one order of maganitude better.
+computationally intensive, the adaptive cut-off will not improve the
+efficency greatly.
+
+The long-range force correction method presents a much better density
+convergence than the uniform and adaptive cut-off simulations: the
+equilibrium densities converge when the cut-off radius is only 3.5,
+see Fig. \ref{fig:tmp5}. The maximum RMS force error is reduced by roughly
+one order of maganitude, comparing to the uniform and adaptive cut-off
+methods, see Tab. \ref{tab:tmp1}. The computationally cost of the
+force correction method is the same as the uniform cut-off methods at
+the same cut-off radius.
+
+% With the
+% same cut-off radius, the computational cost of the force correction is
+% nearly the same as the uniform cut-off methods, see
+% Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is more
+% than one order of maganitude better.
+
 % However, the maximum
@@
 % order of maganitude.
-
+% We also observe that the liquid densities are systemetically higher
+% than the reference results. This fact will be discussed later by
+% comparing with literature results.
+
+The surface tension result of the force correction without pressure
+correction is only slightly better than the uniform and adaptive
+cut-off methods without pressure correction, see Fig. \ref{fig:tmp6}.
 With the long-range pressure correction, the convergence of the
-surface tension of all methods are greatly improved. The discrepancy
-between the corrected and uncorrected pressure is the value of the
-correction, which decreases with increasing cut-off radius. However,
-even at $r_c^\ast=10$, the correction is not negligible for $T^\ast =
-0.70$ and $T^\ast = 0.85$. At higher temperature, the statistical
-uncertainty gets larger, and better convergence is achieved at smaller
-cut-off radius.
-
-Comparing the results of the force correction method at
-$r_c^\ast = 3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the
-force accuracy of the former method is 3--5 times worse than the later
-(see Tab. \ref{tab:tmp1}), however, the
-density and surface tension accuracies are comparable to and
-sometimes even better than the later (see Fig. \ref{fig:tmp5} and
-\ref{fig:tmp6}).
+surface tension of all methods are greatly improved.  The force
+correction method converges at $r_c^\ast = 3.5$, and the
+uniform/adaptive cut-off methods converge at $r_c^\ast = 7.5$.  The
+discrepancy between the corrected and uncorrected tension is the
+amount of the correction, which decreases with the increasing cut-off
+radius. However, even at $r_c^\ast=10$, this correction is not
+negligible.
+
+Comparing the results of the force correction method at $r_c^\ast =
+3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the force
+accuracy of the former method is 3 times worse than the later (see
+Tab. \ref{tab:tmp1}). The equilibrium density accuracy is better than
+the later, and surface tension is as good as the later (see
+Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
 % In the force correction simulation, the
@@
 heterogeneity error dominates in the later, the above observation
-indicates different errors play different roles in the simulations.
-The homogeneity error is actually the variation of the corrected error
-force that has a vanished mean, see Eqn. \eqref{eqn:mean-fcorr}. This
-implies that the corrected error force may point to any direction with
-the same probability, and may be cancelled by itself in a long time
-average.  The heterogeneity error, in contrast, stems from the
-non-vanishing value of the mean error force, which is alway pointing
-at one certain direction (the same direction as the low-to-high
-density jump), and has no oppotunity to be self-cancelled.
+indicates different natures of error play different roles in the
+simulations.  The homogeneity error is actually the variation of the
+corrected error force that has a vanished mean, see
+Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
+force may point to any direction with the same probability, and may be
+cancelled by itself in a long time average.  The heterogeneity error,
+in contrast, stems from the non-vanishing mean value of the error
+force, which is alway pointing at one certain direction (the opposite
+direction of the density gradient), and has low  oppotunity to be
+self-cancelled.
+
+% To verify our simulations, we compare our results in
+% Tab. \ref{tab:comparison} with a wide range of results reported by
+% literature~\cite{janecek2006long, lotfi1992vapour,
+%   errington2003evaluating, ismail2007application}
+
+% We list in Tab. \ref{tab:comparison} a wide range of results reported
+% by literature~\cite{janecek2006long, lotfi1992vapour,
+%   errington2003evaluating, ismail2007application}, as well as our
+% uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
+% results for comparison. The abbreviations in the table are explained
+% in the caption. The MC/LEC, MD/Ewald and our methods are direct
+% simulation of the heterogeneous system. The MD/Npt+test particle and
+% MC/GC-TMMC methods are simulation of homogeneous systems that do not
+% have the difficulties of heterogeneity, and are believed to be more
+% precise than direct simulations~\cite{shen2007comparative}.
+
+% \begin{table}
+%   \centering
+%   \caption{Equilibrium densities and surface tension comparision 
+%     with various literature results: Monte Carlo with long-range
+%     energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
+%     particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
+%     grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
+%     molecular dynamics with dispersion term calculated by the Ewald
+%     summation (MD/Ewald)~\cite{ismail2007application}
+%     and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
+%     proposed by this work. The surface tensions of this work are
+%     corrected by the long-range pressure correction.
+%     The cut-off radius of the Ewald summation is for the real space.
+%   }
+%   \label{tab:comparison}
+%   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
+%   % \begin{tabular}{cccc|cccc}\hline\hline
+%     $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
+%     0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
+%     0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
+%     0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
+%     % 0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
+%     0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
+%     % 0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
+%     0.70 & MD/LFC               & 3.5      & 0.8430(4)   & 0.00209(9)  & 1.139(16) & this work \\\hline
+%     0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
+%     0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
+%     % 0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
+%     0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
+%     % 0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
+%     0.85 & MD/LFC               & 3.5      & 0.7761(3)   & 0.00986(16) & 0.794(15) & this work\\\hline
+%     1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
+%     1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
+%     1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
+%     % 1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
+%     1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
+%     % 1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
+%     1.10 & MD/LFC               & 3.5      & 0.6411(10)   & 0.0559(6)   & 0.302(11)  & this work\\ \hline
+%     1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
+%     1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
+%     % 1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
+%     1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(6) & this work\\
+%     % 1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
+%     1.20 & MD/LFC               & 3.5      & 0.5632(14)  & 0.1002(19)  & 0.130(8) & this work\\
+%     \hline\hline
+%   % \end{tabular}
+%   \end{tabular*}
+% \end{table}
 
@@
 
-\begin{table}
-  \centering
-  \caption{
-    The maximum RMS force error and computational cost of 
-    three methods, namely the uniform cut-off
-    (URC), the adaptive cut-off (ARC) and the long-range
-    force correction (LFC) method.
-    The computational cost is the number of pairwise interaction 
-    measurements, which should be mashine-independent.
-  }\label{tab:tmp1}
-  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
-    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
-    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
-    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
-    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
-0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
-    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
-    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
-    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
-    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
-    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
-    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
-    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
-    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
-    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
-0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
-    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
-    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
-    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
-    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
-  \end{tabular*}
-  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
-    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
-    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
-    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
-    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
-1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
-    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
-    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
-    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
-    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
-    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
-    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
-    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
-    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
-    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
-1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
-    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
-    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
-    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
-    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
-  \end{tabular*}
-\end{table}
-
 % The equilibrium liquid and vapor densities with respect to
@@
 \label{sec:tmp2.2}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/collision-init/init.2.eps}
+  \caption{The initial setup of cluster $A$ and $B$. The initial
+    velocity are equal in maganitude but on opposite direction.}
+  \label{fig:tmp7}
+\end{figure}
 
@@
   \centering
-  \includegraphics[]{fig/collision-init/init.2.eps}
-  \caption{The initial setup of cluster $A$ and $B$. The initial
-    velocity are equal in maganitude but on opposite direction.}
-  \label{fig:tmp7}
+  \includegraphics[]{fig/trajs.eps}
+  \caption{The center of mass trajectory of cluster A. Uniform cut-off
+    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
+    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
+    investigated.  The time interval between two neighboring squares
+    on the trajectory is 4.  }
+  \label{fig:tmp8}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/dists.eps}
+  \caption{The COM distance between cluster $A$ and cluster $B$ versus
+    time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
+    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
+    $r^\ast_c = 2.5$ are investigated.  }
+  \label{fig:tmp9}
 \end{figure}
@@
   \centering
-  \includegraphics[]{fig/trajs.eps}
-  \caption{The center of mass trajectory of cluster A. Uniform cut-off
-    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
-    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
-    investigated.  The time interval between two neighboring squares
-    on the trajectory is 4.  }
-  \label{fig:tmp8}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/dists.eps}
-  \caption{The COM distance between cluster $A$ and cluster $B$ versus
-    time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
-    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
-    $r^\ast_c = 2.5$ are investigated.  }
-  \label{fig:tmp9}
+  \includegraphics[width=0.90\textwidth]{fig/error-rcut-ball.eps} 
+  \includegraphics[width=0.90\textwidth]{fig/error-rcut.eps}
+  \caption{The colliding clusters (the first row), the RMS force error
+    distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
+    row), the cut-off distribution of adaptive cut-off with $r_c^\ast
+    = 5.0$ (the third row) and the magenitude of long-range force
+    correction with $r_c^\ast = 2.5$ (the fourth row). The four
+    columes corresponds to snap shots taken at $t^\ast = 12,\ 24,\
+    36,\ 56$, respectively.  }
+  \label{fig:tmp10}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.90\textwidth]{fig/error-rcut-ball.eps} 
-  \includegraphics[width=0.90\textwidth]{fig/error-rcut.eps}
-  \caption{The colliding clusters (the first row), the RMS force error
-    distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
-    row), the cut-off distribution of adaptive cut-off with $r_c^\ast
-    = 5.0$ (the third row) and the magenitude of long-range force
-    correction with $r_c^\ast = 2.5$ (the fourth row). The four
-    columes corresponds to snap shots taken at $t^\ast = 12,\ 24,\
-    36,\ 56$, respectively.  }
-  \label{fig:tmp10}
+  \includegraphics[]{fig/wy.eps}
+  \caption{The angular velocity of cluster $A$ versus time. Uniform
+    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
+    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.}
+  \label{fig:tmp11}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/ly.eps}
+  \caption{The angular moment of cluster $A$ versus time. Uniform
+    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
+    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.}
+  \label{fig:tmp12}
 \end{figure}
@@
 deviates away from the the correct value by 1 \% at $t^\ast = 130$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/wy.eps}
-  \caption{The angular velocity of cluster $A$ versus time. Uniform
-    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
-    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
-    are investigated.}
-  \label{fig:tmp11}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/ly.eps}
-  \caption{The angular moment of cluster $A$ versus time. Uniform
-    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
-    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
-    are investigated.}
-  \label{fig:tmp12}
-\end{figure}
 

### 2011-10-17 shortRange.inhomo/writeDown/main.tex
add conclusion

@@
 
-\title{The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems}
+\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
 \author{Han Wang}
@@
 short-range interactions can be reduced to an acceptable level of
-$\mathcal O(N)$. The cut-off radius is a user provided algorithmetic
-parameter, so it should have NO effect on the simulation result of
-physical/chemical properties.  Therefore, it is very important to test
-the convergence of the simulation results with respect to the cut-off
-radius before collecting data and deriving conclusions. Fortunately,
+$\mathcal O(N)$.  The cut-off radius neglect all pairwise interactions
+outside the cut-off radius, so it introduces error in the interaction
+calculation. The cut-offed system could be viewed as approximation of
+the original system, therefore, it is very important to test the
+convergence of the properties under study with respect to the cut-off
+radius before deriving conclusions on the origianl system.
+
+Fortunately,
 in most homogeneous systems, a satisfactory convergence can be
@@
 contribution of the mentioned properties to infinity. 
-% The spacial heterogenety of the system in terms of particle density,
+% The spacial inhomogenety of the system in terms of particle density,
 % particle type and change distribution is very common in natrual
@@
 
-Heterogeneous systems, in which density (or atom type) changes within
-the length scale of several molecules, are more universal than
-homogeneous systems in nature. However, the direct molecular
-simulation of heterogeneous systems by the cut-off method will
-encounter non-trival difficulties that do not exist in the homogeneous
-system simulations.  The simulation results are found to converge only
-at a very large cut-off radius value~\cite{duque2004some,
-  ismail2007application}, also denpend on the energy/force continuity
-at the cut-off and the way of applying the long-range
-correction~\cite{trokhymchuk1999computer, guo1997long,
-  mecke1997molecular, janecek2006long, goujon2004monte,
+The inhomogeneous systems, in which the density of certain type of
+atom changes within the length scale of several molecules, are more
+universal in nature. However, the direct molecular simulation of
+inhomogeneous systems by the cut-off method will encounter non-trival
+difficulties that do not exist in the homogeneous system simulations.
+The simulation results are found to converge only at a very large
+cut-off radius value~\cite{duque2004some, ismail2007application}, also
+denpend on the energy/force continuity at the cut-off and the way of
+applying the long-range corrections~\cite{trokhymchuk1999computer,
+  guo1997long, mecke1997molecular, janecek2006long, goujon2004monte,
   shen2007comparative}.  Therefore, it is necessary to systemetically
@@
 develop methods screening out the aforementioned cut-off artifect in
-the heterogeneous systems.
+the inhomogeneous systems.
 
@@
 % example, the systems with long-range electrostatic interactions.  The
-% simulation results in the heterogeneous systems are found to depend on
+% simulation results in the inhomogeneous systems are found to depend on
 % a number of factors of treating the short-range interaction in the
@@
 boost the efficiency of the computation with a good control of the
-error. However, in heterogeneous systems the error study is still
+error. However, in inhomogeneous systems the error study is still
 scarce, even for the simplest cut-off method.
@@
 In this work, we develop the error estimate of the short-range force
-in heterogeneous systems. We prove that the 
-force error is comprised of a homogeneity error and a heterogeneity
+in inhomogeneous systems. We prove that the 
+force error is comprised of a homogeneity error and a inhomogeneity
 error, regardless the particle-particle correlation outside the
-cut-off radius.  In a heterogeneous system composed by several bulk
-regions, an important observation is that the heterogeneity error can
+cut-off radius.  In a inhomogeneous system composed by several bulk
+regions, an important observation is that the inhomogeneity error can
 be more than one order of maganitude larger than the homogeneity
@@
 based on the error estimate to screen out the contribution of the
-heterogeneity error, which can tremendously improve the precision of
+inhomogeneity error, which can tremendously improve the precision of
 simulation without much extra computational load. To show the
@@
 \section{Theoretical background}
-\subsection{Error estimate in a heterogeneous system}
+\subsection{Error estimate in a inhomogeneous system}
 
@@
 the single-component system can be straightforwardly extended to the
-multi-component system without substantial difficulty.  The only the
+multi-component system without any difficulty.  Only the
 force error is estimated in the present paper, because the
@@
 $\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
- These particles are interacting via a
-short-range pairwise interaction denoted by $u(\v r)$ and correspond
-force denoted by $\v f(\v r)$, with a cut-off radius $r_c > 0$.  This
-means the interaction between any pair of particles falling out of the
-cut-off radius is neglected.
+These particles are interacting via a short-range pairwise interaction
+$u(\v r)$ with a cut-off radius $r_c > 0$. The corresponding force is
+denoted by $\v f(\v r)$. 
 % An infinite cut-off radius will lead to
@@
 = 0$. In contrast, the mean error force is not necessarily zero in a
-heterogeneous system:
+inhomogeneous system:
 \begin{align} \label{eqn:tmp3} %\nonumber
@@
 The widely accepted definition of the force error is the \emph{root
-  mean square} (RMS) \emph{error}, which the square root of the second
+  mean square} (RMS) \emph{error}, which is the square root of the second
 moment of the error force $\mathcal E(\v r) =
@@
   =\,&
-  \int_{\mathbb R^3}\vert\v F^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r'
+  \int_{\mathbb R^3}\vert\v f^c(\v r - \v r')\vert^2\rho(\v r')\,\d d\v r'
   + \\\label{eqn:tmp4}
   \,&
-  \int_{\mathbb R^3\times\mathbb R^3}\v F^c(\v r - \v r')\cdot\v F^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
-\end{align}
-The density $\rho(\v r')$ and the pair density $\rho(\v r', \v r'')$
-(also extended to $\mathbb R^3$) are related to the probability
-density $p(\v r')$ and pair probability density $p(\v r', \v r'')$ by
-\begin{align}
-  \rho(\v r') &= N\,p(\v r') \\
-  \rho(\v r', \v r'') &= N(N-1)\,p(\v r', \v r'')
-\end{align}
-% The problem now this how to discretize the integrals in
-% \eqref{eqn:tmp4}. With the piecewise constant numerical integration
-% formulus, we have:
-Notice
-\begin{align} \nonumber
+  \int_{\mathbb R^3\times\mathbb R^3}\v f^c(\v r - \v r')\cdot\v f^c(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
+\end{align}
+Where  $\rho(\v r', \v r'')$ is the pair density. By using the identity
+\begin{align}  \label{eqn:tmp7}
   \rho(\v r', \v r'')
-  & = N (N-1) \,p(\v r', \v r'') \\\nonumber
-  & = N (N-1) \big\{ p(\v r')p(\v r'') + [\,p(\v r', \v r'') -  p(\v r')p(\v r'')\,]\big\} \\\nonumber
-  &= \frac{N-1}N \rho(\v r')\rho(\v r'') + C (\v r', \v r'')\\ \label{eqn:tmp7}
-  &\approx \rho(\v r')\rho(\v r'') + C (\v r', \v r''),
+  = \rho(\v r')\rho(\v r'') + C (\v r', \v r''),
 \end{align}
@@
 \begin{align}
-C (\v r', \v r'') = N (N-1) [\,p(\v r', \v r'') -  p(\v r')p(\v r'')\,]
+C (\v r', \v r'') = [\,\rho(\v r', \v r'') -  \rho(\v r')\rho(\v r'')\,]
 \end{align}
@@
 %  \langle\Delta\v F(\v r)\,\rangle^2 +
-  \mathcal E^2_{\textrm{hetero}}(\v r) +
+  \mathcal E^2_{\textrm{inhomo}}(\v r) +
   \mathcal E^2_{\textrm{correlation}}(\v r).
@@
 If the system is homogeneous and the particle-particle correlation is
-neglected, then only the first term is left in \eqref{eqn:tmp5}, so it
+neglected, then only the first term is left on the right hand side of \eqref{eqn:tmp5}, so it
 is called the homogeneity error.  This term originates from the
 flucuation of the error force $\Delta\v F(\v r)$.  The second term is
-called the heterogeneity error, because it stems from the density
-heterogeneity of the system. It is worth poining out that the
-heterogeneity error is the nothing but the maganitude of the mean error force,
-namely $\mathcal E_{\textrm{hetero}}(\v r) = \vert\langle\Delta\v F(\v
-r)\,\rangle\vert$.  The last term in \eqref{eqn:tmp5} originates from the
+called the inhomogeneity error, because it stems from the density
+inhomogeneity of the system. It is worth poining out that the
+inhomogeneity error is the nothing but the maganitude of the mean error force,
+namely $\mathcal E_{\textrm{inhomo}}(\v r) = \vert\langle\Delta\v F(\v
+r)\,\rangle\vert$.  The last term on right hand side of \eqref{eqn:tmp5} originates from the
 correlation between the particles, so it is called the correlation
@@
 % implies that calculating this term requires more compuational cost
-% than the homogeneity and heterogeneity errors.
+% than the homogeneity and inhomogeneity errors.
 The rest of this paper
-assumes the system is far from the critical point, therefore the
+assumes the 
 correlation error does not dominate in the system, and can be savely
@@
 
-The naive calculation of the error estimate \eqref{eqn:tmp5} requires
+The naive calculation of the convolutions in the error estimate \eqref{eqn:tmp5} requires
 a compuational cost of $\mathcal O(N^2)$. To estimate the force error
 on the fly, the compuational cost of the estimate should be reduced to
-at least $\mathcal O(N\log N)$.  This is achieved by calculating the
-convolutions in \eqref{eqn:tmp5} by the fast Fourier transform. We
+at least $\mathcal O(N\log N)$.  This is achieved by  using the fast Fourier transform. We
 assume the simulation box is uniformly divided in to small bins.  The
@@
 holds due to the fact: the Fourier transform of the convolution
-$K_{\textrm{homo}}\ast\rho$ is equal to the multiplication of
-$\hat{K}_{\textrm{homo}}$ and $\hat\rho$.  The prime on $\v
-k_{k_1,k_2,k_3}$ means that we should use the periodic image $k_\alpha
-- K_\alpha$ instead of $k_\alpha$ when $k_\alpha \geq K_\alpha/2$. By
-definition, the Fourier transform of the density is
+$K_{\textrm{homo}}\ast\rho$ is equal to the multiplication of Fourier transforms
+$\hat{K}_{\textrm{homo}}$ and $\hat\rho$, which are given by
+\begin{align}\label{eqn:f-kernel-homo}
+  \hat K_{\textrm{homo}}(\v k)
+  &=
+  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r,
+\end{align}
+and
 \begin{align}
@@
 \end{align}
-The Fourier transform of the homogeneity kernel is 
-\begin{align}
-  \hat K_{\textrm{homo}}(\v k)
-  &=
-  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r.
-\end{align}
-Most of the short-range interactions are isotropic, therefore
-$K_{\textrm{homo}}(\v r) = K_{\textrm{homo}}(r)$, and
+In Eqn. \eqref{eqn:tmp13}, the prime on $\v k_{k_1,k_2,k_3}$ means
+that the periodic image $k_\alpha - K_\alpha$ should use instead of
+$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.  Most of the short-range
+interactions are isotropic, i.e.  $K_{\textrm{homo}}(\v r) =
+K_{\textrm{homo}}(r)$, then the three-dimensional integral in
+Eqn. \eqref{eqn:f-kernel-homo} can be simplified to a one-dimentional
+integral:
 \begin{align}\label{eqn:kernel-inte}
@@
   =
-  \int_{\mathbb R^3}K_{\textrm{homo}}(r)e^{-2\pi i\v k\cdot\v r}\d d\v r
-  =
-  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr.
-\end{align}
-The last one-dimentional integral can be calculated by numerical
+  % \int_{\mathbb R^3}K_{\textrm{homo}}(r)e^{-2\pi i\v k\cdot\v r}\d d\v r
+  % =
+  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr,
+\end{align}
+which can be calculated by numerical
 integration from $r_c$ to a large upper bound, saying $R_c$. Perfact
-convergence can be achieve by using $R_c = 30\sigma$ throughout the
+convergence can be achieved by using $R_c = 30\sigma$ throughout the
 paper. Since integral \eqref{eqn:kernel-inte} is independent with the
@@
 % the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
-% of this heterogeneous system. The green square denotes the real RMS
+% of this inhomogeneous system. The green square denotes the real RMS
 % force error distribution. It is clear that the error form two peaks in
@@
 % constant error of the bulk liquid and the bulk vapor. The dashed and
-% the dotted blue line are the estimated homogeneity and heterogeneity
+% the dotted blue line are the estimated homogeneity and inhomogeneity
 % errors, and the solid blue line is the sum. In the bulk region, the
 % homogeneity error dominates while in the interfacial region, the
-% heterogeneity error dominates. The esitmated error matches perfactly
+% inhomogeneity error dominates. The esitmated error matches perfactly
 % with the real error at the interfacial region, but presents
@@
 
-A basic observation in a heterogeneous system is that the RMS force
+A basic observation in a inhomogeneous system is that the RMS force
 error is not uniformly distributed. The difference between the maximum
-and minimum error can be as large as more than one order of
-maganitude, in one of the cases we studied, see
-Fig. \ref{fig:tmp2}. Traditionally, a very large cut-off radius is
+and minimum error can be more than one order of
+maganitude,
+% in one of the cases we studied,
+see Fig. \ref{fig:tmp2}. Traditionally, a very large cut-off radius is
 used to reduce the maximum error in the system to reach convergent
-simulation results. Therefore, a huge amount of compuational effort is
-wasted in the low-error region. The idea of the adaptive cut-off
-radius simulation is to use larger cut-off radius for particles in the
-high-error region to control the force error, while to use smaller
-cut-off radius for particles in the low-error region to save
-compuational cost.  The effectiveness of this method relies on a
-diliberated cut-off choice for each particle so that the force error
-is uniformly distributed across the simulation region.  Unfortunately,
-the compuational expense of a naive implementation of this method is
-at least $\mathcal O(N^2\log N)$.  Becasue to determine the cut-off
-radius, we should estimate the RMS force error at least once for each
-particle, and the computational cost of each force error estimate is
-$\mathcal O(N \log N)$.
-
-% Since heterogeneity error dominate the
+simulation results~\cite{ismail2007application}. Therefore, a huge
+amount of compuational effort is wasted in the low-error region. The
+idea of the adaptive cut-off radius simulation is to use larger
+cut-off radius for particles in the high-error region to control the
+force error, while to use smaller cut-off radius for particles in the
+low-error region to save compuational cost.  The effectiveness of this
+method relies on a diliberated cut-off choice for each particle so
+that the force error is uniformly distributed across the simulation
+region.  Unfortunately, the compuational expense of a naive
+implementation of this method is at least $\mathcal O(N^2\log N)$.
+Becasue to determine the cut-off radius, we should estimate the RMS
+force error at least once for each particle, and the computational
+cost of each force error estimate is $\mathcal O(N \log N)$.
+
+% Since inhomogeneity error dominate the
 % force error of the system, such a big cutoff radius is a waste in the
@@
 \begin{enumerate}
-\item The space is divided in to small bins, the size of which is the
+\item The space is uniformly divided in to small bins, the size of which is the
   same as those mentioned in the section \ref{sec:tmp1.3}.  The
@@
   radius. In other words, the cut-off radius is chosen for each bin
-  rather than each particles.
+  rather than for each particles.
   % The cut-off
@@
 defined on the bins.  For a predetermined error control level
-$\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius of a bin is
+$\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius for a bin is
 choosen such that it is the smallest one satisfying the precision
@@
 % means the force error is a combination of a homogeneous contribution,
-% a heterogeneous contribution and a correlational contribution. The
-% heterogeneous force can be applied as a correction to the error:
+% a inhomogeneous contribution and a correlational contribution. The
+% inhomogeneous force can be applied as a correction to the error:
 % \begin{align}\label{eqn:tmp7}
-%   \v F_{\textrm{hetero}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
+%   \v F_{\textrm{inhomo}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
 % \end{align}
@@
 
-In a spacial heterogeneous system, the heterogeneity error may play a
+In a inhomogeneous system, the inhomogeneity error may play a
 dominate role in the simulation, (see examples in section
@@
 by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
-heterogeneity error is to correct the computed force by the mean error
+inhomogeneity error is to correct the computed force by the mean error
 force, namely
@@
 \end{align}
-containing no heterogeneity error.  It worth noticing that the mean
+containing no inhomogeneity contribution.  It worth noticing that the mean
 square error of the corrected force is nothing but the variance of the
@@
 F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
-F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$, which
-contains no heterogeneous contribution.
+F_{\textrm{corr}}(\v r)] = \textrm{Var}[\Delta\v F(\v r)]$.
 
@@
 proposed by earlier works~\cite{guo1997long, mecke1997molecular,
-  janecek2006long, shen2007comparative}. In these works, the density
-profile is assumed to be heterogeneous on only one direction, and the
+  janecek2006long, shen2007comparative}. In those works, the density
+profile is assumed to be inhomogeneous on only one direction, and the
 system is subdivided into slabs perpendicular to that direction to
@@
 profile of the system, so can be used in a wider range of
-heterogeneous simulations.
+inhomogeneous simulations.
 
@@
 
-% In the heterogeneous systems, the previous idea does not
+% In the inhomogeneous systems, the previous idea does not
 % work. Instead, the pressure correction of the system are:
@@
   &= \bigg\langle \sum_{i\neq j} \v K_{\textrm{P}}(\v r_i - \v r_j) \bigg\rangle\\\nonumber
-  & = \int \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
-  & = \int \v K_{\textrm{P}}(\v r' - \v r'')
+  & = \int_{\mathbb R^3\times\mathbb R^3}
+  \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
+  & = \int_{\mathbb R^3\times\mathbb R^3}
+  \v K_{\textrm{P}}(\v r' - \v r'')
   \big[
@@
   \v P^c
-  & = \int \v K_{\textrm{P}}(\v r' - \v r'')
+  & = \int_{\mathbb R^3\times\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'')
   \rho(\v r') \rho(\v r'') 
   \d d\v r'\d d\v r'' \\
-  & = \int
+  & = \int_{\mathbb R^3}
   \Big[
-  \int \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
+  \int_{\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
   \Big]
@@
 - \v r'') \rho(\v r'')\,\d d\v r''$ is identical to the product $\hat
-{\v K}_{\textrm{P}}(\v k)\,\hat \rho(\v k)$. The Fourier transform of
-${\v K}_{\textrm{P}}$ requires more efforts, because unlike
-the convolution kernel of the homogeneity error, this kernel is 
-anisotropic.  Assuming the isotropicity of the short-range interaction,
-the $\alpha\beta$ component of this kernel can be written as
+{\v K}_{\textrm{P}}(\v k)\,\hat \rho(\v k)$.
+Assuming the isotropicity of the short-range interaction,
+the $\alpha\beta$ component of $\v K_{\textrm{P}}$ can be written as
 \begin{align}
@@
 The direct simulation of the liquid-vapor equilibrium is a very
-typical heterogeneous system, which is widely used to study the phase
+typical inhomogeneous system, which is widely used to study the phase
 coexistence properties, for example, the equilibrium liquid/vapor
 density, and the surface tension. The system studied in the present
-paper contains 16,000 standard Lennard-Jones particles that are
+paper contains 16,000 identical standard Lennard-Jones particles that are
 saperated into liquid phase in the center of the box and vapor phase
@@
 literatures \cite{chen1995area, orea2005oscillatory,
-  biscay2009calculation}. In all simulations, the maximum cut-off
+  biscay2009calculation}.
+The system is divided into bins of size $1\times1\times1$ to perform the fast error
+estimate method described in section \label{sec:tmp1.3}.
+In all simulations, the maximum cut-off
 radius considered is $10$, but the reference results for comparison
@@
 the error in the bulk regions.  Two components of the force error,
-namely the homogeneity error and heterogeneity error are presented in
+namely the homogeneity error and inhomogeneity error are presented in
 Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
@@
 line, that means the homogeneity error dominates.  In the interfacial
-region, in the contrary, the heterogeneity error dominate, because the
+region, in the contrary, the inhomogeneity error dominate, because the
 dotted blue line overlaps with the solid one.
@@
     dashed blue line is the homogeneity error contribution, while the
-    dotted blue line is the heterogeneity error contribution. The
+    dotted blue line is the inhomogeneity error contribution. The
     density distribution of the system is presented by red solid line
@@
 
-The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
-method: in the bulk regions, the error is much smaller, therefore, it
-is a waste to use the same cut-off radius as the interfacial
-regions. As mentioned before, the key idea is to use smaller cut-off
+% The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
+% method: in the bulk regions, the error is much smaller, therefore, it
+% is a waste to use the same cut-off radius as the interfacial
+% regions.
+As mentioned before, the key idea of the adaptive cut-off simulation
+is to use smaller cut-off
 radius in the bulk regions, so that the RMS force error is uniformly
@@
 regions, the same cut-off radius as the uniform cut-off simulation,
-namely $7.5$, is chosen from the candidate set as expected.  In the
+namely $7.5$, is used.  In the
 liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
@@
 90 \% computational cost in the liquid and vapor bulk regions,
-respectively.  The error is uniformly distributed, except that in the
-liquid region, the real error is somewhat lower because the error
-estimate overestimate the real error. In constrast with the uniform
+respectively.  The error is uniformly distributed, except in the
+liquid region where the real error is somewhat lower.
+In constrast with the uniform
 cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
-vapor region is very sharp. The similar phenominon is observed by
+vapor region is very sharp. The similar phenominon is observed in
 Ref.~\cite{wang2011}. The same as the uniform cut-off simuation, the
 homogeneity error dominates in the bulk regions, while the
-heterogeneity error dominates in the interfacial region.
+inhomogeneity error dominates in the interfacial region.
 
@@
 error across the simulation region, which implies the contribution of
-the heterogeneity error is successfully removed, or is at least
+the inhomogeneity error is successfully removed, or is at least
 negligible. In the bulk liquid region, the homogeneity error is
@@
 
-% Clearly the contribution of the heterogeneity
+% Clearly the contribution of the inhomogeneity
 % error is successfully removed, because the estimate of homogeneity
@@
 % clear that the error is comparatively uniformly distributed in the
-% space. The estimate heterogeneity error is also dominant at the
+% space. The estimate inhomogeneity error is also dominant at the
 % interfacial region, while the homogeneous error dominants in the bulk
@@
      &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{1-4}
+ 6.0 &\textrm{URC} & $1.1\times 10^{-2}$ & 13 \\\cline{1-4}
      &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
@@
 with long-range pressure correction.  Table \ref{tab:tmp1} presents
-the maximum RMS force error and the computational expense of the the
+the maximum RMS force error and the computational expense of the
 mentioned methods at different cut-off radii. The computational cost
@@
 of the adaptive cut-off depends on the property of the system: if the
-bulk regions dominate the system, and the heterogeneity produces large
+bulk regions dominate the system, and the inhomogeneity produces large
 interfacial force error, then the adaptive cut-off will save a lot of
@@
 correction method converges at $r_c^\ast = 3.5$, and the
-uniform/adaptive cut-off methods converge at $r_c^\ast = 7.5$.  The
+uniform/adaptive cut-off methods converge at $r_c^\ast = 6.0$.  The
 discrepancy between the corrected and uncorrected tension is the
@@
 Comparing the results of the force correction method at $r_c^\ast =
-3.5$ and uniform cut-off radius method at $r_c^\ast = 7.5$, the force
-accuracy of the former method is 3 times worse than the later (see
-Tab. \ref{tab:tmp1}). The equilibrium density accuracy is better than
+3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
+accuracy of the former method is worse than the later (see
+Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than
 the later, and surface tension is as good as the later (see
@@
 % In the force correction simulation, the
-% heterogeneity error is screened out and the force error term is
+% inhomogeneity error is screened out and the force error term is
 % dominated by the homogeneity error. And in the uniform cut-off
-% simulation the force error is dominated by the heterogeneity error.
+% simulation the force error is dominated by the inhomogeneity error.
 Since the homogeneity error dominates in the former simulation and the
-heterogeneity error dominates in the later, the above observation
+inhomogeneity error dominates in the later, the above observation
 indicates different natures of error play different roles in the
@@
 force may point to any direction with the same probability, and may be
-cancelled by itself in a long time average.  The heterogeneity error,
+cancelled by itself in a long time average.  The inhomogeneity error,
 in contrast, stems from the non-vanishing mean value of the error
@@
 % in the caption. The MC/LEC, MD/Ewald and our methods are direct
-% simulation of the heterogeneous system. The MD/Npt+test particle and
+% simulation of the inhomogeneous system. The MD/Npt+test particle and
 % MC/GC-TMMC methods are simulation of homogeneous systems that do not
-% have the difficulties of heterogeneity, and are believed to be more
+% have the difficulties of inhomogeneity, and are believed to be more
 % precise than direct simulations~\cite{shen2007comparative}.
@@
 % same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
-% without heterogeneous pressure correction are connected by solid and
+% without inhomogeneous pressure correction are connected by solid and
 % dashed lines, respectively.  The reference surface tension is
-% presented by the black solid lines. The heterogeneous pressure
+% presented by the black solid lines. The inhomogeneous pressure
 % correction improve the surface tention measurement greatly. The
@@
 precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
-$x = 0.6$, where the major collision mode is the coalescence, and a
+$x^\ast = 0.6$, where the major collision mode is the coalescence, and a
 poor precision of force calculation may lead to a wrong major
@@
 produces better trajectory. The long-range force
-correction method that gets rid of the heterogeneity error also produces
+correction method that gets rid of the inhomogeneity error also produces
 correct trajectory, but the motion along the trajectory is somewhat
@@
 neglectable. It is not efficient to calculate the correction force more
-frequently, because the it takes up 50\% of the
+frequently, because
+every force correction involves FFTs that are comparatively expensive
+especially when the cut-off radius is small. 
+In the present case, FFTs take up 50\% of the
 total computational cost. 
-The FFTs are comparably more expensive than one step of MD simulation.
+% The FFTs are comparably more expensive than one step of MD simulation.
 
@@
 value. However, the angular moment of the force correction simulation
-deviates away from the the correct value by 1 \% at $t^\ast = 130$.
+deviates away from the correct value by 1 \% at $t^\ast = 130$.
 
@@
 In this paper, we developed the force error estimate for non-bonded
-short-range interaction in the heterogeneous system.
+short-range interaction in the inhomogeneous molecular system.  The
+RMS force error can be expressed by a summation of a homogeneity
+error, an inhomogeneity error and a correlation error. In the present
+paper, we only considered the cases, in which the correlation error
+dose not dominate. In an inhomogeneous system, the basic observation
+of the error distribution was that the homogeneity error dominates the
+bulk material region, whereas the inhomogeneity error dominates the
+interfacial region where the density changes within the length scale
+of several molecules. The inhomogeneity error can be more than one
+order of maganitude larger than the homogeneity error.  Two methods
+were proposed to improve the efficiency and accuracy of the
+simulation. The adaptive cut-off method uses smaller cut-off radius
+for the low-error bulk region and larger cut-off radius for the
+high-error interfacial region, so that the RMS force error is
+uniformly distributed over the simulation region. The long-range force
+correction method corrects the force computation by the mean error
+force, so that the inhomogeneity error is removed from the system.
+
+We studied the liquid-vapor equilibrium and the collision of nanoscale
+Lennard-Jones cluster to demonstrate the validity of the proposed
+methods.  All simulation results were compared with the uniform
+cut-off simulations, in which very large cut-off radii were used to
+reach the real convergence.  With the same maximum RMS force error,
+the precision of physical properties of the adaptive cut-off method
+were the same as the uniform cut-off method. From the efficiency
+point, the advantange of the adaptive cut-off method depends on the
+system: if the large bulk regions are connected by high density
+gradient interfaces, the adaptive cut-off method will save a lot
+computational cost.  In the liquid-vapor equilibrium simulation, the
+force correction method improved the force accuracy by one order of
+maganitude without a lot of extra computational expense. The physical
+properties converged at cut-off $r_c^\ast = 3.5$, whereas the uniform
+cut-off method converged at much larger cut-off radii ($r_c^\ast = 6.0$
+for surface tension and $r_c^\ast = 10.0$ for equilibrium
+densities). With nearly the same RMS force error, precision of
+equilibrium densities of the force correction simulation were much
+better than the uniform cut-off simulation.  Since the homogeneity
+error dominated the force correction and the inhomogeneity error
+dominateed the uniform cut-off simulation, we conclude the homogeneity
+error and the inhomogeneity error play different roles on the precision
+of equilibrium liquid-vapor densities.  In the collision cluster case,
+the force correction methods produced high-precision trajectory at a
+very small cut-off radius $r_c^\ast=2.5$, with which the uniform
+cut-off method was qualitatively wrong. However, due to the
+inconsistency of the cluster movment and the correction force
+computation, small deviations of angular velocity and momentum were
+observed.
 

### 2011-10-17 shortRange.inhomo/writeDown/main.tex
backup before revision

@@
 the solid red line for reference.  The error is comparatively constant
-at the bulk liquid and gas region. In contrast, two paaks, which are
+at the bulk liquid and gas region. In contrast, two peaks, which are
 more than one order of maganitude larger than the force errors in bulk
@@
 3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
-accuracy of the former method is worse than the later (see
+accuracy of the former method is a little worse than the later (see
 Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than
@@
 indicates different natures of error play different roles in the
-simulations.  The homogeneity error is actually the variation of the
+equilibrium densities.  The homogeneity error is actually the variation of the
 corrected error force that has a vanished mean, see

### 2011-10-18 shortRange.inhomo/writeDown/main.tex
backup the revise according to Luigi

--- 2011-10-17 shortRange.inhomo/writeDown/main.tex
@@
 interactions. This results in a computational cost scaling $\mathcal
-O(N^2)$ per time step, which rapidly becomes inefficient as the number
-of particles $N$ grows large. A better way is to introduce a cut-off
+O(N^2)$ per time step, which becomes rapidly inefficient as the number
+of particles $N$ grows. A better way is to introduce a cut-off
 radius, outside of which all pairwise interactions are simply
@@
 $\mathcal O(N)$.  The cut-off radius neglect all pairwise interactions
-outside the cut-off radius, so it introduces error in the interaction
-calculation. The cut-offed system could be viewed as approximation of
-the original system, therefore, it is very important to test the
-convergence of the properties under study with respect to the cut-off
-radius before deriving conclusions on the origianl system.
+outside the cut-off radius, so it introduces an error in the interaction
+calculation. Since the cut-offed system can be viewed as an approximation of
+the original system, it is very important to test the
+convergence of properties of interest as a function of the cut-off
+radius.
+% before deriving conclusions on the origianl system.
 
@@
 % system.
-
 The inhomogeneous systems, in which the density of certain type of
-atom changes within the length scale of several molecules, are more
-universal in nature. However, the direct molecular simulation of
-inhomogeneous systems by the cut-off method will encounter non-trival
-difficulties that do not exist in the homogeneous system simulations.
+atom changes within the length scale of several molecules, 
+and thus lack of uniformity, 
+the direct molecular simulation 
+by the cut-off method will encounter non-trivial
+difficulties.
 The simulation results are found to converge only at a very large
 cut-off radius value~\cite{duque2004some, ismail2007application}, also
-denpend on the energy/force continuity at the cut-off and the way of
+depend on the energy/force continuity at the cut-off and the way of
 applying the long-range corrections~\cite{trokhymchuk1999computer,
   guo1997long, mecke1997molecular, janecek2006long, goujon2004monte,
-  shen2007comparative}.  Therefore, it is necessary to systemetically
+  shen2007comparative}.  Therefore, it is necessary to systematically
 study the precision of the short-range interaction calculation, and to
-develop methods screening out the aforementioned cut-off artifect in
+develop methods for screening out the aforementioned cut-off artifact in
 the inhomogeneous systems.
@@
 in inhomogeneous systems. We prove that the 
-force error is comprised of a homogeneity error and a inhomogeneity
-error, regardless the particle-particle correlation outside the
-cut-off radius.  In a inhomogeneous system composed by several bulk
+force error is comprised of a homogeneity error and an inhomogeneity
+error, regardless of the particle-particle correlation outside the
+cut-off radius.  In an inhomogeneous system composed by several bulk
 regions, an important observation is that the inhomogeneity error can
-be more than one order of maganitude larger than the homogeneity
+be more than one order of magnitude larger than the homogeneity
 error, and plays a dominant role in the interfacial region. An
@@
 \section{Theoretical background}
-\subsection{Error estimate in a inhomogeneous system}
-
-In this paper, we only consider the single-component system. Because
-this assumption simplifies the discussion, and the error estimates for
-the single-component system can be straightforwardly extended to the
-multi-component system without any difficulty.  Only the
-force error is estimated in the present paper, because the
+\subsection{Error estimate in an inhomogeneous system}
+
+In this paper, for simplicity,
+we will consider one-component systems, but
+% we only consider the single-component system. Because
+% this assumption simplifies the discussion, and
+the error estimates for
+the one-component system can be straightforwardly extended to the
+multi-component systems.  we consider
+force error in the present paper, because the
 applications are based on molecular dynamics simulation.
@@
 \end{align}
-We measure the force error at an arbitary position in the system,
+We measure the force error at an arbitrary position in the system,
 saying $\v r$, by adding a testing particle to that position.  We
-assume all particles in the system exert forces on the testng
-particle, whereas the testing particle do NOT exert any force on the
+assume all particles in the system exert forces on the testing
+particle, whereas the testing particle does NOT exert any force on the
 system.  The exact force and the computed force (or cut-offed force)
@@
 that all periodic images of the system are considered. In a
-homogeneous system, the surounding of any particle is isotropic, so
+homogeneous system, the surrounding of any particle is isotropic, so
 the \emph{mean error force} vanishes: $\langle\Delta\v F(\v r)\rangle
-= 0$. In contrast, the mean error force is not necessarily zero in a
+= 0$. In contrast, the mean error force is not necessarily zero in an
 inhomogeneous system:
@@
 where $\rho(\v r)$ denotes the particle number density at the position
-$\v r$, and is periodically extended to $\mathbb R^3$. And notice the
+$\v r$, and is periodically extended to $\mathbb R^3$. Notice that the
 error force implicitly depends on the cut-off radius used for the
@@
 moment of the error force $\mathcal E(\v r) =
-\sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$. It can be
-calculate by
+\sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$. This is 
+calculated as:
 \begin{align} \nonumber
@@
 is called the homogeneity error.  This term originates from the
-flucuation of the error force $\Delta\v F(\v r)$.  The second term is
+fluctuation of the error force $\Delta\v F(\v r)$.  The second term is
 called the inhomogeneity error, because it stems from the density
-inhomogeneity of the system. It is worth poining out that the
-inhomogeneity error is the nothing but the maganitude of the mean error force,
+inhomogeneity of the system. It is worth pointing out that the
+inhomogeneity error is nothing but the magnitude of the mean error force,
 namely $\mathcal E_{\textrm{inhomo}}(\v r) = \vert\langle\Delta\v F(\v
@@
 assumes the 
-correlation error does not dominate in the system, and can be savely
+correlation error does not dominate in the system, and can be safely
 neglected.
@@
 The naive calculation of the convolutions in the error estimate \eqref{eqn:tmp5} requires
-a compuational cost of $\mathcal O(N^2)$. To estimate the force error
-on the fly, the compuational cost of the estimate should be reduced to
+a computational cost of $\mathcal O(N^2)$. To estimate the force error
+on the fly, the computational cost of the estimate should be reduced to
 at least $\mathcal O(N\log N)$.  This is achieved by  using the fast Fourier transform. We
@@
 \end{align}
-In Eqn. \eqref{eqn:tmp13}, the prime on $\v k_{k_1,k_2,k_3}$ means
+Note that in Eqn. \eqref{eqn:tmp13}, the prime on $\v k_{k_1,k_2,k_3}$ means
 that the periodic image $k_\alpha - K_\alpha$ should use instead of
-$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.  Most of the short-range
-interactions are isotropic, i.e.  $K_{\textrm{homo}}(\v r) =
+$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
+In Eqn. \eqref{eqn:f-kernel-homo}
+the Fourier transform is performed on $K_{\textrm{homo}}(\v r)$ rather than
+$K_{\textrm{homo}}(\v r - \v r')$.
+Most of the short-range
+interactions are isotropic, so  $K_{\textrm{homo}}(\v r) =
 K_{\textrm{homo}}(r)$, then the three-dimensional integral in
-Eqn. \eqref{eqn:f-kernel-homo} can be simplified to a one-dimentional
+Eqn. \eqref{eqn:f-kernel-homo} can be simplified to a one-dimensional
 integral:
@@
 which can be calculated by numerical
-integration from $r_c$ to a large upper bound, saying $R_c$. Perfact
+integration from $r_c$ to a large upper bound, saying $R_c$. Perfect
 convergence can be achieved by using $R_c = 30\sigma$ throughout the
-paper. Since integral \eqref{eqn:kernel-inte} is independent with the
-density of the system, it can be calculated for only once and stored
-for reference.
-
-Similarly, by \eqref{eqn:tmp3}, the Fourier mode of the the mean error
+paper. Since integral \eqref{eqn:kernel-inte} is independent of the
+density of the system, it is calculated only once and stored.
+
+Similarly, for Eqn. \eqref{eqn:tmp3}, the Fourier mode of the the mean error
 force is
@@
 
-A basic observation in a inhomogeneous system is that the RMS force
+A basic observation in an inhomogeneous system is that the RMS force
 error is not uniformly distributed. The difference between the maximum
 and minimum error can be more than one order of
-maganitude,
+magnitude
 % in one of the cases we studied,
-see Fig. \ref{fig:tmp2}. Traditionally, a very large cut-off radius is
+(see Fig. \ref{fig:tmp2}). Traditionally, a very large cut-off radius is
 used to reduce the maximum error in the system to reach convergent
 simulation results~\cite{ismail2007application}. Therefore, a huge
-amount of compuational effort is wasted in the low-error region. The
+amount of computational effort is wasted in the low-error region. The
 idea of the adaptive cut-off radius simulation is to use larger
@@
 force error, while to use smaller cut-off radius for particles in the
-low-error region to save compuational cost.  The effectiveness of this
-method relies on a diliberated cut-off choice for each particle so
+low-error region to save computational cost.  The effectiveness of this
+method relies on a deliberated cut-off choice for each particle so
 that the force error is uniformly distributed across the simulation
-region.  Unfortunately, the compuational expense of a naive
+region.  Unfortunately, the computational expense of a naive
 implementation of this method is at least $\mathcal O(N^2\log N)$.
-Becasue to determine the cut-off radius, we should estimate the RMS
+Because in order to determine the cut-off radius, we should estimate the RMS
 force error at least once for each particle, and the computational
@@
 
-To make the adaptive cut-off method feasible, we assume
+To make the adaptive cut-off method feasible, we assume:
 \begin{enumerate}
@@
   same as those mentioned in the section \ref{sec:tmp1.3}.  The
-  particles falling in the same bin are assigned by the same cut-off
+  particles falling in the same bin are assigned the same cut-off
   radius. In other words, the cut-off radius is chosen for each bin
@@
 For each cut-off radius in the candidate set, the force error
-$\mathcal E(\v r)$ is calculated by estimate
-\eqref{eqn:tmp5}. Notice the error is calculated by the
-fast algorithm described in section \ref{sec:tmp1.3}, so it is
+$\mathcal E(\v r)$ is calculated by the estimate Eqn.~\eqref{eqn:tmp5}.
+Notice the error is calculated by the
+fast algorithm described in section~\ref{sec:tmp1.3}, so it is
 defined on the bins.  For a predetermined error control level
 $\mathcal E_{\textrm{C}}$, a satisfactory cut-off radius for a bin is
-choosen such that it is the smallest one satisfying the precision
+chosen such that it is the smallest one satisfying the precision
 constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
@@
 cut-off radius will not waste too much computational cost.  Due to the
-thermodynamic flucuation of the system density, the resulting cut-off
+thermodynamic fluctuation of the particle density, the resulting cut-off
 distribution $r_c(\v r_{i_1,i_2,i_3})$ (as a function of bin
-position) needs to be refined for several times by the following scheme:
+position) needs to be refined by the following scheme:
 \begin{align}\label{eqn:rc-refine}
@@
 \end{align}
-so that the fluctuating large-error regions are savely covered by bins
+so that the fluctuating large-error regions are safely covered by bins
 with large cut-off radius.
@@
 % means the force error is a combination of a homogeneous contribution,
-% a inhomogeneous contribution and a correlational contribution. The
+% an inhomogeneous contribution and a correlational contribution. The
 % inhomogeneous force can be applied as a correction to the error:
@@
 
-In a inhomogeneous system, the inhomogeneity error may play a
-dominate role in the simulation, (see examples in section
-\ref{sec:tmp2}).  Since the mean error force can be calculated
-by~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
+In an inhomogeneous system, the inhomogeneity error may play a
+dominate role in the simulation, (see examples in section~\ref{sec:tmp2}).
+Since the mean error force can be calculated
+by Eqn.~\eqref{eqn:tmp17} on the fly, a simple way to screen out the
 inhomogeneity error is to correct the computed force by the mean error
@@
 long-range force correction. This correction works because it takes
-into the force contribution outside the cut-off radius. The mean of
+into account the force contribution outside the cut-off radius. The mean of
 the corrected error force vanishes:
@@
 \end{align}
-containing no inhomogeneity contribution.  It worth noticing that the mean
+containing no inhomogeneity contribution.  It is worth noticing that the mean
 square error of the corrected force is nothing but the variance of the
@@
   janecek2006long, shen2007comparative}. In those works, the density
-profile is assumed to be inhomogeneous on only one direction, and the
+profile is assumed to be inhomogeneous along one direction only, and the
 system is subdivided into slabs perpendicular to that direction to
-calculate the energy/force correction. The advantange of the our force
+calculate the energy/force correction. The advantage of our force
 correction is that it has no geometric restriction on the density
@@
   =\,& 
-  \int_{r_c}^\infty \d dr\, r^4 G(r)\,
+  \int_{r_c}^\infty \d dr\, r^4 G^c(r)\,
   \pi \sqrt{ \frac1{kr} }\,
@@
   =\,& 
-  \int_{r_c}^\infty \d dr\: \,r^4 G(r)\,\pi\,
+  \int_{r_c}^\infty \d dr\: \,r^4 G^c(r)\,\pi\,
   \sqrt{ \frac1{kr} }\,
@@
   \d dr\,
-  r^4G(r)\,\pi\,
+  r^4G^c(r)\,\pi\,
   \sqrt{\frac1{kr}}\:
@@
 paper contains 16,000 identical standard Lennard-Jones particles that are
-saperated into liquid phase in the center of the box and vapor phase
-surrounded, see Fig.~\ref{fig:tmp1}.  The conventional dimensionless
+separated into liquid phase in the center of the box and vapor phase
+surrounded (see Fig.~\ref{fig:tmp1}).  The conventional dimensionless
 unit system is employed: the unit of length, energy, mass and time are
@@
 
-Figure \ref{fig:tmp2} presents the real RMS force error (in green
-square and log-scaled) in a system using a uniform cut-off raidus of $r_c^\ast =
+Fig.~\ref{fig:tmp2} presents the real RMS force error (in green
+square and log-scaled) in a system using a uniform cut-off radius of $r_c^\ast =
 7.5$. The number density distribution along $x$ direction is shown by
 the solid red line for reference.  The error is comparatively constant
-at the bulk liquid and gas region. In contrast, two paaks, which are
-more than one order of maganitude larger than the force errors in bulk
+at the bulk liquid and gas region. In contrast, two peaks, which are
+more than one order of magnitude larger than the force errors in bulk
 regions, form at the interfacial region.  The estimated RMS force
@@
 namely the homogeneity error and inhomogeneity error are presented in
-Fig. \ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
+Fig.~\ref{fig:tmp2} by dashed and dotted blue lines, respectively.  In
 the bulk regions, the dashed blue line overlaps with the solid blue
 line, that means the homogeneity error dominates.  In the interfacial
-region, in the contrary, the inhomogeneity error dominate, because the
+region, instead, the inhomogeneity error dominate, because the
 dotted blue line overlaps with the solid one.
@@
 cut-off distribution is calculated every 20,000 time steps, and is
-refined for twice by \eqref{eqn:rc-refine}. In the interfacial
+refined twice by Eqn.~\eqref{eqn:rc-refine}. In the interfacial
 regions, the same cut-off radius as the uniform cut-off simulation,
@@
 liquid region where the real error is somewhat lower.
-In constrast with the uniform
+In contrast with the uniform
 cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
-vapor region is very sharp. The similar phenominon is observed in
-Ref.~\cite{wang2011}. The same as the uniform cut-off simuation, the
+vapor region is very sharp. The similar phenomenon is observed in
+Ref.~\cite{wang2011}. The same as the uniform cut-off simulation, the
 homogeneity error dominates in the bulk regions, while the
@@
 On the left interface, the correction force is along the positive
-direction of $x$ axis, namely poiting right.  On the right interface,
-the correction force is of the same maganitude but poiting
+direction of $x$ axis, namely pointing right.  On the right interface,
+the correction force is of the same magnitude but pointing
 left. Therefore, the liquid density should be higher and the vapor
@@
 homogeneity error (in blue solid line) are all presented in
-Fig. \ref{fig:tmp4}.  Cleary, the real error follows the homogeneity
+Fig. \ref{fig:tmp4}.  Clearly, the real error follows the homogeneity
 error across the simulation region, which implies the contribution of
@@
     liquid densities with respect to the cut-off radius. All densities
-    are compared with the refence value (black solid line), namely,
-    the liquid and vapor densities meansured with a uniform cut-off
-    radius $r_c^\ast=13$. The gray region denotes the statistcal
+    are compared with the reference value (black solid line), namely,
+    the liquid and vapor densities measured with a uniform cut-off
+    radius $r_c^\ast=13$. The gray region denotes the statistical
     uncertainty of the reference value.  This figure presents the
@@
     The computational cost is the number of pairwise interaction 
-    measurements, which should be mashine-independent.
+    measurements, which should be machine-independent.
   }\label{tab:tmp1}
@@
 the reference value measured by the uniform cut-off simulation of
-$r_c^\ast = 13$, with the statistcal uncertainty denoted by the gray
+$r_c^\ast = 13$, with the statistical uncertainty denoted by the gray
 region. The densities are connected by the the solid lines to guide
@@
 bulk regions dominate the system, and the inhomogeneity produces large
-interfacial force error, then the adaptive cut-off will save a lot of
+interfacial force error, then the adaptive cut-off will save non-negligible
 computational expense. On the other hand, if the interfacial region is
 computationally intensive, the adaptive cut-off will not improve the
-efficency greatly.
+efficiency greatly.
 
@@
 convergence than the uniform and adaptive cut-off simulations: the
-equilibrium densities converge when the cut-off radius is only 3.5,
-see Fig. \ref{fig:tmp5}. The maximum RMS force error is reduced by roughly
-one order of maganitude, comparing to the uniform and adaptive cut-off
-methods, see Tab. \ref{tab:tmp1}. The computationally cost of the
+equilibrium densities converge when the cut-off radius is only 3.5
+(see Fig.~\ref{fig:tmp5}). The maximum RMS force error is reduced by roughly
+one order of magnitude, comparing to the uniform and adaptive cut-off
+methods (see Tab. \ref{tab:tmp1}). The computationally cost of the
 force correction method is the same as the uniform cut-off methods at
@@
 % We also observe that the liquid densities are systemetically higher
-% than the reference results. This fact will be discussed later by
+% than the reference results. This fact will be discussed latter by
 % comparing with literature results.
@@
 correction is only slightly better than the uniform and adaptive
-cut-off methods without pressure correction, see Fig. \ref{fig:tmp6}.
+cut-off methods without pressure correction (see Fig. \ref{fig:tmp6}).
 With the long-range pressure correction, the convergence of the
-surface tension of all methods are greatly improved.  The force
+surface tension of all methods are largely improved.  The force
 correction method converges at $r_c^\ast = 3.5$, and the
@@
 radius. However, even at $r_c^\ast=10$, this correction is not
-negligible.
+negligible, so it is very important for the precise surface tension
+calculation.
 
@@
 3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
-accuracy of the former method is worse than the later (see
-Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than
-the later, and surface tension is as good as the later (see
+accuracy of the former method is a little worse than the latter (see
+Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than,
+and surface tension is equally good (see
 Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
@@
 Since the homogeneity error dominates in the former simulation and the
-inhomogeneity error dominates in the later, the above observation
+inhomogeneity error dominates in the latter, the above observation
 indicates different natures of error play different roles in the
-simulations.  The homogeneity error is actually the variation of the
+equilibrium densities.  The homogeneity error is actually the variation of the
 corrected error force that has a vanished mean, see
 Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
-force may point to any direction with the same probability, and may be
-cancelled by itself in a long time average.  The inhomogeneity error,
+force may point to any direction with the same probability, and may cancel
+in a long time average.  The inhomogeneity error,
 in contrast, stems from the non-vanishing mean value of the error
-force, which is alway pointing at one certain direction (the opposite
-direction of the density gradient), and has low  oppotunity to be
-self-cancelled.
+force, which is always pointing to one certain direction (the opposite
+direction of the density gradient), and has low  opportunity to be
+self-canceled.
 
@@
   \caption{The initial setup of cluster $A$ and $B$. The initial
-    velocity are equal in maganitude but on opposite direction.}
+    velocity are equal in magnitude but on opposite direction.}
   \label{fig:tmp7}
@@
 Fig. \ref{fig:tmp7}. The impact parameter $D$ is defined by the $z$
-corrdinate difference between the center of mass (COM) of the
+coordinate difference between the center of mass (COM) of the
 clusters. The unitless impact factor defined by
@@
 combination of the velocity $u$ and impact factor $x$, and identified
-three major collision modes: the coalescence, the streching seperation
+three major collision modes: the coalescence, the stretching separation
 and the shattering. The major modes were further classified into a
-series submodes. In this paper, we want to study the how the collision
+series submodes. In this paper, we want to study how the collision
 properties are affected by the force 
-precision. Therefore, we focus on one special case: $u^\ast = 2.2$ and
+precision, therefore, we focus on one special case: $u^\ast = 2.2$ and
 $x^\ast = 0.6$, where the major collision mode is the coalescence, and a
@@
 simulation are considered. It is obvious that the trajectory of
-$r_c^\ast = 2.5$ is completely wrong: two clusters seperate after
+$r_c^\ast = 2.5$ is completely wrong: two clusters separate after
 collision. The $r_c^\ast = 5.0$ trajectory is reasonably good, but the
@@
 precision of force calculation is crucial in the study of collision
-dynamics. Althougth the precision of the adaptive cut-off method with
+dynamics. Although the precision of the adaptive cut-off method with
 $r_c^\ast = 5$ is the same as uniform cut-off $r_c^\ast = 5$, the former
@@
     row), the cut-off distribution of adaptive cut-off with $r_c^\ast
-    = 5.0$ (the third row) and the magenitude of long-range force
+    = 5.0$ (the third row) and the magnitude of long-range force
     correction with $r_c^\ast = 2.5$ (the fourth row). The four
-    columes corresponds to snap shots taken at $t^\ast = 12,\ 24,\
+    columns corresponds to snap shots taken at $t^\ast = 12,\ 24,\
     36,\ 56$, respectively.  }
@@
 of Fig. \ref{fig:tmp10} shows that the large cut-off region follows the cluster
-boundaries perfectly. It is much border than the
+boundaries perfectly. It is much broader than the
 large error region, because it is refined by Eqn. \eqref{eqn:rc-refine}
@@
 every 10 time steps. From the fourth row 
-of Fig. \ref{fig:tmp10}, it also follows the moving boundaries the colliding
+of Fig. \ref{fig:tmp10}, it also follows the moving boundaries of the colliding
 clusters. In the bulk region of the clusters, the correction force is
-neglectable. It is not efficient to calculate the correction force more
+negligible. It is not efficient to calculate the correction force more
 frequently, because
@@
 
-The angular velocity is presented in Fig. \ref{fig:tmp11}. The force
+The angular velocity is presented in Fig.~\ref{fig:tmp11}. The force
 correction result is not as precise as other simulations excluding
@@
 % not precise because it is calculated every \recheck{aaa} steps.
-In the Fig. \ref{fig:tmp12} presents the angular moment, which should be
-preserved during the simulations. All uniform simulations
-preserve the angular moment perfectly. The angular moment of the
-adaptive cut-off simulation, which does not precisly preserve the
-Newton's third law, shows deviation but is still around the correct
+Fig.~\ref{fig:tmp12} presents the angular moment, which is
+preserved by all uniform cut-off simulations. The angular moment of the
+adaptive cut-off simulation, which does not precisely preserve the
+Newton's third law, shows deviation but it is still around the correct
 value. However, the angular moment of the force correction simulation
@@
 2.5$. However, as discussed before, 1/2 of the total computational
-effort is spend on calculatng the correction force. This extra expense
-is worthwhile because it improves the simulation results tramendously.
+effort is spent on calculating the correction force. This extra expense
+is worthwhile because it improves the simulation results significantly.
 
@@
 paper, we only considered the cases, in which the correlation error
-dose not dominate. In an inhomogeneous system, the basic observation
+does not dominate. In an inhomogeneous system, the basic observation
 of the error distribution was that the homogeneity error dominates the
@@
 of several molecules. The inhomogeneity error can be more than one
-order of maganitude larger than the homogeneity error.  Two methods
+order of magnitude larger than the homogeneity error.  Two methods
 were proposed to improve the efficiency and accuracy of the
@@
 cut-off simulations, in which very large cut-off radii were used to
-reach the real convergence.  With the same maximum RMS force error,
+achieve real convergence.  With the same maximum RMS force error,
 the precision of physical properties of the adaptive cut-off method
 were the same as the uniform cut-off method. From the efficiency
-point, the advantange of the adaptive cut-off method depends on the
+point of view, the advantage of the adaptive cut-off method depends on the
 system: if the large bulk regions are connected by high density
-gradient interfaces, the adaptive cut-off method will save a lot
+gradient interfaces, the adaptive cut-off method will save a large amount of
 computational cost.  In the liquid-vapor equilibrium simulation, the
 force correction method improved the force accuracy by one order of
-maganitude without a lot of extra computational expense. The physical
+magnitude without large extra computational expense. The physical
 properties converged at cut-off $r_c^\ast = 3.5$, whereas the uniform
@@
 error dominated the force correction and the inhomogeneity error
-dominateed the uniform cut-off simulation, we conclude the homogeneity
+dominated the uniform cut-off simulation, we conclude the homogeneity
 error and the inhomogeneity error play different roles on the precision
@@
 cut-off method was qualitatively wrong. However, due to the
-inconsistency of the cluster movment and the correction force
+inconsistency of the cluster movement and the correction force
 computation, small deviations of angular velocity and momentum were

### 2011-10-19 shortRange.inhomo/writeDown/main.tex
add slides

@@
 were the same as the uniform cut-off method. From the efficiency
-point of view, the advantage of the adaptive cut-off method depends on the
+point of view,
+the adaptive cut-off simulation saved 34\% -- 50\% computational cost
+in liquid-vapor simulation and 18\% in the cluster collision simulation.
+The advantage of the adaptive cut-off method depends on the
 system: if the large bulk regions are connected by high density
 gradient interfaces, the adaptive cut-off method will save a large amount of
-computational cost.  In the liquid-vapor equilibrium simulation, the
+computational cost.
+
+In the liquid-vapor equilibrium simulation, the
 force correction method improved the force accuracy by one order of
@@
 
+\section*{Acknowledgements}
+The authors gratefully thank Luigi Delle Site for for useful comments
+on the manuscript. The work of P.Z. is supported by grants from
+National Natural Science Foundation of China (20490222).
+
 % \newpage

### 2011-10-19 shortRange.inhomo/writeDown/main.tex
revise again due to Luigi, backup

@@
 % system.
-The inhomogeneous systems, in which the density of certain type of
+Instead for inhomogeneous systems, in which the density of certain type of
 atom changes within the length scale of several molecules, 
@@
 error.
-% The correlation error involves a double integral, which
-% implies that calculating this term requires more compuational cost
-% than the homogeneity and inhomogeneity errors.
+The correlation error involves a double integral, which
+implies that the calculation  requires more compuational resources
+than the homogeneity and inhomogeneity errors.
 The rest of this paper
@@
 neglected.
+It is worth pointing out that this is not always true, for example, in
+critical region where the corrlation plays an important role in the system,
+the corrlation error should be taken into account.
 
@@
 Similarly, for Eqn. \eqref{eqn:tmp3}, the Fourier mode of the the mean error
-force is
+force is (in terms of Fourier transform):
 \begin{align}\label{eqn:tmp17}
@@
 square error of the corrected force is nothing but the variance of the
-corrected/uncorrected error force: $\langle\vert\Delta\v
+error force: $\langle\vert\Delta\v
 F_{\textrm{corr}}(\v r)\vert^2\rangle = \textrm{Var}[\Delta\v
@@
 separated into liquid phase in the center of the box and vapor phase
-surrounded (see Fig.~\ref{fig:tmp1}).  The conventional dimensionless
+surrounded (see Fig.~\ref{fig:tmp1}).  The conventional Lennard-Jones
 unit system is employed: the unit of length, energy, mass and time are
@@
 \sigma\sqrt{m/\varepsilon}$), respectively.  All quantities are
-written in the unitless form by adding the superscript ``$\ast$''.
+rescaled by the Lennard-Jones units and added the superscript ``$\ast$''.
 For example, $r^\ast = r / \sigma$, $T^\ast = k_BT / \epsilon$,
@@
 interfacial force error, then the adaptive cut-off will save non-negligible
-computational expense. On the other hand, if the interfacial region is
+computational resources. On the other hand, if the interfacial region is
 computationally intensive, the adaptive cut-off will not improve the
@@
 equilibrium densities.  The homogeneity error is actually the variation of the
-corrected error force that has a vanished mean, see
-Eqn. \eqref{eqn:mean-fcorr}. This implies that the corrected error
+corrected error force with its mean equal to zero (see
+Eqn.~\eqref{eqn:mean-fcorr}). This implies that the corrected error
 force may point to any direction with the same probability, and may cancel
@@
 coordinate difference between the center of mass (COM) of the
-clusters. The unitless impact factor defined by
+clusters. The dimensionless impact factor defined by
 \begin{align}
@@
 gradient interfaces, the adaptive cut-off method will save a large amount of
-computational cost.
+computational resources.
 
@@
 error dominated the force correction and the inhomogeneity error
-dominated the uniform cut-off simulation, we conclude the homogeneity
+dominated the simulation with uniform cut-off, we conclude the homogeneity
 error and the inhomogeneity error play different roles on the precision

### 2011-10-19 shortRange.inhomo/writeDown/main.tex
revise the confusing notation in Fourier transform

@@
 \end{align}
-Here we denote the convolution kernel $\vert\v f^c(\v r)\vert^2$ by
-$K_{\textrm{homo}}(\v r)$.  The second equation in \eqref{eqn:tmp13}
-holds due to the fact: the Fourier transform of the convolution
-$K_{\textrm{homo}}\ast\rho$ is equal to the multiplication of Fourier transforms
-$\hat{K}_{\textrm{homo}}$ and $\hat\rho$, which are given by
-\begin{align}\label{eqn:f-kernel-homo}
-  \hat K_{\textrm{homo}}(\v k)
-  &=
-  \int_{\mathbb R^3}K_{\textrm{homo}}(\v r)e^{-2\pi i\v k\cdot\v r}\,\d d\v r,
-\end{align}
-and
+Here $\vert\v f^c(\v r)\vert^2$ is denoted by
+$K_{\textrm{homo}}(\v r)$.
+The wedge notation $\wedge$ means Fourier transform. The prime on $\v k_{k_1,k_2,k_3}$ means
+that the periodic image $k_\alpha - K_\alpha$ should use instead of
+$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
+The second equation in \eqref{eqn:tmp13}
+holds due to the fact:
+$[\mathcal E^2]^\wedge = [K_{\textrm{homo}}\ast\rho]^\wedge = \hat{K}_{\textrm{homo}} \times \hat\rho$. The Fourier transform of $\rho$ and $K_{\textrm{homo}}$  are
 \begin{align}
@@
   \bigg)
-  \bigg].
-\end{align}
-Note that in Eqn. \eqref{eqn:tmp13}, the prime on $\v k_{k_1,k_2,k_3}$ means
-that the periodic image $k_\alpha - K_\alpha$ should use instead of
-$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
-In Eqn. \eqref{eqn:f-kernel-homo}
-the Fourier transform is performed on $K_{\textrm{homo}}(\v r)$ rather than
-$K_{\textrm{homo}}(\v r - \v r')$.
+  \bigg],
+\end{align}
+and
+\begin{align}\label{eqn:f-kernel-homo}
+  \hat K_{\textrm{homo}}(\v k)
+  &=
+  \int_{\mathbb R^3}K_{\textrm{homo}}(\v s)e^{-2\pi i\v k\cdot\v s}\,\d d\v s.
+\end{align}
 Most of the short-range
@@
   % =
-  \int_{r_c}^\infty \frac{2 r}k\, K_{\textrm{homo}}(r) \sin(2\pi kr)\,\d dr,
+  \int_{r_c}^\infty \frac{2 s}k\, K_{\textrm{homo}}(s) \sin(2\pi ks)\,\d ds,
 \end{align}
@@
   \langle\Delta\v F\rangle^\wedge(\v k) =
-  \hat{\v f}^c(\v k)\,
+  \hat{\v f^c}(\v k)\,
   \hat\rho(\v k),
@@
 \begin{align}\label{eqn:tmp18}
-  \hat{\v f}^c(\v k) 
+  \hat{\v f^c}(\v k) 
   & = 
@@
   \bigg[\,
-  \frac{2\cos(2\pi kr)}{2\pi kr}
-  -\frac{2\sin(2\pi kr)}{(2\pi kr)^2}
+  \frac{2\cos(2\pi kr_c)}{2\pi kr_c}
+  -\frac{2\sin(2\pi kr_c)}{(2\pi kr_c)^2}
   \,\bigg] 
   -
-  \int_{r_c}^\infty 2r\,u(r)\sin(2\pi kr)\,\d d\v r
-  \bigg\}.
-\end{align}
+  \int_{r_c}^\infty 2s\,u(s)\sin(2\pi ks)\,\d ds
+  \bigg\},
+\end{align}
+where $u(r)$ is the isotropic pairwise potential.
 

### 2011-11-16 shortRange.inhomo/writeDown/main.tex
small improvments

@@
   \mathcal E^2_{\textrm{inhomo}}(\v r) +
-  \mathcal E^2_{\textrm{correlation}}(\v r).
+  \mathcal E_{\textrm{correlation}}(\v r).
 \end{align}
@@
 \end{align}
-Here $\vert\v f^c(\v r)\vert^2$ is denoted by
-$K_{\textrm{homo}}(\v r)$.
+Here $K_{\textrm{homo}}(\v r)$ denotes $\vert\v f^c(\v r)\vert^2$.
 The wedge notation $\wedge$ means Fourier transform. The prime on $\v k_{k_1,k_2,k_3}$ means
@@
 Most of the short-range
-interactions are isotropic, so  $K_{\textrm{homo}}(\v r) =
+interactions are isotropic, i.e. $K_{\textrm{homo}}(\v r) =
 K_{\textrm{homo}}(r)$, then the three-dimensional integral in
@@
 chosen such that it is the smallest one satisfying the precision
-constrain $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
+constraint $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
 E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
@@
   \mathcal E^2_{\textrm{homo}}(\v r) +
-  \mathcal E^2_{\textrm{correlation}}(\v r),
+  \mathcal E_{\textrm{correlation}}(\v r),
 \end{align}

### 2011-11-17 longRange.hetero/writeDown/main.tex
add main.tex

\documentclass[aps,pre,preprint]{revtex4-1}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\renewcommand{\v}[1]{\textbf{\textit{#1}}}
\renewcommand{\d}[1]{\textsf{#1}}

\begin{document}

\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
\author{Han Wang}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}
\author{Pingwen Zhang}
% \email{pzhang@pku.edu.cn}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}

\begin{abstract}
\end{abstract}

\maketitle

\section{Theory}
\subsection{Ewald summation}
The Ewald method divides the electrostatic interaction in to three
parts: the direct part, the reciprocal part and the correction
part. that is
\begin{equation}
E = E_{\textrm{dir}} + E_{\textrm{rec}} + E_{\textrm{corr}},
\end{equation}
where 
\begin {align}
E_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
\sum_{i,j = 1}^{N} \frac{q_iq_j \textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}
{\vert\v{r}_{ij} + \v{n}\vert} \\
E_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
\frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m) \\
 E_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
\end {align}
The distance between the two particles is denoted by $\v r_{ij} = \v
r_i - \v r_j$, where $\v r_i$ and $\v r_j$ are positions of particle
$i$ and $j$, respectively.  The lattice in the real space is denoted
by $\v n = n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, where $\v a_\alpha,
\ \alpha=1,2,3$ are box vectors. the structure factor $S(\v m)$ is
defined by
\begin{equation}\label{sm1}
S(\v m) = \sum_{j=1}^N q_j \exp (2 \pi i \v m \cdot \v r_j),
\end{equation}
where $\v m = m_1 \v a_1^\ast + m_2 \v a_2^\ast + m_3 \v a_3^\ast$ is
the reciprocal space lattice vectors. $\v a_\alpha^\ast,\ \alpha = 1,
2, 3$ are conjugate reciprocal vectors of $\v a_\alpha$, defined by
$\v a_\alpha \cdot \v a_\beta^\ast = \delta_{\alpha\beta}$. and $V =
\v a_1 \cdot \v a_2 \times \v a_3$ is the volume of the box.

Both the direct and the reciprocal parts are calculated by cut-off in
real and reciprocal space, respectively. For the reciprocal part the
cut-offed energy reads
\begin{align}
  E_{\textrm{rec}} & =
  \frac1{2\pi V}
  \sum_{
    \begin{subarray}{c}
      \vert m_\alpha\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m)   
\end{align}
where $K_\alpha$ is the number of Fourier modes used on direction
$\alpha$. For convenience, we denote
\begin{align}
  f(\v m) = \frac{\exp(-\pi^2 \v m^2 / \beta^2)}{2\pi V \v m^2}
\end{align}
The truncated reciprocal force acting on particle $i$ is
\begin{align}
  \v F(\v r_i) = - 
  q_i 
  \sum_{
    \begin{subarray}{c}
      \vert m_\alpha\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m) \,
  S(-\v m)\,
  e^{2\pi i\v m\cdot\v r_i}
\end{align}
where
\begin{align}
  \v g(\v m) = -4 \pi \v m i f(\v m)
\end{align}

\subsection{Error estimate for the reciprocal Ewald force}

In this paper, we consider the force error, bacause the applicaions
are based on the molecular dynamics simulation. We study the force
error at arbitrary position $\v r$ by adding a testing particle with
charge $q$ to $\v r$. The difference between the exact force and
calculated force (with error introduced by cut-offs) exerting on the
testing particle are denoted by $\v F(\v r)$ and $\tilde{\v F}(\v r)$,
respectively. Note that the testing particle does NOT exert any force
on the system. The difference between the exact and calculated is
called the \emph{error force} \cite{short}, and is denoted by $\Delta
\v F(\v r) = \v F(\v r) - \tilde{\v F}(\v r)$.  The error of the force
computation is defined by the \emph{root mean square (RMS)}
\emph{error}, which is the square root of the second moment of the
error force: $\mathcal E(\v r) = \sqrt{\langle\vert\Delta\v F(\v
  r)\vert^2\rangle}$.  The notation $\langle\cdot\rangle$ means
ensemble average.

Ref.~\cite{wang2010optimizing} pointed out that it
is reasonable and convenient to estimate the error for the direct and
reciprocal force part seperately. 
The direct part is a short-range
interaction in real space, the error estimate of which
is well established in \cite{short}.
The mean of the error force is
\begin{align}\label{eqn:tmp10}
  \langle\Delta\v F_{\textrm{dir}}(\v r)\rangle
  =q\, [\v K^c_{\textrm{dir}}\ast\rho_q](\v r).
\end{align}
Herein, the ``$\ast$'' notation means convolution.  The direct
convolutional kernel of the error force $\v K^c_{\textrm{dir}}(\v r)$
is defined by
\begin{align}
  \v K^c_{\textrm{dir}}(\v r) =
  \left\{
    \begin{aligned}
      &\,0, &\quad & \vert\v r\vert \leq r_c;\\
      &\frac{\textrm{erfc}(\beta\vert\v r\vert)}{\vert\v r\vert},& & \vert\v r\vert > r_c,
    \end{aligned}
  \right.
\end{align}
where $r_c$ is the cut-off radius in the real space.  The first order
charge distribution function $\rho_q$ is defined by:
\begin{align}
  \rho_q(\v r) = 
  \bigg\langle
  \sum_{j = 1}^N
  \,q_j\,\delta(\v r - \v r_j)
  \bigg\rangle.
\end{align}
With the help of fast Fourier transform (FFT), the convolution in
\eqref{eqn:tmp10} can be calculated with the computational cost of
$\mathcal O(N\log N)$.

And the RMS error is estimated by
\begin{align}\nonumber
  \langle\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle
  = &\,
  q^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r) + 
  q^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r) + \\
  &
  q^2\,\int_{\mathbb R^3\times\mathbb R^3}
  \v K^c_{\textrm{dir}}(\v r-\v r')\cdot
  \v K^c_{\textrm{dir}}(\v r-\v r'')\,
  C_{q^2}(\v r', \v r'')\,
  \d d\v r'\d d\v r''.
\end{align}
The three terms on the right hand side are homogeneity error,
inhomogeneity error and correlation error. The second order charge
distribution $\rho_{q^2}$ is
\begin{align}
  \rho_{q^2}(\v r) = 
  \bigg\langle
  \sum_{j = 1}^N
  \,q^2_j\,\delta(\v r - \v r_j)
  \bigg\rangle.
\end{align}
The charge density correlation function is defined by
\begin{align}
  C_{q^2}(\v r', \v r'')
  =
  \bigg\langle
  \sum_{i\neq j}q_iq_j\delta(\v r'-\v r_i)\delta(\v r''-\v r_j)
  \bigg\rangle
  - \rho_q(\v r')\rho_q(\v r'').
\end{align}
In most situations, neglecting the correlation error will give
satisfactory estimate of the error~\cite{short}. Therefore, 
\begin{align}
  \langle\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle
  = &\,
  q^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r) + 
  q^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r).
\end{align}

The reciprocal error force, namely the difference between the
the exact and truncated reciprocal force, is
\begin{align}
  \Delta \v F_{\textrm{rec}}(\v r)
  = & - 
  q
  \sum_{\vert m_\alpha\vert \geq K_\alpha/2}
  \v g(\v m) \,
  S(-\v m)\,
  e^{2\pi i\v m\cdot\v r} 
\end{align}
It is proved that the mean reciprocal error force is
\begin{align}
  \big\langle
  \Delta \v F_{\textrm{rec}}(\v r)
  \big\rangle
  &= 
  -q\,[\v K_c\ast\rho_q\,] (\v r_i),
\end{align}
where the reciprocal convolutional kernel of the error force $\v
K^c_{\textrm{rec}}$ is defined by:
\begin{align}
  \v K^c_{\textrm{rec}}(\v r) =
  \sum_{
      \vert m_\alpha\vert \geq K_\alpha/2}
  \v g(\v m) \,
  e^{2\pi i\v m\cdot\v r}.
\end{align}
Similarly, with the assumption of uncorrelation, it is shown that
\begin{align}
  \langle\vert\Delta\v F_{\textrm{rec}}(\v r)\vert^2\rangle
  = &\,
  q^2\,[(\v K^c_{\textrm{rec}})^2\ast\rho_{q^2}] (\v r) + 
  q^2\,[\v K^c_{\textrm{rec}}\ast\rho_{q}]^2 (\v r).
\end{align}

From \eqref{eqn:tmp13}, the ensemble average of the squared force error is
\begin{align}\nonumber
  \big\langle
  \vert\Delta\v F(\v r_i)\vert^2
  \big\rangle
  = \,&
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
      \v m_1\neq 0
    \end{subarray}}
  \sum_{
    \begin{subarray}{c}
      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
      \v m_2\neq 0
    \end{subarray}}
  \v g(\v m_1)\cdot\v g(\v m_2) \,
  e^{2\pi i(\v m_1 + \v m_2)\cdot\v r_i} \\ \nonumber
  &
  \bigg\langle
  \sum_{j\neq i}q_j\,e^{-2\pi i\v m_1\cdot\v r_j}  
  \sum_{k\neq i}q_k\,e^{-2\pi i\v m_2\cdot\v r_k}
  \bigg\rangle\\ \nonumber
  = \,&
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
      \v m_1\neq 0
    \end{subarray}}
  \sum_{
    \begin{subarray}{c}
      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
      \v m_2\neq 0
    \end{subarray}}
  \v g(\v m_1)\cdot\v g(\v m_2) \,
  e^{2\pi i(\v m_1 + \v m_2)\cdot\v r_i}\\\nonumber
  &
  \bigg\langle
  \sum_{j\neq i}\,q_j^2\,e^{-2\pi i(\v m_1 + \v m_2)\cdot\v r_j} +
  \sum_{j\neq k}\,q_jq_k\, e^{-2\pi i\v m_1\cdot\v r_j} e^{-2\pi i\v m_2\cdot\v r_k}
  \bigg\rangle
\end{align}
Assuming particle $i$ is independent with $j$ when $i\neq j$, the second term is
approximately $\langle\Delta\v F(\v r_i)\rangle^2$, therefore,
\begin{align}\nonumber
  \big\langle
  \vert\Delta\v F(\v r_i)\vert^2
  \big\rangle
  = \,&
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
      \v m_1\neq 0
    \end{subarray}}
  \sum_{
    \begin{subarray}{c}
      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
      \v m_2\neq 0
    \end{subarray}}
  \v g(\v m_1)\cdot\v g(\v m_2) \\\nonumber
  \,&
  \int
  \bigg\langle
  \sum_{j\neq i}\,q_j^2
  \delta (\v r' - \v r_j)
  \bigg\rangle
  \,e^{2\pi i(\v m_1 + \v m_2)\cdot(\v r_i - \v r')}
  \,\d d\v r' \\ \nonumber
  &+\,
  \langle\Delta\v F(\v r_i)\rangle^2 \\ \nonumber
  =\,&
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
      \v m_1\neq 0
    \end{subarray}}
  \sum_{
    \begin{subarray}{c}
      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
      \v m_2\neq 0
    \end{subarray}}
  \v g(\v m_1)\cdot\v g(\v m_2) 
  \int
  \,e^{2\pi i(\v m_1 + \v m_2)\cdot(\v r_i - \v r')}
  \,\rho_{q^2}(\v r')
  \,\d d\v r' \\  \nonumber
  &+\,
  \langle\Delta\v F(\v r_i)\rangle^2 \\ 
  =\;&
  q^2_i
  \int \v G^2_c(\v r - \v r')\,\rho_{q^2}(\v r')\,\d d\v r'  
  + 
  \langle\Delta\v F(\v r_i)\,\rangle^2 \\
  =\;&
  q_i^2\,[\v G_c^2\ast\rho_{q^2}] (\v r_i) + \langle\Delta\v F(\v r_i)\,\rangle^2 
\end{align}

% \newpage

\bibliography{ref}{}
\bibliographystyle{unsrt}

\end{document}

### 2011-11-23 shortRange.inhomo/writeDown/main.tex
add remarks according to Christof. change the grant number of Pingwen

@@
 \newcommand{\recheck}[1]{{\color{red} #1}}
+\newcommand{\redc}[1]{{\color{red} #1}}
 \renewcommand{\v}[1]{\textbf{\textit{#1}}}
@@
   Sciences, Peking University}
+\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+\author{Christof Sch\"utte}
+\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
 \author{Pingwen Zhang}
@@
 The correlation error involves a double integral, which
-implies that the calculation  requires more compuational resources
+implies that the calculation  requires more computational resources
 than the homogeneity and inhomogeneity errors.
@@
 It is worth pointing out that this is not always true, for example, in
-critical region where the corrlation plays an important role in the system,
-the corrlation error should be taken into account.
+critical region where the correlation plays an important role in the system,
+the correlation error should be taken into account.
 
@@
 In this paper, the mean error force $\langle\Delta\v F(\v r)\rangle$
-is also refered as \emph{correction force} in the context of
+is also referred as \emph{correction force} in the context of
 long-range force correction. This correction works because it takes
@@
 
+\redc{ The precise calculation of the correction force needs the
+  precise knowledge of the density profile of the system (see
+  Eqn. \eqref{eqn:tmp3}). Then the corrected force, in turn, improves
+  the accuracy of the density profile. It is possible that this
+  feedback loop does not converge, namely the system is driven to a
+  totally wrong state by the corresponding incorrect correction
+  force. It may happen when the simulation starts very far from the
+  equilibrium, or when the fluctuation in the system is so large that
+  an accurate calculation of the density profile is impossible.
+  % In
+  % the latter case, the MD simulation are not trivial anyway, for
+  % example, the simulation of critical point.
+  % For these two cases, the traditional MD simulation is also not easy
+  % to handel.
+  In our
+  simulations, we do not observe any failure of convergence. Firstly,
+  the system is far from the critical point, and we always let the
+  simulation starts form a good enough configuration, for example, a
+  snapshot of a simulation with the uniform small cut-off and lower
+  temperature, or a snapshot from another force correction simulation.
+  % or the state of the system changes too fast
+  % comparing with the correction force updating fequency
+  We also observe that the equilibration of the force-corrected
+  system is always as fast as the system simulated by uniform and
+  adaptive cut-off methods. That means, at least in our simulation
+  cases, the force correction does not lead to more effort of 
+  equilibrating the system.
+}
+
 % To verify our simulations, we compare our results in
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 The authors gratefully thank Luigi Delle Site for for useful comments
 on the manuscript. The work of P.Z. is supported by grants from
-National Natural Science Foundation of China (20490222).
+National Natural Science Foundation of China (50930003).
 

### 2011-11-24 longRange.hetero/writeDown/main.tex
backup

@@
 \renewcommand{\d}[1]{\textsf{#1}}
+% \allowdisplaybreaks
 
@@
 In this paper, we consider the force error, bacause the applicaions
-are based on the molecular dynamics simulation. We study the force
-error at arbitrary position $\v r$ by adding a testing particle with
-charge $q$ to $\v r$. The difference between the exact force and
-calculated force (with error introduced by cut-offs) exerting on the
-testing particle are denoted by $\v F(\v r)$ and $\tilde{\v F}(\v r)$,
-respectively. Note that the testing particle does NOT exert any force
-on the system. The difference between the exact and calculated is
-called the \emph{error force} \cite{short}, and is denoted by $\Delta
-\v F(\v r) = \v F(\v r) - \tilde{\v F}(\v r)$.  The error of the force
+are based on the molecular dynamics simulation.  Suppose the system is
+composed by $N$ charged particles located at $\v r_1, \v r_2, \cdots,
+\v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.  We study
+the force error of an arbitrary charge $i$ by the difference between
+the exact force $\v F(\v r_i)$ and calculated force $\tilde{\v F}(\v
+r_i)$ (with error introduced by cut-offs) exerting on the charge $i$.
+The difference between the exact and calculated is called the
+\emph{error force} \cite{short}, and is denoted by $\Delta \v F(\v r_i)
+= \v F(\v r_i) - \tilde{\v F}(\v r_i)$.  The error of the force
 computation is defined by the \emph{root mean square (RMS)}
 \emph{error}, which is the square root of the second moment of the
-error force: $\mathcal E(\v r) = \sqrt{\langle\vert\Delta\v F(\v
-  r)\vert^2\rangle}$.  The notation $\langle\cdot\rangle$ means
+error force: $\mathcal E(\v r_i) = \sqrt{\langle\vert\Delta\v F(\v
+  r_i)\vert^2\rangle}$.  The notation $\langle\cdot\rangle$ means
 ensemble average.
@@
 \begin{align}\label{eqn:tmp10}
-  \langle\Delta\v F_{\textrm{dir}}(\v r)\rangle
-  =q\, [\v K^c_{\textrm{dir}}\ast\rho_q](\v r).
+  \langle\Delta\v F_{\textrm{dir}}(\v r_i)\rangle
+  =q_i\, [\v K^c_{\textrm{dir}}\ast\rho_q](\v r_i).
 \end{align}
@@
 \begin{align}\nonumber
-  \langle\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle
+  \langle\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle
   = &\,
-  q^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r) + 
-  q^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r) + \\
+  q_i^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r_i) + 
+  q_i^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r_i) + \\
   &
-  q^2\,\int_{\mathbb R^3\times\mathbb R^3}
-  \v K^c_{\textrm{dir}}(\v r-\v r')\cdot
-  \v K^c_{\textrm{dir}}(\v r-\v r'')\,
+  q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
+  \v K^c_{\textrm{dir}}(\v r_i-\v r')\cdot
+  \v K^c_{\textrm{dir}}(\v r_i-\v r'')\,
   C_{q^2}(\v r', \v r'')\,
@@
 The three terms on the right hand side are homogeneity error,
-inhomogeneity error and correlation error. The second order charge
-distribution $\rho_{q^2}$ is
+inhomogeneity error and correlation error. The inhomogeneity error is
+nothing but the square of the mean error force \eqref{eqn:tmp10}. The
+second order charge distribution $\rho_{q^2}$ is
 \begin{align}
@@
 \begin{align}
-  \langle\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle
+  \langle\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle
   = &\,
-  q^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r) + 
-  q^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r).
+  q_i^2\,[(\v K^c_{\textrm{dir}})^2\ast\rho_{q^2}] (\v r_i) + 
+  q_i^2\,[\v K^c_{\textrm{dir}}\ast\rho_{q}]^2 (\v r_i).
 \end{align}
@@
 \begin{align}
-  \Delta \v F_{\textrm{rec}}(\v r)
+  \Delta \v F_{\textrm{rec}}(\v r_i)
   = & - 
-  q
+  q_i
   \sum_{\vert m_\alpha\vert \geq K_\alpha/2}
@@
   S(-\v m)\,
-  e^{2\pi i\v m\cdot\v r} 
+  e^{2\pi i\v m\cdot\v r_i} 
 \end{align}
 It is proved that the mean reciprocal error force is
-\begin{align}
+\begin{align}\label{eqn:tmp18}
   \big\langle
-  \Delta \v F_{\textrm{rec}}(\v r)
+  \Delta \v F_{\textrm{rec}}(\v r_i)
   \big\rangle
   &= 
-  -q\,[\v K_c\ast\rho_q\,] (\v r_i),
+  -q_i\,[\v K^c_{\textrm{rec}}\ast\rho_q\,] (\v r_i),
 \end{align}
@@
 \begin{align}
-  \langle\vert\Delta\v F_{\textrm{rec}}(\v r)\vert^2\rangle
+  \langle\vert\Delta\v F_{\textrm{rec}}(\v r_i)\vert^2\rangle
   = &\,
-  q^2\,[(\v K^c_{\textrm{rec}})^2\ast\rho_{q^2}] (\v r) + 
-  q^2\,[\v K^c_{\textrm{rec}}\ast\rho_{q}]^2 (\v r).
+  q_i^2\,[(\v K^c_{\textrm{rec}})^2\ast\rho_{q^2}] (\v r_i) + 
+  q_i^2\,[\v K^c_{\textrm{rec}}\ast\rho_{q}]^2 (\v r_i).
 \end{align}
 
-From \eqref{eqn:tmp13}, the ensemble average of the squared force error is
+% Ref. \cite{short} pointed out that the inhomogeneity error is more
+% harmful than the homogeneity error, so it is interesting to analyze
+% the inhomogeneity error. Apply the Fourier transform on both sides of
+% Eqn. \eqref{eqn:tmp10} and \eqref{eqn:tmp18}:
+% \begin{align}  
+%   \langle\Delta\v F_{\textrm{dir}}\rangle^\wedge(\v m)
+%   &= q_i\,\hat{\v K}^c_{\textrm{dir}}(\v m)\cdot\hat\rho_q(\v m)\\
+%   \langle\Delta\v F_{\textrm{rec}}\rangle^\wedge(\v m)
+%   &= -q_i\,\hat{\v K}^c_{\textrm{rec}}(\v m)\cdot\hat\rho_q(\v m)
+% \end{align}
+% If the charge distribution is \emph{locally} neutral, then all modes
+% of the first order density distribution vanishes, and $\langle\Delta\v
+% F_{\textrm{dir}}\rangle = \langle\Delta\v F_{\textrm{rec}}\rangle = 0$.
+
+\section{SPME}
+
+The principle idea of the SPME method is to approximate the term
+$e^{2\pi i\v m\cdot\v r}$ in the structure factor by the B-spline
+interpolation. Denote the error introduced by this approximation by
+$A(\v m, \v r)\,e^{2\pi i\v m\cdot \v r}$, we are fortunate to have
+the analytical expression of $A(\v m, \v r)$:
+\begin{align}
+  A(\v m, \v r)
+  =
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \frac
+  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  {\sum\limits_{l=-\infty}^{+\infty}
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  \bigg(
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 1
+  \bigg)
+\end{align}
+
+There are two possibility of calculating the reciprocal force from the
+SPME energy. The first one is to differentiate the reciprocal term of
+the original Ewald summation and then approximated the analytical
+force by the B-spline interplation. This way is called
+\emph{ik--differentiation}. The other way is to negative gradient on
+the SPME approximated energy, as proposed in the original SPME paper
+\cite{essmann1995spm}. The later is called \emph{analytical
+differentiation}.
+
+\subsection{Error estimate of the ik-differentiation}
+The error force is 
+\begin{align}\nonumber
+  \Delta\v F(\v r_i)
+  =\;&
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  A(\v m, \v r_i)\,
+  e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  & +\,
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\nonumber
+  & +\,
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  \big[
+  A(\v m, \v r_i) +
+  A(\v m, -\v r_i)
+  \big]
+\end{align}
+The last ``self-interacting term'' is zero because of the symmetricity
+of $\v g(\v m)$ and $A(\v m, \v r)$. 
+By denoting
+\begin{align}
+  \v G_{\alpha,l}(\v r) =
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  \frac
+  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  {\sum\limits_{l=-\infty}^{+\infty}
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  e^{2\pi i\v m\cdot\v r}
+\end{align}
+And if the high wave number terms are neglected, it is proved that the
+mean error force is
+\begin{align}
+  \big\langle
+  \Delta\v F(\v r_i)
+  \big\rangle
+  & \approx
+  - 2 q_i
+  \bigg[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}\v G_{\alpha,l}
+  \big)
+  \ast\rho_q\,
+  \bigg] (\v r_i)
+\end{align}
+Also neglect the high wave number terms, the mean squared error force is 
 \begin{align}\nonumber
@@
   \big\rangle
-  = \,&
-  q^2_i
+  \approx&\, 
+  2q_i^2
+  \bigg[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\bigg] (\v r_i)
+  +
+  4q_i^2\,
+  \bigg[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)^2
+  \ast \rho_{q^2}\,
+  \bigg] (\v r_i) \\
+  &\,+
+  \big\langle
+  \Delta\v F(\v r_i)
+  \big\rangle  ^2
+\end{align}
+
+\subsection{Analytical differetiation}
+
+The error force is 
+\begin{align}\nonumber
+  \Delta\v F(\v r_i)
+  =\;&
+  q_i
   \sum_{
     \begin{subarray}{c}
-      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
-      \v m_1\neq 0
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
     \end{subarray}}
+  -2f(\v m)\,
+  \nabla_{\v r_i}
+  e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,
+  A(\v m, -\v r_j)
+  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  & +\,
+  q_i
   \sum_{
     \begin{subarray}{c}
-      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
-      \v m_2\neq 0
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
     \end{subarray}}
-  \v g(\v m_1)\cdot\v g(\v m_2) \,
-  e^{2\pi i(\v m_1 + \v m_2)\cdot\v r_i} \\ \nonumber
-  &
-  \bigg\langle
-  \sum_{j\neq i}q_j\,e^{-2\pi i\v m_1\cdot\v r_j}  
-  \sum_{k\neq i}q_k\,e^{-2\pi i\v m_2\cdot\v r_k}
-  \bigg\rangle\\ \nonumber
-  = \,&
-  q^2_i
+  -2f(\v m)\,
+  \nabla_{\v r_i}
+  [A(\v m, \v r_i)\,
+  e^{2\pi i\v m\cdot \v r_i} ]
+  \sum_{j\neq i}q_j\,
+  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  & +\,
+  q_i
   \sum_{
     \begin{subarray}{c}
-      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
-      \v m_1\neq 0
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
     \end{subarray}}
+  -2f(\v m)\,
+  A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\
+  & +\,
+  q_i
   \sum_{
     \begin{subarray}{c}
-      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
-      \v m_2\neq 0
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
     \end{subarray}}
-  \v g(\v m_1)\cdot\v g(\v m_2) \,
-  e^{2\pi i(\v m_1 + \v m_2)\cdot\v r_i}\\\nonumber
-  &
-  \bigg\langle
-  \sum_{j\neq i}\,q_j^2\,e^{-2\pi i(\v m_1 + \v m_2)\cdot\v r_j} +
-  \sum_{j\neq k}\,q_jq_k\, e^{-2\pi i\v m_1\cdot\v r_j} e^{-2\pi i\v m_2\cdot\v r_k}
-  \bigg\rangle
+  -2f(\v m)\,
+  e^{-2\pi i\v m\cdot \v r_i}
+  \nabla_{\v r_i} [\,A(\v m, \v r_i) \,e^{2\pi i\v m\cdot\v r_i}\,]  \\\nonumber
+  =&\,
+  \Delta\v F^{\textrm{ik}}(\v r_i)\\\nonumber
+  & +\,
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  -2f(\v m)\,
+  \v B(\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,
+  e^{-2\pi i\v m\cdot\v r_j} \\
+  & +\,
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  -2f(\v m)\,\v B(\v m, \v r_i) 
 \end{align}
-Assuming particle $i$ is independent with $j$ when $i\neq j$, the second term is
-approximately $\langle\Delta\v F(\v r_i)\rangle^2$, therefore,
+With $\v B(\v m, \v r)$ defined by
+\begin{align}\nonumber
+  \v B(\v m, \v r)
+  &=
+  \nabla_{\v r_i}A(\v m, \v r)\\
+  &=
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \frac
+  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  {\sum\limits_{l=-\infty}^{+\infty}
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  2\pi i l K_\alpha\v a_\alpha^\ast\,e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
+\end{align}
+For convenience, we denote
+\begin{align}
+  F_{\alpha,l} (\v r)
+  &=
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  (-2)f(\v m)\,
+  \frac
+  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  {\sum\limits_{l=-\infty}^{+\infty}
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}\,
+  e^{2\pi i\v m\cdot \v r}\\
+  C_{\alpha,l}^{\textrm{self}}
+  &= 
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  (-2)f(\v m)\,
+  \frac
+  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  {\sum\limits_{l=-\infty}^{+\infty}
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}\,
+\end{align}
+We prove:
+\begin{align} \nonumber
+  \langle \Delta\v F(\v r_i)\rangle
+  =\;&
+  \langle \Delta\v F^{\textrm{ik}}(\v r_i)\rangle\\\nonumber
+  &+\,
+  q_i\sum_{\alpha}\sum_{l\neq 0}
+  2\pi i\,l K_\alpha\v a_\alpha^\ast\,e^{2\pi i\,l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  [F_{\alpha,l}\ast\rho_q](\v r_i) \\
+  &+\,
+  q_i\sum_{\alpha}\sum_{l\neq 0}
+  2\pi i\,l K_\alpha\v a_\alpha^\ast\,e^{2\pi i\,l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  C_{\alpha,l}^{\textrm{self}}
+\end{align}
+The ensemble average of the squared force error is
 \begin{align}\nonumber
   \big\langle
-  \vert\Delta\v F(\v r_i)\vert^2
+  \vert \Delta\v F(\v r_i)\vert^2
   \big\rangle
-  = \,&
-  q^2_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
-      \v m_1\neq 0
-    \end{subarray}}
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
-      \v m_2\neq 0
-    \end{subarray}}
-  \v g(\v m_1)\cdot\v g(\v m_2) \\\nonumber
-  \,&
-  \int
-  \bigg\langle
-  \sum_{j\neq i}\,q_j^2
-  \delta (\v r' - \v r_j)
-  \bigg\rangle
-  \,e^{2\pi i(\v m_1 + \v m_2)\cdot(\v r_i - \v r')}
-  \,\d d\v r' \\ \nonumber
-  &+\,
-  \langle\Delta\v F(\v r_i)\rangle^2 \\ \nonumber
-  =\,&
-  q^2_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{1,\alpha}\vert \geq K_\alpha/2\\
-      \v m_1\neq 0
-    \end{subarray}}
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{2,\alpha}\vert \geq K_\alpha/2\\
-      \v m_2\neq 0
-    \end{subarray}}
-  \v g(\v m_1)\cdot\v g(\v m_2) 
-  \int
-  \,e^{2\pi i(\v m_1 + \v m_2)\cdot(\v r_i - \v r')}
-  \,\rho_{q^2}(\v r')
-  \,\d d\v r' \\  \nonumber
-  &+\,
-  \langle\Delta\v F(\v r_i)\rangle^2 \\ 
-  =\;&
-  q^2_i
-  \int \v G^2_c(\v r - \v r')\,\rho_{q^2}(\v r')\,\d d\v r'  
-  + 
-  \langle\Delta\v F(\v r_i)\,\rangle^2 \\
-  =\;&
-  q_i^2\,[\v G_c^2\ast\rho_{q^2}] (\v r_i) + \langle\Delta\v F(\v r_i)\,\rangle^2 
+  =&\,
+  q_i^2
+  \bigg[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\bigg] (\v r_i)
+  +\,
+  4q_i^2\,
+  \bigg[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)^2
+  \ast \rho_{q^2}\,
+  \bigg] (\v r_i) \\\nonumber
+  & +\,
+  q_i^2
+  \bigg[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}
+  \vert
+  \v G_{\alpha,l} + 2\pi i\,l K_\alpha F_{\alpha,l} \v a_\alpha^\ast\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \bigg]
+  (\v r_i) \\
+  & +\,
+  \big\langle \Delta\v F(\v r_i)\big\rangle ^2
 \end{align}
 
-% \newpage
+\section{Numerical tests}
+
+\newpage
+\appendix
+\section{Error estimate of the Ewald summation}
+
+\newpage
 

### 2011-12-15 longRange.hetero/profile.test/template/error.esti.spme.sh
fix bug

@@ -5,7 +5,7 @@ if test ! -d $record_dir; then
     exit
 fi
 
-if test ! -f $record_dir/esti.dir.error.out; then
+if test ! -f $errors_dir/esti.dir.error.out; then
     ./tools/scripts/dir.esti.sh
 fi  
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/gen.conf.sh
back up existing recording dir

@@ -5,6 +5,10 @@ source parameters.sh
 mylog=gen.conf.log
 
 rm -f $mylog
+if test -d $record_dir; then
+    echo "# existing record dir $record_dir, mv to backup"
+    mv -f $record_dir $record_dir.`date +%s`
+fi
 rm -fr $record_dir
 mkdir -p $record_dir
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/dir.esti.sh
back up parameters.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.dir.esti.sh
+cp parameters.sh $errors_dir/parameters.dir.esti.sh
 
 mylog=dir.esti.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/ewald.esti.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.ewald.esti.sh
+cp parameters.sh $errors_dir/parameters.ewald.esti.sh
 
 mylog=ewald.esti.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/ewald.real.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.ewald.real.sh
+cp parameters.sh $errors_dir/parameters.ewald.real.sh
 
 mylog=ewald.real.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/gen.conf.sh

@@ -11,6 +11,7 @@ if test -d $record_dir; then
 fi
 rm -fr $record_dir
 mkdir -p $record_dir
+cp parameters.sh $record_dir
 
 make -j8 -C ./tools/profile/ &> make.log
 make -j8 -C ./tools/real.error/ &>> make.log

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/make.ref.sh

@@ -6,6 +6,8 @@ if test ! -d $record_dir; then
     echo "no record dir $record_dir"
     exit
 fi
+rm -f $record_dir/parameters.make.ref.sh
+cp parameters.sh $record_dir/parameters.make.ref.sh
 
 mylog=make.ref.log
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ana.esti.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.spme.ana.esti.sh
+cp parameters.sh $errors_dir/parameters.spme.ana.esti.sh
 
 mylog=spme.ana.esti.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ana.real.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.spme.ana.real.sh
+cp parameters.sh $errors_dir/parameters.spme.ana.real.sh
 
 mylog=spme.ana.real.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ik.esti.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.spme.ik.esti.sh
+cp parameters.sh $errors_dir/parameters.spme.ik.esti.sh
 
 mylog=spme.ik.esti.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ik.real.sh

@@ -10,6 +10,8 @@ if test ! -d $errors_dir; then
     echo "# no errors dir $errors_dir, make it"
     mkdir -p $errors_dir
 fi
+rm -f $errors_dir/parameters.spme.ik.real.sh
+cp parameters.sh $errors_dir/parameters.spme.ik.real.sh
 
 mylog=spme.ik.real.log
 rm -f $mylog

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/dir.esti.sh
del dir.esti.sh with wrong permission

@@ -1,28 +1,0 @@
-#!/bin/bash
-
-source parameters.sh
-
-if test ! -d $record_dir; then
-    echo "no record dir $record_dir"
-    exit
-fi
-if test ! -d $errors_dir; then
-    echo "# no errors dir $errors_dir, make it"
-    mkdir -p $errors_dir
-fi
-rm -f $errors_dir/parameters.dir.esti.sh
-cp parameters.sh $errors_dir/parameters.dir.esti.sh
-
-mylog=dir.esti.log
-rm -f $mylog
-touch $mylog
-
-make -j8 -C ./tools/analyze/ &>> make.log
-
-# esti the dir error
-./tools/analyze/error.dir -t $record_dir/traj.xtc --refh $real_h --beta $beta --rcut $cal_rcut &>> $mylog
-mv -f rho.x.avg.out $errors_dir/
-mv -f error.out $errors_dir/esti.dir.error.out
-mv -f meanf.out $errors_dir/esti.dir.meanf.out
-
-mv -f make.log $mylog $errors_dir

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/dir.esti.sh
add dir.esti.sh with right permission

@@ -1,0 +1,28 @@
+#!/bin/bash
+
+source parameters.sh
+
+if test ! -d $record_dir; then
+    echo "no record dir $record_dir"
+    exit
+fi
+if test ! -d $errors_dir; then
+    echo "# no errors dir $errors_dir, make it"
+    mkdir -p $errors_dir
+fi
+rm -f $errors_dir/parameters.dir.esti.sh
+cp parameters.sh $errors_dir/parameters.dir.esti.sh
+
+mylog=dir.esti.log
+rm -f $mylog
+touch $mylog
+
+make -j8 -C ./tools/analyze/ &>> make.log
+
+# esti the dir error
+./tools/analyze/error.dir -t $record_dir/traj.xtc --refh $real_h --beta $beta --rcut $cal_rcut &>> $mylog
+mv -f rho.x.avg.out $errors_dir/
+mv -f error.out $errors_dir/esti.dir.error.out
+mv -f meanf.out $errors_dir/esti.dir.meanf.out
+
+mv -f make.log $mylog $errors_dir

### 2011-12-15 longRange.hetero/profile.test/template/parameters.sh
different K on different directions

@@ -22,24 +22,32 @@ peak_dist=5.0
 project_name=two.peaks
 profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
 
-# Ewald parameters
+# param for reference force
 beta=1.0
 ref_rcut=5.0
-ref_K=65
+ref_Kx=257
+ref_Ky=129
+ref_Kz=129
 # regulate parameters. DO NOT MOVE
 beta=`printf "%.3f" $beta`
 ref_rcut=`printf "%.2f" $ref_rcut`
-ref_K=`printf "%03d" $ref_K`
-record_dir=$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$ref_rcut.K$ref_K
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+record_dir=$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$ref_rcut.K${ref_Kx}x${ref_Ky}x${ref_Kz}
 
-# naive summation
+# param for error estimate
 cal_rcut=3.0
-cal_K=59
+cal_Kx=120
+cal_Ky=60
+cal_Kz=60
 cal_order=6
 real_h=1.0
 
 # regulate parameters. DO NOT MOVE
 cal_rcut=`printf "%.2f" $cal_rcut`
-cal_K=`printf "%03d" $cal_K`
+cal_Kx=`printf "%03d" $cal_Kx`
+cal_Ky=`printf "%03d" $cal_Ky`
+cal_Kz=`printf "%03d" $cal_Kz`
 cal_order=`printf "%01d" $cal_order`
-errors_dir=error.$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$cal_rcut.n$cal_order.K$cal_K
+errors_dir=error.$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$cal_rcut.n$cal_order.K${cal_Kx}x${cal_Ky}x${cal_Kz}

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/ewald.esti.sh

@@ -20,7 +20,7 @@ touch $mylog
 make -C ./tools/analyze/ &>> make.log
 
 # esti the rec error
-./tools/analyze/error.ewald -t $record_dir/traj.xtc --kmax $cal_K -k $ref_K --beta $beta &>> $mylog
+./tools/analyze/error.ewald -t $record_dir/traj.xtc --kmaxx $cal_Kx --kmaxy $cal_Ky --kmaxz $cal_Kz --kx $ref_Kx --ky $ref_Ky --kz $ref_Kz --beta $beta &>> $mylog
 mv -f rho.x.avg.out $errors_dir/
 mv -f error.out $errors_dir/esti.rec.ewald.error.out
 mv -f meanf.out $errors_dir/esti.rec.ewald.meanf.out

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/ewald.real.sh

@@ -26,7 +26,7 @@ do
     echo "# #############################################################################" &>> $mylog
     echo "# doing $iname" &>> $mylog
     echo "# #############################################################################" &>> $mylog
-    ./tools/real.error/ewaldSum --config $record_dir/$i --beta $beta --rcut $cal_rcut --grid-number $cal_K --output-force force.ewald.out &>> $mylog
+    ./tools/real.error/ewaldSum --config $record_dir/$i --beta $beta --rcut $cal_rcut --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --output-force force.ewald.out &>> $mylog
     
     tools/real.error/compare.force --config $record_dir/$i --refh $real_h --force-0 $record_dir/force.ref.$iname.out --force-1 force.ewald.out -o error.ewald.$iname.out -m meanf.ewald.$iname.out &>> $mylog
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/make.ref.sh

@@ -22,7 +22,7 @@ do
     echo "# #############################################################################" &>> $mylog
     echo "# doing $iname" &>> $mylog
     echo "# #############################################################################" &>> $mylog
-    ./tools/real.error/ewaldSum --config $record_dir/$i --beta $beta --rcut $ref_rcut --grid-number $ref_K --output-force force.ref.$iname.out &>> $mylog
+    ./tools/real.error/ewaldSum --config $record_dir/$i --beta $beta --rcut $ref_rcut --kx $ref_Kx --ky $ref_Ky --kz $ref_Kz --output-force force.ref.$iname.out &>> $mylog
     mv force.ref.$iname.out $record_dir
 done
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ana.esti.sh

@@ -20,7 +20,7 @@ touch $mylog
 make -C ./tools/analyze/ &>> make.log
 
 # esti the rec error
-./tools/analyze/error.spme.ana -t $record_dir/traj.xtc -k $cal_K --beta $beta --order $cal_order &>> $mylog
+./tools/analyze/error.spme.ana -t $record_dir/traj.xtc --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --beta $beta --order $cal_order &>> $mylog
 mv -f rho.x.avg.out $errors_dir/
 mv -f error.out $errors_dir/esti.rec.spme.ana.error.out
 mv -f meanf.out $errors_dir/esti.rec.spme.ana.meanf.out

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ana.real.sh

@@ -26,7 +26,7 @@ do
     echo "# #############################################################################" &>> $mylog
     echo "# doing $iname" &>> $mylog
     echo "# #############################################################################" &>> $mylog
-    ./tools/real.error/spme --config $record_dir/$i --method fbspline --beta $beta --rcut $cal_rcut --grid-number $cal_K --order $cal_order --output-force force.spme.ana.out &>> $mylog
+    ./tools/real.error/spme --config $record_dir/$i --method fbspline --beta $beta --rcut $cal_rcut --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --order $cal_order --output-force force.spme.ana.out &>> $mylog
     
     tools/real.error/compare.force --config $record_dir/$i --refh $real_h --force-0 $record_dir/force.ref.$iname.out --force-1 force.spme.ana.out -o error.spme.ana.$iname.out -m meanf.spme.ana.$iname.out &>> $mylog
 

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ik.esti.sh

@@ -20,7 +20,7 @@ touch $mylog
 make -C ./tools/analyze/ &>> make.log
 
 # esti the rec error
-./tools/analyze/error.spme.ik -t $record_dir/traj.xtc -k $cal_K --beta $beta --order $cal_order &>> $mylog
+./tools/analyze/error.spme.ik -t $record_dir/traj.xtc --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --beta $beta --order $cal_order &>> $mylog
 mv -f rho.x.avg.out $errors_dir/
 mv -f error.out $errors_dir/esti.rec.spme.ik.error.out
 mv -f meanf.out $errors_dir/esti.rec.spme.ik.meanf.out

### 2011-12-15 longRange.hetero/profile.test/template/tools/scripts/spme.ik.real.sh

@@ -26,7 +26,7 @@ do
     echo "# #############################################################################" &>> $mylog
     echo "# doing $iname" &>> $mylog
     echo "# #############################################################################" &>> $mylog
-    ./tools/real.error/spme --config $record_dir/$i --method bspline --beta $beta --rcut $cal_rcut --grid-number $cal_K --order $cal_order --output-force force.spme.ik.out &>> $mylog
+    ./tools/real.error/spme --config $record_dir/$i --method bspline --beta $beta --rcut $cal_rcut --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --order $cal_order --output-force force.spme.ik.out &>> $mylog
     
     tools/real.error/compare.force --config $record_dir/$i --refh $real_h --force-0 $record_dir/force.ref.$iname.out --force-1 force.spme.ik.out -o error.spme.ik.$iname.out -m meanf.spme.ik.$iname.out &>> $mylog
 

### 2011-12-15 longRange.hetero/profile.test/template/parameters.sh
use uniform ref pool

@@ -2,6 +2,7 @@
 
 nframe_real_error=5
 nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
 
 # gen conf parameters
 Lx=30
@@ -35,6 +36,7 @@ ref_Kx=`printf "%03d" $ref_Kx`
 ref_Ky=`printf "%03d" $ref_Ky`
 ref_Kz=`printf "%03d" $ref_Kz`
 record_dir=$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$ref_rcut.K${ref_Kx}x${ref_Ky}x${ref_Kz}
+record_dir=$config_pool/$record_dir
 
 # param for error estimate
 cal_rcut=3.0

### 2011-12-15 longRange.hetero/profile.test/template/tools/real.error/app/ewaldSum.cpp
print more info

@@ -209,8 +209,12 @@ int main (int argc, char * argv[])
     tmp1 *= unitScale;
   }
   std::cout << "ref beta is " << refbeta << std::endl;
-  std::cout << "ref K0 is " << refK[0] << std::endl;
-  std::cout << "size of K is " << refK[0] << std::endl;
+  std::cout << "ref K0x is " << refK[0] << std::endl;
+  std::cout << "ref K0y is " << refK[1] << std::endl;
+  std::cout << "ref K0z is " << refK[2] << std::endl;
+  std::cout << "size of Kx is " << refK[0] << std::endl;
+  std::cout << "size of Ky is " << refK[1] << std::endl;
+  std::cout << "size of Kz is " << refK[2] << std::endl;
   std::cout << "the ref ES dir error is " << tmp0 << std::endl;
   std::cout << "the ref ES rec error is " << tmp1 << std::endl;
 

### 2011-12-15 longRange.hetero/profile.test/template/parameters.sh
new proj name

@@ -13,14 +13,14 @@ peak_size=20
 rhoh=0.50
 rhol=0.05
 
-project_name=one.peak
+project_name=one_peak
 profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
 
 project_name=uniform
 profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
 
 peak_dist=5.0
-project_name=two.peaks
+project_name=two_peaks
 profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
 
 # param for reference force

### 2011-12-15 longRange.hetero/profile.test/template/tools/profile/app/two_peaks_sep.cpp
add two_peaks_sep.cpp

@@ -1,0 +1,94 @@
+#include "DensityFunction.h"
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+
+#include "RandomGenerator.h"
+
+#include <boost/program_options.hpp>
+namespace po = boost::program_options;
+
+int main(int argc, char * argv[])
+{
+  double Lx, Ly, Lz;
+  double rho;
+  double layer;
+  std::string cfile, tfile;
+  int nframe;
+  unsigned long seed;
+  
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("seed,s", po::value<unsigned long > (&seed)->default_value(1), "random seed")
+      ("Lx,x", po::value<double > (&Lx)->default_value(30.), "box dim of x")
+      ("Ly,y", po::value<double > (&Ly)->default_value(30.), "box dim of y")
+      ("Lz,z", po::value<double > (&Lz)->default_value(30.), "box dim of z")
+      ("layer,t", po::value<double > (&layer)->default_value(4.), "layer thickness")
+      ("rho,r", po::value<double > (&rho)->default_value(0.50), "charge density")
+      ("nframe,n", po::value<int > (&nframe)->default_value(100), "number of frame in trajctory")
+      ("output-conf",  po::value<std::string > (&cfile)->default_value ("conf.gro"), "the output conf file")
+      ("output-traj",  po::value<std::string > (&tfile)->default_value ("traj.xtc"), "the output traj file");
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  RandomGenerator_MT19937::init_genrand (seed);
+
+  printf ("#######################################################\n");
+  printf ("## print two peaks seperating the box\n");
[…]

### 2011-12-15 longRange.hetero/profile.test/template/parameters.sh
add two_peaks_sep, not tested

@@ -23,6 +23,9 @@ peak_dist=5.0
 project_name=two_peaks
 profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
 
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rho $rhoh -n 0"
+
 # param for reference force
 beta=1.0
 ref_rcut=5.0

### 2011-12-15 shortRange.inhomo/writeDown/main.tex
revise according to Christof

@@
-\documentclass[aps,pre,preprint]{revtex4-1}
+\documentclass[aps,pre,preprint]{revtex4}
 % \documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 \begin{abstract}
+  \recheck{
+    In the present paper, we develop an accurate error estimate of the
+    non-bonded short-range interaction for the inhomogeneous molecular
+    systems.
+    The root mean square force error is proved to be decomposed into
+    three additive parts: the homogeneity error, the inhomogeneity error
+    and the correlation error.
+    % The homogeneity error is dominant
+    % in the bulk regions.
+    The magnitude of the inhomogeneity error, which
+    is dominant in the interfacial regions, 
+    can be more than one order of magnitude larger than the homogeneity
+    error.
+    % This is the reason why a direct simulation may waste
+    % a huge amount of computational effort.
+    This is the reason why a standard simulation with fixed
+    cut-off radius is either less accurate if the cut-off is too small,
+    or wastes considerable computational effort if the cut-off is too large.
+    Therefore, based on the error estimate, the adaptive cut-off
+    and long-range force correction methods are proposed to
+    boost the efficiency and accuracy of the simulation, respectively.
+    The
+    effectiveness of the proposed methods are demonstrated by
+    molecular dynamics 
+    simulations of the liquid-vapor equilibrium and the nanoscale particle
+    collision. Different roles of the homogeneity error and inhomogeneity
+    error are also discussed.
+  }
 \end{abstract}
@@
 the one-component system can be straightforwardly extended to the
-multi-component systems.  we consider
-force error in the present paper, because the
-applications are based on molecular dynamics simulation.
+multi-component systems.  We consider
+the force error in the present paper, because the
+applications are based on molecular dynamics simulations.
 % Since the error estimate developed for the one-component system can be
@@
   \v r_{i_1, i_2, i_3} & =
-  \frac{i_1}{K_1}\v a_1 + 
-  \frac{i_2}{K_2}\v a_2 + 
-  \frac{i_3}{K_3}\v a_3,\qquad 0\leq i_\alpha< K_\alpha
-\end{align}
-where $\v a_\alpha$ are box vectors, and $K_\alpha$ is the number of
-division on each direction. In the reciprocal space, a corresponding
+  \frac{i_1}{M_1}\v a_1 + 
+  \frac{i_2}{M_2}\v a_2 + 
+  \frac{i_3}{M_3}\v a_3,\qquad 0\leq i_\alpha< M_\alpha
+\end{align}
+where $\v a_\alpha$ are box vectors, and $M_\alpha$ is the number of
+divisions on each direction. In the reciprocal space, a corresponding
 lattice is set up:
 \begin{align}
-  \v k_{k_1, k_2, k_3} & =
-  k_1\v a_1^\ast +
-  k_2\v a_2^\ast +
-  k_3\v a_3^\ast, \qquad 0\leq k_\alpha<K_\alpha
+  \v k_{m_1, m_2, m_3} & =
+  m_1\v a_1^\ast +
+  m_2\v a_2^\ast +
+  m_3\v a_3^\ast, \qquad 0\leq m_\alpha<M_\alpha
 \end{align}
@@
   & =
-  \frac1V\sum_{k_1=-\infty}^\infty\sum_{k_2=-\infty}^\infty\sum_{k_3=-\infty}^\infty
-  [{\mathcal E}^2_{\textrm{homo}}]^{\wedge}(\v k_{k_1,k_2,k_3})
-  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
+  \frac1V\sum_{m_1=-\infty}^\infty\sum_{m_2=-\infty}^\infty\sum_{m_3=-\infty}^\infty
+  [{\mathcal E}^2_{\textrm{homo}}]^{\wedge}(\v k_{m_1,m_2,m_3})
+  % e^{2\pi i\v k_{m_1,m_2,m_3}\cdot\v r_{i_1,i_2,i_3}}
   \exp\bigg[
   2\pi i\bigg(
-  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
+  \frac{m_1i_1}{M_1} + \frac{m_2i_2}{M_2} + \frac{m_3i_3}{M_3}
   \bigg)
@@
   & =
-  \frac1V\sum_{k_1=0}^{K_1}\sum_{k_2=0}^{K_2}\sum_{k_3=0}^{K_3}
-  \hat{K}_{\textrm{homo}}(\v k'_{k_1,k_2,k_3})\:
-  \hat{\rho}(\v k_{k_1,k_2,k_3})
-  % e^{2\pi i\v k_{k_1,k_2,k_3}\cdot\v r_{i_1,i_2,i_3}}
+  \frac1V\sum_{m_1=0}^{M_1}\sum_{m_2=0}^{M_2}\sum_{m_3=0}^{M_3}
+  \hat{K}_{\textrm{homo}}(\v k'_{m_1,m_2,m_3})\:
+  \hat{\rho}(\v k_{m_1,m_2,m_3})
+  % e^{2\pi i\v k_{m_1,m_2,m_3}\cdot\v r_{i_1,i_2,i_3}}
   \exp\bigg[
   2\pi i\bigg(
-  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
+  \frac{m_1i_1}{M_1} + \frac{m_2i_2}{M_2} + \frac{m_3i_3}{M_3}
   \bigg)
@@
 Here $K_{\textrm{homo}}(\v r)$ denotes $\vert\v f^c(\v r)\vert^2$.
-The wedge notation $\wedge$ means Fourier transform. The prime on $\v k_{k_1,k_2,k_3}$ means
-that the periodic image $k_\alpha - K_\alpha$ should use instead of
-$k_\alpha$ when $k_\alpha \geq K_\alpha/2$.
+The wedge notation $\wedge$ means the Fourier transform. The prime on $\v k_{m_1,m_2,m_3}$ means
+that the periodic image $m_\alpha - M_\alpha$ should use instead of
+$m_\alpha$ when $m_\alpha \geq M_\alpha/2$.
 The second equation in \eqref{eqn:tmp13}
@@
 \begin{align}
-  \hat\rho(\v k_{k_1,k_2,k_3})
+  \hat\rho(\v k_{m_1,m_2,m_3})
   & =
-  \frac{V}{K_1K_2K_3}
-  \sum_{i_1=0}^{K_1}\sum_{i_2=0}^{K_2}\sum_{i_2=0}^{K_2}
+  \frac{V}{M_1M_2M_3}
+  \sum_{i_1=0}^{M_1}\sum_{i_2=0}^{M_2}\sum_{i_3=0}^{M_3}
   \rho(\v r_{i_1,i_2,i_3})
@@
   -2\pi i\bigg(
-  \frac{k_1i_1}{K_1} + \frac{k_2i_2}{K_2} + \frac{k_3i_3}{K_3}
+  \frac{m_1i_1}{M_1} + \frac{m_2i_2}{M_2} + \frac{m_3i_3}{M_3}
   \bigg)
@@
 which can be calculated by numerical
-integration from $r_c$ to a large upper bound, saying $R_c$. Perfect
-convergence can be achieved by using $R_c = 30\sigma$ throughout the
-paper. Since integral \eqref{eqn:kernel-inte} is independent of the
+integration from $r_c$ to a large upper bound, saying $r_u$. \recheck{Perfect
+convergence is achieved by using $r_u = 30\sigma$
+for the dispersion energy $-4\epsilon (\sigma / r)^6$, where $\epsilon$
+and $\sigma$ are the energy and length units.}
+Since integral~\eqref{eqn:kernel-inte} is independent of the
 density of the system, it is calculated only once and stored.
@@
 % in one of the cases we studied,
-(see Fig. \ref{fig:tmp2}). Traditionally, a very large cut-off radius is
+(see Fig. \ref{fig:tmp2}). Traditionally, a very large uniform cut-off radius is
 used to reduce the maximum error in the system to reach convergent
-simulation results~\cite{ismail2007application}. Therefore, a huge
+simulation results~\cite{ismail2007application}.
+\recheck{
+  However, since the computational effort scales as the
+  cube of the cut-off radius, a slightly larger  cut-off
+  will notably increase the computational effort.
+  For example, increasing the cut-off radius
+  from $4\sigma$ to $5\sigma$ will cost
+  twice the computational effort.}
+Therefore, a huge
 amount of computational effort is wasted in the low-error region. The
@@
 that the force error is uniformly distributed across the simulation
-region.  Unfortunately, the computational expense of a naive
-implementation of this method is at least $\mathcal O(N^2\log N)$.
-Because in order to determine the cut-off radius, we should estimate the RMS
+region.
+ In order to determine the cut-off radius, we should estimate the RMS
 force error at least once for each particle, and the computational
-cost of each force error estimate is $\mathcal O(N \log N)$.
+cost of each force error estimate is $\mathcal O(N \log N)$,
+so the total computational expense of 
+this method is at least $\mathcal O(N^2\log N)$, which is
+prohibitive to the on-the-fly application.
 
@@
 that the cut-off radius may not be calculated at a very high
-precision, a slightly (at most $r_c^{\textrm{step}}$) larger
-cut-off radius will not waste too much computational cost.  Due to the
+precision.
+% a slightly (at most $r_c^{\textrm{step}}$) larger
+% cut-off radius
+\recheck{
+  Because if $r_c^{\textrm{step}}$ is sufficiently small,
+  increasing the cut-off radius by no more than $r_c^{\textrm{step}}$
+will not waste too much computational cost.
+Here we recommend that $r_c^{\textrm{step}}$ should be no more than
+0$.25\sigma$ that increases
+the computational effort by 27\% at $r_c = 3.0\sigma$.}
+Due to the
 thermodynamic fluctuation of the particle density, the resulting cut-off
@@
   janecek2006long, shen2007comparative}. In those works, the density
-profile is assumed to be inhomogeneous along one direction only, and the
-system is subdivided into slabs perpendicular to that direction to
+profile is assumed to be inhomogeneous along one direction, and uniform
+on the other two directions.
+The
+system is subdivided into slabs perpendicular to the inhomogeneous direction to
 calculate the energy/force correction. The advantage of our force
-correction is that it has no geometric restriction on the density
+correction is that it has \emph{no} uniformity restriction on the density
 profile of the system, so can be used in a wider range of
@@
 paper contains 16,000 identical standard Lennard-Jones particles that are
-separated into liquid phase in the center of the box and vapor phase
+separated into liquid phase in the center of the periodic box and vapor phase
 surrounded (see Fig.~\ref{fig:tmp1}).  The conventional Lennard-Jones
@@
 denoted by $\epsilon$, $\sigma$, $m$ and $\tau$ ($\tau =
-\sigma\sqrt{m/\varepsilon}$), respectively.  All quantities are
+\sigma\sqrt{m/\varepsilon}$), respectively.  In the rest of this paper,
+all quantities are
 rescaled by the Lennard-Jones units and added the superscript ``$\ast$''.
@@
 The system is divided into bins of size $1\times1\times1$ to perform the fast error
-estimate method described in section \label{sec:tmp1.3}.
+estimate method described in section \ref{sec:tmp1.3}.
 In all simulations, the maximum cut-off
@@
 150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
-13$.
+13$. \recheck {We find that (not shown here)
+  the bigger system leads to the same equilibrium
+  quantities as the smaller system at the same cut-off radius, so
+  it is reasonable to
+  use it to produce the better converged data at $r_c^\ast=13$ and compare them with
+  those obtained in the smaller system.
+}
 
@@
 by the same notations as in the Fig. \ref{fig:tmp2}. The control error
-$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is the same as the maximum
-error in the uniform cut-off simulation with $r_c^\ast=7.5$. The
+$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is almost the same as the maximum
+error in the uniform cut-off simulation with $r_c^\ast=7.5$.
+\recheck{
+  In the rest of the paper, when we mention that ``the cut-off of
+  the adaptive cut-off method is $r_c^\ast$'', we mean the
+  control error is the maximum error of a uniform cut-off simulation
+  using that cut-off $r_c^\ast$. In all the cases considered by
+  the present paper, the maximum of
+  the adapted cut-off radius is almost the same as $r_c^\ast$,
+  and is sometimes marginally larger (no more than $r_c^\textrm{step}$).
+}
+The
 cut-off distribution is calculated every 20,000 time steps, and is
@@
 regions, the same cut-off radius as the uniform cut-off simulation,
-namely $7.5$, is used.  In the
+namely $7.5$, is used.  In the bulk
 liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
-respective, which is notably reduced. Since the computational cost
-grows with $\mathcal O(r_c^3)$, the adaptive cut-off saves 75 \% and
-90 \% computational cost in the liquid and vapor bulk regions,
-respectively.  The error is uniformly distributed, except in the
+which reduce the computational cost
+by a factor of 4 and 10, respectively.
+The error is uniformly distributed, except in the
 liquid region where the real error is somewhat lower.
@@
 cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
-vapor region is very sharp. The similar phenomenon is observed in
-Ref.~\cite{wang2011}. The same as the uniform cut-off simulation, the
+vapor region is very sharp.
+% The similar phenomenon is observed in
+% Ref.~\cite{wang2011}.
+The same as the uniform cut-off simulation, the
 homogeneity error dominates in the bulk regions, while the
@@
 In Fig. \ref{fig:tmp4}, the red solid line presents the $x$ component
+of the 
 correction force that is calculated every 40 time steps. The $y$ and
@@
 pressure. The convergence of the properties of interest with respect
-to the cut-off radius is considered.  For the adaptive cut-off
-simulation, the ``cut-off radius'' means the largest cut-off radius
-used in the simulation region.
+to the cut-off radius is considered.
+% For the adaptive cut-off
+% simulation, the ``cut-off radius'' means the largest cut-off radius
+% used in the simulation region.
 
@@
      &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
- 3.5 &\textrm{ARC} & $8.6\times 10^{-2}$ & 1.9 \\
+ 3.5 &\textrm{ARC} & $7.7\times 10^{-2}$ & 1.9 \\
      &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{1-4}
      &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
- 5.0 &\textrm{ARC} & $2.2\times 10^{-2}$ & 4.5 \\
+ 5.0 &\textrm{ARC} & $2.0\times 10^{-2}$ & 4.2 \\
      &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{1-4}
@@
 with long-range pressure correction.  Table \ref{tab:tmp1} presents
-the maximum RMS force error and the computational expense of the
+the maximum RMS force error and the computational effort of the
 mentioned methods at different cut-off radii. The computational cost
-is given by the average number of pairwise interactions calculated by
-the program, which is platform independent and serves as a good bench
-mark.
+is given by the average numbers of pairwise interactions per time step
+calculated  by
+the program, which is platform independent and serves as a good benchmark.
 
@@
 correction method converges at $r_c^\ast = 3.5$, and the
-uniform/adaptive cut-off methods converge at $r_c^\ast = 6.0$.  The
+uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0\sim 6.0$.  The
 discrepancy between the corrected and uncorrected tension is the
 amount of the correction, which decreases with the increasing cut-off
-radius. However, even at $r_c^\ast=10$, this correction is not
-negligible, so it is very important for the precise surface tension
-calculation.
+radius.
+\recheck{
+  However, even at a rather large cut-off of $r_c^\ast=10$,
+  the amount of the correction is still not negligible, which tells the users
+  that the uncorrected tension calculation is far from convergence.
+  % the extend of which is shown by the
+  % the amount of the correction calculated by the pressure correction method.
+}  
+% However, even at $r_c^\ast=10$, this correction is not
+% negligible, so it is very important for the precise surface tension
+% calculation.
 
@@
 Eqn.~\eqref{eqn:mean-fcorr}). This implies that the corrected error
-force may point to any direction with the same probability, and may cancel
+force may point to any direction with the same probability, and may self-cancel
 in a long time average.  The inhomogeneity error,
@@
 
-\redc{ The precise calculation of the correction force needs the
+{ The precise calculation of the correction force needs the
   precise knowledge of the density profile of the system (see
@@
 The advantage of the adaptive cut-off method depends on the
-system: if the large bulk regions are connected by high density
-gradient interfaces, the adaptive cut-off method will save a large amount of
+system:
+% if the large bulk regions are connected by high density
+% gradient interfaces,
+\recheck{
+  if the computational costs of the bulk regions rather than the
+  interfacial region dominate the system,}
+the adaptive cut-off method will save a notably large amount of the
 computational resources.
@@
 for surface tension and $r_c^\ast = 10.0$ for equilibrium
-densities). With nearly the same RMS force error, precision of
-equilibrium densities of the force correction simulation were much
-better than the uniform cut-off simulation.  Since the homogeneity
-error dominated the force correction and the inhomogeneity error
-dominated the simulation with uniform cut-off, we conclude the homogeneity
+densities).
+% With nearly the same RMS force error, precision of
+% equilibrium densities of the force correction simulation were much
+% better than the uniform cut-off simulation.  Since the homogeneity
+% error dominated the force correction and the inhomogeneity error
+% dominated the simulation with uniform cut-off,
+\recheck{
+We also concluded that the homogeneity
 error and the inhomogeneity error play different roles on the precision
-of equilibrium liquid-vapor densities.  In the collision cluster case,
+of equilibrium liquid-vapor densities: the inhomogeneity error
+is more harmful even though its magnitude is smaller than the homogeneity
+error.}
+In the collision cluster case,
 the force correction methods produced high-precision trajectory at a

### 2011-12-15 shortRange.inhomo/alltext/pubilsh/main.tex
add publish

--- 2011-12-15 shortRange.inhomo/writeDown/main.tex
@@
 \begin{abstract}
-  \recheck{
+  {
     In the present paper, we develop an accurate error estimate of the
@@
 which can be calculated by numerical
-integration from $r_c$ to a large upper bound, saying $r_u$. \recheck{Perfect
+integration from $r_c$ to a large upper bound, saying $r_u$. {Perfect
 convergence is achieved by using $r_u = 30\sigma$
@@
 simulation results~\cite{ismail2007application}.
-\recheck{
+{
   However, since the computational effort scales as the
@@
 % cut-off radius
-\recheck{
+{
   Because if $r_c^{\textrm{step}}$ is sufficiently small,
@@
 150\times 27\times 27$, and a uniform cut-off radius of $r_c^\ast =
-13$. \recheck {We find that (not shown here)
+13$.  {We find that (not shown here)
   the bigger system leads to the same equilibrium
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{fig/t0.85-n16000-rc07.5uni/confout.eps}
+  \includegraphics[width=0.9\textwidth]{figs/confout.eps}
   \caption{The snapshot of the 16000 Lennard-Jones particle system in
@@
   \centering
-  % \includegraphics[]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-rc07.5uni/error.uniform.eps}
+  \includegraphics[]{figs/error.uniform.eps}
   \caption{The RMS force error distribution of the 16000 Lennard-Jones
@@
 error in the uniform cut-off simulation with $r_c^\ast=7.5$.
-\recheck{
+{
   In the rest of the paper, when we mention that ``the cut-off of
@@
 vapor region is very sharp.
-% The similar phenomenon is observed in
-% Ref.~\cite{wang2011}.
+The similar phenomenon is observed in
+Ref.~\cite{wang2011}.
 The same as the uniform cut-off simulation, the
@@
   \centering
-  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.and.error.eps}
+  \includegraphics[]{figs/rcut.and.error.eps}
   \caption{ The RMS force error distribution of the 16000
@@
   \centering
-  % \includegraphics[scale=1]{fig/t0.85-n16000-rc07.5uni/confout-02.eps}
-  \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.and.error.eps}
+  \includegraphics[]{figs/fcorr.and.error.eps}
   \caption{ The RMS force error distribution of the 16000
@@
   \centering
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.gas.eps} 
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t0.70.liquid.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.gas.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.liquid.eps} 
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.gas.eps} 
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.10.liquid.eps} 
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.gas.eps} 
-  % \includegraphics[width=0.42\textwidth]{fig/converge.new/t1.20.liquid.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.70.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t0.85.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.10.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/t1.20.eps} 
+  \includegraphics[width=0.49\textwidth]{figs/t0.85.gas.eps} 
+  \includegraphics[width=0.49\textwidth]{figs/t0.85.liquid.eps} 
   \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
@@
   \centering
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.70.eps} 
-  \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t0.85.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.10.eps} 
-  % \includegraphics[width=0.49\textwidth]{fig/converge.new/tension.t1.20.eps} 
+  \includegraphics[width=0.49\textwidth]{figs/tension.t0.85.eps} 
   \caption{$T^\ast = 0.85$. The convergence of the surface tension
@@
 amount of the correction, which decreases with the increasing cut-off
-radius.
-\recheck{
+radius. {
   However, even at a rather large cut-off of $r_c^\ast=10$,
@@
   \centering
-  \includegraphics[]{fig/collision-init/init.2.eps}
+  \includegraphics[]{figs/init.2.eps}
   \caption{The initial setup of cluster $A$ and $B$. The initial
@@
   \centering
-  \includegraphics[]{fig/trajs.eps}
+  \includegraphics[]{figs/trajs.eps}
   \caption{The center of mass trajectory of cluster A. Uniform cut-off
@@
   \centering
-  \includegraphics[]{fig/dists.eps}
+  \includegraphics[]{figs/dists.eps}
   \caption{The COM distance between cluster $A$ and cluster $B$ versus
@@
   \centering
-  \includegraphics[width=0.90\textwidth]{fig/error-rcut-ball.eps} 
-  \includegraphics[width=0.90\textwidth]{fig/error-rcut.eps}
+  \includegraphics[width=0.90\textwidth]{figs/error-rcut-ball.eps} 
+  \includegraphics[width=0.90\textwidth]{figs/error-rcut.eps}
   \caption{The colliding clusters (the first row), the RMS force error
@@
   \centering
-  \includegraphics[]{fig/wy.eps}
+  \includegraphics[]{figs/wy.eps}
   \caption{The angular velocity of cluster $A$ versus time. Uniform
@@
   \centering
-  \includegraphics[]{fig/ly.eps}
+  \includegraphics[]{figs/ly.eps}
   \caption{The angular moment of cluster $A$ versus time. Uniform
@@
   \centering
-  \includegraphics[]{fig/cost.eps}
+  \includegraphics[]{figs/cost.eps}
   \caption{The computational cost versus time. Uniform
@@
 The advantage of the adaptive cut-off method depends on the
-system:
+system:{
 % if the large bulk regions are connected by high density
 % gradient interfaces,
-\recheck{
   if the computational costs of the bulk regions rather than the
@@
 for surface tension and $r_c^\ast = 10.0$ for equilibrium
-densities).
+densities). {
 % With nearly the same RMS force error, precision of
@@
 % dominated the simulation with uniform cut-off,
-\recheck{
 We also concluded that the homogeneity

### 2011-12-16 shortRange.inhomo/alltext/pubilsh/main.tex
some minor revises

@@
 \author{Han Wang}
+\email{han.wang@fu-berlin.de}
 \affiliation{LMAM and School of Mathematical
@@
     In the present paper, we develop an accurate error estimate of the
-    non-bonded short-range interaction for the inhomogeneous molecular
+    non-bonded short-range interactions for the inhomogeneous molecular
     systems.
@@
 \section{Introduction}
-Non-bonded short-range interaction is encountered in nearly every
+Non-bonded short-range interactions are encountered in nearly every
 molecular simulation.  A naive idea to calculate short-range
@@
 short-range interactions can be reduced to an acceptable level of
-$\mathcal O(N)$.  The cut-off radius neglect all pairwise interactions
+$\mathcal O(N)$.  The cut-off radius neglects all pairwise interactions
 outside the cut-off radius, so it introduces an error in the interaction
@@
 achieved even with a very small cut-off value, for example,
-$2.5\sigma$.  Moreover, it is possible to correct the systematic error
+$2.5\sigma$ for the standard Lennard-Jones 6-12 interaction.
+Moreover, it is possible to correct the systematic error
 of the potential energy, the pressure and the free energy by applying
@@
 contribution of the mentioned properties to infinity. 
-% The spacial inhomogenety of the system in terms of particle density,
+% The spacial inhomogeneity of the system in terms of particle density,
 % particle type and change distribution is very common in natrual
 % system.
-Instead for inhomogeneous systems, in which the density of certain type of
-atom changes within the length scale of several molecules, 
+Instead for inhomogeneous systems, in which the density of a certain type of
+atom may change within the length scale of a few molecules, 
 and thus lack of uniformity, 
-the direct molecular simulation 
+the standard molecular simulation 
 by the cut-off method will encounter non-trivial
@@
 the error. In homogeneous systems, the error analysis of the cut-off
-method has been well established, see~\cite{kolafa1992cutoff} for
+method has been well established, see~\cite{kolafa1992cutoff, wang2011} for
 example. Also the error estimates~\cite{hummer1995numerical,
@@
 cut-off radius.  In an inhomogeneous system composed by several bulk
-regions, an important observation is that the inhomogeneity error can
-be more than one order of magnitude larger than the homogeneity
-error, and plays a dominant role in the interfacial region. An
+regions connected by interfacial regions where the density changes
+rapidly, an important observation is that the
+inhomogeneity error plays a dominant role in the interfacial regions,
+and can be more than one order of magnitude larger than
+the error in the bulk regions. An
 adaptive cut-off method is hereby proposed to equally distribute the
-error across the simulation region, so that a substantial
-computational effort can be saved while the precision of simulation is
+error across the simulation region, so that a considerable
+computational effort can be saved in the bulk regions
+while the precision of simulation is
 preserved. We also proposed a long-range force correction (LFC) method
-based on the error estimate to screen out the contribution of the
-inhomogeneity error, which can tremendously improve the precision of
-simulation without much extra computational load. To show the
+to screen out the contribution of the
+inhomogeneity error, therefore,  the precision of
+simulation is improved without much extra computational load. To show the
 effectiveness of the error estimate and the proposed methods, two
@@
 % In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
-% standard Lennard-Jone particles is set up in a tube with periodic
+% standard Lennard-Jones particles is set up in a tube with periodic
 % boundary condition. The liquid droplet (in the middle of the tube) is
@@
 In this paper, we developed the force error estimate for non-bonded
-short-range interaction in the inhomogeneous molecular system.  The
+short-range interactions in the inhomogeneous molecular systems. The
 RMS force error can be expressed by a summation of a homogeneity
@@
 of the error distribution was that the homogeneity error dominates the
-bulk material region, whereas the inhomogeneity error dominates the
-interfacial region where the density changes within the length scale
-of several molecules. The inhomogeneity error can be more than one
+bulk material regions, whereas the inhomogeneity error dominates the
+interfacial regions where the density changes within the length scale
+of a few molecules. The inhomogeneity error can be more than one
 order of magnitude larger than the homogeneity error.  Two methods
@@
 simulation. The adaptive cut-off method uses smaller cut-off radius
-for the low-error bulk region and larger cut-off radius for the
-high-error interfacial region, so that the RMS force error is
+for the low-error bulk regions and larger cut-off radius for the
+high-error interfacial regions, so that the RMS force error is
 uniformly distributed over the simulation region. The long-range force

### 2011-12-16 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter-1.tex
add letter.to.referee and graphical.abstract

\documentclass{letter}

\usepackage{graphicx}

\renewcommand{\baselinestretch}{1.0}
% \setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
% \sloppy

\address{Institute for Mathematics \\
  Freie Universit\"at Berlin\\
  Arnimallee 6\\
  14195 Berlin, Germany 
}
\signature{Han Wang}

% \def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
% \def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
% \def\urldot{\kern -.10em.\kern -.10em}
% \def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
% \parindent0ex

\begin{document}

\begin{letter}{
    The Referees of\\
    Physical Chemistry Chemical Physics\\
    \vskip 1cm
  }
% \begin{picture}(0,0)
%   \put(-30,22){
%     \parbox{0.25\textwidth}{
% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
%     }
%   }
%   \put(264,10){
%     \parbox{0.25\textwidth}{
% 	\includegraphics[scale=0.28]{Fub-logo.eps}
%     }
%   }
% \end{picture}

\opening{Dear Referees,\vskip .5cm}
Hereby we would like to submit our article:\\

\textbf{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}\\

by H. Wang, Christof Sch\"utte and P. Zhang to:\\

\textbf{Physical Chemistry Chemical Physics}, as a regular article.\\

The molecular dynamics simulation of the inhomogeneous molecular
systems, in which the density of a certain type of atom is lack of
uniformity, will encounter non-trivial difficulties by using the
standard cut-off method. The simulation results are found to converge
only at a very large cut-off radius, so it is computationally very
expensive to obtain precise measurement of the physical properties.\\

To quantitatively study the cut-off artifact, we developed an accurate
error estimate of the standard cut-off method for the inhomogeneous
systems. We proved that the root mean square force error is decomposed
into three additive parts: the homogeneity error, the inhomogeneity
error and the correlation error.  An important observation is that the
inhomogeneity error is dominant in the interfacial regions where the
density changes rapidly, and can be more than one order of magnitude
larger than the error in the bulk regions where the density is
comparatively uniform.  Therefore, a large cut-off value should be
used to suppress the maximum error in the interfacial regions, but at
the mean time,
considerable computational effort is wasted in the bulk regions. \\

We proposed the adaptive cut-off and the force correction method to
avoid the mentioned problem. The adaptive cut-off method uses different
cut-off radii for the interfacial and bulk regions so that the error
is uniformly distributed across the system. The force correction
method removes the inhomogeneity error, therefore, the precision of
force calculation is improved, so a smaller cut-off radius is
acceptable. Both of the proposed methods relies on the quantitative
analysis of the short-range force error.  The effectiveness of
the proposed methods were checked by molecular dynamics simulations of
the liquid-vapor equilibrium and the nanoscale
particle collision.\\

Most of previous error estimates in this field assumed the homogeneity
of the system. As far as we know, the present work for the first time
proposed an error estimate for the short-range interactions in the
inhomogeneous molecular systems, presenting new phenomena that do not
happen in the homogeneous systems.  We showed that the adaptive cut-off
and the force correction methods greatly improve the efficiency and
accuracy, and successfully avoid the problem of the standard cut-off
method, so they should be of special interest for
understanding the inhomogeneous molecular systems, and for
designing high
performance molecular simulation softwares.
\\
\vskip 3cm

\closing{Best regards,}
  % \put(-85,-50){\includegraphics[scale=0.2]{zhang-signature.pdf}}
% }

\end{letter} \end{document}

### 2011-12-16 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter.tex
add letter.to.referee and graphical.abstract

--- 2011-12-16 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter-1.tex
@@
-\documentclass{letter}
+\documentclass{scrlttr2}
+\usepackage{graphicx}
+\usepackage{hyperref}
+% provides a justified text without hyphenation
+\usepackage[none]{hyphenat}
+\renewcommand{\baselinestretch}{1.0}
+\setlength{\footskip}{0cm}
+%\addtolength{\textheight}{10cm}
+\sloppy
 
-\usepackage{graphicx}
-
-\renewcommand{\baselinestretch}{1.0}
-% \setlength{\footskip}{0cm}
-%\addtolength{\textheight}{10cm}
-% \sloppy
-
-\address{Institute for Mathematics \\
+\KOMAoptions{foldmarks=false,fromalign=left,fromrule=true,fromlogo=false,backaddress=false}
+\setkomavar{fromname}{Dr. Han Wang}
+\setkomavar{fromaddress}
+{Department of Mathematics \& Computer Science \\
   Freie Universit\"at Berlin\\
@@
 }
-\signature{Han Wang}
 
-% \def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
-% \def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
-% \def\urldot{\kern -.10em.\kern -.10em}
-% \def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
-% \parindent0ex
+\def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
+\def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
+\def\urldot{\kern -.10em.\kern -.10em}
+\def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
+\parindent0ex
 
 \begin{document}
+\makeatletter
+\@setplength{toaddrvpos}{6em}
+\@setplength{sigbeforevskip}{0.5em}
+\@setplength{sigindent}{0em}
+\@setplength{refvpos}{35ex}
 
@@
     Physical Chemistry Chemical Physics\\
-    \vskip 1cm
+    \vskip 0cm
   }
-% \begin{picture}(0,0)
-%   \put(-30,22){
-%     \parbox{0.25\textwidth}{
-% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
-%     }
-%   }
-%   \put(264,10){
-%     \parbox{0.25\textwidth}{
-% 	\includegraphics[scale=0.28]{Fub-logo.eps}
-%     }
-%   }
-% \end{picture}
+\begin{picture}(0,0)
+  \put(-30,22){
+    \parbox{0.25\textwidth}{
+%	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
+    }
+  }
+  \put(264,10){
+    \parbox{0.25\textwidth}{
+	\includegraphics[scale=0.28]{Fub-logo.pdf}
+    }
+  }
+\end{picture}
 
-\opening{Dear Referees,\vskip .5cm}
+\opening{Dear Referees,}
 Hereby we would like to submit our article:\\
@@
 inhomogeneous molecular systems, presenting new phenomena that do not
-happen in the homogeneous systems.  We showed that the adaptive cut-off
+happen in the homogeneous systems.  We shew that the adaptive cut-off
 and the force correction methods greatly improve the efficiency and
 accuracy, and successfully avoid the problem of the standard cut-off
-method, so they should be of special interest for
-understanding the inhomogeneous molecular systems, and for
-designing high
-performance molecular simulation softwares.
+method, so they should be of special interest for designing high
+performance molecular simulation software.
 \\
-\vskip 3cm
 
-\closing{Best regards,}
+\closing{Best regards,
   % \put(-85,-50){\includegraphics[scale=0.2]{zhang-signature.pdf}}
-% }
+}
+
+% \newpage
+
+% \parindent0ex \textbf{Corresponding author}:\\
+
+% \qquad Pingwen Zhang
+
+% \qquad LMAM and School of Mathematical Sciences
+
+% \qquad Peking University
+
+% \qquad 100871 Beijing, P.R. China
+
+% \qquad Phone: +86-10-62759851
+
+% \qquad Fax: +86-10-62751801
+
+% \qquad \href{mailto:pzhang@pku.edu.cn}{\tt pzhang@pku.edu.cn} \\
+
+% \parindent0ex\textbf{Referees}:\\
+% Furthermore as knowledgeable referees in this field we suggest:
+% \begin{itemize}
+% \item Christoph Dellago \\
+%   Faculty of Physics\\
+%   University of Vienna\\
+%   Boltzmanngasse 5 (1st floor, room 3105) \\
+%   1090 Vienna\\
+%   Austria\\
+%   \href{mailto:Christoph.Dellago@univie.ac.at}{\tt Christoph.Dellago@univie.ac.at}
+% \item Giovanni Ciccotti \\
+%   Department of Physics \\
+%   University of Roma "La Sapienza"\\
+%   P.le Aldo Moro 5\\
+%   00185 Roma\\
+%   Italy\\
+%   \href{mailto:giovanni.ciccotti@phys.uniroma1.it}{\tt giovanni.ciccotti@phys.uniroma1.it}
+% \item Daan Frenkel\\
+%   Cambridge University Centre for Computational Chemistry\\
+%   Department of Chemistry\\
+%   Lensfield Road\\
+%   Cambridge CB2 1EW\\
+%   United Kindom\\
+%   \href{mailto:df246@cam.ac.uk}{\tt df246@cam.ac.uk}
+% \item Kurt Binder\\
+%   KOMET 331 \\
+%   Institute of Physics\\
+%   Johannes Gutenberg University Mainz \\
+%   D 55099 Mainz \\
+%   Germany\\
+%   \href{mailto:kurt.binder@uni-mainz.de}{\tt kurt.binder@uni-mainz.de}
+% \end{itemize}
+
+% \parindent0ex\textbf{Color figures}:
+% \begin{itemize}
+%   \item[] A main aspect of the article is accuracy, therefore even smallest
+%     deviations should be recognizable in the plots. Though we already used
+%     different line styles, coloring is inevitable to distinguish the various
+%     amount of information correctly. Therefore we regard colored versions of
+%     Figure 1 and 2 as essential to provide a clear picture for the reader.
+% \end{itemize}
 

### 2012-02-08 longRange.hetero/writeDown/main.tex
backup

@@
       &\,0, &\quad & \vert\v r\vert \leq r_c;\\
-      &\frac{\textrm{erfc}(\beta\vert\v r\vert)}{\vert\v r\vert},& & \vert\v r\vert > r_c,
+      &,& & \vert\v r\vert > r_c,
+      % \frac{\textrm{erfc}(\beta\vert\v r\vert)}{\vert\v r\vert}
     \end{aligned}
@@
 \begin{align}\nonumber
-  \Delta\v F(\v r_i)
+  \Delta\v F^{\textrm{ik}}(\v r_i)
   =\;&
@@
   \big\langle
-  \Delta\v F(\v r_i)
+  \Delta\v F^{\textrm{ik}}(\v r_i)
   \big\rangle
@@
   \big\langle
-  \vert\Delta\v F(\v r_i)\vert^2
+  \vert\Delta\v F^{\textrm{ik}}(\v r_i)\vert^2
   \big\rangle
@@
   \big\langle
-  \Delta\v F(\v r_i)
+  \Delta\v F^{\textrm{ik}}(\v r_i)
   \big\rangle  ^2
@@
 \begin{align}\nonumber
-  \Delta\v F(\v r_i)
+  \Delta\v F^{\textrm{ana}}(\v r_i)
   =\;&
@@
   & +\,
-  q_i
+  q^2_i
   \sum_{
@@
 \begin{align} \nonumber
-  \langle \Delta\v F(\v r_i)\rangle
+  \langle \Delta\v F^{\textrm{ana}}(\v r_i)\rangle
   =\;&
@@
   2\pi i\,l K_\alpha\v a_\alpha^\ast\,e^{2\pi i\,l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
-  [F_{\alpha,l}\ast\rho_q](\v r_i) \\
+  [F_{\alpha,l}\ast\rho_q](\v r_i) \\\label{eqn:tmp30}
   &+\,
-  q_i\sum_{\alpha}\sum_{l\neq 0}
+  q^2_i\sum_{\alpha}\sum_{l\neq 0}
   2\pi i\,l K_\alpha\v a_\alpha^\ast\,e^{2\pi i\,l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
   C_{\alpha,l}^{\textrm{self}}
+\end{align}
+Neglecting all high frequency terms, we have:
+\begin{align}\label{eqn:tmp31}
+  \langle \Delta\v F^{\textrm{ana}}(\v r_i)\rangle
+  \approx
+  \langle \Delta\v F^{\textrm{ik}}(\v r_i)\rangle,
 \end{align}
@@
   \big\langle
-  \vert \Delta\v F(\v r_i)\vert^2
+  \vert \Delta\v F^{\textrm{ana}}(\v r_i)\vert^2
   \big\rangle
@@
   \ast \rho_{q^2}
-  \,\bigg] (\v r_i)
-  +\,
-  4q_i^2\,
-  \bigg[
-  \big(
-  \sum_{\alpha} \sum_{l\neq 0}  
-  \v G_{\alpha,l}
-  \big)^2
-  \ast \rho_{q^2}\,
-  \bigg] (\v r_i) \\\nonumber
+  \,\bigg] (\v r_i)\\\nonumber
   & +\,
@@
   \bigg]
-  (\v r_i) \\
+  (\v r_i) \\\nonumber
   & +\,
-  \big\langle \Delta\v F(\v r_i)\big\rangle ^2
+  4q_i^2\,
+  \bigg[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)^2
+  \ast \rho_{q^2}\,
+  \bigg] (\v r_i) \\
+  & +\,
+  \big\langle \Delta\v F^{\textrm{ana}}(\v r_i)\big\rangle ^2
 \end{align}
+It worthwhile noting that it will be problemetic to use
+Eq. \eqref{eqn:tmp31} to calculate $\langle \Delta\v F^{\textrm{ana}}(\v r_i)\rangle
+^2$, because by squaring the mean error force, the second and third
+terms in Eq. \eqref{eqn:tmp30} will generate non-trivial low frequency
+terms. Neglecting all high frequency terms, we have:
+\begin{align}\nonumber
+  \big\langle \Delta\v F^{\textrm{ana}}(\v r_i)\big\rangle ^2
+  \approx&\,
+  \big\langle \Delta\v F^{\textrm{ik}}(\v r_i)\big\rangle ^2 \\\nonumber
+  &\,
+  +q_i^2 \sum_{\alpha}\sum_{l\neq 0}
+  4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[F_{\alpha,l}\ast\rho_q]^2 (\v r_i) \\
+  &\,
+  +q_i^4 \sum_{\alpha}\sum_{l\neq 0}
+  4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 
+\end{align}
+the second one on the right hand side is always small, so
+\begin{align}\nonumber
+  \big\langle
+  \vert \Delta\v F^{\textrm{ana}}(\v r_i)\vert^2
+  \big\rangle
+  =&\,
+  q_i^2
+  \bigg[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\bigg] (\v r_i) \\\nonumber
+  & +\,
+  q_i^2
+  \bigg[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}
+  \vert
+  \v G_{\alpha,l} + 2\pi i\,l K_\alpha F_{\alpha,l} \v a_\alpha^\ast\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \bigg]
+  (\v r_i) \\ \nonumber
+  & +\,
+  4q_i^2\,
+  \bigg[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)^2
+  \ast \rho_{q^2}\,
+  \bigg] (\v r_i) \\\nonumber
+  & +\,
+  \big\langle \Delta\v F^{\textrm{ik}}(\v r_i)\big\rangle ^2\\
+  &+\,
+  q_i^4 \sum_{\alpha}\sum_{l\neq 0}
+  4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 
+\end{align}
+the last one is a constant that stems from the self-interaction.
 
 \section{Numerical tests}
+
+We consider two inhomogeneous charge system to verify our error
+estimate.  The first is locally neutral and globally inhomogeneous
+charge system. In the second system, the positive and negative charges
+are well seperated, while the number density of the charges is
+uniform.
+
+\subsection{Example 1: locally neutral}
+
+In this example, 16800 charges are put into a $40\textsf{nm}\times
+20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
+them are carrying a unit positive charge of $+e$, and the other half
+are carrying negative charge of $-e$. The position of these charges
+are randomly generated subject to density distribution shown in
+Fig.~\ref{fig:tmp-rho0}. Both the positive and negative charge
+distributions are spacially inhomogeneous, while the system is locally
+neutral, because the positive and negative charge distributions cancel
+each other.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
+  \caption{Charge distribution of Example 1. The red line
+    denotes the positive charge distribution, while the blue line
+    denotes the negative charge distribution. Since all distributions
+    are uniform on $y$ and $z$ direction, they are plotted as a
+    function of $x$.}
+  \label{fig:tmp-rho0}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
+  \caption{Example 1: the actual (denoted by dots) and estimated
+    (denoted by straight lines) mean error force of the direct part
+    $\langle\Delta \v F_{\textrm{dir}}(\v r)\rangle$ (red), reciprocal
+    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}(\v
+    r)\rangle$ (green) and the reciprocal part of the analytical
+    differentiation $\langle\Delta \v
+    F^{\textrm{ana}}_{\textrm{rec}}(\v r)\rangle$ (blue). The total
+    mean error force of analytical differentiation $\langle\Delta \v
+    F^{\textrm{ana}}(\v r)\rangle$ is given in pink.  Since the charge
+    distribution is uniform on the $y$ and $z$ direction, the $y$ and
+    $z$ dimension of the mean error force is averaged, and the errors
+    are plotted on $x$ direction.  The cut-off in the real space is 3
+    \textsf{nm}, the number of freedom in the reciprocal space is
+    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
+    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
+    the analytical differentiation is 6.}
+  \label{fig:meanf1}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
+  \caption{Example 1: the actual (denoted by dots) and estimated
+    (denoted by straight lines) RMS force error of the direct part
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}(\v
+      r)\vert^2\rangle}$ (red), reciprocal part of Ewald summation
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}(\v
+      r)\vert^2\rangle}$ (green) and the reciprocal part of the
+    analytical differentiation $\sqrt{\langle\vert\Delta \v
+      F^{\textrm{ana}}_{\textrm{rec}}(\v r)\vert^2\rangle}$
+    (blue). The RMS force error of analytical differentiation
+    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
+      r)\vert^2\rangle}$ is given in pink.  Since the charge
+    distribution is uniform on the $y$ and $z$ direction, the $y$ and
+    $z$ dimension of the mean error force is averaged, and the errors
+    are plotted on $x$ direction.  The cut-off in the real space is 3
+    \textsf{nm}, the number of freedom in the reciprocal space is
+    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
+    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
+    the analytical differentiation is 6.}
+  \label{fig:error1}
+\end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.meanf.eps}
+%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.meanf.eps}
+%   \caption{Resulting mean error force}
+%   \label{fig:tmp1}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.error.eps}
+%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.error.eps}
+%   \caption{Resulting RMS errors}
+%   \label{fig:tmp2}
+% \end{figure}
+
+\subsection{Example 2: seperated positive and negative charge}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
+  \caption{Charge distribution of Example 2. The red line
+    denotes the positive charge distribution, while the blue line
+    denotes the negative charge distribution. Since all distributions
+    are uniform on $y$ and $z$ direction, they are plotted as a
+    function of $x$.}
+  \label{fig:tmp-rho2}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
+  \caption{Example 2: the actual (denoted by dots) and estimated
+    (denoted by straight lines) mean error force of the direct part
+    $\langle\Delta \v F_{\textrm{dir}}(\v r)\rangle$ (red), reciprocal
+    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}(\v
+    r)\rangle$ (green) and the reciprocal part of the analytical
+    differentiation $\langle\Delta \v
+    F^{\textrm{ana}}_{\textrm{rec}}(\v r)\rangle$ (blue). The total
+    mean error force of analytical differentiation $\langle\Delta \v
+    F^{\textrm{ana}}(\v r)\rangle$ is given in pink.  Since the charge
+    distribution is uniform on the $y$ and $z$ direction, the $y$ and
+    $z$ dimension of the mean error force is averaged, and the errors
+    are plotted on $x$ direction.  The cut-off in the real space is 3
+    \textsf{nm}, the number of freedom in the reciprocal space is
+    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
+    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
+    the analytical differentiation is 6.}
+  \label{fig:meanf2}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
+  \caption{Example 2: the actual (denoted by dots) and estimated
+    (denoted by straight lines) RMS force error of the direct part
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}(\v
+      r)\vert^2\rangle}$ (red), reciprocal part of Ewald summation
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}(\v
+      r)\vert^2\rangle}$ (green) and the reciprocal part of the
+    analytical differentiation $\sqrt{\langle\vert\Delta \v
+      F^{\textrm{ana}}_{\textrm{rec}}(\v r)\vert^2\rangle}$
+    (blue). The RMS force error of analytical differentiation
+    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
+      r)\vert^2\rangle}$ is given in pink.  Since the charge
+    distribution is uniform on the $y$ and $z$ direction, the $y$ and
+    $z$ dimension of the mean error force is averaged, and the errors
+    are plotted on $x$ direction.  The cut-off in the real space is 3
+    \textsf{nm}, the number of freedom in the reciprocal space is
+    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
+    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
+    the analytical differentiation is 6.}
+  \label{fig:error2}
+\end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.meanf.eps}
+%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.meanf.eps}
+%   \caption{Resulting mean error force}
+%   \label{fig:tmp3}
+% \end{figure}
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.error.eps}
+%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.error.eps}
+%   \caption{Resulting RMS errors}
+%   \label{fig:tmp4}
+% \end{figure}
 

### 2012-02-27 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter-jctc.tex
add missing files

--- 2011-12-16 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter-1.tex
@@
 \begin{letter}{
-    The Referees of\\
-    Physical Chemistry Chemical Physics\\
+    The Editors of\\
+    Journal of Chemical Theory and Computation\\
     \vskip 1cm
@@
 
-\opening{Dear Referees,\vskip .5cm}
+\opening{Dear Editors,\vskip .5cm}
 Hereby we would like to submit our article:\\
@@
 
-\textbf{Physical Chemistry Chemical Physics}, as a regular article.\\
+\textbf{Journal of Chemical Theory and Computation}, as a regular article.\\
 

### 2012-02-27 shortRange.inhomo/alltext/pubilsh.jcp/tex/main.tex
add pubilsh.jcp

--- 2011-12-16 shortRange.inhomo/alltext/pubilsh/main.tex
@@
-\documentclass[aps,pre,preprint]{revtex4}
+\documentclass[preprint]{revtex4}
 % \documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 radius.
-% before deriving conclusions on the origianl system.
 
@@
 contribution of the mentioned properties to infinity. 
-% The spacial inhomogeneity of the system in terms of particle density,
-% particle type and change distribution is very common in natrual
-% system.
 Instead for inhomogeneous systems, in which the density of a certain type of
@@
 the inhomogeneous systems.
-
-% In this paper, we focus on the systems in which
-% atoms/particles are interacting via short-range interactions, because
-% it is a good starting point of the study of more complex systems, for
-% example, the systems with long-range electrostatic interactions.  The
-% simulation results in the inhomogeneous systems are found to depend on
-% a number of factors of treating the short-range interaction in the
-% simulation. For example, the way of calculating the short-range
-% interaction (simple cut-off method or Ewald
-% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
-%   lopez2006liquid, shi2006molecular, ismail2007application}, the
-% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
-%   shen2007comparative}, the way of long-range
-% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
-%   goujon2004monte} and the size and shape of the simulation
-% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
-% It should be noticed that the physical properties are the nature of
-% the system, and should NOT depend on the details of the interaction
-% calculation.
 
@@
 \ref{sec:conclusion}.
-
-% The error estimate of long-range algorithms, for example the Ewald
-% family method~\cite{ewald1921die, hockney1988computer,
-%   deserno1998mue1, darden1993pme, essmann1995spm} and the fast
-% multipole method~\cite{greengard1987fast}, has been well developped in
-% the past 20 years ~\cite{hummer1995numerical, kolafa1992cutoff,
-%   petersen1995accuracy, deserno1998mue2, wang2010optimizing,
-%   dachsel2009error}.
 
@@
 
-% In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
-% standard Lennard-Jones particles is set up in a tube with periodic
-% boundary condition. The liquid droplet (in the middle of the tube) is
-% in equilibrium with the surrounding vapor environment. The red line in
-% the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
-% of this inhomogeneous system. The green square denotes the real RMS
-% force error distribution. It is clear that the error form two peaks in
-% the interfacial region, which is much higher than the relative
-% constant error of the bulk liquid and the bulk vapor. The dashed and
-% the dotted blue line are the estimated homogeneity and inhomogeneity
-% errors, and the solid blue line is the sum. In the bulk region, the
-% homogeneity error dominates while in the interfacial region, the
-% inhomogeneity error dominates. The esitmated error matches perfactly
-% with the real error at the interfacial region, but presents
-% overestimation in the bulk regions. The overestimation probably stems
-% from the neglection of the correlation error in \eqref{eqn:tmp5}.
-
 A basic observation in an inhomogeneous system is that the RMS force
@@
 \subsection{Long-range pressure correction}
-% By the cut-off method, the system lost the pressure contribution from
-% the particles outside the cut-off radius.  In the homogeneous systems,
-% the distribution of particles is assumed to be uniform outside the
-% cut-off radius, and the pressure correction is calculated by
-% integrating the virial from the cut-off to infinity.
-
-% In the inhomogeneous systems, the previous idea does not
-% work. Instead, the pressure correction of the system are:
 
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{figs/confout.eps}
+  \includegraphics[width=0.9\textwidth]{confout.eps}
   \caption{The snapshot of the 16000 Lennard-Jones particle system in
@@
   \centering
-  \includegraphics[]{figs/error.uniform.eps}
+  \includegraphics[]{error.uniform.eps}
   \caption{The RMS force error distribution of the 16000 Lennard-Jones
@@
 
-% The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
-% method: in the bulk regions, the error is much smaller, therefore, it
-% is a waste to use the same cut-off radius as the interfacial
-% regions.
 As mentioned before, the key idea of the adaptive cut-off simulation
@@
   \centering
-  \includegraphics[]{figs/rcut.and.error.eps}
+  \includegraphics[]{rcut.and.error.eps}
   \caption{ The RMS force error distribution of the 16000
@@
 
-% Clearly the contribution of the inhomogeneity
-% error is successfully removed, because the estimate of homogeneity
-% error follows the real error perfectly in the interfacial regions.  In
-% the bulk liquid region, the homogeneity error is slightly
-% overestimated, which is the same as the uniform and adaptive cut-off
-% simulations.
-
 \begin{figure}
   \centering
-  \includegraphics[]{figs/fcorr.and.error.eps}
+  \includegraphics[]{fcorr.and.error.eps}
   \caption{ The RMS force error distribution of the 16000
@@
 
-% As mentioned before, form Fig. \ref{fig:tmp2}, the error dominates at
-% the interfacial regions. The error estimate is sharp in these
-% regions. While in the bulk regions, the error estimate is not sharp,
-% but still acceptable. By the adapt cut-off radius MD, the resulting
-% distribution (averaged on $y$ and $z$ directions) of cut-off radius is
-% given in Fig. \ref{fig:tmp3}. In the interfacial regions, the cut-off
-% radius is adapted to $r_c^\ast = 7.5$. In the bulk liquid and vapor
-% regions, the cut-off radii are approximatly $5.0$ and $3.5$.  The
-% resulting error distribution is ploted in FIg. \ref{fig:tmp4}. It is
-% clear that the error is comparatively uniformly distributed in the
-% space. The estimate inhomogeneity error is also dominant at the
-% interfacial region, while the homogeneous error dominants in the bulk
-% regions.  Since the computational cost is proportional to $r_c^3$,
-% comparing with a simulation using uniform cut-off radius $7.5$, the
-% adaptive cut-off simulation saves 3.4 times and 9.8 times
-% computational cost, respectively. In total, the adaptive cut-off
-% radius method save 50\% of the computational cost.
-
-% We test the uniform and adaptive cut-off methods as well as the
-% correction force method in the mentioned liquid vapor equilibrium
-% system.
-
 To test the effectiveness of the proposed adaptive cut-off and
@@
 to the cut-off radius is considered.
-% For the adaptive cut-off
-% simulation, the ``cut-off radius'' means the largest cut-off radius
-% used in the simulation region.
 
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{figs/t0.85.gas.eps} 
-  \includegraphics[width=0.49\textwidth]{figs/t0.85.liquid.eps} 
+  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
+  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
   \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{figs/tension.t0.85.eps} 
+  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
   \caption{$T^\ast = 0.85$. The convergence of the surface tension
@@
 
-% \begin{table}
-%   \centering
-%   \caption{
-%     The maximum RMS force error and computational cost of 
-%     three methods, namely the uniform cut-off
-%     (URC), the adaptive cut-off (ARC) and the long-range
-%     force correction (LFC) method.
-%     The computational cost is the number of pairwise interaction 
-%     measurements, which should be mashine-independent.
-%   }\label{tab:tmp1}
-%   \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-%     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-% %     & 3.5 &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
-% %     &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
-% %     & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
-% %     &     &\textrm{LFC} & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
-% %     &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
-% % 0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
-% %     &     &\textrm{LFC} & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
-% %     &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
-% %     &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
-% %     &     &\textrm{LFC} & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
-%     &     &\textrm{URC} & $8.6\times 10^{-2}$ & 2.9 \\
-%     & 3.5 &\textrm{ARC} & $6.7\times 10^{-2}$ & 2.1 \\
-%     &     &\textrm{LFC} & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
-%     &     &\textrm{URC} & $2.2\times 10^{-2}$ & 7.8 \\
-%     & 5.0 &\textrm{ARC} & $1.9\times 10^{-2}$ & 4.6 \\
-%     &     &\textrm{LFC} & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
-%     &     &\textrm{URC} & $4.5\times 10^{-3}$ & 24 \\
-% 0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
-%     &     &\textrm{LFC} & $2.3\times 10^{-4}$ & 24 \\\cline{2-5}
-%     &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
-%     &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
-%     &     &\textrm{LFC} & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
-%   \end{tabular*}
-% %   \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
-% %     $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
-% %     & 3.5 &\textrm{LFC} & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
-% %     &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
-% %     & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
-% %     &     &\textrm{LFC} & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
-% %     &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
-% % 1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
-% %     &     &\textrm{LFC} & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
-% %     &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
-% %     &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
-% %     &     &\textrm{LFC} & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
-% % %     & 3.5 &\textrm{LFC} & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
-% % %     &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
-% % %     & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
-% % %     &     &\textrm{LFC} & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
-% % %     &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
-% % % 1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
-% % %     &     &\textrm{LFC} & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
-% % %     &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
-% % %     &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
-% % %     &     &\textrm{LFC} & $3.3\times 10^{-5}$ & 31 \\\hline\hline
-% %   \end{tabular*}
-% \end{table}
-
 In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
@@
 
-% In the higher
-% temperature cases, the thermodynamic flucuation of the system is
-% stronger. Therefore, the meansurement of densities and surface tension
-% are less accurate.
-% At $T^\ast = 0.70$, the gas
-% density converges much faster than the liquid density, while at
-% $T^\ast = 1.20$, the gas and liquid densities almost converges at the
-% same speed, see Fig. \ref{fig:tmp5}.
-
 The liquid and gas densities of the uniform and the adaptive cut-off
@@
 
-% With the
-% same cut-off radius, the computational cost of the force correction is
-% nearly the same as the uniform cut-off methods, see
-% Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is more
-% than one order of maganitude better.
-
-% However, the maximum
-% force error of the force correction method is reduced by about one
-% order of maganitude.
-% We also observe that the liquid densities are systemetically higher
-% than the reference results. This fact will be discussed latter by
-% comparing with literature results.
-
 The surface tension result of the force correction without pressure
@@
   that the uncorrected tension calculation is far from convergence.
-  % the extend of which is shown by the
-  % the amount of the correction calculated by the pressure correction method.
 }
-% However, even at $r_c^\ast=10$, this correction is not
-% negligible, so it is very important for the precise surface tension
-% calculation.
 
@@
 Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
-% In the force correction simulation, the
-% inhomogeneity error is screened out and the force error term is
-% dominated by the homogeneity error. And in the uniform cut-off
-% simulation the force error is dominated by the inhomogeneity error.
 Since the homogeneity error dominates in the former simulation and the
@@
   an accurate calculation of the density profile is impossible.
-  % In
-  % the latter case, the MD simulation are not trivial anyway, for
-  % example, the simulation of critical point.
-  % For these two cases, the traditional MD simulation is also not easy
-  % to handel.
   In our
@@
   temperature, or a snapshot from another force correction simulation.
-  % or the state of the system changes too fast
-  % comparing with the correction force updating fequency
   We also observe that the equilibration of the force-corrected
@@
 
-% To verify our simulations, we compare our results in
-% Tab. \ref{tab:comparison} with a wide range of results reported by
-% literature~\cite{janecek2006long, lotfi1992vapour,
-%   errington2003evaluating, ismail2007application}
-
-% We list in Tab. \ref{tab:comparison} a wide range of results reported
-% by literature~\cite{janecek2006long, lotfi1992vapour,
-%   errington2003evaluating, ismail2007application}, as well as our
-% uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
-% results for comparison. The abbreviations in the table are explained
-% in the caption. The MC/LEC, MD/Ewald and our methods are direct
-% simulation of the inhomogeneous system. The MD/Npt+test particle and
-% MC/GC-TMMC methods are simulation of homogeneous systems that do not
-% have the difficulties of inhomogeneity, and are believed to be more
-% precise than direct simulations~\cite{shen2007comparative}.
-
-% \begin{table}
-%   \centering
-%   \caption{Equilibrium densities and surface tension comparision 
-%     with various literature results: Monte Carlo with long-range
-%     energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
-%     particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
-%     grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
-%     molecular dynamics with dispersion term calculated by the Ewald
-%     summation (MD/Ewald)~\cite{ismail2007application}
-%     and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
-%     proposed by this work. The surface tensions of this work are
-%     corrected by the long-range pressure correction.
-%     The cut-off radius of the Ewald summation is for the real space.
-%   }
-%   \label{tab:comparison}
-%   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
-%   % \begin{tabular}{cccc|cccc}\hline\hline
-%     $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
-%     0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
-%     0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
-%     0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
-%     % 0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
-%     0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
-%     % 0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
-%     0.70 & MD/LFC               & 3.5      & 0.8430(4)   & 0.00209(9)  & 1.139(16) & this work \\\hline
-%     0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
-%     0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
-%     % 0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
-%     0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
-%     % 0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
-%     0.85 & MD/LFC               & 3.5      & 0.7761(3)   & 0.00986(16) & 0.794(15) & this work\\\hline
-%     1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
-%     1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
-%     1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
-%     % 1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
-%     1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
-%     % 1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
-%     1.10 & MD/LFC               & 3.5      & 0.6411(10)   & 0.0559(6)   & 0.302(11)  & this work\\ \hline
-%     1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
-%     1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
-%     % 1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
-%     1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(6) & this work\\
-%     % 1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
-%     1.20 & MD/LFC               & 3.5      & 0.5632(14)  & 0.1002(19)  & 0.130(8) & this work\\
-%     \hline\hline
-%   % \end{tabular}
-%   \end{tabular*}
-% \end{table}
-
-% The reason is the corrected error force has a varnished mean
-% value (, so it may point to any
-% direction with the same possibility.  With the same cut-off radius,
-% the computational cost of the force correction and uniform cut-off
-% methods are nearly the same, see Tab. \ref{tab:tmp1}. However, the
-% maximum force error of the force correction method is about one order
-% of maganitude more precise, comparing with the uniform cut-off
-% simulations.
-
-% The convergence of the surface tension with respect to the cut-off
-% radius is shown in the Fig. \ref{fig:tmp6}. The color notation is the
-% same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
-% without inhomogeneous pressure correction are connected by solid and
-% dashed lines, respectively.  The reference surface tension is
-% presented by the black solid lines. The inhomogeneous pressure
-% correction improve the surface tention measurement greatly. The
-% discrepancy between the corrected and uncorrected pressure is the
-% value of the correction, which decreases with increasing cut-off
-% radius. However, even at $r_c^\ast=10$, the correction is not
-% negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
-% temperature, the statistical uncertainty gets larger, and better
-% convergence is achieved at small cut-off radius.
-
-% Although the force correction is a
-% little better, no substential difference between the different
-% simulation methods is observed. However, the With the
-% pressure correction, the result is acceptable at cut-off 5.0 and
-% satisfactorily converged at cut-off 7.5.
-
-% The equilibrium liquid and vapor densities with respect to
-% the cut-off radius are presented in Fig. \ref{fig:tmp5}. For the
-% adaptive cut-off simulation, the data points represent the largest
-% cut-off radius used in the simulations. All the results are
-% substracted by the reference results, which are calculated at uniform
-% cut-off radius of 13, for a clear comparison. Solid and dashed lines
-% are added to the data points of vapor and liquid densities
-% respectively. For the uniform and adaptive cut-off simulations, the
-% cut-off radii 5, 7.5 and 10 are considered. For the force correction,
-% the cut-off 3.5 is investigated in addition. We perform simulations at
-% different temperature: that are denoted in the plots.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.adapt.eps}
-%   \caption{The adapted cut-off radius of the 16000 Lennard-Jones
-%     particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp3}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/error.adapt.eps}
-%   \caption{The error distribution of the adaptive-cut-off 16000
-%     Lennard-Jones particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp4}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.eps}
-%   \caption{The correction force simulation of the 16000 Lennard-Jones
-%     particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp3}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/error.fcorr.eps}
-%   \caption{The correction force simulation of the adaptive-cut-off 16000
-%     Lennard-Jones particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp4}
-% \end{figure}
-
 \subsection{Collision of nanoscale Lennard-Jones clusters}
@@
   \centering
-  \includegraphics[]{figs/init.2.eps}
+  \includegraphics[]{init.2.eps}
   \caption{The initial setup of cluster $A$ and $B$. The initial
@@
   \centering
-  \includegraphics[]{figs/trajs.eps}
+  \includegraphics[]{trajs.eps}
   \caption{The center of mass trajectory of cluster A. Uniform cut-off
@@
   \centering
-  \includegraphics[]{figs/dists.eps}
+  \includegraphics[]{dists.eps}
   \caption{The COM distance between cluster $A$ and cluster $B$ versus
@@
   \centering
-  \includegraphics[width=0.90\textwidth]{figs/error-rcut-ball.eps} 
-  \includegraphics[width=0.90\textwidth]{figs/error-rcut.eps}
+  \includegraphics[width=0.90\textwidth]{error-rcut-ball.eps} 
+  \includegraphics[width=0.90\textwidth]{error-rcut.eps}
   \caption{The colliding clusters (the first row), the RMS force error
@@
   \centering
-  \includegraphics[]{figs/wy.eps}
+  \includegraphics[]{wy.eps}
   \caption{The angular velocity of cluster $A$ versus time. Uniform
@@
   \centering
-  \includegraphics[]{figs/ly.eps}
+  \includegraphics[]{ly.eps}
   \caption{The angular moment of cluster $A$ versus time. Uniform
@@
   \centering
-  \includegraphics[]{figs/cost.eps}
+  \includegraphics[]{cost.eps}
   \caption{The computational cost versus time. Uniform
@@
 
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+\begin{thebibliography}{10}
+
+\bibitem{frenkel02b}
+Daan Frenkel and Berend Smit.
+\newblock {\em Understanding Molecular Simulation}.
+\newblock Academic Press, San Diego, second edition, 2002.
+
+\bibitem{allen87a}
+Mike~P. Allen and Dominik~J. Tildesley.
+\newblock {\em Computer Simulation of Liquids}.
+\newblock Oxford Science Publications. Clarendon Press, Oxford, 1 edition,
+  1987.
+
+\bibitem{duque2004some}
+D.~Duque and L.F. Vega.
+\newblock Some issues on the calculation of interfacial properties by molecular
+  simulation.
+\newblock {\em The Journal of chemical physics}, 121:8611, 2004.
+
+\bibitem{ismail2007application}
+P.J. in~'t Veld, A.E. Ismail, and G.S. Grest.
+\newblock Application of ewald summations to long-range dispersion forces.
+\newblock {\em The Journal of Chemical Physics}, 127:144711, 2007.
+
+\bibitem{trokhymchuk1999computer}
+A.~Trokhymchuk and J.~Alejandre.
+\newblock Computer simulations of liquid/vapor interface in lennard-jones
+  fluids: Some questions and answers.
+\newblock {\em The Journal of Chemical Physics}, 111:8510, 1999.
+
+\bibitem{guo1997long}
+MX~Guo and BC~Lu.
+\newblock Long-range corrections to thermodynamic properties of inhomogeneous
+  systems with planar interfaces.
+\newblock {\em Journal of Chemical Physics}, 106(9):3688--3695, 1997.
+
+\bibitem{mecke1997molecular}
+M.~Mecke, J.~Winkelmann, and J.~Fischer.
+\newblock Molecular dynamics simulation of the liquid-vapor interface: The
+  lennard-jones fluid.
+\newblock {\em Journal of Chemical Physics}, 107(21):9264--9270, 1997.
+
+\bibitem{janecek2006long}
+J.~Jane{c}ek.
+\newblock Long range corrections in inhomogeneous simulations.
+\newblock {\em J. Phys. Chem. B}, 110(12):6264--6269, 2006.
+
+\bibitem{goujon2004monte}
+F.~Goujon, P.~Malfreyt, J.M. Simon, A.~Boutin, B.~Rousseau, and A.H. Fuchs.
+\newblock Monte carlo versus molecular dynamics simulations in heterogeneous
+  systems: An application to the n-pentane liquid-vapor interface.
+\newblock {\em The Journal of chemical physics}, 121:12559, 2004.
+
+\bibitem{shen2007comparative}
+V.K. Shen, R.D. Mountain, and J.R. Errington.
+\newblock Comparative study of the effect of tail corrections on surface
+  tension determined by molecular simulation.
+\newblock {\em J. Phys. Chem. B}, 111(22):6198--6207, 2007.
+
+\bibitem{kolafa1992cutoff}
+J.~Kolafa and J.W. Perram.
+\newblock Cutoff errors in the ewald summation formulae for point charge
+  systems.
+\newblock {\em Molecular Simulation}, 9(5):351--368, 1992.
+
+\bibitem{wang2011}
+H.~Wang and P.~Zhang.
+\newblock Optimizing working parameters of the twin-range cutoff method in
+  terms of accuracy and efficiency.
+\newblock {\em submitted}, 2011.
+
+\bibitem{hummer1995numerical}
+G.~Hummer.
+\newblock The numerical accuracy of truncated ewald sums for periodic systems
+  with long-range coulomb interactions.
+\newblock {\em Chemical physics letters}, 235(3-4):297--302, 1995.
+
+\bibitem{petersen1995accuracy}
+H.G. Petersen.
+\newblock Accuracy and efficiency of the particle mesh ewald method.
+\newblock {\em The Journal of chemical physics}, 103:3668, 1995.
+
+\bibitem{deserno1998mue2}
+M.~Deserno and C.~Holm.
+\newblock How to mesh up ewald sums. ii. an accurate error estimate for the
+  particle--particle--particle-mesh algorithm.
+\newblock {\em The Journal of Chemical Physics}, 109:7694, 1998.
+
+\bibitem{wang2010optimizing}
+H.~Wang, F.~Dommert, and C.~Holm.
+\newblock Optimizing working parameters of the smooth particle mesh ewald
+  algorithm in terms of accuracy and efficiency.
+\newblock {\em The Journal of chemical physics}, 133:034117, 2010.
+
+\bibitem{ewald1921die}
+P.~P. Ewald.
+\newblock Die berechnung optischer und elektrostatischer gitterpotentiale.
+\newblock {\em Ann. Phys.}, 369(3):253--287, 1921.
+
+\bibitem{hockney1988computer}
+R.~W. Hockney and J.~W. Eastwood.
+\newblock {\em Computer Simulation Using Particles}.
+\newblock IOP, London, 1988.
+
+\bibitem{deserno1998mue1}
+M.~Deserno and C.~Holm.
+\newblock How to mesh up ewald sums. i. a theoretical and numerical comparison
+  of various particle mesh routines.
+\newblock {\em The Journal of Chemical Physics}, 109:7678, 1998.
+
+\bibitem{darden1993pme}
+T.~Darden, D.~York, and L.~Pedersen.
+\newblock Particle mesh ewald: An n· log (n) method for ewald sums in large
+  systems.
+\newblock {\em The Journal of Chemical Physics}, 98:10089, 1993.
+
+\bibitem{essmann1995spm}
+U.~Essmann, L.~Perera, M.L. Berkowitz, T.~Darden, H.~Lee, and L.G. Pedersen.
+\newblock A smooth particle mesh ewald method.
+\newblock {\em The Journal of Chemical Physics}, 103(19):8577, 1995.
+
+\bibitem{limbach06a}
+H.~J. Limbach, A.~Arnold, B.~A. Mann, and C.~Holm.
+\newblock {ESPResSo} -- an extensible simulation package for research on soft
+  matter systems.
+\newblock {\em Comp. Phys. Comm.}, 174(9):704--727, May 2006.
+
+\bibitem{flyvbjerg1989error}
+H.~Flyvbjerg and HG~Petersen.
+\newblock Error estimates on averages of correlated data.
+\newblock {\em The Journal of Chemical Physics}, 91:461, 1989.
+
+\bibitem{nose1984molecular}
+S.~Nos{\'e}.
+\newblock A molecular dynamics method for simulations in the canonical
+  ensemble.
+\newblock {\em Molecular Physics}, 52(2):255--268, 1984.
+
+\bibitem{hoover1985canonical}
+W.G. Hoover.
+\newblock Canonical dynamics: Equilibrium phase-space distributions.
+\newblock {\em Physical Review A}, 31(3):1695--1697, 1985.
+
+\bibitem{chen1995area}
+L.J. Chen.
+\newblock Area dependence of the surface tension of a lennard-jones fluid from
+  molecular dynamics simulations.
+\newblock {\em The Journal of chemical physics}, 103:10214, 1995.
+
+\bibitem{orea2005oscillatory}
+P.~Orea, J.~L{\'o}pez-Lemus, and J.~Alejandre.
+\newblock Oscillatory surface tension due to finite-size effects.
+\newblock {\em The Journal of chemical physics}, 123:114702, 2005.
+
+\bibitem{biscay2009calculation}
+F.~Biscay, A.~Ghoufi, F.~Goujon, V.~Lachet, and P.~Malfreyt.
+\newblock Calculation of the surface tension from monte carlo simulations: Does
+  the model impact on the finite-size effects?
+\newblock {\em The Journal of chemical physics}, 130:184710, 2009.
+
+\bibitem{kalweit2006collision}
+M.~Kalweit and D.~Drikakis.
+\newblock Collision dynamics of nanoscale lennard-jones clusters.
+\newblock {\em Physical Review B}, 74(23):235415, 2006.
+
+\end{thebibliography}
 

### 2012-02-29 longRange.hetero/publish/main.tex
add publish

\documentclass[aps,pre,preprint]{revtex4}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\renewcommand{\v}[1]{\textbf{\textit{#1}}}
\renewcommand{\d}[1]{\textsf{#1}}
% \allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}

\begin{document}

\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
\author{Han Wang}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}
\author{Pingwen Zhang}
% \email{pzhang@pku.edu.cn}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}

\begin{abstract}
\end{abstract}

\maketitle

\section{Theory}

\subsection{Error estimate for
  the pairwise interactions in a charged system}

In this paper, we consider the force error, bacause the applicaions
are based on the molecular dynamics simulation.  Suppose the system is
composed by $N$ charged particles located at $\v r_1, \v r_2, \cdots,
\v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.  We study
the force error of an arbitrary charge $i$ by calculating the
difference between the exact force and calculated force exerting on
the charge $i$, which is called the \emph{error force}
\cite{wang2012} and denoted by $\Delta \v F(\v r_i)$.
% and is denoted by
% $\Delta \v F(\v r_i) = \v F(\v r_i) - \tilde{\v F}(\v r_i)$.
The maganitude of the force computation error 
% error of the force computation
is defined by the \emph{root mean square (RMS)} \emph{error}, which is
the square root of the second moment of the error force: $\mathcal
E(\v r_i) = \sqrt{\langle\vert\Delta\v F(\v r_i)\vert^2\rangle}$.  The
notation $\langle\cdot\rangle$ means ensemble average.  We also
estimate the the ensemble average of the error force (also called
\emph{mean error force}), namly $\langle\Delta\v F(\v r_i)\rangle$,
which plays an important role in the error analysis of the
inhomogeneous systems~\cite{wang2012}.

For error the pairwise interactions, we have the following theorem:
\begin{theorem}\label{thm:tmp1}
  Let a periodic molecular system be composed by $N$ charged particles
  located at $\v r_1, \v r_2, \cdots, \v r_N$ with charges $q_1, q_2,
  \cdots, q_N$, respectively.
  % Let the box vectors be $\v a_\alpha, \
  % \alpha=1,2,3$, and denote the lattice in the real space by $\v n =
  % n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, $n_\alpha\in\mathbb Z$.
  If the error force of an arbitary particle $i$ is
  \begin{align}\label{eqn:tmp10}
    \Delta \v F(\v r_i) =
    % \sum^\ast_{\v n}
    \sum_{j=1}^N\,q_iq_j \v K(\v r_i - \v r_j),
  \end{align}
  then the mean error force is
  \begin{align}\label{eqn:tmp11}
    \langle\Delta\v F(\v r_i)\rangle
    =q_i\, [\v K\ast\rho_q](\v r_i),
  \end{align}
  and the RMS error is
  \begin{align}\nonumber
    \mathcal E (\v r_i) 
    = &\,
    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:tmp12}
    &+
    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
    \v K(\v r_i-\v r')\cdot
    \v K(\v r_i-\v r'')\,
    C_{q^2}(\v r', \v r'')\,
    \d d\v r'\d d\v r''.
  \end{align}
  Where $\ast$ denotes the convolution, and
  % The $\rho_q$, $\rho_{q^2}$ and
  % $C_{q^2}$ are defined by:
  \begin{align}\label{eqn:tmp13}
    \rho_q(\v r)
    &= 
    \bigg\langle
    \sum_{j = 1}^N
    \,q_j\,\delta(\v r - \v r_j)
    \bigg\rangle,\\\label{eqn:tmp14}
    \rho_{q^2}(\v r)
    &= 
    \bigg\langle
    \sum_{j = 1}^N
    \,q^2_j\,\delta(\v r - \v r_j)
    \bigg\rangle,\\\label{eqn:tmp15}
    C_{q^2}(\v r', \v r'')
    &=
    \bigg\langle
    \sum_{i\neq j}
    q_iq_j\delta(\v r'-\v r_i)\delta(\v r''-\v r_j)
    \bigg\rangle
    - \rho_q(\v r')\rho_q(\v r'').
  \end{align}
  Notice the definitions of $\rho_q(\v r)$, $\rho_{q^2}(\v r)$ and
  $C_{q^2}(\v r', \v r'')$ are periodically extended to
  $\mathbb{R}^3$, $\mathbb{R}^3$ and $\mathbb{R}^3\times\mathbb R^3$,
  respectively.
\end{theorem}
\begin{proof}
  By definition, the mean error force is:
  \begin{align*}
    \langle\Delta\v F(\v r_i)\rangle
    &=
    q_i\bigg\langle \sum_{j=1}^Nq_j\v K(\v r_i -\v r_j)\bigg\rangle\\
    &=
    q_i\int_{\mathbb R^3}\v K(\v r_i - \v r')
    \bigg\langle \sum_{j=1}^Nq_j\delta (\v r' -\v r_j)\bigg\rangle
    \,\d d\v r'\\
    &= 
    q_i\, [\v K\ast\rho_q](\v r_i),
  \end{align*}
  The RMS force error is calculated by:
  \begin{align*} \nonumber
    \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
    =\,&
    q_i^2\bigg\langle\sum_{j,k}
    q_jq_k\v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)\bigg\rangle \\ \nonumber
    =\,&
    q_i^2\bigg\langle\sum_{j=1}^N
    q_j^2\vert\v K(\v r - \v r_j)\vert^2
    \bigg\rangle +
    q_i^2\bigg\langle\sum_{j\neq k}
    q_jq_k \v K(\v r - \v r_j)\cdot\v K(\v r - \v r_k)
    \bigg\rangle \\ \nonumber
    =\,&
    q_i^2\int_{\mathbb R^3}
    \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
    \\
    & +
    q_i^2\int_{\mathbb R^3\times\mathbb R^3}
    \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
    [\,\rho_q(\v r')\rho_q(\v r'') + C_{q_2}(\v r',\v r'')\,]
    \,\d d\v r'\d d\v r''\\
    = \,&
    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\
    &+
    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
    \v K(\v r_i-\v r')\cdot
    \v K(\v r_i-\v r'')\,
    C_{q^2}(\v r', \v r'')\,
    \d d\v r'\d d\v r''. \qquad\qed
    % \int_{\mathbb R^3\times\mathbb R^3}\v K(\v r - \v r')\cdot\v K(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
  \end{align*}
\end{proof}
Here are some remarks concerning Theorem~\ref{thm:tmp1}:
\begin{itemize}
\item The function $\v K(\v r)$ is called \emph{the error force
    kernel}.
  % It should be well defined for $\v r = \v 0$. For
  % the cut-off method, $\v K(\v 0) = \v 0$. For the reciprocal part 
\item The densities $\rho_q(\v r)$ and $\rho_{q^2}(\v r)$ defined in
  Eqn.~\eqref{eqn:tmp13} and \eqref{eqn:tmp14} are called \emph{the
    first order charge density distribution (CDD)} and \emph{the
    second order charge density distribution},
  respectively. $C_{q^2}(\v r, \v r')$ defined in
  Eqn.~\eqref{eqn:tmp15} is the pairwise charge correlation function.
\item Analog to the short-range error estimate~\cite{wang2012}, the
  three terms on the r.h.s. of Eqn.~\eqref{eqn:tmp12} are called the
  homogeneity error, the inhomogeneity error and the correlation
  error, respectively. The homogeneity error and the inhomogeneity
  error can be calculated at the cost of $\mathcal O(N\log N)$ by the
  fast Fourier transform (FFT) (see Ref.~\cite{wang2012} for details).
  However, the calculation of the correlation error costs $\mathcal
  O(N^2\log N)$, because it involves a twofold convolution. In this
  study, the contribution of the correlation error is neglicted.
  % In
  % section~\ref{sec:tmp3}, it is shown neglicting the 
\item A non-zero mean error force~\eqref{eqn:tmp11} was proof to be
  harmful to the simulation in the case of the short-range force
  calculation~\cite{wang2012}.  In the case of the charge system, this
  term is non-zero only when the system is NOT locally neutral. For
  most of the simulation cases, the locally neutral condition is
  satisfied, so the mean error force and the inhomogeneity error
  vanish.
  % The
  % serious artifical effect due to the inhomogeneity error of
  % short-range interaction~\cite{wang2012} does not exist in most
  % charged systems.
\end{itemize}

\subsection{Ewald summation and its error estimate}
The Ewald method divides the electrostatic interaction in to three
parts: the direct part, the reciprocal part and the correction
part. that is
\begin{equation}
E = E_{\textrm{dir}} + E_{\textrm{rec}} + E_{\textrm{corr}},
\end{equation}
where 
\begin {align}\label{eqn:tmp2}
E_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
\sum_{i,j = 1}^{N} \frac{q_iq_j \textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}
{\vert\v{r}_{ij} + \v{n}\vert} \\\label{eqn:tmp3}
E_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
\frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m) \\\label{eqn:tmp4}
 E_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
\end {align}
The distance between the two particles is denoted by $\v r_{ij} = \v
r_i - \v r_j$, where $\v r_i$ and $\v r_j$ are positions of particle
$i$ and $j$, respectively.  The lattice in the real space is denoted
by $\v n = n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, where $\v a_\alpha,
\ \alpha=1,2,3$ are box vectors. the structure factor $S(\v m)$ is
defined by
\begin{equation}\label{sm1}
S(\v m) = \sum_{j=1}^N q_j \exp (2 \pi i \v m \cdot \v r_j),
\end{equation}
where $\v m = m_1 \v a_1^\ast + m_2 \v a_2^\ast + m_3 \v a_3^\ast$ is
the reciprocal space lattice vectors. $\v a_\alpha^\ast,\ \alpha = 1,
2, 3$ are conjugate reciprocal vectors of $\v a_\alpha$, defined by
$\v a_\alpha \cdot \v a_\beta^\ast = \delta_{\alpha\beta}$. and $V =
\v a_1 \cdot \v a_2 \times \v a_3$ is the volume of the box.

The complementary error function $\textrm{erfc}(r)$ in
Eqn.~\eqref{eqn:tmp2} decays exponentially as $r$ goes to infinity.
Therefore, it is a short-range interaction in the real space, which
can be calculated by the standard cut-off and neighbor list
method~\cite{frenkel02b} at a cost of $\mathcal O(N)$.  The reciprocal
part also decays exponentially as the maganitude of the Fourier mode
$\vert\v m\vert$ increases. Therefore, in practice, the infinit
summation in Eqn.~\eqref{eqn:tmp3} is truncated, and only a finite
summation is calculated:
% Both the direct and the reciprocal parts are calculated by cut-off in
% real and reciprocal space, respectively.
% For the reciprocal part the cut-offed energy reads
\begin{align}\label{eqn:tmp6}
  E^{\textrm{tr}}_{\textrm{rec}} & =
  % \frac1{2\pi V}
  \sum_{
    \begin{subarray}{c}
      \vert m_\alpha\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  % \frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m)   
  f(\v m)\, S(\v m) S(-\v m),
\end{align}
where, for short,
\begin{align}
  f(\v m) := \frac{\exp(-\pi^2 \v m^2 / \beta^2)}{2\pi V \v m^2},
\end{align}
and $K_\alpha$ is the number of Fourier modes used on direction
$\alpha$.  The truncated reciprocal force acting on particle $i$ is
\begin{align}\nonumber
  \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
  &= - 
  q_i 
  \sum_{
    \begin{subarray}{c}
      \vert m_\alpha\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m) \,
  S(-\v m)\,
  e^{2\pi i\v m\cdot\v r_i}, \\\label{eqn:tmp8}
  &= - 
  \sum_j   q_iq_j
  \sum_{
    \begin{subarray}{c}
      \vert m_\alpha\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m) \,
  e^{2\pi i\v m\cdot\v r_{ij}},
\end{align}
where
\begin{align}
  \v g(\v m) = -4 \pi \v m i f(\v m).
\end{align}

% Ref.~\cite{wang2010optimizing} pointed out that it is reasonable and
% convenient to estimate the error for the direct and reciprocal part
% seperately, namely $\Delta\v F(\v r_i) = \Delta\v F_{\textrm{dir}}(\v
% r_i) + \Delta\v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)$.  The
% $\Delta\v F_{\textrm{dir}}$ and $ \Delta\v
% F^{\textrm{tr}}_{\textrm{rec}}$ denote the direct error force and
% reciprocal error force, respectively.  The superscript ``tr'' denotes
% the reciprocal force is calculated by truncating the infinite Ewald
% summation. Other superscripts are introduced later in the paper to
% denote the error force of the fast algoritms
% that treat the Ewald summation more elaborately.

Both the direct part and reciprocal part of the Ewald summation can be
written in the form of Eqn.~\eqref{eqn:tmp11}.  The direct
error force kernel is defined by:
% The direct part is a short-range interaction in real space, so it is
% usually treated by the cut-off method, which gives a error force
% kernel of
\begin{align}
  \v K^{\textrm{cut}}_{\textrm{dir}}(\v r) =
  \left\{
    \begin{aligned}
      &\,0, &\quad & r \leq r_c;\\
      &
      \Big[
      \frac{2\beta}{\sqrt\pi} e^{-\beta^2r^2} + \frac{\textrm{erfc}(\beta r)}{r}
      \Big]\frac{\v r}{r^2}
      ,& & r > r_c,
      % \frac{\textrm{erfc}(\beta\vert\v r\vert)}{\vert\v r\vert}
    \end{aligned}
  \right.
\end{align}
where $r = \vert\v r\vert$, and $r_c$ is the cut-off radius in the
real space.
% The reciprocal error force, namely the difference between
% the the exact and truncated reciprocal force, is
% \begin{align}
%   \Delta \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
%   = & - 
%   \sum_j\,q_iq_j
%   \sum_{\vert m_\alpha\vert \geq K_\alpha/2}
%   \v g(\v m) \,
%   e^{2\pi i\v m\cdot\v r_{ij}}.
% \end{align}
% Therefore,
The reciprocal error force kernel is given by:
\begin{align}
  \v K^{\textrm{tr}}_{\textrm{rec}}(\v r) =
  \sum_{
      \vert m_\alpha\vert \geq K_\alpha/2}
  \v g(\v m) \,
  e^{2\pi i\v m\cdot\v r}.
\end{align}
By the Therefore \ref{thm:tmp1}, the error estimate of the
truncated Ewald summation is straightforward.

% Ref. \cite{short} pointed out that the inhomogeneity error is more
% harmful than the homogeneity error, so it is interesting to analyze
% the inhomogeneity error. Apply the Fourier transform on both sides of
% Eqn. \eqref{eqn:tmp10} and \eqref{eqn:tmp18}:
% \begin{align}  
%   \langle\Delta\v F_{\textrm{dir}}\rangle^\wedge(\v m)
%   &= q_i\,\hat{\v K}^c_{\textrm{dir}}(\v m)\cdot\hat\rho_q(\v m)\\
%   \langle\Delta\v F_{\textrm{rec}}\rangle^\wedge(\v m)
%   &= -q_i\,\hat{\v K}^c_{\textrm{rec}}(\v m)\cdot\hat\rho_q(\v m)
% \end{align}
% If the charge distribution is \emph{locally} neutral, then all modes
% of the first order density distribution vanishes, and $\langle\Delta\v
% F_{\textrm{dir}}\rangle = \langle\Delta\v F_{\textrm{rec}}\rangle = 0$.

\subsection{The smooth particle mesh Ewald method}

The naive calculation of the reciprocal Ewald summation
\eqref{eqn:tmp6} will result in a computational cost of $\mathcal
O(N^2)$. It has been shown that with a careful tuning of parameter
$\beta$ and the reciprocal space truncation $K_\alpha$, the
computational cost is reduced to $\mathcal O(N^{3/2})$
\cite{perram1988asc}, which becomes not applicable when the system
size is larger than several hundreds of charged particles. Both the
particle mesh Ewald (PME) \cite{darden1993pme} and the smooth particle
mesh Ewald (SPME) \cite{essmann1995spm} methods are designed to reduce
the computational cost to $\mathcal O(N\log N)$ in nearly the same
way.  Since the SPME method is more precise \cite{deserno1998mue1} and
more popular than the PME, we will focus our discussion on the
former. All the error estimates develop by the current paper can be
easily extended to PME method.  The principle idea of the SPME method
is first to calculate the term $e^{2\pi i\v m\cdot\v r}$ on a uniform
lattice in the real space.  Therefore, all Fourier transforms can be
accerlerated by the fast Fourier transform (FFT), that is why the
computational cost of SPME is reduced to $\mathcal O(N\log N)$. Then,
for any particle position $\v r_i$, the value of $e^{2\pi i\v m\cdot\v
  r_i}$ is interpolated by the known values on the neighboring lattice
points.  The PME method uses Lagrangian interpolation, while the SPME
uses B-spline interpolation that is more precise, and has higher order
of smoothness.

The SPME method provides two possibilities of calculating the
reciprocal force. The first one is to differentiate (with respect to
the particle position) the reciprocal term of the truncated Ewald
energy and then approximate the derived force \eqref{eqn:tmp8} by the
B-spline interplation. This way is called
\emph{ik--differentiation}. The alternative way notices the high-order
smoothness of the B-spline interpolation, and derive the force by
differentiating the B-spline approximated reciprocal Ewald energy
(also truncated). This way was proposed by the original SPME paper
\cite{essmann1995spm}, and is called the \emph{analytical
  differentiation}.  It has been shown that using the same parameters,
the ik-differentiation is more precise than the analytical
differentiation, but it requres twice more FFTs, which is a bottleneck
for the communication in parallel
implementations~\cite{wang2010optimizing}. Since the SPME method is
not the point of the present paper, we refer the readers to, for
example, Ref. \cite{essmann1995spm, deserno1998mue1,
  wang2010optimizing} for details of this method.

\subsection{Error estimate of the ik-differentiation}

From the precise calculation of the reciprocal summation to the SPME
fast algorithm, the electrostatic interaction is approximated by two
steps.  The first step is the truncation of the reciprocal summation,
i.e. Eqn. \eqref{eqn:tmp6}. The second step is the approximation of
$e^{2\pi i\v m\cdot\v r}$ by B-spline
interpolation. Ref. \cite{wang2010optimizing} has pointed out that the
error due to the first step is negligible comparing with the second
step, at least for the parameters of practical interest. Numerical
examples supporting this argument in inhomogeneous systems are also
given in Section \ref{sec:tmp3}.  Therefore, to estimate the force
error, it is enough to compare the SPME force with the
\emph{truncated} Ewald force \eqref{eqn:tmp8}.

As mentioned above, the SPME error mainly oringinated from approximate
the term $e^{2\pi i\v m\cdot\v r}$ by the B-spline
interpolation. Denote the error introduced by this approximation by
$A(\v m, \v r)\,e^{2\pi i\v m\cdot \v r}$, we are fortunate to have
the analytical expression of $A(\v m, \v r)$:
\begin{align}\label{eqn:tmp18}
  A(\v m, \v r)
  =
  \sum_{\alpha=1}^3\sum_{l\neq 0}
  \frac
  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  {\sum\limits_{l=-\infty}^{+\infty}
    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  \bigg(
  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 1
  \bigg).
\end{align}
The error force of the ik-differentiation is therfore
\begin{align}\nonumber
  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
  =\;&
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m)\,
  A(\v m, \v r_i)\,
  e^{2\pi i\v m\cdot \v r_i}
  \sum_{j\neq i}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
  & +\,
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m)\,
  e^{2\pi i\v m\cdot \v r_i}
  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:tmp19}
  & +\,
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m)\,
  \big[
  A(\v m, \v r_i) +
  A(\v m, -\v r_i)
  \big].
\end{align}
The last ``self-interacting term'' is zero, because of the
symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$.  Unfortunately, the
error force of ik-differentiation~\eqref{eqn:tmp19} cannot be written
in the form of~\eqref{eqn:tmp11}, so the error estimate derived by
Theorem~\ref{thm:tmp1} cannot be used here. However, it is still
possible to develop the error estimate for the ik-differentiation.
Here we only want to present the key idea and the formula of the error
estimate, and leave all details to the Appendix \ref{}.  We notice the
term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot\v r}$ with $l\neq 0$
in Eqn.~\eqref{eqn:tmp18} introduces some high-wave-number terms in
the expression of the error estimate.  If $K_\alpha$ is large enough,
then due to the thermal fluctuation of the system, the peaks and
valleys of the high-wave-number terms may canncels in the the
emsemble-averaged error estimate.
% Based on this observation, it is
% still possible to develop the error estimate for the
% ik-differentiation.
% And if the high wave number terms are neglected,
Therefore, by neglecting these terms, it is proved that the mean error
force of the ik-differentiation is
\begin{align}
  \big\langle
  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
  \big\rangle
  & \approx
  - 2 q_i
  \bigg[
  \big(
  \sum_{\alpha}\sum_{l\neq 0}\v G_{\alpha,l}
  \big)
  \ast\rho_q\,
  \bigg] (\v r_i),
\end{align}
% Also neglect the high wave number terms,
and the RMS force error is 
\begin{align}\nonumber
  \big\langle
  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2
  \big\rangle
  \approx&\, 
  2q_i^2
  \bigg[\,
  \big(
  \sum_{\alpha} \sum_{l\neq 0}
  \vert \v G_{\alpha,l}\vert^2
  \big)
  \ast \rho_{q^2}
  \,\bigg] (\v r_i)
  +
  4q_i^2\,
  \bigg[
  \big(
  \sum_{\alpha} \sum_{l\neq 0}  
  \v G_{\alpha,l}
  \big)^2
  \ast \rho_{q^2}\,
  \bigg] (\v r_i) \\
  &\,+
  \big\langle
  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
  \big\rangle^2.
\end{align}
Where
\begin{align}
  \v G_{\alpha,l}(\v r) =
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  \v g(\v m)\,
  \frac
  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  {\sum\limits_{l=-\infty}^{+\infty}
    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  e^{2\pi i\v m\cdot\v r}.
\end{align}
$G_{\alpha,l}(\v r)$ does not depends on the coordinates of particles,
so it can be calculated once and stored in a table for further uses.

\subsection{Error estimate of the analytical differetiation}

The error force of the analytical differetiation is 
\begin{align}\nonumber
  \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)
  =\;&
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,
  \nabla_{\v r_i}
  e^{2\pi i\v m\cdot \v r_i}
  \sum_{j\neq i}q_j\,
  A(\v m, -\v r_j)
  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
  & +\,
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,
  \nabla_{\v r_i}
  [A(\v m, \v r_i)\,
  e^{2\pi i\v m\cdot \v r_i} ]
  \sum_{j\neq i}q_j\,
  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
  & +\,
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\\nonumber
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,
  A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\
  & +\,
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,
  e^{-2\pi i\v m\cdot \v r_i}
  \nabla_{\v r_i} [\,A(\v m, \v r_i) \,e^{2\pi i\v m\cdot\v r_i}\,]  \\\nonumber
  =&\,
  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\\\nonumber
  & +\,
  q_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,
  \v B(\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i}
  \sum_{j\neq i}q_j\,
  e^{-2\pi i\v m\cdot\v r_j} \\\label{eqn:ana.error.force}
  & +\,
  q^2_i
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  -2f(\v m)\,\v B(\v m, \v r_i) 
\end{align}
With $\v B(\v m, \v r)$ defined by
\begin{align}\nonumber
  \v B(\v m, \v r)
  &=
  \nabla_{\v r_i}A(\v m, \v r)\\
  &=
  \sum_{\alpha=1}^3\sum_{l\neq 0}
  \frac
  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  {\sum\limits_{l=-\infty}^{+\infty}
    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  2\pi i l K_\alpha\v a_\alpha^\ast\,e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
\end{align}
The last term in Eqn.~\eqref{eqn:ana.error.force} is due to the
self-interaction~\cite{cerutti2009staggered, ballenegger2011removal,
  neelov2010interlaced}, which does not depends on the coordinates of
particles. Therefore, it can be calculated explicitly, and substracted
from the analytical force during the simulation. The computational cost of
the self-interacting term costs is very low comparing with the SPME
force calculation.

Neglecting all high frequency terms, we have the mean error force of
analytical differetiation:
\begin{align}\label{eqn:tmp31}
  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\rangle
  \approx
  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\rangle.
\end{align}
The RMS force error is 
\begin{align}\nonumber
  \big\langle
  \vert \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\vert^2
  \big\rangle
  \approx&\,
  q_i^2
  \bigg[\,
  \big(
  \sum_{\alpha} \sum_{l\neq 0}
  \vert \v G_{\alpha,l}\vert^2
  \big)
  \ast \rho_{q^2}
  \,\bigg] (\v r_i) \\\nonumber
  & +\,
  q_i^2
  \bigg[
  \big(
  \sum_{\alpha}\sum_{l\neq 0}
  \vert
  \v G_{\alpha,l} + 2\pi i\,l K_\alpha F_{\alpha,l} \v a_\alpha^\ast\vert^2
  \big)
  \ast \rho_{q^2}
  \bigg]
  (\v r_i) \\ \nonumber
  & +\,
  4q_i^2\,
  \bigg[
  \big(
  \sum_{\alpha} \sum_{l\neq 0}  
  \v G_{\alpha,l}
  \big)^2
  \ast \rho_{q^2}\,
  \bigg] (\v r_i) \\\nonumber
  & +\,
  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2\\
  &+\,
  q_i^4 \sum_{\alpha}\sum_{l\neq 0}
  4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 .
\end{align}
% The last one is a constant that stems from the self-interaction, which
% do not depends on the
Where
\begin{align}
  F_{\alpha,l} (\v r)
  &=
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  (-2)f(\v m)\,
  \frac
  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  {\sum\limits_{l=-\infty}^{+\infty}
    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}\,
  e^{2\pi i\v m\cdot \v r},\\
  C_{\alpha,l}^{\textrm{self}}
  &= 
  \sum_{
    \begin{subarray}{c}
      \vert m_{\alpha}\vert < K_\alpha/2\\
      \v m\neq 0
    \end{subarray}}
  (-2)f(\v m)\,
  \frac
  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
  {\sum\limits_{l=-\infty}^{+\infty}
    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}.
\end{align}
$F_{\alpha,l} (\v r)$ and $C_{\alpha,l}^{\textrm{self}}$ 
do not depends on the coordinates of particles,
so they can be tabulated in advance for the simulation.

\subsection{The error estimate of the total force}

In the previous subsections, we estimate the error of direct part and
reciprocal part seperately. Here we provide the error estimate for the
total force. The mean of the total error force is simply:
\begin{align}
  \langle\Delta\v F^{\textrm{x}}(\v r_i) \rangle
  &=
  \langle\Delta\v F_{\textrm{dir}}(\v r_i) \rangle +
  \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) \rangle,
\end{align}
where \textrm{x} can be \textrm{tr}, \textrm{ik} or \textrm{ana},
standing for the truncated Ewald summation, the ik-differentiation
and the analytical differetiation, respectively. The mean square
total force is
\begin{align}\nonumber
  \langle\,\vert\Delta\v F^{\textrm{x}}(\v r_i)\vert^2\rangle
  = \,&
  \langle\,\vert
  \Delta\v F_{\textrm{dir}}(\v r_i) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) 
  \vert^2 \rangle \\\nonumber
  = \,&
  \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle +
  \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\vert^2\rangle +
  2\,\langle\Delta\v F_{\textrm{dir}}(\v r_i)\rangle
  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\rangle \\\label{eqn:tmp36}
  &
  + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
\end{align}
Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i), \Delta\v
F^{\textrm{x}}_{\textrm{rec}}(\v r_i))$ denotes the correlation of
$\Delta\v F_{\textrm{dir}}(\v r_i)$ and $\Delta\v
F^{\textrm{x}}_{\textrm{rec}}(\v r_i)$:
\begin{align}\label{eqn:tmp37}
  \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
  & =
  \langle
  \Delta\v F_{\textrm{dir}}(\v r_i)\cdot
  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
  \rangle -
  \langle
  \Delta\v F_{\textrm{dir}}(\v r_i)
  \rangle\cdot
  \langle
  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
  \rangle.
\end{align}
In Eqn.~\eqref{eqn:tmp36}, the estimates of errors
$\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle $,
$\langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
r_i)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
r_i)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
r_i)\rangle $ have been established. In section \ref{sec:tmp3}, it is
shown that the correlation between the direct and reciprocal error
force can be safely neglected.

\section{Numerical tests}\label{sec:tmp3}

We consider two inhomogeneous charge system to verify our error
estimate.  The first is locally neutral and globally inhomogeneous
charge system. In the second system, the positive and negative charges
are well seperated, while the number density of the charges is
uniform.

\subsection{Example 1: locally neutral}

\begin{figure}
  \centering
  \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
  \caption{Charge distribution of Example 1. The red line
    denotes the positive charge distribution, while the blue line
    denotes the negative charge distribution. Since all distributions
    are uniform on $y$ and $z$ direction, they are plotted as a
    function of $x$.}
  \label{fig:tmp-rho0}
\end{figure}

In this example, 16800 charges are put into a $40\textsf{nm}\times
20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
them are carrying a unit positive charge of $+e$, and the other half
are carrying negative charge of $-e$. The position of these charges
are randomly generated subject to density distribution shown in
Fig.~\ref{fig:tmp-rho0}.  The profile of the positive and negative
charge distributions are identical, namely the minus of the negative
distribution is the same as the positive distribution. Therefore the
positive and negative charge distributions cancel each other, and the
system is locally neutral. Both the density distributions are highly
inhomogeneous, take the positive distribution for example: between 11
\textsf{nm} and 29 \textsf{nm}, the charge density is
$1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
$0.05\;\textsf{e/nm}^3$.

\begin{figure}
  \centering
  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
  \caption{Example 1: the actual (denoted by dots) and estimated
    (denoted by straight lines) mean error force of the direct part
    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal
    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}p\rangle$ (green) and the reciprocal part of the analytical
    differentiation $\langle\Delta \v
    F^{\textrm{ana}}_{\textrm{rec}}\rangle$ (blue). The total
    mean error force of analytical differentiation $\langle\Delta \v
    F^{\textrm{ana}}\rangle$ is given in pink.  Since the charge
    distribution is uniform on the $y$ and $z$ direction, the $y$ and
    $z$ dimension of the mean error force is averaged, and the errors
    are plotted on $x$ direction.  The cut-off in the real space is 3
    \textsf{nm}, the number of freedom in the reciprocal space is
    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
    the analytical differentiation is 6.}
  \label{fig:meanf1}
\end{figure}

Fig.~\ref{fig:meanf1} presents the mean error force of the direct part
$\langle\Delta \v F_{\textrm{dir}}\rangle$, reciprocal part of Ewald
summation $\langle\Delta \v F_{\textrm{rec}}\rangle$ and the
reciprocal part of the analytical differentiation $\langle\Delta \v
F^{\textrm{ana}}_{\textrm{rec}}\rangle$. The total mean error force of
analytical differentiation, which is simply $\langle\Delta \v
F^{\textrm{ana}}\rangle = \langle\Delta \v F_{\textrm{dir}}\rangle +
\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$, is also
given.  The real and estimated mean error forces are denoted by dots
and straight lines, respectively. All estimates are consistent very
well with real errors.  Since the system is locally neutral, the first
order charge distribution $\rho_q$ is naturally zero, therefore, by
Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:tmp31}, all
the mean error forces should varnish. Numerical resutls in
Fig. \ref{fig:meanf1} verifies with the above discussion.

\begin{figure}
  \centering
  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
  \caption{Example 1: the actual (denoted by dots) and estimated
    (denoted by straight lines) RMS force error of the direct part
    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$
    (red), reciprocal part of Ewald summation
    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}\vert^2\rangle}$
    (green) and the reciprocal part of the analytical differentiation
    $\sqrt{\langle\vert\Delta \v
      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
    force error of analytical differentiation
    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}\vert^2\rangle}$ is
    given in pink.  Since the charge distribution is uniform on the
    $y$ and $z$ direction, the $y$ and $z$ dimension of the mean error
    force is averaged, and the errors are plotted on $x$ direction.
    The cut-off in the real space is 3 \textsf{nm}, the number of
    freedom in the reciprocal space is $100\times 50\times 50$, the
    parameter $\beta$ is $1.0\; \textsf{nm}^{-1}$ and the order of
    B-spline interpolation used for the analytical differentiation is
    6.}
  \label{fig:error1}
\end{figure}

Fig.~\ref{fig:error1} presents the RMS force error of the direct part
$\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$,
reciprocal part of Ewald summation $\sqrt{\langle\vert\Delta \v
  F_{\textrm{rec}}\vert^2\rangle}$, the reciprocal part of the
analytical differentiation $\sqrt{\langle\vert\Delta \v
  F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ and the total
analytical differentiation force $\sqrt{\langle\vert\Delta \v
  F^{\textrm{ana}}\vert^2\rangle}$.  The real and estimated mean error
forces are denoted by dots and straight lines, respectively. All the
error estimates are overlapping with the real errors, that means the
error estimates developed by the present paper are very sharp.
% Since all mean error forces varnish, the RMS force errors
% consists of only the homogeneous contribution. 
In the high charge density region, the error is comparatively larger
than the low charge density region. For the direct part, the ratio is
roughly the sqare root of the density ratio. For the reciprocal part
this ratio is lower. The reciprocal error of the analytical
differentiation is 4 orders of maganitudes large than that of the
Ewald summation, which means the Ewald summation is much more precice
than the fast algorithm based on mesh discretization.

% \begin{figure}
%   \centering
%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.meanf.eps}
%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.meanf.eps}
%   \caption{Resulting mean error force}
%   \label{fig:tmp1}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.error.eps}
%   \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.error.eps}
%   \caption{Resulting RMS errors}
%   \label{fig:tmp2}
% \end{figure}

\subsection{Example 2: seperated positive and negative charge}

\begin{figure}
  \centering
  \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
  \caption{Charge distribution of Example 2. The red line
    denotes the positive charge distribution, while the blue line
    denotes the negative charge distribution. Since all distributions
    are uniform on $y$ and $z$ direction, they are plotted as a
    function of $x$.}
  \label{fig:tmp-rho2}
\end{figure}

In this example, 16800 charges are put into a $40\textsf{nm}\times
20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
them are carrying a unit positive charge of $+e$, and the other half
are carrying negative charge of $-e$. The position of these charges
are randomly generated subject to density distribution shown in
Fig.~\ref{fig:tmp-rho2}. The nagative charges are seperated from their
counter ions, but the whole system is kept neutral. This case rarely
happen in real simulation, but is serves as a good test of the error
estimates in extreme situations.

\begin{figure}
  \centering
  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
  \caption{Example 2: the actual (denoted by dots) and estimated
    (denoted by straight lines) mean error force of the direct part
    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal part
    of Ewald summation $\langle\Delta \v F_{\textrm{rec}}\rangle$
    (green) and the reciprocal part of the analytical differentiation
    $\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$
    (blue). The total mean error force of analytical differentiation
    $\langle\Delta \v F^{\textrm{ana}}\rangle$ is given in pink.
    Since the charge distribution is uniform on the $y$ and $z$
    direction, the $y$ and $z$ dimension of the mean error force is
    averaged, and the errors are plotted on $x$ direction. The
    algorithmic parameters are the same as Fig.~\ref{fig:meanf1}.}
  \label{fig:meanf2}
\end{figure}

Fig.~\ref{fig:meanf2} shows the mean error forces of Example 2. All
notations in the Figure are the same as Example 1.  Although the
charge distribution is not usual in this case, the error estimates are
accurate. The two peaks of direct mean force error presented at the
positive-negative interface result from the seperation of the positive
and nagative charges, i.e., a non-vanishing first order charge
distribution $\rho_q$.  Similar phenomena were observed by
Ref.~\cite{wang2012}. The reciprocal mean force error is much smaller
than the direct one, so the contribution to the total mean force error
is not important.

\begin{figure}
  \centering
  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
  \caption{Example 2: the actual (denoted by dots) and estimated
    (denoted by straight lines) RMS force error of the direct part
    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}(\v
      r)\vert^2\rangle}$ (red), reciprocal part of Ewald summation
    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}(\v
      r)\vert^2\rangle}$ (green) and the reciprocal part of the
    analytical differentiation $\sqrt{\langle\vert\Delta \v
      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
    force error of analytical differentiation
    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
      r)\vert^2\rangle}$ is given in pink.  Since the charge
    distribution is uniform on the $y$ and $z$ direction, the $y$ and
    $z$ dimension of the mean error force is averaged, and the errors
    are plotted on $x$ direction. The algorithmic parameters are the
    same as Fig.~\ref{fig:meanf1}.}
  \label{fig:error2}
\end{figure}

Fig. \ref{fig:error2} shows the RMS errors of Example 2. The
corresponding error estimates are accurate. In this case the second
order charge distrubution is a constant, therefore the contribution to
the error is also a constant. The same as Example 1, the reciprocal
error of Ewald sum is much smaller than the direct error and the
reciprocal error of analytical differentiation.  The error peak at the
positive-negative interface, is only 3 times larger than the error of
the bulk regions. For the dispersion interaction, the interfacial
error could be more than one order of maganitude larger than the bulk
error. That is because the direct interaction converges much faster
than the dispersion interaciton ($e^{-r^2}$ v.s. $r^{-6}$).

% \begin{figure}
%   \centering
%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.meanf.eps}
%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.meanf.eps}
%   \caption{Resulting mean error force}
%   \label{fig:tmp3}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ik.error.eps}
%   \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.error.eps}
%   \caption{Resulting RMS errors}
%   \label{fig:tmp4}
% \end{figure}

\newpage
\appendix
\section{Error estimate of the Ewald summation}

\newpage

\bibliography{ref}{}
\bibliographystyle{unsrt}

\end{document}

### 2012-02-29 longRange.hetero/publish/fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/parameters.spme.ik.real.sh

@@ -1,0 +1,58 @@
+#!/bin/bash
+
+nframe_real_error=5
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+
+# gen conf parameters
+Lx=40
+Ly=20
+Lz=20
+layerWith=2
+peak_size=20
+rhoh=1.00
+rhol=0.05
+
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rho $rhoh -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+# param for reference force
+beta=1.0
+ref_rcut=6.0
+ref_Kx=129
+ref_Ky=65
+ref_Kz=65
+# regulate parameters. DO NOT MOVE
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+record_dir=$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$ref_rcut.K${ref_Kx}x${ref_Ky}x${ref_Kz}
+record_dir=$config_pool/$record_dir
+
+# param for error estimate
+cal_rcut=3.0
+cal_Kx=101
+cal_Ky=51
+cal_Kz=51
+cal_order=6
+real_h=1.0
+
+# regulate parameters. DO NOT MOVE
+cal_rcut=`printf "%.2f" $cal_rcut`
+cal_Kx=`printf "%03d" $cal_Kx`
+cal_Ky=`printf "%03d" $cal_Ky`
+cal_Kz=`printf "%03d" $cal_Kz`
+cal_order=`printf "%01d" $cal_order`
[…]

### 2012-02-29 longRange.hetero/publish/fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/parameters.spme.ik.real.sh

@@ -1,0 +1,58 @@
+#!/bin/bash
+
+nframe_real_error=5
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+
+# gen conf parameters
+Lx=40
+Ly=20
+Lz=20
+layerWith=2
+peak_size=20
+rhoh=1.00
+rhol=0.05
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rho $rhoh -n 0"
+
+# param for reference force
+beta=1.0
+ref_rcut=6.0
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+record_dir=$project_name.box${Lx}x${Ly}x${Lz}.b$beta.r$ref_rcut.K${ref_Kx}x${ref_Ky}x${ref_Kz}
+record_dir=$config_pool/$record_dir
+
+# param for error estimate
+cal_rcut=3.0
+cal_Kx=101
+cal_Ky=51
+cal_Kz=51
+cal_order=6
+real_h=1.0
+
+# regulate parameters. DO NOT MOVE
+cal_rcut=`printf "%.2f" $cal_rcut`
+cal_Kx=`printf "%03d" $cal_Kx`
+cal_Ky=`printf "%03d" $cal_Ky`
+cal_Kz=`printf "%03d" $cal_Kz`
+cal_order=`printf "%01d" $cal_order`
[…]

### 2012-03-04 longRange.hetero/publish/main.tex
added staggered mesh section

@@
 the analytical expression of $A(\v m, \v r)$:
-\begin{align}\label{eqn:tmp18}
+\begin{align}\label{eqn:error-A}
   A(\v m, \v r)
@@
   \sum_{\alpha=1}^3\sum_{l\neq 0}
-  \frac
+  Z_{\alpha,l}(\v m)
+  (
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 1
+  ),
+\end{align}
+with
+\begin{align}
+  Z_{\alpha,l}(\v m) = \frac
   {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
   {\sum\limits_{l=-\infty}^{+\infty}
-    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
-  \bigg(
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 1
-  \bigg).
+    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}.
 \end{align}
@@
 The last ``self-interacting term'' is zero, because of the
-symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$.  Unfortunately, the
-error force of ik-differentiation~\eqref{eqn:tmp19} cannot be written
+symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$.
+Therefore,
+\begin{align}\nonumber
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
+  =\;&
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  A(\v m, \v r_i)\,
+  e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\label{eqn:ik.error.force}
+  & +\,
+  q_i
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \v g(\v m)\,
+  e^{2\pi i\v m\cdot \v r_i}
+  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}
+\end{align}
+Unfortunately, the
+error force of ik-differentiation~\eqref{eqn:ik.error.force} cannot be written
 in the form of~\eqref{eqn:tmp11}, so the error estimate derived by
@@
 term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot\v r}$ with $l\neq 0$
-in Eqn.~\eqref{eqn:tmp18} introduces some high-wave-number terms in
+in Eqn.~\eqref{eqn:error-A} introduces some high-wave-number terms in
 the expression of the error estimate.  If $K_\alpha$ is large enough,
@@
 force of the ik-differentiation is
-\begin{align}
+\begin{align}\label{eqn:ik.meanf}
   \big\langle
@@
   \ast \rho_{q^2}
-  \,\bigg] (\v r_i)
-  +
+  \,\bigg] (\v r_i)\\\nonumber
+  &\,+
   4q_i^2\,
@@
   \ast \rho_{q^2}\,
-  \bigg] (\v r_i) \\
+  \bigg] (\v r_i) \\\label{eqn:ik.error}
   &\,+
@@
   \v g(\v m)\,
-  \frac
-  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
-  {\sum\limits_{l=-\infty}^{+\infty}
-    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  Z_{\alpha,l}(\v m)\,
   e^{2\pi i\v m\cdot\v r}.
@@
   -2f(\v m)\,
-  A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\
+  A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\\nonumber
   & +\,
@@
   &=
-  \nabla_{\v r_i}A(\v m, \v r)\\
+  \nabla_{\v r}\,A(\v m, \v r)\\
   &=
   \sum_{\alpha=1}^3\sum_{l\neq 0}
-  \frac
-  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
-  {\sum\limits_{l=-\infty}^{+\infty}
-    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
+  Z_{\alpha,l}(\v m)\,
   2\pi i l K_\alpha\v a_\alpha^\ast\,e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
@@
 analytical differetiation:
-\begin{align}\label{eqn:tmp31}
+\begin{align}\label{eqn:ana.meanf}
   \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\rangle
@@
   & +\,
-  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2\\
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2\\\label{eqn:ana.error}
   &+\,
@@
   (-2)f(\v m)\,
-  \frac
-  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
-  {\sum\limits_{l=-\infty}^{+\infty}
-    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}\,
+  Z_{\alpha,l}(\v m)\,
   e^{2\pi i\v m\cdot \v r},\\
@@
   (-2)f(\v m)\,
-  \frac
-  {\big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}
-  {\sum\limits_{l=-\infty}^{+\infty}
-    \big(\dfrac{2\pi m_\alpha}{K_\alpha} + 2\pi l\big)^{-n}}.
+  Z_{\alpha,l}(\v m).
 \end{align}
@@
 so they can be tabulated in advance for the simulation.
+
+\subsection{The staggered Mesh Ewald method}
+
+The staggered Method Ewald method~\cite{cerutti2009staggered,
+  neelov2010interlaced} calculate the reciprocal force on two meshes,
+one of which locates at the middle of the other.  Then the two forces
+are averaged to cancel the error. Here we study the staggered Mesh
+Ewald method from the error point of view.
+The shift of the mesh can be effective treated as shifting all
+particles on the opposite direction. Since the system is periodic, the
+shift to which direction is not important. For convenience, we shift
+all particles to the positive direction for half the grid size, namely
+by a vector $\v s = \sum_\alpha\frac1{2K_\alpha}\v a_\alpha$. From
+Eqn.~\eqref{eqn:error-A}, we have
+\begin{align}
+  \frac12\, [A(\v m, \v r) + A(\v m, \v r+\v s)]
+  =&
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \frac12\,
+  Z_{\alpha,l}(\v m)\,
+  \bigg[
+  (1 + e^{\pi i l})e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 2
+  \bigg].
+\end{align}
+Therefore, when $l$ is odd, $1 + e^{\pi i l}$ vanishes. So the $\frac12\,[A(\v
+m, \v r) + A(\v m, \v r+\v s)]$ can be approximated by the leading
+order:
+\begin{align}
+  \frac12\, [A(\v m, \v r) + A(\v m, \v r+\v s)]
+  \approx&
+  -\sum_{\alpha=1}^3\sum_{l\neq 0}
+  Z_{\alpha,l}(\v m).
+\end{align}
+Then from Eqn.~\eqref{eqn:ik.error.force}, we have the error force of
+the staggered ik-differentiation:
+\begin{align}
+  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r_i)
+  \approx -2q_i
+  \sum_jq_j
+  \sum_\alpha\sum_{l\neq 0}
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  g(\v m) Z_{\alpha,l}(\v m)\,e^{2\pi i\v m\cdot(\v r_i-\v r_j)}.
+\end{align}
+This is a pairwise interaction, therefore, from
+Theorem~\ref{thm:tmp1}, we have the error estimates:
+\begin{align}\label{eqn:ik.st.meanf}
+  \big\langle
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \big\rangle
+  & \approx
+  - 2 q_i
+  \bigg[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}\v G_{\alpha,l}
+  \big)
+  \ast\rho_q\,
+  \bigg] (\v r_i),
+\end{align}
+% Also neglect the high wave number terms,
+and the RMS force error is 
+\begin{align}\label{eqn:ik.st.error}
+  \big\langle
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2
+  \big\rangle
+  \approx&\,
+  4q_i^2\,
+  \bigg[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)^2
+  \ast \rho_{q^2}\,
+  \bigg] (\v r_i) +
+  \big\langle
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \big\rangle^2.
+\end{align}
+The superscript ``st'' denotes the staggered mesh method.
+The mean error force of the staggered ik-differentiation is the
+same as the staggered ik-differentiation. The RMS error is improved, because
+$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2\big\rangle -
+\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2\big\rangle=
+2q_i^2
+\big[\,
+\big(
+\sum_{\alpha} \sum_{l\neq 0}
+\vert \v G_{\alpha,l}\vert^2
+\big)
+\ast \rho_{q^2}
+\,\big] (\v r_i) \geq 0$.
+
+For the analytical differetiation, similarly we have: $\frac12\,[\v
+B(\v m,\v r) + \v B(\v m, \v r+\v s)] \approx 0$. Therefore, from
+Eqn.~\eqref{eqn:ana.error.force}, the error force of the staggered
+analytical differetiation is approximately the same as the staggered
+ik-differentiation, so are all the error estimates:
+\begin{align}
+  \Delta\v F^{\textrm{ana,st}}_{\textrm{rec}}(\v r_i)
+  &\approx
+  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r_i)\\
+  \big\langle
+  \Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)
+  \big\rangle
+  &\approx
+  \big\langle
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \big\rangle\\
+  \big\langle
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)\vert^2
+  \big\rangle
+  &\approx
+  \big\langle
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2
+  \big\rangle
+\end{align}
+The error from the self-interaction term is automatically fixed by the
+staggered mesh. The RMS force error is improved because it is not
+difficult to see 
+$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\vert^2\big\rangle -
+\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)\vert^2\big\rangle
+\geq 0$.
 
@@
 order charge distribution $\rho_q$ is naturally zero, therefore, by
-Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:tmp31}, all
+Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:ana.meanf}, all
 the mean error forces should varnish. Numerical resutls in

### 2012-03-18 longRange.hetero/publish/main.tex
backup

@@
 which plays an important role in the error analysis of the
-inhomogeneous systems~\cite{wang2012}.
-
-For error the pairwise interactions, we have the following theorem:
+short-range inhomogeneous systems~\cite{wang2012}.
+
+One of the main results of this research is the error estimate for
+the error force that can be written as a summation of
+pairwise interactions:
 \begin{theorem}\label{thm:tmp1}
@@
   If the error force of an arbitary particle $i$ is
-  \begin{align}\label{eqn:tmp10}
+  \begin{align}\label{eqn:thm-error-force}
     \Delta \v F(\v r_i) =
@@
   then the mean error force is
-  \begin{align}\label{eqn:tmp11}
+  \begin{align}\label{eqn:thm-meanf}
     \langle\Delta\v F(\v r_i)\rangle
@@
     q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
-    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:tmp12}
+    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:thm-error}
     &+
@@
   % $C_{q^2}$ are defined by:
-  \begin{align}\label{eqn:tmp13}
+  \begin{align}\label{eqn:def-rhoq}
     \rho_q(\v r)
@@
     \,q_j\,\delta(\v r - \v r_j)
-    \bigg\rangle,\\\label{eqn:tmp14}
+    \bigg\rangle,\\\label{eqn:def-rhoq2}
     \rho_{q^2}(\v r)
@@
     \,q^2_j\,\delta(\v r - \v r_j)
-    \bigg\rangle,\\\label{eqn:tmp15}
-    C_{q^2}(\v r', \v r'')
+    \bigg\rangle,\\\label{eqn:def-rho2}
+    \rho^{(2)}(\v r, \v r')
     &= 
     \bigg\langle
-    \sum_{i\neq j}
-    q_iq_j\delta(\v r'-\v r_i)\delta(\v r''-\v r_j)
-    \bigg\rangle
-    - \rho_q(\v r')\rho_q(\v r'').
+    \sum_{j\neq k}
+    q_jq_k\delta(\v r-\v r_j)\delta(\v r'-\v r_k)
+    \bigg\rangle,\\\label{eqn:def-c}
+    C(\v r, \v r')
+    &=
+    \rho^{(2)}(\v r, \v r')    
+    - \rho_q(\v r)\rho_q(\v r').
   \end{align}
   Notice the definitions of $\rho_q(\v r)$, $\rho_{q^2}(\v r)$ and
-  $C_{q^2}(\v r', \v r'')$ are periodically extended to
+  $\rho^{(2)}(\v r, \v r')$ are periodically extended to
   $\mathbb{R}^3$, $\mathbb{R}^3$ and $\mathbb{R}^3\times\mathbb R^3$,
@@
   The RMS force error is calculated by:
-  \begin{align*} \nonumber
+  \begin{align} \nonumber
     \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
@@
     \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
-    \\
+    \\\label{eqn:prf-error-step3}
     & +
@@
     \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
-    [\,\rho_q(\v r')\rho_q(\v r'') + C_{q_2}(\v r',\v r'')\,]
-    \,\d d\v r'\d d\v r''\\
-    = \,&
-    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
-    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\
-    &+
-    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i-\v r')\cdot
-    \v K(\v r_i-\v r'')\,
-    C_{q^2}(\v r', \v r'')\,
-    \d d\v r'\d d\v r''. \qquad\qed
+    \rho^{(2)}(\v r', \v r'')
+    \,\d d\v r'\d d\v r''\\\nonumber
+    =\,&
+    q_i^2\int_{\mathbb R^3}
+    \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+    +
+    q_i^2
+    \bigg[
+    \int_{\mathbb R^3}
+    \v K(\v r_i - \v r')\rho_{q}(\v r')\,\d d\v r'
+    \bigg]^2
+    \\ \nonumber
+    & +
+    q_i^2\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
+    C(\v r', \v r'')
+    \,\d d\v r'\d d\v r''.\qquad\qed
+    % = \,&
+    % q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
+    % q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\
+    % &+
+    % q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
+    % \v K(\v r_i-\v r')\cdot
+    % \v K(\v r_i-\v r'')\,
+    % C_{q^2}(\v r', \v r'')\,
+    % \d d\v r'\d d\v r''. \qquad\qed
     % \int_{\mathbb R^3\times\mathbb R^3}\v K(\v r - \v r')\cdot\v K(\v r - \v r'')\rho(\v r', \v r'')\,\d d\v r'\d d\v r''.
-  \end{align*}
+  \end{align}
 \end{proof}
@@
 \begin{itemize}
-\item The function $\v K(\v r)$ is called \emph{the error force
-    kernel}.
+% \item
+%   This theorem provides the error estimate for the interactions, whose
+%   error force can be
+%   written as a summation of pairwise interactions. 
   % It should be well defined for $\v r = \v 0$. For
@@
 \item The densities $\rho_q(\v r)$ and $\rho_{q^2}(\v r)$ defined in
-  Eqn.~\eqref{eqn:tmp13} and \eqref{eqn:tmp14} are called \emph{the
-    first order charge density distribution (CDD)} and \emph{the
-    second order charge density distribution},
-  respectively. $C_{q^2}(\v r, \v r')$ defined in
-  Eqn.~\eqref{eqn:tmp15} is the pairwise charge correlation function.
+  Eqn.~\eqref{eqn:def-rhoq} and \eqref{eqn:def-rhoq2} are called \emph{the
+    first order charge distribution} and \emph{the
+    second order charge distribution},
+  respectively.
+  $\rho^{(2)}(\v r, \v r')$ in Eqn.~\eqref{eqn:def-rho2}
+  is the \emph{pairwise charge distribution}.
+  When the positions of any two different charges are independent,
+  $\rho^{(2)}(\v r, \v r') = \frac{N-1}{N}\rho_q(\v r)\rho_q(\v r')$.
+  Since $N$ is always a large number in real simulations, we take
+  $\rho^{(2)}(\v r, \v r') = \rho_q(\v r)\rho_q(\v r')$ for convenience.
+  $C_{q^2}(\v r, \v r')$ defined in
+  Eqn.~\eqref{eqn:def-c} is the \emph{pairwise charge correlation function},
+  which describes the strength of the correlation between  two
+  different charges. When they are independent, $C_{q^2}(\v r, \v r')$
+  vanishes, otherwise $C_{q^2}(\v r, \v r') \neq 0$.
+  Most of the error estimates assumed the independency of the
+  particles in the system~\cite{kolafa1992cutoff, deserno1998mue2, wang2010optimizing, wang2012},
+  however, this could be problematic in the strongly correlated
+  systems~\cite{deserno1998mue2, wang2010optimizing}.
+  Also see Sec.~\ref{sec:example3} for example.
+\item
+  The \emph{pairwise form}
+  of the interaction (see Eqn.~\eqref{eqn:thm-error-force}) is the key to derive
+  the error estimates Eqn.~\eqref{eqn:thm-meanf} and \eqref{eqn:thm-error}.
+  The function $\v K(\v r)$ is called \emph{the error force
+    kernel}.
+  By setting $q_i = q_j = 1$, the theorem~\ref{thm:tmp1} directly proves
+  the error estimates for the short-range interaction
+  in inhomogeneous systems, which was derived in Ref.~\cite{wang2012}. 
 \item Analog to the short-range error estimate~\cite{wang2012}, the
-  three terms on the r.h.s. of Eqn.~\eqref{eqn:tmp12} are called the
+  three terms on the r.h.s. of Eqn.~\eqref{eqn:thm-error} are called the
   homogeneity error, the inhomogeneity error and the correlation
-  error, respectively. The homogeneity error and the inhomogeneity
+  error, respectively.
+  This is denoted by:
+  \begin{align}\label{eqn:error-split}
+    \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
+    =
+    \mathcal E^2_{\textrm{homo}}(\v r_i) +
+    \mathcal E^2_{\textrm{inhomo}}(\v r_i) +
+    \mathcal E_{\textrm{correlation}}(\v r_i).
+  \end{align}
+  The homogeneity error and the inhomogeneity
   error can be calculated at the cost of $\mathcal O(N\log N)$ by the
   fast Fourier transform (FFT) (see Ref.~\cite{wang2012} for details).
-  However, the calculation of the correlation error costs $\mathcal
-  O(N^2\log N)$, because it involves a twofold convolution. In this
-  study, the contribution of the correlation error is neglicted.
+  However, the full calculation of the correlation error costs $\mathcal
+  O(N^2\log N)$, because it involves a twofold convolution.
+  % In this
+  % study, the contribution of the correlation error is neglicted.
   % In
   % section~\ref{sec:tmp3}, it is shown neglicting the 
-\item A non-zero mean error force~\eqref{eqn:tmp11} was proof to be
-  harmful to the simulation in the case of the short-range force
-  calculation~\cite{wang2012}.  In the case of the charge system, this
-  term is non-zero only when the system is NOT locally neutral. For
+\item A non-varnishing mean error force~\eqref{eqn:thm-meanf} was proved
+  to be
+  harmful to the calculation of the short-range interaction
+  in inhomogeneity systems~\cite{wang2012}.
+  In the case of the charged system, this
+  term is non-zero only when the system is NOT locally neutral,
+  i.e. a non-zero first order charge distribution. For
   most of the simulation cases, the locally neutral condition is
@@
 
+\subsection{First neighbor approximation of the correlation
+error}
+
+In this section, we consider the first neighbor approximation of the
+correlation error. Here ``first neighbors'' means the neighboring
+atoms that are connected by the chemical bond.  In most molecular
+force fields, such bonds are modeled by a rigid connection between two
+atoms.  Therefore, the correlation between such an atom pair is very
+strong. As an example, we consider a typical three point charge water
+model TIP3P~\cite{jorgensen1983comparison}: each hydrogen atom carries
+a charge of $q_{\textrm{H}} = +0.417e$ and each oxygen atom carries a charge of
+$q_{\textrm{O}} = -0.834e$. Within one molecule, the H-O bond and H-O-H angle are
+rigid. 
+% In the system of water, the relative position of the oxygen and
+% hydrogen atoms within one molecule is fixed. Therefore, according
+% to this property, it is possible to improve the quality of the
+% error estimate.
+Starts from Eqn.~\eqref{eqn:prf-error-step3},
+\begin{align} \nonumber
+  \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
+  =\,&
+  q_i^2\int_{\mathbb R^3}
+  \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+  \\
+  & +
+  q_i^2\int_{\mathbb R^3\times\mathbb R^3}
+  \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
+  \rho^{(2)}(\v r', \v r'')
+  \,\d d\v r'\d d\v r'',
+\end{align}
+where the definition of $\rho^{(2)}(\v r', \v r'')$ is given by
+Eqn.~\eqref{eqn:def-rho2}.
+% \begin{align}
+%   q_{q^2}(\v r', \v r'') =
+%   \bigg\langle
+%   \sum_{j\neq k}q_j q_k\delta(\v r' - \v r_j)\delta(\v r'' - \v r_k)
+%   \bigg\rangle.
+% \end{align}
+We seperately consider the first neighbor contribution
+and other contributions to
+the pairwise density $\rho^{(2)}(\v r', \v r'')$.  Denoting
+$\Omega_j = \{ \,k\,\vert\,
+\textrm{atom $k$ is the first neighbor of atom $j$} \,\}$,
+% the set of the first neighbors of the $j$-th atom by $\Omega_j$,
+we have:
+\begin{align}\label{eqn:split-rho-q2}
+  \rho^{(2)}(\v r', \v r'')
+  = &\,
+  \bigg\langle
+  \sum_j\sum_{k\in\Omega_j}q_j q_k\delta(\v r' - \v r_j)\delta(\v r'' - \v r_k)
+  \bigg\rangle
+  +
+  \bigg\langle
+  \sum_j\sum_{k\notin\Omega_j}q_j q_k\delta(\v r' - \v r_j)\delta(\v r'' - \v r_k)
+  \bigg\rangle.
+\end{align}
+For any atom $k$ that is not the first neighbor of atom $j$, we
+assume that its position is independent with atom $j$, then
+second part on the r.h.s. of the Eqn.~\eqref{eqn:split-rho-q2} is
+approximately $\frac{N-3}{N}\rho_q(\v r')\rho_q(\v r'')\approx
+\rho_q(\v r')\rho_q(\v r'')$.
+% If the number of atoms in the system is
+% large, this should be a good approximation.
+Therefore, the first part
+on the r.h.s. of Eqn.~\eqref{eqn:split-rho-q2} is actually the
+pairwise charge corrlation function:
+\begin{align}\label{eqn:fnc-correlation-water}
+  C_{q^2}(\v r', \v r'') =
+  \bigg\langle
+  \sum_j\sum_{k\in\Omega_j}q_jq_k\delta(\v r' - \v r_j)\delta(\v r'' - \v r_k)
+  \bigg\rangle.
+\end{align}
+% If connected by the chemical bond, the position of the first neighbors
+% $k$ is not independent with the atom $j$, so their correlation is
+% strong, and should be calculated explicitly to improve the quality of
+% the error estimate.
+By inserting Eqn.~\eqref{eqn:fnc-correlation-water} into
+the correlation error, we have:
+\begin{align}
+  \mathcal E_{\textrm{correlation}}(\v r_i)
+  = q_i^2\sum_j\sum_{k\in\Omega_j}q_jq_k
+  \big\langle
+  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \big\rangle_{\v r_j,\v r_k}
+\end{align}
+Denoting the index set of the oxygen atoms by $\Omega_{\textrm{O}}$,
+and the index set of the hydrogen atoms by $\Omega_{\textrm{H}}$, 
+we have:
+\begin{align}\nonumber
+  \mathcal E_{\textrm{correlation}}(\v r_i)
+  = &\,
+  q_i^2\sum_{j\in\Omega_{\textrm{O}}}\sum_{k\in\Omega_j}q_jq_k
+  \big\langle
+  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \big\rangle_{\v r_j,\v r_k} \\ \nonumber
+  &\,+ 
+  q_i^2\sum_{j\in\Omega_{\textrm{H}}}\sum_{k\in\Omega_j}q_jq_k
+  \big\langle
+  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \big\rangle_{\v r_j,\v r_k} \\\nonumber
+  = &\,
+  q_i^2
+  \int_{\mathbb R^3}
+  \v K(\v r_i - \v r')\cdot
+  \big\langle
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_1})+
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_2})
+  \big\rangle\,\rho_{\textrm{O}}(\v r')
+  \d d\v r' \\\label{eqn:c-error-1}
+  & \,+
+  q_i^2
+  \int_{\mathbb R^3}
+  \v K(\v r_i - \v r')\cdot
+  \big\langle
+  q_{\textrm{O}}\v K(\v r_i - \v r' + \v s_{\textrm{O}})+
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}})
+  \big\rangle\,\rho_{\textrm{H}}(\v r')
+  \d d\v r'
+\end{align}
+If positions of the three atom within one molecule are
+$\v r_{\textrm{H}_1}$, $\v r_{\textrm{H}_2}$ and $\v r_{\textrm{O}}$, then
+$\v s_{\textrm{H}_1} = \v r_{\textrm{H}_1} - \v r_{\textrm{O}}$, 
+$\v s_{\textrm{H}_2} = \v r_{\textrm{H}_2} - \v r_{\textrm{O}}$,
+$\v s_{\textrm{O}} = \v r_{\textrm{O}} - \v r_{\textrm{H}_1}$ and
+$\v s_{\textrm{H}} = \v r_{\textrm{H}_2} - \v r_{\textrm{H}_1}$.
+The two ensemble averages in Eqn.~\eqref{eqn:c-error-1}
+is taken over all possible water directions 
+at position $\v r'$. As an approximation, we
+assume these averages are  spacially uniform, namely independet with $\v r'$.
+This assumption may be  problematic
+in the regions where the preference of water  drection is different
+with others.
+% In the example considered by the present paper in section~\ref{sec:tmp3},
+% it is shown to be a good approximation to obtain the estimate of the
+% correlation error.
+One possible way to calculate the ensemble averages in
+Eqn.~\eqref{eqn:c-error-1} is by the Fourier transform
+of the error force kernel:
+\begin{align} \nonumber
+  &\big\langle
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_1})+
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_2})
+  \big\rangle \\ \nonumber
+  =\,&
+  \frac1V\bigg\langle
+  \sum_{\v m}
+  q_{\textrm{H}}\hat{\v K}(\v m)
+  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{H}_1})} +
+  \sum_{\v m}
+  q_{\textrm{H}}\hat{\v K}(\v m)
+  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{H}_2})}
+  \bigg\rangle \\\nonumber
+  =\,&
+  \frac1V\sum_{\v m}
+  \hat{\v K}(\v m)
+  e^{2\pi i\v m\cdot(\v r_i - \v r')}
+  \,  
+  \langle
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_1}} +
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_2}}
+  \rangle,
+\end{align}
+where ``$\wedge$'' denotes the forward Fourier transform. By denoting
+\begin{align}
+  \hat T_{\textrm{O}}(\v m)
+  &= 
+  \langle
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_1}} +
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_2}}
+  \rangle,\\
+  \hat T_{\textrm{H}}(\v m)
+  &= 
+  \langle
+  q_{\textrm{O}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}} +
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}}}
+  \rangle.
+\end{align}
+The Eqn.~\eqref{eqn:c-error-1} becomes:
+\begin{align}\nonumber
+  \mathcal E_{\textrm{correlation}}(\v r_i)
+  =&\,
+  q_i^2
+  \int_{\mathbb R^3}
+  \v K(\v r_i - \v r')\cdot
+  (\hat T_{\textrm{O}}\hat{\v K})^{\vee}(\v r_i - \v r')
+  \,\rho_{\textrm{O}}(\v r')
+  \,\d d\v r' \\\label{eqn:c-error-water}
+  & \,+
+  q_i^2
+  \int_{\mathbb R^3}
+  \v K(\v r_i - \v r')\cdot
+  (\hat T_{\textrm{H}}\hat{\v K})^{\vee}(\v r_i - \v r')
+  \,\rho_{\textrm{H}}(\v r')
+  \,\d d\v r',
+\end{align}
+where ``$\vee$'' denotes the backward Fourier transform.
+In the Fourier space, the error force kernel $\v K(\v r)$ is
+influenced by the prefactors $T_{\textrm{O}}$ and $T_{\textrm{H}}$,
+which are accounting for the atomic correlation within one water
+molecule.
+
+% For the second term, do variable change $\v r'' = \v r' + \v s$, we have:
+% \begin{align}
+%   \textrm{II} = & 
+%   q_i^2
+%   \int_{\mathbb R^3}\d d\v r'\v K(\v r_i - \v r')
+%   \int_{\mathbb R^3}\d d\v s\,
+%   \v K(\v r_i - \v r' - \v s)\,
+%   \rho_{q^2}(\v r', \v r' + \v s).
+% \end{align}
+% Split the integral region of the variable $\v s$ into the first
+% neighbor shell $\mathcal B(\v r', R_s)$ and the reset $\mathbb R -
+% \mathcal B(\v r', R_s)$. In the case of water, the first neighbor
+% shell means the region where a single molecule occupies. Within this
+% shell, the relative position of the oxygen and two hydrogens are
+% always fixed. Outside of the first neighbor shell, the position of
+% oxygens and hydrogens are belongs to different molecules, so the their
+% positions are assumed to be independent. In most cases, the first
+% neighbor shell is small comparing to the simulation box size,
+% therefore,
+% \begin{align}\nonumber
+%   \textrm{II}_{\textrm{out}} = & \,
+%   q_i^2
+%   \int_{\mathbb R^3}\d d\v r'\v K(\v r_i - \v r')
+%   \int_{\mathbb R^3 - \mathcal B(\v r', s)}\d d\v s\,
+%   \v K(\v r_i - \v r' - \v s)\,
+%   \rho_{q^2}(\v r', \v r' + \v s) \\ \nonumber
+%   = &\,
+%   q_i^2
+%   \int_{\mathbb R^3}\d d\v r'\v K(\v r_i - \v r') \rho_q(\v r')
+%   \int_{\mathbb R^3 - \mathcal B(\v r', s)}\d d\v s\,
+%   \v K(\v r_i - \v r' - \v s)\,
+%   \rho_q(\v r' + \v s) \\
+%   \approx &\,
+%   q_i^2
+%   [\v K\ast\rho_{q}]^2 (\v r_i)
+% \end{align}
+
 \subsection{Ewald summation and its error estimate}
@@
 parts: the direct part, the reciprocal part and the correction
-part. that is
+part:
 \begin{equation}
@@
 The distance between the two particles is denoted by $\v r_{ij} = \v
-r_i - \v r_j$, where $\v r_i$ and $\v r_j$ are positions of particle
-$i$ and $j$, respectively.  The lattice in the real space is denoted
+r_i - \v r_j$.  The lattice in the real space is denoted
 by $\v n = n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, where $\v a_\alpha,
@@
   \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
-  &= - 
+  &= 
   q_i 
@@
   e^{2\pi i\v m\cdot\v r_i}, \\\label{eqn:tmp8}
-  &= - 
+  &= 
   \sum_j   q_iq_j
@@
 Both the direct part and reciprocal part of the Ewald summation can be
-written in the form of Eqn.~\eqref{eqn:tmp11}.  The direct
+written in the pairwise form of Eqn.~\eqref{eqn:thm-error-force}.  The direct
 error force kernel is defined by:
@@
 
-\subsection{The smooth particle mesh Ewald method}
+\subsection{The smooth particle mesh Ewald method \&
+the staggered mesh Ewald method}
 
@@
 O(N^2)$. It has been shown that with a careful tuning of parameter
-$\beta$ and the reciprocal space truncation $K_\alpha$, the
-computational cost is reduced to $\mathcal O(N^{3/2})$
-\cite{perram1988asc}, which becomes not applicable when the system
+$\beta$, real space cut-off radius $r_c$
+and the reciprocal space truncation $K_\alpha$, the
+optimal computational cost is $\mathcal O(N^{3/2})$~\cite{perram1988asc},
+which becomes not applicable when the system
 size is larger than several hundreds of charged particles. Both the
@@
 former. All the error estimates develop by the current paper can be
-easily extended to PME method.  The principle idea of the SPME method
+easily extended to the PME method.  The principle idea of the SPME method
 is first to calculate the term $e^{2\pi i\v m\cdot\v r}$ on a uniform
 lattice in the real space.  Therefore, all Fourier transforms can be
-accerlerated by the fast Fourier transform (FFT), that is why the
+accerlerated by the fast Fourier transform (FFT) algoritm, that is why the
 computational cost of SPME is reduced to $\mathcal O(N\log N)$. Then,
@@
 points.  The PME method uses Lagrangian interpolation, while the SPME
-uses B-spline interpolation that is more precise, and has higher order
+uses B-spline interpolation,  which is more precise, and has higher order
 of smoothness.
@@
 B-spline interplation. This way is called
-\emph{ik--differentiation}. The alternative way notices the high-order
+\emph{ik--differentiation}~\cite{deserno1998mue1}.
+The alternative way notices the high-order
 smoothness of the B-spline interpolation, and derive the force by
 differentiating the B-spline approximated reciprocal Ewald energy
-(also truncated). This way was proposed by the original SPME paper
+(also truncated). The second way was proposed by the original SPME paper
 \cite{essmann1995spm}, and is called the \emph{analytical
-  differentiation}.  It has been shown that using the same parameters,
+  differentiation}~\cite{deserno1998mue1}.
+It has been shown that using the same parameters,
 the ik-differentiation is more precise than the analytical
@@
 for the communication in parallel
-implementations~\cite{wang2010optimizing}. Since the SPME method is
+implementations~\cite{wang2010optimizing}.
+For the ik-differentiation, the calculated force is not the negative
+gradient of the calculated energy. The analytical differentiation
+does not have this problem, but it (to the approximation precision)
+violates the Newton's third law.
+Since the SPME method is
 not the point of the present paper, we refer the readers to, for
@@
 
+The staggered mesh approach or originally call ``interlacing'' was first
+developed by Hockney and Eastwood~\cite{hockney1988computer}, and was
+recently applied to SPME (staggered mesh Ewald~\cite{cerutti2009staggered})
+and P3M (interlaced P3M~\cite{neelov2010interlaced}).
+It calculates the
+reciprocal force on two meshes,
+one of which locates at the lattice volume center
+of the other, and then the two reciprocal forces are averaged.
+It is shown that staggering the meshes
+cancels error in the force computation, and greatly improves the
+accuracy~\cite{cerutti2009staggered, neelov2010interlaced}.
+Implementing the staggered mesh method for SPME is
+relatively simple, and involves only little modification to the
+existing codes.
+% : calculated the reciprocal force by the existing
+% methods, either ik-differentiation or analytical differentiation, on
+% the two staggered meshes, and then average these results.
+% It is shown latter that the staggered mesh cencels
+% high-wave-number terms in the error force, and 
+% preserves the Newton's third law for the analytical differentiation.
+Obviously, the staggered mesh ik-/analytical differentiation
+cost twice as much on the
+reciprocal part as the original version.
+
 \subsection{Error estimate of the ik-differentiation}
+\label{sec:error-ik}
 
@@
 
-As mentioned above, the SPME error mainly oringinated from approximate
+As mentioned above, the SPME error mainly oringinates from approximating
 the term $e^{2\pi i\v m\cdot\v r}$ by the B-spline
-interpolation. Denote the error introduced by this approximation by
+interpolation. Denoting the error introduced by this approximation by
 $A(\v m, \v r)\,e^{2\pi i\v m\cdot \v r}$, we are fortunate to have
@@
   e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:tmp19}
+  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:ik.error.force.1}
   & +\,
@@
 \end{align}
-The last ``self-interacting term'' is zero, because of the
-symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$.
+Due to the symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$,
+the last term in Eqn.~\eqref{eqn:ik.error.force.1},
+i.e. the ``self-interacting term'', is zero.
 Therefore,
@@
 error force of ik-differentiation~\eqref{eqn:ik.error.force} cannot be written
-in the form of~\eqref{eqn:tmp11}, so the error estimate derived by
+in the form of~\eqref{eqn:thm-error-force}, so the error estimate derived by
 Theorem~\ref{thm:tmp1} cannot be used here. However, it is still
 possible to develop the error estimate for the ik-differentiation.
-Here we only want to present the key idea and the formula of the error
-estimate, and leave all details to the Appendix \ref{}.  We notice the
+Here we only want to present the key idea and the final  error
+estimates, and leave all details of calculating the error estimates
+to the Appendix~\ref{sec:appendix}.  We notice the
 term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot\v r}$ with $l\neq 0$
@@
 \subsection{Error estimate of the analytical differetiation}
+\label{sec:error-ana}
 
@@
 from the analytical force during the simulation. The computational cost of
-the self-interacting term costs is very low comparing with the SPME
-force calculation.
+the self-interaction term costs is very low comparing with the SPME
+force calculation. It is shown that the self-interaction  error
+dominate in the low charge density regions~\cite{cerutti2009staggered}.
+Therefore, we always remove the self-interaction term for
+the analytical differetiation, and call it as the original analytical
+differetiation when comparing it with the staggered mesh analytical
+differetiation.
 
@@
   \ast \rho_{q^2}\,
-  \bigg] (\v r_i) \\\nonumber
+  \bigg] (\v r_i) \\\label{eqn:ana.error}
   & +\,
-  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2\\\label{eqn:ana.error}
-  &+\,
-  q_i^4 \sum_{\alpha}\sum_{l\neq 0}
-  4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 .
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2
+  % &+\,
+  % q_i^4 \sum_{\alpha}\sum_{l\neq 0}
+  % 4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 .
 \end{align}
@@
   Z_{\alpha,l}(\v m)\,
-  e^{2\pi i\v m\cdot \v r},\\
-  C_{\alpha,l}^{\textrm{self}}
-  &= 
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  (-2)f(\v m)\,
-  Z_{\alpha,l}(\v m).
-\end{align}
-$F_{\alpha,l} (\v r)$ and $C_{\alpha,l}^{\textrm{self}}$ 
-do not depends on the coordinates of particles,
-so they can be tabulated in advance for the simulation.
-
-\subsection{The staggered Mesh Ewald method}
-
-The staggered Method Ewald method~\cite{cerutti2009staggered,
-  neelov2010interlaced} calculate the reciprocal force on two meshes,
-one of which locates at the middle of the other.  Then the two forces
-are averaged to cancel the error. Here we study the staggered Mesh
-Ewald method from the error point of view.
+  e^{2\pi i\v m\cdot \v r}.
+  % \\
+  % C_{\alpha,l}^{\textrm{self}}
+  % &= 
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_{\alpha}\vert < K_\alpha/2\\
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % (-2)f(\v m)\,
+  % Z_{\alpha,l}(\v m).
+\end{align}
+% $F_{\alpha,l} (\v r)$ and $C_{\alpha,l}^{\textrm{self}}$ 
+% do not depends on the coordinates of particles,
+% so they can be tabulated in advance for the simulation.
+$F_{\alpha,l} (\v r)$ 
+does not depends on the coordinates of particles,
+so it can be tabulated in advance for the simulation.
+
+\subsection{Error estimate of the staggered mesh Ewald methods}
+
 The shift of the mesh can be effective treated as shifting all
@@
 \end{align}
-This is a pairwise interaction, therefore, from
-Theorem~\ref{thm:tmp1}, we have the error estimates:
+This is a pairwise interaction, the Theorem~\ref{thm:tmp1} is applicable.
+Moreover, since both the exact and the error
+force are pairwise,  the Newton's third law is preserved by the
+calculated force.
+From Theorem~\ref{thm:tmp1}, we have the error estimates:
 \begin{align}\label{eqn:ik.st.meanf}
@@
 The mean error force of the staggered ik-differentiation is the
-same as the staggered ik-differentiation. The RMS error is improved, because
+same as the original ik-differentiation.
+The RMS error is improved, because
 $\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2\big\rangle -
@@
 ik-differentiation, so are all the error estimates:
-\begin{align}
+\begin{align}\label{eqn:ana-st-error-force}
   \Delta\v F^{\textrm{ana,st}}_{\textrm{rec}}(\v r_i)
@@
 The error from the self-interaction term is automatically fixed by the
-staggered mesh. The RMS force error is improved because it is not
+staggered mesh.
+The RMS force error is improved because it is not
 difficult to see 
@@
 \geq 0$.
+Eqn.~\eqref{eqn:ana-st-error-force} implies, to the
+leading order of approximation, the staggered
+mesh ik-differentiation and staggered mesh analytical differetiation
+are the same method. Considering the latter uses
+only one half of  FFTs as the former, it might be preferabel
+in large scale parallel simulations.
+From Eqn.~\eqref{eqn:ana.error.force}
+and~\eqref{eqn:ana-st-error-force}, the Newton's
+third law is preserved by the staggered method analytical differetiation.
 
@@
 \end{align}
-where \textrm{x} can be \textrm{tr}, \textrm{ik} or \textrm{ana},
-standing for the truncated Ewald summation, the ik-differentiation
-and the analytical differetiation, respectively. The mean square
-total force is
+where \textrm{x}
+denotes any method for the reciprocal Ewald summation, which
+could be truncated Ewald summation (``tr''), ik-/analytical differetiation
+(``ik''/''ana'') or staggered method
+ik-/analytical differetiation (``st,ik''/''st,ana'').
+The mean square total force is
 \begin{align}\nonumber
@@
   2\,\langle\Delta\v F_{\textrm{dir}}(\v r_i)\rangle
-  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\rangle \\\label{eqn:tmp36}
+  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\rangle \\
+  \label{eqn:error-total}
   &
@@
 F^{\textrm{x}}_{\textrm{rec}}(\v r_i)$:
-\begin{align}\label{eqn:tmp37}
+\begin{align}\label{eqn:error-total-corr}
   \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
@@
 \end{align}
-In Eqn.~\eqref{eqn:tmp36}, the estimates of errors
+In Eqn.~\eqref{eqn:error-total}, the estimates of errors
 $\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle $,
@@
 r_i)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
-r_i)\rangle $ have been established. In section \ref{sec:tmp3}, it is
-shown that the correlation between the direct and reciprocal error
-force can be safely neglected.
+r_i)\rangle $ have been established.
+In practice, the correlation~\eqref{eqn:error-total-corr}
+is often assumed to be varnished.
+% In section \ref{sec:tmp3}, it is
+% shown that the correlation between the direct and reciprocal error
+% force can be safely neglected.
 
@@
 
-We consider two inhomogeneous charge system to verify our error
-estimate.  The first is locally neutral and globally inhomogeneous
-charge system. In the second system, the positive and negative charges
-are well seperated, while the number density of the charges is
-uniform.
-
-\subsection{Example 1: locally neutral}
+We consider three inhomogeneous charge system to verify our error
+estimate.
+The first two are artifically designed to verify the formula of
+the error estimates. The third is a real simulation
+of liquid-vapor equilibriated water system, in order to test the
+quality  of error estimates in real inhomogeneous system.
+
+% The first is locally neutral and globally inhomogeneous
+% charge system. In the second system, the positive and negative charges
+% are well seperated, while the number density of the charges is
+% uniform.
+
+\subsection{Example 1: a locally neutral system.}
+\label{sec:example1}
 
@@
   \centering
-  \includegraphics[width=.48\textwidth]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
-  \caption{Charge distribution of Example 1. The red line
-    denotes the positive charge distribution, while the blue line
-    denotes the negative charge distribution. Since all distributions
-    are uniform on $y$ and $z$ direction, they are plotted as a
-    function of $x$.}
-  \label{fig:tmp-rho0}
+  \includegraphics[]{fig.new/rand1/fig.rho.eps}
+  \caption{
+    The charge number density  of Example 2.
+    The red line: positive charge. The blue line: negative charge.
+    Since the charges are uniformly distributed
+    on $y$ and $z$ direction, the densities are averaged on $y$ and $z$,
+    and plotted as a
+    function of $x$.
+  }
+  \label{fig:tmp-rho1}
 \end{figure}
 
-In this example, 16800 charges are put into a $40\textsf{nm}\times
-20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
-them are carrying a unit positive charge of $+e$, and the other half
-are carrying negative charge of $-e$. The position of these charges
-are randomly generated subject to density distribution shown in
-Fig.~\ref{fig:tmp-rho0}.  The profile of the positive and negative
-charge distributions are identical, namely the minus of the negative
-distribution is the same as the positive distribution. Therefore the
-positive and negative charge distributions cancel each other, and the
-system is locally neutral. Both the density distributions are highly
-inhomogeneous, take the positive distribution for example: between 11
-\textsf{nm} and 29 \textsf{nm}, the charge density is
-$1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
-and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
-$0.05\;\textsf{e/nm}^3$.
+In this example,  41472 charges are put into a
+$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
+periodic simulation box. One third of
+them are carrying negative charge of $-0.834e$, and the other two thirds
+are carrying positive charge of $+0.417e$.
+The position of these charges
+are randomly generated subject to the number density shown in
+Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
+charge   is twice as large as that of the negative charge,
+which means  the
+positive and negative charges cancel, and the
+system is \emph{locally} neutral. Notice the amount of charges
+and the density distributions are intentionally chosen the same as
+example 3~(see section \ref{sec:example3}), 
+for an easy comparison.  The only difference is that the positions
+of charges are independent  in this example,
+while they are correlated in example 3.
+% Both the density distributions are highly
+% inhomogeneous, take the positive distribution for example: between 11
+% \textsf{nm} and 29 \textsf{nm}, the charge density is
+% $1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
+% and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
+% $0.05\;\textsf{e/nm}^3$.
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
+%   \caption{Example 1: the actual (denoted by dots) and estimated
+%     (denoted by straight lines) mean error force of the direct part
+%     $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal
+%     part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}p\rangle$ (green) and the reciprocal part of the analytical
+%     differentiation $\langle\Delta \v
+%     F^{\textrm{ana}}_{\textrm{rec}}\rangle$ (blue). The total
+%     mean error force of analytical differentiation $\langle\Delta \v
+%     F^{\textrm{ana}}\rangle$ is given in pink.  Since the charge
+%     distribution is uniform on the $y$ and $z$ direction, the $y$ and
+%     $z$ dimension of the mean error force is averaged, and the errors
+%     are plotted on $x$ direction.  The cut-off in the real space is 3
+%     \textsf{nm}, the number of freedom in the reciprocal space is
+%     $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
+%     \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
+%     the analytical differentiation is 6.}
+%   \label{fig:meanf1}
+% \end{figure}
+
+% Fig.~\ref{fig:meanf1} presents the mean error force of the direct part
+% $\langle\Delta \v F_{\textrm{dir}}\rangle$, reciprocal part of Ewald
+% summation $\langle\Delta \v F_{\textrm{rec}}\rangle$ and the
+% reciprocal part of the analytical differentiation $\langle\Delta \v
+% F^{\textrm{ana}}_{\textrm{rec}}\rangle$. The total mean error force of
+% analytical differentiation, which is simply $\langle\Delta \v
+% F^{\textrm{ana}}\rangle = \langle\Delta \v F_{\textrm{dir}}\rangle +
+% \langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$, is also
+% given.  The real and estimated mean error forces are denoted by dots
+% and straight lines, respectively. All estimates are consistent very
+% well with real errors.  Since the system is locally neutral, the first
+% order charge distribution $\rho_q$ is naturally zero, therefore, by
+% Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:ana.meanf}, all
+% the mean error forces should varnish. Numerical resutls in
+% Fig. \ref{fig:meanf1} verifies with the above discussion.
 
@@
   \centering
-  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
-  \caption{Example 1: the actual (denoted by dots) and estimated
-    (denoted by straight lines) mean error force of the direct part
-    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal
-    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}p\rangle$ (green) and the reciprocal part of the analytical
-    differentiation $\langle\Delta \v
-    F^{\textrm{ana}}_{\textrm{rec}}\rangle$ (blue). The total
-    mean error force of analytical differentiation $\langle\Delta \v
-    F^{\textrm{ana}}\rangle$ is given in pink.  Since the charge
-    distribution is uniform on the $y$ and $z$ direction, the $y$ and
-    $z$ dimension of the mean error force is averaged, and the errors
-    are plotted on $x$ direction.  The cut-off in the real space is 3
-    \textsf{nm}, the number of freedom in the reciprocal space is
-    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
-    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
-    the analytical differentiation is 6.}
-  \label{fig:meanf1}
-\end{figure}
-
-Fig.~\ref{fig:meanf1} presents the mean error force of the direct part
-$\langle\Delta \v F_{\textrm{dir}}\rangle$, reciprocal part of Ewald
-summation $\langle\Delta \v F_{\textrm{rec}}\rangle$ and the
-reciprocal part of the analytical differentiation $\langle\Delta \v
-F^{\textrm{ana}}_{\textrm{rec}}\rangle$. The total mean error force of
-analytical differentiation, which is simply $\langle\Delta \v
-F^{\textrm{ana}}\rangle = \langle\Delta \v F_{\textrm{dir}}\rangle +
-\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$, is also
-given.  The real and estimated mean error forces are denoted by dots
-and straight lines, respectively. All estimates are consistent very
-well with real errors.  Since the system is locally neutral, the first
-order charge distribution $\rho_q$ is naturally zero, therefore, by
-Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:ana.meanf}, all
-the mean error forces should varnish. Numerical resutls in
-Fig. \ref{fig:meanf1} verifies with the above discussion.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/error.one_peak.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
-  \caption{Example 1: the actual (denoted by dots) and estimated
-    (denoted by straight lines) RMS force error of the direct part
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$
-    (red), reciprocal part of Ewald summation
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}\vert^2\rangle}$
-    (green) and the reciprocal part of the analytical differentiation
-    $\sqrt{\langle\vert\Delta \v
-      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
-    force error of analytical differentiation
-    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}\vert^2\rangle}$ is
-    given in pink.  Since the charge distribution is uniform on the
-    $y$ and $z$ direction, the $y$ and $z$ dimension of the mean error
-    force is averaged, and the errors are plotted on $x$ direction.
-    The cut-off in the real space is 3 \textsf{nm}, the number of
-    freedom in the reciprocal space is $100\times 50\times 50$, the
-    parameter $\beta$ is $1.0\; \textsf{nm}^{-1}$ and the order of
-    B-spline interpolation used for the analytical differentiation is
-    6.}
+  \includegraphics[]{fig.new/fig.rand1.error.eps}
+  \caption{
+    Example 1: the real RMS errors and the corresponding
+    estimates. Different colors denote
+    different parts of the Ewald summation. Red: the direct
+    part of Ewald summation. Green: the reciprocal
+    part of Ewald summation, calculated by truncation.
+    ``$\times$'' denotes the real error, and the solid line denotes
+    the estimated error.
+    Blue: the reciprocal part of Ewald summation, calculated
+    by fast algorithms. ``$\blacksquare$'': real error of
+    the oringinal analytical
+    differentiation. ``$\boxdot$'': real error of the oringinal ik-differentiation.
+    ``$\times$'': real error of the staggered mesh analytical differentiation.
+    ``$+$'': real error of the staggered mesh ik-differentiation.
+    Dashed line: estimated oringinal analytical differentiation.
+    Dotted line: estimated oringinal ik-differentiation.
+    Solid line: estimated staggered mesh ik-/analytical differentiation.
+    The RMS errors are averged over $y$ and $z$ directions, and are
+    plotted against $x$ axis.
+    The cut-off in the real space is 1.31 \textsf{nm}, the number of
+    freedom in the reciprocal space is $120\times 60\times 60$, the
+    parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
+    B-spline interpolation is 6.
+    }
+    % Example 1: the actual (denoted by dots) and estimated
+    % (denoted by straight lines) RMS force error of the direct part
+    % $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$
+    % (red), reciprocal part of Ewald summation
+    % $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}\vert^2\rangle}$
+    % (green) and the reciprocal part of the analytical differentiation
+    % $\sqrt{\langle\vert\Delta \v
+    %   F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
+    % force error of analytical differentiation
+    % $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}\vert^2\rangle}$ is
+    % given in pink.  Since the charge distribution is uniform on the
+    % $y$ and $z$ direction, the $y$ and $z$ dimension of the mean error
+    % force is averaged, and the errors are plotted on $x$ direction.
+    % The cut-off in the real space is 3 \textsf{nm}, the number of
+    % freedom in the reciprocal space is $100\times 50\times 50$, the
+    % parameter $\beta$ is $1.0\; \textsf{nm}^{-1}$ and the order of
+    % B-spline interpolation used for the analytical differentiation is
+    % 6.}
   \label{fig:error1}
@@
 
-Fig.~\ref{fig:error1} presents the RMS force error of the direct part
-$\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$,
-reciprocal part of Ewald summation $\sqrt{\langle\vert\Delta \v
-  F_{\textrm{rec}}\vert^2\rangle}$, the reciprocal part of the
-analytical differentiation $\sqrt{\langle\vert\Delta \v
-  F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ and the total
-analytical differentiation force $\sqrt{\langle\vert\Delta \v
-  F^{\textrm{ana}}\vert^2\rangle}$.  The real and estimated mean error
-forces are denoted by dots and straight lines, respectively. All the
-error estimates are overlapping with the real errors, that means the
-error estimates developed by the present paper are very sharp.
+Fig.~\ref{fig:error1} presents the real RMS error (by points) and the
+corresponding error esimates (by lines) of the cut-offed Ewald direct
+part, the truncated Ewald reciprocal part, the original ik-/analytical
+differentiations and the staggered mesh ik-/analytical
+differentiations. All the error estimates are consistent very well
+with the real errors, that means the error estimates developed by the
+present paper are very sharp.  The parameters of are
+chosen to be the same for an easy comparison among these 
+SPME branches.  The errors of FFT
+based fast Ewald methods are 8 orders of maganitudes large than that of
+the truncated Ewald summation.
+This supports the argument raised in
+Sec.~\ref{sec:error-ik}: the error introduced by truncting the
+reciprocal Ewald summation is much smaller than that introduced by
+approximating $e^{2\pi i\v m\cdot\v r}$.
+The original ik-differentiation is much more accurate than
+the original analytical differentiation.
+With the staggered mesh,
+the error of the analytical differentiation reduces by more than 50\%,
+while the accuracy of the ik-differentiation is only marginally
+improved.
+The errors of the staggered mesh ik- and analytical differentiation
+are identical, which supports the theoretical prediction.
+The original ik-differentiation uses 4
+FFT transforms, and the original analytical differentiation uses
+only 2.  Therefore, the staggered mesh analytical differentiation uses
+the same amount of FFTs as the original ik-differentiation, and saves
+one half than the staggered mesh ik-differentiation.  As mentioned before,
+the FFT is a bottleneck of communication on massive parallel
+super-computers, so the staggered mesh analytical differentiation
+might have advantages on these systems.
+
+% Fig.~\ref{fig:error1} presents the RMS force error of the direct part
+% $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$,
+% reciprocal part of Ewald summation $\sqrt{\langle\vert\Delta \v
+%   F_{\textrm{rec}}\vert^2\rangle}$, the reciprocal part of the
+% analytical differentiation $\sqrt{\langle\vert\Delta \v
+%   F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ and the total
+% analytical differentiation force $\sqrt{\langle\vert\Delta \v
+%   F^{\textrm{ana}}\vert^2\rangle}$.  The real and estimated mean error
+% forces are denoted by dots and straight lines, respectively. All the
+% error estimates are overlapping with the real errors, that means the
+% error estimates developed by the present paper are very sharp.
 % Since all mean error forces varnish, the RMS force errors
 % consists of only the homogeneous contribution. 
-In the high charge density region, the error is comparatively larger
-than the low charge density region. For the direct part, the ratio is
-roughly the sqare root of the density ratio. For the reciprocal part
-this ratio is lower. The reciprocal error of the analytical
-differentiation is 4 orders of maganitudes large than that of the
-Ewald summation, which means the Ewald summation is much more precice
-than the fast algorithm based on mesh discretization.
+% In the high charge density region, the error is comparatively larger
+% than the low charge density region. For the direct part, the ratio is
+% roughly the sqare root of the density ratio. For the reciprocal part
+% this ratio is lower. The reciprocal error of the analytical
+% differentiation is 4 orders of maganitudes large than that of the
+% Ewald summation, which means the Ewald summation is much more precice
+% than the fast algorithm based on mesh discretization.
 
@@
 \subsection{Example 2: seperated positive and negative charge}
+\label{sec:example2}
 
@@
   \centering
-  \includegraphics[width=.48\textwidth]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.rho.eps}
+  % \includegraphics[width=.48\textwidth]{fig.new/rand2/fig.rho.eps}
+  \includegraphics[]{fig.new/rand2/fig.rho.eps}
   \caption{Charge distribution of Example 2. The red line
@@
 
-In this example, 16800 charges are put into a $40\textsf{nm}\times
-20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
-them are carrying a unit positive charge of $+e$, and the other half
-are carrying negative charge of $-e$. The position of these charges
-are randomly generated subject to density distribution shown in
-Fig.~\ref{fig:tmp-rho2}. The nagative charges are seperated from their
+In this example, the setting is nearly the same as
+example 1: 41472 charges are put into a
+$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
+periodic simulation box. One third of them are carrying negative
+charge of $-0.834e$, and the other two thirds are carrying positive
+charge of $+0.417e$.  The only difference is that all positive charges
+are moved to the region where the density of negative charge is low,
+see Fig.~\ref{fig:tmp-rho2}.
+In this system, the nagative charges are seperated from their
 counter ions, but the whole system is kept neutral. This case rarely
-happen in real simulation, but is serves as a good test of the error
+happens in real simulation, but serves as a good test of the error
 estimates in extreme situations.
@@
   \centering
-  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.meanf.eps}
-  \caption{Example 2: the actual (denoted by dots) and estimated
-    (denoted by straight lines) mean error force of the direct part
-    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal part
-    of Ewald summation $\langle\Delta \v F_{\textrm{rec}}\rangle$
-    (green) and the reciprocal part of the analytical differentiation
-    $\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$
-    (blue). The total mean error force of analytical differentiation
-    $\langle\Delta \v F^{\textrm{ana}}\rangle$ is given in pink.
-    Since the charge distribution is uniform on the $y$ and $z$
-    direction, the $y$ and $z$ dimension of the mean error force is
-    averaged, and the errors are plotted on $x$ direction. The
-    algorithmic parameters are the same as Fig.~\ref{fig:meanf1}.}
+  \includegraphics[]{fig.new/fig.rand2.meanf.eps}
+  \caption{
+    Example 2: the real mean error forces and the corresponding
+    estimates. All symbols and working parameters are the same
+    as     Fig.~\ref{fig:error1}.
+    The reciprocal mean error forces vanish, so the points and lines
+    overlap each other. 
+    The errors are averged over $y$ and $z$ directions, and are
+    plotted against $x$ axis.
+    % Red: the direct
+    % part of Ewald summation. Green: the reciprocal
+    % part of Ewald summation, calculated by truncation.
+    % ``$\times$'' denotes the real error, and the solid line denotes
+    % the estimated error.
+    % Blue: the reciprocal part of Ewald summation, calculated
+    % by fast algorithms. ``$\blacksquare$'': real error of
+    % the oringinal analytical
+    % differentiation. 
+    % ``$\times$'': real error of the staggered mesh analytical differentiation.
+    % Dashed line: estimated oringinal analytical differentiation.
+    % Solid line: estimated staggered mesh ik-/analytical differentiation.
+    % The $x$ component of the
+    % error forces are averged over $y$ and $z$ directions, and are
+    % plotted against $x$ axis.
+    % The cut-off in the real space is 1.31 \textsf{nm}, the number of
+    % freedom in the reciprocal space is $120\times 60\times 60$, the
+    % parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
+    % B-spline interpolation is 6.
+    }
   \label{fig:meanf2}
@@
 
-Fig.~\ref{fig:meanf2} shows the mean error forces of Example 2. All
-notations in the Figure are the same as Example 1.  Although the
+Fig.~\ref{fig:meanf2} shows the real mean error forces (by points) and the
+corresponding error esimates (by lines) of cut-offed Ewald direct
+part, truncated Ewald reciprocal part, the original
+and the staggered mesh analytical differentiation. All
+notations in the figure are the same as Example 1.  Although the
 charge distribution is not usual in this case, the error estimates are
-accurate. The two peaks of direct mean force error presented at the
-positive-negative interface result from the seperation of the positive
-and nagative charges, i.e., a non-vanishing first order charge
-distribution $\rho_q$.  Similar phenomena were observed by
-Ref.~\cite{wang2012}. The reciprocal mean force error is much smaller
-than the direct one, so the contribution to the total mean force error
-is not important.
+sharp. The two peaks of the direct mean  error force present at the
+positive-negative interface, due to the seperation of the positive
+and nagative charges, i.e., a non-vanishing and fast changing first order charge
+distribution $\rho_q$.  Similar phenomena were reported by
+Ref.~\cite{wang2012}. Surprisingly, 
+the reciprocal mean error forces
+do not present any singularity, and varnish
+all over the simulation region.
 
@@
   \centering
-  \includegraphics[]{fig/error.two_peaks_sep.box40x20x20.b1.000.r3.00.n6.K101x051x051/fig.ana.ewald.error.eps}
-  \caption{Example 2: the actual (denoted by dots) and estimated
-    (denoted by straight lines) RMS force error of the direct part
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}(\v
-      r)\vert^2\rangle}$ (red), reciprocal part of Ewald summation
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}(\v
-      r)\vert^2\rangle}$ (green) and the reciprocal part of the
-    analytical differentiation $\sqrt{\langle\vert\Delta \v
-      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
-    force error of analytical differentiation
-    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
-      r)\vert^2\rangle}$ is given in pink.  Since the charge
-    distribution is uniform on the $y$ and $z$ direction, the $y$ and
-    $z$ dimension of the mean error force is averaged, and the errors
-    are plotted on $x$ direction. The algorithmic parameters are the
-    same as Fig.~\ref{fig:meanf1}.}
+  \includegraphics[]{fig.new/fig.rand2.error.eps}
+  \caption{
+    Example 2: the real RMS error and the corresponding
+    estimates.
+    The symbols and working parameters used in this figure are the same as
+    Fig.~\ref{fig:error1}.
+    The real and estimated error of the original ik-differentiation
+    are very closed to the staggered mesh Ewald results, so
+    they are not shown in this figure for clarity, 
+    The errors are averged over $y$ and $z$ directions, and are
+    plotted against $x$ axis.
+  }
   \label{fig:error2}
@@
 
-Fig. \ref{fig:error2} shows the RMS errors of Example 2. The
-corresponding error estimates are accurate. In this case the second
-order charge distrubution is a constant, therefore the contribution to
-the error is also a constant. The same as Example 1, the reciprocal
-error of Ewald sum is much smaller than the direct error and the
-reciprocal error of analytical differentiation.  The error peak at the
-positive-negative interface, is only 3 times larger than the error of
-the bulk regions. For the dispersion interaction, the interfacial
-error could be more than one order of maganitude larger than the bulk
-error. That is because the direct interaction converges much faster
-than the dispersion interaciton ($e^{-r^2}$ v.s. $r^{-6}$).
+Fig.~\ref{fig:error2} presents the real RMS error of example 2. The
+results of the original and staggered mesh ik-differentiation are not
+shown, because they are nearly indistinguishable from the staggered
+mesh analytical differentiation in this plot.
+All the error estimates consist with the real errors.
+Steming from the inhomogeneity error,
+two peaks of the direct error form at the interfacial
+regions, and are much larger than the error in bulk
+regions~\cite{wang2012}.
+The reciprocal RMS errors only contain homogeneity contributions,
+due to the varnished mean error force.
+Similar with Example 1, the truncated Ewald
+method is much more precise than the fast algorithms, and the
+staggered mesh method improves the accuracy of analytical
+differentiation by more than 50\%.
+
+% Fig. \ref{fig:error2} shows the RMS errors of Example 2. The
+% corresponding error estimates are accurate. In this case the second
+% order charge distrubution is a constant, therefore the contribution to
+% the error is also a constant. The same as Example 1, the reciprocal
+% error of Ewald sum is much smaller than the direct error and the
+% reciprocal error of analytical differentiation.  The error peak at the
+% positive-negative interface, is only 3 times larger than the error of
+% the bulk regions. For the dispersion interaction, the interfacial
+% error could be more than one order of maganitude larger than the bulk
+% error. That is because the direct interaction converges much faster
+% than the dispersion interaciton ($e^{-r^2}$ v.s. $r^{-6}$).
 
@@
 
+\subsection{Example 3: a water system in gas-liquid phase equilibrium}
+\label{sec:example3}
+
+This example studies the gas-liquid phase equilibrum of a water
+system. The size of the simulation box and number of charges are the
+same as Example 1 (Sec.~\ref{sec:example1}): 13824 TIP3P water
+molecules~\cite{jorgensen1983comparison} are put into a
+$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
+periodic simulation box.  The molecules dynamics simulations of this
+system is performed by Gromacs 4.5~\cite{hess2008gromacs}.  The system
+is coupled to a velocity rescale thermostat~\cite{bussi2007canonical}
+at temperature 300~\textsf{K}, and simulated long enough to reach the
+equilibrium. After the equibrium,
+the water molecules seperate into the liquid and vapor phases.
+The number densities of oxygen and hydrogen atoms
+are the same as those shown by Fig.~\ref{fig:tmp-rho1}.
+50 consequential snapshots of
+the system are taken along the MD trajectory
+with a time interval of 20~\textsf{ps}.  These
+snapshots are used to calculate the real error and the charge densities
+for the error estimates.
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.new//fig.water.orig.error.eps}
+  \caption{
+    Example 3: the real RMS errors and the corresponding
+    estimates of original ik- and analytical differentiation.
+    The symbols are the same as Fig.~\ref{fig:error1}.
+    The cut-off in the real space is 1.35 \textsf{nm}, the number of
+    freedom in the reciprocal space is $120\times 60\times 60$, the
+    parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
+    B-spline interpolation is 6.
+  }   
+  \label{fig:water-error0}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.new//fig.water.ana.st.error.eps}
+  \caption{
+    Example 3: the real RMS errors and the corresponding
+    estimates. 
+    Red ``$\times$'': the real direct error.
+    Red solid line: the estimated direct error.
+    Blue ``$\times$'': the real error of the staggered mesh
+    analytical differentiation.
+    Blue ``$+$'': the real error of the staggered mesh
+    ik-differentiation, it is overlapping with the analytical differentiation.
+    Blue dashed line: the error estimate of  the staggered mesh Ewald method.
+    Blue solid line: the error estimate including the first
+    neighbor approximation of the correlation error.
+    The RMS errors are averged over $y$ and $z$ directions, and are
+    plotted against $x$ axis.
+    The cut-off in the real space is 1.35 \textsf{nm}, the number of
+    freedom in the reciprocal space is $120\times 60\times 60$, the
+    parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
+    B-spline interpolation is 6.
+  }   
+  \label{fig:water-error}
+\end{figure}
+
+The real and estimated error of the staggered mesh analytical
+differentiation are presented in Fig.~\ref{fig:water-error}.  In this
+case, due to the correlation of the charge positions, the assumption
+of independent positions is disturbed, so all estimates overestimate
+the real errors.
+The error estimate of the staggered mesh analytical differentiation is 6.8 times
+larger than the real error, which is not acceptable.
+This means in the water system, the
+positional correlation of charges plays a very important role
+in the error estimate. More surprisingly, the correlation
+actually reduces the error in force computation.
+Currently we have no explaination for this phenomenon.
+Anyway, the correlation error $\mathcal
+E_{\textrm{correlation}}$ should be included to develop a more accurate error
+estimate. 
+By including the first neighbor approximation of the
+correlation error, the error estimate is imporved greatly
+(as indicated by the arrow in Fig.~\ref{fig:water-error}), and is only
+twice as large as the real error.
+This means among all atomic
+correlates (i.e. the chemical bonds, the van der Waals interactions,
+the hydrogen bonds, etc.), the first neighbor correlation (chemical bond)
+is the most important one, and all
+the rest account for the remaining discrepancy between the estimated and real
+error.
+The quality of the error estimate for the direct
+part is still good (though not perfect): the error is overestimated by~50\%.
+This indecates that the
+first neigbor correlation is not that important in the error estimate of
+the direct part.
+Ref.~\cite{wang2010optimizing} showed that the error estimate that
+is even three times larger than the real error
+still works well in the parameter tuning process,
+so the error estimate provided by the present paper is good enough
+for the such practical applications.
+% In this example, although both error estimates are
+% not as sharp as the uncorrelated examples (Example 1 \& 2), they are
+% good enough to derive for the parameter
+% optimization~\cite{wang2010optimizing}.
+
+\section{Conclusions and remarks}
+
+In this paper, we proposed the error estimate for some state-of-art
+algoritms calculating the long-range electrostatic interaction
+in a molecular system. They were the Ewald summation, the smooth
+particle mesh Ewald (SPME, both ik- and analytical differentiation)
+and staggered mesh Ewald (both ik- and analytical differentiation).
+Unlike previous error estimates, the new error estimates were
+developed for inhomogeneous systems, and did not assume
+the uniformity of charge distribution, which is a too strong assumption
+for most real molecular simulations.
+Moreover, for the pairwise error force, we developed the
+first neighbor approximation of the correlation error, which greatly
+improved the qulity of the error estimate in the water system.
+% was shown to be playing a very important role in an inhomogeneous
+% water system.
+
+Some minor contributions of the present work are:
+\begin{itemize}
+\item In a locally neutral charge system, the inhomogeneity
+  error was proved to vanish. Therefore, the error
+  is of good property, and no adaptive method nor
+  force correction~\cite{wang2012} is necessary. Fortunately, most
+  real molecular systems are locally neutral.
+\item We explicitly gave the expression of the self-interaction term
+  in the analytical differentiation, which was proved to dominant the
+  force error in low density systems~\cite{cerutti2009staggered}.  The
+  expression helped removing the self-interaction at a very low
+  computational cost.
+\item The error estimate showed that the Staggered mesh Ewald
+  (both ik- and analytical differentiation) are always more precise than
+  the original SPME.
+\item Unlike the original analytical differentiation
+  that violates the Newton's third law, the staggered mesh analytical
+  differentiation strictly preserves it.
+\item We also proved the equivalence of the staggered mesh ik- and analytical
+  differentiation, to the leading order of the force error.
+  The staggered mesh analytical differentiation requires only one half
+  FFTs as the ik-differentiation, so the former may be preferable
+  for massive parallel simulation, due to the bottleneck of all-to-all
+  communication required by the parallel FFT.
+\end{itemize}
+
+The effectivenss of the proposed error estimates was verified by
+three numerical tests: two ideal inhomogeneous cases, in which the charges
+are randomly distributed,
+and one real water system, in which the charges are correlated.
+In the ideal cases, the all error estimates are sharp, even in the extreme
+case: positive and negative charges are globally seperated. 
+In the water system,  all estimates overestimate the real error,
+because of the correlation of charges.
+The qulitity of  error estimates for the
+real space  and the original SPME is acceptable.
+However, the error estimate neglecting the charge correlation
+is not applicable  for the staggered mesh Ewald method.
+We included the correlation error by the first neighbor approximation,
+and the 
+the qulity of the
+error estimate (of staggered mesh Ewald) was improved greatly.
+This indicates among all possible correlations, the first
+neighbor correlation is dominant.
+
+This paper only focuses on the accuracy of the
+mentioned long-range alrgoritms.
+We do not touch the topic of comparing the efficiency of these algoritms.
+For a fair comparison, we propose controling a target accuracy,
+optimizing working parameters for each algorithm and then comparing
+the excution speed.
+Such a comparison includes the topic of the hardware architecture,
+the communication bandwidth,
+the software implementation, the scale of the problem,
+the density of the system, etc.. They are far beyond the scope of the current
+work, and will be discuss in the following research.
+
 \newpage
@@
 \section{Error estimate of the Ewald summation}
+\label{sec:appendix}
 

### 2012-03-19 longRange.hetero/publish/main.tex
backup before improve theorem 1

@@
 The real and estimated error of the staggered mesh analytical
-differentiation are presented in Fig.~\ref{fig:water-error}.  In this
+differentiation are presented in Fig.~\ref{fig:water-error0}
+and Fig.~\ref{fig:water-error}.  In this
 case, due to the correlation of the charge positions, the assumption
@@
 the real errors.
+The quality of the direct
+part errors estimates is still good (though not perfect):
+the error is overestimated by~50\%.
+The ik-differentiation error is overestimated by 2.6 times,
+while the analytical differentiation error is overestimated by 4.7 times.
+% This indecates that the
+% first neigbor correlation is not that important in the error estimate of
+% the direct part.
+Ref.~\cite{wang2010optimizing} showed that the error estimate
+(ik-differentiation in a homogeneous water system) that
+is even three times larger than the real error
+still works well in the parameter tuning process, so 
+error estimate for the ik-differentiation is acceptable, but the error
+estimate for the analytical differentiation is problematic.
 The error estimate of the staggered mesh analytical differentiation is 6.8 times
-larger than the real error, which is not acceptable.
-This means in the water system, the
+larger than the real error,
+which means the
 positional correlation of charges plays a very important role
 in the error estimate. More surprisingly, the correlation
-actually reduces the error in force computation.
+actually greatly reduces the error in force computation.
 Currently we have no explaination for this phenomenon.
@@
 error.
-The quality of the error estimate for the direct
-part is still good (though not perfect): the error is overestimated by~50\%.
-This indecates that the
-first neigbor correlation is not that important in the error estimate of
-the direct part.
-Ref.~\cite{wang2010optimizing} showed that the error estimate that
-is even three times larger than the real error
-still works well in the parameter tuning process,
-so the error estimate provided by the present paper is good enough
-for the such practical applications.
+The error estimate for staggered mesh Ewald is now good enough
+for the parameter tuning application.
 % In this example, although both error estimates are
@@
 The qulitity of  error estimates for the
-real space  and the original SPME is acceptable.
+real space  and the original ik-differentiation is acceptable.
 However, the error estimate neglecting the charge correlation

### 2012-03-21 longRange.hetero/publish/main.tex
backup the first finished version for publish

--- 2012-03-18 longRange.hetero/publish/main.tex
@@
 
-\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
+\title{The Error Estimate for Computing Electrostatic Interaction
+  in the Inhomogeneous and Correlated Molecular Systems:
+  for the Ewald Summation, SPME and Staggered Mesh Ewald.
+}
 \author{Han Wang}
-\affiliation{LMAM and School of Mathematical
-  Sciences, Peking University}
+\email{han.wang@fu-berlin.de}
+\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+\author{Christof Sch\"utte}
+\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
 \author{Pingwen Zhang}
@@
 \begin{abstract}
+
 \end{abstract}
@@
 \maketitle
+
+\section{Introduction}
+
+The calculation of long-range electrostatic interaction is a very
+important topic in the molecular simulations.  Due to the very slow
+decay of the interaction with respect to the distance between charges,
+the cut-off and neighbor list algoritm does not work, and moreover the
+energy of the system is only conditionally convergent.  One of the
+first algoritms handling this problem is the Ewald summation that
+dates back to 1920's~\cite{ewald1921die}.  However, it is shown that
+with a careful tuning of working parameters, the optimal computational
+cost of the Ewald summation is of $\mathcal
+O(N^{3/2})$~\cite{perram1988asc}, which is not feasible for morden
+large scale molecular simulations. The particle mesh Ewald (PME)
+method~\cite{darden1993pme}, the smooth particle mesh Ewald (SPME)
+method~\cite{essmann1995spm} and the particle-particle-particle-mesh
+(P3M) method~\cite{hockney1988computer, deserno1998mue1} are the most
+popular Ewald-based fast algorithms that reduces the computational
+cost to $\mathcal O(N\log N)$. More recently, the staggered mesh or
+``interlacing'' technique firtly developed in
+1970's~\cite{chen1974reduction,eastwood1976optimal} is applied to SPME
+(called staggered mesh Ewald)~\cite{cerutti2009staggered} and P3M
+(called interlaced P3M)~\cite{neelov2010interlaced}, and is showed to
+improve the accuracy of these algorithms.
+
+The fast algoritms have achieved great success in the computer
+simulation of charged molecular systems over the past three decades.
+However, the fact that the user should provide six working parameters
+for these methods may be problematic: it is diffcult to try out the
+most efficient parameter set, and an arbitary choice may lead to
+qualitively wrong simulation result. This problem can be solved by an
+in-depth study of the error introduced by these algrotims, namly the
+error estimate~\cite{petersen1995accuracy, deserno1998mue2,
+  wang2010optimizing, neelov2010interlaced, ballenegger2012convert},
+by which the error is described by a function of the working
+parameter.  By these error estimates, a work flow was designed to
+automatically determine the nearly optimal combination of parameters,
+in the sense that it is fastest one given a demanding
+accuracy~\cite{wang2010optimizing}. However, so far, all error
+estimates assume the homogeneity of the charge distribution, and the
+independency of any pair of charges (i.e. the charges are
+uncorrelated), but neither of them is satisfactorily fulfilled in most
+realistic systems of practical interest.  For example, the lipid biomembrane
+solving in water: the carbon chains of the lipids carry no charge, and
+the charges are correlated by covalent bonds, van der Waals
+interaction, hydrogen bonding network, etc..  Therefore, the current
+error estimates may be problematic, or even not applicable.  A lot of
+research have shown that due to the correlation of charges, the error estimates
+obviously deviate from the real
+error~\cite{deserno1998mue2,wang2010optimizing,ballenegger2012convert}.
+
+The purpose of this research is to develop an realiable force error
+estimate in inhomogeneous and strongly correlated molecular systems.
+We estimate the force error because the application is the molecular
+dynamics (MD) simulation.  Firstly, a most general error estimate
+frame work for the pairwise interactions is set up. We prove that the
+error is decomposed into three additive parts: the homogeneity error,
+the inhomogeneity error and the correlation error~\cite{wang2012}. The
+homogeneity and inhomogeneity error can be calculated at a cost of
+$\mathcal O(N\log N)$ given the convolutional form of the error
+estimates.  Then a way is proposed to calculate the approximation of
+correlation error at cost of $\mathcal O(N\log N)$. Though it is
+possible to improve the accuracy of the approximation systematically,
+numerical results show that it is good enough
+to consider the correlation stems from
+the neighboring atoms within the same molecule
+in an inhomogeneous water system.  Following this framework, we
+develop the error estimate for the Ewald summation, the SPME method
+and the staggered method Ewald method. We study the SPME method
+because it is the one of the most popular long-range algorithms among
+the mainstream MD simulation packages, for example,
+AMBER~\cite{case2005amber}, GROMACS~\cite{van2005gromacs,
+  hess2008gromacs} and NAMD~\cite{phillips2005scalable}.  The estimate
+of the homogeneity and inhomogeneous errors is tested by by two
+randomly distributed inhomogeneous charges systems, and is proved to
+be very sharp in these ideal systems.  By studying a real
+inhomogeneous water system, the nearest neigbor approximation of
+correlation error is proved to improve the quality of error estimate
+greatly. This paper is ended by conclusions and remarks in
+section~\ref{sec:conclusions}.
+
+% Then a
+% systematical approach to calculate the correlation error app
 
@@
     % \sum^\ast_{\v n}
-    \sum_{j=1}^N\,q_iq_j \v K(\v r_i - \v r_j),
+    \sum_{j=1}^N\,q_iq_j \v K(\v r_i, \v r_j),
   \end{align}
@@
     \langle\Delta\v F(\v r_i)\rangle
-    =q_i\, [\v K\ast\rho_q](\v r_i),
+    =q_i\, \int_{\mathbb R^3}\v K (\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r',
   \end{align}
@@
     = &\,
-    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
-    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:thm-error}
+    q_i^2\,\int_{\mathbb R^3}\vert\v K(\v r_i,\v r')\vert^2\,\rho_{q^2} (\v r')\,\d d\v r' + 
+    q_i^2\,
+    \big[
+    \int_{\mathbb R^3}\v K(\v r_i,\v r')\,\rho_{q}(\v r')\,\d d\v r'
+    \,\big]^2
+    \\\label{eqn:thm-error}
     &+
     q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i-\v r')\cdot
-    \v K(\v r_i-\v r'')\,
+    \v K(\v r_i,\v r')\cdot
+    \v K(\v r_i,\v r'')\,
     C_{q^2}(\v r', \v r'')\,
@@
     &=
-    q_i\bigg\langle \sum_{j=1}^Nq_j\v K(\v r_i -\v r_j)\bigg\rangle\\
+    q_i\bigg\langle \sum_{j=1}^Nq_j\v K(\v r_i,\v r_j)\bigg\rangle\\
     &=
-    q_i\int_{\mathbb R^3}\v K(\v r_i - \v r')
+    q_i\int_{\mathbb R^3}\v K(\v r_i, \v r')
     \bigg\langle \sum_{j=1}^Nq_j\delta (\v r' -\v r_j)\bigg\rangle
@@
     &= 
-    q_i\, [\v K\ast\rho_q](\v r_i),
+    q_i\,\int\v K(\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r'.
   \end{align*}
@@
     q_i^2\bigg\langle\sum_{j,k}
-    q_jq_k\v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)\bigg\rangle \\ \nonumber
+    q_jq_k\v K(\v r_i, \v r_j)\cdot\v K(\v r_i, \v r_k)\bigg\rangle \\ \nonumber
     =\,&
     q_i^2\bigg\langle\sum_{j=1}^N
-    q_j^2\vert\v K(\v r - \v r_j)\vert^2
+    q_j^2\vert\v K(\v r, \v r_j)\vert^2
     \bigg\rangle +
     q_i^2\bigg\langle\sum_{j\neq k}
-    q_jq_k \v K(\v r - \v r_j)\cdot\v K(\v r - \v r_k)
+    q_jq_k \v K(\v r, \v r_j)\cdot\v K(\v r, \v r_k)
     \bigg\rangle \\ \nonumber
@@
     q_i^2\int_{\mathbb R^3}
-    \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+    \vert\v K(\v r_i, \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
     \\\label{eqn:prf-error-step3}
@@
     q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
+    \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
     \rho^{(2)}(\v r', \v r'')
@@
     q_i^2\int_{\mathbb R^3}
-    \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+    \vert\v K(\v r_i , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
     +
     q_i^2
-    \bigg[
+    \big[
     \int_{\mathbb R^3}
-    \v K(\v r_i - \v r')\rho_{q}(\v r')\,\d d\v r'
-    \bigg]^2
+    \v K(\v r_i , \v r')\rho_{q}(\v r')\,\d d\v r'
+    \big]^2
     \\ \nonumber
@@
     q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
+    \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
     C(\v r', \v r'')
@@
 \end{proof}
-Here are some remarks concerning Theorem~\ref{thm:tmp1}:
+\begin{corollary}\label{thm:tmp2}
+  If the function $\v K$ has the property
+  \begin{align}
+    \label{eqn:cor-kernel}
+    \v K(\v r_i,\v r_j) = \v K(\v r_i - \v r_j),    
+  \end{align}
+  then the error estimates are in the convolution form, namely:
+  \begin{align}\label{eqn:cor-meanf}
+    \langle\Delta\v F(\v r_i)\rangle
+    =q_i\, [\v K\ast\rho_q](\v r_i),
+  \end{align}
+  and 
+  \begin{align}\nonumber
+    \mathcal E (\v r_i) 
+    = &\,
+    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
+    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:cor-error}
+    &+
+    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r_i-\v r')\cdot
+    \v K(\v r_i-\v r'')\,
+    C_{q^2}(\v r', \v r'')\,
+    \d d\v r'\d d\v r''.
+  \end{align}
+  Where $\ast$ denotes the convolution.
+\end{corollary}
+
+Here are some remarks concerning Theorem~\ref{thm:tmp1} and Corollary~\ref{thm:tmp2}:
 \begin{itemize}
@@
   the error estimates Eqn.~\eqref{eqn:thm-meanf} and \eqref{eqn:thm-error}.
-  The function $\v K(\v r)$ is called \emph{the error force
+  The function $\v K(\v r_i, \v r_j)$ is called \emph{the error force
     kernel}.
-  By setting $q_i = q_j = 1$, the theorem~\ref{thm:tmp1} directly proves
+  By setting $q_i = q_j = 1$, the corollary~\ref{thm:tmp2} directly proves
   the error estimates for the short-range interaction
@@
   \end{align}
-  The homogeneity error and the inhomogeneity
+\item
+  Without the property $\v K(\v r_i,\v r_j) = \v K(\v r_i - \v r_j)$,
+  theorem~\ref{thm:tmp1} calculate the homogeneity and inhomogeneity
+  error at a cost of $\mathcal O(N^2\log N)$, and correlation error
+  at a cost of $\mathcal O(N^3\log N)$.
+  By writting the error estimates in the covolution form in
+  the corollary~\ref{thm:tmp2},
+  the homogeneity error and the inhomogeneity
   error can be calculated at the cost of $\mathcal O(N\log N)$ by the
@@
 
-\subsection{First neighbor approximation of the correlation
+\subsection{Nearest neighbor approximation of the correlation
 error}
 
-In this section, we consider the first neighbor approximation of the
-correlation error. Here ``first neighbors'' means the neighboring
-atoms that are connected by the chemical bond.  In most molecular
-force fields, such bonds are modeled by a rigid connection between two
-atoms.  Therefore, the correlation between such an atom pair is very
-strong. As an example, we consider a typical three point charge water
-model TIP3P~\cite{jorgensen1983comparison}: each hydrogen atom carries
-a charge of $q_{\textrm{H}} = +0.417e$ and each oxygen atom carries a charge of
-$q_{\textrm{O}} = -0.834e$. Within one molecule, the H-O bond and H-O-H angle are
-rigid. 
+In this section, we consider the nearest neighbor approximation of the
+correlation error. Here the definition of the ``nearest neighbor'' is
+very flexible, basically it means the neigbors of a charge that are
+not very far away. It could be defined by the charges falling in some
+certain neighboring range or charge connected by a chemical bonds.
+% Here ``first neighbors'' means the neighboring
+% atoms that are connected by the chemical bond.  In most molecular
+% force fields, such bonds are modeled by a rigid connection between two
+% atoms.  Therefore, the correlation between such an atom pair is very
+% strong.
 % In the system of water, the relative position of the oxygen and
@@
   q_i^2\int_{\mathbb R^3}
-  \vert\v K(\v r_i - \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+  \vert\v K(\v r_i , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
   \\
@@
   q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-  \v K(\v r_i - \v r')\cdot\v K(\v r_i - \v r'')\,
+  \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
   \rho^{(2)}(\v r', \v r'')
@@
 % \end{align}
-We seperately consider the first neighbor contribution
+We seperately consider the  contribution from nearest neigbors
 and other contributions to
@@
 $\Omega_j = \{ \,k\,\vert\,
-\textrm{atom $k$ is the first neighbor of atom $j$} \,\}$,
+\textrm{atom $k$ is the nearest neighbor of atom $j$} \,\}$,
 % the set of the first neighbors of the $j$-th atom by $\Omega_j$,
@@
 \end{align}
-For any atom $k$ that is not the first neighbor of atom $j$, we
-assume that its position is independent with atom $j$, then
+We assume two charges are independent if they are not nearest neighbors.
+Then
 second part on the r.h.s. of the Eqn.~\eqref{eqn:split-rho-q2} is
-approximately $\frac{N-3}{N}\rho_q(\v r')\rho_q(\v r'')\approx
-\rho_q(\v r')\rho_q(\v r'')$.
+approximately $\frac{N-\#(\Omega_j)}{N}\rho_q(\v r')\rho_q(\v r'')\approx
+\rho_q(\v r')\rho_q(\v r'')$, where $\#(\Omega_j)$ is the number of nearest neighbors considered. This approximation is valid only when the number
+of neigbors considered is small comparing with the number of charges
+in the system.
 % If the number of atoms in the system is
@@
 \begin{align}\label{eqn:fnc-correlation-water}
-  C_{q^2}(\v r', \v r'') =
+  C_{q^2}(\v r', \v r'') \approx
   \bigg\langle
@@
   \mathcal E_{\textrm{correlation}}(\v r_i)
-  = q_i^2\sum_j\sum_{k\in\Omega_j}q_jq_k
+  \approx q_i^2\sum_j\sum_{k\in\Omega_j}q_jq_k
   \big\langle
-  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
   \big\rangle_{\v r_j,\v r_k}
 \end{align}
-Denoting the index set of the oxygen atoms by $\Omega_{\textrm{O}}$,
-and the index set of the hydrogen atoms by $\Omega_{\textrm{H}}$, 
-we have:
+The quality of this approximation depends on how to define the
+``nearest neighbors''. In the system of liquid and gas, the
+correlation is only short-ranged, so it is possible to systematically
+impove the accuracy by considering more and more neigbors as long as
+the number of neigbors is small comparing with the size of the system.
+
+As an example, we consider a typical three point charge water model
+TIP3P~\cite{jorgensen1983comparison}: each hydrogen atom carries a
+charge of $q_{\textrm{H}} = +0.417e$ and each oxygen atom carries a
+charge of $q_{\textrm{O}} = -0.834e$. Within one molecule, the H-O
+bond and H-O-H angle are rigid, so the correlation within one molecule
+is very strong.  Therefore, in this case, we define the nearest neighbor by the
+atoms within the same water molecule.  Denoting the index set of the oxygen
+atoms by $\Omega_{\textrm{O}}$, and the index set of the hydrogen
+atoms by $\Omega_{\textrm{H}}$, we have:
 \begin{align}\nonumber
@@
   \big\langle
-  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
   \big\rangle_{\v r_j,\v r_k} \\ \nonumber
@@
   \big\langle
-  \v K(\v r_i - \v r_j)\cdot\v K(\v r_i - \v r_k)
+  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
   \big\rangle_{\v r_j,\v r_k} \\\nonumber
@@
   \int_{\mathbb R^3}
-  \v K(\v r_i - \v r')\cdot
-  \big\langle
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_1})+
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_2})
-  \big\rangle\,\rho_{\textrm{O}}(\v r')
+  \v K(\v r_i , \v r')\cdot
+  2\big\langle
+  q_{\textrm{H}}\v K(\v r_i , \v r' + \v s_{\textrm{O}})
+  \big\rangle\,
+  \rho_{\textrm{O}}(\v r')
   \d d\v r' \\\label{eqn:c-error-1}
@@
   \int_{\mathbb R^3}
-  \v K(\v r_i - \v r')\cdot
+  \v K(\v r_i , \v r')\cdot
   \big\langle
-  q_{\textrm{O}}\v K(\v r_i - \v r' + \v s_{\textrm{O}})+
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}})
+  q_{\textrm{O}}\v K(\v r_i , \v r' - \v s_{\textrm{O}})+
+  q_{\textrm{H}}\v K(\v r_i , \v r' + \v s_{\textrm{H}})
   \big\rangle\,\rho_{\textrm{H}}(\v r')
@@
 $\v r_{\textrm{H}_1}$, $\v r_{\textrm{H}_2}$ and $\v r_{\textrm{O}}$, then
-$\v s_{\textrm{H}_1} = \v r_{\textrm{H}_1} - \v r_{\textrm{O}}$, 
-$\v s_{\textrm{H}_2} = \v r_{\textrm{H}_2} - \v r_{\textrm{O}}$,
-$\v s_{\textrm{O}} = \v r_{\textrm{O}} - \v r_{\textrm{H}_1}$ and
+% $\v s_{\textrm{H}_1} = \v r_{\textrm{H}_1} - \v r_{\textrm{O}}$, 
+% $\v s_{\textrm{H}_2} = \v r_{\textrm{H}_2} - \v r_{\textrm{O}}$,
+% $\v s_{\textrm{O}} = \v r_{\textrm{O}} - \v r_{\textrm{H}_1}$ and
+% $\v s_{\textrm{H}} = \v r_{\textrm{H}_2} - \v r_{\textrm{H}_1}$.
+$\v s_{\textrm{O}} = \v r_{\textrm{H}_1} - \v r_{\textrm{O}}$ and
 $\v s_{\textrm{H}} = \v r_{\textrm{H}_2} - \v r_{\textrm{H}_1}$.
@@
 with others.
+
+To calculate the nearest neighbor approximated correlation error,
+we assume the error force kernel
+has the form $\v K(\v r_i , \v r_j) = \v K(\v r_i - \v r_j)$, so
+the integrals can be written in the covolution form and accelerated by the FFT.
 % In the example considered by the present paper in section~\ref{sec:tmp3},
@@
 \begin{align} \nonumber
-  &\big\langle
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_1})+
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{H}_2})
-  \big\rangle \\ \nonumber
+  \big\langle
+  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{O}})
+  \big\rangle 
   =\,&
@@
   q_{\textrm{H}}\hat{\v K}(\v m)
-  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{H}_1})} +
-  \sum_{\v m}
-  q_{\textrm{H}}\hat{\v K}(\v m)
-  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{H}_2})}
+  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{O}})} 
   \bigg\rangle \\\nonumber
@@
   \frac1V\sum_{\v m}
-  \hat{\v K}(\v m)
-  e^{2\pi i\v m\cdot(\v r_i - \v r')}
-  \,  
   \langle
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_1}} +
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_2}}
-  \rangle,
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}}
+  \rangle\,
+  \hat{\v K}(\v m)\,
+  e^{2\pi i\v m\cdot(\v r_i - \v r')},
 \end{align}
@@
   &= 
-  \langle
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_1}} +
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}_2}}
+  2\langle
+  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}}
   \rangle,\\
@@
   \langle
-  q_{\textrm{O}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}} +
+  q_{\textrm{O}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}} +
   q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}}}
@@
 
-Both the direct part and reciprocal part of the Ewald summation can be
-written in the pairwise form of Eqn.~\eqref{eqn:thm-error-force}.  The direct
-error force kernel is defined by:
+Both the error force kernel of the direct and reciprocal
+part of the Ewald summation can be
+written in the form of Eqn.~\eqref{eqn:cor-kernel}.  The direct
+part is:
 % The direct part is a short-range interaction in real space, so it is
@@
 \end{align}
-By the Therefore \ref{thm:tmp1}, the error estimate of the
+By the corollary~\ref{thm:tmp2}, the error estimate of the
 truncated Ewald summation is straightforward.
@@
 Unfortunately, the
-error force of ik-differentiation~\eqref{eqn:ik.error.force} cannot be written
-in the form of~\eqref{eqn:thm-error-force}, so the error estimate derived by
-Theorem~\ref{thm:tmp1} cannot be used here. However, it is still
-possible to develop the error estimate for the ik-differentiation.
+error force kernel of ik-differentiation
+cannot be written
+in the form of~\eqref{eqn:cor-kernel}, so the error estimate derived by
+corollary~\ref{thm:tmp2} cannot be used here. However, it is still
+possible to develop the error estimate with convolution form.
 Here we only want to present the key idea and the final  error
@@
   - 2 q_i
-  \bigg[
+  \big[
   \big(
@@
   \ast\rho_q\,
-  \bigg] (\v r_i),
+  \big] (\v r_i),
 \end{align}
@@
   2q_i^2
-  \bigg[\,
+  \big[
   \big(
@@
   \ast \rho_{q^2}
-  \,\bigg] (\v r_i)\\\nonumber
+  \,\big] (\v r_i)\\\nonumber
   &\,+
   4q_i^2\,
-  \bigg[
+  \big[
   \big(
@@
   \ast \rho_{q^2}\,
-  \bigg] (\v r_i) \\\label{eqn:ik.error}
+  \big] (\v r_i) \\\label{eqn:ik.error}
   &\,+
@@
 so it can be calculated once and stored in a table for further uses.
+The nearest neighbor approximation to the correlation error is:
+\begin{align}\nonumber
+  \mathcal E^{\textrm{ik}}_{\textrm{correlation}}(\v r_i)
+  =\,&
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \v G_{\alpha,l}\cdot[\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}
+  \,\big] (\v r_i) \\\nonumber
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}\,
+  \big] (\v r_i) \\\nonumber
+  \,&+
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \v G_{\alpha,l}\cdot[\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}
+  \,\big] (\v r_i) \\
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}\,
+  \big] (\v r_i).
+\end{align}
 
@@
   &=
-  \nabla_{\v r}\,A(\v m, \v r)\\
+  \nabla_{\v r}\,A(\v m, \v r)\\\label{eqn:error-B}
   &=
@@
   q_i^2
-  \bigg[\,
+  \big[
   \big(
@@
   \ast \rho_{q^2}
-  \,\bigg] (\v r_i) \\\nonumber
+  \,\big] (\v r_i) \\\nonumber
   & +\,
   q_i^2
-  \bigg[
+  \big[
   \big(
@@
   \vert
-  \v G_{\alpha,l} + 2\pi i\,l K_\alpha F_{\alpha,l} \v a_\alpha^\ast\vert^2
+  % \v G_{\alpha,l} + 2\pi i\,l K_\alpha F_{\alpha,l} \v a_\alpha^\ast\vert^2
+  \v G_{\alpha,l} + \v F_{\alpha,l}\vert^2
   \big)
   \ast \rho_{q^2}
-  \bigg]
+  \big]
   (\v r_i) \\ \nonumber
@@
   4q_i^2\,
-  \bigg[
+  \big[
   \big(
@@
   \ast \rho_{q^2}\,
-  \bigg] (\v r_i) \\\label{eqn:ana.error}
+  \big] (\v r_i) \\\label{eqn:ana.error}
   & +\,
@@
 \begin{align}
-  F_{\alpha,l} (\v r)
+  \v F_{\alpha,l} (\v r)
   &=
@@
     \end{subarray}}
-  (-2)f(\v m)\,
+  -4 \pi i\, l K_\alpha \v a^\ast_\alpha\,f(\v m)\,
   Z_{\alpha,l}(\v m)\,
@@
 % so they can be tabulated in advance for the simulation.
-$F_{\alpha,l} (\v r)$ 
+$\v F_{\alpha,l} (\v r)$ 
 does not depends on the coordinates of particles,
 so it can be tabulated in advance for the simulation.
+The nearest neighbor approximation to the correlation error is
+\begin{align}\nonumber
+  \mathcal E^{\textrm{ana}}_{\textrm{correlation}}(\v r_i)
+  =\,&
+  q_i^2
+  \big[\,
+  \big\{
+  \sum_{\alpha} \sum_{l\neq 0}
+  (\v G_{\alpha,l}+\v F_{\alpha,l})\cdot
+  [\hat T_{\textrm{O}} (\hat{\v G}_{\alpha,l}+\hat{\v F}_{\alpha,l})]^{\vee}
+  \big\}
+  \ast \rho_{\textrm{O}}
+  \,\big] (\v r_i) \\\nonumber
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}\,
+  \big] (\v r_i) \\\nonumber
+  \,&+
+  q_i^2
+  \big[\,
+  \big\{
+  \sum_{\alpha} \sum_{l\neq 0}
+  (\v G_{\alpha,l}+\v F_{\alpha,l})\cdot
+  [\hat T_{\textrm{H}} (\hat{\v G}_{\alpha,l}+\hat{\v F}_{\alpha,l})]^{\vee}
+  \big\}
+  \ast \rho_{\textrm{H}}
+  \,\big] (\v r_i) \\
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}\,
+  \big] (\v r_i) 
+\end{align}
 
@@
   Z_{\alpha,l}(\v m)\,
-  \bigg[
+  \big[
   (1 + e^{\pi i l})e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 2
-  \bigg].
+  \big].
 \end{align}
@@
 \end{align}
-This is a pairwise interaction, the Theorem~\ref{thm:tmp1} is applicable.
+The error force kernel has the form of Eqn.~\eqref{eqn:cor-kernel},
+then the corollary~\ref{thm:tmp2} is applicable.
 Moreover, since both the exact and the error
-force are pairwise,  the Newton's third law is preserved by the
+force are anti-symmetric,  the Newton's third law is preserved by the
 calculated force.
@@
   \ast \rho_{q^2}\,
-  \bigg] (\v r_i) +
+  \big] (\v r_i) +
   \big\langle
@@
 mesh ik-differentiation and staggered mesh analytical differetiation
-are the same method. Considering the latter uses
+are equivalent. Considering the latter uses
 only one half of  FFTs as the former, it might be preferabel
@@
 and~\eqref{eqn:ana-st-error-force}, the Newton's
-third law is preserved by the staggered method analytical differetiation.
+third law is preserved by the staggered mesh analytical differetiation.
 
@@
     estimates of original ik- and analytical differentiation.
-    The symbols are the same as Fig.~\ref{fig:error1}.
-    The cut-off in the real space is 1.35 \textsf{nm}, the number of
-    freedom in the reciprocal space is $120\times 60\times 60$, the
-    parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
-    B-spline interpolation is 6.
+    Red: the direct part.
+    Green: the original ik-differentiation.
+    Blue: the original analytical differentiation.
+    ``$\times$'': the real error.
+    Dashed line: the RMS error estimate.
+    Solid  line: the RMS error estimate, with the nearest neighbor
+    approximation of correlation error.
+    The working parameters are the same as exaple 1.
+    The black arrows indecate the improvement
+    of error estimate by including nearest neighbor
+    approximation of correlation error.
   }   
@@
     estimates. 
-    Red ``$\times$'': the real direct error.
-    Red solid line: the estimated direct error.
     Blue ``$\times$'': the real error of the staggered mesh
@@
     Blue dashed line: the error estimate of  the staggered mesh Ewald method.
-    Blue solid line: the error estimate including the first
+    Blue solid line: the error estimate including the nearest
     neighbor approximation of the correlation error.
@@
     plotted against $x$ axis.
-    The cut-off in the real space is 1.35 \textsf{nm}, the number of
-    freedom in the reciprocal space is $120\times 60\times 60$, the
-    parameter $\beta$ is $2.5\; \textsf{nm}^{-1}$, and the order of
-    B-spline interpolation is 6.
+    The working parameters are the same as example 1.
+    The black arrow indecates the improvement
+    of error estimate by including nearest neighbor
+    approximation of correlation error.
   }   
@@
 
-The real and estimated error of the staggered mesh analytical
-differentiation are presented in Fig.~\ref{fig:water-error}.  In this
-case, due to the correlation of the charge positions, the assumption
-of independent positions is disturbed, so all estimates overestimate
+The real and estimated errors of the original SPME
+(both ik- and analytical differentiation)
+and the staggered mesh Ewald (both ik- and analytical differentiation)
+are in Fig.~\ref{fig:water-error0}
+and Fig.~\ref{fig:water-error}.
+The staggered method ik- and analytical differentiation
+are also equivalent in this case, so they are mentioned by the ``staggered
+mesh Ewald''  for convenience.
+In this case, due to the correlation of the charge positions, the assumption
+of independent positions is disturbed, so all estimates deviate from
 the real errors.
-The error estimate of the staggered mesh analytical differentiation is 6.8 times
-larger than the real error, which is not acceptable.
-This means in the water system, the
-positional correlation of charges plays a very important role
-in the error estimate. More surprisingly, the correlation
-actually reduces the error in force computation.
+The quality of the direct
+part errors estimates is still good (though not perfect):
+the error is overestimated by~50\%.
+The RMS errors of the ik-differentiation, analytical differentiation
+and the staggered mesh Ewald method are
+overestimated by 2.6, 4.7 and 6.8 times, respectively.
+Notice the only difference between this example and example 1 is the correlation
+of the charges in the system,
+so it plays a very important role in the RMS error. 
+More surprisingly, the correlation
+actually  reduces the error in the force computation.
 Currently we have no explaination for this phenomenon.
@@
 estimate. 
-By including the first neighbor approximation of the
-correlation error, the error estimate is imporved greatly
-(as indicated by the arrow in Fig.~\ref{fig:water-error}), and is only
-twice as large as the real error.
-This means among all atomic
+By including the nearest neighbor approximation of the
+correlation error, the quality of all error estimates is imporved greatly
+(as indicated by the arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}).
+Now the RMS errors of ik-differentiation, analytical differentiation
+and staggered mesh Ewald method
+are overestimated by a factor of 1.16, 1.44 and 1.86,
+respectively.
+Ref.~\cite{wang2010optimizing} showed that the error estimate
+(ik-differentiation in a homogeneous water system) that
+is even three times larger than the real error
+still works well in the parameter tuning process, 
+so the error estimate for  all methods are now good enough
+for the parameter tuning application.
+The great improvement by the nearest neighbor approximation 
+means that  among all atomic
 correlates (i.e. the chemical bonds, the van der Waals interactions,
-the hydrogen bonds, etc.), the first neighbor correlation (chemical bond)
+the hydrogen bonds, etc.), the nearest neighbor correlation (rigid
+modeling of H-O bond and H-O-H angle)
 is the most important one, and all
@@
 error.
-The quality of the error estimate for the direct
-part is still good (though not perfect): the error is overestimated by~50\%.
-This indecates that the
-first neigbor correlation is not that important in the error estimate of
-the direct part.
-Ref.~\cite{wang2010optimizing} showed that the error estimate that
-is even three times larger than the real error
-still works well in the parameter tuning process,
-so the error estimate provided by the present paper is good enough
-for the such practical applications.
+
+% pbut the error
+% estimate for the analytical differentiation is problematic.
+% The error estimate of the staggered mesh analytical differentiation is 6.8 times
+% larger than the real error,
+% which means the
+% positional correlation of charges plays a very important role
+% in the error estimate. More surprisingly, the correlation
+% actually greatly reduces the error in force computation.
+% Currently we have no explaination for this phenomenon.
+% Anyway, the correlation error $\mathcal
+% E_{\textrm{correlation}}$ should be included to develop a more accurate error
+% estimate. 
+% By including the first neighbor approximation of the
+% correlation error, the error estimate is imporved greatly
+% (as indicated by the arrow in Fig.~\ref{fig:water-error}), and is only
+% twice as large as the real error.
+% This means among all atomic
+% correlates (i.e. the chemical bonds, the van der Waals interactions,
+% the hydrogen bonds, etc.), the first neighbor correlation (chemical bond)
+% is the most important one, and all
+% the rest account for the remaining discrepancy between the estimated and real
+% error.
+% The error estimate for staggered mesh Ewald is now good enough
+% for the parameter tuning application.
 % In this example, although both error estimates are
@@
 \section{Conclusions and remarks}
+\label{sec:conclusions}
 
@@
 and staggered mesh Ewald (both ik- and analytical differentiation).
-Unlike previous error estimates, the new error estimates were
-developed for inhomogeneous systems, and did not assume
-the uniformity of charge distribution, which is a too strong assumption
-for most real molecular simulations.
-Moreover, for the pairwise error force, we developed the
-first neighbor approximation of the correlation error, which greatly
+Unlike previous error estimates, the new error estimates did not
+assume the homogeneity and uncorrelation of the system,
+which is a too strong assumption for most real molecular simulations.
+The correlation of the charges is considered by the nearest
+neighbor approximation, which greatly
 improved the qulity of the error estimate in the water system.
-% was shown to be playing a very important role in an inhomogeneous
-% water system.
 
@@
 The qulitity of  error estimates for the
-real space  and the original SPME is acceptable.
-However, the error estimate neglecting the charge correlation
-is not applicable  for the staggered mesh Ewald method.
-We included the correlation error by the first neighbor approximation,
-and the 
-the qulity of the
-error estimate (of staggered mesh Ewald) was improved greatly.
+real space  is acceptable.
+% However, the error estimate neglecting the charge correlation
+% is not applicable  for the staggered mesh Ewald method.
+The error estimates for the reciprocal space fast algoritms
+are greatly improved by including the first neighbor approximation
+to the correlation error.
 This indicates among all possible correlations, the first
@@
 \appendix
-\section{Error estimate of the Ewald summation}
+\section{Error estimate of the smooth particle mesh
+Ewald method}
 \label{sec:appendix}
+
+\subsection{ik-differentiation}
+Starting from Eqn.~\eqref{eqn:ik.error.force}, we have the error force kernel
+of the ik-differentiation:
+\begin{align}
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j)
+  =
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  [\,A(\v m, \v r_i) + A(\v m,-\v r_j)\,]
+  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+\end{align}
+By inserting Eqn.~\eqref{eqn:error-A}, the error force kernel is
+\begin{align}
+  \label{eqn:ik.kernel.2}
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j)
+  =
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \,(
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  Z_{\alpha,l}(\v m)
+  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+\end{align}
+To calculate the mean error force estimate, we should
+calculate the integral of
+$\int \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r')\rho_q(\v r')\,\d d\v r$.
+By Eqn.~\eqref{eqn:ik.kernel.2}, we should calculate
+$  \int e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r'}\rho_q(\v r')
+\,e^{2\pi i\v m\cdot\v r'}\,\d d\v r'$, which is the inverse Fourier transform
+of $e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r'}\rho_q(\v r')$. Notice,
+for example, when $\alpha=1$ we have:
+\begin{align}
+  [\,\rho_q(\v r')\,e^{-2\pi i l K_1\v a^\ast_1\cdot \v r'}\,] ^\vee
+  (m_1, m_2, m_3)
+  = \check\rho(m_1-lK_1, m_2, m_3).
+\end{align}
+Since $\vert m_1\vert < K_1/2$ and $l\neq 0$,
+$\check\rho(m_1-lK_1, m_2, m_3)$ is
+the high wave number (higher than $K_\alpha / 2$) part of the density profile.
+If the density is smooth enough, this term can be resonably neglected.
+Therefore,
+\begin{align}\nonumber
+  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r_i)\rangle
+  =\,&
+  q_i\, \int_{\mathbb R^3}
+  \v K^{\textrm{ik}}_{\textrm{rec}} (\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r'\\
+  \approx\,&
+  q_i
+  \big\{
+  \big[
+  \sum_{\alpha}\sum_{l\neq 0}
+  (e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}   - 2 )
+  \v G_{\alpha,l}
+  \big]
+  \ast\rho_q\,
+  \big\} (\v r_i),
+\end{align}
+Further neglecting the
+high-wave-number term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}$, we reach:
+\begin{align}
+  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r_i)\rangle
+  \approx\,&
+  -2q_i
+  \big[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}\v G_{\alpha,l}
+  \big)
+  \ast\rho_q\,
+  \big] (\v r_i).
+\end{align}
+
+To calculate the RMS error, we square the error force kernel:
+\begin{align}\nonumber
+  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r_j)\vert^2
+  =\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{
+    \begin{subarray}{c}
+      \vert n_{\alpha}\vert < K_\alpha/2\\
+      \v n\neq 0
+    \end{subarray}}
+  \sum_{\alpha,\beta}
+  \sum_{l_1,l_2}
+  \v g(\v m)\cdot\v g(\v n)\,
+  Z_{\alpha,l_1}(\v m)Z_{\beta,l_2}(\v n)
+  \\\nonumber
+  &\,
+  \times
+  \,(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  \,(
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
+  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+  - 2
+  )\\
+  &\,
+  \times
+  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
+\end{align}
+By  carefully calculating
+$  (
+e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+- 2
+)
+\,(
+e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
+e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+- 2
+)$:
+\begin{align}\nonumber
+  &(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  \,(
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
+  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+  - 2
+  ) \\ \nonumber
+  = \,&
+  e^{2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r_i} +
+  e^{-2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r_j} \\
+  \label{eqn:ik.cal.tmp1}
+  &-2(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  ) 
+  -2(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  ) + 4
+\end{align}
+The first two term on the r.h.s. of Eqn.~\eqref{eqn:ik.cal.tmp1}
+are not high-wave-number terms only when $l_1 = l_2$ and $\alpha=\beta$.
+The third and fourth terms are definitly high-wave-number terms.
+Therefore, we have the error estimate
+for the RMS homogeneity error:
+\begin{align}\nonumber
+  [\mathcal E^{\textrm{ik}}_{\textrm{homo}}(\v r_i)]^2
+  = \,&
+  \int
+  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r')\vert^2
+  \rho_{q^2}(\v r')\,\d d\v r' \\
+  \approx\,&  
+  2q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\big] (\v r_i)
+  +
+  4q_i^2\,
+  \big[
+  \vert
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \vert^2
+  \ast \rho_{q^2}\,
+  \big] (\v r_i) 
+\end{align}
+
+It is also possible to calculate the first neighbor approximation for the
+ik-differentiation. Firstly, we have:
+\begin{align}\nonumber
+  \big\langle
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j+\v s)
+  \big\rangle
+  = \,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  Z_{\alpha,l}(\v m)
+  \v g(\v m) \\ \nonumber
+  \,&
+  \times
+  \big\langle
+  (
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r_j + \v s)}
+  - 2
+  )\,
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j -\v s)}
+  \big\rangle \\
+  \approx\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  (
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} 
+  - 2
+  )\,
+  Z_{\alpha,l}(\v m)
+  \v g(\v m)
+  \hat T_s(\v m)
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}  
+\end{align}
+So
+\begin{align}\nonumber
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r_j)\cdot
+  \big\langle
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j+\v s)
+  \big\rangle
+  =\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{
+    \begin{subarray}{c}
+      \vert n_{\alpha}\vert < K_\alpha/2\\
+      \v n\neq 0
+    \end{subarray}}
+  \sum_{\alpha,\beta}
+  \sum_{l_1,l_2}
+  \v g(\v m)\cdot\v g(\v n)\,
+  Z_{\alpha,l_1}(\v m)Z_{\beta,l_2}(\v n)\hat T_s(\v n)
+  \\\nonumber
+  &\,
+  \times
+  \,(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  \,(
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i}
+  - 2
+  )\\
+  &\,
+  \times
+  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
+\end{align}
+The first term in Eqn.~\eqref{eqn:c-error-1} yields
+% \begin{align}
+%   q_i^2 q_{\textrm{H}}
+%   \int
+%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r)\cdot
+%   \big\langle
+%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r+\v s)
+%   \big\rangle\,\rho_{\textrm{O}}(\v r)\,
+%   \d d\v r
+% \end{align}
+\begin{align}\nonumber
+  \mathcal E_{\textrm{correlation}}(\v r_i)
+  =\,&
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \v G_{\alpha,l}\cdot[\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}
+  \,\big] (\v r_i) \\\nonumber
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}\,
+  \big] (\v r_i) \\\nonumber
+  \,&+
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \v G_{\alpha,l}\cdot[\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}
+  \,\big] (\v r_i) \\
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}\,
+  \big] (\v r_i) 
+\end{align}
+
+\subsection{analytical differentiation}
+Starting from Eqn.~\eqref{eqn:ana.error.force}, we have the error force kernel
+of the analytical differentiation (notice the self-interacting term is removed):
+\begin{align}
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j)
+  =
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \{
+  [A(\v m, \v r_i) + A(\v m,-\v r_j)\,]
+  \v g(\v m) -
+  2\v B(\v m,\v r_i) f(\v m)
+  \}
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+\end{align}
+By inserting Eqn.~\eqref{eqn:error-A} and \eqref{eqn:error-B}, we have
+\begin{align}\nonumber
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j)
+  =\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \big[
+  \,(
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  \v g(\v m)
+  \\  \label{eqn:ik.kernel.2}
+  \,&
+  - 4\pi i l K_\alpha\v a_\alpha^\ast e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  f(\v m)
+  \big]
+  Z_{\alpha,l}(\v m)
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}  
+\end{align}
+Following  the same idea as the error estimate of  ik-differentiation,
+\begin{align}
+  \langle\Delta\v F^{\textrm{ana}}_{\textrm{rec}}(\v r_i)\rangle
+  \approx\,&
+  -2q_i
+  \big[
+  \big(
+  \sum_{\alpha}\sum_{l\neq 0}\v G_{\alpha,l}
+  \big)
+  \ast\rho_q\,
+  \big] (\v r_i).
+\end{align}
+To calculate the RMS error, we start from
+\begin{align}
+  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i,\v r_j)\vert^2
+  =\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{
+    \begin{subarray}{c}
+      \vert n_{\alpha}\vert < K_\alpha/2\\
+      \v n\neq 0
+    \end{subarray}}
+  \sum_{\alpha,\beta}
+  \sum_{l_1,l_2}
+  \\\nonumber
+  &\,
+  \big[
+  \,(
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  - 2
+  )
+  \v g(\v m)
+  - 4\pi i l_1 K_\alpha\v a_\alpha^\ast e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  f(\v m)
+  \big] \\\nonumber
+  \,&
+  \times
+  \big[
+  \,(
+  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+  - 2
+  )
+  \v g(\v n)
+  - 4\pi i l_2 K_\beta\v a_\beta^\ast e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i}
+  f(\v n)
+  \big]
+  \\
+  &\,
+  \times
+  Z_{\alpha,l_1}(\v m)Z_{\beta,l_2}(\v n)
+  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
+\end{align}
+Similar to the calculation of \eqref{eqn:ik.cal.tmp1}, one can eventually
+prove the error estimate for the homogeneity RMS error:
+\begin{align}\nonumber
+  [\mathcal E^{\textrm{ana}}_{\textrm{homo}}(\v r_i)]^2
+  = \,&
+  \int
+  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i,\v r')\vert^2
+  \rho_{q^2}(\v r')\,\d d\v r' \\\nonumber
+  \approx\,&  
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\big] (\v r_i) +
+  q_i^2
+  \big[\,
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}
+  \vert \v G_{\alpha,l} +\v F_{\alpha,l}\vert^2
+  \big)
+  \ast \rho_{q^2}
+  \,\big] (\v r_i) \\
+  \,&+
+  4q_i^2\,
+  \big[
+  \vert
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \vert^2
+  \ast \rho_{q^2}\,
+  \big] (\v r_i) 
+\end{align}
+
+To calculate the first neighbor approximation to the correlation error, 
+\begin{align}\nonumber
+  \big\langle
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j + \v s)
+  \big\rangle
+  =\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \bigg\langle
+  \big[
+  \,(
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r_j + \v s)}
+  - 2
+  )
+  \v g(\v m)
+  \\\nonumber
+  \,&
+  - 4\pi i l K_\alpha\v a_\alpha^\ast e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  f(\v m)
+  \big]
+  Z_{\alpha,l}(\v m)
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j - \v s)}
+  \bigg\rangle \\\nonumber
+  \approx\,&
+  \sum_{
+    \begin{subarray}{c}
+      \vert m_{\alpha}\vert < K_\alpha/2\\
+      \v m\neq 0
+    \end{subarray}}
+  \sum_{\alpha=1}^3\sum_{l\neq 0}
+  \big[
+  \,(
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} 
+  - 2
+  )
+  \v g(\v m)
+  \\
+  \,&
+  - 4\pi i l K_\alpha\v a_\alpha^\ast e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  f(\v m)
+  \big] T_s(\v m)
+  Z_{\alpha,l}(\v m)
+  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}.
+\end{align}
+Inserting
+$\big\langle
+\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j + \v s)
+\big\rangle$
+into \eqref{eqn:c-error-1}, we have the first neighbor approximation to the
+correlation error:
+\begin{align}\nonumber
+  \mathcal E_{\textrm{correlation}}(\v r_i)
+  =\,&
+  q_i^2
+  \big[\,
+  \big\{
+  \sum_{\alpha} \sum_{l\neq 0}
+  (\v G_{\alpha,l}+\v F_{\alpha,l})\cdot
+  [\hat T_{\textrm{O}} (\hat{\v G}_{\alpha,l}+\hat{\v F}_{\alpha,l})]^{\vee}
+  \big\}
+  \ast \rho_{\textrm{O}}
+  \,\big] (\v r_i) \\\nonumber
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}\,
+  \big] (\v r_i) \\\nonumber
+  \,&+
+  q_i^2
+  \big[\,
+  \big\{
+  \sum_{\alpha} \sum_{l\neq 0}
+  (\v G_{\alpha,l}+\v F_{\alpha,l})\cdot
+  [\hat T_{\textrm{H}} (\hat{\v G}_{\alpha,l}+\hat{\v F}_{\alpha,l})]^{\vee}
+  \big\}
+  \ast \rho_{\textrm{H}}
+  \,\big] (\v r_i) \\
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}\,
+  \big] (\v r_i) 
+\end{align}
 

### 2012-03-23 longRange.hetero/publish/main.tex
nearly finished, ask for advice

@@
 
-The calculation of long-range electrostatic interaction is a very
+The calculation of the long-range electrostatic interaction is a very
 important topic in the molecular simulations.  Due to the very slow
 decay of the interaction with respect to the distance between charges,
-the cut-off and neighbor list algoritm does not work, and moreover the
+the short-range fast algorithms (the cell list and neighbor list
+algorithms) do not work, and the
 energy of the system is only conditionally convergent.  One of the
-first algoritms handling this problem is the Ewald summation that
-dates back to 1920's~\cite{ewald1921die}.  However, it is shown that
+first algorithms handling this problem was the Ewald summation, dating
+back to the 1920's~\cite{ewald1921die}.  However, it has been shown that
 with a careful tuning of working parameters, the optimal computational
 cost of the Ewald summation is of $\mathcal
-O(N^{3/2})$~\cite{perram1988asc}, which is not feasible for morden
-large scale molecular simulations. The particle mesh Ewald (PME)
+O(N^{3/2})$~\cite{perram1988asc}, which is not feasible for modern
+large scale molecular simulations.
+Therefore, several Ewald based fast algorithms were proposed to reduce the
+computational cost to a scalable level: $\mathcal O(N\log N)$. Some of them
+are
+the particle mesh Ewald (PME)
 method~\cite{darden1993pme}, the smooth particle mesh Ewald (SPME)
 method~\cite{essmann1995spm} and the particle-particle-particle-mesh
-(P3M) method~\cite{hockney1988computer, deserno1998mue1} are the most
-popular Ewald-based fast algorithms that reduces the computational
-cost to $\mathcal O(N\log N)$. More recently, the staggered mesh or
-``interlacing'' technique firtly developed in
-1970's~\cite{chen1974reduction,eastwood1976optimal} is applied to SPME
+(P3M) method~\cite{hockney1988computer, deserno1998mue1}.
+More recently, the staggered mesh or
+``interlacing'' technique~\cite{chen1974reduction,eastwood1976optimal}
+was applied to SPME
 (called staggered mesh Ewald)~\cite{cerutti2009staggered} and P3M
-(called interlaced P3M)~\cite{neelov2010interlaced}, and is showed to
+(called interlaced P3M)~\cite{neelov2010interlaced}, and was showed to
 improve the accuracy of these algorithms.
-
-The fast algoritms have achieved great success in the computer
-simulation of charged molecular systems over the past three decades.
+In this paper, we focus on the Ewald summation, the SPME and
+the staggered mesh Ewald methods. The Ewald summation is the starting
+point of all the mentioned fast algorithm. SPME
+is the one of the most popular long-range algorithms among
+the mainstream molecular simulation packages, for example,
+AMBER~\cite{case2005amber}, GROMACS~\cite{van2005gromacs,
+  hess2008gromacs} and NAMD~\cite{phillips2005scalable}.
+
+The aforementioned fast algorithms have achieved great success
+over the past three decades.
 However, the fact that the user should provide six working parameters
-for these methods may be problematic: it is diffcult to try out the
-most efficient parameter set, and an arbitary choice may lead to
-qualitively wrong simulation result. This problem can be solved by an
-in-depth study of the error introduced by these algrotims, namly the
-error estimate~\cite{petersen1995accuracy, deserno1998mue2,
+for these methods may be problematic: it is difficult to try out the
+most efficient parameter set in such a high dimensional parameter space.
+The experiential choices may be either less accurate or waste
+computational effort.
+This problem can be solved by an
+in-depth study of the error introduced by these algorithms, namely the
+error estimate~\cite{kolafa1992cutoff, hummer1995numerical,
+  petersen1995accuracy, deserno1998mue2,
   wang2010optimizing, neelov2010interlaced, ballenegger2012convert},
 by which the error is described by a function of the working
-parameter.  By these error estimates, a work flow was designed to
+parameters.  Using the error estimates, a work flow has been designed to
 automatically determine the nearly optimal combination of parameters,
-in the sense that it is fastest one given a demanding
+in the sense that it is the fastest one given a demanding
 accuracy~\cite{wang2010optimizing}. However, so far, all error
@@
 independency of any pair of charges (i.e. the charges are
-uncorrelated), but neither of them is satisfactorily fulfilled in most
-realistic systems of practical interest.  For example, the lipid biomembrane
+uncorrelated), but neither of the assumptions is satisfactorily
+fulfilled in most molecular
+systems of practical interest.  For example, the lipid biomembrane
 solving in water: the carbon chains of the lipids carry no charge, and
-the charges are correlated by covalent bonds, van der Waals
-interaction, hydrogen bonding network, etc..  Therefore, the current
+the charges are correlated by the covalent bonds, the van der Waals
+interaction, the hydrogen bonding network, etc..  Therefore, the current
 error estimates may be problematic, or even not applicable.  A lot of
@@
 
-The purpose of this research is to develop an realiable force error
-estimate in inhomogeneous and strongly correlated molecular systems.
+The purpose of this research is to develop a reliable  error
+estimate in inhomogeneous and correlated molecular systems.
 We estimate the force error because the application is the molecular
-dynamics (MD) simulation.  Firstly, a most general error estimate
-frame work for the pairwise interactions is set up. We prove that the
+dynamics (MD) simulation.  Firstly, a general error estimate
+frame work for the pairwise interaction is set up. We prove that the
 error is decomposed into three additive parts: the homogeneity error,
-the inhomogeneity error and the correlation error~\cite{wang2012}. The
-homogeneity and inhomogeneity error can be calculated at a cost of
-$\mathcal O(N\log N)$ given the convolutional form of the error
-estimates.  Then a way is proposed to calculate the approximation of
-correlation error at cost of $\mathcal O(N\log N)$. Though it is
-possible to improve the accuracy of the approximation systematically,
-numerical results show that it is good enough
-to consider the correlation stems from
-the neighboring atoms within the same molecule
-in an inhomogeneous water system.  Following this framework, we
-develop the error estimate for the Ewald summation, the SPME method
-and the staggered method Ewald method. We study the SPME method
-because it is the one of the most popular long-range algorithms among
-the mainstream MD simulation packages, for example,
-AMBER~\cite{case2005amber}, GROMACS~\cite{van2005gromacs,
-  hess2008gromacs} and NAMD~\cite{phillips2005scalable}.  The estimate
-of the homogeneity and inhomogeneous errors is tested by by two
-randomly distributed inhomogeneous charges systems, and is proved to
-be very sharp in these ideal systems.  By studying a real
-inhomogeneous water system, the nearest neigbor approximation of
-correlation error is proved to improve the quality of error estimate
-greatly. This paper is ended by conclusions and remarks in
+the inhomogeneity error and the correlation error~\cite{wang2012}.
+These error estimates are only of theoretical interest, and
+not applicable, because the computational costs of the error estimates
+are $\mathcal O(N^2\log N)$ (homogeneity and inhomogeneity error)
+and $\mathcal O(N^3\log N)$ (correlation error).
+If the error force has a special form so that the error estimates
+can be written as convolutions, the computational costs
+are reduced to $\mathcal O(N\log N)$ and 
+$\mathcal O(N^2\log N)$, respectively.
+The computational cost of the correlation error is further
+reduce to $\mathcal O(N\log N)$ by the nearest neighbor approximation
+technique, which assume the system is only short-range correlated. This
+is the case for most the liquid and gas system far from critical point.
+Following this framework, we
+develop the error estimates for the Ewald summation, the SPME method
+and the staggered method Ewald method.   The estimates
+of the homogeneity and inhomogeneous errors are tested by two
+randomly distributed inhomogeneous charges systems
+(i.e. the charges are not correlated), and is proved to
+be very sharp.
+The error estimates are also tested in a real inhomogeneous water system,
+in which the charge correlation plays a very important role
+on the force error. By 
+including the nearest neighbor approximation of
+correlation error, the quality of the estimates
+is impressively enhanced.
+This paper is ended by conclusions and remarks in
 section~\ref{sec:conclusions}.
+
+% The
+% homogeneity and inhomogeneity error can be calculated at a cost of
+% $\mathcal O(N\log N)$ given the convolutional form of the error
+% estimates.  Then a way is proposed to calculate the approximation of
+% correlation error at cost of $\mathcal O(N\log N)$. Though it is
+% possible to improve the accuracy of the approximation systematically,
+% numerical results show that it is good enough
+% to consider the correlation stems from
+% the neighboring atoms within the same molecule
+% in an inhomogeneous water system.
+
+% Following this framework, we
+% develop the error estimate for the Ewald summation, the SPME method
+% and the staggered method Ewald method.   The estimate
+% of the homogeneity and inhomogeneous errors is tested by by two
+% randomly distributed inhomogeneous charges systems, and is proved to
+% be very sharp in these ideal systems.  By studying a real
+% inhomogeneous water system, the nearest neigbor approximation of
+% correlation error is proved to improve the quality of error estimate
+% greatly. This paper is ended by conclusions and remarks in
+% section~\ref{sec:conclusions}.
 
@@
 
-In this paper, we consider the force error, bacause the applicaions
-are based on the molecular dynamics simulation.  Suppose the system is
+In this paper, we consider the system with periodic boundary condition.
+Suppose it is
 composed by $N$ charged particles located at $\v r_1, \v r_2, \cdots,
@@
 % $\Delta \v F(\v r_i) = \v F(\v r_i) - \tilde{\v F}(\v r_i)$.
-The maganitude of the force computation error 
+The magnitude of the force computation error 
 % error of the force computation
@@
 estimate the the ensemble average of the error force (also called
-\emph{mean error force}), namly $\langle\Delta\v F(\v r_i)\rangle$,
+\emph{mean error force}), namely $\langle\Delta\v F(\v r_i)\rangle$,
 which plays an important role in the error analysis of the
-short-range inhomogeneous systems~\cite{wang2012}.
+inhomogeneous systems~\cite{wang2012}.
 
@@
   % n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, $n_\alpha\in\mathbb Z$.
-  If the error force of an arbitary particle $i$ is
+  If the error force of an arbitrary particle $i$ is
   \begin{align}\label{eqn:thm-error-force}
@@
   \begin{align}\nonumber
-    \mathcal E (\v r_i) 
+    \mathcal E^2 (\v r_i) 
     = &\,
@@
     C_{q^2}(\v r', \v r'')\,
-    \d d\v r'\d d\v r''.
-  \end{align}
-  Where $\ast$ denotes the convolution, and
+    \d d\v r'\d d\v r'',
+  \end{align}
+  where
   % The $\rho_q$, $\rho_{q^2}$ and
@@
   \end{align}
-  then the error estimates are in the convolution form, namely:
+  then the error estimates are convolutions, namely:
   \begin{align}\label{eqn:cor-meanf}
@@
     C_{q^2}(\v r', \v r'')\,
-    \d d\v r'\d d\v r''.
-  \end{align}
-  Where $\ast$ denotes the convolution.
+    \d d\v r'\d d\v r'',
+  \end{align}
+  where ``$\ast$'' denotes the convolution.
 \end{corollary}
@@
   Most of the error estimates assumed the independency of the
-  particles in the system~\cite{kolafa1992cutoff, deserno1998mue2, wang2010optimizing, wang2012},
+  particles in the system~\cite{kolafa1992cutoff, hummer1995numerical, deserno1998mue2, petersen1995accuracy, wang2010optimizing, neelov2010interlaced, ballenegger2012convert, wang2012},
   however, this could be problematic in the strongly correlated
@@
   at a cost of $\mathcal O(N^3\log N)$.
-  By writting the error estimates in the covolution form in
+  By writing the error estimates in the convolution form in
   the corollary~\ref{thm:tmp2},
@@
 
-\subsection{Nearest neighbor approximation of the correlation
+\subsection{Nearest-neighbor approximation of the correlation
 error}
-
-In this section, we consider the nearest neighbor approximation of the
-correlation error. Here the definition of the ``nearest neighbor'' is
-very flexible, basically it means the neigbors of a charge that are
-not very far away. It could be defined by the charges falling in some
-certain neighboring range or charge connected by a chemical bonds.
+The full computation of the correlation error cost at least $\mathcal
+O(N^2\log N)$, which is still not applicable.
+So we consider the nearest-neighbor approximation to reduce
+the computational cost.
+Here the definition of the ``nearest neighbors'' is
+very flexible, basically it means the nearby neighbors that are
+strongly correlated. It could also be defined by the charges falling in some
+certain neighboring range or charges connected by a chemical bonds.
 % Here ``first neighbors'' means the neighboring
@@
 % error estimate.
-Starts from Eqn.~\eqref{eqn:prf-error-step3},
+Starting from Eqn.~\eqref{eqn:prf-error-step3},
 \begin{align} \nonumber
@@
 % \end{align}
-We seperately consider the  contribution from nearest neigbors
+We separately consider the  contribution from the nearest neighbors
 and other contributions to
@@
 approximately $\frac{N-\#(\Omega_j)}{N}\rho_q(\v r')\rho_q(\v r'')\approx
-\rho_q(\v r')\rho_q(\v r'')$, where $\#(\Omega_j)$ is the number of nearest neighbors considered. This approximation is valid only when the number
-of neigbors considered is small comparing with the number of charges
+\rho_q(\v r')\rho_q(\v r'')$,
+where $\#(\Omega_j)$ is the number of nearest neighbors considered.
+The approximation is valid only when the number
+of neighbors in $\Omega_j$ is small comparing with the number of charges
 in the system.
@@
 on the r.h.s. of Eqn.~\eqref{eqn:split-rho-q2} is actually the
-pairwise charge corrlation function:
+pairwise charge correlation function:
 \begin{align}\label{eqn:fnc-correlation-water}
@@
 correlation is only short-ranged, so it is possible to systematically
-impove the accuracy by considering more and more neigbors as long as
-the number of neigbors is small comparing with the size of the system.
+improve the accuracy by considering more and more neighbors as long as
+the number of neighbors is small comparing with the size of the system.
 
@@
 at position $\v r'$. As an approximation, we
-assume these averages are  spacially uniform, namely independet with $\v r'$.
-This assumption may be  problematic
-in the regions where the preference of water  drection is different
+assume these averages are  spatially uniform, namely independent with $\v r'$.
+It may be  problematic
+in the regions where the preference of water  direction is different
 with others.
-
-To calculate the nearest neighbor approximated correlation error,
-we assume the error force kernel
-has the form $\v K(\v r_i , \v r_j) = \v K(\v r_i - \v r_j)$, so
-the integrals can be written in the covolution form and accelerated by the FFT.
+If the error force kernel
+has the form $\v K(\v r_i , \v r_j) = \v K(\v r_i - \v r_j)$, 
+the integrals can be written in the convolution form and accelerated by the FFT.
 % In the example considered by the present paper in section~\ref{sec:tmp3},
@@
 Eqn.~\eqref{eqn:c-error-1} is by the Fourier transform
-of the error force kernel:
+of the error force kernel, for example
 \begin{align} \nonumber
@@
   q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}}}
-  \rangle.
-\end{align}
-The Eqn.~\eqref{eqn:c-error-1} becomes:
+  \rangle,
+\end{align}
+the Eqn.~\eqref{eqn:c-error-1} becomes:
 \begin{align}\nonumber
@@
 method~\cite{frenkel02b} at a cost of $\mathcal O(N)$.  The reciprocal
-part also decays exponentially as the maganitude of the Fourier mode
-$\vert\v m\vert$ increases. Therefore, in practice, the infinit
+part also decays exponentially as the magnitude of the Fourier mode
+$\vert\v m\vert$ increases. Therefore, in practice, the infinite
 summation in Eqn.~\eqref{eqn:tmp3} is truncated, and only a finite
@@
 
-The naive calculation of the reciprocal Ewald summation
-\eqref{eqn:tmp6} will result in a computational cost of $\mathcal
-O(N^2)$. It has been shown that with a careful tuning of parameter
-$\beta$, real space cut-off radius $r_c$
-and the reciprocal space truncation $K_\alpha$, the
-optimal computational cost is $\mathcal O(N^{3/2})$~\cite{perram1988asc},
+% The naive calculation of the reciprocal Ewald summation
+% \eqref{eqn:tmp6} will result in a computational cost of $\mathcal
+% O(N^2)$. It has been shown that with a careful tuning of parameter
+% $\beta$, real space cut-off radius $r_c$
+% and the reciprocal space truncation $K_\alpha$,
+
+As mentioned before, the 
+optimal computational cost of the Ewald summation
+is $\mathcal O(N^{3/2})$,
 which becomes not applicable when the system
-size is larger than several hundreds of charged particles. Both the
-particle mesh Ewald (PME) \cite{darden1993pme} and the smooth particle
-mesh Ewald (SPME) \cite{essmann1995spm} methods are designed to reduce
-the computational cost to $\mathcal O(N\log N)$ in nearly the same
-way.  Since the SPME method is more precise \cite{deserno1998mue1} and
-more popular than the PME, we will focus our discussion on the
-former. All the error estimates develop by the current paper can be
-easily extended to the PME method.  The principle idea of the SPME method
-is first to calculate the term $e^{2\pi i\v m\cdot\v r}$ on a uniform
-lattice in the real space.  Therefore, all Fourier transforms can be
-accerlerated by the fast Fourier transform (FFT) algoritm, that is why the
-computational cost of SPME is reduced to $\mathcal O(N\log N)$. Then,
+size is larger than several hundreds of charged particles.
+Both the PME ans SPME methods
+are designed to reduce
+the computational cost  in nearly the same
+way.
+% Since the SPME method is more precise \cite{deserno1998mue1} and
+% more popular than the PME, we will focus our discussion on the
+% former. All the error estimates develop by the current paper can be
+% easily extended to the PME method.
+Starting from the reciprocal part of the Ewald summation,
+they firstly  calculate the term $e^{2\pi i\v m\cdot\v r}$ on a uniform
+mesh in the real space.  Therefore, all calculation of structure factors
+can be
+accelerated by the fast Fourier transform (FFT), that is why the
+computational cost of PME/SPME is reduced to $\mathcal O(N\log N)$. Then,
 for any particle position $\v r_i$, the value of $e^{2\pi i\v m\cdot\v
-  r_i}$ is interpolated by the known values on the neighboring lattice
+  r_i}$ is interpolated by the known values on the neighboring mesh
 points.  The PME method uses Lagrangian interpolation, while the SPME
@@
 of smoothness.
+The working parameters of these methods are
+the splitting parameter $\beta$,
+the cut-off radius in real space $r_c$,
+the order of interpolation $n$ and
+the number of mesh points on each direction:  $K_\alpha,\ \alpha = 1,2,3$.
+Notice $K_\alpha/2$ is the truncation
+of the reciprocal summation.
 
@@
 energy and then approximate the derived force \eqref{eqn:tmp8} by the
-B-spline interplation. This way is called
-\emph{ik--differentiation}~\cite{deserno1998mue1}.
+B-spline interpolation. This way is called
+\emph{ik-differentiation}.
 The alternative way notices the high-order
@@
 \cite{essmann1995spm}, and is called the \emph{analytical
-  differentiation}~\cite{deserno1998mue1}.
+  differentiation}.
 It has been shown that using the same parameters,
 the ik-differentiation is more precise than the analytical
-differentiation, but it requres twice more FFTs, which is a bottleneck
+differentiation, but it uses twice more FFTs, which is a bottleneck
 for the communication in parallel
@@
 
-The staggered mesh approach or originally call ``interlacing'' was first
-developed by Hockney and Eastwood~\cite{hockney1988computer}, and was
-recently applied to SPME (staggered mesh Ewald~\cite{cerutti2009staggered})
-and P3M (interlaced P3M~\cite{neelov2010interlaced}).
+The staggered mesh approach or originally call ``interlacing'' was
+recently applied to SPME (staggered mesh Ewald~\cite{cerutti2009staggered}).
 It calculates the
 reciprocal force on two meshes,
-one of which locates at the lattice volume center
+one of which locates at the mesh element center
 of the other, and then the two reciprocal forces are averaged.
@@
 cancels error in the force computation, and greatly improves the
-accuracy~\cite{cerutti2009staggered, neelov2010interlaced}.
+accuracy.
 Implementing the staggered mesh method for SPME is
@@
 $e^{2\pi i\v m\cdot\v r}$ by B-spline
-interpolation. Ref. \cite{wang2010optimizing} has pointed out that the
+interpolation. It has been shown that the
 error due to the first step is negligible comparing with the second
-step, at least for the parameters of practical interest. Numerical
+step,
+at least for the parameters of practical interest~\cite{wang2010optimizing}.
+Numerical
 examples supporting this argument in inhomogeneous systems are also
@@
 
-As mentioned above, the SPME error mainly oringinates from approximating
+As mentioned above, the SPME error mainly originates from approximating
 the term $e^{2\pi i\v m\cdot\v r}$ by the B-spline
@@
 $A(\v m, \v r)\,e^{2\pi i\v m\cdot \v r}$, we are fortunate to have
-the analytical expression of $A(\v m, \v r)$:
+the analytical expression of $A(\v m, \v r)$~\cite{schoenberg1987cardinal}:
 \begin{align}\label{eqn:error-A}
@@
 \end{align}
-The error force of the ik-differentiation is therfore
+The error force of the ik-differentiation is therefore
 \begin{align}\nonumber
@@
 Here we only want to present the key idea and the final  error
-estimates, and leave all details of calculating the error estimates
+estimates, and leave all details of the derivation 
 to the Appendix~\ref{sec:appendix}.  We notice the
@@
 then due to the thermal fluctuation of the system, the peaks and
-valleys of the high-wave-number terms may canncels in the the
-emsemble-averaged error estimate.
+valleys of the high-wave-number terms may cancels in the the
+ensemble-averaged error estimate.
 % Based on this observation, it is
@@
 $G_{\alpha,l}(\v r)$ does not depends on the coordinates of particles,
-so it can be calculated once and stored in a table for further uses.
+so it can be calculated once and stored in a table for future uses.
 The nearest neighbor approximation to the correlation error is:
@@
 
-\subsection{Error estimate of the analytical differetiation}
+\subsection{Error estimate of the analytical differentiation}
 \label{sec:error-ana}
 
-The error force of the analytical differetiation is 
+The error force of the analytical differentiation is 
 \begin{align}\nonumber
   \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)
-  =\;&
-  q_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  -2f(\v m)\,
-  \nabla_{\v r_i}
-  e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,
-  A(\v m, -\v r_j)
-  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
-  & +\,
-  q_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  -2f(\v m)\,
-  \nabla_{\v r_i}
-  [A(\v m, \v r_i)\,
-  e^{2\pi i\v m\cdot \v r_i} ]
-  \sum_{j\neq i}q_j\,
-  e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
-  & +\,
-  q^2_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\\nonumber
-      \v m\neq 0
-    \end{subarray}}
-  -2f(\v m)\,
-  A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\\nonumber
-  & +\,
-  q^2_i
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  -2f(\v m)\,
-  e^{-2\pi i\v m\cdot \v r_i}
-  \nabla_{\v r_i} [\,A(\v m, \v r_i) \,e^{2\pi i\v m\cdot\v r_i}\,]  \\\nonumber
+  % =\;&
+  % q_i
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_{\alpha}\vert < K_\alpha/2\\
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % -2f(\v m)\,
+  % \nabla_{\v r_i}
+  % e^{2\pi i\v m\cdot \v r_i}
+  % \sum_{j\neq i}q_j\,
+  % A(\v m, -\v r_j)
+  % e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  % & +\,
+  % q_i
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_{\alpha}\vert < K_\alpha/2\\
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % -2f(\v m)\,
+  % \nabla_{\v r_i}
+  % [A(\v m, \v r_i)\,
+  % e^{2\pi i\v m\cdot \v r_i} ]
+  % \sum_{j\neq i}q_j\,
+  % e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  % & +\,
+  % q^2_i
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_{\alpha}\vert < K_\alpha/2\\\nonumber
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % -2f(\v m)\,
+  % A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\\nonumber
+  % & +\,
+  % q^2_i
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_{\alpha}\vert < K_\alpha/2\\
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % -2f(\v m)\,
+  % e^{-2\pi i\v m\cdot \v r_i}
+  % \nabla_{\v r_i} [\,A(\v m, \v r_i) \,e^{2\pi i\v m\cdot\v r_i}\,]  \\\nonumber
   =&\,
@@
   neelov2010interlaced}, which does not depends on the coordinates of
-particles. Therefore, it can be calculated explicitly, and substracted
+particles. Therefore, it can be calculated explicitly, and subtracted
 from the analytical force during the simulation. The computational cost of
-the self-interaction term costs is very low comparing with the SPME
+the self-interaction term is very low comparing with the SPME
 force calculation. It is shown that the self-interaction  error
 dominate in the low charge density regions~\cite{cerutti2009staggered}.
-Therefore, we always remove the self-interaction term for
-the analytical differetiation, and call it as the original analytical
-differetiation when comparing it with the staggered mesh analytical
-differetiation.
+Therefore, we always remove the self-interaction term from
+the analytical differentiation.
+% , and call it as the original analytical
+% differetiation when comparing it with the staggered mesh analytical
+% differetiation.
 
 Neglecting all high frequency terms, we have the mean error force of
-analytical differetiation:
+analytical differentiation:
 \begin{align}\label{eqn:ana.meanf}
@@
 % so they can be tabulated in advance for the simulation.
+Similar to $\v G_{\alpha,l}(\v r)$,
 $\v F_{\alpha,l} (\v r)$ 
 does not depends on the coordinates of particles,
-so it can be tabulated in advance for the simulation.
+so it can be tabulated  for the simulation.
 The nearest neighbor approximation to the correlation error is
@@
   \ast \rho_{\textrm{H}}\,
-  \big] (\v r_i) 
+  \big] (\v r_i).
 \end{align}
@@
 
-The shift of the mesh can be effective treated as shifting all
-particles on the opposite direction. Since the system is periodic, the
-shift to which direction is not important. For convenience, we shift
-all particles to the positive direction for half the grid size, namely
+The shift of the mesh can be effectively treated as shifting all
+particles on the opposite direction. Since the system is periodic,
+the direction of shift is not important. For convenience, we shift
+all particles to the positive direction for half the mesh element size, namely
 by a vector $\v s = \sum_\alpha\frac1{2K_\alpha}\v a_\alpha$. From
@@
 the staggered ik-differentiation:
-\begin{align}
+\begin{align}\label{eqn:ik-st-error-force}
   \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r_i)
@@
 \end{align}
-The error force kernel has the form of Eqn.~\eqref{eqn:cor-kernel},
+Therefore, the error force kernel is
+\begin{align}
+  \v K^{\textrm{ik,st}}_{\textrm{rec}}(\v r)
+  = -2
+  \sum_\alpha\sum_{l\neq 0}\v G_{\alpha,l}(\v r),
+\end{align}
 then the corollary~\ref{thm:tmp2} is applicable.
-Moreover, since both the exact and the error
-force are anti-symmetric,  the Newton's third law is preserved by the
-calculated force.
-From Theorem~\ref{thm:tmp1}, we have the error estimates:
+% Moreover, since both the exact and the error
+% force are anti-symmetric,  the Newton's third law is preserved by the
+% calculated force.
+We have the error estimates:
 \begin{align}\label{eqn:ik.st.meanf}
@@
 % Also neglect the high wave number terms,
-and the RMS force error is 
+and the RMS force error:
 \begin{align}\label{eqn:ik.st.error}
@@
 \,\big] (\v r_i) \geq 0$.
-
-For the analytical differetiation, similarly we have: $\frac12\,[\v
+The nearest neighbor approximation to the correlation error is:
+\begin{align}\nonumber
+  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r_i)
+  =\,&
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{O}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{O}}\,
+  \big] (\v r_i) \\\nonumber
+  \,&+
+  4q_i^2\,
+  \big[
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  \v G_{\alpha,l}
+  \big)
+  \cdot
+  \big(
+  \sum_{\alpha} \sum_{l\neq 0}  
+  [\,\hat T_{\textrm{H}}\hat{\v G}_{\alpha,l}]^{\vee}
+  \big)
+  \ast \rho_{\textrm{H}}\,
+  \big] (\v r_i).
+\end{align}
+
+For the analytical differentiation, similarly we have: $\frac12\,[\v
 B(\v m,\v r) + \v B(\v m, \v r+\v s)] \approx 0$. Therefore, from
 Eqn.~\eqref{eqn:ana.error.force}, the error force of the staggered
-analytical differetiation is approximately the same as the staggered
+analytical differentiation is approximately the same as the staggered
 ik-differentiation, so are all the error estimates:
@@
   \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2
-  \big\rangle
-\end{align}
-The error from the self-interaction term is automatically fixed by the
-staggered mesh.
+  \big\rangle\\
+  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r_i)
+  &\approx
+  \mathcal E^{\textrm{ana,st}}_{\textrm{correlation}}(\v r_i)
+\end{align}
+The correction of the self-interacting error is not necessary,
+because it is automatically canceled by the staggered mesh.
+% The error from the self-interaction term is automatically fixed by the
+% staggered mesh.
 The RMS force error is improved because it is not
@@
 leading order of approximation, the staggered
-mesh ik-differentiation and staggered mesh analytical differetiation
+mesh ik- and analytical differentiation
 are equivalent. Considering the latter uses
-only one half of  FFTs as the former, it might be preferabel
+only one half of  FFTs as the former, it might be preferable
 in large scale parallel simulations.
-From Eqn.~\eqref{eqn:ana.error.force}
-and~\eqref{eqn:ana-st-error-force}, the Newton's
-third law is preserved by the staggered mesh analytical differetiation.
+From Eqn.~\eqref{eqn:ik-st-error-force}
+and~\eqref{eqn:ana-st-error-force}, it is obvious that the Newton's
+third law is better preserved by the staggered mesh methods.
 
@@
 In the previous subsections, we estimate the error of direct part and
-reciprocal part seperately. Here we provide the error estimate for the
+reciprocal part separately. Here we provide the error estimate for the
 total force. The mean of the total error force is simply:
@@
 denotes any method for the reciprocal Ewald summation, which
-could be truncated Ewald summation (``tr''), ik-/analytical differetiation
+could be truncated Ewald summation (``tr''), ik-/analytical differentiation
 (``ik''/''ana'') or staggered method
-ik-/analytical differetiation (``st,ik''/''st,ana'').
+ik-/analytical differentiation (``st,ik''/''st,ana'').
 The mean square total force is
@@
 
-We consider three inhomogeneous charge system to verify our error
-estimate.
-The first two are artifically designed to verify the formula of
-the error estimates. The third is a real simulation
-of liquid-vapor equilibriated water system, in order to test the
-quality  of error estimates in real inhomogeneous system.
+We consider three inhomogeneous charge systems to verify our error
+estimates.
+The first two are artificially designed to verify the 
+homogeneity and inhomogeneity error estimates. The third is a 
+liquid-vapor equilibrium water system, in order to test the
+quality  of error estimates in inhomogeneous and correlated system.
 
@@
 The position of these charges
-are randomly generated subject to the number density shown in
+are randomly generated subjecting to the number density shown in
 Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
 charge   is twice as large as that of the negative charge,
-which means  the
+so the
 positive and negative charges cancel, and the
@@
     by fast algorithms. ``$\blacksquare$'': real error of
-    the oringinal analytical
-    differentiation. ``$\boxdot$'': real error of the oringinal ik-differentiation.
+    the original analytical
+    differentiation. ``$\boxdot$'': real error of the original ik-differentiation.
     ``$\times$'': real error of the staggered mesh analytical differentiation.
     ``$+$'': real error of the staggered mesh ik-differentiation.
-    Dashed line: estimated oringinal analytical differentiation.
-    Dotted line: estimated oringinal ik-differentiation.
+    Dashed line: estimated original analytical differentiation.
+    Dotted line: estimated original ik-differentiation.
     Solid line: estimated staggered mesh ik-/analytical differentiation.
-    The RMS errors are averged over $y$ and $z$ directions, and are
+    The RMS errors are averaged over $y$ and $z$ directions, and are
     plotted against $x$ axis.
@@
 Fig.~\ref{fig:error1} presents the real RMS error (by points) and the
-corresponding error esimates (by lines) of the cut-offed Ewald direct
+corresponding error estimates (by lines) of the cut-offed Ewald direct
 part, the truncated Ewald reciprocal part, the original ik-/analytical
-differentiations and the staggered mesh ik-/analytical
-differentiations. All the error estimates are consistent very well
-with the real errors, that means the error estimates developed by the
-present paper are very sharp.  The parameters of are
+differentiation and the staggered mesh ik-/analytical
+differentiation. All the error estimates are consistent very well
+with the real errors.  The parameters are
 chosen to be the same for an easy comparison among these 
-SPME branches.  The errors of FFT
-based fast Ewald methods are 8 orders of maganitudes large than that of
+reciprocal space methods.  The errors of FFT
+based fast Ewald methods are 8 orders of magnitudes large than that of
 the truncated Ewald summation.
-This supports the argument raised in
-Sec.~\ref{sec:error-ik}: the error introduced by truncting the
+This supports the argument addressed in
+Sec.~\ref{sec:error-ik}: the error introduced by truncating the
 reciprocal Ewald summation is much smaller than that introduced by
 approximating $e^{2\pi i\v m\cdot\v r}$.
-The original ik-differentiation is much more accurate than
+The original ik-differentiation is more accurate than
 the original analytical differentiation.
@@
 the FFT is a bottleneck of communication on massive parallel
-super-computers, so the staggered mesh analytical differentiation
-might have advantages on these systems.
+super-computers,
+so the methods using less FFTs may have advantages on these machines.
 
@@
 
-\subsection{Example 2: seperated positive and negative charge}
+\subsection{Example 2: separated positive and negative charge}
 \label{sec:example2}
@@
 In this example, the setting is nearly the same as
-example 1: 41472 charges are put into a
-$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
-periodic simulation box. One third of them are carrying negative
-charge of $-0.834e$, and the other two thirds are carrying positive
-charge of $+0.417e$.  The only difference is that all positive charges
+example 1. The only difference is that all positive charges
 are moved to the region where the density of negative charge is low,
 see Fig.~\ref{fig:tmp-rho2}.
-In this system, the nagative charges are seperated from their
+In this system, the negative charges are separated from their
 counter ions, but the whole system is kept neutral. This case rarely
-happens in real simulation, but serves as a good test of the error
+happens in real simulation, but it serves as a good test of the error
 estimates in extreme situations.
@@
     overlap each other. 
-    The errors are averged over $y$ and $z$ directions, and are
+    The errors are averaged over $y$ and $z$ directions, and are
     plotted against $x$ axis.
@@
 Fig.~\ref{fig:meanf2} shows the real mean error forces (by points) and the
-corresponding error esimates (by lines) of cut-offed Ewald direct
-part, truncated Ewald reciprocal part, the original
-and the staggered mesh analytical differentiation. All
+corresponding error estimates (by lines) of cut-offed Ewald direct
+part, truncated Ewald reciprocal part, the ik-/analytical
+differentiation 
+and the staggered mesh ik-/analytical differentiation. All
 notations in the figure are the same as Example 1.  Although the
-charge distribution is not usual in this case, the error estimates are
+charge distribution is not usual in this case, the error estimates are still
 sharp. The two peaks of the direct mean  error force present at the
-positive-negative interface, due to the seperation of the positive
-and nagative charges, i.e., a non-vanishing and fast changing first order charge
-distribution $\rho_q$.  Similar phenomena were reported by
+positive-negative interface, due to the separation of the positive
+and negative charges, i.e., a non-vanishing and fast changing first order charge
+distribution $\rho_q$.  Similar phenomena was reported by
 Ref.~\cite{wang2012}. Surprisingly, 
@@
     they are not shown in this figure for clarity, 
-    The errors are averged over $y$ and $z$ directions, and are
+    The errors are averaged over $y$ and $z$ directions, and are
     plotted against $x$ axis.
@@
 
-Fig.~\ref{fig:error2} presents the real RMS error of example 2. The
-results of the original and staggered mesh ik-differentiation are not
-shown, because they are nearly indistinguishable from the staggered
-mesh analytical differentiation in this plot.
+Fig.~\ref{fig:error2} presents the real and estimated
+RMS error of example 2. The
+the original ik-differentiation is not
+shown, because it is nearly indistinguishable from the staggered
+mesh ik-/analytical differentiation in this plot.
 All the error estimates consist with the real errors.
-Steming from the inhomogeneity error,
+Stemming from the inhomogeneity error,
 two peaks of the direct error form at the interfacial
@@
 
-This example studies the gas-liquid phase equilibrum of a water
+This example studies the gas-liquid phase equilibrium of a water
 system. The size of the simulation box and number of charges are the
@@
 periodic simulation box.  The molecules dynamics simulations of this
-system is performed by Gromacs 4.5~\cite{hess2008gromacs}.  The system
+system was performed by GROMACS 4.5~\cite{hess2008gromacs}.  The system
 is coupled to a velocity rescale thermostat~\cite{bussi2007canonical}
 at temperature 300~\textsf{K}, and simulated long enough to reach the
-equilibrium. After the equibrium,
-the water molecules seperate into the liquid and vapor phases.
+equilibrium. After the equilibrium,
+the water molecules separate into the liquid and vapor phases.
 The number densities of oxygen and hydrogen atoms
@@
     ``$\times$'': the real error.
-    Dashed line: the RMS error estimate.
-    Solid  line: the RMS error estimate, with the nearest neighbor
-    approximation of correlation error.
-    The working parameters are the same as exaple 1.
-    The black arrows indecate the improvement
+    Dashed line: the error estimate, without the correlation error estimate.
+    Solid  line: the error estimate, with the nearest neighbor
+    approximation of the correlation error.
+    The working parameters are the same as example 1.
+    The black arrows indicate the improvement
     of error estimate by including nearest neighbor
@@
     ik-differentiation, it is overlapping with the analytical differentiation.
-    Blue dashed line: the error estimate of  the staggered mesh Ewald method.
-    Blue solid line: the error estimate including the nearest
+    Blue dashed line: the error estimate, without the correlation error.
+    Blue solid line: the error estimate, with the nearest
     neighbor approximation of the correlation error.
-    The RMS errors are averged over $y$ and $z$ directions, and are
+    The RMS errors are averaged over $y$ and $z$ directions, and are
     plotted against $x$ axis.
     The working parameters are the same as example 1.
-    The black arrow indecates the improvement
+    The black arrow indicates the improvement
     of error estimate by including nearest neighbor
@@
 are in Fig.~\ref{fig:water-error0}
-and Fig.~\ref{fig:water-error}.
-The staggered method ik- and analytical differentiation
-are also equivalent in this case, so they are mentioned by the ``staggered
-mesh Ewald''  for convenience.
-In this case, due to the correlation of the charge positions, the assumption
-of independent positions is disturbed, so all estimates deviate from
-the real errors.
+and Fig.~\ref{fig:water-error}, respectively.
+Unlike previous examples, the real error of ik- and analytical differentiation
+are nearly the same.
+The staggered mesh ik- and analytical differentiation
+are also equivalent in this case, and are $\sim$70\% more accurate
+than the original ik-/analytical differentiation.
+In this case,
+all estimates without considering the correlation error
+deviate from the real errors.
 The quality of the direct
@@
 The RMS errors of the ik-differentiation, analytical differentiation
-and the staggered mesh Ewald method are
+and the staggered mesh ik-/analytical differentiation are
 overestimated by 2.6, 4.7 and 6.8 times, respectively.
-Notice the only difference between this example and example 1 is the correlation
+Notice the only difference between this example
+and example 1 (in which the estimates were very sharp) is the correlation
 of the charges in the system,
-so it plays a very important role in the RMS error. 
+which plays a very important role in the RMS error. 
 More surprisingly, the correlation
 actually  reduces the error in the force computation.
-Currently we have no explaination for this phenomenon.
-Anyway, the correlation error $\mathcal
-E_{\textrm{correlation}}$ should be included to develop a more accurate error
-estimate. 
+Currently we have no explanation for this phenomena.
+% Anyway, the correlation error $\mathcal
+% E_{\textrm{correlation}}$ should be included to develop a more accurate error
+% estimate. 
 By including the nearest neighbor approximation of the
-correlation error, the quality of all error estimates is imporved greatly
-(as indicated by the arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}).
+correlation error, the quality of all error estimates is improved greatly,
+as indicated by the arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
 Now the RMS errors of ik-differentiation, analytical differentiation
-and staggered mesh Ewald method
+and staggered mesh ik-/analytical differentiation
 are overestimated by a factor of 1.16, 1.44 and 1.86,
@@
 In this paper, we proposed the error estimate for some state-of-art
-algoritms calculating the long-range electrostatic interaction
-in a molecular system. They were the Ewald summation, the smooth
-particle mesh Ewald (SPME, both ik- and analytical differentiation)
-and staggered mesh Ewald (both ik- and analytical differentiation).
-Unlike previous error estimates, the new error estimates did not
-assume the homogeneity and uncorrelation of the system,
-which is a too strong assumption for most real molecular simulations.
-The correlation of the charges is considered by the nearest
-neighbor approximation, which greatly
-improved the qulity of the error estimate in the water system.
+algorithms calculating the long-range electrostatic interaction in a
+molecular system. They were the Ewald summation, the smooth particle
+mesh Ewald (SPME, both ik- and analytical differentiation) and
+staggered mesh Ewald (both ik- and analytical differentiation).
+Unlike previous error estimates, the new error estimates did NOT
+assume the homogeneity and uncorrelation of the system, which is a too
+strong assumption for most molecular simulations of practical
+interest.  A general error estimate framework was firstly proposed, by
+which the RMS error was proved to be composed by three additive parts:
+the homogeneity error, the inhomogeneity error and the correlation
+error.  The homogeneity and inhomogeneity error estimates are
+computationally feasible 
+only when they can be written in a
+convolution form.  The correlation error that is a twofold
+convolution was approximated by the nearest neighbor approximation, in
+order to reduce the computational cost to $\mathcal O(N\log N)$.
+
+% The correlation of the charges is considered by the nearest
+% neighbor approximation, which greatly
+% improved the qulity of the error estimate in the water system.
 
@@
   force error in low density systems~\cite{cerutti2009staggered}.  The
-  expression helped removing the self-interaction at a very low
+  expression helped removing the self-interaction term at a very low
   computational cost.
@@
 
-The effectivenss of the proposed error estimates was verified by
+The effectiveness of the proposed error estimates was verified by
 three numerical tests: two ideal inhomogeneous cases, in which the charges
@@
 In the ideal cases, the all error estimates are sharp, even in the extreme
-case: positive and negative charges are globally seperated. 
+case: positive and negative charges are globally separated. 
 In the water system,  all estimates overestimate the real error,
 because of the correlation of charges.
-The qulitity of  error estimates for the
+The quality of  error estimates for the
 real space  is acceptable.
@@
 % is not applicable  for the staggered mesh Ewald method.
-The error estimates for the reciprocal space fast algoritms
+The error estimates for the reciprocal space fast algorithms
 are greatly improved by including the first neighbor approximation
@@
 This paper only focuses on the accuracy of the
-mentioned long-range alrgoritms.
-We do not touch the topic of comparing the efficiency of these algoritms.
-For a fair comparison, we propose controling a target accuracy,
-optimizing working parameters for each algorithm and then comparing
-the excution speed.
+mentioned long-range algorithms.
+We do not touch the topic of comparing the efficiency of these algorithms.
+To be fair,
+we propose 
+optimizing the working parameters for each algorithm with a
+predetermined accuracy before
+comparing
+the real execution speed.
 Such a comparison includes the topic of the hardware architecture,
 the communication bandwidth,
-the software implementation, the scale of the problem,
+the software implementation, the scalability of the problem,
 the density of the system, etc.. They are far beyond the scope of the current
@@
 the high wave number (higher than $K_\alpha / 2$) part of the density profile.
-If the density is smooth enough, this term can be resonably neglected.
+If the density is smooth enough, this term can be reasonably neglected.
 Therefore,
@@
 are not high-wave-number terms only when $l_1 = l_2$ and $\alpha=\beta$.
-The third and fourth terms are definitly high-wave-number terms.
+The third and fourth terms are definitely high-wave-number terms.
 Therefore, we have the error estimate

### 2012-04-19 longRange.hetero/profile.test/template/tools/profile/src/DensityFunction.cpp
fix bug

@@ -170,7 +170,7 @@ genConf_rand_water_gro (const char * filename,
     do{
       posi[3*i][0] = RandomGenerator_MT19937::genrand_real2() * Lx;
     } while (RandomGenerator_MT19937::genrand_real1() > 
-	     positive (posi[i][0]) / max);
+	     positive (posi[3*i][0]) / max);
     posi[3*i][1] = RandomGenerator_MT19937::genrand_real2() * Ly;
     posi[3*i][2] = RandomGenerator_MT19937::genrand_real2() * Lz;
     std::vector<double > shift(3, 0.);
@@ -280,7 +280,7 @@ genXtc_rand_water (const char * filename,
       do{
 	posi[3*i][0] = RandomGenerator_MT19937::genrand_real2() * Lx;
       } while (RandomGenerator_MT19937::genrand_real1() > 
-	       positive (posi[i][0]) / max);
+	       positive (posi[3*i][0]) / max);
       posi[3*i][1] = RandomGenerator_MT19937::genrand_real2() * Ly;
       posi[3*i][2] = RandomGenerator_MT19937::genrand_real2() * Lz;
       std::vector<double > shift(3, 0.);

### 2012-04-20 shortRange.inhomo/alltext/poster/poster.tex
add poster

\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\mode<presentation>
  {
  \usetheme{Berlin}
  %\usetheme{Dreuw}
  }
  \usepackage{times}
  \usepackage{amsmath,amsthm, amssymb, latexsym}
  \boldmath
  \usepackage{exscale}
  \usepackage[english]{babel}
  \usepackage[latin1]{inputenc}
  \usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}
  \usepackage{ragged2e} 
  \renewcommand\baselinestretch{1.08}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
  \graphicspath{{figures/}}
  \title{How to optimize the parameters of the\\Smooth Particle Mesh Ewald algorithm}
  \author{Han Wang \inst{1}, Florian Dommert \inst{2}, Christian Holm \inst{2}}
  \institute[]{ \footnotesize
    \inst{1} LMAM and School of Mathematical Sciences, Peking University, \textit{Beijing}, China  \\
    \inst{2} Institute for Computational Physics, Universit\"at Stuttgart, \textit{Stuttgart}, Germany
  }
  %\date{Jul. 31th, 2007}
%  \RequirePackage{tangocolors}
%  \setbeamercolor{headline}{fg=black,bg=tagray}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
  \begin{document}

  \newcommand{\redc}[1]{{\color{red} #1}}
  \newcommand{\bluec}[1]{{\color{blue} #1}}
  \renewcommand{\v}[1]{\textbf{\textit{#1}}}
  \renewcommand{\d}[1]{\textrm{#1}}

  \begin{frame}{} 
    \vfill
    \begin{beamercolorbox}[wd=\paperwidth]{headline}
      \begin{columns}[T]
        \begin{column}{.2\paperwidth}
          \begin{center}
            \hspace{4ex}\includegraphics[width=.5\linewidth]{logo/pku.png}
          \end{center}
        \end{column}
        \begin{column}{.6\paperwidth}
          \vskip1ex
          % \raggedleft
          \centering
          \usebeamercolor{title in headline}{\color{fg}\textbf{\LARGE{\inserttitle}}\\[1ex]}
          \usebeamercolor{author in headline}{\color{fg}\large{\insertauthor}\\[1ex]}
          \usebeamercolor{institute in headline}{\color{fg}\large{\insertinstitute}\\[1ex]}     
          \vskip4ex
        \end{column}
        \begin{column}{.2\paperwidth}
          \begin{center}
            \vspace*{-1em}
            \hspace{-2ex}\includegraphics[width=.4\linewidth]{logo/unilogo}\\
            \vspace*{0.5em}
            \hspace{-2ex}\includegraphics[width=.6\linewidth]{logo/Logo_ICP_T_V2}
            \vfill
          \end{center}
        \end{column}
      \end{columns}
    \end{beamercolorbox}

    \vfill
    \vspace{-1cm}
    \begin{columns}[t]
      \begin{column}{.32\linewidth}
        \vfill
        \begin{block}{\large Abstract}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          We derive an error estimate for the smooth Particle Mesh Ewald~(SPME)
          algorithm, which is often used for Molecular Dynamics simulations, and
          applied it to an ionic system to test its va\-lid\-i\-ty. Various
          combinations of parameters were tested for two different
          implementations of the SPME algorithm to proof the quality of the
          estimate, resulting in a parameter tuning algorithm for SPME.
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large Electrostatic energy}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          The electrostatic energy of a periodic ionic system is 
          \begin{equation*}\bluec{ E = \frac12
              \sum^\ast_{n}\sum_{i,j}\frac{q_i q_j}{\vert \v r_{ij} +
                \v n\vert},}
          \end{equation*} 
          and the essential difficulty to apply this formula follows from its 
          \redc{``long range''} nature.
          \vspace*{-1.2ex}
          \begin{figure}
            \centering 
            \includegraphics[width=0.75\textwidth]{figs/decay.pdf}
          \end{figure}
          \vspace*{-1.5ex}
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large Ewald summation}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          A good way to deal with the electrostatic in\-ter\-action in periodic
          systems was proposed by Ewald in 1921:
          \begin{align*}
            E &=  E_{\textrm{dir}} +E_{\textrm{rec}}+E_{\textrm{corr}}\\
            E_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
            \sum_{i,j = 1}^{N} \frac{q_iq_j\, \redc{\textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}}
            {\vert\v{r}_{ij} + \v{n}\vert} \\ \label{Erec-ewald}
            E_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
            \frac{\redc{\exp(-\pi^2\v m^2 / \beta^2)}}{\v m^2} S(\v m) S(-\v m) \\
            E_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
          \end {align*}
          Consider the \redc{``short range''} nature of the red terms in both real and
          reciprocal space, and the structure factor $S(\v m)$ given by:
          \begin{equation*}
            S(\v m) = \sum_{j=1}^N q_j \exp (2 \pi i \v m \cdot \v r_j).
          \end{equation*}
          Unfortunately, the computational cost is \redc{$\mathcal O(N^{3/2})$}
          at the best.          
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large $O(N \log N)$ algorithms}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          In the last two decades, some successful algorithms have
          been developed: 
          \begin{itemize}
          \item The \redc Particle--\redc Particle--\redc Particle--\redc Mesh method
          \item The \redc Particle \redc Mesh \redc Ewald method 
          \item The \redc Smooth \redc Particle \redc Mesh \redc Ewald method 
          \end{itemize}

          \bluec{\textbf{Key point:}} The term $ \exp (2 \pi i
          \v m \cdot \v r_j) $ is just calculated on a given number of grid
          points. To derive its value at any other position, an interpolation is 
          using the known values on the neighboring grid points. Therefore 
          Fast Fourier transforms (FFT) can be applied for the calculation of
          the reciprocal part and the computational cost is drastically
          decreased to \redc{$\mathcal O(N\log N)$}.
        \end{minipage}
        \end{block}
      \end{column}
      \begin{column}{.32\linewidth}
        \vfill
        \begin{block}{\large The parameters in SPME}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          \begin{itemize}
          \item \bluec{$\beta$} corresponds to the same parameter as in the Ewald summation.
          \item \bluec{$r_c$} is the cut off used in the neighbor list method
            for the direct part.
          \item \bluec{$n$}  defines the order of the cardinal B-splines.
          \item \bluec{$\v K$}  contains the number of grid points used to
            discrete the space in every dimension.
          \end{itemize}
          It is not a prior clear how to choose these parameters properly, but
          an arbitrary choice may lead to \redc{totally wrong results}.

          When using SPME method, there are two possible ways of
          calculating forces in the charged system, that differ in the
          computational effort and accuracy, considering the same set of
          parameters.
          \vspace*{-0.5ex}
          \begin{itemize}
            \item \bluec{ik differentiation}\vspace{0.4ex}
              \begin{minipage}{0.975\textwidth} 
                Multiplying the reciprocal energy with the vector \bluec{$ik$} in
                reciprocal space, and transforming the result back to real
                space corresponds to a derivative and yields the force. However
                \redc{4} FFTs are required, but momentum is \redc{conserved}.
              \end{minipage}\vspace*{0.2ex}
            \item \bluec{analytical differentiation}\vspace{0.4ex}
            \begin{minipage}{0.975\textwidth}
            The forces are derived from the the derivative of the approximated
            energy. Only \redc{2} FFTs are required, but momentum is \redc{not}
            conserved.
            \vspace*{-0.2ex}
        \end{minipage}
          \end{itemize}
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large Designing a parameter tuning algorithm}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          To tune the parameters, we need:
          \begin{itemize}\justifying
          \item \bluec{Error estimates} that ensure the algorithm to give
            correct results. 
          \item \bluec{CPU-time estimates} that yield the most time-saving
            parameters for a given allowed error.
          \end{itemize}
        \end{minipage}
        \end{block}
        \begin{block}{\large CPU-time estimate}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          \begin{itemize}
          \item Direct part \quad \redc{$T^{\textrm{dir}} \approx
              C_dr_c^3$}
          \item Reciprocal part 
            \begin{itemize}
            \item ik differentiation \newline
              \redc{$
                T^{\textrm{rec}}_{\textrm{ik}}
                \approx 2 C_s Nn^3 + 4\, C_f  K_1K_2K_3 \log (K_1K_2K_3) 
                $}
            \item analytical differentiation\newline
              \redc{$
                T^{\textrm{rec}}_{\textrm{ana}}
                \approx 3C_s Nn^3 + 2\, C_f  K_1K_2K_3 \log (K_1K_2K_3).
                $}
            \end{itemize}
          \end{itemize}
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large Error estimates}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          As a measure the root mean square (RMS) force error is widely used:
          $$ \bluec{\varepsilon(r_c, \v K,
            n, \beta) = \sqrt{\langle(\v F^{\textrm{exact}} - \v
              F^{\textrm{{approx}}})^2\rangle} },$$
          with $\v F^{\d {exact}}$ and $\v F^{\d {approx}}$ denoting the
          exact forces and interactions derived with the SPME,
          respectively, and estimated in direct~(green) and
          reciprocal space~(blue) independently.
          \vspace{-1ex}
          \begin{figure}
            \includegraphics[width=0.9\textwidth]{figs/bspline-order6.pdf}
          \vspace{-1ex}
            \caption{The actual and estimated error resulting from the ik
              differentiation scheme as a function of $\beta$ at a fixed order
              $n=6$ }
          \end{figure}
        \end{minipage}
          \vspace{-0.4ex}
        \end{block}
      \end{column}
      \begin{column}{.32\linewidth}
        \vfill
        \begin{block}{\large Error estimates}
          \begin{minipage}[c]{.975\linewidth}
        \begin{figure}
          \includegraphics[width=0.95\textwidth]{figs/bspline-mesh32.pdf}
          \caption{The actual and estimated error as a
          function of $\beta$ resulting from the ik
          differentiation scheme when applying a fixed grid size of $\v K = (32, 32, 32)$ .}  
        \end{figure} 
        \end{minipage}
        \end{block}
        \vfill
        \begin{block}{\large Parameter tuning}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          From the mathematical point of view, the parameter tuning
          problem is a constrained optimization problem:\bluec{
            \begin{align*} 
              \min\quad &  T (r_c, \v K, n, \beta),\\
              \textrm{\textbf{s.t.}}\quad & \varepsilon (r_c, \v K, n, \beta) \leq \varepsilon^\ast
            \end{align*}}The interpolation order $n$ is restricted to $ 2, 4, 6, 8$ and
          $K_\alpha$ should be able to decompose into small prime
          numbers, such as 2, 3, 5 and 7. We solve this problem by
          \redc{a splitting strategy}, that implies solving the following two
          problems independently \bluec{
          \begin{align*}
            (1) & \left\{
          \begin{aligned}
            \min\quad & 
            T^{\textrm{dir}} (r_c, \beta_0), \\* 
            \textrm{\textbf{s.t.}}\quad & 
            \varepsilon^{\textrm{dir}} (r_c, \beta_0) \leq \varepsilon^\ast_{\textrm{dir}},
          \end{aligned}\right. \\ 
          (2) & \left\{\begin{aligned}
            \min\quad & 
            T^{\textrm{rec}} (\v K, n, \beta_0), \\* 
            \textrm{\textbf{s.t.}}\quad & 
            \varepsilon^{\textrm{rec}} (\v K, n, \beta_0) \leq \varepsilon^\ast_{\textrm{rec}},
          \end{aligned}\right.
        \end{align*}}
        by the \redc{bisection method}. The splitting parameter $\beta_0$ is
        finally derived by the \redc{0.618 searching method}.
        \vspace{-1.9ex}
          \begin{figure}
            \includegraphics[width=0.85\textwidth]{figs/both-time-1e-3.pdf}
        \vspace{-1ex}
            \caption{Computational cost of ik differentiated SPME
              method as a function of particle number. The target
              precision is $\varepsilon^\ast=10^{-3}$.}
        \vspace{-1ex}
          \end{figure}
        \end{minipage}
        \end{block}
        \begin{block}{\large Further findings}
          \vspace{1ex}
          \begin{minipage}[c]{.975\linewidth}
          \begin{itemize}
%           \item The error estimation is proved to be sharp.
%           \item We demonstrate the parameter tuning algorithm produces
%             reasonable parameters for SPME.
          \item\justifying For the tested machines, there is \redc{no
              significant difference} between ik and analytical
            differentiation regarding precision and CPU time. The
            analytical differentiation, however lacks momentum
            conservation, a deficiency that has to be removed in order
            to avoid spurious drifts.
          \item The parameters $r_c, n, \beta$ only depend on the charge
            density, target precision and used machine,
            and do \redc{NOT} depend on the size of system~$N$. However the
            value $K_1K_2K_3$ is roughly \redc{proportional} to $N$. 
            \redc{Therefore we can tune the parameters for one reference system and derive
              parameters any system based on the reference system.}
          \end{itemize}
        \end{minipage}
        \vspace{-0.15ex}
        \end{block}
%         \begin{block}{Emails}
%           \texttt{han\_wang@math.pku.edu.cn} \\
%           \texttt{dommert@icp.uni-stuttgart.de} \\
%           \texttt{holm@icp.uni-stuttgart.de}
%         \end{block}
      \end{column}
    \end{columns}
        \vfill
  \end{frame}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Local Variables: 
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_1.charge0.834.box14.9x7.4x7.4.b2.500.r1.30.n6.K121x061x061/parameters.ewald.real.sh
add fig.new

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_1.charge0.834.box14.9x7.4x7.4.b2.500.r1.31.n6.K121x061x061/parameters.spme.ana.real.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_1_bond.charge0.834.box14.9x7.4x7.4.b2.500.r1.40.n6.K121x061x061/parameters.spme.ik.esti.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=1
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_1_bond
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge --water-conf water.gro"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_2.charge0.834.box14.9x7.4x7.4.b2.500.r1.30.n6.K121x061x061/parameters.spme.ik.st.real.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_2
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_2.charge0.834.box14.9x7.4x7.4.b2.500.r1.31.n6.K121x061x061/parameters.spme.ana.st.real.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_2
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.rand_water_2.charge0.834.box14.9x7.4x7.4.b2.500.r1.31.n6.K121x061x061/parameters.spme.ik.esti.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=5
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+project_name=rand_water_2
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.water.charge0.834.box14.9x7.4x7.4.b2.500.r1.30.n6.K121x061x061/parameters.spme.ik.noHO.st.real.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=5
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=49.177
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.water.charge0.834.box14.9x7.4x7.4.b2.500.r1.35.n6.K121x061x061/parameters.spme.st.esti.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 longRange.hetero/publish/fig.new/error.water.charge0.834.box14.9x7.4x7.4.b2.500.r1.40.n6.K121x061x061/parameters.spme.ik.st.real.sh

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=5
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=49.177
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-04-20 shortRange.inhomo/alltext/poster/poster.tex
first version

@@
-\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
+\documentclass[final,hyperref={pdfpagelabels=false},fleqn]{beamer}
 \mode<presentation>
@@
   \usetheme{Berlin}
-  %\usetheme{Dreuw}
+  % \usetheme{Dreuw}
+  % \usetheme{Singapore}
+  % \usetheme{Boadilla}
+  % \usetheme{Copenhagen}
+  % \usetheme{Madrid}
 }
 \usepackage{times}
-  \usepackage{amsmath,amsthm, amssymb, latexsym}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+% \usepackage[fleqn]{amsmath}
+% \usepackage{amsthm}
+% \usepackage{amssymb}
+% \usepackage{latexsym}
 \boldmath
@@
 \usepackage[latin1]{inputenc}
-  \usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}
+\usepackage[orientation=portrait,size=a1]{beamerposter}
+% \usepackage[orientation=portrait,size=a0,scale=1.4,debug]{beamerposter}
 \usepackage{ragged2e} 
@@
 
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-  \graphicspath{{figures/}}
-  \title{How to optimize the parameters of the\\Smooth Particle Mesh Ewald algorithm}
-  \author{Han Wang \inst{1}, Florian Dommert \inst{2}, Christian Holm \inst{2}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 5
+\title{Estimating the force computation error in inhomogeneous and correlated molecular systems}
+\author{Han Wang\inst{1}, Christof Sch\"utte\inst{1}, Pingwen Zhang\inst{2}}
 \institute[]{ \footnotesize
-    \inst{1} LMAM and School of Mathematical Sciences, Peking University, \textit{Beijing}, China  \\
-    \inst{2} Institute for Computational Physics, Universit\"at Stuttgart, \textit{Stuttgart}, Germany
+  \inst{1} Institute for Mathematics, Freie Universit\"at Berlin, Germany\\
+  \inst{2} LMAM and School of Mathematical Sciences, Peking University, P.R. China  
 }
-  %\date{Jul. 31th, 2007}
+% \date{Jul. 31th, 2007}
 %  \RequirePackage{tangocolors}
@@
 
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 5
+
 \begin{document}
@@
 \begin{frame}{}
-    \vfill
+  % \vskip -1cm
   \begin{beamercolorbox}[wd=\paperwidth]{headline}
     \begin{columns}[T]
-        \begin{column}{.2\paperwidth}
+      \begin{column}{.18\paperwidth}
         \begin{center}
-            \hspace{4ex}\includegraphics[width=.5\linewidth]{logo/pku.png}
+          \hspace{4ex}\includegraphics[width=.6\linewidth]{logo/500px-Seal_of_Free_University_of_Berlin.png}
         \end{center}
@@
         \centering
-          \usebeamercolor{title in headline}{\color{fg}\textbf{\LARGE{\inserttitle}}\\[1ex]}
+        \usebeamercolor{title in headline}{\color{fg}\textbf{\Large{\inserttitle}}\\[1ex]}
         \usebeamercolor{author in headline}{\color{fg}\large{\insertauthor}\\[1ex]}
@@
       \end{column}
-        \begin{column}{.2\paperwidth}
+      \begin{column}{.18\paperwidth}
         \begin{center}
-            \vspace*{-1em}
-            \hspace{-2ex}\includegraphics[width=.4\linewidth]{logo/unilogo}\\
-            \vspace*{0.5em}
-            \hspace{-2ex}\includegraphics[width=.6\linewidth]{logo/Logo_ICP_T_V2}
-            \vfill
+          \hspace{4ex}\includegraphics[width=.61\linewidth]{logo/pku.png}
+          % \vspace*{-1em}
+          % \hspace{-2ex}\includegraphics[width=.4\linewidth]{logo/unilogo}\\
+          % \vspace*{0.5em}
+          % \hspace{-2ex}\includegraphics[width=.6\linewidth]{logo/Logo_ICP_T_V2}
+          % \vfill
         \end{center}
@@
   \vfill
-    \vspace{-1cm}
+  % \vspace{-1cm}
   \begin{columns}[t]
-      \begin{column}{.32\linewidth}
+    \begin{column}{.48\linewidth}
       \vfill
@@
         \begin{minipage}[c]{.975\linewidth}
-          We derive an error estimate for the smooth Particle Mesh Ewald~(SPME)
-          algorithm, which is often used for Molecular Dynamics simulations, and
-          applied it to an ionic system to test its va\-lid\-i\-ty. Various
-          combinations of parameters were tested for two different
-          implementations of the SPME algorithm to proof the quality of the
-          estimate, resulting in a parameter tuning algorithm for SPME.
+          We derive the error estimate of force computation (both short-range
+          and long-range interactions) in inhomogeneous and correlated systems.
+          The root mean squared (RMS) error is proved to be composed of
+          three additive parts: the homogeneity error, the inhomogeneity error
+          and the correlation error. Numerical methods are proposed to
+          estimate these errors at an acceptable computational cost, namely
+          $\mathcal O(N\log N)$. The unphysical artifacts of the force error
+          are also discussed by examples.
         \end{minipage}
       \end{block}
-        \vfill
-        \begin{block}{\large Electrostatic energy}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          The electrostatic energy of a periodic ionic system is 
-          \begin{equation*}\bluec{ E = \frac12
-              \sum^\ast_{n}\sum_{i,j}\frac{q_i q_j}{\vert \v r_{ij} +
-                \v n\vert},}
-          \end{equation*} 
-          and the essential difficulty to apply this formula follows from its 
-          \redc{``long range''} nature.
-          \vspace*{-1.2ex}
+      \vspace{.3ex}
+      \begin{block}{Motivations}
+        \textbf{Why study the force calculation:}
+        \begin{itemize}
+        \item Computationally intensive: \redc{$ \sim 90 \%$}.
+        \item One of the main sources of the \redc{``error''}.
+        \item Inhomogeneity: \redc{unphysical artifacts}.
+        \item Correlation: complexity of error estimate.
+        \end{itemize}
+        \textbf{What can we do with the error estimates:}
+        \begin{itemize}
+        \item Understanding \& correcting
+          the unphysical artifacts, quantitatively.
+        \item Correction to \redc{force, energy, pressure, etc.}
+        \item Boost the \redc{accuracy \& efficiency} of simulation automatically.
+        \end{itemize}
+      \end{block}
+      \vspace{.3ex}
+      \begin{block}{Theory}
+        Let a periodic molecular system be composed by $N$ charged
+        particles located at $\v r_1, \v r_2, \cdots, \v r_N$ with
+        charges $q_1, q_2, \cdots, q_N$, respectively. If the error
+        force of a testing particle located at $\v r$ with charge $q$
+        is: \bluec{
+          \begin{align}\label{eqn:thm-error-force}
+            \Delta \v F(\v r) =
+            q\sum_{j=1}^N\,q_j \v K(\v r, \v r_j),
+          \end{align}}
+        then the mean error force is estimated by
+        \bluec{
+          \begin{align}
+            \langle\Delta\v F(\v r)\rangle
+            =
+            q\int_{\mathbb R^3}\v K(\v r , \v r')\,\rho_q(\v r')\,\d d\v r'.
+          \end{align}
+        }
+        The RMS error is estimated by:
+        \bluec{
+          \begin{align} 
+            \langle\vert\Delta\v F(\v r)\vert^2\rangle
+            = 
+            \redc{\mathcal E^2_{\textrm{homo}}(\v r)} +
+            % \langle\Delta\v F(\v r)\,\rangle^2 +
+            \redc{\mathcal E^2_{\textrm{inhomo}}(\v r)} +
+            \redc{\mathcal E_{\textrm{correlation}}(\v r)},
+          \end{align}
+        }
+        with\bluec{
+          \begin{align}
+            &{\mathcal E^2_{\textrm{homo}}(\v r)}
+            = \,
+            q^2\int_{\mathbb R^3}\vert\v K(\v r, \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r', \\
+            &{\mathcal E^2_{\textrm{inhomo}}(\v r)}
+            = \,
+            q^2\bigg[\int_{\mathbb R^3}\v K(\v r, \v r')\rho_q(\v r')\,\d d\v r'\,\bigg]^2
+            \redc{ = \langle\Delta\v F(\v r)\,\rangle^2},
+            \\
+            &{\mathcal E_{\textrm{correlation}}(\v r)}
+            =\,
+            q^2\int_{\mathbb R^3\times\mathbb R^3}\v K(\v r, \v r')\cdot\v K(\v r, \v r'')\,C_{q^2}(\v r', \v r'')\,\d d\v r'\d d\v r''.
+          \end{align}}
+        When the kernel has a convolution form:
+        \bluec{
+          \begin{align}
+            \v K(\v r,\v r') = \v K(\v r- \v r'),
+          \end{align}
+        }
+        the computational cost of the homogeneity error and inhomogeneity error estimates are
+        \redc{$\mathcal O(N\log N)$}, while the correlation error
+        is \bluec{$\mathcal O(N^2\log N)$}. Nearest neighbor approximation: \redc{$\mathcal O(N\log N)$}.        
+        % First neighbor approximation of the correlation error, take water for example:
+        % \bluec{
+        %   \begin{align}\nonumber
+        %     \mathcal E_{\textrm{correlation}}(\v r)
+        %     =&\,
+        %     q^2
+        %     \int_{\mathbb R^3}
+        %     \v K(\v r - \v r')\cdot
+        %     (\hat T_{\textrm{O}}\hat{\v K})^{\vee}(\v r - \v r')
+        %     \,\rho_{\textrm{O}}(\v r')
+        %     \,\d d\v r' \\\label{eqn:c-error-water}
+        %     & \,+
+        %     q^2
+        %     \int_{\mathbb R^3}
+        %     \v K(\v r - \v r')\cdot
+        %     (\hat T_{\textrm{H}}\hat{\v K})^{\vee}(\v r - \v r')
+        %     \,\rho_{\textrm{H}}(\v r')
+        %     \,\d d\v r',
+        %   \end{align}}
+        % where
+        % \bluec{
+        %   \begin{align}
+        %     \hat T_{\textrm{O}}(\v m)
+        %     &= 
+        %     2\langle
+        %     q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}}
+        %     \rangle,\\
+        %     \hat T_{\textrm{H}}(\v m)
+        %     &= 
+        %     \langle
+        %     q_{\textrm{O}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}} +
+        %     q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}}}
+        %     \rangle.
+        %   \end{align}}
+        % The correlation error can be approximately calculated at the cost of
+        % \redc{$\mathcal O(N\log N)$}.
+      \end{block}
+      \vspace{.3ex}
+      \begin{block}{Long-range force \& pressure correction}
+        The calculated force can be corrected by the mean error force:
+        \bluec{
+          \begin{align}\label{eqn:define-fcorr}
+            \v F_{\textrm{corr}}(\v r) = {\v F}_{\textrm{orig}}(\v r) + \langle\Delta\v F(\v r)\rangle.
+          \end{align}}
+        The new mean error force varnishes:
+        \bluec{
+          \begin{align}\label{eqn:mean-fcorr}
+            \langle\Delta\v F_{\textrm{corr}}(\v r)\rangle
+            =
+            \big\langle\,
+            \v F(\v r) - {\v F}_{\textrm{orig}}(\v r) - \langle\Delta\v F(\v r)\rangle\,
+            \big\rangle \redc{= 0}.
+          \end{align}}
+        The mean square error is given by
+        \bluec{
+          \begin{align} \nonumber
+            \langle\vert\Delta\v F_{\textrm{corr}}(\v r)\vert^2\rangle
+            & =
+            \redc{\mathcal E^2_{\textrm{homo}}(\v r)} +
+            \redc{\mathcal E_{\textrm{correlation}}(\v r)}.
+          \end{align}}
+        No inhomogeneity error any more! Pressure correction:
+        \bluec{
+          \begin{align} 
+            \v P_{\textrm{corr}}
+            & = \int_{\mathbb R^3\times\mathbb R^3}
+            \frac1{2V}[\v r\otimes\v K](\v r' - \v r'')
+            \rho(\v r') \rho(\v r'') 
+            \d d\v r'\d d\v r'' 
+          \end{align}}          
+      \end{block}
+    \end{column}
+    \begin{column}{.48\linewidth}
+      \begin{block}{Adaptive cut-off}
+        Use larger cut-off radius for interfacial regions, while use smaller
+        cut-off radius for bulk regions. The error estimate guarantee the error
+        is uniformly distributed.
+      \end{block}
+      \begin{block}{Short-range example}
         \begin{figure}
           \centering
-            \includegraphics[width=0.75\textwidth]{figs/decay.pdf}
+          \includegraphics[width=0.85\textwidth]{figs/t0.85-n16000-rc07.5uni/confout-02.eps}\\
+          \includegraphics[width=0.85\textwidth]{figs/t0.85-n16000-rc07.5uni/error-uniform.eps}
+          \caption{An inhomogeneous system: liquid-vapor equilibrium of Lennard-Jones particles.
+            $T^\ast = 0.85$.}
         \end{figure}
-          \vspace*{-1.5ex}
-        \end{minipage}
       \end{block}
-        \vfill
-        \begin{block}{\large Ewald summation}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          A good way to deal with the electrostatic in\-ter\-action in periodic
-          systems was proposed by Ewald in 1921:
-          \begin{align*}
-            E &=  E_{\textrm{dir}} +E_{\textrm{rec}}+E_{\textrm{corr}}\\
-            E_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
-            \sum_{i,j = 1}^{N} \frac{q_iq_j\, \redc{\textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}}
-            {\vert\v{r}_{ij} + \v{n}\vert} \\ \label{Erec-ewald}
-            E_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
-            \frac{\redc{\exp(-\pi^2\v m^2 / \beta^2)}}{\v m^2} S(\v m) S(-\v m) \\
-            E_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
-          \end {align*}
-          Consider the \redc{``short range''} nature of the red terms in both real and
-          reciprocal space, and the structure factor $S(\v m)$ given by:
-          \begin{equation*}
-            S(\v m) = \sum_{j=1}^N q_j \exp (2 \pi i \v m \cdot \v r_j).
-          \end{equation*}
-          Unfortunately, the computational cost is \redc{$\mathcal O(N^{3/2})$}
-          at the best.          
-        \end{minipage}
-        \end{block}
-        \vfill
-        \begin{block}{\large $O(N \log N)$ algorithms}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          In the last two decades, some successful algorithms have
-          been developed: 
-          \begin{itemize}
-          \item The \redc Particle--\redc Particle--\redc Particle--\redc Mesh method
-          \item The \redc Particle \redc Mesh \redc Ewald method 
-          \item The \redc Smooth \redc Particle \redc Mesh \redc Ewald method 
-          \end{itemize}
-
-          \bluec{\textbf{Key point:}} The term $ \exp (2 \pi i
-          \v m \cdot \v r_j) $ is just calculated on a given number of grid
-          points. To derive its value at any other position, an interpolation is 
-          using the known values on the neighboring grid points. Therefore 
-          Fast Fourier transforms (FFT) can be applied for the calculation of
-          the reciprocal part and the computational cost is drastically
-          decreased to \redc{$\mathcal O(N\log N)$}.
-        \end{minipage}
+      \begin{block}{Convergence check with respect to cut-off}
+        \begin{figure}
+          \centering
+          \includegraphics[width=0.85\textwidth]{figs/converge.new/t0p85-gas.eps}\\
+          \includegraphics[width=0.85\textwidth]{figs/converge.new/tension-t0p85.eps} 
+          \caption{Convergence check of equilibrium vapor density and
+            surface tension with respect to cut-off radius.
+            Reference (black line with gray region denoting the
+            uncertainty) was obtained at cut-off of $r^\ast_c =
+            13$. URC: uniform cut-off, ARC: the adaptive cut-off and
+            LFC: the long-range force correction, LPC: long-range
+            pressure correction. }
+        \end{figure}
+        % \begin{figure}
+        %   \centering
+        %   \includegraphics[width=0.85\textwidth]{figs/converge.new/t0p85-liquid.eps} 
+        % \end{figure}
       \end{block}
     \end{column}
-      \begin{column}{.32\linewidth}
-        \vfill
-        \begin{block}{\large The parameters in SPME}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          \begin{itemize}
-          \item \bluec{$\beta$} corresponds to the same parameter as in the Ewald summation.
-          \item \bluec{$r_c$} is the cut off used in the neighbor list method
-            for the direct part.
-          \item \bluec{$n$}  defines the order of the cardinal B-splines.
-          \item \bluec{$\v K$}  contains the number of grid points used to
-            discrete the space in every dimension.
-          \end{itemize}
-          It is not a prior clear how to choose these parameters properly, but
-          an arbitrary choice may lead to \redc{totally wrong results}.
-
-          When using SPME method, there are two possible ways of
-          calculating forces in the charged system, that differ in the
-          computational effort and accuracy, considering the same set of
-          parameters.
-          \vspace*{-0.5ex}
-          \begin{itemize}
-            \item \bluec{ik differentiation}\vspace{0.4ex}
-              \begin{minipage}{0.975\textwidth} 
-                Multiplying the reciprocal energy with the vector \bluec{$ik$} in
-                reciprocal space, and transforming the result back to real
-                space corresponds to a derivative and yields the force. However
-                \redc{4} FFTs are required, but momentum is \redc{conserved}.
-              \end{minipage}\vspace*{0.2ex}
-            \item \bluec{analytical differentiation}\vspace{0.4ex}
-            \begin{minipage}{0.975\textwidth}
-            The forces are derived from the the derivative of the approximated
-            energy. Only \redc{2} FFTs are required, but momentum is \redc{not}
-            conserved.
-            \vspace*{-0.2ex}
-        \end{minipage}
-          \end{itemize}
-        \end{minipage}
-        \end{block}
-        \vfill
-        \begin{block}{\large Designing a parameter tuning algorithm}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          To tune the parameters, we need:
-          \begin{itemize}\justifying
-          \item \bluec{Error estimates} that ensure the algorithm to give
-            correct results. 
-          \item \bluec{CPU-time estimates} that yield the most time-saving
-            parameters for a given allowed error.
-          \end{itemize}
-        \end{minipage}
-        \end{block}
-        \begin{block}{\large CPU-time estimate}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          \begin{itemize}
-          \item Direct part \quad \redc{$T^{\textrm{dir}} \approx
-              C_dr_c^3$}
-          \item Reciprocal part 
-            \begin{itemize}
-            \item ik differentiation \newline
-              \redc{$
-                T^{\textrm{rec}}_{\textrm{ik}}
-                \approx 2 C_s Nn^3 + 4\, C_f  K_1K_2K_3 \log (K_1K_2K_3) 
-                $}
-            \item analytical differentiation\newline
-              \redc{$
-                T^{\textrm{rec}}_{\textrm{ana}}
-                \approx 3C_s Nn^3 + 2\, C_f  K_1K_2K_3 \log (K_1K_2K_3).
-                $}
-            \end{itemize}
-          \end{itemize}
-        \end{minipage}
-        \end{block}
-        \vfill
-        \begin{block}{\large Error estimates}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          As a measure the root mean square (RMS) force error is widely used:
-          $$ \bluec{\varepsilon(r_c, \v K,
-            n, \beta) = \sqrt{\langle(\v F^{\textrm{exact}} - \v
-              F^{\textrm{{approx}}})^2\rangle} },$$
-          with $\v F^{\d {exact}}$ and $\v F^{\d {approx}}$ denoting the
-          exact forces and interactions derived with the SPME,
-          respectively, and estimated in direct~(green) and
-          reciprocal space~(blue) independently.
-          \vspace{-1ex}
-          \begin{figure}
-            \includegraphics[width=0.9\textwidth]{figs/bspline-order6.pdf}
-          \vspace{-1ex}
-            \caption{The actual and estimated error resulting from the ik
-              differentiation scheme as a function of $\beta$ at a fixed order
-              $n=6$ }
-          \end{figure}
-        \end{minipage}
-          \vspace{-0.4ex}
-        \end{block}
-      \end{column}
-      \begin{column}{.32\linewidth}
-        \vfill
-        \begin{block}{\large Error estimates}
-          \begin{minipage}[c]{.975\linewidth}
-        \begin{figure}
-          \includegraphics[width=0.95\textwidth]{figs/bspline-mesh32.pdf}
-          \caption{The actual and estimated error as a
-          function of $\beta$ resulting from the ik
-          differentiation scheme when applying a fixed grid size of $\v K = (32, 32, 32)$ .}  
-        \end{figure} 
-        \end{minipage}
-        \end{block}
-        \vfill
-        \begin{block}{\large Parameter tuning}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          From the mathematical point of view, the parameter tuning
-          problem is a constrained optimization problem:\bluec{
-            \begin{align*} 
-              \min\quad &  T (r_c, \v K, n, \beta),\\
-              \textrm{\textbf{s.t.}}\quad & \varepsilon (r_c, \v K, n, \beta) \leq \varepsilon^\ast
-            \end{align*}}The interpolation order $n$ is restricted to $ 2, 4, 6, 8$ and
-          $K_\alpha$ should be able to decompose into small prime
-          numbers, such as 2, 3, 5 and 7. We solve this problem by
-          \redc{a splitting strategy}, that implies solving the following two
-          problems independently \bluec{
-          \begin{align*}
-            (1) & \left\{
-          \begin{aligned}
-            \min\quad & 
-            T^{\textrm{dir}} (r_c, \beta_0), \\* 
-            \textrm{\textbf{s.t.}}\quad & 
-            \varepsilon^{\textrm{dir}} (r_c, \beta_0) \leq \varepsilon^\ast_{\textrm{dir}},
-          \end{aligned}\right. \\ 
-          (2) & \left\{\begin{aligned}
-            \min\quad & 
-            T^{\textrm{rec}} (\v K, n, \beta_0), \\* 
-            \textrm{\textbf{s.t.}}\quad & 
-            \varepsilon^{\textrm{rec}} (\v K, n, \beta_0) \leq \varepsilon^\ast_{\textrm{rec}},
-          \end{aligned}\right.
-        \end{align*}}
-        by the \redc{bisection method}. The splitting parameter $\beta_0$ is
-        finally derived by the \redc{0.618 searching method}.
-        \vspace{-1.9ex}
-          \begin{figure}
-            \includegraphics[width=0.85\textwidth]{figs/both-time-1e-3.pdf}
-        \vspace{-1ex}
-            \caption{Computational cost of ik differentiated SPME
-              method as a function of particle number. The target
-              precision is $\varepsilon^\ast=10^{-3}$.}
-        \vspace{-1ex}
-          \end{figure}
-        \end{minipage}
-        \end{block}
-        \begin{block}{\large Further findings}
-          \vspace{1ex}
-          \begin{minipage}[c]{.975\linewidth}
-          \begin{itemize}
-%           \item The error estimation is proved to be sharp.
-%           \item We demonstrate the parameter tuning algorithm produces
-%             reasonable parameters for SPME.
-          \item\justifying For the tested machines, there is \redc{no
-              significant difference} between ik and analytical
-            differentiation regarding precision and CPU time. The
-            analytical differentiation, however lacks momentum
-            conservation, a deficiency that has to be removed in order
-            to avoid spurious drifts.
-          \item The parameters $r_c, n, \beta$ only depend on the charge
-            density, target precision and used machine,
-            and do \redc{NOT} depend on the size of system~$N$. However the
-            value $K_1K_2K_3$ is roughly \redc{proportional} to $N$. 
-            \redc{Therefore we can tune the parameters for one reference system and derive
-              parameters any system based on the reference system.}
-          \end{itemize}
-        \end{minipage}
-        \vspace{-0.15ex}
-        \end{block}
-%         \begin{block}{Emails}
-%           \texttt{han\_wang@math.pku.edu.cn} \\
-%           \texttt{dommert@icp.uni-stuttgart.de} \\
-%           \texttt{holm@icp.uni-stuttgart.de}
-%         \end{block}
-      \end{column}
+    % \begin{column}{.32\linewidth}
+    % \end{column}
   \end{columns}

### 2012-04-20 shortRange.inhomo/alltext/slides/ucsb.2012.04/slide.tex
add ucsb

\documentclass{beamer}

% \usepackage{CJKnumb}\usepackage{beamerthemesplit}

\mode<article>
{
  \usepackage{beamerbasearticle}
  \usepackage{fullpage}
  \usepackage{hyperref}
}

%\usepackage{beamerthemesplit} 
%\usepackage{beamerthemeshadow}  
%\usepackage[width=2cm,dark,tab]{beamerthemesidebar}

% Setup appearance:

%\usetheme{Darmstadt}
\usefonttheme[onlylarge]{structurebold}
\setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
\setbeamertemplate{navigation symbols}{}

\renewcommand\arraystretch{1.5}

% Standard packages

\usepackage[english]{babel}
%\usepackage[latin1]{inputenc}

\usepackage{epsf}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{tabularx}

% \usepackage[usenames,dvipsnames]{color}
\definecolor{shadow}{gray}{0.8}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\shadowc}[1]{{\color{shadow} #1}}
\definecolor{myyellow}{HTML}{FFB700}
\newcommand{\yellowc}[1]{{\color{myyellow} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\renewcommand{\v}[1]{\textbf{\textit{#1}}}
\renewcommand{\d}[1]{\textrm{#1}}

\usepackage{amsfonts}
\newcommand{\tickYes}{\checkmark}
\usepackage{pifont}
\newcommand{\tickNo}{\hspace{1pt}\ding{55}}

% \usetheme{Boadilla}
% \usetheme{Copenhagen}
% \usetheme{Madrid}
\usetheme{Singapore}

\begin{document}
%\title{Comparative atomistic and coarse-grained study of water: Simulation details vs. Simulation feasibility}
%\title[Optimizing SPME]{Optimizing Working Parameters of the Smooth Particle Mesh Ewald Algorithm}
\title[]{
  Estimating the force computation error in inhomogeneous and correlated
  molecular systems
}
%
\author{Han Wang}
\institute[FUB] {
  Institute for Mathematics, Freie Universit\"at Berlin, Germany
\vskip 0.4cm
Joint with: Christof Sch\"utte (FUB), Pingwen Zhang (PKU)}
\date[12 Apr 2012]{12 Apr 2012}
\frame{\titlepage}

% \begin{frame}{Why?}
%   \begin{itemize}
%     \vfill
%   \item <1-> Why force computation?
%     \begin{itemize}\itemsep 3pt
%     \item <2->Molecular dynamics simulation.
%     \item <3->Computationally intensive: \redc{$ \sim 90 \%$}
%     \item <4->One of the main sources of the \redc{``error''}.
%     \item <5->May introduce \redc{unphysical artifacts}.
%     \end{itemize}
%     \vfill
%   \item <6-> Why error estimate?
%     \begin{itemize}\itemsep 3pt
%     \item <7->Understanding \& correcting
%       the unphysical artifacts, quantitatively.
%     \item <8->Correction to force, energy, pressure, etc.
%     \item <9->Boost the efficiency of simulation automatically.
%     \end{itemize}
%     \vfill
%   \end{itemize}
% \end{frame}

\begin{frame}{Why?}
  Why force computation?
  \begin{itemize}\itemsep 3pt
  \item <2->Molecular dynamics simulation.
  \item <3->Computationally intensive: \redc{$ \sim 90 \%$}
  \item <4->One of the main sources of the \redc{``error''}.
  \item <5->May introduce \redc{unphysical artifacts}.
  \end{itemize}
  \vfill
\end{frame}

\begin{frame}{Unphysical artifacts due to the force error}
  \begin{itemize}\itemsep 10pt
  \item Example system:
    \begin{figure}
      \centering
      \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/confout-02.eps}
    \end{figure}
  \item Equilibrium densities:
    \begin{figure}
    \centering
    \includegraphics[width=0.49\textwidth]{figs/converge.new/t0p85-gas-1.eps} 
    \includegraphics[width=0.49\textwidth]{figs/converge.new/t0p85-liquid-1.eps} 
  \end{figure}  
  \end{itemize}
\end{frame}

\begin{frame}{Why?}
  Why error estimate?
  \begin{itemize}\itemsep 3pt
  \item <2->Understanding \& correcting
    the unphysical artifacts, quantitatively.
  \item <3->Correction to \redc{force, energy, pressure, etc.}
  \item <4->Boost the accuracy \& efficiency of simulation automatically.
  \end{itemize}  
  \vfill
\end{frame}

\begin{frame}{The working parameters of SPME} {A 6 dimensional parameter space!}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/long-range/error-uniform.eps}
  \end{figure}  
\end{frame}

\begin{frame}{Overview of the error estimates}
  \begin{itemize}
  \vfill
  \item<1->   Conditions for the error estimate:
  \begin{enumerate}\itemsep 3pt
  \item \redc{Homogeneity}.
  \item Particles are \redc{uncorrelated}.
  \end{enumerate}
  \vfill
\item<2->   Current error estimates:
  \begin{table}
    \centering
    \begin{tabular*}{0.85\textwidth}{l@{\extracolsep{\fill}}ll}\hline\hline
      Conditions & cut-off & SPME \\\hline
      1+2 & \bluec{\tickYes\quad$\mathcal O(1)$}  & \bluec{\tickYes\quad$\mathcal O(1)$} \\
      2   & \redc{\tickYes\quad$\mathcal O(N\log N)$} & \redc{\tickYes\quad$\mathcal O(N\log N)$} \\
      none& \redc{\tickNo\quad$\mathcal O(N^2\log N)$} & \redc{\tickNo\quad$\mathcal O(N^2\log N)$} \\
          &  & \redc{N.N.A. $\mathcal O(N\log N)$} \\\hline\hline
    \end{tabular*}
  \end{table}
  \vfill
  \end{itemize}
\end{frame}

\begin{frame}{The error estimate}
  \begin{itemize}
  \item <1-> The error force
    \bluec{
      \begin{align*}
        \Delta \v F(\v r)
        &=
        \v F_{\textrm{calculate}}(\v r) - \v F_{\textrm{exact}}(\v r)
      \end{align*}}
  \item <2-> Define the error force kernel
    \bluec{
      \begin{align*}
        \Delta \v F(\v r)
        &=
        q \sum_{j=1}^N q_j \,\v K(\v r, \v r_j)
      \end{align*}}
    It is possible for most main stream force calculation algorithms: cut-off, SPME, P3M, etc.
  \item <3-> The kernel of cut-off method:
    \bluec{
      \begin{align*}
        \v K(\v r,\v r') =
        \left\{
          \begin{array}{ll}
            0, & \vert\v r - \v r'\vert\leq r_c; \\
            \v F(\vert\v r-\v r'\vert), & \vert\v r - \v r'\vert > r_c.
          \end{array}
        \right.
      \end{align*}}
    \vfill
  \end{itemize}
\end{frame}

\begin{frame}{The error estimate}
  \begin{itemize}\itemsep -10pt
  \item<1->   The mean error force is
    \bluec{
      \begin{align*}
        \langle\Delta\v F(\v r)\rangle
        =
        q\int_{\mathbb R^3}\v K(\v r , \v r')\,\rho_q(\v r')\,\d d\v r'
      \end{align*}
    }
  \vskip -10cm
\item<2->   The error:
  \bluec{
    \begin{align*} \nonumber
      \langle\vert\Delta\v F(\v r)\vert^2\rangle
      = 
      \redc{\mathcal E^2_{\textrm{homo}}(\v r)} +
      % \langle\Delta\v F(\v r)\,\rangle^2 +
      \redc{\mathcal E^2_{\textrm{inhomo}}(\v r)} +
      \redc{\mathcal E_{\textrm{correlation}}(\v r)}.
    \end{align*}
  }
  with\bluec{
  \begin{align*}
    \redc{\mathcal E^2_{\textrm{homo}}(\v r)}
    = &\,
    q^2\int_{\mathbb R^3}\vert\v K(\v r, \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'  \\
    \redc{\mathcal E^2_{\textrm{inhomo}}(\v r)}
    = &\,
    q^2\bigg[\int_{\mathbb R^3}\v K(\v r, \v r')\rho_q(\v r')\,\d d\v r'\,\bigg]^2
    \redc{ = \langle\Delta\v F(\v r)\,\rangle^2}
    \\
    \redc{\mathcal E_{\textrm{correlation}}(\v r)}
    =&\,
    q^2\int_{\mathbb R^3\times\mathbb R^3}\v K(\v r, \v r')\cdot\v K(\v r, \v r'')\,C_{q^2}(\v r', \v r'')\,\d d\v r'\d d\v r''
  \end{align*}}
  \end{itemize}
\end{frame}

\begin{frame}{Liquid-vapor equilibrium of Lennard-Jones particles}
  \begin{figure}
    \centering
    \includegraphics[scale=1]{figs/t0.85-n16000-rc07.5uni/confout-02.eps}\\
    \includegraphics[]{figs/t0.85-n16000-rc07.5uni/error-uniform.eps}
  \end{figure}
\end{frame}

\begin{frame}{cut-off in bulk}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-bulk-step00.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off in bulk}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-bulk-step01.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off in bulk}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-bulk-step02.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off in bulk}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-bulk-step03.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off at interface}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-bulk-step00.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off at interface}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-interface-step03.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off at interface}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-interface-step04.eps}
  \end{figure}  
\end{frame}

\begin{frame}{cut-off at interface}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/t0.85-n16000-rc07.5uni/cut-interface-step05.eps}
  \end{figure}  
\end{frame}

\begin{frame}{Equilibrium gas density}
  \begin{figure}
    \centering
    \includegraphics[]{figs/converge.new/t0p85-gas.eps} 
  \end{figure}
  URC: uniform cut-off, ARC: adaptive cut-off, LFC: long-range force correction.
\end{frame}

\begin{frame}{Equilibrium liquid density}
  \begin{figure}
    \centering
    \includegraphics[]{figs/converge.new/t0p85-liquid.eps} 
  \end{figure}
  URC: uniform cut-off, ARC: adaptive cut-off, LFC: long-range force correction.
\end{frame}

\begin{frame}{Surface tension}
  \begin{figure}
    \centering
    \includegraphics[]{figs/converge.new/tension-t0p85.eps} 
  \end{figure}
  URC: uniform cut-off, ARC: adaptive cut-off, LFC: long-range force correction,
  LPC: long-range pressure correction.
\end{frame}

\begin{frame}{Electrostatic interaction and Ewald summation}
  \begin{itemize}
  \item<1->   Electrostatic interaction:
  \begin{equation*}\bluec{
    U_{\textrm{ele}} = \frac12 \sum^\ast_{n}\sum_{i,j}\frac{q_i q_j}{\vert \v r_{ij} + \v n\vert}}
  \end{equation*}
\item <2->
  Ewald summation (1921) splits the
  energy into three parts
  \bluec{
  \begin {align*}
    U_{\textrm{ele}} &=  U_{\textrm{dir}} + U_{\textrm{rec}}+ U_{\textrm{corr}}\\
    U_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
    \sum_{i,j = 1}^{N} \frac{q_iq_j\, \redc{\textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}}
    {\vert\v{r}_{ij} + \v{n}\vert} \\ \label{Erec-ewald}
    U_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
    \frac{\redc{\exp(-\pi^2\v m^2 / \beta^2)}}{\v m^2} S(\v m) S(-\v m) \\
    U_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
  \end {align*}}
  \end{itemize}
\end{frame}

\begin{frame}{Smooth Particle Mesh Ewald Method (SPME)}{Basic concepts}
  \begin{itemize}\itemsep -5pt
  \item<1-> The structure factor \bluec{$S(\v m)$} is
    defined by \bluec{
      \begin{equation*}\label{sm1}
        S(\v m) = \sum_{j=1}^N q_j \exp (2 \pi i \v m \cdot \v r_j),
      \end{equation*}}
  \item<2-> Optimal computational cost\footnote{
    \bluec{J. Perram, H. Petersen and S. De Leeuw, Mol. Phys. \textbf{65}, 875 (1988).}}: \redc{$\mathcal O(N^{1.5})$}.
    \vskip .5cm
  \item<3-> \redc{SPME}\footnote{
    \bluec{U. Essmann, \textit{et. al.}, J. Chem. Phys. \textbf{103}, 8577 (1995).}}: interpolate \bluec{$S(\v m)$} on grid, then FFT.
    The computational cost is 
  \begin{align*}
    \begin{tabular}[t]{c}
      \redc{$\mathcal O(N)$}\\
      {direct}
    \end{tabular}
    +
    \begin{tabular}[t]{c}
      \redc{$\mathcal O(N)$}\\
      {interpolation}
    \end{tabular}
    +
    \begin{tabular}[t]{c}
      \redc{$\mathcal O(N\log N)$}\\
      {FFTs}
    \end{tabular}
    =
    \begin{tabular}[t]{c}
      \redc{$\mathcal O(N\log N)$}\\
      {total cost}
    \end{tabular}
    \end{align*}
  \end{itemize}
\end{frame}

\begin{frame}{Smooth Particle Mesh Ewald Method (SPME)}
  {The working parameters is 6 dimensional}
  \vfill
  To use SPME method, one should provide the following parameters.
  \vfill
  \begin{itemize}
    \item \redc{$\beta$} \quad The controlling parameter.
    \item \redc{$r_c$} \quad The direct space cut-off radius.
    \item \redc{$\v K$} \quad The reciprocal space cut-off. The number of FFT grid points.
    \item \redc{$n$} \quad The order of cardinal B-spline interpolation.
  \end{itemize}
  \vfill An arbitrary combination may lead to \redc{totally wrong
    results}. \vfill
\end{frame}

\begin{frame}{The parameter tuning of SPME }
  The parameter tuning is a constrained optimization problem:\footnote{
    \bluec{H. Wang, F. Dommert and C. Holm, J. Chem. Phys. \textbf{133}, 034117 (2010).}}
  \bluec{
    \begin{align*} 
      \min\quad &  T (r_c, \v K, n, \beta),\\
      \textrm{\textbf{s.t.}}\quad & \mathcal E (r_c, \v K, n, \beta) = \mathcal E_{\textrm{C}}
    \end{align*}}
  \redc{Nearly optimal} working parameters can be found \redc{automatically}.
\end{frame}

\begin{frame}{The inhomogeneity problem of SPME}
  \begin{itemize}
  \item <1-> The mean error force is
    \bluec{
      \begin{align*}
        \langle\Delta\v F(\v r)\rangle
        =
        q\int_{\mathbb R^3}\v K(\v r , \v r')\,\rho_q(\v r')\,\d d\v r'
      \end{align*}
    }
    with
    \begin{align*}
      \bluec{  \rho_q(\v r) = 
        \bigg\langle
        \sum_{j = 1}^N
        q_j\delta(\v r - \v r_j)
        \bigg\rangle
      }
    \end{align*}    
  \item <2-> Varnishes if the system is \redc{locally neutral}.
  \end{itemize}
\end{frame}

\begin{frame}{Error estimate in an inhomogeneous and uncorrelated system}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/long-range-inhomo/rand1-error.eps}
  \end{figure}  
\end{frame}

\begin{frame}{The trouble in water system}{Staggered mesh SPME}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/long-range-inhomo/water-st-error-1.eps}
  \end{figure}  
\end{frame}

\begin{frame}{Nearest neighbor approximation of the correlation error}{Staggered mesh SPME}
  \begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figs/long-range-inhomo/water-st-error-2.eps}
  \end{figure}  
\end{frame}

\begin{frame}
  \vfill
  \centerline{ \Huge
    Thanks!  }
  \vfill
\end{frame}

\end{document}

### 2012-04-20 longRange.hetero/publish/main.tex
add alltext
fix bugs

@@
-\documentclass[aps,pre,preprint]{revtex4}
-% \documentclass[aps,pre,twocolumn]{revtex4-1}
-% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
+\documentclass[aps,pre,preprint,unsortedaddress]{revtex4}
+% \documentclass[aps,pre,unsortedaddress]{revtex4-1}
+%\documentclass[aps,pre,twocolumn]{revtex4-1}
+%\documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
 
@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+\author{Pingwen Zhang}
+\affiliation{LMAM and School of Mathematical Sciences, Peking University}
 \author{Christof Sch\"utte}
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\author{Pingwen Zhang}
-% \email{pzhang@pku.edu.cn}
-\affiliation{LMAM and School of Mathematical
-  Sciences, Peking University}
 
@@
 error estimate~\cite{kolafa1992cutoff, hummer1995numerical,
-  petersen1995accuracy, deserno1998mue2,
+  petersen1995accuracy, deserno1998mue2, stern2008mesh,
   wang2010optimizing, neelov2010interlaced, ballenegger2012convert},
@@
     q_i^2\bigg\langle\sum_{j=1}^N
-    q_j^2\vert\v K(\v r, \v r_j)\vert^2
+    q_j^2\vert\v K(\v r_i, \v r_j)\vert^2
     \bigg\rangle +
     q_i^2\bigg\langle\sum_{j\neq k}
-    q_jq_k \v K(\v r, \v r_j)\cdot\v K(\v r, \v r_k)
+    q_jq_k \v K(\v r_i, \v r_j)\cdot\v K(\v r_i, \v r_k)
     \bigg\rangle \\ \nonumber
@@
   that violates the Newton's third law, the staggered mesh analytical
-  differentiation strictly preserves it.
+  differentiation preserves it to the leading order.
 \item We also proved the equivalence of the staggered mesh ik- and analytical
@@
 
-\newpage
 \appendix
@@
   \v g(\v m)
-  \\  \label{eqn:ik.kernel.2}
+  \\ 
   \,&
@@
 
-\newpage
-
 \bibliography{ref}{}

### 2012-04-23 shortRange.inhomo/alltext/pubilsh/main.tex
add missing files
trying to make everything better.

@@
 of the potential energy, the pressure and the free energy by applying
-the standard long range correction (LRC)~\cite{allen87a}, which
+the standard long-range correction (LRC)~\cite{allen87a}, which
 assumes the uniformity outside the cut-off radius and integrates the
@@
 
+\recheck{ One possible way to avoid the cut-off difficulty is to
+  modify the short-range interaction by a shifting approach: inside a
+  certain radius the origianl interaction is kept, while outside it the
+  interaction is screen by a shift function, so that goes to
+  zero smoothly. The amount of Shifting is minor in most cases,
+  however, it actually changes the way of
+  modelling molecules. For example, it
+  has been shown that shifting the dispersion remarkably changes the
+  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
+  Since the dispersion term 
+  can be derived by quantum mechanical arguments, and has the physical
+  reality, the unshifted interaction is
+  prefered and investigated by most studies
+  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
+  % Shifting the direct part of the Ewald summation actually
+  % violates the Coulomb's law in the way that depends on the
+  % splitting parameter, so it should be treated carefully.
+  % Here we would like to suggest treating the shifting approach
+  % as a special case 
+}
 % In this paper, we focus on the systems in which
@@
   wang2010optimizing} for long-range Ewald family
-methods~\cite{ewald1921die, hockney1988computer, deserno1998mue1,
-  darden1993pme, essmann1995spm} have provided a profound
+methods~\cite{ewald1921die, hockney1988computer, 
+  darden1993pme, essmann1995spm, deserno1998mue1} have provided a profound
 understanding of the accuracy of force calculation, and introduced
@@
 inhomogeneity error, therefore,  the precision of
-simulation is improved without much extra computational load. To show the
+simulation is improved without much extra computational load.
+
+To show the
 effectiveness of the error estimate and the proposed methods, two
@@
 properties, and the colliding nanoscale clusters for dynamical
-properties. Finally, conclusions are given in section
-\ref{sec:conclusion}.
+properties.
+\recheck{
+  In these example, we investigate the Lennard-Jones interaction, which
+  is one of the most widely used in molecular simulations.
+  However, the error estimate,
+  the adaptive cut-off and long-range correction methods
+  are not restricted to the Lennard-Jones: it can
+  be applied to other types of short-range interactions without 
+  difficulty, such as
+  Buckingham, the direct part of Ewald summation~\cite{ewald1921die}, etc..
+  We want to stress that the main contribution and the research interest is the
+  quantitative study of the force computation error by cuting-off
+  the short-range interaction.
+  The examples, which are comparatively simple and ideal,
+  are used only for testing the validity of the error
+  estimate and the proposed methods,
+  and demostrating the role of different errors in the simulations.
+  The error study in more realistic systems requires the
+  estimates of the electrostatic interaction,
+  which are calculated by the long-range algorithms, such as
+  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
+  P3M~\cite{deserno1998mue1}, etc..
+  The space of the present paper is not enough for
+  these algorithms, so they will be delivered in the future work.
+}
+% Finally, conclusions are given in section
+% \ref{sec:conclusion}.
 
@@
 % this assumption simplifies the discussion, and
-the error estimates for
+the error estimate for
 the one-component system can be straightforwardly extended to the
@@
 
+\recheck{
+  We want to stress again the main research interest of the present paper is the
+  error estimate, the proposed adaptive cut-off and long-range
+  correction methods. The examples are used to demonstrate
+  the validity of these theoretical results. The applications
+  of the error estimate can be more general than the studied examples.
+  Other kind the short-range interaction (not only the Lennard-Jones
+  but also the Buckingham,
+  the direct part of the Ewald summation, etc.),
+  and other kinds of inhomogeneity
+  (not only  planar and merging spirical interfaces)
+  can be easily studied by the error estiamtes and the proposed methods.
+  The error study of
+  more realistic systems requires the error estiamtes of the long-range
+  algoritms, and careful comparisons with the short-range error.
+  Since the present paper is focusing on the short-range
+  interactions, and the space is limited,
+  they will be given in the future work.
+}
+
 \section*{Acknowledgments}
-The authors gratefully thank Luigi Delle Site for for useful comments
+The authors gratefully thank Luigi Delle Site for useful comments
 on the manuscript. The work of P.Z. is supported by grants from

### 2012-04-23 shortRange.inhomo/alltext/pubilsh/main.tex
fix typos

@@
   modify the short-range interaction by a shifting approach: inside a
-  certain radius the origianl interaction is kept, while outside it the
+  certain radius the original interaction is kept, while outside it the
   interaction is screen by a shift function, so that goes to
@@
   however, it actually changes the way of
-  modelling molecules. For example, it
+  modeling molecules. For example, it
   has been shown that shifting the dispersion remarkably changes the
@@
   reality, the unshifted interaction is
-  prefered and investigated by most studies
+  preferred and investigated by most studies
   (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
@@
   We want to stress that the main contribution and the research interest is the
-  quantitative study of the force computation error by cuting-off
+  quantitative study of the force computation error by cutting-off
   the short-range interaction.
@@
   estimate and the proposed methods,
-  and demostrating the role of different errors in the simulations.
+  and demonstrating the role of different errors in the simulations.
   The error study in more realistic systems requires the
@@
 $r_c^\ast = 10$, and eliminates the finite size effect reported in
-literatures \cite{chen1995area, orea2005oscillatory,
+literature~\cite{chen1995area, orea2005oscillatory,
   biscay2009calculation}.
@@
   and other kinds of inhomogeneity
-  (not only  planar and merging spirical interfaces)
-  can be easily studied by the error estiamtes and the proposed methods.
+  (not only  planar and merging spherical interfaces)
+  can be easily studied by the error estimates and the proposed methods.
   The error study of
-  more realistic systems requires the error estiamtes of the long-range
-  algoritms, and careful comparisons with the short-range error.
+  more realistic systems requires the error estimates of the long-range
+  algorithms, and careful comparisons with the short-range error.
   Since the present paper is focusing on the short-range

### 2012-04-25 longRange.hetero/publish/main.tex
using the concept of testing particle.

@@
 composed by $N$ charged particles located at $\v r_1, \v r_2, \cdots,
-\v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.  We study
-the force error of an arbitrary charge $i$ by calculating the
-difference between the exact force and calculated force exerting on
-the charge $i$, which is called the \emph{error force}
-\cite{wang2012} and denoted by $\Delta \v F(\v r_i)$.
-% and is denoted by
-% $\Delta \v F(\v r_i) = \v F(\v r_i) - \tilde{\v F}(\v r_i)$.
+\v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.
+We study the force of a testing particle located at $\v r$, which
+feels interactions from all charges $q_1, q_2, \cdots, q_N$
+in the system, and does not
+exert force on them.
+The \emph{error force} is defined by the difference between
+the exact force and the calculated
+force on the testing particle
+\cite{wang2012}, and is denoted by $\Delta \v F(\v r)$.
 The magnitude of the force computation error 
-% error of the force computation
 is defined by the \emph{root mean square (RMS)} \emph{error}, which is
 the square root of the second moment of the error force: $\mathcal
-E(\v r_i) = \sqrt{\langle\vert\Delta\v F(\v r_i)\vert^2\rangle}$.  The
+E(\v r) = \sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$.  The
 notation $\langle\cdot\rangle$ means ensemble average.  We also
 estimate the the ensemble average of the error force (also called
-\emph{mean error force}), namely $\langle\Delta\v F(\v r_i)\rangle$,
+\emph{mean error force}), namely $\langle\Delta\v F(\v r)\rangle$,
 which plays an important role in the error analysis of the
@@
   % n_1 \v a_1 + n_2 \v a_2 + n_3 \v a_3$, $n_\alpha\in\mathbb Z$.
-  If the error force of an arbitrary particle $i$ is
+  If the error force of the testing particle with charge $q$ has the form:
   \begin{align}\label{eqn:thm-error-force}
-    \Delta \v F(\v r_i) =
+    \Delta \v F(\v r) =
     % \sum^\ast_{\v n}
-    \sum_{j=1}^N\,q_iq_j \v K(\v r_i, \v r_j),
+    q\sum_{j=1}^N\,q_j \v K(\v r, \v r_j),
   \end{align}
@@
   \begin{align}\label{eqn:thm-meanf}
-    \langle\Delta\v F(\v r_i)\rangle
-    =q_i\, \int_{\mathbb R^3}\v K (\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r',
+    \langle\Delta\v F(\v r)\rangle
+    =q\, \int_{\mathbb R^3}\v K (\v r,\v r')\,\rho_q(\v r')\,\d d\v r',
   \end{align}
@@
   \begin{align}\nonumber
-    \mathcal E^2 (\v r_i) 
+    \mathcal E^2 (\v r) 
     = &\,
-    q_i^2\,\int_{\mathbb R^3}\vert\v K(\v r_i,\v r')\vert^2\,\rho_{q^2} (\v r')\,\d d\v r' + 
-    q_i^2\,
-    \big[
-    \int_{\mathbb R^3}\v K(\v r_i,\v r')\,\rho_{q}(\v r')\,\d d\v r'
+    q^2\,\int_{\mathbb R^3}\vert\v K(\v r,\v r')\vert^2\,\rho_{q^2} (\v r')\,\d d\v r' + 
+    q^2\,
+    \big[
+    \int_{\mathbb R^3}\v K(\v r,\v r')\,\rho_{q}(\v r')\,\d d\v r'
     \,\big]^2
@@
     &+
-    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i,\v r')\cdot
-    \v K(\v r_i,\v r'')\,
+    q^2\,\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r,\v r')\cdot
+    \v K(\v r,\v r'')\,
     C_{q^2}(\v r', \v r'')\,
@@
   \begin{align*}
-    \langle\Delta\v F(\v r_i)\rangle
+    \langle\Delta\v F(\v r)\rangle
     &=
-    q_i\bigg\langle \sum_{j=1}^Nq_j\v K(\v r_i,\v r_j)\bigg\rangle\\
+    q\bigg\langle \sum_{j=1}^Nq_j\v K(\v r,\v r_j)\bigg\rangle\\
     &=
-    q_i\int_{\mathbb R^3}\v K(\v r_i, \v r')
+    q\int_{\mathbb R^3}\v K(\v r, \v r')
     \bigg\langle \sum_{j=1}^Nq_j\delta (\v r' -\v r_j)\bigg\rangle
@@
     &= 
-    q_i\,\int\v K(\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r'.
+    q\,\int_{\mathbb R^3}\v K(\v r,\v r')\,\rho_q(\v r')\,\d d\v r'.
   \end{align*}
@@
   \begin{align} \nonumber
-    \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
+    \langle\vert\Delta\v F(\v r)\vert^2\rangle
     =\,&
-    q_i^2\bigg\langle\sum_{j,k}
-    q_jq_k\v K(\v r_i, \v r_j)\cdot\v K(\v r_i, \v r_k)\bigg\rangle \\ \nonumber
+    q^2\bigg\langle\sum_{j,k}
+    q_jq_k\v K(\v r, \v r_j)\cdot\v K(\v r, \v r_k)\bigg\rangle \\ \nonumber
     =\,&
-    q_i^2\bigg\langle\sum_{j=1}^N
-    q_j^2\vert\v K(\v r_i, \v r_j)\vert^2
+    q^2\bigg\langle\sum_{j=1}^N
+    q_j^2\vert\v K(\v r, \v r_j)\vert^2
     \bigg\rangle +
-    q_i^2\bigg\langle\sum_{j\neq k}
-    q_jq_k \v K(\v r_i, \v r_j)\cdot\v K(\v r_i, \v r_k)
+    q^2\bigg\langle\sum_{j\neq k}
+    q_jq_k \v K(\v r, \v r_j)\cdot\v K(\v r, \v r_k)
     \bigg\rangle \\ \nonumber
     =\,&
-    q_i^2\int_{\mathbb R^3}
-    \vert\v K(\v r_i, \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+    q^2\int_{\mathbb R^3}
+    \vert\v K(\v r, \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
     \\\label{eqn:prf-error-step3}
     & +
-    q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
+    q^2\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r , \v r')\cdot\v K(\v r , \v r'')\,
     \rho^{(2)}(\v r', \v r'')
@@
     =\,&
-    q_i^2\int_{\mathbb R^3}
-    \vert\v K(\v r_i , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+    q^2\int_{\mathbb R^3}
+    \vert\v K(\v r , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
     +
-    q_i^2
+    q^2
     \big[
     \int_{\mathbb R^3}
-    \v K(\v r_i , \v r')\rho_{q}(\v r')\,\d d\v r'
+    \v K(\v r , \v r')\rho_{q}(\v r')\,\d d\v r'
     \big]^2
@@
     & +
-    q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
+    q^2\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r , \v r')\cdot\v K(\v r , \v r'')\,
     C(\v r', \v r'')
@@
     % = \,&
-    % q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
-    % q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\
+    % q^2\,[(\v K)^2\ast\rho_{q^2}] (\v r) + 
+    % q^2\,[\v K\ast\rho_{q}]^2 (\v r) \\
     % &+
-    % q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
-    % \v K(\v r_i-\v r')\cdot
-    % \v K(\v r_i-\v r'')\,
+    % q^2\,\int_{\mathbb R^3\times\mathbb R^3}
+    % \v K(\v r-\v r')\cdot
+    % \v K(\v r-\v r'')\,
     % C_{q^2}(\v r', \v r'')\,
@@
     \label{eqn:cor-kernel}
-    \v K(\v r_i,\v r_j) = \v K(\v r_i - \v r_j),    
+    \v K(\v r,\v r') = \v K(\v r - \v r'),    
   \end{align}
@@
   \begin{align}\label{eqn:cor-meanf}
-    \langle\Delta\v F(\v r_i)\rangle
-    =q_i\, [\v K\ast\rho_q](\v r_i),
+    \langle\Delta\v F(\v r)\rangle
+    =q\, [\v K\ast\rho_q](\v r),
   \end{align}
@@
   \begin{align}\nonumber
-    \mathcal E (\v r_i) 
+    \mathcal E (\v r) 
     = &\,
-    q_i^2\,[(\v K)^2\ast\rho_{q^2}] (\v r_i) + 
-    q_i^2\,[\v K\ast\rho_{q}]^2 (\v r_i) \\\label{eqn:cor-error}
+    q^2\,[(\v K)^2\ast\rho_{q^2}] (\v r) + 
+    q^2\,[\v K\ast\rho_{q}]^2 (\v r) \\\label{eqn:cor-error}
     &+
-    q_i^2\,\int_{\mathbb R^3\times\mathbb R^3}
-    \v K(\v r_i-\v r')\cdot
-    \v K(\v r_i-\v r'')\,
-    C_{q^2}(\v r', \v r'')\,
+    q^2\,\int_{\mathbb R^3\times\mathbb R^3}
+    \v K(\v r-\v r')\cdot
+    \v K(\v r-\v r'')\,
+    C(\v r', \v r'')\,
     \d d\v r'\d d\v r'',
@@
   $\rho^{(2)}(\v r, \v r') = \rho_q(\v r)\rho_q(\v r')$ for convenience.
-  $C_{q^2}(\v r, \v r')$ defined in
+  $C(\v r, \v r')$ defined in
   Eqn.~\eqref{eqn:def-c} is the \emph{pairwise charge correlation function},
   which describes the strength of the correlation between  two
-  different charges. When they are independent, $C_{q^2}(\v r, \v r')$
-  vanishes, otherwise $C_{q^2}(\v r, \v r') \neq 0$.
+  different charges. When they are independent, $C(\v r, \v r')$
+  vanishes, otherwise $C(\v r, \v r') \neq 0$.
   Most of the error estimates assumed the independency of the
@@
   the error estimates Eqn.~\eqref{eqn:thm-meanf} and \eqref{eqn:thm-error}.
-  The function $\v K(\v r_i, \v r_j)$ is called \emph{the error force
+  The function $\v K(\v r, \v r')$ is called \emph{the error force
     kernel}.
@@
   \begin{align}\label{eqn:error-split}
-    \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
+    \langle\vert\Delta\v F(\v r)\vert^2\rangle
     =
-    \mathcal E^2_{\textrm{homo}}(\v r_i) +
-    \mathcal E^2_{\textrm{inhomo}}(\v r_i) +
-    \mathcal E_{\textrm{correlation}}(\v r_i).
+    \mathcal E^2_{\textrm{homo}}(\v r) +
+    \mathcal E^2_{\textrm{inhomo}}(\v r) +
+    \mathcal E_{\textrm{correlation}}(\v r).
   \end{align}
 \item
-  Without the property $\v K(\v r_i,\v r_j) = \v K(\v r_i - \v r_j)$,
-  theorem~\ref{thm:tmp1} calculate the homogeneity and inhomogeneity
-  error at a cost of $\mathcal O(N^2\log N)$, and correlation error
-  at a cost of $\mathcal O(N^3\log N)$.
+  Without the property $\v K(\v r,\v r') = \v K(\v r - \v r')$,
+  theorem~\ref{thm:tmp1} calculates the homogeneity and inhomogeneity
+  error at a cost of $\mathcal O(N^2)$, and correlation error
+  at a cost of $\mathcal O(N^3)$.
   By writing the error estimates in the convolution form in
@@
 Here the definition of the ``nearest neighbors'' is
-very flexible, basically it means the nearby neighbors that are
+very flexible. Basically it means the nearby neighbors that are
 strongly correlated. It could also be defined by the charges falling in some
@@
 \begin{align} \nonumber
-  \langle\vert\Delta\v F(\v r_i)\vert^2\rangle
+  \langle\vert\Delta\v F(\v r)\vert^2\rangle
   =\,&
-  q_i^2\int_{\mathbb R^3}
-  \vert\v K(\v r_i , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
+  q^2\int_{\mathbb R^3}
+  \vert\v K(\v r , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
   \\
   & +
-  q_i^2\int_{\mathbb R^3\times\mathbb R^3}
-  \v K(\v r_i , \v r')\cdot\v K(\v r_i , \v r'')\,
+  q^2\int_{\mathbb R^3\times\mathbb R^3}
+  \v K(\v r , \v r')\cdot\v K(\v r , \v r'')\,
   \rho^{(2)}(\v r', \v r'')
@@
 \begin{align}\label{eqn:fnc-correlation-water}
-  C_{q^2}(\v r', \v r'') \approx
+  C(\v r', \v r'') \approx
   \bigg\langle
@@
 \begin{align}
-  \mathcal E_{\textrm{correlation}}(\v r_i)
-  \approx q_i^2\sum_j\sum_{k\in\Omega_j}q_jq_k
+  \mathcal E_{\textrm{correlation}}(\v r)
+  \approx q^2\sum_j\sum_{k\in\Omega_j}q_jq_k
   \big\langle
-  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
+  \v K(\v r , \v r_j)\cdot\v K(\v r , \v r_k)
   \big\rangle_{\v r_j,\v r_k}
@@
 The quality of this approximation depends on how to define the
-``nearest neighbors''. In the system of liquid and gas, the
-correlation is only short-ranged, so it is possible to systematically
-improve the accuracy by considering more and more neighbors as long as
+``nearest neighbors''. In the systems
+of liquid and gas far from critical point,
+the correlation is only short-ranged, so charges are nearest neighbors when
+their correlations are considered important.
+It is also possible to systematically
+improve the approximation by considering more and more neighbors as long as
 the number of neighbors is small comparing with the size of the system.
@@
 bond and H-O-H angle are rigid, so the correlation within one molecule
-is very strong.  Therefore, in this case, we define the nearest neighbor by the
+is important.  Therefore, in this case, we define the nearest neighbor by the
 atoms within the same water molecule.  Denoting the index set of the oxygen
@@
 \begin{align}\nonumber
-  \mathcal E_{\textrm{correlation}}(\v r_i)
+  \mathcal E_{\textrm{correlation}}(\v r)
   = &\,
-  q_i^2\sum_{j\in\Omega_{\textrm{O}}}\sum_{k\in\Omega_j}q_jq_k
+  q^2\sum_{j\in\Omega_{\textrm{O}}}\sum_{k\in\Omega_j}q_jq_k
   \big\langle
-  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
+  \v K(\v r , \v r_j)\cdot\v K(\v r , \v r_k)
   \big\rangle_{\v r_j,\v r_k} \\ \nonumber
   &\,+ 
-  q_i^2\sum_{j\in\Omega_{\textrm{H}}}\sum_{k\in\Omega_j}q_jq_k
+  q^2\sum_{j\in\Omega_{\textrm{H}}}\sum_{k\in\Omega_j}q_jq_k
   \big\langle
-  \v K(\v r_i , \v r_j)\cdot\v K(\v r_i , \v r_k)
+  \v K(\v r , \v r_j)\cdot\v K(\v r , \v r_k)
   \big\rangle_{\v r_j,\v r_k} \\\nonumber
   = &\,
-  q_i^2
+  q^2
   \int_{\mathbb R^3}
-  \v K(\v r_i , \v r')\cdot
+  \v K(\v r , \v r')\cdot
   2\big\langle
-  q_{\textrm{H}}\v K(\v r_i , \v r' + \v s_{\textrm{O}})
+  q_{\textrm{H}}\v K(\v r , \v r' + \v s_{\textrm{O}})
   \big\rangle\,
@@
   & \,+
-  q_i^2
+  q^2
   \int_{\mathbb R^3}
-  \v K(\v r_i , \v r')\cdot
+  \v K(\v r , \v r')\cdot
   \big\langle
-  q_{\textrm{O}}\v K(\v r_i , \v r' - \v s_{\textrm{O}})+
-  q_{\textrm{H}}\v K(\v r_i , \v r' + \v s_{\textrm{H}})
+  q_{\textrm{O}}\v K(\v r , \v r' - \v s_{\textrm{O}})+
+  q_{\textrm{H}}\v K(\v r , \v r' + \v s_{\textrm{H}})
   \big\rangle\,\rho_{\textrm{H}}(\v r')
@@
 If the error force kernel
-has the form $\v K(\v r_i , \v r_j) = \v K(\v r_i - \v r_j)$, 
+has the form $\v K(\v r , \v r') = \v K(\v r - \v r')$, 
 the integrals can be written in the convolution form and accelerated by the FFT.
@@
   \big\langle
-  q_{\textrm{H}}\v K(\v r_i - \v r' + \v s_{\textrm{O}})
+  q_{\textrm{H}}\v K(\v r - \v r' - \v s_{\textrm{O}})
   \big\rangle 
@@
   q_{\textrm{H}}\hat{\v K}(\v m)
-  e^{2\pi i\v m\cdot(\v r_i - \v r' + \v s_{\textrm{O}})} 
+  e^{2\pi i\v m\cdot(\v r - \v r' - \v s_{\textrm{O}})} 
   \bigg\rangle \\\nonumber
@@
   \langle
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}}
+  q_{\textrm{H}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}}
   \rangle\,
   \hat{\v K}(\v m)\,
-  e^{2\pi i\v m\cdot(\v r_i - \v r')},
+  e^{2\pi i\v m\cdot(\v r - \v r')},
 \end{align}
@@
   2\langle
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}}
+  q_{\textrm{H}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}}
   \rangle,\\
@@
   \langle
-  q_{\textrm{O}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}} +
-  q_{\textrm{H}}\,e^{2\pi i\v m\cdot\v s_{\textrm{H}}}
+  q_{\textrm{O}}\,e^{2\pi i\v m\cdot\v s_{\textrm{O}}} +
+  q_{\textrm{H}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{H}}}
   \rangle,
@@
 \begin{align}\nonumber
-  \mathcal E_{\textrm{correlation}}(\v r_i)
+  \mathcal E_{\textrm{correlation}}(\v r)
   =&\,
-  q_i^2
+  q^2
   \int_{\mathbb R^3}
-  \v K(\v r_i - \v r')\cdot
-  (\hat T_{\textrm{O}}\hat{\v K})^{\vee}(\v r_i - \v r')
+  \v K(\v r - \v r')\cdot
+  (\hat T_{\textrm{O}}\hat{\v K})^{\vee}(\v r - \v r')
   \,\rho_{\textrm{O}}(\v r')
@@
   & \,+
-  q_i^2
+  q^2
   \int_{\mathbb R^3}
-  \v K(\v r_i - \v r')\cdot
-  (\hat T_{\textrm{H}}\hat{\v K})^{\vee}(\v r_i - \v r')
+  \v K(\v r - \v r')\cdot
+  (\hat T_{\textrm{H}}\hat{\v K})^{\vee}(\v r - \v r')
   \,\rho_{\textrm{H}}(\v r')
@@
 \begin{align}\nonumber
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)
   =\;&
-  q_i
+  q
   \sum_{
@@
   \v g(\v m)\,
-  A(\v m, \v r_i)\,
-  e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+  A(\v m, \v r)\,
+  e^{2\pi i\v m\cdot \v r}
+  \sum_{j}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
   & +\,
-  q_i
+  q
   \sum_{
@@
   \v g(\v m)\,
-  e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:ik.error.force.1}
+  e^{2\pi i\v m\cdot \v r}
+  \sum_{j}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:ik.error.force.1}
   & +\,
-  q_i
+  q
   \sum_{
@@
   \big[
-  A(\v m, \v r_i) +
-  A(\v m, -\v r_i)
+  A(\v m, \v r) +
+  A(\v m, -\v r)
   \big].
@@
   \v g(\v m)\,
-  A(\v m, \v r_i)\,
-  e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\label{eqn:ik.error.force}
+  A(\v m, \v r)\,
+  e^{2\pi i\v m\cdot \v r}
+  \sum_{j}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\label{eqn:ik.error.force}
   & +\,
-  q_i
+  q
   \sum_{
@@
   \v g(\v m)\,
-  e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}
+  e^{2\pi i\v m\cdot \v r}
+  \sum_{j}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}
 \end{align}
@@
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)
   \big\rangle
   & \approx
-  - 2 q_i
+  - 2 q
   \big[
@@
   \ast\rho_q\,
-  \big] (\v r_i),
+  \big] (\v r),
 \end{align}
@@
   \big\langle
-  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)\vert^2
   \big\rangle
   \approx&\, 
-  2q_i^2
+  2q^2
   \big[
@@
   \ast \rho_{q^2}
-  \,\big] (\v r_i)\\\nonumber
+  \,\big] (\v r)\\\nonumber
   &\,+
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{q^2}\,
-  \big] (\v r_i) \\\label{eqn:ik.error}
+  \big] (\v r) \\\label{eqn:ik.error}
   &\,+
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)
   \big\rangle^2.
@@
 \begin{align}\nonumber
-  \mathcal E^{\textrm{ik}}_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ik}}_{\textrm{correlation}}(\v r)
   =\,&
-  q_i^2
+  q^2
   \big[\,
@@
   \ast \rho_{\textrm{O}}
-  \,\big] (\v r_i) \\\nonumber
+  \,\big] (\v r) \\\nonumber
   \,&+
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{\textrm{O}}\,
-  \big] (\v r_i) \\\nonumber
+  \big] (\v r) \\\nonumber
   \,&+
-  q_i^2
+  q^2
   \big[\,
@@
   \ast \rho_{\textrm{H}}
-  \,\big] (\v r_i) \\
+  \,\big] (\v r) \\
   \,&+
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{\textrm{H}}\,
-  \big] (\v r_i).
+  \big] (\v r).
 \end{align}
@@
 \begin{align}\nonumber
-  \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r)
   % =\;&
-  % q_i
+  % q
   % \sum_{
@@
   % -2f(\v m)\,
-  % \nabla_{\v r_i}
-  % e^{2\pi i\v m\cdot \v r_i}
+  % \nabla_{\v r}
+  % e^{2\pi i\v m\cdot \v r}
   % \sum_{j\neq i}q_j\,
@@
   % & +\,
-  % q_i
+  % q
   % \sum_{
@@
   % -2f(\v m)\,
-  % \nabla_{\v r_i}
-  % [A(\v m, \v r_i)\,
-  % e^{2\pi i\v m\cdot \v r_i} ]
+  % \nabla_{\v r}
+  % [A(\v m, \v r)\,
+  % e^{2\pi i\v m\cdot \v r} ]
   % \sum_{j\neq i}q_j\,
@@
   % & +\,
-  % q^2_i
+  % q^2
   % \sum_{
@@
   % -2f(\v m)\,
-  % A(-\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i} \nabla_{\v r_i}e^{2\pi i\v m\cdot\v r_i} \\\nonumber
+  % A(-\v m, \v r)\,e^{2\pi i\v m\cdot \v r} \nabla_{\v r}e^{2\pi i\v m\cdot\v r} \\\nonumber
   % & +\,
-  % q^2_i
+  % q^2
   % \sum_{
@@
   % -2f(\v m)\,
-  % e^{-2\pi i\v m\cdot \v r_i}
-  % \nabla_{\v r_i} [\,A(\v m, \v r_i) \,e^{2\pi i\v m\cdot\v r_i}\,]  \\\nonumber
+  % e^{-2\pi i\v m\cdot \v r}
+  % \nabla_{\v r} [\,A(\v m, \v r) \,e^{2\pi i\v m\cdot\v r}\,]  \\\nonumber
   =&\,
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\\\nonumber
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)\\\nonumber
   & +\,
-  q_i
+  q
   \sum_{
@@
   -2f(\v m)\,
-  \v B(\v m, \v r_i)\,e^{2\pi i\v m\cdot \v r_i}
-  \sum_{j\neq i}q_j\,
+  \v B(\v m, \v r)\,e^{2\pi i\v m\cdot \v r}
+  \sum_{j}q_j\,
   e^{-2\pi i\v m\cdot\v r_j} \\\label{eqn:ana.error.force}
   & +\,
-  q^2_i
+  q^2
   \sum_{
@@
     \end{subarray}}
-  -2f(\v m)\,\v B(\v m, \v r_i) 
+  -2f(\v m)\,\v B(\v m, \v r) 
 \end{align}
@@
 \begin{align}\label{eqn:ana.meanf}
-  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\rangle
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r)\rangle
   \approx
-  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\rangle.
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)\rangle.
 \end{align}
@@
   \big\langle
-  \vert \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\vert^2
+  \vert \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r)\vert^2
   \big\rangle
   \approx&\,
-  q_i^2
+  q^2
   \big[
@@
   \ast \rho_{q^2}
-  \,\big] (\v r_i) \\\nonumber
+  \,\big] (\v r) \\\nonumber
   & +\,
-  q_i^2
+  q^2
   \big[
@@
   \big]
-  (\v r_i) \\ \nonumber
+  (\v r) \\ \nonumber
   & +\,
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{q^2}\,
-  \big] (\v r_i) \\\label{eqn:ana.error}
+  \big] (\v r) \\\label{eqn:ana.error}
   & +\,
-  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r)\big\rangle ^2
   % &+\,
-  % q_i^4 \sum_{\alpha}\sum_{l\neq 0}
+  % q^4 \sum_{\alpha}\sum_{l\neq 0}
   % 4\pi^2l^2K_\alpha^2\vert\v a_{\alpha}^\ast\vert^2[C_{\alpha,l}^{\textrm{self}}]^2 .
@@
 \begin{align}\nonumber
-  \mathcal E^{\textrm{ana}}_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ana}}_{\textrm{correlation}}(\v r)
   =\,&
-  q_i^2
+  q^2
   \big[\,
@@
 \begin{align}\label{eqn:ik-st-error-force}
-  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r_i)
-  \approx -2q_i
+  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r)
+  \approx -2q
   \sum_jq_j
@@
     \end{subarray}}
-  g(\v m) Z_{\alpha,l}(\v m)\,e^{2\pi i\v m\cdot(\v r_i-\v r_j)}.
+  g(\v m) Z_{\alpha,l}(\v m)\,e^{2\pi i\v m\cdot(\v r-\v r_j)}.
 \end{align}
@@
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)
   \big\rangle
   & \approx
-  - 2 q_i
+  - 2 q
   \big[
@@
   \big\langle
-  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)\vert^2
   \big\rangle
   \approx&\,
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{q^2}\,
-  \big] (\v r_i) +
+  \big] (\v r) +
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)
   \big\rangle^2.
@@
 The RMS error is improved, because
-$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2\big\rangle -
-\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2\big\rangle=
-2q_i^2
+$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)\vert^2\big\rangle -
+\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)\vert^2\big\rangle=
+2q^2
 \big[\,
@@
 \ast \rho_{q^2}
-\,\big] (\v r_i) \geq 0$.
+\,\big] (\v r) \geq 0$.
 The nearest neighbor approximation to the correlation error is:
 \begin{align}\nonumber
-  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r)
   =\,&
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{\textrm{O}}\,
-  \big] (\v r_i) \\\nonumber
+  \big] (\v r) \\\nonumber
   \,&+
-  4q_i^2\,
+  4q^2\,
   \big[
@@
 \begin{align}\label{eqn:ana-st-error-force}
-  \Delta\v F^{\textrm{ana,st}}_{\textrm{rec}}(\v r_i)
+  \Delta\v F^{\textrm{ana,st}}_{\textrm{rec}}(\v r)
   &\approx
-  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r_i)\\
+  \Delta\v F^{\textrm{ik,st}}_{\textrm{rec}}(\v r)\\
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r)
   \big\rangle
@@
   \big\langle
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)
   \big\rangle\\
   \big\langle
-  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)\vert^2
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r)\vert^2
   \big\rangle
@@
   \big\langle
-  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r_i)\vert^2
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik,st}}(\v r)\vert^2
   \big\rangle\\
-  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ik,st}}_{\textrm{correlation}}(\v r)
   &\approx
-  \mathcal E^{\textrm{ana,st}}_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ana,st}}_{\textrm{correlation}}(\v r)
 \end{align}
@@
 difficult to see 
-$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\vert^2\big\rangle -
-\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r_i)\vert^2\big\rangle
+$\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r)\vert^2\big\rangle -
+\big\langle\vert\Delta\v F_{\textrm{rec}}^{\textrm{ana,st}}(\v r)\vert^2\big\rangle
 \geq 0$.
@@
 \begin{align}
-  \langle\Delta\v F^{\textrm{x}}(\v r_i) \rangle
+  \langle\Delta\v F^{\textrm{x}}(\v r) \rangle
   &=
-  \langle\Delta\v F_{\textrm{dir}}(\v r_i) \rangle +
-  \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) \rangle,
+  \langle\Delta\v F_{\textrm{dir}}(\v r) \rangle +
+  \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) \rangle,
 \end{align}
@@
 \begin{align}\nonumber
-  \langle\,\vert\Delta\v F^{\textrm{x}}(\v r_i)\vert^2\rangle
+  \langle\,\vert\Delta\v F^{\textrm{x}}(\v r)\vert^2\rangle
   = \,&
   \langle\,\vert
-  \Delta\v F_{\textrm{dir}}(\v r_i) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) 
+  \Delta\v F_{\textrm{dir}}(\v r) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) 
   \vert^2 \rangle \\\nonumber
   = \,&
-  \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle +
-  \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\vert^2\rangle +
-  2\,\langle\Delta\v F_{\textrm{dir}}(\v r_i)\rangle
-  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\rangle \\
+  \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle +
+  \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\vert^2\rangle +
+  2\,\langle\Delta\v F_{\textrm{dir}}(\v r)\rangle
+  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\rangle \\
   \label{eqn:error-total}
   &
-  + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
-\end{align}
-Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i), \Delta\v
-F^{\textrm{x}}_{\textrm{rec}}(\v r_i))$ denotes the correlation of
-$\Delta\v F_{\textrm{dir}}(\v r_i)$ and $\Delta\v
-F^{\textrm{x}}_{\textrm{rec}}(\v r_i)$:
+  + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
+\end{align}
+Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r), \Delta\v
+F^{\textrm{x}}_{\textrm{rec}}(\v r))$ denotes the correlation of
+$\Delta\v F_{\textrm{dir}}(\v r)$ and $\Delta\v
+F^{\textrm{x}}_{\textrm{rec}}(\v r)$:
 \begin{align}\label{eqn:error-total-corr}
-  \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
+  \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
   & =
   \langle
-  \Delta\v F_{\textrm{dir}}(\v r_i)\cdot
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
+  \Delta\v F_{\textrm{dir}}(\v r)\cdot
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
   \rangle -
   \langle
-  \Delta\v F_{\textrm{dir}}(\v r_i)
+  \Delta\v F_{\textrm{dir}}(\v r)
   \rangle\cdot
   \langle
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
   \rangle.
@@
 In Eqn.~\eqref{eqn:error-total}, the estimates of errors
-$\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle $,
+$\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle $,
 $\langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
-r_i)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
-r_i)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
-r_i)\rangle $ have been established.
+r)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
+r)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
+r)\rangle $ have been established.
 In practice, the correlation~\eqref{eqn:error-total-corr}
@@
 \begin{align}
-  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j)
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r')
   =
@@
     \end{subarray}}
-  [\,A(\v m, \v r_i) + A(\v m,-\v r_j)\,]
-  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+  [\,A(\v m, \v r) + A(\v m,-\v r')\,]
+  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r-\v r')}
 \end{align}
@@
   \label{eqn:ik.kernel.2}
-  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j)
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r')
   =
@@
   \,(
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r'}
   - 2
@@
   Z_{\alpha,l}(\v m)
-  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+  \v g(\v m)\,e^{-2\pi i\v m\cdot(\v r-\v r')}
 \end{align}
@@
 \begin{align}\nonumber
-  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r_i)\rangle
+  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r)\rangle
   =\,&
-  q_i\, \int_{\mathbb R^3}
-  \v K^{\textrm{ik}}_{\textrm{rec}} (\v r_i,\v r')\,\rho_q(\v r')\,\d d\v r'\\
+  q\, \int_{\mathbb R^3}
+  \v K^{\textrm{ik}}_{\textrm{rec}} (\v r,\v r')\,\rho_q(\v r')\,\d d\v r'\\
   \approx\,&
-  q_i
+  q
   \big\{
@@
   \sum_{\alpha}\sum_{l\neq 0}
-  (e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}   - 2 )
+  (e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r}   - 2 )
   \v G_{\alpha,l}
@@
   \ast\rho_q\,
-  \big\} (\v r_i),
+  \big\} (\v r),
 \end{align}
 Further neglecting the
-high-wave-number term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}$, we reach:
+high-wave-number term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r}$, we reach:
 \begin{align}
-  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r_i)\rangle
+  \langle\Delta\v F^{\textrm{ik}}_{\textrm{rec}}(\v r)\rangle
   \approx\,&
-  -2q_i
+  -2q
   \big[
@@
   \ast\rho_q\,
-  \big] (\v r_i).
+  \big] (\v r).
 \end{align}
@@
 \begin{align}\nonumber
-  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r_j)\vert^2
+  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r,\v r')\vert^2
   =\,&
@@
   \,(
-  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r'}
   - 2
@@
   \,(
-  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
-  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r} +
+  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r'}
   - 2
@@
   \times
-  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
+  e^{-2\pi i(\v m-\v n)\cdot(\v r-\v r')}
 \end{align}
@@
 $  (
-e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r} +
+e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r'}
 - 2
@@
 \,(
-e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
-e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r} +
+e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r'}
 - 2
@@
   &(
-  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r'}
   - 2
@@
   = \,&
-  e^{2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r_i} +
-  e^{-2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r_j} \\
+  e^{2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r} +
+  e^{-2\pi i(l_1K_\alpha\v a^\ast_\alpha - l_2K_\beta\v a^\ast_\beta)\cdot\v r'} \\
   \label{eqn:ik.cal.tmp1}
   &-2(
-  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r'}
   ) 
   -2(
-  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_j}
+  e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r'}
   ) + 4
@@
 are not high-wave-number terms only when $l_1 = l_2$ and $\alpha=\beta$.
-The third and fourth terms are definitely high-wave-number terms.
+The third and fourth terms are always high-wave-number terms,
+because $l_1\neq 0$ and $l_2\neq 0$.
 Therefore, we have the error estimate
@@
 \begin{align}\nonumber
-  [\mathcal E^{\textrm{ik}}_{\textrm{homo}}(\v r_i)]^2
+  [\mathcal E^{\textrm{ik}}_{\textrm{homo}}(\v r)]^2
   = \,&
   \int
-  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r')\vert^2
+  \vert\v K^{\textrm{ik}}_{\textrm{rec}}(\v r,\v r')\vert^2
   \rho_{q^2}(\v r')\,\d d\v r' \\
   \approx\,&  
-  2q_i^2
+  2q^2
   \big[\,
@@
   \ast \rho_{q^2}
-  \,\big] (\v r_i)
+  \,\big] (\v r)
   +
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \ast \rho_{q^2}\,
-  \big] (\v r_i) 
+  \big] (\v r) 
 \end{align}
@@
   \big\langle
-  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j+\v s)
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r'+\v s)
   \big\rangle
@@
   (
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r_j + \v s)}
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r' + \v s)}
   - 2
   )\,
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j -\v s)}
+  e^{-2\pi i\v m\cdot(\v r-\v r' -\v s)}
   \big\rangle \\
@@
   (
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} 
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
   - 2
@@
   \hat T_s(\v m)
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}  
+  e^{-2\pi i\v m\cdot(\v r-\v r')}  
 \end{align}
@@
 \begin{align}\nonumber
-  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r_j)\cdot
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r,\v r')\cdot
   \big\langle
-  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r_j+\v s)
+  \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r'+\v s)
   \big\rangle
@@
   \,(
-  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i}
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r}
   - 2
@@
   \times
-  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
-\end{align}
-The first term in Eqn.~\eqref{eqn:c-error-1} yields
+  e^{-2\pi i(\v m-\v n)\cdot(\v r-\v r')}
+\end{align}
+Inserting it into Eqn.~\eqref{eqn:c-error-1}, also neglect the high
+frequency terms yields
 % \begin{align}
-%   q_i^2 q_{\textrm{H}}
+%   q^2 q_{\textrm{H}}
 %   \int
-%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i,\v r)\cdot
+%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r,\v r)\cdot
 %   \big\langle
-%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r_i, \v r+\v s)
+%   \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r+\v s)
 %   \big\rangle\,\rho_{\textrm{O}}(\v r)\,
@@
 \begin{align}\nonumber
-  \mathcal E_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ik}}_{\textrm{correlation}}(\v r)
   =\,&
-  q_i^2
+  q^2
   \big[\,
@@
   \ast \rho_{\textrm{H}}\,
-  \big] (\v r_i) 
+  \big] (\v r) 
 \end{align}
@@
 \begin{align}
-  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j)
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r, \v r')
   =
@@
   \{
-  [A(\v m, \v r_i) + A(\v m,-\v r_j)\,]
+  [A(\v m, \v r) + A(\v m,-\v r')\,]
   \v g(\v m) -
-  2\v B(\v m,\v r_i) f(\v m)
+  2\v B(\v m,\v r) f(\v m)
   \}
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}
+  e^{-2\pi i\v m\cdot(\v r-\v r')}
 \end{align}
@@
 \begin{align}\nonumber
-  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j)
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r, \v r')
   =\,&
@@
   \,&
-  - 4\pi i l K_\alpha\v a_\alpha^\ast e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  - 4\pi i l K_\alpha\v a_\alpha^\ast e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r}
   f(\v m)
@@
   Z_{\alpha,l}(\v m)
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}  
+  e^{-2\pi i\v m\cdot(\v r-\v r')}  
 \end{align}
@@
 \begin{align}
-  \langle\Delta\v F^{\textrm{ana}}_{\textrm{rec}}(\v r_i)\rangle
+  \langle\Delta\v F^{\textrm{ana}}_{\textrm{rec}}(\v r)\rangle
   \approx\,&
-  -2q_i
+  -2q
   \big[
@@
 \begin{align}
-  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i,\v r_j)\vert^2
+  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r,\v r')\vert^2
   =\,&
@@
   \v g(\v m)
-  - 4\pi i l_1 K_\alpha\v a_\alpha^\ast e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r_i}
+  - 4\pi i l_1 K_\alpha\v a_\alpha^\ast e^{2\pi i l_1 K_\alpha\v a^\ast_\alpha\cdot \v r}
   f(\v m)
@@
   \,(
-  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i} +
-  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_j}
+  e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r} +
+  e^{-2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r'}
   - 2
@@
   \v g(\v n)
-  - 4\pi i l_2 K_\beta\v a_\beta^\ast e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r_i}
+  - 4\pi i l_2 K_\beta\v a_\beta^\ast e^{2\pi i l_2 K_\beta\v a^\ast_\beta\cdot \v r}
   f(\v n)
@@
   Z_{\alpha,l_1}(\v m)Z_{\beta,l_2}(\v n)
-  e^{-2\pi i(\v m-\v n)\cdot(\v r_i-\v r_j)}
+  e^{-2\pi i(\v m-\v n)\cdot(\v r-\v r')}
 \end{align}
@@
 \begin{align}\nonumber
-  [\mathcal E^{\textrm{ana}}_{\textrm{homo}}(\v r_i)]^2
+  [\mathcal E^{\textrm{ana}}_{\textrm{homo}}(\v r)]^2
   = \,&
   \int
-  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i,\v r')\vert^2
+  \vert\v K^{\textrm{ana}}_{\textrm{rec}}(\v r,\v r')\vert^2
   \rho_{q^2}(\v r')\,\d d\v r' \\\nonumber
   \approx\,&  
-  q_i^2
+  q^2
   \big[\,
@@
   \ast \rho_{q^2}
-  \,\big] (\v r_i) +
-  q_i^2
+  \,\big] (\v r) +
+  q^2
   \big[\,
@@
   \ast \rho_{q^2}
-  \,\big] (\v r_i) \\
+  \,\big] (\v r) \\
   \,&+
-  4q_i^2\,
+  4q^2\,
   \big[
@@
   \big\langle
-  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j + \v s)
+  \v K^{\textrm{ana}}_{\textrm{rec}}(\v r, \v r' + \v s)
   \big\rangle
@@
   \,(
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} +
-  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r_j + \v s)}
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} +
+  e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot (\v r' + \v s)}
   - 2
@@
   Z_{\alpha,l}(\v m)
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j - \v s)}
+  e^{-2\pi i\v m\cdot(\v r-\v r' - \v s)}
   \bigg\rangle \\\nonumber
@@
   \,(
-  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r_i} 
+  e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
   - 2
@@
   Z_{\alpha,l}(\v m)
-  e^{-2\pi i\v m\cdot(\v r_i-\v r_j)}.
+  e^{-2\pi i\v m\cdot(\v r-\v r')}.
 \end{align}
@@
 $\big\langle
-\v K^{\textrm{ana}}_{\textrm{rec}}(\v r_i, \v r_j + \v s)
+\v K^{\textrm{ana}}_{\textrm{rec}}(\v r, \v r' + \v s)
 \big\rangle$
@@
 \begin{align}\nonumber
-  \mathcal E_{\textrm{correlation}}(\v r_i)
+  \mathcal E^{\textrm{ana}}_{\textrm{correlation}}(\v r)
   =\,&
-  q_i^2
+  q^2
   \big[\,

### 2012-04-25 longRange.hetero/publish/main.tex
fix bugs

@@
 \documentclass[aps,pre,preprint,unsortedaddress]{revtex4}
-% \documentclass[aps,pre,unsortedaddress]{revtex4-1}
+% \documentclass[aps,jcp,unsortedaddress]{revtex4-1}
 %\documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 \begin{abstract}
-
+  In this work, we develop the accurate error estimates for
+  some state-of-art algorithms of long-range electrostatic interaction
+  in inhomogeneous and correlated molecular systems.
+  They are the Ewald summation, the smooth particle mesh Ewald (SPME) and
+  the staggered mesh Ewald method. Two branches of force computation, namely
+  the ik- and analytical differentiation, are considered. All the
+  estimates are developed by proposing a more general framework:
+  if the error force is of pairwise form,
+  then the root mean square force error is composed by three additive parts,
+  the homogeneity error, the inhomogeneity error and the correlation
+  error. Computationally scalable estimates (estimating the errors
+  at the cost $\mathcal O(N\log N)$) are developed for all the considered
+  algorithms.
+  The effectiveness of the proposed estimates and the important role of
+  the correlation error are carefully checked and demonstrated by
+  example systems.
 \end{abstract}
@@
 important topic in the molecular simulations.  Due to the very slow
-decay of the interaction with respect to the distance between charges,
-the short-range fast algorithms (the cell list and neighbor list
+decay of the interaction strength with respect to the distance between charges,
+the typical short-range fast algorithms (cut-off + neighbor list
 algorithms) do not work, and the
 energy of the system is only conditionally convergent.  One of the
-first algorithms handling this problem was the Ewald summation, dating
-back to the 1920's~\cite{ewald1921die}.  However, it has been shown that
+first algorithms handling this problem is the Ewald summation, dating
+back to the 1920's~\cite{ewald1921die}.  It has been shown that
 with a careful tuning of working parameters, the optimal computational
-cost of the Ewald summation is of $\mathcal
+cost of the Ewald summation is  $\mathcal
 O(N^{3/2})$~\cite{perram1988asc}, which is not feasible for modern
@@
 was applied to SPME
-(called staggered mesh Ewald)~\cite{cerutti2009staggered} and P3M
-(called interlaced P3M)~\cite{neelov2010interlaced}, and was showed to
-improve the accuracy of these algorithms.
+(called the staggered mesh Ewald)~\cite{cerutti2009staggered} and P3M
+(called the interlaced P3M)~\cite{neelov2010interlaced}, and was showed to
+improve the accuracy of these algorithms greatly.
 In this paper, we focus on the Ewald summation, the SPME and
 the staggered mesh Ewald methods. The Ewald summation is the starting
-point of all the mentioned fast algorithm. SPME
+point of all the mentioned fast algorithm. The SPME
 is the one of the most popular long-range algorithms among
@@
 automatically determine the nearly optimal combination of parameters,
-in the sense that it is the fastest one given a demanding
+in the sense that it is the fastest one satisfying a demanding
 accuracy~\cite{wang2010optimizing}. However, so far, all error
@@
 fulfilled in most molecular
-systems of practical interest.  For example, the lipid biomembrane
-solving in water: the carbon chains of the lipids carry no charge, and
-the charges are correlated by the covalent bonds, the van der Waals
+systems of practical interest.  For example, the lipid bilayer membrane
+solving in water: the hydrophobic tail(s) of the lipids carry no charge, and
+the charges in the system
+are correlated by the covalent bonds, the van der Waals
 interaction, the hydrogen bonding network, etc..  Therefore, the current
-error estimates may be problematic, or even not applicable.  A lot of
+error estimates may be problematic, or even not applicable.  Several
 research have shown that due to the correlation of charges, the error estimates
@@
 dynamics (MD) simulation.  Firstly, a general error estimate
-frame work for the pairwise interaction is set up. We prove that the
+framework for the pairwise interaction is set up. We prove that the
 error is decomposed into three additive parts: the homogeneity error,
 the inhomogeneity error and the correlation error~\cite{wang2012}.
-These error estimates are only of theoretical interest, and
-not applicable, because the computational costs of the error estimates
-are $\mathcal O(N^2\log N)$ (homogeneity and inhomogeneity error)
-and $\mathcal O(N^3\log N)$ (correlation error).
-If the error force has a special form so that the error estimates
-can be written as convolutions, the computational costs
-are reduced to $\mathcal O(N\log N)$ and 
-$\mathcal O(N^2\log N)$, respectively.
-The computational cost of the correlation error is further
-reduce to $\mathcal O(N\log N)$ by the nearest neighbor approximation
-technique, which assume the system is only short-range correlated. This
-is the case for most the liquid and gas system far from critical point.
+% These error estimates are only of theoretical interest, and
+% not applicable, because the computational costs of the error estimates
+% are $\mathcal O(N^2)$ (homogeneity and inhomogeneity error)
+% and $\mathcal O(N^3)$ (correlation error).
+% If the error force has a special form so that the error estimates
+% can be written as convolutions, the computational costs
+% are reduced to $\mathcal O(N\log N)$ and 
+% $\mathcal O(N^2\log N)$, respectively.
+The computational cost of the homogeneity and inhomogeneity
+error is $\mathcal O(N\log N)$ when the error force kernel is
+of convolution form.
+The  correlation error can also be
+estimated at a cost of $\mathcal O(N\log N)$
+by the nearest neighbor approximation
+technique, which assume the error  is dominated by  short-range correlation.
+This
+is the case for most the liquid and gas systems far from critical point.
+Generally speaking,
+when the error force can be written as a pairwise form, 
+all estimate are derived easily under this framework.
 Following this framework, we
@@
 of the homogeneity and inhomogeneous errors are tested by two
-randomly distributed inhomogeneous charges systems
-(i.e. the charges are not correlated), and is proved to
+randomly distributed inhomogeneous charges systems,
+% (i.e. the charges are not correlated),
+and is proved to
 be very sharp.
@@
 E(\v r) = \sqrt{\langle\vert\Delta\v F(\v r)\vert^2\rangle}$.  The
-notation $\langle\cdot\rangle$ means ensemble average.  We also
+notation $\langle\cdot\rangle$ means the ensemble average.  We also
 estimate the the ensemble average of the error force (also called
@@
   \begin{align}\nonumber
-    \mathcal E (\v r) 
+    \mathcal E^2 (\v r) 
     = &\,
@@
   however, this could be problematic in the strongly correlated
-  systems~\cite{deserno1998mue2, wang2010optimizing}.
+  systems~\cite{deserno1998mue2, wang2010optimizing, ballenegger2012convert}.
   Also see Sec.~\ref{sec:example3} for example.
@@
     kernel}.
-  By setting $q_i = q_j = 1$, the corollary~\ref{thm:tmp2} directly proves
+  By setting $q_i = q_j = 1$, the corollary~\ref{thm:tmp2} proves
   the error estimates for the short-range interaction
@@
   \begin{align}\label{eqn:error-split}
-    \langle\vert\Delta\v F(\v r)\vert^2\rangle
+    % \langle\vert\Delta\v F(\v r)\vert^2\rangle
+    \mathcal E^2(\v r)
     =
@@
 \item
-  Without the property $\v K(\v r,\v r') = \v K(\v r - \v r')$,
-  theorem~\ref{thm:tmp1} calculates the homogeneity and inhomogeneity
+  % Without the property $\v K(\v r,\v r') = \v K(\v r - \v r')$,
+  Theorem~\ref{thm:tmp1} calculates the homogeneity and inhomogeneity
   error at a cost of $\mathcal O(N^2)$, and correlation error
@@
   harmful to the calculation of the short-range interaction
-  in inhomogeneity systems~\cite{wang2012}.
+  in inhomogeneous systems~\cite{wang2012}.
   In the case of the charged system, this
@@
 error}
-The full computation of the correlation error cost at least $\mathcal
+The full computation of the correlation error costs at least $\mathcal
 O(N^2\log N)$, which is still not applicable.
@@
 $\Omega_j = \{ \,k\,\vert\,
-\textrm{atom $k$ is the nearest neighbor of atom $j$} \,\}$,
+\textrm{atom $k$ is one of the nearest neighbors of atom $j$} \,\}$,
 % the set of the first neighbors of the $j$-th atom by $\Omega_j$,
@@
 $\alpha$.  The truncated reciprocal force acting on particle $i$ is
-\begin{align}\nonumber
+\begin{align}
+  % \nonumber
   \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
-  &= 
-  q_i 
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_\alpha\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  \v g(\v m) \,
-  S(-\v m)\,
-  e^{2\pi i\v m\cdot\v r_i}, \\\label{eqn:tmp8}
+  % &= 
+  % q_i 
+  % \sum_{
+  %   \begin{subarray}{c}
+  %     \vert m_\alpha\vert < K_\alpha/2\\
+  %     \v m\neq 0
+  %   \end{subarray}}
+  % \v g(\v m) \,
+  % S(-\v m)\,
+  % e^{2\pi i\v m\cdot\v r_i}, \\
+  \label{eqn:tmp8}
   &= 
@@
 \end{align}
-The error force of the ik-differentiation is therefore
-\begin{align}\nonumber
-  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)
-  =\;&
-  q
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  \v g(\v m)\,
-  A(\v m, \v r)\,
-  e^{2\pi i\v m\cdot \v r}
-  \sum_{j}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
-  & +\,
-  q
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  \v g(\v m)\,
-  e^{2\pi i\v m\cdot \v r}
-  \sum_{j}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:ik.error.force.1}
-  & +\,
-  q
-  \sum_{
-    \begin{subarray}{c}
-      \vert m_{\alpha}\vert < K_\alpha/2\\
-      \v m\neq 0
-    \end{subarray}}
-  \v g(\v m)\,
-  \big[
-  A(\v m, \v r) +
-  A(\v m, -\v r)
-  \big].
-\end{align}
-Due to the symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$,
-the last term in Eqn.~\eqref{eqn:ik.error.force.1},
-i.e. the ``self-interacting term'', is zero.
-Therefore,
+Due to symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$, the
+``self-interacting'' term of the
+ik-differentiation vanishes~\cite{wang2010optimizing}.
+The error force is therefore
+% \begin{align}\nonumber
+%   \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r)
+%   =\;&
+%   q
+%   \sum_{
+%     \begin{subarray}{c}
+%       \vert m_{\alpha}\vert < K_\alpha/2\\
+%       \v m\neq 0
+%     \end{subarray}}
+%   \v g(\v m)\,
+%   A(\v m, \v r)\,
+%   e^{2\pi i\v m\cdot \v r}
+%   \sum_{j}q_j\,e^{-2\pi i\v m\cdot\v r_j} \\\nonumber
+%   & +\,
+%   q
+%   \sum_{
+%     \begin{subarray}{c}
+%       \vert m_{\alpha}\vert < K_\alpha/2\\
+%       \v m\neq 0
+%     \end{subarray}}
+%   \v g(\v m)\,
+%   e^{2\pi i\v m\cdot \v r}
+%   \sum_{j}q_j\,A(\v m, -\v r_j)\,e^{-2\pi i\v m\cdot\v r_j}\\\label{eqn:ik.error.force.1}
+%   & +\,
+%   q
+%   \sum_{
+%     \begin{subarray}{c}
+%       \vert m_{\alpha}\vert < K_\alpha/2\\
+%       \v m\neq 0
+%     \end{subarray}}
+%   \v g(\v m)\,
+%   \big[
+%   A(\v m, \v r) +
+%   A(\v m, -\v r)
+%   \big].
+% \end{align}
+% Due to the symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$,
+% the last term in Eqn.~\eqref{eqn:ik.error.force.1},
+% i.e. the ``self-interacting term'', is zero.
+% Therefore,
 \begin{align}\nonumber
@@
 Unfortunately, the
-error force kernel of ik-differentiation
+error force kernel
 cannot be written
@@
 corollary~\ref{thm:tmp2} cannot be used here. However, it is still
-possible to develop the error estimate with convolution form.
+possible to develop the error estimate with convolution form under
+some approximations.
 Here we only want to present the key idea and the final  error
@@
 so it can be calculated once and stored in a table for future uses.
-The nearest neighbor approximation to the correlation error is:
+The nearest neighbor approximation to the correlation error
+in a water system is:
 \begin{align}\nonumber
@@
 force calculation. It is shown that the self-interaction  error
-dominate in the low charge density regions~\cite{cerutti2009staggered}.
+dominate when charge density is low~\cite{cerutti2009staggered}.
 Therefore, we always remove the self-interaction term from
@@
 the direction of shift is not important. For convenience, we shift
-all particles to the positive direction for half the mesh element size, namely
+all particles to the positive direction by half the mesh element size, namely
 by a vector $\v s = \sum_\alpha\frac1{2K_\alpha}\v a_\alpha$. From
@@
 
-\subsection{The error estimate of the total force}
-
-In the previous subsections, we estimate the error of direct part and
-reciprocal part separately. Here we provide the error estimate for the
-total force. The mean of the total error force is simply:
-\begin{align}
-  \langle\Delta\v F^{\textrm{x}}(\v r) \rangle
-  &=
-  \langle\Delta\v F_{\textrm{dir}}(\v r) \rangle +
-  \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) \rangle,
-\end{align}
-where \textrm{x}
-denotes any method for the reciprocal Ewald summation, which
-could be truncated Ewald summation (``tr''), ik-/analytical differentiation
-(``ik''/''ana'') or staggered method
-ik-/analytical differentiation (``st,ik''/''st,ana'').
-The mean square total force is
-\begin{align}\nonumber
-  \langle\,\vert\Delta\v F^{\textrm{x}}(\v r)\vert^2\rangle
-  = \,&
-  \langle\,\vert
-  \Delta\v F_{\textrm{dir}}(\v r) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) 
-  \vert^2 \rangle \\\nonumber
-  = \,&
-  \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle +
-  \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\vert^2\rangle +
-  2\,\langle\Delta\v F_{\textrm{dir}}(\v r)\rangle
-  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\rangle \\
-  \label{eqn:error-total}
-  &
-  + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
-\end{align}
-Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r), \Delta\v
-F^{\textrm{x}}_{\textrm{rec}}(\v r))$ denotes the correlation of
-$\Delta\v F_{\textrm{dir}}(\v r)$ and $\Delta\v
-F^{\textrm{x}}_{\textrm{rec}}(\v r)$:
-\begin{align}\label{eqn:error-total-corr}
-  \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
-  & =
-  \langle
-  \Delta\v F_{\textrm{dir}}(\v r)\cdot
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
-  \rangle -
-  \langle
-  \Delta\v F_{\textrm{dir}}(\v r)
-  \rangle\cdot
-  \langle
-  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
-  \rangle.
-\end{align}
-In Eqn.~\eqref{eqn:error-total}, the estimates of errors
-$\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle $,
-$\langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
-r)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
-r)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
-r)\rangle $ have been established.
-In practice, the correlation~\eqref{eqn:error-total-corr}
-is often assumed to be varnished.
-% In section \ref{sec:tmp3}, it is
-% shown that the correlation between the direct and reciprocal error
-% force can be safely neglected.
+% \subsection{The error estimate of the total force}
+
+% In the previous subsections, we estimate the error of direct part and
+% reciprocal part separately. Here we provide the error estimate for the
+% total force. The mean of the total error force is simply:
+% \begin{align}
+%   \langle\Delta\v F^{\textrm{x}}(\v r) \rangle
+%   &=
+%   \langle\Delta\v F_{\textrm{dir}}(\v r) \rangle +
+%   \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) \rangle,
+% \end{align}
+% where \textrm{x}
+% denotes any method for the reciprocal Ewald summation, which
+% could be truncated Ewald summation (``tr''), ik-/analytical differentiation
+% (``ik''/''ana'') or staggered method
+% ik-/analytical differentiation (``st,ik''/''st,ana'').
+% The mean square total force is
+% \begin{align}\nonumber
+%   \langle\,\vert\Delta\v F^{\textrm{x}}(\v r)\vert^2\rangle
+%   = \,&
+%   \langle\,\vert
+%   \Delta\v F_{\textrm{dir}}(\v r) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r) 
+%   \vert^2 \rangle \\\nonumber
+%   = \,&
+%   \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle +
+%   \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\vert^2\rangle +
+%   2\,\langle\Delta\v F_{\textrm{dir}}(\v r)\rangle
+%   \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)\rangle \\
+%   \label{eqn:error-total}
+%   &
+%   + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
+%   \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
+% \end{align}
+% Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r), \Delta\v
+% F^{\textrm{x}}_{\textrm{rec}}(\v r))$ denotes the correlation of
+% $\Delta\v F_{\textrm{dir}}(\v r)$ and $\Delta\v
+% F^{\textrm{x}}_{\textrm{rec}}(\v r)$:
+% \begin{align}\label{eqn:error-total-corr}
+%   \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r),
+%   \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r))
+%   & =
+%   \langle
+%   \Delta\v F_{\textrm{dir}}(\v r)\cdot
+%   \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
+%   \rangle -
+%   \langle
+%   \Delta\v F_{\textrm{dir}}(\v r)
+%   \rangle\cdot
+%   \langle
+%   \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r)
+%   \rangle.
+% \end{align}
+% In Eqn.~\eqref{eqn:error-total}, the estimates of errors
+% $\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle $,
+% $\langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
+% r)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
+% r)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
+% r)\rangle $ have been established.
+% In practice, the correlation~\eqref{eqn:error-total-corr}
+% is often assumed to be varnished.
+% % In section \ref{sec:tmp3}, it is
+% % shown that the correlation between the direct and reciprocal error
+% % force can be safely neglected.
 
@@
 and the density distributions are intentionally chosen the same as
-example 3~(see section \ref{sec:example3}), 
+Example 3~(see section \ref{sec:example3}), 
 for an easy comparison.  The only difference is that the positions
 of charges are independent  in this example,
-while they are correlated in example 3.
+while they are correlated in Example 3.
 % Both the density distributions are highly
@@
 with the real errors.  The parameters are
-chosen to be the same for an easy comparison among these 
+chosen to be the same for an easy comparison among the
 reciprocal space methods.  The errors of FFT
@@
 the same amount of FFTs as the original ik-differentiation, and saves
-one half than the staggered mesh ik-differentiation.  As mentioned before,
+one half FFTs than the staggered mesh ik-differentiation.  As mentioned before,
 the FFT is a bottleneck of communication on massive parallel
@@
 In this example, the setting is nearly the same as
-example 1. The only difference is that all positive charges
+Example 1. The only difference is that all positive charges
 are moved to the region where the density of negative charge is low,
@@
 Fig.~\ref{fig:error2} presents the real and estimated
-RMS error of example 2. The
+RMS error of Example 2. The
 the original ik-differentiation is not
@@
 method is much more precise than the fast algorithms, and the
-staggered mesh method improves the accuracy of analytical
+staggered mesh improves the accuracy of analytical
 differentiation by more than 50\%.
@@
     approximation of the correlation error.
-    The working parameters are the same as example 1.
+    The working parameters are the same as Example 1.
     The black arrows indicate the improvement
@@
     plotted against $x$ axis.
-    The working parameters are the same as example 1.
+    The working parameters are the same as Example 1.
     The black arrow indicates the improvement
@@
 Notice the only difference between this example
-and example 1 (in which the estimates were very sharp) is the correlation
+and Example 1 (in which the estimates were very sharp) is the correlation
 of the charges in the system,
@@
 means that  among all atomic
-correlates (i.e. the chemical bonds, the van der Waals interactions,
-the hydrogen bonds, etc.), the nearest neighbor correlation (rigid
-modeling of H-O bond and H-O-H angle)
+correlates (i.e. the rigid H-O bond and H-O-H angle, the van der Waals interactions,
+the hydrogen bonds, etc.), the rigid bond and angle correlation
+% (rigid
+% modeling of H-O bond and H-O-H angle)
 is the most important one, and all
@@
 
-In this paper, we proposed the error estimate for some state-of-art
+In this paper, we proposed the error estimates for some state-of-art
 algorithms calculating the long-range electrostatic interaction in a
@@
 mesh Ewald (SPME, both ik- and analytical differentiation) and
-staggered mesh Ewald (both ik- and analytical differentiation).
-Unlike previous error estimates, the new error estimates did NOT
-assume the homogeneity and uncorrelation of the system, which is a too
+the staggered mesh Ewald (both ik- and analytical differentiation).
+Unlike the previous error estimates, the new error estimates did NOT
+assume the homogeneity and uncorrelation of the system, which was a too
 strong assumption for most molecular simulations of practical
-interest.  A general error estimate framework was firstly proposed, by
-which the RMS error was proved to be composed by three additive parts:
+interest.  A general error estimate framework was proposed
+to study all the aforementioned estimates.
+When the error force has a pairwise form,
+the RMS error was proved to be composed by three additive parts:
 the homogeneity error, the inhomogeneity error and the correlation
-error.  The homogeneity and inhomogeneity error estimates are
-computationally feasible 
-only when they can be written in a
-convolution form.  The correlation error that is a twofold
-convolution was approximated by the nearest neighbor approximation, in
-order to reduce the computational cost to $\mathcal O(N\log N)$.
+error.
+Moreover, the framework quantitatively provided the estimate
+of all these error components, and suggested a computationally
+scalable way (at the cost of $\mathcal O(N\log N)$) to calculate them.
+
+% the estimates for all these error 
+% were easily derived by the proposed framework.
+
+% by
+% which the RMS error was proved to be composed by three additive parts:
+% the homogeneity error, the inhomogeneity error and the correlation
+% error.
+
+% The homogeneity and inhomogeneity error estimates are
+% computationally feasible 
+% only when they can be written in a
+% convolution form.  The correlation error that is a twofold
+% convolution was approximated by the nearest neighbor approximation, in
+% order to reduce the computational cost to $\mathcal O(N\log N)$.
 
@@
 Some minor contributions of the present work are:
-\begin{itemize}
+\begin{itemize}\itemsep -3pt
 \item In a locally neutral charge system, the inhomogeneity
@@
   force correction~\cite{wang2012} is necessary. Fortunately, most
-  real molecular systems are locally neutral.
+  molecular systems of practical interests are locally neutral.
 \item We explicitly gave the expression of the self-interaction term
@@
   computational cost.
-\item The error estimate showed that the Staggered mesh Ewald
+\item The error estimate showed that the staggered mesh Ewald
   (both ik- and analytical differentiation) are always more precise than
@@
 three numerical tests: two ideal inhomogeneous cases, in which the charges
-are randomly distributed,
-and one real water system, in which the charges are correlated.
-In the ideal cases, the all error estimates are sharp, even in the extreme
-case: positive and negative charges are globally separated. 
-In the water system,  all estimates overestimate the real error,
+were uncorrelated,
+and one real water system, in which the charges were correlated.
+In the ideal cases, the all error estimates were sharp, even in an extreme
+case: positive and negative charges were globally separated. 
+In the water system,  all estimates overestimated the real error,
 because of the correlation of charges.
-The quality of  error estimates for the
-real space  is acceptable.
+The quality of the real space error estimates 
+was acceptable.
 % However, the error estimate neglecting the charge correlation
@@
 The error estimates for the reciprocal space fast algorithms
-are greatly improved by including the first neighbor approximation
+were greatly improved by including the first neighbor approximation
 to the correlation error.
-This indicates among all possible correlations, the first
-neighbor correlation is dominant.
+This indicated among all possible correlations,
+the rigid bond and angle correlation within one molecule
+was dominant.
 
@@
 the software implementation, the scalability of the problem,
-the density of the system, etc.. They are far beyond the scope of the current
+the inhomogeneity of the system, etc..
+They are far beyond the scope of the current
 work, and will be discuss in the following research.

### 2012-04-30 shortRange.inhomo/alltext/pubilsh/main.tex
fix bug
small improves, argue the methods are not expensive

@@
-\documentclass[preprint]{revtex4}
+\documentclass[aps, pre, preprint]{revtex4}
 % \documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 
-\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
+\title{The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems}
 \author{Han Wang}
@@
     boost the efficiency and accuracy of the simulation, respectively.
+    The way of correcting the long-range contribution of pressure
+    is also developed for the inhomogeneous system.
     The
@@
 
-\recheck{ One possible way to avoid the cut-off difficulty is to
+{ One possible way to avoid the cut-off difficulty is to
   modify the short-range interaction by a shifting approach: inside a
   certain radius the original interaction is kept, while outside it the
-  interaction is screen by a shift function, so that goes to
-  zero smoothly. The amount of Shifting is minor in most cases,
+  interaction is screened by a shift function, so that it goes to
+  zero smoothly and rapidly. The amount of shifting is minor in most cases,
   however, it actually changes the way of
@@
   preferred and investigated by most studies
-  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
+  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical}).
   % Shifting the direct part of the Ewald summation actually
@@
 
-In this work, we develop the error estimate of the short-range force
-in inhomogeneous systems. We prove that the 
+In this work, we develop the error estimate of the short-range interaction,
+and the long-range force and pressure corrections
+for the inhomogeneous systems. We prove that the 
 force error is comprised of a homogeneity error and an inhomogeneity
@@
 properties, and the colliding nanoscale clusters for dynamical
-properties.
-\recheck{
+properties.{
   In these example, we investigate the Lennard-Jones interaction, which
@@
   difficulty, such as
-  Buckingham, the direct part of Ewald summation~\cite{ewald1921die}, etc..
+  Buckingham, the direct part of Ewald family algorithms~\cite{ewald1921die, darden1993pme, essmann1995spm, deserno1998mue1}, etc..
   We want to stress that the main contribution and the research interest is the
@@
 These particles are interacting via a short-range pairwise interaction
-$u(\v r)$ with a cut-off radius $r_c > 0$. The corresponding force is
+$u(\v r)$ with a cut-off radius $r_c > 0$.
+The corresponding force is
 denoted by $\v f(\v r)$. 
+Most short-range interactions satisfy $\vert
+u(r)\vert\leq C r^{-m}$, $m>3$, which guarantees an absolute convergence of the
+energy.
+Throughout the paper, the only assumptions made on the interaction are:
+(1) the interaction is short-ranged and (2)
+it is calculated by the cut-off method.
+Therefore, our approach works for a large group of widely used interactions, 
+for example, the Lennard-Jones interaction, the Buckingham interaction,
+the direct part of Ewald family algorithms, and so forth.
 % An infinite cut-off radius will lead to
@@
 % value of the cut-off radius.
-The force error mainly stems from the neglected interaction outside
+
+The force error stems from the neglected interaction outside
 the cut-off radius, so it is convenient to consider the complementary
@@
 E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
-O(MN\log N)$.  The idea of this algorithm is based on the observation
+O(MN\log N)$.
+The idea of this algorithm is based on the observation
 that the cut-off radius may not be calculated at a very high
@@
 
+Since the density profile of the system changes
+very slow comparing with the typical time step used in the MD simulation,
+the cut-off distribution is not calculated every time step.
+Instead,
+for example, in the liquid-vapor equilibrium simulation
+(see Sec.~\ref{sec:tmp2.1}),
+the cut-off distribution is calculated every 20,000 time steps,
+so the extra load of adapting the cut-off is only marginal
+in the simulation, i.e. proportional to $ \frac{M}{20,000}N\log N$.
+
 % This
@@
 
-\subsection{Long-range Force correction}
+\subsection{Long-range force correction}
 
@@
 
+In most cases, the ensemble average of the error force
+does not change very fast comparing with the typical time step used in a MD
+simulation. Therefore, it is not necessary to calculate
+the correction force every time step. Instead, for example,
+we calculate it every 40 time steps in the liquid-vapor equilibrium
+testing system (see Sec.~\ref{sec:tmp2.1}), which takes
+no more than 10\% of the total computational cost.
+If the long-range interaction calculations (which needs FFTs anyway)
+are involved, this ratio should be even lower.
 The idea of the long-range force correction is very similar to those
@@
 cut-off distribution is calculated every 20,000 time steps, and is
-refined twice by Eqn.~\eqref{eqn:rc-refine}. In the interfacial
+refined twice by Eqn.~\eqref{eqn:rc-refine}.
+Due to this low cut-off redistribution frequency,
+the extra cost of this adaptive method is only marginal
+comparing with the total computational cost.
+In the interfacial
 regions, the same cut-off radius as the uniform cut-off simulation,
@@
 of the 
-correction force that is calculated every 40 time steps. The $y$ and
+correction force that is calculated every 40 time steps.
+The extra computational cost is no more than 10\% of the total
+computational costs in all the tested cases.
+The $y$ and
 $z$ components are not shown because their magnitudes are negligible.
@@
 clusters, the error is much lower. The cut-off distribution of the
-adaptive cut-off method is updated every 200 time steps. The third row
+adaptive cut-off method is updated every 200 time steps.
+The third row
 of Fig. \ref{fig:tmp10} shows that the large cut-off region follows the cluster
@@
 
-\recheck{
+{
   We want to stress again the main research interest of the present paper is the
@@
   but also the Buckingham,
-  the direct part of the Ewald summation, etc.),
+  the direct part of the Ewald family algorithms, etc.),
   and other kinds of inhomogeneity

### 2012-05-01 shortRange.inhomo/alltext/pubilsh/main.tex
small revises

@@
 
-\section{Conclusions}\label{sec:conclusion}
+\section{Conclusions and discussions}\label{sec:conclusion}
 
@@
   the validity of these theoretical results. The applications
-  of the error estimate can be more general than the studied examples.
+  of the error estimate is more general than the studied examples,
+  because we only assumed the interaction is short-ranged and
+  treated by the cut-off method.
   Other kind the short-range interaction (not only the Lennard-Jones
@@
   can be easily studied by the error estimates and the proposed methods.
+  However, it is impossible to test all possible cases within one paper.
   The error study of

### 2012-05-01 longRange.hetero/publish/sendfile/main.tex
add sendfile

--- 2012-04-25 longRange.hetero/publish/main.tex
@@
 
-\title{The Error Estimate for Computing Electrostatic Interaction
+\title{The Numerical Accuracy of Computing Electrostatic Interaction
   in the Inhomogeneous and Correlated Molecular Systems:
-  for the Ewald Summation, SPME and Staggered Mesh Ewald.
+  for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.
 }
@@
   In this work, we develop the accurate error estimates for
-  some state-of-art algorithms of long-range electrostatic interaction
+  three state-of-art algorithms of long-range electrostatic interaction
   in inhomogeneous and correlated molecular systems.
   They are the Ewald summation, the smooth particle mesh Ewald (SPME) and
-  the staggered mesh Ewald method. Two branches of force computation, namely
+  the staggered mesh Ewald methods. Two branches of force computation, namely
   the ik- and analytical differentiation, are considered. All the
@@
 \end{align}
-Due to symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$, the
+Due to the symmetry of $\v g(\v m)$ and $A(\v m, \v r)$, the
 ``self-interacting'' term of the
@@
   \centering
-  \includegraphics[]{fig.new/rand1/fig.rho.eps}
+  \includegraphics[]{rand1.rho.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.new/fig.rand1.error.eps}
+  \includegraphics[]{fig.rand1.error.eps}
   \caption{
@@
   % \includegraphics[width=.48\textwidth]{fig.new/rand2/fig.rho.eps}
-  \includegraphics[]{fig.new/rand2/fig.rho.eps}
+  \includegraphics[]{rand2.rho.eps}
   \caption{Charge distribution of Example 2. The red line
@@
   \centering
-  \includegraphics[]{fig.new/fig.rand2.meanf.eps}
+  \includegraphics[]{fig.rand2.meanf.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.new/fig.rand2.error.eps}
+  \includegraphics[]{fig.rand2.error.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.new//fig.water.orig.error.eps}
+  \includegraphics[]{fig.water.orig.error.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.new//fig.water.ana.st.error.eps}
+  \includegraphics[]{fig.water.ana.st.error.eps}
   \caption{
@@
 
-In this paper, we proposed the error estimates for some state-of-art
+In this paper, we proposed the error estimates for three state-of-art
 algorithms calculating the long-range electrostatic interaction in a
@@
 mesh Ewald (SPME, both ik- and analytical differentiation) and
-the staggered mesh Ewald (both ik- and analytical differentiation).
+the staggered mesh Ewald (both ik- and analytical differentiation) methods.
 Unlike the previous error estimates, the new error estimates did NOT
@@
 The error estimates for the reciprocal space fast algorithms
-were greatly improved by including the first neighbor approximation
+were impressively improved by including the first neighbor approximation
 to the correlation error.

### 2012-05-02 longRange.hetero/publish/sendfile/main.tex
fix bugs

@@
 decay of the interaction strength with respect to the distance between charges,
-the typical short-range fast algorithms (cut-off + neighbor list
-algorithms) do not work, and the
+the typical short-range fast algorithms (e.g. the cut-off + neighbor list
+algorithm) do not work, and the
 energy of the system is only conditionally convergent.  One of the
@@
 for these methods may be problematic: it is difficult to try out the
-most efficient parameter set in such a high dimensional parameter space.
-The experiential choices may be either less accurate or waste
+most efficient parameter set in such a 6-dimensional parameter space.
+The experiential choices may be either less accurate or wasting
 computational effort.
@@
 Following this framework, we
-develop the error estimates for the Ewald summation, the SPME method
-and the staggered method Ewald method.   The estimates
-of the homogeneity and inhomogeneous errors are tested by two
+develop the error estimates for the Ewald summation, the SPME 
+and the staggered method Ewald methods.   The estimates
+of the homogeneity and inhomogeneity errors are tested by two
 randomly distributed inhomogeneous charges systems,
@@
   \end{align}
+  The first term on the r.h.s. of \eqref{eqn:error-split} is called
+  the ``homogeneity error'', but it does NOT mean this term is
+  homogeneous or originated from a homogeneous density profile.  It is
+  named so because the error estimate only contains this term in the
+  homogeneous and uncorrelated system. It is the term studied by most
+  previous error estimates.
 \item
@@
 strongly correlated. It could also be defined by the charges falling in some
-certain neighboring range or charges connected by a chemical bonds.
+certain neighboring range or charges connected by chemical bonds.
 % Here ``first neighbors'' means the neighboring
@@
 bond and H-O-H angle are rigid, so the correlation within one molecule
-is important.  Therefore, in this case, we define the nearest neighbor by the
+is considered important.  Therefore, in this case, we define the nearest neighbor by the
 atoms within the same water molecule.  Denoting the index set of the oxygen
@@
 
-\subsection{The smooth particle mesh Ewald method \&
-the staggered mesh Ewald method}
+\subsection{The SPME \&
+staggered mesh Ewald methods}
 
@@
 energy and then approximate the derived force \eqref{eqn:tmp8} by the
-B-spline interpolation. This way is called
+B-spline interpolation. This way is called the
 \emph{ik-differentiation}.
@@
 
-\subsection{Error estimate of the ik-differentiation}
+\subsection{Error estimate of the SPME ik-differentiation}
 \label{sec:error-ik}
@@
 Here we only want to present the key idea and the final  error
-estimates, and leave all details of the derivation 
+estimate, and leave all details of the derivation 
 to the Appendix~\ref{sec:appendix}.  We notice the
@@
 \end{align}
-$G_{\alpha,l}(\v r)$ does not depends on the coordinates of particles,
+$\v G_{\alpha,l}(\v r)$ does not depends on the coordinates of particles,
 so it can be calculated once and stored in a table for future uses.
@@
 
-\subsection{Error estimate of the analytical differentiation}
+\subsection{Error estimate of the SPME analytical differentiation}
 \label{sec:error-ana}
@@
     \end{subarray}}
-  -2f(\v m)\,\v B(\v m, \v r) 
-\end{align}
-With $\v B(\v m, \v r)$ defined by
+  -2f(\v m)\,\v B(\v m, \v r),
+\end{align}
+with $\v B(\v m, \v r)$ defined by
 \begin{align}\nonumber
@@
   Z_{\alpha,l}(\v m)\,
-  2\pi i l K_\alpha\v a_\alpha^\ast\,e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} 
+  2\pi i l K_\alpha\v a_\alpha^\ast\,e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r}.
 \end{align}
@@
 from the analytical force during the simulation. The computational cost of
-the self-interaction term is very low comparing with the SPME
+the self-interaction term is low comparing with the SPME
 force calculation. It is shown that the self-interaction  error
@@
 
-\subsection{Error estimate of the staggered mesh Ewald methods}
+\subsection{Error estimate of the staggered mesh Ewald method}
 
@@
 liquid-vapor equilibrium water system, in order to test the
-quality  of error estimates in inhomogeneous and correlated system.
+quality  of the nearest neighbor approximation for the correlated system.
 
@@
 
-\subsection{Example 1: a locally neutral system.}
+\subsection{Example 1: A locally neutral inhomogeneous system}
 \label{sec:example1}
@@
 Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
-charge   is twice as large as that of the negative charge,
+charge   is twice as larger as that of the negative charge,
 so the
@@
 reciprocal space methods.  The errors of FFT
-based fast Ewald methods are 8 orders of magnitudes large than that of
+based fast Ewald methods are 8 orders of magnitudes larger than that of
 the truncated Ewald summation.
@@
 
-\subsection{Example 2: separated positive and negative charge}
+\subsection{Example 2: Separated positive and negative charge}
 \label{sec:example2}
@@
 regions, and are much larger than the error in bulk
-regions~\cite{wang2012}.
+regions.
 The reciprocal RMS errors only contain homogeneity contributions,
@@
 
-\subsection{Example 3: a water system in gas-liquid phase equilibrium}
+\subsection{Example 3: A water system in gas-liquid phase equilibrium}
 \label{sec:example3}
@@
 The quality of the direct
-part errors estimates is still good (though not perfect):
+part error estimate is still good (though not perfect):
 the error is overestimated by~50\%.
@@
   force error in low density systems~\cite{cerutti2009staggered}.  The
-  expression helped removing the self-interaction term at a very low
+  expression helped removing the self-interaction term at a comparatively low
   computational cost.
@@
 the rigid bond and angle correlation within one molecule
-was dominant.
+is dominant.
 

### 2012-05-02 longRange.hetero/publish/sendfile/main.tex
fix bugs

@@
 Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
-charge   is twice as larger as that of the negative charge,
+charge   is twice as large as that of the negative charge,
 so the

### 2012-06-03 longRange.hetero/alltext/publish/main.tex
mv dirs to alltext

--- 2012-05-02 longRange.hetero/publish/sendfile/main.tex
@@
   \centering
-  \includegraphics[]{rand1.rho.eps}
+  \includegraphics[]{fig.new/rand1/fig.rho.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.rand1.error.eps}
+  \includegraphics[]{fig.new/fig.rand1.error.eps}
   \caption{
@@
   % \includegraphics[width=.48\textwidth]{fig.new/rand2/fig.rho.eps}
-  \includegraphics[]{rand2.rho.eps}
+  \includegraphics[]{fig.new/rand2/fig.rho.eps}
   \caption{Charge distribution of Example 2. The red line
@@
   \centering
-  \includegraphics[]{fig.rand2.meanf.eps}
+  \includegraphics[]{fig.new/fig.rand2.meanf.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.rand2.error.eps}
+  \includegraphics[]{fig.new/fig.rand2.error.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.water.orig.error.eps}
+  \includegraphics[]{fig.new//fig.water.orig.error.eps}
   \caption{
@@
   \centering
-  \includegraphics[]{fig.water.ana.st.error.eps}
+  \includegraphics[]{fig.new//fig.water.ana.st.error.eps}
   \caption{

### 2012-06-03 longRange.hetero/alltext/writeDown/main.tex
mv dirs to alltext

--- 2012-02-08 longRange.hetero/writeDown/main.tex
@@
 where 
-\begin {align}
+\begin {align}\label{eqn:tmp2}
 E_{\textrm{dir}} & = \frac12 \sum^{\ast}_{\v n}
 \sum_{i,j = 1}^{N} \frac{q_iq_j \textrm{erfc}(\beta \vert\v{r}_{ij} + \v{n}\vert)}
-{\vert\v{r}_{ij} + \v{n}\vert} \\
+{\vert\v{r}_{ij} + \v{n}\vert} \\\label{eqn:tmp3}
 E_{\textrm{rec}} & = \frac1{2\pi V} \sum_{\v m \neq 0}
-\frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m) \\
+\frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m) \\\label{eqn:tmp4}
  E_{\textrm{corr}}& = -\frac\beta{\sqrt \pi} \sum_{i=1}^N q_i^2
@@
 
-Both the direct and the reciprocal parts are calculated by cut-off in
-real and reciprocal space, respectively. For the reciprocal part the
-cut-offed energy reads
-\begin{align}
-  E_{\textrm{rec}} & =
-  \frac1{2\pi V}
+The complementary error function $\textrm{erfc}(r)$ in
+Eqn.~\eqref{eqn:tmp2} decays exponentially as $r$ goes to infinity.
+Therefore, it is a short-range interaction in the real space, which
+can be calculated by the standard neighbor list
+method~\cite{frenkel02b} at a cost of $\mathcal O(N)$.  The reciprocal
+part also decays exponentially as the maganitude of the Fourier mode
+$\vert\v m\vert$ increases. Therefore, in practice, the infinit
+summation in Eqn.~\eqref{eqn:tmp3} is truncated, and only a finite
+summation is calculated:
+% Both the direct and the reciprocal parts are calculated by cut-off in
+% real and reciprocal space, respectively.
+% For the reciprocal part the cut-offed energy reads
+\begin{align}\label{eqn:tmp6}
+  E^{\textrm{tr}}_{\textrm{rec}} & =
+  % \frac1{2\pi V}
   \sum_{
@@
     \end{subarray}}
-  \frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m)   
+  % \frac{\exp(-\pi^2\v m^2 / \beta^2)}{\v m^2} S(\v m) S(-\v m)   
+  f(\v m)\, S(\v m) S(-\v m),
 \end{align}
-where $K_\alpha$ is the number of Fourier modes used on direction
-$\alpha$. For convenience, we denote
+where
 \begin{align}
-  f(\v m) = \frac{\exp(-\pi^2 \v m^2 / \beta^2)}{2\pi V \v m^2}
+  f(\v m) = \frac{\exp(-\pi^2 \v m^2 / \beta^2)}{2\pi V \v m^2},
 \end{align}
-The truncated reciprocal force acting on particle $i$ is
-\begin{align}
-  \v F(\v r_i) = - 
+and $K_\alpha$ is the number of Fourier modes used on direction
+$\alpha$.  The truncated reciprocal force acting on particle $i$ is
+\begin{align}\label{eqn:tmp8}
+  \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i) = - 
   q_i 
@@
   S(-\v m)\,
-  e^{2\pi i\v m\cdot\v r_i}
+  e^{2\pi i\v m\cdot\v r_i},
 \end{align}
@@
 \begin{align}
-  \v g(\v m) = -4 \pi \v m i f(\v m)
+  \v g(\v m) = -4 \pi \v m i f(\v m).
 \end{align}
 
-\subsection{Error estimate for the reciprocal Ewald force}
+\subsection{Error estimate for the Ewald summation}
 
@@
 \v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.  We study
-the force error of an arbitrary charge $i$ by the difference between
-the exact force $\v F(\v r_i)$ and calculated force $\tilde{\v F}(\v
-r_i)$ (with error introduced by cut-offs) exerting on the charge $i$.
-The difference between the exact and calculated is called the
-\emph{error force} \cite{short}, and is denoted by $\Delta \v F(\v r_i)
-= \v F(\v r_i) - \tilde{\v F}(\v r_i)$.  The error of the force
-computation is defined by the \emph{root mean square (RMS)}
-\emph{error}, which is the square root of the second moment of the
-error force: $\mathcal E(\v r_i) = \sqrt{\langle\vert\Delta\v F(\v
-  r_i)\vert^2\rangle}$.  The notation $\langle\cdot\rangle$ means
-ensemble average.
+the force error of an arbitrary charge $i$ by calculating the
+difference between the exact force and calculated force exerting on
+the charge $i$, which is called the \emph{error force}
+\cite{wang2012} and denoted by $\Delta \v F(\v r_i)$.
+% and is denoted by
+% $\Delta \v F(\v r_i) = \v F(\v r_i) - \tilde{\v F}(\v r_i)$.
+The maganitude of the force computation error 
+% error of the force computation
+is defined by the \emph{root mean square (RMS)} \emph{error}, which is
+the square root of the second moment of the error force: $\mathcal
+E(\v r_i) = \sqrt{\langle\vert\Delta\v F(\v r_i)\vert^2\rangle}$.  The
+notation $\langle\cdot\rangle$ means ensemble average.
+Ref.~\cite{wang2010optimizing} pointed out that it is reasonable and
+convenient to estimate the error for the direct and reciprocal part
+seperately, namely $\Delta\v F(\v r_i) = \Delta\v F_{\textrm{dir}}(\v
+r_i) + \Delta\v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)$.  The
+$\Delta\v F_{\textrm{dir}}$ and $ \Delta\v
+F^{\textrm{tr}}_{\textrm{rec}}$ denote the direct error force and
+reciprocal error force, respectively.  The superscript ``tr'' denotes
+the reciprocal force is calculated by truncating the infinite Ewald
+summation. Other superscripts are introduced later in the paper to
+denote the error force of the fast algoritms
+that treat the Ewald summation more elaborately.
 
-Ref.~\cite{wang2010optimizing} pointed out that it
-is reasonable and convenient to estimate the error for the direct and
-reciprocal force part seperately. 
 The direct part is a short-range
 interaction in real space, the error estimate of which
-is well established in \cite{short}.
+is well established in \cite{wang2012}.
 The mean of the error force is
@@
     \begin{aligned}
-      &\,0, &\quad & \vert\v r\vert \leq r_c;\\
-      &,& & \vert\v r\vert > r_c,
+      &\,0, &\quad & r \leq r_c;\\
+      &
+      \Big[
+      \frac{2\beta}{\sqrt\pi} e^{-\beta^2r^2} + \frac{\textrm{erfc}(\beta r)}{r}
+      \Big]\frac{\v r}{r^2}
+      ,& & r > r_c,
       % \frac{\textrm{erfc}(\beta\vert\v r\vert)}{\vert\v r\vert}
@@
 \end{align}
-where $r_c$ is the cut-off radius in the real space.  The first order
+where $r = \vert\v r\vert$, and  $r_c$ is the cut-off radius in the real space.  The first order
 charge distribution function $\rho_q$ is defined by:
@@
 In most situations, neglecting the correlation error will give
-satisfactory estimate of the error~\cite{short}. Therefore, 
+satisfactory estimate of the error~\cite{wang2012}. Therefore, 
 \begin{align}
@@
 \begin{align}
-  \Delta \v F_{\textrm{rec}}(\v r_i)
+  \Delta \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
   = & - 
@@
   \big\langle
-  \Delta \v F_{\textrm{rec}}(\v r_i)
+  \Delta \v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)
   \big\rangle
   &= 
-  -q_i\,[\v K^c_{\textrm{rec}}\ast\rho_q\,] (\v r_i),
+  -q_i\,[\v K^{\textrm{tr}}_{\textrm{rec}}\ast\rho_q\,] (\v r_i),
 \end{align}
@@
 \begin{align}
-  \v K^c_{\textrm{rec}}(\v r) =
+  \v K^{\textrm{tr}}_{\textrm{rec}}(\v r) =
   \sum_{
@@
 \begin{align}
-  \langle\vert\Delta\v F_{\textrm{rec}}(\v r_i)\vert^2\rangle
+  \langle\vert\Delta\v F^{\textrm{tr}}_{\textrm{rec}}(\v r_i)\vert^2\rangle
   = &\,
-  q_i^2\,[(\v K^c_{\textrm{rec}})^2\ast\rho_{q^2}] (\v r_i) + 
-  q_i^2\,[\v K^c_{\textrm{rec}}\ast\rho_{q}]^2 (\v r_i).
+  q_i^2\,[(\v K^{\textrm{tr}}_{\textrm{rec}})^2\ast\rho_{q^2}] (\v r_i) + 
+  q_i^2\,[\v K^{\textrm{tr}}_{\textrm{rec}}\ast\rho_{q}]^2 (\v r_i).
 \end{align}
@@
 
-\section{SPME}
+\subsection{The smooth particle mesh Ewald method}
 
-The principle idea of the SPME method is to approximate the term
-$e^{2\pi i\v m\cdot\v r}$ in the structure factor by the B-spline
+The naive calculation of the reciprocal Ewald summation
+\eqref{eqn:tmp6} will result in a computational cost of $\mathcal
+O(N^2)$. It has been shown that with a careful tuning of parameter
+$\beta$ and the reciprocal space truncation $K_\alpha$, the
+computational cost is reduced to $\mathcal O(N^{3/2})$
+\cite{perram1988asc}, which becomes not applicable when the system
+size is larger than several hundreds of charged particles. Both the
+particle mesh Ewald (PME) \cite{darden1993pme} and the smooth particle
+mesh Ewald (SPME) \cite{essmann1995spm} methods are designed to reduce
+the computational cost to $\mathcal O(N\log N)$ in nearly the same
+way.  Since the SPME method is more precise \cite{deserno1998mue1} and
+more popular than the PME, we will focus our discussion on the
+former. All the error estimates develop by the current paper can be
+easily extended to PME method.  The principle idea of the SPME method
+is first to calculate the term $e^{2\pi i\v m\cdot\v r}$ on a uniform
+lattice in the real space.  Therefore, all Fourier transforms can be
+accerlerated by the fast Fourier transform (FFT), that is why the
+computational cost of SPME is reduced to $\mathcal O(N\log N)$. Then,
+for any particle position $\v r_i$, the value of $e^{2\pi i\v m\cdot\v
+  r_i}$ is interpolated by the known values on the neighboring lattice
+points.  The PME method uses Lagrangian interpolation, while the SPME
+uses B-spline interpolation that is more precise, and has higher order
+of smoothness.
+
+The SPME method provides two possibilities of calculating the
+reciprocal force. The first one is to differentiate (with respect to
+the particle position) the reciprocal term of the truncated Ewald
+energy and then approximate the derived force \eqref{eqn:tmp8} by the
+B-spline interplation. This way is called
+\emph{ik--differentiation}. The alternative way notices the high-order
+smoothness of the B-spline interpolation, and derive the force by
+differentiating the B-spline approximated reciprocal Ewald energy
+(also truncated). This way was proposed by the original SPME paper
+\cite{essmann1995spm}, and is called the \emph{analytical
+  differentiation}.  It has been shown that using the same parameters,
+the ik-differentiation is more precise than the analytical
+differentiation, but it requres twice more FFTs, which is a bottleneck
+for the communication in parallel
+implementations~\cite{wang2010optimizing}. Since the SPME method is
+not the point of the present paper, we refer the readers to, for
+example, Ref. \cite{essmann1995spm, deserno1998mue1,
+  wang2010optimizing} for details of this method.
+
+\subsection{Error estimate of the ik-differentiation}
+
+From the precise calculation of the reciprocal summation to the SPME
+fast algorithm, the electrostatic interaction is approximated by two
+steps.  The first step is the truncation of the reciprocal summation,
+i.e. Eqn. \eqref{eqn:tmp6}. The second step is the approximation of
+$e^{2\pi i\v m\cdot\v r}$ by B-spline
+interpolation. Ref. \cite{wang2010optimizing} has pointed out that the
+error due to the first step is negligible comparing with the second
+step, at least for the parameters of practical interest. Numerical
+examples supporting this argument in inhomogeneous systems are also
+given in Section \ref{sec:tmp3}.  Therefore, to estimate the force
+error, it is enough to compare the SPME force with the
+\emph{truncated} Ewald force \eqref{eqn:tmp8}.
+
+As mentioned above, the SPME error mainly oringinated from approximate
+the term $e^{2\pi i\v m\cdot\v r}$ by the B-spline
 interpolation. Denote the error introduced by this approximation by
@@
   e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r} - 1
-  \bigg)
+  \bigg).
 \end{align}
-
-There are two possibility of calculating the reciprocal force from the
-SPME energy. The first one is to differentiate the reciprocal term of
-the original Ewald summation and then approximated the analytical
-force by the B-spline interplation. This way is called
-\emph{ik--differentiation}. The other way is to negative gradient on
-the SPME approximated energy, as proposed in the original SPME paper
-\cite{essmann1995spm}. The later is called \emph{analytical
-differentiation}.
-
-\subsection{Error estimate of the ik-differentiation}
-The error force is 
+The error force of the ik-differentiation is therfore
 \begin{align}\nonumber
-  \Delta\v F^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
   =\;&
@@
   A(\v m, -\v r_i)
-  \big]
+  \big].
 \end{align}
@@
   \big\langle
-  \Delta\v F^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
   \big\rangle
@@
   \big\langle
-  \vert\Delta\v F^{\textrm{ik}}(\v r_i)\vert^2
+  \vert\Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\vert^2
   \big\rangle
@@
   \big\langle
-  \Delta\v F^{\textrm{ik}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)
   \big\rangle  ^2
@@
 
-\subsection{Analytical differetiation}
+\subsection{Error estimate of the analytical differetiation}
 
-The error force is 
+The error force of the analytical differetiation is 
 \begin{align}\nonumber
-  \Delta\v F^{\textrm{ana}}(\v r_i)
+  \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)
   =\;&
@@
   =&\,
-  \Delta\v F^{\textrm{ik}}(\v r_i)\\\nonumber
+  \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\\\nonumber
   & +\,
@@
 \begin{align} \nonumber
-  \langle \Delta\v F^{\textrm{ana}}(\v r_i)\rangle
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\rangle
   =\;&
-  \langle \Delta\v F^{\textrm{ik}}(\v r_i)\rangle\\\nonumber
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\rangle\\\nonumber
   &+\,
@@
 \begin{align}\label{eqn:tmp31}
-  \langle \Delta\v F^{\textrm{ana}}(\v r_i)\rangle
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\rangle
   \approx
-  \langle \Delta\v F^{\textrm{ik}}(\v r_i)\rangle,
+  \langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\rangle,
 \end{align}
@@
   \big\langle
-  \vert \Delta\v F^{\textrm{ana}}(\v r_i)\vert^2
+  \vert \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\vert^2
   \big\rangle
@@
   & +\,
-  \big\langle \Delta\v F^{\textrm{ana}}(\v r_i)\big\rangle ^2
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2
 \end{align}
@@
 \begin{align}\nonumber
-  \big\langle \Delta\v F^{\textrm{ana}}(\v r_i)\big\rangle ^2
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ana}}(\v r_i)\big\rangle ^2
   \approx&\,
-  \big\langle \Delta\v F^{\textrm{ik}}(\v r_i)\big\rangle ^2 \\\nonumber
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\big\rangle ^2 \\\nonumber
   &\,
@@
   & +\,
-  \big\langle \Delta\v F^{\textrm{ik}}(\v r_i)\big\rangle ^2\\
+  \big\langle \Delta\v F_{\textrm{rec}}^{\textrm{ik}}(\v r_i)\big\rangle ^2\\
   &+\,
@@
 
-\section{Numerical tests}
+\subsection{The error estimate of the total force}
+
+In the previous subsections, we estimate the error of direct part and
+reciprocal part seperately. Here we provide the error estimate for the
+total force. The mean of the total error force is simply:
+\begin{align}
+  \langle\Delta\v F^{\textrm{x}}(\v r_i) \rangle
+  &=
+  \langle\Delta\v F_{\textrm{dir}}(\v r_i) \rangle +
+  \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) \rangle,
+\end{align}
+where \textrm{x} can be \textrm{tr}, \textrm{ik} or \textrm{ana},
+standing for the truncated Ewald summation, the ik-differentiation
+and the analytical differetiation, respectively. The mean square
+total force is
+\begin{align}\nonumber
+  \langle\,\vert\Delta\v F^{\textrm{x}}(\v r_i)\vert^2\rangle
+  = \,&
+  \langle\,\vert
+  \Delta\v F_{\textrm{dir}}(\v r_i) + \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i) 
+  \vert^2 \rangle \\\nonumber
+  = \,&
+  \langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle +
+  \langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\vert^2\rangle +
+  2\,\langle\Delta\v F_{\textrm{dir}}(\v r_i)\rangle
+  \cdot \langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)\rangle \\\label{eqn:tmp36}
+  &
+  + 2\,\textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
+\end{align}
+Where $ \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i), \Delta\v
+F^{\textrm{x}}_{\textrm{rec}}(\v r_i))$ denotes the correlation of
+$\Delta\v F_{\textrm{dir}}(\v r_i)$ and $\Delta\v
+F^{\textrm{x}}_{\textrm{rec}}(\v r_i)$:
+\begin{align}\label{eqn:tmp37}
+  \textrm{Corr}(\Delta\v F_{\textrm{dir}}(\v r_i),
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i))
+  & =
+  \langle
+  \Delta\v F_{\textrm{dir}}(\v r_i)\cdot
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
+  \rangle -
+  \langle
+  \Delta\v F_{\textrm{dir}}(\v r_i)
+  \rangle\cdot
+  \langle
+  \Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v r_i)
+  \rangle.
+\end{align}
+In Eqn.~\eqref{eqn:tmp36}, the estimates of errors
+$\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r_i)\vert^2\rangle $,
+$\langle\,\vert\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
+r_i)\vert^2\rangle $, $\langle\Delta\v F_{\textrm{dir}}(\v
+r_i)\rangle$ and $\langle\Delta\v F^{\textrm{x}}_{\textrm{rec}}(\v
+r_i)\rangle $ have been established. In section \ref{sec:tmp3}, it is
+shown that the correlation between the direct and reciprocal error
+force can be safely neglected.
+
+\section{Numerical tests}\label{sec:tmp3}
 
@@
 \subsection{Example 1: locally neutral}
-
-In this example, 16800 charges are put into a $40\textsf{nm}\times
-20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
-them are carrying a unit positive charge of $+e$, and the other half
-are carrying negative charge of $-e$. The position of these charges
-are randomly generated subject to density distribution shown in
-Fig.~\ref{fig:tmp-rho0}. Both the positive and negative charge
-distributions are spacially inhomogeneous, while the system is locally
-neutral, because the positive and negative charge distributions cancel
-each other.
 
@@
 
+In this example, 16800 charges are put into a $40\textsf{nm}\times
+20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
+them are carrying a unit positive charge of $+e$, and the other half
+are carrying negative charge of $-e$. The position of these charges
+are randomly generated subject to density distribution shown in
+Fig.~\ref{fig:tmp-rho0}.  The profile of the positive and negative
+charge distributions are identical, namely the minus of the negative
+distribution is the same as the positive distribution. Therefore the
+positive and negative charge distributions cancel each other, and the
+system is locally neutral. Both the density distributions are highly
+inhomogeneous, take the positive distribution for example: between 11
+\textsf{nm} and 29 \textsf{nm}, the charge density is
+$1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
+and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
+$0.05\;\textsf{e/nm}^3$.
+
 \begin{figure}
@@
     (denoted by straight lines) mean error force of the direct part
-    $\langle\Delta \v F_{\textrm{dir}}(\v r)\rangle$ (red), reciprocal
-    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}(\v
-    r)\rangle$ (green) and the reciprocal part of the analytical
+    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal
+    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}p\rangle$ (green) and the reciprocal part of the analytical
     differentiation $\langle\Delta \v
-    F^{\textrm{ana}}_{\textrm{rec}}(\v r)\rangle$ (blue). The total
+    F^{\textrm{ana}}_{\textrm{rec}}\rangle$ (blue). The total
     mean error force of analytical differentiation $\langle\Delta \v
-    F^{\textrm{ana}}(\v r)\rangle$ is given in pink.  Since the charge
+    F^{\textrm{ana}}\rangle$ is given in pink.  Since the charge
     distribution is uniform on the $y$ and $z$ direction, the $y$ and
@@
 
+Fig.~\ref{fig:meanf1} presents the mean error force of the direct part
+$\langle\Delta \v F_{\textrm{dir}}\rangle$, reciprocal part of Ewald
+summation $\langle\Delta \v F_{\textrm{rec}}\rangle$ and the
+reciprocal part of the analytical differentiation $\langle\Delta \v
+F^{\textrm{ana}}_{\textrm{rec}}\rangle$. The total mean error force of
+analytical differentiation, which is simply $\langle\Delta \v
+F^{\textrm{ana}}\rangle = \langle\Delta \v F_{\textrm{dir}}\rangle +
+\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$, is also
+given.  The real and estimated mean error forces are denoted by dots
+and straight lines, respectively. All estimates are consistent very
+well with real errors.  Since the system is locally neutral, the first
+order charge distribution $\rho_q$ is naturally zero, therefore, by
+Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:tmp31}, all
+the mean error forces should varnish. Numerical resutls in
+Fig. \ref{fig:meanf1} verifies with the above discussion.
+
 \begin{figure}
@@
     (denoted by straight lines) RMS force error of the direct part
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}(\v
-      r)\vert^2\rangle}$ (red), reciprocal part of Ewald summation
-    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}(\v
-      r)\vert^2\rangle}$ (green) and the reciprocal part of the
-    analytical differentiation $\sqrt{\langle\vert\Delta \v
-      F^{\textrm{ana}}_{\textrm{rec}}(\v r)\vert^2\rangle}$
-    (blue). The RMS force error of analytical differentiation
-    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
-      r)\vert^2\rangle}$ is given in pink.  Since the charge
-    distribution is uniform on the $y$ and $z$ direction, the $y$ and
-    $z$ dimension of the mean error force is averaged, and the errors
-    are plotted on $x$ direction.  The cut-off in the real space is 3
-    \textsf{nm}, the number of freedom in the reciprocal space is
-    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
-    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
-    the analytical differentiation is 6.}
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$
+    (red), reciprocal part of Ewald summation
+    $\sqrt{\langle\vert\Delta \v F_{\textrm{rec}}\vert^2\rangle}$
+    (green) and the reciprocal part of the analytical differentiation
+    $\sqrt{\langle\vert\Delta \v
+      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
+    force error of analytical differentiation
+    $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}\vert^2\rangle}$ is
+    given in pink.  Since the charge distribution is uniform on the
+    $y$ and $z$ direction, the $y$ and $z$ dimension of the mean error
+    force is averaged, and the errors are plotted on $x$ direction.
+    The cut-off in the real space is 3 \textsf{nm}, the number of
+    freedom in the reciprocal space is $100\times 50\times 50$, the
+    parameter $\beta$ is $1.0\; \textsf{nm}^{-1}$ and the order of
+    B-spline interpolation used for the analytical differentiation is
+    6.}
   \label{fig:error1}
 \end{figure}
+
+Fig.~\ref{fig:error1} presents the RMS force error of the direct part
+$\sqrt{\langle\vert\Delta \v F_{\textrm{dir}}\vert^2\rangle}$,
+reciprocal part of Ewald summation $\sqrt{\langle\vert\Delta \v
+  F_{\textrm{rec}}\vert^2\rangle}$, the reciprocal part of the
+analytical differentiation $\sqrt{\langle\vert\Delta \v
+  F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ and the total
+analytical differentiation force $\sqrt{\langle\vert\Delta \v
+  F^{\textrm{ana}}\vert^2\rangle}$.  The real and estimated mean error
+forces are denoted by dots and straight lines, respectively. All the
+error estimates are overlapping with the real errors, that means the
+error estimates developed by the present paper are very sharp.
+% Since all mean error forces varnish, the RMS force errors
+% consists of only the homogeneous contribution. 
+In the high charge density region, the error is comparatively larger
+than the low charge density region. For the direct part, the ratio is
+roughly the sqare root of the density ratio. For the reciprocal part
+this ratio is lower. The reciprocal error of the analytical
+differentiation is 4 orders of maganitudes large than that of the
+Ewald summation, which means the Ewald summation is much more precice
+than the fast algorithm based on mesh discretization.
 
@@
 
+In this example, 16800 charges are put into a $40\textsf{nm}\times
+20\textsf{nm}\times 20\textsf{nm}$ periodic simulation box. Half of
+them are carrying a unit positive charge of $+e$, and the other half
+are carrying negative charge of $-e$. The position of these charges
+are randomly generated subject to density distribution shown in
+Fig.~\ref{fig:tmp-rho2}. The nagative charges are seperated from their
+counter ions, but the whole system is kept neutral. This case rarely
+happen in real simulation, but is serves as a good test of the error
+estimates in extreme situations.
+
 \begin{figure}
@@
     (denoted by straight lines) mean error force of the direct part
-    $\langle\Delta \v F_{\textrm{dir}}(\v r)\rangle$ (red), reciprocal
-    part of Ewald summation $\langle\Delta \v F_{\textrm{rec}}(\v
-    r)\rangle$ (green) and the reciprocal part of the analytical
-    differentiation $\langle\Delta \v
-    F^{\textrm{ana}}_{\textrm{rec}}(\v r)\rangle$ (blue). The total
-    mean error force of analytical differentiation $\langle\Delta \v
-    F^{\textrm{ana}}(\v r)\rangle$ is given in pink.  Since the charge
-    distribution is uniform on the $y$ and $z$ direction, the $y$ and
-    $z$ dimension of the mean error force is averaged, and the errors
-    are plotted on $x$ direction.  The cut-off in the real space is 3
-    \textsf{nm}, the number of freedom in the reciprocal space is
-    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
-    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
-    the analytical differentiation is 6.}
+    $\langle\Delta \v F_{\textrm{dir}}\rangle$ (red), reciprocal part
+    of Ewald summation $\langle\Delta \v F_{\textrm{rec}}\rangle$
+    (green) and the reciprocal part of the analytical differentiation
+    $\langle\Delta \v F^{\textrm{ana}}_{\textrm{rec}}\rangle$
+    (blue). The total mean error force of analytical differentiation
+    $\langle\Delta \v F^{\textrm{ana}}\rangle$ is given in pink.
+    Since the charge distribution is uniform on the $y$ and $z$
+    direction, the $y$ and $z$ dimension of the mean error force is
+    averaged, and the errors are plotted on $x$ direction. The
+    algorithmic parameters are the same as Fig.~\ref{fig:meanf1}.}
   \label{fig:meanf2}
 \end{figure}
+
+Fig.~\ref{fig:meanf2} shows the mean error forces of Example 2. All
+notations in the Figure are the same as Example 1.  Although the
+charge distribution is not usual in this case, the error estimates are
+accurate. The two peaks of direct mean force error presented at the
+positive-negative interface result from the seperation of the positive
+and nagative charges, i.e., a non-vanishing first order charge
+distribution $\rho_q$.  Similar phenomena were observed by
+Ref.~\cite{wang2012}. The reciprocal mean force error is much smaller
+than the direct one, so the contribution to the total mean force error
+is not important.
 
@@
     analytical differentiation $\sqrt{\langle\vert\Delta \v
-      F^{\textrm{ana}}_{\textrm{rec}}(\v r)\vert^2\rangle}$
-    (blue). The RMS force error of analytical differentiation
+      F^{\textrm{ana}}_{\textrm{rec}}\vert^2\rangle}$ (blue). The RMS
+    force error of analytical differentiation
     $\sqrt{\langle\vert\Delta \v F^{\textrm{ana}}(\v
@@
     $z$ dimension of the mean error force is averaged, and the errors
-    are plotted on $x$ direction.  The cut-off in the real space is 3
-    \textsf{nm}, the number of freedom in the reciprocal space is
-    $100\times 50\times 50$, the parameter $\beta$ is $1.0\;
-    \textsf{nm}^{-1}$ and the order of B-spline interpolation used for
-    the analytical differentiation is 6.}
+    are plotted on $x$ direction. The algorithmic parameters are the
+    same as Fig.~\ref{fig:meanf1}.}
   \label{fig:error2}
 \end{figure}
+
+Fig. \ref{fig:error2} shows the RMS errors of Example 2. The
+corresponding error estimates are accurate. In this case the second
+order charge distrubution is a constant, therefore the contribution to
+the error is also a constant. The same as Example 1, the reciprocal
+error of Ewald sum is much smaller than the direct error and the
+reciprocal error of analytical differentiation.  The error peak at the
+positive-negative interface, is only 3 times larger than the error of
+the bulk regions. For the dispersion interaction, the interfacial
+error could be more than one order of maganitude larger than the bulk
+error. That is because the direct interaction converges much faster
+than the dispersion interaciton ($e^{-r^2}$ v.s. $r^{-6}$).
 

### 2012-06-03 longRange.hetero/alltext/slides/sjtu.2012.06/figs/long-range-inhomo/error.water.charge0.834.box14.9x7.4x7.4.b2.500.r1.31.n6.K121x061x061/parameters.spme.ana.noHO.st.real.sh
add slides

@@ -1,0 +1,71 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2012-07-02 longRange.hetero/alltext/publish/resubmit/lett.tex
add resubmit

\documentclass[a4paper]{article}

\begin{document}

Reviewer  1 Comments:

At a glance, the paper by Han Wang and colleagues appears to be another error estimator for P3M and related electrostatics methods.  But, after taking in the second paragraph it becomes clear that the authors are much more than mathematically inclined on the subject, and have indeed performed a useful service to the simulations community by incorporating the correlation of molecular charges into their error estimates.  It is probably not of tremendous practical benefit in an application like an Ewald parameter optimizer, as these programs can just repeat an electrostatic calculation on a representative snapshot of a simulation and estimate the error directly from the resulting forces.  However, it is of value to have a formal expression for the effect of charge correlations on these errors, and it may be instrumental in devising a pairwise approximate correction to electrostatic forces obtained from coarse grids.  The paper will require minor modifications so that the authors do not run afoul of various members of the community who hold strong opinions, but otherwise appears to be fit for publication.

In the introduction, the authors should probably take the perspective that SPME is a special case of P3M.  In the opinions of the developers of SPME, the derivation differs from P3M although it leads to similar results, but even TA Darden acknowledges that the reciprocal space component of the non-smooth PME algorithm was inspired by P3M.  It is probably best to phrase SPME as such and not offend anyone.  The interlacing technique was first applied in the 1970s, as the authors have cited.  It was originally a means of reducing the memory requirements of these calculations—electrostatics on the two grids were solved serially.  Finally, the sentence “We prove that the error is decomposed…” should be changed to “We show that the error may be approximately decomposed…” to indicate that the estimator is, in the end, approximate but relevant to real systems.

Cosmetically, the authors should combine the two figures showing the charge distributions of Examples 1 and 2, to ensure they appear side-by-side in the published version.

The authors are reasonable to focus on the error arising from the reciprocal space approximations in the various P3M-related methods; the error arising from the direct space part of the calculation is simpler to assess.  However, because the authors give so much attention to SPME and the Staggered Mesh method which, as published, built on SPME, the authors should include some plot of the effect of grid spacing, Gaussian smoothing function width (Ewald coefficient), and interpolation order—these are the determinants of the accuracy of the reciprocal space calculation in these fast methods.  How does the estimator do in terms of getting the various trends correct?  What is the effect of correlated charge positions on the error and the estimates under changing interpolation order?  This is at the heart of the difference between ik- and analytic differentiation that the authors have otherwise carefully investigated.  It would also be helpful to see a plot of the error estimator’s performance as a function of the “near neighbor” definition.  Define near neighbors strictly by length, and plot the error estimator's accuracy as a continuous function of the near neighbor cutoff.  Extra credit for detailing the computation time as a function of the same parameter!

One other point of discussion that might be relevant to this paper is the significance of the results on force-shifted coulomb interactions (see the simulation methods of Valerie Dagget and colleagues, or the Wolfe Method as reviewed in J. Chem. Phys. 124:234104 and elsewhere).  These methods, based strictly on local “electrostatic” interactions computed by modifying Coulomb’s law, are often trotted out as alternatives to Ewald summation though their application is still limited (which is, in the opinion of this reviewer, as it should be).  A principal assumption of these methods, which is often used circuitously to defend their application, is that real systems are locally neutral or that electrostatic correlations decay on the length scale of a few water layers.  Wang and colleagues may be able to analyze these methods, provide insights into the appearance of their validity, and identify their limitations rigorously.  A formal analysis of these methods is not required for this paper, but a possible direction the authors might explore in the future.

The authors have done an excellent job of manipulating the mathematical foundations of these fast electrostatics methods.  With minor modifications and extensions of the study, which this reviewer does not intend to be onerous, this work should be published without further hindrance.

Reviewer  2 Comments:

The article deals with the derivation of an accurate error estimate for the Ewald and SPME mesh Ewald method that can be used for inhomogeneous and correlated charged systems.

Error estimates for long range algorithms are always useful for periodic charged systems, since due to the long range nature, no exact calculation is possible, but one rather has to truncate the interactions at some point, and hence is forced to introduce errors.  Ideally, one would like to know for a specific method before doing an expensive calculation how to choose method parameters such that I reach a certain accuracy. Such error estimates have been developed in the past, but normally only under the assumption that the charges are randomly distributed. Here, the authors extend these error estimates to the very relevant cases of inhomogeneous and/or correlated systems.

I find the article in general very readable and informative, and also suited for this journal. I have just a few comments that the authors might want to take into account in a minor revised version, before this article, in my opinion, is ready for publication:

Page 7, line 23:
The definition of a discrete set of nearest neighbors $\Omega_j$ might not readily avaible in all cases. For example, for simple liquids it may be more feasible to use the radial distribution function $g(r)$ up to a certain radius $r_c$, where $g(r) \approx 1$ for $r > c_c$. Then the sum has to be replaced by an integral over $r$.  Because of the close relation of $\rho^{(2)}$ and $g(r)$, the equations should be easy to adapt to such a notation.

Page 15, line 45:
I believe I saw that the for interlaced P$^3$M algorithm, which is very similar to the staggered SMPE algorithm,  the approximation to leading order of the error estimate is not justified, at least for higher precisions. This approximation could lead to a visible deviation from the true errors. In this context it might be useful to recalculate the numerical examples at higher precision. Usually, deviations start to be visible from about an RMS of $10^{-4}$.

Page 16, line 34:
Again, In the very similarly structured interlaced P$^3$M algorithm,  there are differences in accuracy between the $i\mathbf{k}$- and analytical differentiation at higher precisions.At this point it might not be justified  to assume that both can be treated in the same way. Similarly to the approximation of the $i\mathbf{k}$ error formula, it would be useful to do calculations at higher precision than those presented in the paper, and compare them

The manuscript contains a few misprints, and the language could be polished on a few occasions by a native speaker.

Reviewer 3 Comments:

The authors have introduced a way to study electrostatic force errors in correlated systems by assuming that the dominant correlations are short-ranged which should usually work--they acknowledge this may not work for systems near phase transitions. I like this paper and would like to see it published after minor complaints are addressed.

Firstly, the main contribution is to introduce a way to rapidly evaluate the force error, including that due to short ranged (bonded) pair interactions. Some readers may be confused by this, since bonded pair electrostatic interactions are considered to be NOT CALCULATED. However, in Ewald like methods the reciprocal contribution cannot be easily excluded for atom pairs and is surprisingly large even for bonded pairs. I think including this point somewhere in the discussion will help many readers. Note that errors for bonded pairs may be at least partly responsible for the disappointing performance of multiple time step methods. (they are high frequency in time)

I am curious about the fact that correlation reduces force errors compared to usual estimates. I wonder if this is somehow due to electrostatic forces on bonded pairs being anti-correlated due to opposing charge signs e.g. on Oxygen and Hydrogens of H2O.

Otherwise I have a number of minor grammatical and typo complaints:

page 3 lines 9,14  The term "research" could be replaced by "papers" on line 9 and "paper" on 14
another possibility is "manuscript"

page 3 line 27 "which assume the error" $\rightarrow$ "which assumes the error"
page 3 line 43 "nearest neighbor approximation of correlation error": insert "the" before "correlation"
page 3 line 54 "we consider the system" $\rightarrow$ "we consider a system"
page 3 line 55 "is composed by N" $\rightarrow$ "is composed of N"
page 3 line 56 "the force of a" $\rightarrow$ "the force on a"
page 4 line 18 "error estimate for the error force" seems like 1st "error' is unnecessary
              perhaps replace with "following estimate for the error force"---also the term "error force" could be
              replaced with "force error" here and elsewhere and I think the text would flow better
page 6 line 16 "Most of the error estimates" $\rightarrow$ "Most previous error estimates"
page 6 line 32: "Analog to" $\rightarrow$ "Analogous to"
page 7 line 3 "A non-varnishing" $\rightarrow$ "A non-vanishing"
page 7 line 10,11: "the locally neutral condition" $\rightarrow$ "the local neutrality condition"
page 7 line 21: "which is still not applicable" $\rightarrow$ "which is still not tractable" or maybe "computationally feasible"
page 7 line 46: "Then the second part" $\rightarrow$ "Then the second term". Also on line 54 "part" $\rightarrow$ "term"
page 7 line 52: "small comparing with" $\rightarrow$ "small compared with" or "small in comparison with". same for pg 8 line 16
page 8 line 42: "Ensemble averages is taken" $\rightarrow$ "Ensemble averages are taken"
page 10 line 1: "ia the reciprocal" $\rightarrow$ "are the reciprocal"
page 11 line 8: "becomes not applicable" as in page 7 line 21 I think "intractable" is better here
page 11 line 10: "PME ans SPME" ; "ans" $\rightarrow$ "and"
page 12 line 7: "only little" $\rightarrow$ "only a small"
page 14 line 33: "It is shown that the self-interaction error dominate" $\rightarrow$ "It has been shown that the sel-interaction
                   error dominates"
page 17 line 49: "Twice as larger" $\rightarrow$ "Twice as large"
page 18 line 43: "cut-offed" $\rightarrow$ "truncated"
page 18 line 47: "are consistent very well with" $\rightarrow$ "are consistently accurate compared with" or "accurately track"
page 18 line 60: "reduces by more than" $\rightarrow$ "is reduced by more than"
page 19 line 34: "FFTs than" $\rightarrow$ "FFTs compared to"
page 19 line 55: again "cut-offed" $\rightarrow$ "truncated"
page 20 line 34: "was reported" $\rightarrow$ "were reported"
page 20 line 35: "varnish" $\rightarrow$ "vanish"
page 20 line 41: "error estimates consist with" $\rightarrow$ "error estimates are consistent with" or
                                                  "error estimates accurately track"

page 23 line 57: "composed by three additive" $\rightarrow$ "composed of three additive"
page 24 line 11: "the error is of good property" Not clear what is meant. Do you mean total error is not
                 contaminated by this?
page 24 line 18: "was proved to dominant" $\rightarrow$ "was proved to dominate"
page 24 line 19: "helped removing" $\rightarrow$ "helped to remove"
page 24 line 35: "only one half FFTs" $\rightarrow$ "only one half the FFTs"
page 27, line 15: "Inserting it into Eqn (17), also neglect" $\rightarrow$ "Inserting this into Eqn (17) while neglecting"

\end{document}

### 2012-07-02 longRange.hetero/alltext/publish/resubmit/main.tex
add resubmit

--- 2012-05-02 longRange.hetero/publish/sendfile/main.tex
@@
 More recently, the staggered mesh or
-``interlacing'' technique~\cite{chen1974reduction,eastwood1976optimal}
+xb``interlacing'' technique~\cite{chen1974reduction,eastwood1976optimal}
 was applied to SPME
@@
 error estimates may be problematic, or even not applicable.  Several
-research have shown that due to the correlation of charges, the error estimates
+papers have shown that due to the correlation of charges, the error estimates
 obviously deviate from the real
@@
 
-The purpose of this research is to develop a reliable  error
+The purpose of this manuscript is to develop a reliable  error
 estimate in inhomogeneous and correlated molecular systems.
@@
 by the nearest neighbor approximation
-technique, which assume the error  is dominated by  short-range correlation.
+technique, which assumes the error  is dominated by  short-range correlation.
 This

### 2012-07-03 longRange.hetero/alltext/publish/resubmit/lett.tex
fix typos, add fig.rho.eps

@@
 
-Reviewer  1 Comments:
+\noindent
+Reviewer  1 Comments:\\
 
-At a glance, the paper by Han Wang and colleagues appears to be another error estimator for P3M and related electrostatics methods.
-But, after taking in the second paragraph it becomes clear that the authors are much more than mathematically inclined on the subject, and have indeed performed a useful service to the simulations community by incorporating the correlation of molecular charges into their error estimates.
-It is probably not of tremendous practical benefit in an application like an Ewald parameter optimizer, as these programs can just repeat an electrostatic calculation on a representative snapshot of a simulation and estimate the error directly from the resulting forces.
-However, it is of value to have a formal expression for the effect of charge correlations on these errors, and it may be instrumental in devising a pairwise approximate correction to electrostatic forces obtained from coarse grids.
-The paper will require minor modifications so that the authors do not run afoul of various members of the community who hold strong opinions, but otherwise appears to be fit for publication.
+\textit{ At a glance, the paper by Han Wang and colleagues appears to
+  be another error estimator for P3M and related electrostatics
+  methods.  But, after taking in the second paragraph it becomes clear
+  that the authors are much more than mathematically inclined on the
+  subject, and have indeed performed a useful service to the
+  simulations community by incorporating the correlation of molecular
+  charges into their error estimates.  It is probably not of
+  tremendous practical benefit in an application like an Ewald
+  parameter optimizer, as these programs can just repeat an
+  electrostatic calculation on a representative snapshot of a
+  simulation and estimate the error directly from the resulting
+  forces.  However, it is of value to have a formal expression for the
+  effect of charge correlations on these errors, and it may be
+  instrumental in devising a pairwise approximate correction to
+  electrostatic forces obtained from coarse grids.  The paper will
+  require minor modifications so that the authors do not run afoul of
+  various members of the community who hold strong opinions, but
+  otherwise appears to be fit for publication.
+}
 
+?
+
+\textit{
 In the introduction, the authors should probably take the perspective that SPME is a special case of P3M.
@@
 Finally, the sentence “We prove that the error is decomposed…” should be changed to “We show that the error may be approximately decomposed…” to indicate that the estimator is, in the end, approximate but relevant to real systems.
+}\\
 
+not done\\
+
+\textit{
 Cosmetically, the authors should combine the two figures showing the charge distributions of Examples 1 and 2, to ensure they appear side-by-side in the published version.
+}\\
 
@@
 another possibility is "manuscript"
-
 page 3 line 27 "which assume the error" $\rightarrow$ "which assumes the error"
@@
 page 3 line 56 "the force of a" $\rightarrow$ "the force on a"
-page 4 line 18 "error estimate for the error force" seems like 1st "error' is unnecessary
+*page 4 line 18 "error estimate for the error force" seems like 1st "error' is unnecessary
               perhaps replace with "following estimate for the error force"---also the term "error force" could be
@@
 page 23 line 57: "composed by three additive" $\rightarrow$ "composed of three additive"
-page 24 line 11: "the error is of good property" Not clear what is meant. Do you mean total error is not
+*page 24 line 11: "the error is of good property" Not clear what is meant. Do you mean total error is not
                  contaminated by this?

### 2012-07-03 longRange.hetero/alltext/publish/resubmit/main.tex
fix typos, add fig.rho.eps

--- 2012-05-02 longRange.hetero/publish/sendfile/main.tex
@@
   if the error force is of pairwise form,
-  then the root mean square force error is composed by three additive parts,
+  then the root mean square force error is composed \redc{of} three additive parts,
   the homogeneity error, the inhomogeneity error and the correlation
@@
 by the nearest neighbor approximation
-technique, which assume the error  is dominated by  short-range correlation.
+technique, which \redc{assumes} the error  is dominated by  short-range correlation.
 This
@@
 including the nearest neighbor approximation of
-correlation error, the quality of the estimates
+\redc{the} correlation error, the quality of the estimates
 is impressively enhanced.
@@
 
-In this paper, we consider the system with periodic boundary condition.
+In this paper, we consider a system with periodic boundary condition.
 Suppose it is
-composed by $N$ charged particles located at $\v r_1, \v r_2, \cdots,
+composed \redc{of} $N$ charged particles located at $\v r_1, \v r_2, \cdots,
 \v r_N$ with charges $q_1, q_2, \cdots, q_N$, respectively.
-We study the force of a testing particle located at $\v r$, which
+We study the force \redc{on} a testing particle located at $\v r$, which
 feels interactions from all charges $q_1, q_2, \cdots, q_N$
@@
 
-One of the main results of this research is the error estimate for
+One of the main results of this research is the \redc{following} estimate for
 the error force that can be written as a summation of
@@
 \begin{theorem}\label{thm:tmp1}
-  Let a periodic molecular system be composed by $N$ charged particles
+  Let a periodic molecular system be composed of $N$ charged particles
   located at $\v r_1, \v r_2, \cdots, \v r_N$ with charges $q_1, q_2,
@@
   vanishes, otherwise $C(\v r, \v r') \neq 0$.
-  Most of the error estimates assumed the independency of the
+  Most \redc{previous} error estimates assumed the independency of the
   particles in the system~\cite{kolafa1992cutoff, hummer1995numerical, deserno1998mue2, petersen1995accuracy, wang2010optimizing, neelov2010interlaced, ballenegger2012convert, wang2012},
@@
   in inhomogeneous systems, which was derived in Ref.~\cite{wang2012}. 
-\item Analog to the short-range error estimate~\cite{wang2012}, the
+\item \redc{Analogous} to the short-range error estimate~\cite{wang2012}, the
   three terms on the r.h.s. of Eqn.~\eqref{eqn:thm-error} are called the
@@
   % section~\ref{sec:tmp3}, it is shown neglicting the 
-\item A non-varnishing mean error force~\eqref{eqn:thm-meanf} was proved
+\item A non-vanishing mean error force~\eqref{eqn:thm-meanf} was proved
   to be
@@
   i.e. a non-zero first order charge distribution. For
-  most of the simulation cases, the locally neutral condition is
+  most of the simulation cases, the \redc{local neutrality} condition is
   satisfied, so the mean error force and the inhomogeneity error
@@
 The full computation of the correlation error costs at least $\mathcal
-O(N^2\log N)$, which is still not applicable.
+O(N^2\log N)$, which is still not \redc{tractable}.
 So we consider the nearest-neighbor approximation to reduce
@@
 Then
-second part on the r.h.s. of the Eqn.~\eqref{eqn:split-rho-q2} is
+second \redc{term} on the r.h.s. of the Eqn.~\eqref{eqn:split-rho-q2} is
 approximately $\frac{N-\#(\Omega_j)}{N}\rho_q(\v r')\rho_q(\v r'')\approx
@@
 The approximation is valid only when the number
-of neighbors in $\Omega_j$ is small comparing with the number of charges
+of neighbors in $\Omega_j$ is small \redc{compared} with the number of charges
 in the system.
@@
 % large, this should be a good approximation.
-Therefore, the first part
+Therefore, the first \redc{term}
 on the r.h.s. of Eqn.~\eqref{eqn:split-rho-q2} is actually the
@@
 improve the approximation by considering more and more neighbors as long as
-the number of neighbors is small comparing with the size of the system.
+the number of neighbors is small \redc{compared} with the size of the system.
 
@@
 The two ensemble averages in Eqn.~\eqref{eqn:c-error-1}
-is taken over all possible water directions 
+\redc{are} taken over all possible water directions 
 at position $\v r'$. As an approximation, we
@@
 % positions are assumed to be independent. In most cases, the first
-% neighbor shell is small comparing to the simulation box size,
+% neighbor shell is small compared to the simulation box size,
 % therefore,
@@
 where $\v m = m_1 \v a_1^\ast + m_2 \v a_2^\ast + m_3 \v a_3^\ast$ is
-the reciprocal space lattice vectors. $\v a_\alpha^\ast,\ \alpha = 1,
+the reciprocal space lattice \redc{vector}. $\v a_\alpha^\ast,\ \alpha = 1,
 2, 3$ are conjugate reciprocal vectors of $\v a_\alpha$, defined by
@@
 is $\mathcal O(N^{3/2})$,
-which becomes not applicable when the system
+which becomes not \redc{tractable} when the system
 size is larger than several hundreds of charged particles.
-Both the PME ans SPME methods
+Both the PME \redc{and} SPME methods
 are designed to reduce
@@
 Implementing the staggered mesh method for SPME is
-relatively simple, and involves only little modification to the
+relatively simple, and involves only \redc{a small} modification to the
 existing codes.
@@
 interpolation. It has been shown that the
-error due to the first step is negligible comparing with the second
+error due to the first step is negligible \redc{compared} with the second
 step,
@@
 from the analytical force during the simulation. The computational cost of
-the self-interaction term is low comparing with the SPME
-force calculation. It is shown that the self-interaction  error
-dominate when charge density is low~\cite{cerutti2009staggered}.
+the self-interaction term is low \redc{compared} with the SPME
+force calculation. It \redc{has been} shown that the self-interaction  error
+\redc{dominates} when the charge density is low~\cite{cerutti2009staggered}.
 Therefore, we always remove the self-interaction term from
@@
 % In practice, the correlation~\eqref{eqn:error-total-corr}
-% is often assumed to be varnished.
+% is often assumed to be vanished.
 % % In section \ref{sec:tmp3}, it is
@@
   \caption{
-    The charge number density  of Example 2.
+    The charge number density  of Example 1.
     The red line: positive charge. The blue line: negative charge.
@@
 % Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:ana.meanf}, all
-% the mean error forces should varnish. Numerical resutls in
+% the mean error forces should vanish. Numerical resutls in
 % Fig. \ref{fig:meanf1} verifies with the above discussion.
@@
 Fig.~\ref{fig:error1} presents the real RMS error (by points) and the
-corresponding error estimates (by lines) of the cut-offed Ewald direct
+corresponding error estimates (by lines) of the \redc{truncated} Ewald direct
 part, the truncated Ewald reciprocal part, the original ik-/analytical
 differentiation and the staggered mesh ik-/analytical
-differentiation. All the error estimates are consistent very well
-with the real errors.  The parameters are
+differentiation. All the error estimates \redc{are consistently accurate compared with}
+the real errors.  The parameters are
 chosen to be the same for an easy comparison among the
@@
 With the staggered mesh,
-the error of the analytical differentiation reduces by more than 50\%,
+the error of the analytical differentiation \redc{is reduced} by more than 50\%,
 while the accuracy of the ik-differentiation is only marginally
@@
 the same amount of FFTs as the original ik-differentiation, and saves
-one half FFTs than the staggered mesh ik-differentiation.  As mentioned before,
+one half FFTs \redc{compared to} the staggered mesh ik-differentiation.  As mentioned before,
 the FFT is a bottleneck of communication on massive parallel
@@
 % error estimates developed by the present paper are very sharp.
-% Since all mean error forces varnish, the RMS force errors
+% Since all mean error forces vanish, the RMS force errors
 % consists of only the homogeneous contribution. 
@@
 Fig.~\ref{fig:meanf2} shows the real mean error forces (by points) and the
-corresponding error estimates (by lines) of cut-offed Ewald direct
+corresponding error estimates (by lines) of \redc{truncated} Ewald direct
 part, truncated Ewald reciprocal part, the ik-/analytical
@@
 and negative charges, i.e., a non-vanishing and fast changing first order charge
-distribution $\rho_q$.  Similar phenomena was reported by
+distribution $\rho_q$.  Similar phenomena \redc{were} reported by
 Ref.~\cite{wang2012}. Surprisingly, 
 the reciprocal mean error forces
-do not present any singularity, and varnish
+do not present any singularity, and vanish
 all over the simulation region.
@@
 mesh ik-/analytical differentiation in this plot.
-All the error estimates consist with the real errors.
+All the error estimates \redc{are consistent with} the real errors.
 Stemming from the inhomogeneity error,
@@
 The reciprocal RMS errors only contain homogeneity contributions,
-due to the varnished mean error force.
+due to the vanished mean error force.
 Similar with Example 1, the truncated Ewald
@@
 When the error force has a pairwise form,
-the RMS error was proved to be composed by three additive parts:
+the RMS error was proved to be composed \redc{of} three additive parts:
 the homogeneity error, the inhomogeneity error and the correlation
@@
 \item In a locally neutral charge system, the inhomogeneity
-  error was proved to vanish. Therefore, the error
-  is of good property, and no adaptive method nor
+  error was proved to vanish, therefore, no adaptive method nor
   force correction~\cite{wang2012} is necessary. Fortunately, most
@@
 \item We explicitly gave the expression of the self-interaction term
-  in the analytical differentiation, which was proved to dominant the
+  in the analytical differentiation, which was proved to \redc{dominate} the
   force error in low density systems~\cite{cerutti2009staggered}.  The
-  expression helped removing the self-interaction term at a comparatively low
+  expression helped \redc{to remove} the self-interaction term at a comparatively low
   computational cost.
@@
   differentiation, to the leading order of the force error.
-  The staggered mesh analytical differentiation requires only one half
+  The staggered mesh analytical differentiation requires only one half \redc{the}
   FFTs as the ik-differentiation, so the former may be preferable
@@
 \end{align}
-Inserting it into Eqn.~\eqref{eqn:c-error-1}, also neglect the high
+Inserting \redc{this} into Eqn.~\eqref{eqn:c-error-1} \redc{while neglecting} the high
 frequency terms yields

### 2012-07-03 longRange.hetero/alltext/publish/fig.new/error.rand_water_1_bond.charge0.834.box14.9x7.4x7.4.b2.500.r1.40.n6.K121x061x061/parameters.spme.ana.selfCorr.real.sh
add conf 5

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-nframe_real_error=1
+nframe_real_error=5
 nframe_traj=100
 config_pool=~/study/longRange.hetero/profile.test/config.pool
 water_template=$config_pool/water.one_peak

### 2012-07-09 longRange.hetero/profile.test/template/tools/scripts/spme.st.h2o.gr.esti.sh
add spme.st.h2o.gr.esti.sh

@@ -1,0 +1,35 @@
+#!/bin/bash
+
+source parameters.sh
+
+if test ! -d $record_dir; then
+    echo "no record dir $record_dir"
+    exit
+fi
+if test ! -d $errors_dir; then
+    echo "# no errors dir $errors_dir, make it"
+    mkdir -p $errors_dir
+fi
+rm -f $errors_dir/parameters.spme.st.h2o.gr.esti.sh
+cp parameters.sh $errors_dir/parameters.spme.st.h2o.gr.esti.sh
+
+mylog=spme.st.h2o.gr.esti.log
+rm -f $mylog
+touch $mylog
+
+make -C -j8 ./tools/analyze/ &>> make.log
+
+# esti the rec error
+if test ! -f $record_dir/water.gro; then
+    echo "# no orientation file $record_dir/water.gro"
+    exit
+fi
+./tools/analyze/error.spme.st.h2o.gr -t $record_dir/traj.xtc -q $record_dir/charge.tab --my-charge $charge --kx $cal_Kx --ky $cal_Ky --kz $cal_Kz --beta $beta --order $cal_order --orientation $record_dir/water.gro --rhoMol $rhoh --gr-up $gr_up --rdf-OO $record_dir/rdf.oo.1e-2.xvg --rdf-OH $record_dir/rdf.oh.1e-2.xvg --rdf-HH $record_dir/rdf.hh.1e-2.xvg &>> $mylog
+mv -f rho.x.avg.out $errors_dir/
+mv -f error.out $errors_dir/esti.rec.spme.st.h2o.gr.error.out
+mv -f meanf.out $errors_dir/esti.rec.spme.st.h2o.gr.meanf.out
+
+# combine rec with dir
+./tools/analyze/combine.error --dir-meanf $errors_dir/esti.dir.meanf.out --rec-meanf $errors_dir/esti.rec.spme.st.h2o.gr.meanf.out  --dir-error $errors_dir/esti.dir.error.out --rec-error $errors_dir/esti.rec.spme.st.h2o.gr.error.out --output-error $errors_dir/esti.spme.st.h2o.gr.error.out --output-meanf $errors_dir/esti.spme.st.h2o.gr.meanf.out &>> $mylog
+
+mv -f make.log $mylog $errors_dir

### 2012-07-09 longRange.hetero/profile.test/template/parameters.sh
add gr_up to parameter

@@ -61,6 +61,7 @@ cal_Ky=61
 cal_Kz=61
 cal_order=6
 real_h=0.5
+gr_up=0.6
 
 # regulate parameters. DO NOT MOVE
 cal_rcut=`printf "%.2f" $cal_rcut`

### 2012-07-09 longRange.hetero/profile.test/template/error.esti.spme.sh
improve error.esti.spme.sh

@@ -24,6 +24,8 @@ if echo $project_name | grep -v rand | grep water &> /dev/null; then
     ./tools/scripts/spme.ana.h2o.esti.sh
     echo "# esti spme st h2o"
     ./tools/scripts/spme.st.h2o.esti.sh
+    echo "# esti spme st h2o"
+    ./tools/scripts/spme.st.h2o.gr.esti.sh
 fi
 
 gp_file_names="pl.water.ana.error.gp pl.water.ik.error.gp pl.ana.error.gp  pl.ana.meanf.gp  pl.ik.error.gp  pl.ik.meanf.gp"

### 2012-07-09 longRange.hetero/alltext/publish/resubmit/lett.tex
back up

@@
 \documentclass[a4paper]{article}
+
+\usepackage[dvips]{graphicx}
 
@@
 
+\textit{ Cosmetically, the authors should combine the two figures
+  showing the charge distributions of Examples 1 and 2, to ensure they
+  appear side-by-side in the published version.
+}
+
+We delete Fig.3 and plot the charge distribution of Example 2 together
+with Example 1 in the new Fig.1. Changes to the caption and
+descriptions are maded correspondingly.\\
+
 \textit{
-Cosmetically, the authors should combine the two figures showing the charge distributions of Examples 1 and 2, to ensure they appear side-by-side in the published version.
+The authors are reasonable to focus on the error arising from the
+reciprocal space approximations in the various P3M-related methods;
+the error arising from the direct space part of the calculation is
+simpler to assess.  However, because the authors give so much
+attention to SPME and the Staggered Mesh method which, as published,
+built on SPME, the authors should include some plot of the effect of
+grid spacing, Gaussian smoothing function width (Ewald coefficient),
+and interpolation order -- these are the determinants of the accuracy of
+the reciprocal space calculation in these fast methods.  How does the
+estimator do in terms of getting the various trends correct?  What is
+the effect of correlated charge positions on the error and the
+estimates under changing interpolation order?  This is at the heart of
+the difference between ik- and analytic differentiation that the
+authors have otherwise carefully investigated.  It would also be
+helpful to see a plot of the error estimator’s performance as a
+function of the “near neighbor” definition.  Define near neighbors
+strictly by length, and plot the error estimator's accuracy as a
+continuous function of the near neighbor cutoff.  Extra credit for
+detailing the computation time as a function of the same parameter!
 }\\
 
-The authors are reasonable to focus on the error arising from the reciprocal space approximations in the various P3M-related methods; the error arising from the direct space part of the calculation is simpler to assess.
-However, because the authors give so much attention to SPME and the Staggered Mesh method which, as published, built on SPME, the authors should include some plot of the effect of grid spacing, Gaussian smoothing function width (Ewald coefficient), and interpolation order—these are the determinants of the accuracy of the reciprocal space calculation in these fast methods.
-How does the estimator do in terms of getting the various trends correct?
-What is the effect of correlated charge positions on the error and the estimates under changing interpolation order?
-This is at the heart of the difference between ik- and analytic differentiation that the authors have otherwise carefully investigated.
-It would also be helpful to see a plot of the error estimator’s performance as a function of the “near neighbor” definition.
-Define near neighbors strictly by length, and plot the error estimator's accuracy as a continuous function of the near neighbor cutoff.
-Extra credit for detailing the computation time as a function of the same parameter!
+\textit{
+One other point of discussion that might be relevant to this paper is
+the significance of the results on force-shifted coulomb interactions
+(see the simulation methods of Valerie Dagget and colleagues, or the
+Wolfe Method as reviewed in J. Chem. Phys. 124:234104 and elsewhere).
+These methods, based strictly on local “electrostatic” interactions
+computed by modifying Coulomb’s law, are often trotted out as
+alternatives to Ewald summation though their application is still
+limited (which is, in the opinion of this reviewer, as it should be).
+A principal assumption of these methods, which is often used
+circuitously to defend their application, is that real systems are
+locally neutral or that electrostatic correlations decay on the length
+scale of a few water layers.  Wang and colleagues may be able to
+analyze these methods, provide insights into the appearance of their
+validity, and identify their limitations rigorously.  A formal
+analysis of these methods is not required for this paper, but a
+possible direction the authors might explore in the future.
+}
 
-One other point of discussion that might be relevant to this paper is the significance of the results on force-shifted coulomb interactions (see the simulation methods of Valerie Dagget and colleagues, or the Wolfe Method as reviewed in J.
-Chem.
-Phys.
-124:234104 and elsewhere).
-These methods, based strictly on local “electrostatic” interactions computed by modifying Coulomb’s law, are often trotted out as alternatives to Ewald summation though their application is still limited (which is, in the opinion of this reviewer, as it should be).
-A principal assumption of these methods, which is often used circuitously to defend their application, is that real systems are locally neutral or that electrostatic correlations decay on the length scale of a few water layers.
-Wang and colleagues may be able to analyze these methods, provide insights into the appearance of their validity, and identify their limitations rigorously.
-A formal analysis of these methods is not required for this paper, but a possible direction the authors might explore in the future.
+We gratefully thank the reviewer for the suggestion of an interesting
+extension of the present work.\\
 
-The authors have done an excellent job of manipulating the mathematical foundations of these fast electrostatics methods.
-With minor modifications and extensions of the study, which this reviewer does not intend to be onerous, this work should be published without further hindrance.
+\textit{
+The authors have done an excellent job of manipulating the
+mathematical foundations of these fast electrostatics methods.  With
+minor modifications and extensions of the study, which this reviewer
+does not intend to be onerous, this work should be published without
+further hindrance.
+}\\
 
-Reviewer  2 Comments:
+\noindent
+Reviewer  2 Comments:\\
 
-The article deals with the derivation of an accurate error estimate for the Ewald and SPME mesh Ewald method that can be used for inhomogeneous and correlated charged systems.
+\textit{ The article deals with the derivation of an accurate error
+  estimate for the Ewald and SPME mesh Ewald method that can be used
+  for inhomogeneous and correlated charged systems.
+}
 
-Error estimates for long range algorithms are always useful for periodic charged systems, since due to the long range nature, no exact calculation is possible, but one rather has to truncate the interactions at some point, and hence is forced to introduce errors.
-Ideally, one would like to know for a specific method before doing an expensive calculation how to choose method parameters such that I reach a certain accuracy.
-Such error estimates have been developed in the past, but normally only under the assumption that the charges are randomly distributed.
-Here, the authors extend these error estimates to the very relevant cases of inhomogeneous and/or correlated systems.
+\textit{
+Error estimates for long range algorithms are always useful for
+periodic charged systems, since due to the long range nature, no exact
+calculation is possible, but one rather has to truncate the
+interactions at some point, and hence is forced to introduce errors.
+Ideally, one would like to know for a specific method before doing an
+expensive calculation how to choose method parameters such that I
+reach a certain accuracy. Such error estimates have been developed in
+the past, but normally only under the assumption that the charges are
+randomly distributed. Here, the authors extend these error estimates
+to the very relevant cases of inhomogeneous and/or correlated systems.
+}
 
-I find the article in general very readable and informative, and also suited for this journal.
-I have just a few comments that the authors might want to take into account in a minor revised version, before this article, in my opinion, is ready for publication:
+\textit{
+  I find the article in general very readable and informative, and
+  also suited for this journal. I have just a few comments that the
+  authors might want to take into account in a minor revised version,
+  before this article, in my opinion, is ready for publication:
+}\\
 
@@
 
-Reviewer 3 Comments:
+\vskip 1cm
+\noindent
+Reviewer 3 Comments:\\
 
-The authors have introduced a way to study electrostatic force errors in correlated systems by assuming that the dominant correlations are short-ranged which should usually work--they acknowledge this may not work for systems near phase transitions.
-I like this paper and would like to see it published after minor complaints are addressed.
+\textit{
+The authors have introduced a way to study electrostatic force errors
+in correlated systems by assuming that the dominant correlations are
+short-ranged which should usually work--they acknowledge this may not
+work for systems near phase transitions. I like this paper and would
+like to see it published after minor complaints are addressed.
+}
 
-Firstly, the main contribution is to introduce a way to rapidly evaluate the force error, including that due to short ranged (bonded) pair interactions.
-Some readers may be confused by this, since bonded pair electrostatic interactions are considered to be NOT CALCULATED.
-However, in Ewald like methods the reciprocal contribution cannot be easily excluded for atom pairs and is surprisingly large even for bonded pairs.
-I think including this point somewhere in the discussion will help many readers.
-Note that errors for bonded pairs may be at least partly responsible for the disappointing performance of multiple time step methods.
-(they are high frequency in time)
+\textit{
+Firstly, the main contribution is to introduce a way to rapidly
+evaluate the force error, including that due to short ranged (bonded)
+pair interactions. Some readers may be confused by this, since bonded
+pair electrostatic interactions are considered to be NOT
+CALCULATED. However, in Ewald like methods the reciprocal contribution
+cannot be easily excluded for atom pairs and is surprisingly large
+even for bonded pairs. I think including this point somewhere in the
+discussion will help many readers. Note that errors for bonded pairs
+may be at least partly responsible for the disappointing performance
+of multiple time step methods. (they are high frequency in time)
+}
 
-I am curious about the fact that correlation reduces force errors compared to usual estimates.
-I wonder if this is somehow due to electrostatic forces on bonded pairs being anti-correlated due to opposing charge signs e.g.
-on Oxygen and Hydrogens of H2O.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{correlation.eps}
+  \caption{The schematic plot of two interacting water molecules.
+    When we calculate the force error of the left oxygen atom, the
+    correlation with its bonded hydrogens are not considered, but
+    the correlations within any neighboring molecule are considered,
+    as indicated by the solid lines with two arrows.}
+  \label{fig:1}
+\end{figure}
 
+We define the force error by inserting a testing charge into the
+considered system, and comparing the calculated and exact force on
+it. In the considered water system (Example 3), the subtle difference
+between this setting to the realistic case is that the testing charge
+has no correlation with the charges in the system, while any real
+charge is bonded to two neighboring charges (via H-O bond and H-O-H
+angle).  Therefore, the error estimate does not consider the
+correlation between a charge and the its bonded neighbors, but it does
+consider all bonding correlations within any neighboring molecule (see
+Fig.~\ref{fig:1} of this letter). This is consistent with the usually
+setting of bonded pair atoms, as mentioned by the reviewer, the
+electrostatic interaction between them should not be calculated.
+
+We therefore added the following sentence to make this point clearer:
+\textbf{
+  We define the force error by inserting a
+testing charge into the water system, and comparing the
+calculated and exact force on it. This definition implicitly assumes
+the independency between the testing particle and the
+system. Therefore, it sould be noted that the correlation error
+estimate (20)
+neglects the possible bonding
+of the testing particle to any hydrogen/oxygen atom, and
+calculates all bonded correlations
+within its {neighboring} molecules. This is consistent
+with the usual setting of the bonded atoms: the electrostatic interaction
+between them is considered to be \emph{not} calculated.}
+
+The inclusion of the correlation between the testing
+charge and the system is also possible, but this is beyond the scope
+of the present paper, and will be addressed in the following studies.\\
+
+% Therefore, in all the estimates, the error due to the
+% bonded pair interactions is automatically eliminated by the
+% definition.
+
+% The inclusion of the correlation between the testing
+% charge and the system is also possible, but this is beyond the scope
+% of the present paper, and will be addressed in the following studies.
+% To make this point clearer, we add the following sentence:
+% \textbf{Here we implicitly assumes that the testing particle is independent
+% with the system, but it is not the case in real systems. For example,
+% in the water system considered in Sec.III, each atom is bonded
+% to two neighboring atoms (via the rigid H-O bond and H-O-H angle).
+% Fortunately, this may not be a big problem, firstly because the bonded pair
+% electrostatic interacions are considert to be \emph{not} calculated;
+% secondly because the non-bonded pair correlation contributes only
+% minority part to the total error (see also Sec.III).}
+
+% As a matter of fact, in Example 3, the electrostatic interactions
+% within one water molecule is \emph{not} calculated. This may not be
+% computationally economic in practice, however, it is important to
+% remove it in our theoretical study, becuase, as mensioned by the
+% reviewer, the bonded pair electrostatic interaction is considered to
+% be not calculated.
+
+\textit{
+I am curious about the fact that correlation reduces force errors
+compared to usual estimates. I wonder if this is somehow due to
+electrostatic forces on bonded pairs being anti-correlated due to
+opposing charge signs e.g. on Oxygen and Hydrogens of $H_2O$.
+}
+
+As far as we concerned, it is not possible to test this point
+directly, but we think it is a likely explanation to the observed
+phenomenon.  Consider the extreme case: wihin one molecule, the
+hydorgen and oxygen atoms locate at the same point (strongest
+correlation), then the positive and negative charge cancels, so the
+error vanishes. In case of TIP3P water model, the H-O distence is 0.1~nm and
+the H-H distance is 0.16~nm, which are much smaller than the typical
+center-of-mass distance between two neighboring molecules (0.31~nm).
+We added this point to the paper.
+\\
+
+\textit{
 Otherwise I have a number of minor grammatical and typo complaints:
+}
 
-page 3 lines 9,14  The term "research" could be replaced by "papers" on line 9 and "paper" on 14
-another possibility is "manuscript"
-page 3 line 27 "which assume the error" $\rightarrow$ "which assumes the error"
-page 3 line 43 "nearest neighbor approximation of correlation error": insert "the" before "correlation"
-page 3 line 54 "we consider the system" $\rightarrow$ "we consider a system"
-page 3 line 55 "is composed by N" $\rightarrow$ "is composed of N"
-page 3 line 56 "the force of a" $\rightarrow$ "the force on a"
-*page 4 line 18 "error estimate for the error force" seems like 1st "error' is unnecessary
-              perhaps replace with "following estimate for the error force"---also the term "error force" could be
-              replaced with "force error" here and elsewhere and I think the text would flow better
-page 6 line 16 "Most of the error estimates" $\rightarrow$ "Most previous error estimates"
-page 6 line 32: "Analog to" $\rightarrow$ "Analogous to"
-page 7 line 3 "A non-varnishing" $\rightarrow$ "A non-vanishing"
-page 7 line 10,11: "the locally neutral condition" $\rightarrow$ "the local neutrality condition"
-page 7 line 21: "which is still not applicable" $\rightarrow$ "which is still not tractable" or maybe "computationally feasible"
-page 7 line 46: "Then the second part" $\rightarrow$ "Then the second term". Also on line 54 "part" $\rightarrow$ "term"
-page 7 line 52: "small comparing with" $\rightarrow$ "small compared with" or "small in comparison with". same for pg 8 line 16
-page 8 line 42: "Ensemble averages is taken" $\rightarrow$ "Ensemble averages are taken"
-page 10 line 1: "ia the reciprocal" $\rightarrow$ "are the reciprocal"
-page 11 line 8: "becomes not applicable" as in page 7 line 21 I think "intractable" is better here
-page 11 line 10: "PME ans SPME" ; "ans" $\rightarrow$ "and"
-page 12 line 7: "only little" $\rightarrow$ "only a small"
-page 14 line 33: "It is shown that the self-interaction error dominate" $\rightarrow$ "It has been shown that the sel-interaction
-                   error dominates"
-page 17 line 49: "Twice as larger" $\rightarrow$ "Twice as large"
-page 18 line 43: "cut-offed" $\rightarrow$ "truncated"
-page 18 line 47: "are consistent very well with" $\rightarrow$ "are consistently accurate compared with" or "accurately track"
-page 18 line 60: "reduces by more than" $\rightarrow$ "is reduced by more than"
-page 19 line 34: "FFTs than" $\rightarrow$ "FFTs compared to"
-page 19 line 55: again "cut-offed" $\rightarrow$ "truncated"
-page 20 line 34: "was reported" $\rightarrow$ "were reported"
-page 20 line 35: "varnish" $\rightarrow$ "vanish"
-page 20 line 41: "error estimates consist with" $\rightarrow$ "error estimates are consistent with" or
-                                                  "error estimates accurately track"
+The grammatical mistakes and typos have been corrected according to the reviewer.
+% We want to explain two points:\\
 
-page 23 line 57: "composed by three additive" $\rightarrow$ "composed of three additive"
-*page 24 line 11: "the error is of good property" Not clear what is meant. Do you mean total error is not
-                 contaminated by this?
-page 24 line 18: "was proved to dominant" $\rightarrow$ "was proved to dominate"
-page 24 line 19: "helped removing" $\rightarrow$ "helped to remove"
-page 24 line 35: "only one half FFTs" $\rightarrow$ "only one half the FFTs"
-page 27, line 15: "Inserting it into Eqn (17), also neglect" $\rightarrow$ "Inserting this into Eqn (17) while neglecting"
+% \textit{
+% page 4 line 18 ``error estimate for the error force'' seems like 1st ``error'' is unnecessary
+%               perhaps replace with ``following estimate for the error force''---also the term ``error force'' could be
+%               replaced with ``force error'' here and elsewhere and I think the text would flow better
+%             }
+
+% We use ``error force'' because we want to stress it is a force, not a error, which may be a scalor, and be confused with the ``RMS force error''.\\
+
+% \textit{
+% page 24 line 11: ``the error is of good property'' Not clear what is meant. Do you mean total error is not
+%                  contaminated by this?
+%                }
+
+%                Yes, the we removed ``the error is of good property'',
+%                the logic of the sentence is
 

### 2012-07-09 longRange.hetero/alltext/publish/resubmit/main.tex
back up

@@
 exert force on them.
+% \recheck{
+% Here we implicitly assumes that the testing particle is independent
+% with the system, but it is not the case in real systems. For example,
+% in the water system considered in Sec.~\ref{sec:tmp3}, each atom is bonded
+% to two neighboring atoms (via the rigid H-O bond and H-O-H angle).
+% Fortunately, this may not be a big problem, firstly because the bonded pair
+% electrostatic interacions are considert to be \emph{not} calculated;
+% secondly because the non-bonded pair correlation contributes only
+% minority part to the total error (see also Sec.~\ref{sec:tmp3}).
+% }
 The \emph{error force} is defined by the difference between
@@
   \vert\v K(\v r , \v r')\vert^2\rho_{q^2}(\v r')\,\d d\v r'
-  \\
+  \\\label{eqn:start-corr}
   & +
@@
 charge of $q_{\textrm{H}} = +0.417e$ and each oxygen atom carries a
-charge of $q_{\textrm{O}} = -0.834e$. Within one molecule, the H-O
-bond and H-O-H angle are rigid, so the correlation within one molecule
-is considered important.  Therefore, in this case, we define the nearest neighbor by the
-atoms within the same water molecule.  Denoting the index set of the oxygen
-atoms by $\Omega_{\textrm{O}}$, and the index set of the hydrogen
-atoms by $\Omega_{\textrm{H}}$, we have:
+charge of $q_{\textrm{O}} = -0.834e$.  \recheck{ There are two types
+  of correlation in the system: the bonded correlation and the
+  non-bonded correlation. The former originates from the rigid H-O
+  bond and H-O-H angle within one molecule. The latter originates from
+  the intermolecular non-bonded interaction: the van der Waals and
+  the electrostatic interaction.
+}
+% Within one molecule, the H-O bond and
+% H-O-H angle are rigid, so the correlation within one molecule is
+% considered important.
+% Therefore, in this case,
+
+We firstly consider the bonded correlation, and define the nearest
+neighbor by the atoms within the same water molecule.  Denoting the
+index set of the oxygen atoms by $\Omega_{\textrm{O}}$, and the index
+set of the hydrogen atoms by $\Omega_{\textrm{H}}$, we have:
 \begin{align}\nonumber
@@
 where ``$\wedge$'' denotes the forward Fourier transform. By denoting
-\begin{align}
+\begin{align}\label{eqn:tom}
   \hat T_{\textrm{O}}(\v m)
@@
   q_{\textrm{H}}\,e^{-2\pi i\v m\cdot\v s_{\textrm{O}}}
-  \rangle,\\
+  \rangle,\\\label{eqn:thm}
   \hat T_{\textrm{H}}(\v m)
@@
 molecule. 
-
+\recheck{
+It sould be noted that we define the force error by inserting a
+testing charge into the water system, and comparing the
+calculated and exact force on it. This definition implicitly assumes
+the independency between the testing particle and the
+system. Therefore, the correlation error
+estimate~\eqref{eqn:c-error-water}
+actually neglects the correlation
+of the testing particle to the system, and
+calculates the error from all bonded correlations
+within its {neighboring} molecules, as illustrated by Fig.~\ref{fig:tmp-add0}.
+This is consistent
+with the usual setting of the bonded atoms: the electrostatic interaction
+between them is considered to be \emph{not} calculated.
+Throughout this paper, we also do not calculated this interaction.
+% the intramolecular non-bonded
+% interaction is not calculated.
+}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{correlation.1.eps}
+  \caption{The schematic plot of two interacting water molecules.
+    When we calculate the force error of the left oxygen atom, the
+    correlation with its bonded hydrogens are not considered, but
+    the correlations within any neighboring molecule are considered,
+    as indicated by the solid lines with two arrows.}
+  \label{fig:tmp-add0}
+\end{figure}
+
+\recheck{ If the system is homogeneous and isotropic, the pair
+  correlation function $\rho^{(2)}(\v r', \v r'')$ in
+  Eqn.~\eqref{eqn:start-corr} can be represented by the radial
+  distribution functions (RDFs).
+  Following the same discussion as the bonded correlation,
+  the non-bonded correlation error can also be estimated.
+  The functions $T_{\textrm{O}}$ and $T_{\textrm{H}}$
+  are given by
+  \begin{align}\label{eqn:nb-nna-1}
+    \hat T_{\textrm{O}} (\v m)
+    &= \int_0^{\infty}
+    [q_{_{\textrm{H}}} \rho_{_{\textrm{H}}} \tilde g_{_{\textrm{OH}}}(r)
+    +q_{_{\textrm{O}}} \rho_{_{\textrm{O}}} \tilde g_{_{\textrm{OO}}}(r)]
+    \,\frac{\sin(2\pi m r)}{2\pi mr}\,4\pi r^2 \d dr,\\\label{eqn:nb-nna-2}
+    \hat T_{\textrm{H}} (\v m)
+    &= \int_0^{\infty}
+    [q_{_{\textrm{H}}} \rho_{_{\textrm{H}}} \tilde g_{_{\textrm{HH}}}(r)
+    +q_{_{\textrm{O}}} \rho_{_{\textrm{O}}} \tilde g_{_{\textrm{OH}}}(r)]
+    \,\frac{\sin(2\pi m r)}{2\pi mr}\,4\pi r^2 \d dr,
+  \end{align}
+  where
+  $\tilde g_{_{\textrm{OO}}}(r) = g_{_{\textrm{OO}}}(r) - 1$,
+  $\tilde g_{_{\textrm{OH}}}(r) = g_{_{\textrm{OH}}}(r) - 1$ and
+  $\tilde g_{_{\textrm{HH}}}(r) = g_{_{\textrm{HH}}}(r) - 1$.
+  $g_{_{\textrm{OO}}}(r)$, $g_{_{\textrm{OH}}}(r)$ and $g_{_{\textrm{HH}}}(r)$
+  are the RDFs of oxygen-oxygen, oxgygen-hydrogen and hydrogen-hydrogen,
+  respectively. $\rho_{_{\textrm{H}}}$ and $\rho_{_{\textrm{O}}}$ are
+  the homogeneous number densities
+  of the hydrogen and oxgygen atoms, respectively.
+  For a short-range correlated system, the RDFs converges to 1
+  as $r$ goes to infinity, so the integrals in Eqn.~\eqref{eqn:nb-nna-1}
+  and \eqref{eqn:nb-nna-2} are converging. Practically, we integrate
+  them to a upper bond denoted by $R_g$.
+
+  It can be seen that both the bonded and non-bonded correlation error
+  estimates require some uniformity of the correlation in the system:
+  the bonded estimate requires the uniformity of the water
+  direction, while the non-bonded estimate requires the uniformity
+  of the density distribution and the isotropicity of the system.
+  These restrictions should be carefully investigated before using
+  these error estimates.
+  If the restrictions are seriously perturbed,
+  one can either uses these estimates for 
+  some regions (or sub-system of the whole system) that
+  still preserve the uniformity,
+  or estimate the correlation error at the cost of
+  $\mathcal O(N^2\log N)$, if the correlation in the system is highly
+  inhomogeneous.  
+  % one can either estimate the correlation error at the cost of
+  % $\mathcal O(N^2\log N)$, or estimate the correlation error for
+  % some regions (or sub-system of the whole system) that
+  % still preserve those uniformity.
+
+}
 % For the second term, do variable change $\v r'' = \v r' + \v s$, we have:
@@
 order:
-\begin{align}
+\begin{align}\label{eqn:leading-order-1}
   \frac12\, [A(\v m, \v r) + A(\v m, \v r+\v s)]
@@
 
-For the analytical differentiation, similarly we have: $\frac12\,[\v
-B(\v m,\v r) + \v B(\v m, \v r+\v s)] \approx 0$. Therefore, from
+For the analytical differentiation, similarly we have:
+\begin{align}\label{eqn:leading-order-2}
+\frac12\,[\v
+B(\v m,\v r) + \v B(\v m, \v r+\v s)] \approx 0.  
+\end{align}
+Therefore, from
 Eqn.~\eqref{eqn:ana.error.force}, the error force of the staggered
@@
   \centering
-  \includegraphics[]{rand1.rho.eps}
+  \includegraphics[]{fig.rho.eps}
   \caption{
-    The charge number density  of Example 1.
-    The red line: positive charge. The blue line: negative charge.
+    The charge number density  of Example 1 and 2.
+    The red solid line: positive charge of Example 1.
+    The red dashed line: positive charge of Example 2.
+    The blue line: negative charge.
     Since the charges are uniformly distributed
@@
   }
-  \label{fig:tmp-rho1}
+  \label{fig:tmp-rho}
 \end{figure}
@@
 are randomly generated subjecting to the number density shown in
-Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
+Fig.~\ref{fig:tmp-rho}.  The number density of the  positive
 charge   is twice as large as that of the negative charge,
@@
 
-\begin{figure}
-  \centering
-  % \includegraphics[width=.48\textwidth]{fig.new/rand2/fig.rho.eps}
-  \includegraphics[]{rand2.rho.eps}
-  \caption{Charge distribution of Example 2. The red line
-    denotes the positive charge distribution, while the blue line
-    denotes the negative charge distribution. Since all distributions
-    are uniform on $y$ and $z$ direction, they are plotted as a
-    function of $x$.}
-  \label{fig:tmp-rho2}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   % \includegraphics[width=.48\textwidth]{fig.new/rand2/fig.rho.eps}
+%   \includegraphics[]{rand2.rho.eps}
+%   \caption{Charge distribution of Example 2. The red line
+%     denotes the positive charge distribution, while the blue line
+%     denotes the negative charge distribution. Since all distributions
+%     are uniform on $y$ and $z$ direction, they are plotted as a
+%     function of $x$.}
+%   \label{fig:tmp-rho2}
+% \end{figure}
 
@@
 are moved to the region where the density of negative charge is low,
-see Fig.~\ref{fig:tmp-rho2}.
+see Fig.~\ref{fig:tmp-rho}.
 In this system, the negative charges are separated from their
@@
 The number densities of oxygen and hydrogen atoms
-are the same as those shown by Fig.~\ref{fig:tmp-rho1}.
+are the same as Example 1, see Fig.~\ref{fig:tmp-rho}.
 50 consequential snapshots of
@@
     Blue: the original analytical differentiation.
-    ``$\times$'': the real error.
+    ``$\times$'' or ``+'': the real error.
     Dashed line: the error estimate, without the correlation error estimate.
-    Solid  line: the error estimate, with the nearest neighbor
+    Solid  line: the error estimate, with the \recheck{bonded} nearest neighbor
     approximation of the correlation error.
@@
     The black arrows indicate the improvement
-    of error estimate by including nearest neighbor
+    of error estimate by including \recheck{bonded} nearest neighbor
     approximation of correlation error.
@@
   \centering
-  \includegraphics[]{fig.water.ana.st.error.eps}
+  \includegraphics[]{fig.water.ana.st.error.more.eps}
   \caption{
@@
     analytical differentiation.
-    Blue ``$+$'': the real error of the staggered mesh
+    \recheck{
+    Blue ``$\boxdot$'': the real error of the
+    randomized COM testing case, calculated by
+    the staggered mesh analytical differentiation.}
+    Green ``$+$'': the real error of the staggered mesh
     ik-differentiation, it is overlapping with the analytical differentiation.
     Blue dashed line: the error estimate, without the correlation error.
-    Blue solid line: the error estimate, with the nearest
+    Blue solid line: the error estimate, with the \recheck{bonded} nearest
     neighbor approximation of the correlation error.
+    \recheck{
+      Short blue dotted line: the error estimate
+    for the liquid phase including both the bonded and non-bonded
+    nearest neighbor approximations.}
     The RMS errors are averaged over $y$ and $z$ directions, and are
@@
     The black arrow indicates the improvement
-    of error estimate by including nearest neighbor
+    of error estimate by including \recheck{bonded} nearest neighbor
     approximation of correlation error.
+    \recheck{
+    The black dotted arrow indicates the improvement of
+    further including non-bonded nearest neighbor approximation.}
   }   
@@
 actually  reduces the error in the force computation.
-Currently we have no explanation for this phenomena.
+%Currently we have no explanation for this phenomena.
 % Anyway, the correlation error $\mathcal
@@
 % estimate.
-By including the nearest neighbor approximation of the
+\recheck{ Thanks to the reviewer of this paper, one likely
+  explanation is that the electrostatic forces
+  exerted by bonded pairs
+  being anti-correlated due to opposing charge signs.
+  The extreme case is the overlapping of one oxygen atom with two
+  hydrogen atoms, the charges cancels, so the error vanishes.
+  In case of the TIP3P water model, the H-O distence is 0.1~\textsf{nm},
+  which is much smaller than the typical
+  center-of-mass distance between two neighboring water
+  molecules (0.31~\textsf{nm}),
+  therefore, the bonding correlation tends to neutralize the molecule
+  and reduce the force error.
+}
+By including the \recheck{bonded} nearest neighbor approximation of the 
 correlation error, the quality of all error estimates is improved greatly,
-as indicated by the arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
+as indicated by the solid arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
 Now the RMS errors of ik-differentiation, analytical differentiation
@@
 for the parameter tuning application.
-The great improvement by the nearest neighbor approximation 
-means that  among all atomic
-correlates (i.e. the rigid H-O bond and H-O-H angle, the van der Waals interactions,
-the hydrogen bonds, etc.), the rigid bond and angle correlation
-% (rigid
-% modeling of H-O bond and H-O-H angle)
-is the most important one, and all
-the rest account for the remaining discrepancy between the estimated and real
-error.
+\recheck{
+  Since we
+  mainly worry about the validity of the leading order
+  approximation made in
+  Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+  we further varify the error estimate
+  of the staggered mesh Ewald method 
+  by calculating
+  the real error of the following testing case
+  (we call it the randomized COM testing case):
+  randomly redistribute the water molecules according to the same
+  center-of-mass (COM) distribution, while keeping
+  the bonds and direction of the molecules unchanged.
+  Since the non-bonded correlation is removed from this case,
+  a good consistency (see Fig.~\ref{fig:water-error}, and later
+  Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4}) of its
+  actual error with the estimate validates the correctness of 
+  the error estimate and 
+  the leading order
+  approximation~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+
+  In this example, the non-bonded nearest
+  neighbor approximation cannot be used directly in this example, 
+  because the system is inhomogeneous, and the RDFs are ill-defined.
+  However, the system contains a comparatively homogeneous liquid region,
+  where we can define the RDFs and calculate the non-bonded
+  nearest neighbor
+  approximation. The result error estimate is presented by the
+  dashed blue line in Fig.~\ref{fig:water-error}.
+  The upper bond $R_g$ for integrating Eqn.~\eqref{eqn:nb-nna-1} and
+  \eqref{eqn:nb-nna-2} is chosen to be $1.2$~\textsf{nm}. A good
+  converging with respect to the integrating rand
+  is observed (for clarity, not shown in the figure),
+  when $R_g$ is larger than $0.6$~\textsf{nm}.
+  As indicated by the figure, the error estimate is further improved.
+  However, there is still a discrepancy between the real and estimate
+  error. Currently we cannot explain. It may originate from 
+  assuming the testing particle is independent with the system, but
+  we cannot check this point, because the correlation of the testing
+  particle with the system is beyond the theoretical framework of the
+  present paper.
+  From Fig.~\ref{fig:water-error}, we conclude that
+  the bonded correlation dominate the correlation error, compared to
+  the non-bonded correlation. Therefore, if not state otherwise,
+  we only consider the bonded nearest neighbor approximation.}
+
+% The great improvement by the bonded nearest neighbor approximation 
+% means that  among all atomic
+% correlates (i.e. the rigid H-O bond and H-O-H angle, the van der Waals interactions,
+% the hydrogen bonds, etc.), the rigid bond and angle correlation
+% % (rigid
+% % modeling of H-O bond and H-O-H angle)
+% is the most important one, and all
+% the rest account for the remaining discrepancy between the estimated and real
+% error.
 
@@
 % optimization~\cite{wang2010optimizing}.
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.mesh.ik.ana.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and grid spacings.
+    Red: the direct part. Green: the original ik-differentiation.
+    Blue: the original analytical differentiation. ``$\times$'' and
+    ``+'' denote the actual error.  The solid and dashed lines denote
+    the error estimates with and without nearest neighbor
+    approximation, respectively. The plotted direct space cut-off radii are
+    $r_c = 0.9$, $1.1$, $1.3$ and  $1.7\:\textsf{nm}$. The
+    reciprocal space grid spacings $h$  are approximately
+    $0.248$, $0.124$ and $0.062\:\textsf{nm}$, corresponding to
+    grids $60\times 30\times 30$, $120\times 60\times 60$ and
+    $240\times 120\times 120$, respectively. The order of B-spline
+    interpolation is 6.
+  }
+  \label{fig:tmp-add1}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.order.ik.ana.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and interpolation orders.
+    The symbols are the same as Fig.~\ref{fig:tmp-add1}.
+    The plotted orders of B-spline interpolation are $n=4$, 6 and 8.
+    The reciprocal space grid spacings $h$ is approximately
+    $0.124\:\textsf{nm}$, corresponding to
+    a $120\times 60\times 60$ grid.
+  }
+  \label{fig:tmp-add2}
+\end{figure}
+
+\recheck{
+In Fig.~\ref{fig:tmp-add1} -- \ref{fig:tmp-add4}, we present the 
+actual and estimated RMS error of the liquid phase as a function of
+the Ewald splitting parameter $\beta$, using various cut-off radii,
+interpolation orders, and reciprocal grid spacings.
+Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add2} show the results of the
+original ik-/analytical differentiation,
+while Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4} present
+the staggered mesh ik-/analytical differentiation.
+In
+Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add3},
+the interpolation order is fixed to $n=6$,
+and we plot the actual and estimated errors using the direct space
+cut-off radii $r_c = 0.9$, $1.1$, $1.3$ and $1.7\:\textsf{nm}$, and
+the reciprocal space grid spacings $h = 0.248$, $0.124$ and
+$0.062\:\textsf{nm}$. In Fig.~\ref{fig:tmp-add2} and \ref{fig:tmp-add4}, the 
+grid spacing is fixed to $h = 0.248\:\textsf{nm}$, and
+we plot interpolation orders of $n=4$, 6 and 8.
+Like the
+homogeneous water system studied in the literature (see for
+example Ref.~\cite{wang2010optimizing, ballenegger2012convert}),
+when $\beta$ is small the direct error dominates, when  $\beta$ is
+large the reciprocal error dominates.
+Therefore, given a set of parameters ($r_c$, $n$ and $h$),
+the $\beta$ at the crossover of the direct and reciprocal errors
+achieves the nearly best accuracy and should be used in simulations.
+For all cut-off radii,
+the quality of the direct error estimate is satisfactory when the
+error is small than $10^{-1}\:\textsf{kJ/(mol nm)}$.
+It is also observed that the quality of the error estimate is better
+for larger $\beta$ than for smaller $\beta$.
+As expected, the figures show that
+the smaller grid spacing and larger interpolation order
+enable more accuracy force computation. 
+Unlike the uncorrelated testing examples 1 and 2, the actual precision of the 
+original ik- and analytical differentiation are nearly the same.
+This implies that the latter may be more preferable than
+the former for the water simulation,
+because it needs only one half FFTs as the former, which could be
+highly advantageous for massive parallel simulations.
+In most testing cases the staggered mesh ik- differentiation is
+equivalent to the staggered mesh analytical differentiation. However,
+we obsever exceptions at small $\beta$ when the interpolation order is $n=4$,
+see Fig.~\ref{fig:tmp-add4}.
+This indicates the leading order approximations to the staggered
+mesh interpolation errors,
+i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+are not satisfactory.
+Fortunately,
+this may not be a big problem, because the very small $\beta$ is seldomly
+used in practice,
+and a extremely large cut-off radius is needed to achieve the best
+efficiency for such a $\beta$. In Fig.~\ref{fig:tmp-add4} at $n=4$, the largest
+$r_c = 1.7\:\textsf{nm}$ is corresponding to a choice of $\beta$ at
+$1.9\:\textsf{nm}^{-1}$, where the ik- and analytical differentiations
+are still close.
+With the nearest neighbor approximation, the quality of the
+reciprocal error estimates is impressively improved, especially
+for the original analytical differentiation and the staggered mesh
+Ewald method.
+The same as discussed before, we also compare the error of the
+randomized COM testing case with the error esitmates. 
+In most cases, they are perfectly consistent, which strongly supports
+the bonded nearest neighbor approximation proposed by this paper.
+However, as expected, when the
+leading order approximations to the staggered
+mesh interpolation errors
+Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2} are
+not good (see $n=4$ and small $\beta$),
+the randomized COM error deviates from the error estimate.
+}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.mesh.st.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and grid spacings.
+    Red: the direct part. Green: the staggered mesh ik-differentiation.
+    Blue: the staggered mesh analytical differentiation. ``$\times$'' and
+    ``+'' denote the actual error.  The solid and dashed lines denote
+    the error estimates with and without nearest neighbor
+    approximation, respectively.
+    The error estimates for the staggered mesh ik- and analytical
+    differentiations are identical, so only the blue lines are presented.
+    The blue ``$\boxdot$'' indicates the radomized COM testing case,
+    calculated by the
+    staggered mesh analytical differentiation. The same results
+    of the ik-differentiation are not shown because they are overalpping
+    with the analytical differentiation.
+    The plotted direct space cut-off radii are
+    $r_c = 0.9$, $1.1$, $1.3$ and  $1.7\:\textsf{nm}$. The
+    reciprocal space grid spacings $h$  are approximately
+    $0.248$, $0.124$ and $0.062\:\textsf{nm}$, corresponding to
+    grids $60\times 30\times 30$, $120\times 60\times 60$ and
+    $240\times 120\times 120$, respectively. The order of B-spline
+    interpolation is 6.
+  }
+  \label{fig:tmp-add3}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.order.st.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and interpolation orders.
+    The symbols are the same as Fig.~\ref{fig:tmp-add3}.
+    The plotted orders of B-spline interpolation are $n=4$, 6 and 8.
+    The reciprocal space grid spacings $h$ is approximately
+    $0.124\:\textsf{nm}$, corresponding to
+    a $120\times 60\times 60$ grid.
+  }
+  \label{fig:tmp-add4}
+\end{figure}
 

### 2012-07-11 longRange.hetero/alltext/publish/resubmit/lett.tex
finish first revise, add figures

@@
 \begin{document}
+\noindent
+Dear Prof. Rothlisberger,\\
+
+Thank you very much for the reports. We would like to thank also the
+reviewers for the positive reports and for the suggestions, which help
+us improving the quality of the manuscript. The revisions are
+reported below in detail.\\
+
+In the revised manuscript, all the additions are marked in red, to help the
+reviewers to located them immediately in the text.\\
 
@@
 
-?
-
-\textit{
-In the introduction, the authors should probably take the perspective that SPME is a special case of P3M.
-In the opinions of the developers of SPME, the derivation differs from P3M although it leads to similar results, but even TA Darden acknowledges that the reciprocal space component of the non-smooth PME algorithm was inspired by P3M.
-It is probably best to phrase SPME as such and not offend anyone.
-The interlacing technique was first applied in the 1970s, as the authors have cited.
-It was originally a means of reducing the memory requirements of these calculations—electrostatics on the two grids were solved serially.
-Finally, the sentence “We prove that the error is decomposed…” should be changed to “We show that the error may be approximately decomposed…” to indicate that the estimator is, in the end, approximate but relevant to real systems.
+We have modified the introduction according to this point.
+Please see the 4-th line of the second paragraph of the introduction:
+\textbf{
+  This problem can be solved by repeating and comparing
+  the force calculation by
+  using different parameter sets
+  on a representative snapshot of the system,
+  see eg. Ref.[16].
+An other approach is the 
+  in-depth theoretical study
+of the error introduced by the algorithms, namely the
+error estimate,
+by which the error is described by a function of the working
+parameters...
 }\\
 
-not done\\
+\textit{ In the introduction, the authors should probably take the
+  perspective that SPME is a special case of P3M.  In the opinions of
+  the developers of SPME, the derivation differs from P3M although it
+  leads to similar results, but even TA Darden acknowledges that the
+  reciprocal space component of the non-smooth PME algorithm was
+  inspired by P3M.  It is probably best to phrase SPME as such and not
+  offend anyone.  The interlacing technique was first applied in the
+  1970s, as the authors have cited.  It was originally a means of
+  reducing the memory requirements of these
+  calculations—electrostatics on the two grids were solved serially.
+  Finally, the sentence ``We prove that the error is decomposed...''
+  should be changed to ``We show that the error may be approximately
+  decomposed...'' to indicate that the estimator is, in the end,
+  approximate but relevant to real systems.
+}
+
+We have added the comment (see the 12-th line of the 1st paragraph
+of the introduction:
+\textbf{It has been demonstrated that the SPME is actually
+  a special case of the P3M method [6,7].}
+The sentence ``We prove that the error is decomposed...'' has been
+changed to \textbf{We show that the error may be approximately
+  decomposed...}
+\\
 
@@
 
-We delete Fig.3 and plot the charge distribution of Example 2 together
-with Example 1 in the new Fig.1. Changes to the caption and
-descriptions are maded correspondingly.\\
+We delete the old Fig.3,
+and plot the charge distribution of Example 2 together
+with Example 1 in the new Fig.2. Changes to the caption and
+descriptions have been made correspondingly.\\
 
@@
 detailing the computation time as a function of the same parameter!
-}\\
+}
+
+We add new Fig. 9-12 to show how the error estimates
+with bonded nearest neighbor approximations are able to catch the
+trends of the real errors with various Ewald coefficient $\beta$, direct space
+cut-off radius $r_c$, reciprocal space grid spacing $h$ and B-spline
+interpolation order $n$.
+% These figures show the error estimate
+% with the bonded nearest neighbor approximation correctly catches the
+% trend of changing working parameters.
+
+In the revised manuscript,
+we consider two types of the correlations:
+(1) the bonded correlation
+that originates from the rigid H-O
+bond and H-O-H angle within one molecule,
+and (2) the
+non-bonded correlation or the
+intermolecular correlation that originates from
+a complex coupling of various intermolecular interaction.
+Estimates for the bonded correlation
+have already been developed by the old manuscript,
+while the non-bonded estimate
+is newly developed according to the reviewers' suggestion.
+Please note that
+both the bonded and non-bonded nearest neighbor approximations
+require some uniformity of the correlation in the system:
+the bonded estimate requires the uniformity of the water
+direction preference, while the non-bonded estimate requires the uniformity
+of the density distribution and the isotropicity of the system.
+Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
+For the non-bonded correlation,  the nearest neighbor approximation 
+is expressed in terms of the radial distribution
+functions (RDFs). In example 3, a global RDF is not well defined,
+so we calculated the RDF and nearest neighbor approximation
+only for the liquid phase, see the dotted line in Fig.7. By adding
+the non-bonded correlation, the quality of the error estimate
+is further improved.
+Also the convergence with respect to
+the neighboring range $R_g$ is investigated (Fig.8). 
+\\
 
@@
 
-Page 7, line 23:
-The definition of a discrete set of nearest neighbors $\Omega_j$ might not readily avaible in all cases.
-For example, for simple liquids it may be more feasible to use the radial distribution function $g(r)$ up to a certain radius $r_c$, where $g(r) \approx 1$ for $r > c_c$.
-Then the sum has to be replaced by an integral over $r$.
-Because of the close relation of $\rho^{(2)}$ and $g(r)$, the equations should be easy to adapt to such a notation.
+\textit{ Page 7, line 23: The definition of a discrete set of nearest
+  neighbors $\Omega_j$ might not readily avaible in all cases. For
+  example, for simple liquids it may be more feasible to use the
+  radial distribution function $g(r)$ up to a certain radius $r_c$,
+  where $g(r) \approx 1$ for $r > r_c$. Then the sum has to be
+  replaced by an integral over $r$.  Because of the close relation of
+  $\rho^{(2)}$ and $g(r)$, the equations should be easy to adapt to
+  such a notation.  }
 
-Page 15, line 45:
-I believe I saw that the for interlaced P$^3$M algorithm, which is very similar to the staggered SMPE algorithm,  the approximation to leading order of the error estimate is not justified, at least for higher precisions.
-This approximation could lead to a visible deviation from the true errors.
-In this context it might be useful to recalculate the numerical examples at higher precision.
-Usually, deviations start to be visible from about an RMS of $10^{-4}$.
+In the revised manuscript, the correlation error are considered
+in two types: 
+(1) the bonded correlation
+that originates from the rigid H-O
+bond and H-O-H angle within one molecule,
+and (2) the
+non-bonded correlation or the
+intermolecular correlation that originates from
+a complex coupling of various intermolecular interaction.
+Estimates for the bonded correlation
+have already been developed by the old manuscript,
+while the non-bonded estimate
+is newly developed according to the reviewers' suggestion.
+Please note that
+both the bonded and non-bonded nearest neighbor approximations
+require some uniformity of the correlation in the system:
+the bonded estimate requires the uniformity of the water
+direction preference, while the non-bonded estimate requires the uniformity
+of the density distribution and the isotropicity of the system, which
+are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
+%Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
+For the non-bonded correlation,  the nearest neighbor approximation 
+is expressed in terms of the radial distribution
+functions (RDFs) in the new Eqn. (21) and (22).
+In example 3, a global RDF is not well defined
+(because the system is inhomogeneous),
+so we calculated the RDF and nearest neighbor approximation
+only for the liquid phase, see the dotted line in Fig.7. By adding the
+non-bonded correlation, the quality of the error estimate
+is further improved.
+Also the convergence with respect to
+the neighboring range $R_g$ (the $r_c$ in the reviewer's comment)
+is investigated (Fig.8). 
+\\
 
-Page 16, line 34:
-Again, In the very similarly structured interlaced P$^3$M algorithm,  there are differences in accuracy between the $i\mathbf{k}$- and analytical differentiation at higher precisions.At this point it might not be justified  to assume that both can be treated in the same way.
-Similarly to the approximation of the $i\mathbf{k}$ error formula, it would be useful to do calculations at higher precision than those presented in the paper, and compare them
+\textit{ Page 15, line 45: I believe I saw that the for interlaced
+  P$^3$M algorithm, which is very similar to the staggered SMPE
+  algorithm, the approximation to leading order of the error estimate
+  is not justified, at least for higher precisions. This approximation
+  could lead to a visible deviation from the true errors. In this
+  context it might be useful to recalculate the numerical examples at
+  higher precision. Usually, deviations start to be visible from about
+  an RMS of $10^{-4}$.  }
 
-The manuscript contains a few misprints, and the language could be polished on a few occasions by a native speaker.
+\textit{ Page 16, line 34: Again, In the very similarly structured
+  interlaced P$^3$M algorithm, there are differences in accuracy
+  between the $i\mathbf{k}$- and analytical differentiation at higher
+  precisions. At this point it might not be justified to assume that
+  both can be treated in the same way. Similarly to the approximation
+  of the $i\mathbf{k}$ error formula, it would be useful to do
+  calculations at higher precision than those presented in the paper,
+  and compare them. }
+
+As far as we concerned,
+direct error estimates with the higher order terms are not easy.
+Therefore, we investigate this issue in another way:
+we compare the estimate (with non-bonded nearest neighbor
+approximation) with the real error of the randomized COM test
+(see the description of this test in page 25).
+Since the only approximation made in the estimate is the leading order
+approximation, the difference between the estimate and the real error
+of randomized COM test is actually the contribution from the higher
+order terms discarded by (48) and (53).
+In Fig. 9-12,
+we check this difference in a wide parameter range, and see in most
+cases the estimate overlaps with the real error, which means
+the leading order is a good approximation. 
+However,
+we do observe exceptions
+at large $\beta$ when the grid spacing is $h=0.248\:\textsf{nm}$,
+see Fig.11, and
+at small $\beta$ when the interpolation order is $n=4$,
+see Fig.12.
+That means the higher order terms may play a role in the staggered
+mesh interpolation errors. It also explains the unexpected discrepancy
+between the staggered mesh ik- and analytical differentiation
+at small $\beta$, $n=4$.
+\\
+
+% if the lead order
+% is a good approximation, then two consequences are implied: (1) the
+% equivalency of the staggered mesh ik- and analytical differentiation;
+% (2) the overlapping of the estimate (with non-bonded nearest neighbor
+% approximation) with the real error of the randomized COM testing case
+% (see the description of this testing case in page 25).  In Fig. 9-12
+% we check these two points for a wide parameter range, and see in most
+% cases they are correct. This provide a strong evidence for the
+% justification of the leading order approximation.
+
+\textit{ The manuscript contains a few misprints, and the language
+  could be polished on a few occasions by a native speaker.  }
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\textwidth]{correlation.eps}
-  \caption{The schematic plot of two interacting water molecules.
-    When we calculate the force error of the left oxygen atom, the
-    correlation with its bonded hydrogens are not considered, but
-    the correlations within any neighboring molecule are considered,
-    as indicated by the solid lines with two arrows.}
-  \label{fig:1}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.7\textwidth]{correlation.eps}
+%   \caption{The schematic plot of two interacting water molecules.
+%     When we calculate the force error of the left oxygen atom, the
+%     correlation with its bonded hydrogens are not considered, but
+%     the correlations within any neighboring molecule are considered,
+%     as indicated by the solid lines with two arrows.}
+%   \label{fig:1}
+% \end{figure}
 
@@
 charge is bonded to two neighboring charges (via H-O bond and H-O-H
-angle).  Therefore, the error estimate does not consider the
-correlation between a charge and the its bonded neighbors, but it does
-consider all bonding correlations within any neighboring molecule (see
-Fig.~\ref{fig:1} of this letter). This is consistent with the usually
+angle), as is illustrated by the new Fig.1.
+% Therefore, the error estimate does not consider the
+% correlation between a charge and the its bonded neighbors, but it does
+% consider all bonding correlations within any neighboring molecule (see
+% new Fig.1 of the paper).
+This definition is actually consistent with the usually
 setting of bonded pair atoms, as mentioned by the reviewer, the
-electrostatic interaction between them should not be calculated.
+electrostatic interaction between them is not calculated.
+Throughout this paper, we remove this  interaction from the
+standard long-range algorithms.
 
-We therefore added the following sentence to make this point clearer:
-\textbf{
-  We define the force error by inserting a
-testing charge into the water system, and comparing the
-calculated and exact force on it. This definition implicitly assumes
-the independency between the testing particle and the
-system. Therefore, it sould be noted that the correlation error
-estimate (20)
-neglects the possible bonding
-of the testing particle to any hydrogen/oxygen atom, and
-calculates all bonded correlations
-within its {neighboring} molecules. This is consistent
-with the usual setting of the bonded atoms: the electrostatic interaction
-between them is considered to be \emph{not} calculated.}
+% We therefore added the following sentence to make this point clearer:
+% \textbf{
+%   We define the force error by inserting a
+% testing charge into the water system, and comparing the
+% calculated and exact force on it. This definition implicitly assumes
+% the independency between the testing particle and the
+% system. Therefore, it sould be noted that the correlation error
+% estimate (20)
+% neglects the possible bonding
+% of the testing particle to any hydrogen/oxygen atom, and
+% calculates all bonded correlations
+% within its {neighboring} molecules. This is consistent
+% with the usual setting of the bonded atoms: the electrostatic interaction
+% between them is considered to be \emph{not} calculated.}
 
@@
 directly, but we think it is a likely explanation to the observed
-phenomenon.  Consider the extreme case: wihin one molecule, the
-hydorgen and oxygen atoms locate at the same point (strongest
-correlation), then the positive and negative charge cancels, so the
-error vanishes. In case of TIP3P water model, the H-O distence is 0.1~nm and
-the H-H distance is 0.16~nm, which are much smaller than the typical
-center-of-mass distance between two neighboring molecules (0.31~nm).
-We added this point to the paper.
+phenomenon.  Consider the extreme case: within one molecule, the
+hydrogen and oxygen atoms locate at the same point (strongest
+correlation), then the positive and negative charges cancel, so the
+error vanishes. In the case of TIP3P water model, the H-O distance is 0.1~nm,
+which is much smaller than the typical
+center-of-mass distance between two neighboring molecules (0.31~nm),
+therefore, the bonded correlation tends to neutralize the molecule
+and reduce the force error.
+We have added this point to the paper.
 \\

### 2012-07-11 longRange.hetero/alltext/publish/resubmit/main.tex
finish first revise, add figures

--- 2012-07-03 longRange.hetero/alltext/publish/resubmit/main.tex
@@
 (P3M) method~\cite{hockney1988computer, deserno1998mue1}.
+\recheck{
+It has been demonstrated that the SPME is actually
+a special case of the P3M method~\cite{deserno1998mue1, ballenegger2012convert}.}
 More recently, the staggered mesh or
@@
 However, the fact that the user should provide six working parameters
-for these methods may be problematic: it is difficult to try out the
+for these methods may be problematic: it is difficult to find the
 most efficient parameter set in such a 6-dimensional parameter space.
-The experiential choices may be either less accurate or wasting
-computational effort.
-This problem can be solved by an
-in-depth study of the error introduced by these algorithms, namely the
+% The experiential choices may be either less accurate or wasting
+% computational effort.
+% This problem can be solved by an
+\recheck{
+  This problem can be solved by repeating and comparing
+  the force calculation by
+  using different parameter sets
+  on a representative snapshot of the system,
+  see e.g. Ref.~\cite{abraham2011optimization}.}
+\recheck{An other approach is the 
+  in-depth theoretical study}
+of the error introduced by the algorithms, namely the
 error estimate~\cite{kolafa1992cutoff, hummer1995numerical,
@@
 dynamics (MD) simulation.  Firstly, a general error estimate
-framework for the pairwise interaction is set up. We prove that the
-error is decomposed into three additive parts: the homogeneity error,
-the inhomogeneity error and the correlation error~\cite{wang2012}.
+framework for the pairwise interaction is set up.
+\recheck{We show that the
+  error may be approximately
+  decomposed into three additive parts: the homogeneity error,
+the inhomogeneity error and the correlation error~\cite{wang2012}.}
 % These error estimates are only of theoretical interest, and
@@
 
-\subsection{Nearest-neighbor approximation of the correlation
+\subsection{Nearest neighbor approximation of the correlation
 error}
@@
 O(N^2\log N)$, which is still not \redc{tractable}.
-So we consider the nearest-neighbor approximation to reduce
+So we consider the nearest neighbor approximation to reduce
 the computational cost.
@@
 very flexible. Basically it means the nearby neighbors that are
-strongly correlated. It could also be defined by the charges falling in some
-certain neighboring range or charges connected by chemical bonds.
+strongly correlated. It could be defined \recheck{either}
+by the charges falling in some
+certain neighboring range, or \recheck{by} charges connected by chemical bonds.
 % Here ``first neighbors'' means the neighboring
@@
 charge of $q_{\textrm{H}} = +0.417e$ and each oxygen atom carries a
-charge of $q_{\textrm{O}} = -0.834e$. Within one molecule, the H-O
-bond and H-O-H angle are rigid, so the correlation within one molecule
-is considered important.  Therefore, in this case, we define the nearest neighbor by the
-atoms within the same water molecule.  Denoting the index set of the oxygen
-atoms by $\Omega_{\textrm{O}}$, and the index set of the hydrogen
-atoms by $\Omega_{\textrm{H}}$, we have:
+charge of $q_{\textrm{O}} = -0.834e$.  \recheck{ There are two types
+  of correlation in this system: (1) the bonded correlation
+  that originates from the rigid H-O
+  bond and H-O-H angle within one molecule,
+  and (2) the
+  non-bonded correlation or the
+  intermolecular correlation that originates from
+  a complex coupling of various intermolecular interaction, such as
+  the van der Waals interaction,
+  the hydrogen bonding and etc..
+% Within one molecule, the H-O bond and
+% H-O-H angle are rigid, so the correlation within one molecule is
+% considered important.
+% Therefore, in this case,
+}
+
+We firstly consider the bonded correlation, and define the nearest
+neighbor by the atoms within the same water molecule.  Denoting the
+index set of the oxygen atoms by $\Omega_{\textrm{O}}$, and the index
+set of the hydrogen atoms by $\Omega_{\textrm{H}}$, we have:
 \begin{align}\nonumber
@@
 influenced by the prefactors $T_{\textrm{O}}$ and $T_{\textrm{H}}$,
-which are accounting for the atomic correlation within one water
+which are accounting for the bonded correlation within one water
 molecule. 
-
+\recheck{
+It should be noted that we define the force error by inserting a
+testing charge into the water system, and comparing the
+calculated and exact force on it. This definition implicitly assumes
+the independency between the testing particle and the
+system, as illustrated by Fig.~\ref{fig:tmp-add0}.
+% Therefore, the correlation error
+% estimate~\eqref{eqn:c-error-water}
+% actually neglects the correlation
+% of the testing particle to the system, and
+% calculates the error from all bonded correlations
+% within its {neighboring} molecules, as illustrated by Fig.~\ref{fig:tmp-add0}.
+It is consistent
+with the usual setting of the bonded pair atoms: the electrostatic interaction
+between them is considered to be \emph{not} calculated.
+Throughout this paper, we remove this  interaction from the
+standard long-range algorithms.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{correlation.1.eps}
+  \caption{The schematic plot of two interacting water molecules.
+    When we calculate the force error of the left oxygen atom (it is now
+    a testing charge), the
+    correlation with its bonded hydrogens are not considered, but
+    the correlations within any neighboring molecule are considered
+    by the bonded nearest neighbor approximation,
+    as indicated by the solid lines with two arrows.}
+  \label{fig:tmp-add0}
+\end{figure}
+
+\recheck{
+  For the non-bonded correlation,
+  we define the nearest neighbor
+  by non-bonded atoms closer than a certain radius $R_g$ (neighboring range).
+  If the system is homogeneous and isotropic, the pair
+  correlation function $\rho^{(2)}(\v r', \v r'')$ in
+  Eqn.~\eqref{eqn:start-corr} can be represented by the radial
+  distribution functions (RDFs).
+  Following the same way as the bonded correlation,
+  the non-bonded correlation error can be estimated:
+  the functions $T_{\textrm{O}}$ and $T_{\textrm{H}}$
+  are given by
+  \begin{align}\label{eqn:nb-nna-1}
+    \hat T_{\textrm{O}} (\v m)
+    &= \int_0^{R_g}
+    [q_{_{\textrm{H}}} \rho_{_{\textrm{H}}} \tilde g_{_{\textrm{OH}}}(r)
+    +q_{_{\textrm{O}}} \rho_{_{\textrm{O}}} \tilde g_{_{\textrm{OO}}}(r)]
+    \,\frac{\sin(2\pi m r)}{2\pi mr}\,4\pi r^2 \d dr,\\\label{eqn:nb-nna-2}
+    \hat T_{\textrm{H}} (\v m)
+    &= \int_0^{R_g}
+    [q_{_{\textrm{H}}} \rho_{_{\textrm{H}}} \tilde g_{_{\textrm{HH}}}(r)
+    +q_{_{\textrm{O}}} \rho_{_{\textrm{O}}} \tilde g_{_{\textrm{OH}}}(r)]
+    \,\frac{\sin(2\pi m r)}{2\pi mr}\,4\pi r^2 \d dr,
+  \end{align}
+  where
+  $\tilde g_{_{\textrm{OO}}}(r) = g_{_{\textrm{OO}}}(r) - 1$,
+  $\tilde g_{_{\textrm{OH}}}(r) = g_{_{\textrm{OH}}}(r) - 1$ and
+  $\tilde g_{_{\textrm{HH}}}(r) = g_{_{\textrm{HH}}}(r) - 1$.
+  $g_{_{\textrm{OO}}}(r)$, $g_{_{\textrm{OH}}}(r)$ and $g_{_{\textrm{HH}}}(r)$
+  are the RDFs of oxygen-oxygen, oxygen-hydrogen and hydrogen-hydrogen,
+  respectively. $\rho_{_{\textrm{H}}}$ and $\rho_{_{\textrm{O}}}$ are
+  the homogeneous number densities
+  of the hydrogen and oxygen atoms, respectively.
+  For a short-range correlated system, the RDFs converges to 1
+  as $r$ goes to infinity, so the integrals in Eqn.~\eqref{eqn:nb-nna-1}
+  and \eqref{eqn:nb-nna-2} are convergent with respect to
+  increasing $R_g$.
+
+  Both the bonded and non-bonded nearest neighbor approximations
+  require some uniformity of the correlation in the system:
+  the bonded estimate requires the uniformity of the water
+  direction preference, while the non-bonded estimate requires the uniformity
+  of the density distribution and the isotropicity of the system.
+  These requirements should be carefully checked before using
+  these error estimates.
+  If the they are seriously violated,
+  one can either use these estimates for 
+  some regions (or sub-systems of the whole system) that
+  still preserve the uniformity,
+  or estimate the correlation error at the cost of
+  $\mathcal O(N^2\log N)$, if the correlation in the system is highly
+  inhomogeneous.  
+  % one can either estimate the correlation error at the cost of
+  % $\mathcal O(N^2\log N)$, or estimate the correlation error for
+  % some regions (or sub-system of the whole system) that
+  % still preserve those uniformity.
+
+}
 % For the second term, do variable change $\v r'' = \v r' + \v s$, we have:
@@
 \end{align}
+\recheck{The validity of this approximation and a similar approximation
+  \eqref{eqn:leading-order-2}
+  will be numerically checked in Sec.~\ref{sec:example3}.}
 Then from Eqn.~\eqref{eqn:ik.error.force}, we have the error force of
@@
   \centering
-  \includegraphics[]{rand1.rho.eps}
+  \includegraphics[]{fig.rho.eps}
   \caption{
-    The charge number density  of Example 1.
-    The red line: positive charge. The blue line: negative charge.
+    The charge number density  of Example 1 and 2.
+    The red solid line: the positive charge of Example 1.
+    The red dashed line: the positive charge of Example 2.
+    The blue line: the negative charge.
     Since the charges are uniformly distributed
@@
     analytical differentiation.
-    Blue ``$+$'': the real error of the staggered mesh
+    \recheck{
+    Blue ``$\boxdot$'': the real error of the
+    randomized COM test, calculated by
+    the staggered mesh analytical differentiation.}
+    Green ``$+$'': the real error of the staggered mesh
     ik-differentiation, it is overlapping with the analytical differentiation.
     Blue dashed line: the error estimate, without the correlation error.
-    Blue solid line: the error estimate, with the nearest
+    Blue solid line: the error estimate, with the \recheck{bonded} nearest
     neighbor approximation of the correlation error.
+    \recheck{
+      Short blue dotted line: the error estimate
+    for the liquid phase including both the bonded and non-bonded
+    nearest neighbor approximations.}
     The RMS errors are averaged over $y$ and $z$ directions, and are
@@
     The black arrow indicates the improvement
-    of error estimate by including nearest neighbor
-    approximation of correlation error.
+    of error estimate by including \recheck{bonded} nearest neighbor
+    approximation.
+    \recheck{
+    The black dotted arrow indicates the improvement of
+    further including non-bonded nearest neighbor approximation.}
   }   
   \label{fig:water-error}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.gr.eps}
+  \caption{The convergence of the non-bonded nearest neighbor approximation with respect to the neighboring range $R_g$.}
+  \label{fig:gr-conv}
 \end{figure}
@@
 % estimate.
-By including the nearest neighbor approximation of the
+\recheck{ Thanks to the reviewer of this paper, one likely
+  explanation is that the electrostatic forces
+  exerted by bonded pairs
+  are anti-correlated due to opposing charge signs.
+  The extreme case is the overlapping of one oxygen atom with two
+  hydrogen atoms: the charges cancels, so the error vanishes.
+  In case of the TIP3P water model, the H-O bond is 0.1~\textsf{nm},
+  which is much smaller than the typical
+  center-of-mass (COM) distance between two neighboring water
+  molecules (0.31~\textsf{nm}),
+  therefore, the bonded correlation tends to neutralize the molecule
+  and reduce the force error.}
+
+By including the \recheck{bonded} nearest neighbor approximation of the 
 correlation error, the quality of all error estimates is improved greatly,
-as indicated by the arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
+as indicated by the solid arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
 Now the RMS errors of ik-differentiation, analytical differentiation
@@
 for the parameter tuning application.
-The great improvement by the nearest neighbor approximation 
-means that  among all atomic
-correlates (i.e. the rigid H-O bond and H-O-H angle, the van der Waals interactions,
-the hydrogen bonds, etc.), the rigid bond and angle correlation
-% (rigid
-% modeling of H-O bond and H-O-H angle)
-is the most important one, and all
-the rest account for the remaining discrepancy between the estimated and real
-error.
+\recheck{
+  Since we
+  worry about the validity of the leading order
+  approximation in
+  Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+  we consider 
+  the staggered mesh Ewald method in the following testing case
+  (we call it the randomized COM test):
+  randomly redistribute the water molecules according to the same
+  COM distribution, while keeping
+  the bonds and direction of the molecules unchanged.
+  A perfect error estimate including the bonded nearest neighbor
+  approximation
+  should overlap with the real error of the randomized COM test,
+  because there is NO non-bonded correlation in the randomized COM system.
+  Since the only approximation made in the error estimate
+  is the leading order approximation, the difference between
+  the estimate and the real error of the randomized COM test
+  comes from the higher order contributions discarded by
+  Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+  In Fig.~\ref{fig:water-error}, the overlapping of the estimate
+  with the real error justifies the effectiveness of the
+  leading order approximation. We will investigate this issue
+  in a wider parameter range later.
+  % Since the non-bonded correlation is removed from this case,
+  % a good consistency (see Fig.~\ref{fig:water-error}, and later
+  % Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4}) of the 
+  % actual error with the estimate validates the correctness of 
+  % the bonded nearest neighbor approximation, and
+  % implies the reliablility of 
+  % the leading order
+  % approximation~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.  
+  The prerequisite of the bonded nearest neighbor approximation
+  is basically fulfilled:
+  the water direction preference in the bulk liquid and
+  vapor regions is uniform (actually it is isotropic).
+  Although
+  we observe a preference of the dipole moment along the $x$ direction
+  at the liquid-vapor interface, it is relatively weak and has  no
+  obvious side-effect on the error estimate.
+
+  The non-bonded nearest
+  neighbor approximation \eqref{eqn:nb-nna-1} and \eqref{eqn:nb-nna-2}
+  cannot be directly used  in this example, 
+  because the system is inhomogeneous, and the RDFs are not well-defined.
+  However, the system contains a comparatively homogeneous liquid region,
+  where we can compute the RDFs and the non-bonded
+  nearest neighbor
+  approximation. The resulting error estimate is presented by the
+  dotted blue line in Fig.~\ref{fig:water-error}.
+  (We do not consider the estimate in the vapor region because
+  the error is much smaller than the liquid region.)
+  The $R_g$ is chosen to be $1.2$~\textsf{nm}. A good
+  convergence with respect to the neighboring range is observed,
+  when it is larger than $0.6$~\textsf{nm},
+  and includes all major structures in the RDFs,
+  see Fig.~\ref{fig:gr-conv}.
+  As indicated by the Fig.~\ref{fig:water-error},
+  the RMS error estimate is further improved by the non-bonded
+  nearest neighbor approximation.
+  However, there is still a discrepancy between the real and estimated
+  error, which we cannot explain. It may originate from 
+  assuming the testing particle is independent with the system, but
+  we cannot check this point, because investigating the
+  correlation of the testing
+  particle with the system is beyond the theoretical framework of the
+  present paper.
+  In Fig.~\ref{fig:water-error}, the improvement marked by the solid
+  arrow is much larger than that marked by the dotted arrow,
+  so the bonded correlation dominates the correlation error, compared to
+  the non-bonded correlation.
+  If not stated otherwise,
+  we only consider the bonded nearest neighbor approximation.}
+
+% The great improvement by the bonded nearest neighbor approximation 
+% means that  among all atomic
+% correlates (i.e. the rigid H-O bond and H-O-H angle, the van der Waals interactions,
+% the hydrogen bonds, etc.), the rigid bond and angle correlation
+% % (rigid
+% % modeling of H-O bond and H-O-H angle)
+% is the most important one, and all
+% the rest account for the remaining discrepancy between the estimated and real
+% error.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.mesh.ik.ana.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and grid spacings.
+    Red: the direct part. Green: the original ik-differentiation.
+    Blue: the original analytical differentiation. ``$\times$'' and
+    ``+'' denote the actual error.  The solid and dashed lines denote
+    the error estimates with and without bonded nearest neighbor
+    approximation, respectively. The plotted direct space cut-off radii are
+    $r_c = 0.9$, $1.1$, $1.3$ and  $1.7\:\textsf{nm}$. The
+    reciprocal space grid spacings $h$  are approximately
+    $0.248$, $0.124$ and $0.062\:\textsf{nm}$, corresponding to
+    grids $60\times 30\times 30$, $120\times 60\times 60$ and
+    $240\times 120\times 120$, respectively. The order of the B-spline
+    interpolation is 6.
+  }
+  \label{fig:tmp-add1}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.order.ik.ana.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and interpolation orders.
+    The symbols are the same as Fig.~\ref{fig:tmp-add1}.
+    The plotted orders of the B-spline interpolation are $n=4$, 6 and 8.
+    The reciprocal space grid spacing $h$ is approximately
+    $0.124\:\textsf{nm}$, corresponding to
+    a $120\times 60\times 60$ grid.
+  }
+  \label{fig:tmp-add2}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.mesh.st.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and grid spacings.
+    Red: the direct part. Green: the staggered mesh ik-differentiation.
+    Blue: the staggered mesh analytical differentiation. ``$\times$'' and
+    ``+'' denote the actual error.  The solid and dashed lines denote
+    the error estimates with and without bonded nearest neighbor
+    approximation, respectively.
+    The error estimates for the staggered mesh ik- and analytical
+    differentiations are identical, so only the blue lines are presented.
+    The blue ``$\boxdot$'' indicates the real error of the randomized COM test,
+    calculated by the
+    staggered mesh analytical differentiation. The same results
+    of the ik-differentiation are not shown.
+    The plotted direct space cut-off radii are
+    $r_c = 0.9$, $1.1$, $1.3$ and  $1.7\:\textsf{nm}$. The
+    reciprocal space grid spacings $h$  are approximately
+    $0.248$, $0.124$ and $0.062\:\textsf{nm}$, corresponding to
+    grids $60\times 30\times 30$, $120\times 60\times 60$ and
+    $240\times 120\times 120$, respectively. The order of the B-spline
+    interpolation is 6.
+  }
+  \label{fig:tmp-add3}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.order.st.eps}
+  % \includegraphics[]{fig.mesh.st.eps}
+  \caption{Example 3: the actual and estimated RMS error of the liquid
+    phase as a function of the Ewald splitting parameter $\beta$,
+    with various cut-off radii and interpolation orders.
+    The symbols are the same as Fig.~\ref{fig:tmp-add3}.
+    The plotted orders of the B-spline interpolation are $n=4$, 6 and 8.
+    The reciprocal space grid spacing $h$ is approximately
+    $0.124\:\textsf{nm}$, corresponding to
+    a $120\times 60\times 60$ grid.
+  }
+  \label{fig:tmp-add4}
+\end{figure}
+
+\recheck{
+In Fig.~\ref{fig:tmp-add1} -- \ref{fig:tmp-add4}, we present the 
+actual and estimated RMS error of the liquid phase as a function of
+the Ewald splitting parameter $\beta$, using various cut-off radii,
+interpolation orders, and reciprocal grid spacings.
+Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add2} show the results of the
+original ik-/analytical differentiation,
+while Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4} present
+the staggered mesh ik-/analytical differentiation.
+In
+Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add3},
+the interpolation order is fixed to $n=6$,
+and we plot the actual and estimated errors using the direct space
+cut-off radii $r_c = 0.9$, $1.1$, $1.3$ and $1.7\:\textsf{nm}$, and
+the reciprocal space grid spacings $h = 0.248$, $0.124$ and
+$0.062\:\textsf{nm}$. In Fig.~\ref{fig:tmp-add2} and \ref{fig:tmp-add4}, the 
+grid spacing is fixed to $h = 0.248\:\textsf{nm}$, and
+we plot interpolation orders of $n=4$, 6 and 8.
+Like the
+homogeneous water system studied in the literature (see for
+example Ref.~\cite{wang2010optimizing, ballenegger2012convert}),
+when $\beta$ is small the direct error dominates, when  $\beta$ is
+large the reciprocal error dominates.
+Therefore, given a set of parameters ($r_c$, $n$ and $h$),
+the $\beta$ at the crossover of the direct and reciprocal errors
+achieves the nearly optimal accuracy and should be used in simulations.
+For all cut-off radii,
+the quality of the direct error estimate is satisfactory when the
+direct error is small than $10^{-1}\:\textsf{kJ/(mol nm)}$.
+It is also observed that the quality of the error estimate is better
+for larger $\beta$ than for smaller $\beta$.
+As expected, the Figures \ref{fig:tmp-add1} -- \ref{fig:tmp-add4} show that
+the smaller grid spacings and larger interpolation orders
+enable more accuracy force computation. 
+Unlike the uncorrelated testing examples 1 and 2, the actual precisions of the 
+original ik- and analytical differentiation are nearly the same,
+see Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add2}.
+This implies that the latter may be more preferable than
+the former for the massive parallel water simulations,
+because it needs only one half FFTs of the former.
+% Fortunately,
+% this may not be a big problem, because the very small $\beta$ is seldomly
+% used in practice,
+% and a extremely large cut-off radius is needed to achieve the best
+% efficiency for such a $\beta$. In Fig.~\ref{fig:tmp-add4} at $n=4$, the largest
+% $r_c = 1.7\:\textsf{nm}$ is corresponding to a choice of $\beta$ at
+% $1.9\:\textsf{nm}^{-1}$, where the ik- and analytical differentiations
+% are still close.
+With the bonded nearest neighbor approximation, the
+reciprocal error estimates are impressively improved compared
+to those without considering the charge correlation,
+and are able to correctly
+catch the trends of real errors with various working parameters,
+see Fig.~\ref{fig:tmp-add1} -- \ref{fig:tmp-add4}.
+The improvement of
+the original analytical differentiation and the staggered mesh
+Ewald method is larger than that of the original ik-differentiation.
+% The same as discussed before, we also compare the error of the
+% randomized COM testing case with the error esitmates. 
+As discussed before, we compare the error estimate (including
+bonded nearest neighbor approximation)
+with the real error of the randomized COM test.
+In most cases in Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4},
+a perfect overlapping is observed, which justifies the
+leading order approximation proposed in
+Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+However,
+we do observe exceptions
+at large $\beta$ when the grid spacing is $h=0.248\:\textsf{nm}$
+(see Fig.~\ref{fig:tmp-add3}), and
+at small $\beta$ when the interpolation order is $n=4$
+(see Fig.~\ref{fig:tmp-add4}).
+The deviations indicate that the 
+higher order terms discarded by
+Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}
+may play a role in the staggered
+mesh interpolation errors in these situations.
+This interpretation also
+explains the unexpected deviation of the  staggered mesh
+ik-differentiation from the analytical differentiation
+at  small $\beta$, $n=4$.
+
+% is why the staggered mesh
+% ik- differentiation starts deviating from the analytical
+% differentiation
+
+% As discussed before, a good leading order approximation
+% (i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2})
+% implies:
+% (1) the equivalency of staggered mesh ik- and analytical differentiation;
+% (2) the consistency of the estimate
+% with the real error of the randomized COM testing case.
+% In most cases in Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4},
+% these two points are verified. 
+% However,
+% we do obsever exceptions at small $\beta$ when the interpolation order is $n=4$
+% (see Fig.~\ref{fig:tmp-add4}),
+% where higher order terms may play a role in the  staggered
+% mesh interpolation errors
+% \eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+
+% In most cases, the staggered mesh error estimate is perfectly consistent
+% with the real error of the randomized COM testing case (see
+% Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4})
+% which demonstrates the reliability of the
+% leading order approximation
+% \eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+% However, at $n=4$ and small $\beta$,
+% a small gap between the estimate and the real error is observed, which
+% implies that the higher order terms may play a role in the error.
+
+% In most testing cases the staggered mesh ik-differentiation is
+% equivalent to the staggered mesh analytical differentiation,
+% see Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4}. However,
+% we obsever exceptions at small $\beta$ when the interpolation order is $n=4$,
+% see Fig.~\ref{fig:tmp-add4}.
+% This indicates the leading order approximations to the staggered
+% mesh interpolation errors,
+% i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+% may be not satisfactory.
+
+% However, as expected, when the
+% leading order approximations to the staggered
+% mesh interpolation errors
+% (i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}) are
+% not good ($n=4$ and small $\beta$),
+% the randomized COM error deviates from the error estimate.
+}
+
 \section{Conclusions and remarks}
@@
 The error estimates for the reciprocal space fast algorithms
-were impressively improved by including the first neighbor approximation
+were impressively improved by including the \recheck{bonded}
+first neighbor approximation
 to the correlation error.

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/lett.tex
fix bugs according to jctc template.

@@
 \textbf{
-  This problem can be solved by repeating and comparing
-  the force calculation by
+  This problem can be solved by  comparing
+  the forces calculated by
   using different parameter sets
   on a representative snapshot of the system,
-  see eg. Ref.[16].
+  see e.g. Ref.[16].
 An other approach is the 
@@
 changed to \textbf{We show that the error may be approximately
-  decomposed...}
+  decomposed...}, please see the 4-th line of the third paragraph of the
+introduction.
 \\
@@
 interpolation order $n$.
+Please also see the discussions added
+from the last line of page 29.
 % These figures show the error estimate
@@
 In the revised manuscript,
-we consider two types of the correlations:
+we consider both of the two types of the correlations:
 (1) the bonded correlation
@@
 while the non-bonded estimate
-is newly developed according to the reviewers' suggestion.
+is newly added according to the reviewers' suggestion.
 Please note that
@@
 the bonded estimate requires the uniformity of the water
-direction preference, while the non-bonded estimate requires the uniformity
+direction preference (as has been discussed in the old manuscript),
+while the non-bonded estimate requires the uniformity
 of the density distribution and the isotropicity of the system.
@@
 is expressed in terms of the radial distribution
-functions (RDFs). In example 3, a global RDF is not well defined,
+functions (RDFs), see the new Eq. (21) and (22). In example 3, a global RDF is not well defined,
 so we calculated the RDF and nearest neighbor approximation
@@
 Also the convergence with respect to
-the neighboring range $R_g$ is investigated (Fig.8). 
+the neighboring range $R_g$ is investigated, see Fig.8.
+Relavant changes to the manuscript
+have been made on page 9,
+11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
+in red for convenience.
 \\
@@
 the bonded estimate requires the uniformity of the water
-direction preference, while the non-bonded estimate requires the uniformity
+direction preference (as has been discussed in the old manuscript),
+while the non-bonded estimate requires the uniformity
 of the density distribution and the isotropicity of the system, which
 are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
-%Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
+Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
 For the non-bonded correlation,  the nearest neighbor approximation 
@@
 is investigated (Fig.8). 
+Relavant changes to the manuscript
+have been made on page 9,
+11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
+in red for convenience.
 \\
@@
 Therefore, we investigate this issue in another way:
-we compare the estimate (with non-bonded nearest neighbor
+we compare the estimate (with bonded nearest neighbor
 approximation) with the real error of the randomized COM test
-(see the description of this test in page 25).
+(see the description of this test at the 4th line from bottom of page 28).
 Since the only approximation made in the estimate is the leading order
@@
 at small $\beta$, $n=4$.
+Relavant changes to the manuscript
+have been made on page 28 (5-th line from the bottom), 32 (5-th line from the bottom).
 \\
@@
 Throughout this paper, we remove this  interaction from the
-standard long-range algorithms.
+standard long-range algorithms.  This discuss has been added to
+the manuscript, see from the 3rd line under Eq.20.
 
@@
 and reduce the force error.
-We have added this point to the paper.
+We have added this point to the paper, see line 10 on page 28.
 \\

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/main.tex
fix bugs according to jctc template.

@@
-\documentclass[aps,pre,preprint,unsortedaddress]{revtex4}
+\documentclass[journal=jacsat,manuscript=article]{achemso}
+% \documentclass[aps,pre,preprint,unsortedaddress]{revtex4}
 % \documentclass[aps,jcp,unsortedaddress]{revtex4-1}
@@
 %\documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
+\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
 
@@
 \usepackage{amssymb}
-\usepackage[dvips]{graphicx}
+% \usepackage[dvips]{graphicx}
 \usepackage{color}
@@
 \newcommand{\redc}[1]{{\color{red} #1}}
+% \newcommand{\recheck}[1]{{\textbf{#1}}}
+% \newcommand{\redc}[1]{{\textbf{#1}}}
 \renewcommand{\v}[1]{\textbf{\textit{#1}}}
@@
 
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}
 \newtheorem{lemma}[theorem]{Lemma}
@@
 
-\begin{document}
-
-\title{The Numerical Accuracy of Computing Electrostatic Interaction
-  in the Inhomogeneous and Correlated Molecular Systems:
-  for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.
-}
 \author{Han Wang}
@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+
+\title[\texttt{achemso} demonstration]
+{The Numerical Accuracy of Computing Electrostatic Interaction
+  in the Inhomogeneous and Correlated Molecular Systems:
+  for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.
+}
+
+\begin{document}
 
@@
 \recheck{
-  This problem can be solved by repeating and comparing
-  the force calculation by
+  This problem can be solved by comparing
+  the forces calculated by
   using different parameter sets
@@
 is impressively enhanced.
-This paper is ended by conclusions and remarks in
-section~\ref{sec:conclusions}.
+This paper is ended by conclusions and remarks in the last
+section.
 
@@
 
-Here are some remarks concerning Theorem~\ref{thm:tmp1} and Corollary~\ref{thm:tmp2}:
+Here are some remarks concerning \ref{thm:tmp1} and Corollary 2:
+%~\ref{thm:tmp2}:
 \begin{itemize}
@@
 \item The densities $\rho_q(\v r)$ and $\rho_{q^2}(\v r)$ defined in
-  Eqn.~\eqref{eqn:def-rhoq} and \eqref{eqn:def-rhoq2} are called \emph{the
+  \ref{eqn:def-rhoq} and \ref{eqn:def-rhoq2} are called \emph{the
     first order charge distribution} and \emph{the
@@
   respectively.
-  $\rho^{(2)}(\v r, \v r')$ in Eqn.~\eqref{eqn:def-rho2}
+  $\rho^{(2)}(\v r, \v r')$ in \ref{eqn:def-rho2}
   is the \emph{pairwise charge distribution}.
@@
   $C(\v r, \v r')$ defined in
-  Eqn.~\eqref{eqn:def-c} is the \emph{pairwise charge correlation function},
+  \ref{eqn:def-c} is the \emph{pairwise charge correlation function},
   which describes the strength of the correlation between  two
@@
   systems~\cite{deserno1998mue2, wang2010optimizing, ballenegger2012convert}.
-  Also see Sec.~\ref{sec:example3} for example.
+  Also see the Example 3 presented later in this paper.
 \item
   The \emph{pairwise form}
-  of the interaction (see Eqn.~\eqref{eqn:thm-error-force}) is the key to derive
-  the error estimates Eqn.~\eqref{eqn:thm-meanf} and \eqref{eqn:thm-error}.
+  of the interaction (see \ref{eqn:thm-error-force}) is the key to derive
+  the error estimates \ref{eqn:thm-meanf} and \ref{eqn:thm-error}.
   The function $\v K(\v r, \v r')$ is called \emph{the error force
     kernel}.
-  By setting $q_i = q_j = 1$, the corollary~\ref{thm:tmp2} proves
+  By setting $q_i = q_j = 1$, the
+  % corollary~\ref{thm:tmp2}
+  Corollary~2
+  proves
   the error estimates for the short-range interaction
@@
 \item \redc{Analogous} to the short-range error estimate~\cite{wang2012}, the
-  three terms on the r.h.s. of Eqn.~\eqref{eqn:thm-error} are called the
+  three terms on the r.h.s. of \ref{eqn:thm-error} are called the
   homogeneity error, the inhomogeneity error and the correlation
@@
   \end{align}
-  The first term on the r.h.s. of \eqref{eqn:error-split} is called
+  The first term on the r.h.s. of \ref{eqn:error-split} is called
   the ``homogeneity error'', but it does NOT mean this term is
@@
   % Without the property $\v K(\v r,\v r') = \v K(\v r - \v r')$,
-  Theorem~\ref{thm:tmp1} calculates the homogeneity and inhomogeneity
+  \ref{thm:tmp1} calculates the homogeneity and inhomogeneity
   error at a cost of $\mathcal O(N^2)$, and correlation error
@@
   By writing the error estimates in the convolution form in
-  the corollary~\ref{thm:tmp2},
+  the
+  % corollary~\ref{thm:tmp2},
+  Corollary~2,
   the homogeneity error and the inhomogeneity
@@
   % section~\ref{sec:tmp3}, it is shown neglicting the 
-\item A non-vanishing mean error force~\eqref{eqn:thm-meanf} was proved
+\item A non-vanishing mean error force~\ref{eqn:thm-meanf} was proved
   to be
@@
 % error estimate.
-Starting from Eqn.~\eqref{eqn:prf-error-step3},
+Starting from \ref{eqn:prf-error-step3},
 \begin{align} \nonumber
@@
 where the definition of $\rho^{(2)}(\v r', \v r'')$ is given by
-Eqn.~\eqref{eqn:def-rho2}.
+\ref{eqn:def-rho2}.
 % \begin{align}
@@
 Then
-second \redc{term} on the r.h.s. of the Eqn.~\eqref{eqn:split-rho-q2} is
+second \redc{term} on the r.h.s. of the \ref{eqn:split-rho-q2} is
 approximately $\frac{N-\#(\Omega_j)}{N}\rho_q(\v r')\rho_q(\v r'')\approx
@@
 Therefore, the first \redc{term}
-on the r.h.s. of Eqn.~\eqref{eqn:split-rho-q2} is actually the
+on the r.h.s. of \ref{eqn:split-rho-q2} is actually the
 pairwise charge correlation function:
@@
 % the error estimate.
-By inserting Eqn.~\eqref{eqn:fnc-correlation-water} into
+By inserting \ref{eqn:fnc-correlation-water} into
 the correlation error, we have:
@@
   intermolecular correlation that originates from
-  a complex coupling of various intermolecular interaction, such as
+  a complex coupling of various intermolecular interactions, such as
   the van der Waals interaction,
@@
 We firstly consider the bonded correlation, and define the nearest
-neighbor by the atoms within the same water molecule.  Denoting the
+neighbors by the atoms within the same water molecule.  Denoting the
 index set of the oxygen atoms by $\Omega_{\textrm{O}}$, and the index
@@
 $\v s_{\textrm{H}} = \v r_{\textrm{H}_2} - \v r_{\textrm{H}_1}$.
-The two ensemble averages in Eqn.~\eqref{eqn:c-error-1}
+The two ensemble averages in \ref{eqn:c-error-1}
 \redc{are} taken over all possible water directions 
@@
 One possible way to calculate the ensemble averages in
-Eqn.~\eqref{eqn:c-error-1} is by the Fourier transform
+\ref{eqn:c-error-1} is by the Fourier transform
 of the error force kernel, for example
@@
 \end{align}
-the Eqn.~\eqref{eqn:c-error-1} becomes:
+the \ref{eqn:c-error-1} becomes:
 \begin{align}\nonumber
@@
 the independency between the testing particle and the
-system, as illustrated by Fig.~\ref{fig:tmp-add0}.
+system, as illustrated by \ref{fig:tmp-add0}.
 % Therefore, the correlation error
-% estimate~\eqref{eqn:c-error-water}
+% estimate~\ref{eqn:c-error-water}
 % actually neglects the correlation
@@
 Throughout this paper, we remove this interaction from the
-standard long-range algorithms.}
+standard long-range calculations.}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{correlation.1.eps}
+  \includegraphics[width=0.5\textwidth]{correlation.eps}
   \caption{The schematic plot of two interacting water molecules.
@@
     a testing charge), the
-    correlation with its bonded hydrogens are not considered, but
-    the correlations within any neighboring molecule are considered
-    by the bonded nearest neighbor approximation,
+    correlation with its bonded hydrogens are not considered.
+    The correlations within any neighboring molecule are considered,
     as indicated by the solid lines with two arrows.}
@@
   For the non-bonded correlation,
-  we define the nearest neighbor
+  we define the nearest neighbors
   by non-bonded atoms closer than a certain radius $R_g$ (neighboring range).
@@
   correlation function $\rho^{(2)}(\v r', \v r'')$ in
-  Eqn.~\eqref{eqn:start-corr} can be represented by the radial
+  \ref{eqn:start-corr} can be represented by the radial
   distribution functions (RDFs).
   Following the same way as the bonded correlation,
-  the non-bonded correlation error can be estimated:
+  the nearest neighbor approximation of
+  the non-bonded correlation error is estimated:
   the functions $T_{\textrm{O}}$ and $T_{\textrm{H}}$
@@
   For a short-range correlated system, the RDFs converges to 1
-  as $r$ goes to infinity, so the integrals in Eqn.~\eqref{eqn:nb-nna-1}
-  and \eqref{eqn:nb-nna-2} are convergent with respect to
+  as $r$ goes to infinity, so the integrals in \ref{eqn:nb-nna-1}
+  and \ref{eqn:nb-nna-2} are convergent with respect to
   increasing $R_g$.
@@
 The complementary error function $\textrm{erfc}(r)$ in
-Eqn.~\eqref{eqn:tmp2} decays exponentially as $r$ goes to infinity.
+\ref{eqn:tmp2} decays exponentially as $r$ goes to infinity.
 Therefore, it is a short-range interaction in the real space, which
@@
 $\vert\v m\vert$ increases. Therefore, in practice, the infinite
-summation in Eqn.~\eqref{eqn:tmp3} is truncated, and only a finite
+summation in \ref{eqn:tmp3} is truncated, and only a finite
 summation is calculated:
@@
 part of the Ewald summation can be
-written in the form of Eqn.~\eqref{eqn:cor-kernel}.  The direct
+written in the form of \ref{eqn:cor-kernel}.  The direct
 part is:
@@
 \end{align}
-By the corollary~\ref{thm:tmp2}, the error estimate of the
+By the
+% corollary~\ref{thm:tmp2},
+Corollary~2,
+the error estimate of the
 truncated Ewald summation is straightforward.
@@
 % the inhomogeneity error. Apply the Fourier transform on both sides of
-% Eqn. \eqref{eqn:tmp10} and \eqref{eqn:tmp18}:
+% \ref{eqn:tmp10} and \ref{eqn:tmp18}:
 % \begin{align}  
@@
 % The naive calculation of the reciprocal Ewald summation
-% \eqref{eqn:tmp6} will result in a computational cost of $\mathcal
+% \ref{eqn:tmp6} will result in a computational cost of $\mathcal
 % O(N^2)$. It has been shown that with a careful tuning of parameter
@@
 the particle position) the reciprocal term of the truncated Ewald
-energy and then approximate the derived force \eqref{eqn:tmp8} by the
+energy and then approximate the derived force \ref{eqn:tmp8} by the
 B-spline interpolation. This way is called the
@@
 steps.  The first step is the truncation of the reciprocal summation,
-i.e. Eqn. \eqref{eqn:tmp6}. The second step is the approximation of
+i.e. \ref{eqn:tmp6}. The second step is the approximation of
 $e^{2\pi i\v m\cdot\v r}$ by B-spline
@@
 examples supporting this argument in inhomogeneous systems are also
-given in Section \ref{sec:tmp3}.  Therefore, to estimate the force
+given later in this paper.  Therefore, to estimate the force
 error, it is enough to compare the SPME force with the
-\emph{truncated} Ewald force \eqref{eqn:tmp8}.
+\emph{truncated} Ewald force \ref{eqn:tmp8}.
 
@@
 % Due to the symmetricity of $\v g(\v m)$ and $A(\v m, \v r)$,
-% the last term in Eqn.~\eqref{eqn:ik.error.force.1},
+% the last term in \ref{eqn:ik.error.force.1},
 % i.e. the ``self-interacting term'', is zero.
@@
 cannot be written
-in the form of~\eqref{eqn:cor-kernel}, so the error estimate derived by
-corollary~\ref{thm:tmp2} cannot be used here. However, it is still
+in the form of~\ref{eqn:cor-kernel}, so the error estimate derived by
+% corollary~\ref{thm:tmp2}
+Corollary~2
+cannot be used here. However, it is still
 possible to develop the error estimate with convolution form under
@@
 estimate, and leave all details of the derivation 
-to the Appendix~\ref{sec:appendix}.  We notice the
+to the appendix.  We notice the
 term $e^{2\pi i l K_\alpha\v a^\ast_\alpha\cdot\v r}$ with $l\neq 0$
-in Eqn.~\eqref{eqn:error-A} introduces some high-wave-number terms in
+in \ref{eqn:error-A} introduces some high-wave-number terms in
 the expression of the error estimate.  If $K_\alpha$ is large enough,
@@
 \end{align}
-The last term in Eqn.~\eqref{eqn:ana.error.force} is due to the
+The last term in \ref{eqn:ana.error.force} is due to the
 self-interaction~\cite{cerutti2009staggered, ballenegger2011removal,
@@
 by a vector $\v s = \sum_\alpha\frac1{2K_\alpha}\v a_\alpha$. From
-Eqn.~\eqref{eqn:error-A}, we have
+\ref{eqn:error-A}, we have
 \begin{align}
@@
 \recheck{The validity of this approximation and a similar approximation
-  \eqref{eqn:leading-order-2}
-  will be numerically checked in Sec.~\ref{sec:example3}.}
-Then from Eqn.~\eqref{eqn:ik.error.force}, we have the error force of
+  \ref{eqn:leading-order-2}
+  will be numerically checked later.}
+Then from \ref{eqn:ik.error.force}, we have the error force of
 the staggered ik-differentiation:
@@
 \end{align}
-then the corollary~\ref{thm:tmp2} is applicable.
+then the
+% corollary~\ref{thm:tmp2}
+Corollary~2
+is applicable.
 % Moreover, since both the exact and the error
@@
 Therefore, from
-Eqn.~\eqref{eqn:ana.error.force}, the error force of the staggered
+\ref{eqn:ana.error.force}, the error force of the staggered
 analytical differentiation is approximately the same as the staggered
@@
 \geq 0$.
-Eqn.~\eqref{eqn:ana-st-error-force} implies, to the
+\ref{eqn:ana-st-error-force} implies, to the
 leading order of approximation, the staggered
@@
 in large scale parallel simulations.
-From Eqn.~\eqref{eqn:ik-st-error-force}
-and~\eqref{eqn:ana-st-error-force}, it is obvious that the Newton's
+From \ref{eqn:ik-st-error-force}
+and~\ref{eqn:ana-st-error-force}, it is obvious that the Newton's
 third law is better preserved by the staggered mesh methods.
@@
 % \end{align}
-% In Eqn.~\eqref{eqn:error-total}, the estimates of errors
+% In \ref{eqn:error-total}, the estimates of errors
 % $\langle\,\vert\Delta\v F_{\textrm{dir}}(\v r)\vert^2\rangle $,
@@
 % r)\rangle $ have been established.
-% In practice, the correlation~\eqref{eqn:error-total-corr}
+% In practice, the correlation~\ref{eqn:error-total-corr}
 % is often assumed to be vanished.
@@
 are randomly generated subjecting to the number density shown in
-Fig.~\ref{fig:tmp-rho}.  The number density of the  positive
+\ref{fig:tmp-rho}.  The number density of the  positive
 charge   is twice as large as that of the negative charge,
@@
 and the density distributions are intentionally chosen the same as
-Example 3~(see section \ref{sec:example3}), 
+Example 3,
+% ~(see section \ref{sec:example3}), 
 for an easy comparison.  The only difference is that the positions
@@
 % order charge distribution $\rho_q$ is naturally zero, therefore, by
-% Eqn. \eqref{eqn:tmp10}, \eqref{eqn:tmp18} and \eqref{eqn:ana.meanf}, all
+% \ref{eqn:tmp10}, \ref{eqn:tmp18} and \ref{eqn:ana.meanf}, all
 % the mean error forces should vanish. Numerical resutls in
@@
 
-Fig.~\ref{fig:error1} presents the real RMS error (by points) and the
+\ref{fig:error1} presents the real RMS error (by points) and the
 corresponding error estimates (by lines) of the \redc{truncated} Ewald direct
@@
 the truncated Ewald summation.
-This supports the argument addressed in
-Sec.~\ref{sec:error-ik}: the error introduced by truncating the
+This supports the argument addressed earlier:
+% Sec.~\ref{sec:error-ik}:
+the error introduced by truncating the
 reciprocal Ewald summation is much smaller than that introduced by
@@
 are moved to the region where the density of negative charge is low,
-see Fig.~\ref{fig:tmp-rho}.
+see \ref{fig:tmp-rho}.
 In this system, the negative charges are separated from their
@@
     estimates. All symbols and working parameters are the same
-    as     Fig.~\ref{fig:error1}.
+    as     \ref{fig:error1}.
     The reciprocal mean error forces vanish, so the points and lines
@@
 
-Fig.~\ref{fig:meanf2} shows the real mean error forces (by points) and the
+\ref{fig:meanf2} shows the real mean error forces (by points) and the
 corresponding error estimates (by lines) of \redc{truncated} Ewald direct
@@
     The symbols and working parameters used in this figure are the same as
-    Fig.~\ref{fig:error1}.
+    \ref{fig:error1}.
     The real and estimated error of the original ik-differentiation
@@
 
-Fig.~\ref{fig:error2} presents the real and estimated
+\ref{fig:error2} presents the real and estimated
 RMS error of Example 2. The
@@
 system. The size of the simulation box and number of charges are the
-same as Example 1 (Sec.~\ref{sec:example1}): 13824 TIP3P water
+same as Example 1:
+% (Sec.~\ref{sec:example1}):
+13824 TIP3P water
 molecules~\cite{jorgensen1983comparison} are put into a
@@
 The number densities of oxygen and hydrogen atoms
-are the same as Example 1, see Fig.~\ref{fig:tmp-rho}.
+are the same as Example 1, see \ref{fig:tmp-rho}.
 50 consequential snapshots of
@@
 and the staggered mesh Ewald (both ik- and analytical differentiation)
-are in Fig.~\ref{fig:water-error0}
-and Fig.~\ref{fig:water-error}, respectively.
+are in \ref{fig:water-error0}
+and \ref{fig:water-error}, respectively.
 Unlike previous examples, the real error of ik- and analytical differentiation
@@
   hydrogen atoms: the charges cancels, so the error vanishes.
-  In case of the TIP3P water model, the H-O bond is 0.1~\textsf{nm},
-  which is much smaller than the typical
+  In the case of the TIP3P water model, the H-O bond is 0.1~\textsf{nm},
+  which is much shorter than the typical
   center-of-mass (COM) distance between two neighboring water
@@
 correlation error, the quality of all error estimates is improved greatly,
-as indicated by the solid arrows in Fig.~\ref{fig:water-error0} and \ref{fig:water-error}.
+as indicated by the solid arrows in \ref{fig:water-error0} and \ref{fig:water-error}.
 Now the RMS errors of ik-differentiation, analytical differentiation
@@
   approximation in
-  Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+  \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2},
   we consider 
@@
   approximation
-  should overlap with the real error of the randomized COM test,
-  because there is NO non-bonded correlation in the randomized COM system.
+  should be very close to the real error of the randomized COM test,
+  because there is NO non-bonded correlation in the test system.
   Since the only approximation made in the error estimate
@@
   comes from the higher order contributions discarded by
-  Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
-  In Fig.~\ref{fig:water-error}, the overlapping of the estimate
+  \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}.
+  In \ref{fig:water-error}, the overlapping of the estimate
   with the real error justifies the effectiveness of the
@@
   % the leading order
-  % approximation~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.  
+  % approximation~\ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}.  
   The prerequisite of the bonded nearest neighbor approximation
@@
   Although
-  we observe a preference of the dipole moment along the $x$ direction
+  we observe (not shown)
+  a preference of the dipole moment along the $x$ direction
   at the liquid-vapor interface, it is relatively weak and has  no
@@
   The non-bonded nearest
-  neighbor approximation \eqref{eqn:nb-nna-1} and \eqref{eqn:nb-nna-2}
+  neighbor approximation \ref{eqn:nb-nna-1} and \ref{eqn:nb-nna-2}
   cannot be directly used  in this example, 
@@
   approximation. The resulting error estimate is presented by the
-  dotted blue line in Fig.~\ref{fig:water-error}.
+  dotted blue line in \ref{fig:water-error}.
   (We do not consider the estimate in the vapor region because
   the error is much smaller than the liquid region.)
-  The $R_g$ is chosen to be $1.2$~\textsf{nm}. A good
-  convergence with respect to the neighboring range is observed,
-  when it is larger than $0.6$~\textsf{nm},
-  and includes all major structures in the RDFs,
-  see Fig.~\ref{fig:gr-conv}.
-  As indicated by the Fig.~\ref{fig:water-error},
+  The neighboring range $R_g$ is chosen to be $1.2$~\textsf{nm}.
+  % A good
+  % convergence with respect to the neighboring range is observed,
+  The error estimate converges
+  when $R_g$
+  % includes all major structures in the RDFs, i.e.
+  is larger than $0.6$~\textsf{nm},
+  see \ref{fig:gr-conv}.
+  As indicated by the \ref{fig:water-error},
   the RMS error estimate is further improved by the non-bonded
@@
   error, which we cannot explain. It may originate from 
-  assuming the testing particle is independent with the system, but
+  assuming that the testing particle is independent with the system, but
   we cannot check this point, because investigating the
-  correlation of the testing
-  particle with the system is beyond the theoretical framework of the
+  correlation between the testing
+  particle and the system is beyond the theoretical framework of the
   present paper.
-  In Fig.~\ref{fig:water-error}, the improvement marked by the solid
+  In \ref{fig:water-error}, the improvement marked by the solid
   arrow is much larger than that marked by the dotted arrow,
@@
     with various cut-off radii and interpolation orders.
-    The symbols are the same as Fig.~\ref{fig:tmp-add1}.
+    The symbols are the same as \ref{fig:tmp-add1}.
     The plotted orders of the B-spline interpolation are $n=4$, 6 and 8.
@@
     with various cut-off radii and interpolation orders.
-    The symbols are the same as Fig.~\ref{fig:tmp-add3}.
+    The symbols are the same as \ref{fig:tmp-add3}.
     The plotted orders of the B-spline interpolation are $n=4$, 6 and 8.
@@
 \recheck{
-In Fig.~\ref{fig:tmp-add1} -- \ref{fig:tmp-add4}, we present the 
+In \ref{fig:tmp-add1} -- \ref{fig:tmp-add4}, we present the 
 actual and estimated RMS error of the liquid phase as a function of
@@
 interpolation orders, and reciprocal grid spacings.
-Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add2} show the results of the
+\ref{fig:tmp-add1} and \ref{fig:tmp-add2} show the results of the
 original ik-/analytical differentiation,
-while Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4} present
+while \ref{fig:tmp-add3} and \ref{fig:tmp-add4} present
 the staggered mesh ik-/analytical differentiation.
 In
-Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add3},
+\ref{fig:tmp-add1} and \ref{fig:tmp-add3},
 the interpolation order is fixed to $n=6$,
-and we plot the actual and estimated errors using the direct space
+and we plot the errors using the direct space
 cut-off radii $r_c = 0.9$, $1.1$, $1.3$ and $1.7\:\textsf{nm}$, and
 the reciprocal space grid spacings $h = 0.248$, $0.124$ and
-$0.062\:\textsf{nm}$. In Fig.~\ref{fig:tmp-add2} and \ref{fig:tmp-add4}, the 
+$0.062\:\textsf{nm}$. In \ref{fig:tmp-add2} and \ref{fig:tmp-add4}, the 
 grid spacing is fixed to $h = 0.248\:\textsf{nm}$, and
@@
 for larger $\beta$ than for smaller $\beta$.
-As expected, the Figures \ref{fig:tmp-add1} -- \ref{fig:tmp-add4} show that
+As expected, the \ref{fig:tmp-add1} -- \ref{fig:tmp-add4} show that
 the smaller grid spacings and larger interpolation orders
-enable more accuracy force computation. 
+enable more accurate force computation. 
 Unlike the uncorrelated testing examples 1 and 2, the actual precisions of the 
 original ik- and analytical differentiation are nearly the same,
-see Fig.~\ref{fig:tmp-add1} and \ref{fig:tmp-add2}.
+see \ref{fig:tmp-add1} and \ref{fig:tmp-add2}.
 This implies that the latter may be more preferable than
@@
 catch the trends of real errors with various working parameters,
-see Fig.~\ref{fig:tmp-add1} -- \ref{fig:tmp-add4}.
+see \ref{fig:tmp-add1} -- \ref{fig:tmp-add4}.
 The improvement of
@@
 with the real error of the randomized COM test.
-In most cases in Fig.~\ref{fig:tmp-add3} and \ref{fig:tmp-add4},
+In most cases in \ref{fig:tmp-add3} and \ref{fig:tmp-add4},
 a perfect overlapping is observed, which justifies the
 leading order approximation proposed in
-Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+\ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}.
 However,
@@
 at large $\beta$ when the grid spacing is $h=0.248\:\textsf{nm}$
-(see Fig.~\ref{fig:tmp-add3}), and
+(see \ref{fig:tmp-add3}), and
 at small $\beta$ when the interpolation order is $n=4$
-(see Fig.~\ref{fig:tmp-add4}).
+(see \ref{fig:tmp-add4}).
 The deviations indicate that the 
 higher order terms discarded by
-Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}
-may play a role in the staggered
-mesh interpolation errors in these situations.
-This interpretation also
-explains the unexpected deviation of the  staggered mesh
+\ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}
+may play a role
+% in the staggered mesh interpolation errors
+in these situations.
+This may also
+explain the unexpected deviation of the  staggered mesh
 ik-differentiation from the analytical differentiation
@@
 % As discussed before, a good leading order approximation
-% (i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2})
+% (i.e. \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2})
 % implies:
@@
 % mesh interpolation errors
-% \eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+% \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}.
 
@@
 % leading order approximation
-% \eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}.
+% \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}.
 % However, at $n=4$ and small $\beta$,
@@
 % mesh interpolation errors,
-% i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2},
+% i.e. \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2},
 % may be not satisfactory.
@@
 % mesh interpolation errors
-% (i.e. Eqn.~\eqref{eqn:leading-order-1} and \eqref{eqn:leading-order-2}) are
+% (i.e. \ref{eqn:leading-order-1} and \ref{eqn:leading-order-2}) are
 % not good ($n=4$ and small $\beta$),
@@
 
-\subsection{ik-differentiation}
-Starting from Eqn.~\eqref{eqn:ik.error.force}, we have the error force kernel
+\subsection{The ik-differentiation}
+Starting from \ref{eqn:ik.error.force}, we have the error force kernel
 of the ik-differentiation:
@@
 \end{align}
-By inserting Eqn.~\eqref{eqn:error-A}, the error force kernel is
+By inserting \ref{eqn:error-A}, the error force kernel is
 \begin{align}
@@
 $\int \v K^{\textrm{ik}}_{\textrm{rec}}(\v r, \v r')\rho_q(\v r')\,\d d\v r$.
-By Eqn.~\eqref{eqn:ik.kernel.2}, we should calculate
+By \ref{eqn:ik.kernel.2}, we should calculate
 $  \int e^{-2\pi i l K_\alpha\v a^\ast_\alpha\cdot \v r'}\rho_q(\v r')
@@
 \end{align}
-The first two term on the r.h.s. of Eqn.~\eqref{eqn:ik.cal.tmp1}
+The first two term on the r.h.s. of \ref{eqn:ik.cal.tmp1}
 are not high-wave-number terms only when $l_1 = l_2$ and $\alpha=\beta$.
@@
 \end{align}
-Inserting \redc{this} into Eqn.~\eqref{eqn:c-error-1} \redc{while neglecting} the high
+Inserting \redc{this} into \ref{eqn:c-error-1} \redc{while neglecting} the high
 frequency terms yields
@@
 
-\subsection{analytical differentiation}
-Starting from Eqn.~\eqref{eqn:ana.error.force}, we have the error force kernel
+\subsection{The analytical differentiation}
+Starting from \ref{eqn:ana.error.force}, we have the error force kernel
 of the analytical differentiation (notice the self-interacting term is removed):
@@
 \end{align}
-By inserting Eqn.~\eqref{eqn:error-A} and \eqref{eqn:error-B}, we have
+By inserting \ref{eqn:error-A} and \ref{eqn:error-B}, we have
 \begin{align}\nonumber
@@
 \end{align}
-Similar to the calculation of \eqref{eqn:ik.cal.tmp1}, one can eventually
+Similar to the calculation of \ref{eqn:ik.cal.tmp1}, one can eventually
 prove the error estimate for the homogeneity RMS error:
@@
 \big\rangle$
-into \eqref{eqn:c-error-1}, we have the first neighbor approximation to the
+into \ref{eqn:c-error-1}, we have the first neighbor approximation to the
 correlation error:
@@
 \bibliography{ref}{}
-\bibliographystyle{unsrt}
+% \bibliographystyle{achemso}
 

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/lett.tex
delete figure, fix bug in letter

@@
 the neighboring range $R_g$ is investigated, see Fig.8.
-Relavant changes to the manuscript
+Relevant changes to the manuscript
 have been made on page 9,
@@
 is investigated (Fig.8). 
-Relavant changes to the manuscript
+Relevant changes to the manuscript
 have been made on page 9,
@@
 at small $\beta$, $n=4$.
-Relavant changes to the manuscript
+Relevant changes to the manuscript
 have been made on page 28 (5-th line from the bottom), 32 (5-th line from the bottom).

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/lett.tex
everything black, improve letter

@@
 
-In the revised manuscript, all the additions are marked in red, to help the
+In the revised manuscript, all the major additions are marked in red, to help the
 reviewers to located them immediately in the text.\\
@@
 intermolecular correlation that originates from
-a complex coupling of various intermolecular interaction.
+a complex coupling of various intermolecular interactions.
 Estimates for the bonded correlation
@@
 is newly added according to the reviewers' suggestion.
+The nearest neighbors are defined by neighbors closer than
+a neighboring range $R_g$.
+The non-bonded nearest neighbor approximation 
+is expressed in terms of the radial distribution
+functions (RDFs), see the new Eq. (21) and (22).
 Please note that
@@
 Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
-For the non-bonded correlation,  the nearest neighbor approximation 
-is expressed in terms of the radial distribution
-functions (RDFs), see the new Eq. (21) and (22). In example 3, a global RDF is not well defined,
+In example 3, a global RDF is not well defined,
 so we calculated the RDF and nearest neighbor approximation
@@
 
-In the revised manuscript, the correlation error are considered
-in two types: 
+In the revised manuscript,
+we consider both of the two types of the correlations:
 (1) the bonded correlation
@@
 while the non-bonded estimate
-is newly developed according to the reviewers' suggestion.
+is newly added according to the reviewers' suggestion.
+The nearest neighbors are defined by neighbors closer than
+a neighboring range $R_g$ (i.e. the $r_c$ in the reviewer's comment).
+The non-bonded nearest neighbor approximation 
+is expressed in terms of the radial distribution
+functions (RDFs), see the new Eq. (21) and (22).
 Please note that
@@
 Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
-For the non-bonded correlation,  the nearest neighbor approximation 
-is expressed in terms of the radial distribution
-functions (RDFs) in the new Eqn. (21) and (22).
-In example 3, a global RDF is not well defined
-(because the system is inhomogeneous),
+In example 3, a global RDF is not well defined (because the system is inhomogeneous),
 so we calculated the RDF and nearest neighbor approximation
-only for the liquid phase, see the dotted line in Fig.7. By adding the
-non-bonded correlation, the quality of the error estimate
+only for the liquid phase, see the dotted line in Fig.7. By adding
+the non-bonded correlation, the quality of the error estimate
 is further improved.
 Also the convergence with respect to
-the neighboring range $R_g$ (the $r_c$ in the reviewer's comment)
-is investigated (Fig.8). 
+the neighboring range $R_g$ is investigated, see Fig.8.
 Relevant changes to the manuscript

### 2012-07-23 shortRange.inhomo/alltext/writeDown/fig/fcorrColl-x0.60-u2.20-rc2.5-14/plots/plot.rho.gif.sh
new figure settings for resubmission

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+target=$*
+
+for i in $target;
+do
+    echo "# processing $i"
+    p1=`echo $i | cut -d '.' -f 1`
+    p2=`echo $i | cut -d '.' -f 2`
+    p3=`echo $i | cut -d '.' -f 3`
+    out=$p1.$p2.$p3.gif
+    sed -e "/^set out/s/'.*'/'$out'/g" rho.one.gp |\
+    sed -e "/^spl/s/'.*'/'$i'/g" > tmp.gp
+    gnuplot tmp.gp
+done
+
+gifsicle --delay=10 $p1.*.*.gif > rho.out.gif

### 2012-07-23 shortRange.inhomo/alltext/pubilsh.pre/resubmit/lett.tex
add resubmit

\documentclass[a4paper]{article}

\begin{document}

\noindent
{Dear Editors,}\\

Hereby we would like to resubmit our article
(Manuscript No. ES10751):\\

\textbf{The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems
},\\

by H. Wang, C. Sch\"uette and P. Zhang to:\\

\textbf{Physical Review E}, as a regular article.\\

We would like to thank the referees for carefully reading our
manuscript and the comments helping us to finally provide a clearer
and more valuable article.  Some changes to the manuscript have been
done, as suggested by the
referees, and are explained in the following.\\

\textbf{Referee 2}\\

\textit{I also did not understand how the adaptive cutoff method results were
plotted as a function of cutoff distance in Figs 5 \& 6. A variety of
cutoffs are being used, yet it is plotted against a single cutoff
distance?}

Throughout the paper, when we mention
that ``the cut-off of
the adaptive cut-off method is $r_c^\ast$'', we mean that its
control error is the maximum error of a uniform cut-off simulation
using that cut-off $r_c^\ast$.
Under this setting,  the maximum 
cut-off radius of the adaptive cut-off method is the same as,
or sometimes marginally larger  than
$r_c^\ast$ (no more than $r_c^{\textrm{\tiny{step}}}$).
We have made this point clear in the captions of Figures 5 and 6.
\\

\textit{
I also suggest you make brief mention of the following issues, and
explain how your methods deal with them:
}

\textit{
(1) Does the ARC method (adaptive cut-off) make sense for long-range
Coulombic calculations where there is a short-range part with a cutoff
coupled to a long-range Kspace calculation (e.g. particle-mesh Ewald).
This is a commonly used approach for charged molecular systems (e.g.
solvated biomolecules). In that case, I believe the Kspace formulation
depends on their being a single cutoff on the short-range portion.
}

We have submitted a paper, titled ``The Numerical Accuracy of Computing
Electrostatic Interaction in the Inhomogeneous and Correlated
Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh
Ewald Methods'', dealing with the Ewald type long-range
algorithms. In that paper, we concluded that the locally neutral systems
do not have the error anomaly at the interfacial regions. Since
most practical charged systems are locally neutral, we are safe and
do not need ARC (adaptive cut-off) or LFC (long-range force correction)
for the electrostatic calculation.
\\

\textit{
(2) Can the spatial error estimation technique and 2 correction
methods be used for either periodic or non-periodic systems?
}

As far as we concerned, the error estimate technique and proposed
corrections can only be used to periodic systems.
We have added the following sentence to stress this point
(line 5, page 26):
\textbf{It should be noticed that the porposed error estimate and correction
methods can only be used to periodic systems.}
\\

\textit{
  (3) You say that the additional cost of the methods is small even
though they involve FFTs that scale as $N\log N$, compared to the $O(N)$
scaling of short-range MD. Your timing results bear this out, however
these examples were all fairly small systems. If large simulations are
performed (e.g. multi-million atoms), is the extra cost still small?}

This is a very important comment, because
the cost of FFTs $O(N\log N)$ will overcome the cost of short-range
interaction $O(N)$ at some point when the system is very
big. Eventually the computationaly cost will be overwhelmed by the
FFTs as the size of the system grows to infinity.
This point should be noticed.  Fortunately, for the systems
also calculate long-range interactions, the short-range error estimate
scales the same as the Ewald type long-range algorithms.
We have added the following remarks to the paper:
(line 5 from the bottom, page 26):
\textbf{In the systems tested by the present paper, the computational
  load of the error estimate is small compared to that of the
  short-range interaction.
  However, it should be noticed that
  the cost of the error estimate scales as $\mathcal O(N\log N)$,
  which may become intractable when the $\mathcal O(N)$ scaling
  short-range system is extremely large, and eventually
  overwhelms the total computational cost as the
  system size grows to infinity.
  If the system also needs long-range electrostatic calculation
  that is usually treated by the $\mathcal O(N\log N)$ scaling
  Ewald type algorithms [22-24],
  the extra load of the error estimate is likely to be acceptable.
}

\end{document}

### 2012-07-23 shortRange.inhomo/alltext/pubilsh.pre/resubmit/main.tex
add resubmit

--- 2012-05-01 shortRange.inhomo/alltext/pubilsh/main.tex
@@
   \centering
-  \includegraphics[]{figs/error.uniform.eps}
-  \caption{The RMS force error distribution of the 16000 Lennard-Jones
+  \includegraphics[]{error.uniform.eps}
+  \caption{(Color online)
+    The RMS force error distribution of the 16000 Lennard-Jones
     particle system at $T^\ast=0.85$ with a uniform cut-off radius of
-    $r_c^\ast = 7.5$. The green squares present the real error. The
-    solid blue line is the error estimate by \eqref{eqn:tmp5}. The
-    dashed blue line is the homogeneity error contribution, while the
-    dotted blue line is the inhomogeneity error contribution. The
-    density distribution of the system is presented by red solid line
+    $r_c^\ast = 7.5$. The green (light gray) squares present the real error. The
+    solid blue (dark gray) line is the error estimate by \eqref{eqn:tmp5}. The
+    dashed blue (dark gray) line
+    is the homogeneity error contribution, while the
+    dotted blue (dark gray) line
+    is the inhomogeneity error contribution. The
+    density distribution of the system is presented by red (middle gray)
+    solid line
     for reference.  All properties are properly averaged on the $y$
@@
   \centering
-  \includegraphics[]{figs/rcut.and.error.eps}
-  \caption{ The RMS force error distribution of the 16000
+  \includegraphics[]{rcut.and.error.eps}
+  \caption{ (Color online)
+    The RMS force error distribution of the 16000
     Lennard-Jones particle system at $T^\ast=0.85$ with adaptive
@@
     with $r_c^\ast=7.5$.  The resulting cut-off radius distribution is
-    presented by the red line. All other notations are the same as
+    presented by the red (middle gray) line. All other notations are the same as
     Fig.~\ref{fig:tmp2}.}
@@
   \centering
-  \includegraphics[]{figs/fcorr.and.error.eps}
-  \caption{ The RMS force error distribution of the 16000
+  \includegraphics[]{fcorr.and.error.eps}
+  \caption{ (Color online)
+    The RMS force error distribution of the 16000
     Lennard-Jones particle system at $T^\ast=0.85$ with long-range
@@
     radius is $r^\ast_c = 7.5$. The $x$ component of the correction
-    force is presented by the solid red line. The green squares
-    present the real error. The solid blue line presents the estimated
+    force is presented by the solid red (middle gray) line.
+    The green (light gray) squares
+    present the real error. The solid blue (dark gray)
+    line presents the estimated
     homogeneity error. }
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{figs/t0.85.gas.eps} 
-  \includegraphics[width=0.49\textwidth]{figs/t0.85.liquid.eps} 
-  \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
+  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
+  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
+  \caption{(Color online)
+    $T^\ast = 0.85$. The convergence of the equilibrium gas and
     liquid densities with respect to the cut-off radius. All densities
@@
     uncertainty of the reference value.  This figure presents the
-    results of three methods, namely the uniform cut-off (URC), the
-    adaptive cut-off (ARC) and the force correction (LFC) method. }
+    results of three methods,
+    namely the uniform cut-off (URC) in red (middle gray), the
+    adaptive cut-off (ARC) in green (light gray)
+    and the force correction (LFC) method in blue (dark gray).
+    The cut-off of
+    the adaptive cut-off method is $r_c^\ast$ means its
+    control error is the maximum error of a uniform cut-off simulation
+    using that cut-off $r_c^\ast$.
+    Under this setting,  the maximum 
+    cut-off radius of the adaptive cut-off method is the same as,
+    or sometimes marginally larger  than
+    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
+  }
   \label{fig:tmp5}
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{figs/tension.t0.85.eps} 
-  \caption{$T^\ast = 0.85$. The convergence of the surface tension
+  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
+  \caption{(Color online)
+    $T^\ast = 0.85$. The convergence of the surface tension
     with respect to the cut-off radius.  This figure presents the
-    results of three methods, namely the uniform cut-off (URC), the
-    adaptive cut-off (ARC) and the long-range force correction (LFC)
-    method.  The results with and without long-range pressure
+    results of three methods,
+    namely the uniform cut-off (URC) in red (middle gray),
+    the adaptive cut-off (ARC) in green (light gray)
+    and the long-range force correction (LFC) method in blue (dark gray).
+    The results with and without long-range pressure
     correction (LPC) are shown together for comparison. The reference
-    surface tensions, shown by solid black lines, are measured by the
-    uniform cut-off method with $r_c^\ast=13$ using LPC.}
+    surface tension, shown by the solid black line, is measured by the
+    uniform cut-off method with $r_c^\ast=13$ using LPC.
+    The cut-off of
+    the adaptive cut-off method is $r_c^\ast$ means its
+    control error is the maximum error of a uniform cut-off simulation
+    using that cut-off $r_c^\ast$.
+    Under this setting,  the maximum 
+    cut-off radius of the adaptive cut-off method is the same as,
+    or sometimes marginally larger  than
+    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
+    % This setting leads to a maximum 
+    % cut-off radius that is almost the same as $r_c^\ast$.
+  }
   \label{fig:tmp6}
@@
   \centering
-  \includegraphics[]{figs/init.2.eps}
-  \caption{The initial setup of cluster $A$ and $B$. The initial
+  \includegraphics[]{init.2.eps}
+  \caption{
+    (Color online)
+    The initial setup of cluster $A$ and $B$. The initial
     velocity are equal in magnitude but on opposite direction.}
@@
   \centering
-  \includegraphics[]{figs/trajs.eps}
-  \caption{The center of mass trajectory of cluster A. Uniform cut-off
+  \includegraphics[]{trajs.eps}
+  \caption{(Color online)
+    The center of mass trajectory of cluster A. Uniform cut-off
     (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
@@
   \centering
-  \includegraphics[]{figs/dists.eps}
-  \caption{The COM distance between cluster $A$ and cluster $B$ versus
+  \includegraphics[]{dists.eps}
+  \caption{(Color online)
+    The COM distance between cluster $A$ and cluster $B$ versus
     time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
@@
   \centering
-  \includegraphics[width=0.90\textwidth]{figs/error-rcut-ball.eps} 
-  \includegraphics[width=0.90\textwidth]{figs/error-rcut.eps}
-  \caption{The colliding clusters (the first row), the RMS force error
+  \includegraphics[width=0.90\textwidth]{error-rcut-ball.eps} 
+  \includegraphics[width=0.90\textwidth]{error-rcut.eps}
+  \caption{(Color online)
+    The colliding clusters (the first row), the RMS force error
     distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
@@
   \centering
-  \includegraphics[]{figs/wy.eps}
-  \caption{The angular velocity of cluster $A$ versus time. Uniform
+  \includegraphics[]{wy.eps}
+  \caption{(Color online)
+    The angular velocity of cluster $A$ versus time. Uniform
     cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
@@
   \centering
-  \includegraphics[]{figs/ly.eps}
-  \caption{The angular moment of cluster $A$ versus time. Uniform
+  \includegraphics[]{ly.eps}
+  \caption{(Color online)
+    The angular moment of cluster $A$ versus time. Uniform
     cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
@@
   \centering
-  \includegraphics[]{figs/cost.eps}
-  \caption{The computational cost versus time. Uniform
+  \includegraphics[]{cost.eps}
+  \caption{(Color online)
+    The computational cost versus time. Uniform
     cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
@@
 force, so that the inhomogeneity error is removed from the system.
+It should be noticed that the porposed error estimate and correction
+methods can only be used to periodic systems.
 
@@
 {
+  In the systems tested by the present paper, the computational
+  load of the error estimate is small compared to that of the
+  short-range interaction.
+  However, it should be noticed that
+  the cost of the error estimate scales as $\mathcal O(N\log N)$,
+  which may become intractable when the $\mathcal O(N)$ scaling
+  short-range system is extremely large, and eventually
+  overwhelms the total computational cost as the
+  system size grows to infinity.
+  If the system also needs long-range electrostatic calculation
+  that is usually treated by the $\mathcal O(N\log N)$ scaling
+  Ewald type algorithms~\cite{darden1993pme, essmann1995spm, deserno1998mue1},
+  the extra load of the error estimate is likely to be acceptable.
   We want to stress again the main research interest of the present paper is the

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/lett.tex
finish response

@@
 
-by H. Wang, C. Sch\"uette and P. Zhang to:\\
+by H. Wang, C. Sch\"utte and P. Zhang to:\\
 
@@
 that ``the cut-off of
-the adaptive cut-off method is $r_c^\ast$'', we mean that its
-control error is the maximum error of a uniform cut-off simulation
-using that cut-off $r_c^\ast$.
+the adaptive cut-off method is $r_c^\ast$'', we mean that the
+control error  $\mathcal E^\ast_{\textrm{\tiny{C}}}$
+is the same as the maximum error of a uniform cut-off simulation
+using $r_c^\ast$.
 Under this setting,  the maximum 
@@
 $r_c^\ast$ (no more than $r_c^{\textrm{\tiny{step}}}$).
-We have made this point clear in the captions of Figures 5 and 6.
+We have changed the captions of Figures 5 and 6 to make it clear.
 \\
@@
 
-We have submitted a paper, titled ``The Numerical Accuracy of Computing
+We  have recently submitted a paper,
+titled ``The Numerical Accuracy of Computing
 Electrostatic Interaction in the Inhomogeneous and Correlated
 Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh
-Ewald Methods'', dealing with the Ewald type long-range
-algorithms. In that paper, we concluded that the locally neutral systems
-do not have the error anomaly at the interfacial regions. Since
-most practical charged systems are locally neutral, we are safe and
-do not need ARC (adaptive cut-off) or LFC (long-range force correction)
-for the electrostatic calculation.
+Ewald Methods''.
+In that paper, the error estimates for both the
+direct space short-range part and the reciprocal space long-range
+part are developed.
+We prove that the inhomogeneity error vanishes in the
+locally neutral systems, so
+there is no error anomaly at the interfacial regions. Since
+most practical charged systems are locally neutral,
+we are basically safe and
+do not need neither ARC (adaptive cut-off)
+nor LFC (long-range force correction)
+for the electrostatic calculation. We 
+have also tested an artificial system that is NOT locally neutral. We find
+the direct space error presents similar error anomaly at the interface,
+while the reciprocal error (Kspace error) does not
+have any anomaly.
+Therefore, the reciprocal force calculation
+needs no adjustment, so the reciprocal space working parameters
+(interpolation order and grid spacing) and the splitting
+parameter can be fixed. When these parameters are fixed, the direct
+space force calculation is decoupled from the reciprocal space,
+so the ARC can be applied.
 \\
@@
 We have added the following sentence to stress this point
-(line 5, page 26):
-\textbf{It should be noticed that the porposed error estimate and correction
-methods can only be used to periodic systems.}
+(line 8, page 26):
+\textbf{It should be noticed that the proposed error estimate and correction
+methods can only be used for periodic systems.}
 \\
@@
 This is a very important comment, because
-the cost of FFTs $O(N\log N)$ will overcome the cost of short-range
-interaction $O(N)$ at some point when the system is very
-big. Eventually the computationaly cost will be overwhelmed by the
+the cost of FFTs ($O(N\log N)$) will overcome the cost of short-range
+interaction ($O(N)$) at some point when the system is very
+large. Eventually the computationally cost will be overwhelmed by the
 FFTs as the size of the system grows to infinity.
@@
 scales the same as the Ewald type long-range algorithms.
-We have added the following remarks to the paper:
-(line 5 from the bottom, page 26):
+We have added the following remarks to the paper
+(2nd line from the bottom, page 26):
 \textbf{In the systems tested by the present paper, the computational
@@
   However, it should be noticed that
-  the cost of the error estimate scales as $\mathcal O(N\log N)$,
-  which may become intractable when the $\mathcal O(N)$ scaling
-  short-range system is extremely large, and eventually
+  the cost of the error estimate scales as $\mathcal O(N\log N)$.
+  If the system only has short-range interaction that
+  scales as $\mathcal O(N)$, the load of the error estimate
+  may become comparatively expensive when the system is large,
+  and eventually
   overwhelms the total computational cost as the

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/main.tex
finish response

@@
   (see e.g. Ref.~\cite{potoff1998critical, perez2006critical}).
-  % Shifting the direct part of the Ewald summation actually
-  % violates the Coulomb's law in the way that depends on the
-  % splitting parameter, so it should be treated carefully.
-  % Here we would like to suggest treating the shifting approach
-  % as a special case 
 }
-% In this paper, we focus on the systems in which
-% atoms/particles are interacting via short-range interactions, because
-% it is a good starting point of the study of more complex systems, for
-% example, the systems with long-range electrostatic interactions.  The
-% simulation results in the inhomogeneous systems are found to depend on
-% a number of factors of treating the short-range interaction in the
-% simulation. For example, the way of calculating the short-range
-% interaction (simple cut-off method or Ewald
-% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
-%   lopez2006liquid, shi2006molecular, ismail2007application}, the
-% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
-%   shen2007comparative}, the way of long-range
-% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
-%   goujon2004monte} and the size and shape of the simulation
-% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
-% It should be noticed that the physical properties are the nature of
-% the system, and should NOT depend on the details of the interaction
-% calculation.
 
@@
 }
-% Finally, conclusions are given in section
-% \ref{sec:conclusion}.
-
-% The error estimate of long-range algorithms, for example the Ewald
-% family method~\cite{ewald1921die, hockney1988computer,
-%   deserno1998mue1, darden1993pme, essmann1995spm} and the fast
-% multipole method~\cite{greengard1987fast}, has been well developped in
-% the past 20 years ~\cite{hummer1995numerical, kolafa1992cutoff,
-%   petersen1995accuracy, deserno1998mue2, wang2010optimizing,
-%   dachsel2009error}.
 
@@
 we will consider one-component systems, but
-% we only consider the single-component system. Because
-% this assumption simplifies the discussion, and
 the error estimate for
@@
 applications are based on molecular dynamics simulations.
-% Since the error estimate developed for the one-component system can be
-% directly extended to multi-component system without substantial
-% difficulty, the discussion in this paper will focus on one-component
-% system for symplicity. 
 Suppose the system is composed by $N$ identical particles located at
@@
 the direct part of Ewald family algorithms, and so forth.
-% An infinite cut-off radius will lead to
-% a precise calculation of interaction, but it is impractical.
-% The error of computing interaction is mainly introduced by a finit
-% value of the cut-off radius.
 
@@
 \subsection{Adaptive cut-off radius method}
-
-% In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
-% standard Lennard-Jones particles is set up in a tube with periodic
-% boundary condition. The liquid droplet (in the middle of the tube) is
-% in equilibrium with the surrounding vapor environment. The red line in
-% the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
-% of this inhomogeneous system. The green square denotes the real RMS
-% force error distribution. It is clear that the error form two peaks in
-% the interfacial region, which is much higher than the relative
-% constant error of the bulk liquid and the bulk vapor. The dashed and
-% the dotted blue line are the estimated homogeneity and inhomogeneity
-% errors, and the solid blue line is the sum. In the bulk region, the
-% homogeneity error dominates while in the interfacial region, the
-% inhomogeneity error dominates. The esitmated error matches perfactly
-% with the real error at the interfacial region, but presents
-% overestimation in the bulk regions. The overestimation probably stems
-% from the neglection of the correlation error in \eqref{eqn:tmp5}.
 
@@
 prohibitive to the on-the-fly application.
-
-% Since inhomogeneity error dominate the
-% force error of the system, such a big cutoff radius is a waste in the
-% bulk liquid and vapor regions. One possible way is to use adapt
-% cut-off radius according to the error distribution, so that larger
-% cut-off radii are used in the interfacial region while smaller cut-off
-% radii are used in the bulk regions.  More precisely, the aim of the
-% adaptive cut-off method is to equivalently distributed the force error
-% over the simulation region.
 
@@
 
-% This
-% means the force error is a combination of a homogeneous contribution,
-% an inhomogeneous contribution and a correlational contribution. The
-% inhomogeneous force can be applied as a correction to the error:
-% \begin{align}\label{eqn:tmp7}
-%   \v F_{\textrm{inhomo}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
-% \end{align}
-
 \subsection{Long-range force correction}
@@
 
-% \textrm{Var}[\Delta\v F_{\textrm{corr}}(\v r)] =
-
-% This means if we correct the computed force by the mean of the error
-% force, namely applying to each particle $\tilde{\v F}^c(\v r) =
-% \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle$ instead of
-% $\tilde{\v F}(\v r)$.
-
 \subsection{Long-range pressure correction}
-% By the cut-off method, the system lost the pressure contribution from
-% the particles outside the cut-off radius.  In the homogeneous systems,
-% the distribution of particles is assumed to be uniform outside the
-% cut-off radius, and the pressure correction is calculated by
-% integrating the virial from the cut-off to infinity.
-
-% In the inhomogeneous systems, the previous idea does not
-% work. Instead, the pressure correction of the system are:
 
@@
 K_{\textrm{P}}$, therefore,
-% For simplicity, let us consider the general form the the corrections:
-% \begin{align}
-%   Q = \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle
-% \end{align}
-% For the pressure correction, $K$ is replaced by $\frac{1}{2V}\v
-% r\otimes\v f^c$.  By using \eqref{eqn:tmp7}, we have
 \begin{align}\nonumber
@@
 
-% Clearly the contribution of the inhomogeneity
-% error is successfully removed, because the estimate of homogeneity
-% error follows the real error perfectly in the interfacial regions.  In
-% the bulk liquid region, the homogeneity error is slightly
-% overestimated, which is the same as the uniform and adaptive cut-off
-% simulations.
-
 \begin{figure}
@@
     and the force correction (LFC) method in blue (dark gray).
-    The cut-off of
-    the adaptive cut-off method is $r_c^\ast$ means its
-    control error is the maximum error of a uniform cut-off simulation
-    using that cut-off $r_c^\ast$.
+    ``The cut-off of
+    the adaptive cut-off method is $r_c^\ast$'' means that the
+    control error  $\mathcal E^\ast_{\textrm{C}}$
+    is the same as the maximum error of a uniform cut-off simulation
+    using $r_c^\ast$.
     Under this setting,  the maximum 
@@
     uniform cut-off method with $r_c^\ast=13$ using LPC.
-    The cut-off of
-    the adaptive cut-off method is $r_c^\ast$ means its
-    control error is the maximum error of a uniform cut-off simulation
-    using that cut-off $r_c^\ast$.
+    ``The cut-off of
+    the adaptive cut-off method is $r_c^\ast$'' means that the
+    control error  $\mathcal E^\ast_{\textrm{C}}$
+    is the same as the maximum error of a uniform cut-off simulation
+    using $r_c^\ast$.
     Under this setting,  the maximum 
@@
 }
-
-% To verify our simulations, we compare our results in
-% Tab. \ref{tab:comparison} with a wide range of results reported by
-% literature~\cite{janecek2006long, lotfi1992vapour,
-%   errington2003evaluating, ismail2007application}
-
-% We list in Tab. \ref{tab:comparison} a wide range of results reported
-% by literature~\cite{janecek2006long, lotfi1992vapour,
-%   errington2003evaluating, ismail2007application}, as well as our
-% uniform ($r_c^\ast = 13$) and force correction ($r_c^\ast = 5.0$)
-% results for comparison. The abbreviations in the table are explained
-% in the caption. The MC/LEC, MD/Ewald and our methods are direct
-% simulation of the inhomogeneous system. The MD/Npt+test particle and
-% MC/GC-TMMC methods are simulation of homogeneous systems that do not
-% have the difficulties of inhomogeneity, and are believed to be more
-% precise than direct simulations~\cite{shen2007comparative}.
-
-% \begin{table}
-%   \centering
-%   \caption{Equilibrium densities and surface tension comparision 
-%     with various literature results: Monte Carlo with long-range
-%     energy correction (MC/LEC)~\cite{janecek2006long}, Npt+test
-%     particle molecular dynamics (MD/Npt+test particle)~\cite{lotfi1992vapour},
-%     grand-canonical transition-matrix Monte Carlo (MC/GC-TMMC)~\cite{errington2003evaluating},
-%     molecular dynamics with dispersion term calculated by the Ewald
-%     summation (MD/Ewald)~\cite{ismail2007application}
-%     and uniform cut-off (URC) and long-range force correction (LFC) molecular dynamics
-%     proposed by this work. The surface tensions of this work are
-%     corrected by the long-range pressure correction.
-%     The cut-off radius of the Ewald summation is for the real space.
-%   }
-%   \label{tab:comparison}
-%   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}clllllc}\hline\hline
-%   % \begin{tabular}{cccc|cccc}\hline\hline
-%     $T^\ast$ & Method & $r_c^\ast$ & $\rho^\ast_{\textrm{liq}}$ & $\rho^\ast_{\textrm{vap}}$ & $\gamma^\ast$ & Source \\\hline
-%     0.70 & MC/LEC               & 2.5      & 0.842(1)    & 0.0021(2)   & 1.21(2)   & \cite{janecek2006long}\\
-%     0.70 & MD/Npt+test particle & 5.0      & 0.84266(18) & 0.00193(10) & -         & \cite{lotfi1992vapour}\\
-%     0.70 & MC/GC-TMMC           & 1/2 box  & 0.8424(13)  & 0.001992(2) & 1.182(10) & \cite{errington2003evaluating}\\
-%     % 0.70 & MD/Ewald             & 5.0(real)& 0.8414(1)   & 0.0020(0)   & 1.141(11) & \cite{ismail2007application}\\
-%     0.70 & MD/URC               & 13.0     & 0.8423(2)   & 0.0020(0)   & 1.128(10) & this work \\
-%     % 0.70 & MD/LFC               & 5.0      & 0.8424(2)   & 0.0021(1)   & 1.145(11) & this work \\\hline
-%     0.70 & MD/LFC               & 3.5      & 0.8430(4)   & 0.00209(9)  & 1.139(16) & this work \\\hline
-%     0.85 & MD/Npt+test particle & 5.0      & 0.77623(25) & 0.00970(22) & -         & \cite{lotfi1992vapour}\\
-%     0.85 & MC/GC-TMMC           & 1/2 box  & 0.7760(10)  & 0.009611(9) & 0.837(2)  & \cite{errington2003evaluating}\\
-%     % 0.85 & MD/Ewald             & 5.0(real)& 0.7750(1)   & 0.0098(0)   & 0.818(15) & \cite{ismail2007application}\\
-%     0.85 & MD/URC               & 13.0     & 0.7758(3)   & 0.0098(1)   & 0.794(09) & this work \\
-%     % 0.85 & MD/LFC               & 5.0      & 0.7760(4)   & 0.0098(1)   & 0.823(21) & this work\\\hline
-%     0.85 & MD/LFC               & 3.5      & 0.7761(3)   & 0.00986(16) & 0.794(15) & this work\\\hline
-%     1.10 & MC/LEC               & 2.5      & 0.642(1)    & 0.054(1)    & 0.33(2)   & \cite{janecek2006long}\\
-%     1.10 & MD/Npt+test particle & 5.0      & 0.6401(12)  & 0.0533(14)  & -         & \cite{lotfi1992vapour}\\
-%     1.10 & MC/GC-TMMC           & 1/2 box  & 0.6410(7)   & 0.05485(5)  & 0.343(2)  & \cite{errington2003evaluating}\\
-%     % 1.10 & MD/Ewald             & 5.0(real)& 0.6383(1)   & 0.0553(0)   & 0.302(11) & \cite{ismail2007application}\\
-%     1.10 & MD/URC               & 13.0     & 0.6399(9)   & 0.0560(8)   & 0.300(07) & this work\\
-%     % 1.10 & MD/LFC               & 5.0      & 0.6405(9)   & 0.0553(6)   & 0.293(9)  & this work\\ \hline
-%     1.10 & MD/LFC               & 3.5      & 0.6411(10)   & 0.0559(6)   & 0.302(11)  & this work\\ \hline
-%     1.20 & MC/LEC               & 2.5      & 0.566(1)    & 0.109(2)    & 0.16(2)   & \cite{janecek2006long}\\
-%     1.20 & MD/Npt+test particle & 5.0      & 0.5661(22)  & 0.0987(16)  & -         & \cite{lotfi1992vapour}\\
-%     % 1.20 & MD/Ewald             & 5.0(real)& 0.5627(2)   & 0.0942(0)   & 0.156(14) & \cite{ismail2007application}\\
-%     1.20 & MD/URC               & 13.0     & 0.5624(11)  & 0.1002(5)   & 0.131(6) & this work\\
-%     % 1.20 & MD/LFC               & 5.0      & 0.5651(22)  & 0.0987(11)  & 0.136(17) & this work\\
-%     1.20 & MD/LFC               & 3.5      & 0.5632(14)  & 0.1002(19)  & 0.130(8) & this work\\
-%     \hline\hline
-%   % \end{tabular}
-%   \end{tabular*}
-% \end{table}
-
-% The reason is the corrected error force has a varnished mean
-% value (, so it may point to any
-% direction with the same possibility.  With the same cut-off radius,
-% the computational cost of the force correction and uniform cut-off
-% methods are nearly the same, see Tab. \ref{tab:tmp1}. However, the
-% maximum force error of the force correction method is about one order
-% of maganitude more precise, comparing with the uniform cut-off
-% simulations.
-
-% The convergence of the surface tension with respect to the cut-off
-% radius is shown in the Fig. \ref{fig:tmp6}. The color notation is the
-% same as Fig. \ref{fig:tmp5}.  Surface tensions measured with and
-% without inhomogeneous pressure correction are connected by solid and
-% dashed lines, respectively.  The reference surface tension is
-% presented by the black solid lines. The inhomogeneous pressure
-% correction improve the surface tention measurement greatly. The
-% discrepancy between the corrected and uncorrected pressure is the
-% value of the correction, which decreases with increasing cut-off
-% radius. However, even at $r_c^\ast=10$, the correction is not
-% negligible for $T^\ast = 0.70$ and $T^\ast = 0.85$. At higher
-% temperature, the statistical uncertainty gets larger, and better
-% convergence is achieved at small cut-off radius.
-
-% Although the force correction is a
-% little better, no substential difference between the different
-% simulation methods is observed. However, the With the
-% pressure correction, the result is acceptable at cut-off 5.0 and
-% satisfactorily converged at cut-off 7.5.
-
-% The equilibrium liquid and vapor densities with respect to
-% the cut-off radius are presented in Fig. \ref{fig:tmp5}. For the
-% adaptive cut-off simulation, the data points represent the largest
-% cut-off radius used in the simulations. All the results are
-% substracted by the reference results, which are calculated at uniform
-% cut-off radius of 13, for a clear comparison. Solid and dashed lines
-% are added to the data points of vapor and liquid densities
-% respectively. For the uniform and adaptive cut-off simulations, the
-% cut-off radii 5, 7.5 and 10 are considered. For the force correction,
-% the cut-off 3.5 is investigated in addition. We perform simulations at
-% different temperature: that are denoted in the plots.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/rcut.adapt.eps}
-%   \caption{The adapted cut-off radius of the 16000 Lennard-Jones
-%     particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp3}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-adapt-e0.0045-extend/error.adapt.eps}
-%   \caption{The error distribution of the adaptive-cut-off 16000
-%     Lennard-Jones particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp4}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/fcorr.eps}
-%   \caption{The correction force simulation of the 16000 Lennard-Jones
-%     particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp3}
-% \end{figure}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/t0.85-n16000-fcorr-rc07.5-feq0200/error.fcorr.eps}
-%   \caption{The correction force simulation of the adaptive-cut-off 16000
-%     Lennard-Jones particle system at $T^\ast=0.85$.}
-%   \label{fig:tmp4}
-% \end{figure}
 
@@
 force, so that the inhomogeneity error is removed from the system.
-It should be noticed that the porposed error estimate and correction
-methods can only be used to periodic systems.
+It should be noticed that the proposed error estimate and correction
+methods can only be used for periodic systems.
 
@@
 system:{
-% if the large bulk regions are connected by high density
-% gradient interfaces,
   if the computational costs of the bulk regions rather than the
@@
 densities). {
-% With nearly the same RMS force error, precision of
-% equilibrium densities of the force correction simulation were much
-% better than the uniform cut-off simulation.  Since the homogeneity
-% error dominated the force correction and the inhomogeneity error
-% dominated the simulation with uniform cut-off,
 We also concluded that the homogeneity

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/main.tex
revise according to pre

@@
 \renewcommand{\v}[1]{\textbf{\textit{#1}}}
-\renewcommand{\d}[1]{\textsf{#1}}
+\renewcommand{\d}[1]{\textit{#1}}
 
@@
 interactions is to explicitly calculate all pairwise
-interactions. This results in a computational cost scaling $\mathcal
-O(N^2)$ per time step, which becomes rapidly inefficient as the number
+interactions. This results in a computational cost scaling $\mathit{O}(N^2)$ per time step, which becomes rapidly inefficient as the number
 of particles $N$ grows. A better way is to introduce a cut-off
@@
 short-range interactions can be reduced to an acceptable level of
-$\mathcal O(N)$.  The cut-off radius neglects all pairwise interactions
+$\mathit{O}(N)$.  The cut-off radius neglects all pairwise interactions
 outside the cut-off radius, so it introduces an error in the interaction
@@
 cut-off radius value~\cite{duque2004some, ismail2007application}, also
-depend on the energy/force continuity at the cut-off and the way of
+depend on the energy (force) continuity at the cut-off and the way of
 applying the long-range corrections~\cite{trokhymchuk1999computer,
@@
 The naive calculation of the convolutions in the error estimate \eqref{eqn:tmp5} requires
-a computational cost of $\mathcal O(N^2)$. To estimate the force error
+a computational cost of $\mathit{O}(N^2)$. To estimate the force error
 on the fly, the computational cost of the estimate should be reduced to
-at least $\mathcal O(N\log N)$.  This is achieved by  using the fast Fourier transform. We
+at least $\mathit{O}(N\log N)$.  This is achieved by  using the fast Fourier transform. We
 assume the simulation box is uniformly divided in to small bins.  The
@@
 force error at least once for each particle, and the computational
-cost of each force error estimate is $\mathcal O(N \log N)$,
+cost of each force error estimate is $\mathit{O}(N \log N)$,
 so the total computational expense of 
-this method is at least $\mathcal O(N^2\log N)$, which is
+this method is at least $\mathit{O}(N^2\log N)$, which is
 prohibitive to the on-the-fly application.
@@
 constraint $\mathcal E(\v r_{i_1,i_2,i_3}) \leq \mathcal
-E_{\textrm{C}}$. The computational cost of this algorithm is $\mathcal
-O(MN\log N)$.
+E_{\textrm{C}}$. The computational cost of this algorithm is $\mathit{O}(MN\log N)$.
 The idea of this algorithm is based on the observation
@@
 system is subdivided into slabs perpendicular to the inhomogeneous direction to
-calculate the energy/force correction. The advantage of our force
+calculate the energy or force correction. The advantage of our force
 correction is that it has \emph{no} uniformity restriction on the density
@@
 typical inhomogeneous system, which is widely used to study the phase
-coexistence properties, for example, the equilibrium liquid/vapor
-density, and the surface tension. The system studied in the present
+coexistence properties, for example, the equilibrium liquid-vapor
+densities, and the surface tension. The system studied in the present
 paper contains 16,000 identical standard Lennard-Jones particles that are
@@
   \centering
-  \includegraphics[]{error.uniform.eps}
+  \includegraphics[]{pre.error.uniform.eps}
   \caption{(Color online)
@@
   \centering
-  \includegraphics[]{rcut.and.error.eps}
+  \includegraphics[]{pre.rcut.and.error.eps}
   \caption{ (Color online)
@@
   \centering
-  \includegraphics[]{fcorr.and.error.eps}
+  \includegraphics[]{pre.fcorr.and.error.eps}
   \caption{ (Color online)
@@
 In the Fig. \ref{fig:tmp5} and Fig. \ref{fig:tmp6}, the convergence of
-the equilibrium liquid/vapor densities and surface tension are
+the equilibrium liquid-vapor densities and surface tension are
 investigated with respect to the increasing cut-off radius. The red,
@@
 maximum of force error (see Tab. \ref{tab:tmp1}) and introducing
-larger homogeneous force error in the bulk liquid/gas regions will not
+larger homogeneous force error in the bulk liquid or gas regions will not
 disturb the accuracy of the equilibrium densities and surface tension.
@@
 correction method converges at $r_c^\ast = 3.5$, and the
-uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0\sim 6.0$.  The
+uniform (adaptive) cut-off methods converge at $r_c^\ast = 5.0\sim 6.0$.  The
 discrepancy between the corrected and uncorrected tension is the
@@
   \centering
-  \includegraphics[]{trajs.eps}
+  \includegraphics[]{pre.trajs.eps}
   \caption{(Color online)
     The center of mass trajectory of cluster A. Uniform cut-off
-    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
+    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c^\ast =
     5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
@@
     time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
-    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
+    cut-off (ARC) $r_c^\ast = 5.0$ and long-range force correction (LFC)
     $r^\ast_c = 2.5$ are investigated.  }
@@
   \centering
-  \includegraphics[]{wy.eps}
+  \includegraphics[]{pre.wy.eps}
   \caption{(Color online)
@@
     cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
-    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    $r_c^\ast = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
     are investigated.}
@@
   \centering
-  \includegraphics[]{ly.eps}
+  \includegraphics[]{pre.ly.eps}
   \caption{(Color online)
@@
   \centering
-  \includegraphics[]{cost.eps}
+  \includegraphics[]{pre.cost.eps}
   \caption{(Color online)
@@
     cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
-    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
-    are investigated.}
+    $r_c^\ast = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
+    are investigated.
+    The computational cost is counted by
+    the number of calculated pairwise interactions.
+  }
   \label{fig:tmp13}
@@
   However, it should be noticed that
-  the cost of the error estimate scales as $\mathcal O(N\log N)$.
+  the cost of the error estimate scales as $\mathit{O}(N\log N)$.
   If the system only has short-range interaction that
-  scales as $\mathcal O(N)$, the load of the error estimate
+  scales as $\mathit{O}(N)$, the load of the error estimate
   may become comparatively expensive when the system is large,
@@
   If the system also needs long-range electrostatic calculation
-  that is usually treated by the $\mathcal O(N\log N)$ scaling
+  that is usually treated by the $\mathit{O}(N\log N)$ scaling
   Ewald type algorithms~\cite{darden1993pme, essmann1995spm, deserno1998mue1},

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/fig/fcorrColl-x0.60-u2.20-rc2.5-14/plots/plot.fcorr.gif.sh
add fig source files

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+target=$*
+
+for i in $target;
+do
+    echo "# processing $i"
+    p1=`echo $i | cut -d '.' -f 1`
+    p2=`echo $i | cut -d '.' -f 2`
+    p3=`echo $i | cut -d '.' -f 3`
+    out=$p1.$p2.$p3.gif
+    sed -e "/^set out/s/'.*'/'$out'/g" fcorr.one.gp |\
+    sed -e "/^spl/s/'.*'/'$i'/g" > tmp.gp
+    gnuplot tmp.gp
+done
+
+gifsicle --delay=10 $p1.*.*.gif > fcorr.out.gif

### 2014-09-07 longRange.hetero/profile.test/template/echo.record.sh
add missing files

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+source parameters.sh
+
+echo $record_dir

### 2014-09-07 longRange.hetero/profile.test/template/tools/analyze/include/back.h

@@ -1,0 +1,111 @@
+#ifndef __ErrorEstimate_SPME_Ana_SelfCorr_h_wanghan__
+#define __ErrorEstimate_SPME_Ana_SelfCorr_h_wanghan__
+
+#include <fftw3.h>
+#include <gsl/gsl_math.h>
+#include "Defines.h"
+#include "DensityProfile.h"
+
+class ErrorEstimate_SPME_Ana_SelfCorr
+{
+  IntVectorType K;
+  // IntVectorType Kmax;
+  int kcut;
+  int numk;
+  double beta;
+  int order;
+  int nele;
+  MatrixType vecA;
+  MatrixType vecAStar;
+  double volume;
+private:
+  void freeAll();
+  void calV();
+  void calAStar();
+  void calKernel();
+  inline int  index3to1 (const IntVectorType i,
+			 const IntVectorType N) const;
+  inline void index1to3 (const unsigned input,
+			 const IntVectorType N,
+			 IntVectorType * i) const;
+  fftw_complex ** myMalloc (int numOfk, int nele);
+  void myFree (int numOfk, fftw_complex ** a);
+private:
+  fftw_complex *rho1;
+  fftw_complex *rho2;
+  fftw_complex *k1mx, *k1my, *k1mz;
+  fftw_complex *k1rx, *k1ry, *k1rz;
+  fftw_complex *k2ma, *k2mb;
+  fftw_complex *error1x, *error1y, *error1z;
+  fftw_complex *error1;
+  fftw_complex *error2;
+  double self_error;
+  double qself_error;
+
+  fftw_plan p_forward_rho1, p_forward_rho2;
+  fftw_plan p_backward_k1mx;
+  fftw_plan p_backward_k1my;
+  fftw_plan p_backward_k1mz;
+  fftw_plan p_forward_k2a;
+  fftw_plan p_forward_k2b;
+  fftw_plan p_backward_error1x;
+  fftw_plan p_backward_error1y;
+  fftw_plan p_backward_error1z;
+  fftw_plan p_backward_error2;
+
+  fftw_complex **Fmx; // k
+  fftw_complex **Fmy;
+  fftw_complex **Fmz;
+  fftw_complex **FConvRho1x;
+  fftw_complex **FConvRho1y;
+  fftw_complex **FConvRho1z;
+  fftw_complex **Frx;
+  fftw_complex **Fry;
+  fftw_complex **Frz;
+  fftw_complex *selfx;
+  fftw_complex *selfy;
[…]

### 2014-09-07 longRange.hetero/profile.test/template/tools/cal.mean.error/app/cal.mean.error.cpp

@@ -1,0 +1,73 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include "StringSplit.h"
+
+#include <boost/program_options.hpp>
+namespace po = boost::program_options;
+
+int main(int argc, char * argv[])
+{  
+  po::options_description desc ("Allow options");
+
+  double xlo, xup;
+  unsigned colume;
+  std::string file;
+  
+  desc.add_options()
+      ("help,h", "print this message")
+      ("colume,c", po::value<unsigned > (&colume)->default_value(2), "colume")
+      ("xlow,l", po::value<double > (&xlo)->default_value(5.0), "value of lower bound")
+      ("xup,u",  po::value<double > (&xup)->default_value(10.), "value of upper bound")
+      ("input,i", po::value<std::string > (&file)->default_value ("force.ref"), "input file");
+  
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  int ci = colume - 1;
+  double sum = 0.;
+  int count = 0;
+  char line[20480];
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    std::cerr << "cannot open file " << file << std::endl;
+    return 1;
+  }
+  while (fgets(line, sizeof(line), fp) != NULL){
+    if (line[0] == '#') continue;
+    std::vector<std::string > words;
+    StringOperation::split (std::string(line), words);
+    if (words.size() < colume){
+      std::cerr << "wrong line fomat, do nothing" << std::endl;
+      return 1;
+    }
+    double xx = atof(words[0].c_str());
+    if (xx >= xlo && xx <= xup){
+      double value = atof(words[ci].c_str());
+      sum += value * value;
+      count ++;
+    }
+  }
+
+  if (count != 0){
+    printf ("average_error: %e\n", sqrt(sum / double(count)));
+  }
+
+  return 0;
+}

### 2014-09-07 longRange.hetero/profile.test/template/tools/profile/app/cutBox.cpp

@@ -1,0 +1,92 @@
+#include "DensityFunction.h"
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include "RandomGenerator.h"
+
+#include <boost/program_options.hpp>
+namespace po = boost::program_options;
+#include "GroFileManager.h"
+
+int main(int argc, char * argv[])
+{
+  std::string ifile, ofile;
+  std::vector<double > cut (3);
+  double extension = 0.;
+  
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("new-x,x", po::value<double > (&cut[0])->default_value(-1.), "cut on x")
+      ("new-y,y", po::value<double > (&cut[1])->default_value(-1.), "cut on y")
+      ("new-z,z", po::value<double > (&cut[2])->default_value(-1.), "cut on z")
+      ("extension,e", po::value<double > (&extension)->default_value(0.1), "extension")
+      ("input,i",   po::value<std::string > (&ifile)->default_value ("conf.gro"), "the input file")
+      ("output,o",  po::value<std::string > (&ofile)->default_value ("out.gro"), "the output file");
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  printf ("#######################################################\n");
+  printf ("## cut: %f %f %f\n", cut[0], cut[1], cut[2]);
+  printf ("#######################################################\n");
+
+  std::vector<int > resdindex, atomindex;
+  std::vector<std::string > resdname, atomname;
+  std::vector<std::vector<double > > posi, velo;
+  std::vector<double > box;
+  
+  GroFileManager::read (ifile, resdindex, resdname, atomname, atomindex,
+			posi, velo, box);
+
+  std::vector<int > resdindex1, atomindex1;
+  std::vector<std::string > resdname1, atomname1;
[…]

### 2014-09-07 longRange.hetero/alltext/publish/fig.new/error.water.charge0.834.box14.9x7.4x7.4.b2.500.r1.31.n6.K121x061x061/parameters.spme.st.h2o.gr.esti.sh
add missing files

@@ -1,0 +1,72 @@
+#!/bin/bash
+
+nframe_real_error=50
+nframe_traj=100
+config_pool=~/study/longRange.hetero/profile.test/config.pool
+water_template=$config_pool/water.one_peak
+
+# gen conf parameters
+Lx=14.896480
+Ly=7.448240
+Lz=7.448240
+layerWith=0.90
+peak_size=7.6
+rhoh=32.784
+rhol=0.005
+charge=0.834
+
+# project command
+project_name=uniform
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --rho $rhoh -n 0"
+
+peak_dist=5.0
+project_name=two_peaks
+profile_command="$project_name -d $peak_dist -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0"
+
+project_name=two_peaks_sep
+profile_command="$project_name -x $Lx -y $Ly -z $Lz --layer $layerWith --rhoh $rhoh --rhol $rhol -n 0"
+
+project_name=one_peak
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=rand_water_1
+profile_command="$project_name -x $Lx -y $Ly -z $Lz -p $peak_size -t $layerWith -u $rhoh -l $rhol -n 0 --charge $charge"
+
+project_name=water
+
+# param for reference force
+beta=2.5
+ref_rcut=2.1
+ref_Kx=161
+ref_Ky=81
+ref_Kz=81
+# regulate parameters. DO NOT MOVE
+nframe_real_error=`printf "%03d" $nframe_real_error`
+beta=`printf "%.3f" $beta`
+ref_rcut=`printf "%.2f" $ref_rcut`
+ref_Kx=`printf "%03d" $ref_Kx`
+ref_Ky=`printf "%03d" $ref_Ky`
+ref_Kz=`printf "%03d" $ref_Kz`
+Lx=`printf "%.1f" $Lx`
+Ly=`printf "%.1f" $Ly`
+Lz=`printf "%.1f" $Lz`
+charge=`printf "%.3f" $charge`
[…]

### 2014-10-22 force.kernel/test.kernels/app/main.cpp
fix bug in loading data

@@ -17,14 +17,15 @@ using namespace std;
 #include "nb_kernels.h"
 #include "nb_interactions.h"
 #include "RandomGenerator.h"
+#include "Stopwatch.h"
 
 const int MDDIM = 3;
 typedef float ValueType;
 
 int main(int argc, char * argv[])
 {
-  int n0 = 100;
-  int n1 = 4*2;
+  int n0 = 10000;
+  int n1 = 4*10000;
   ValueType cutoff[1] = {5.0};
   ValueType param [4] = {0.};
   param[0] = 24;
@@ -36,10 +37,11 @@ int main(int argc, char * argv[])
     coord[ii] = RandomGenerator_MT19937::genrand_real3();
     vdwtype[ii] = 0;
   }
-  // ValueType * force = (ValueType *) malloc (sizeof(ValueType) * MDDIM * n0);
-  // for (int ii = 0; ii < n0 * MDDIM; ++ii){
-  //   coord[ii] = RandomGenerator_MT19937::genrand_real3();
-  // }
+  ValueType * force = (ValueType *) malloc (sizeof(ValueType) * MDDIM * n0);
+  ValueType * force_shift = (ValueType *) malloc (sizeof(ValueType) * MDDIM * n0);
+  for (int ii = 0; ii < n0 * MDDIM; ++ii){
+    force[ii] = force_shift[ii] = 0;
+  }
   int * neighbor_index = (int *) malloc (sizeof(int) * n1);
   for (int ii = 0; ii < n1; ++ii){
     neighbor_index[ii] = int(RandomGenerator_MT19937::genrand_real2() * n0);
@@ -50,8 +52,9 @@ int main(int argc, char * argv[])
     neighbor_index_data[ii+1] = n1;
   }
 
-  int iindex = 0;
-  
+  Stopwatch mywatch;
+
+  mywatch.start();
   nb_pair_force <3,
 		 float,
 		 nb_interaction_geometric_none_tag,
@@ -59,11 +62,22 @@ int main(int argc, char * argv[])
 		 nb_interaction_electrostatic_null_tag,
 		 nb_interaction_vanderWaals_cutoff_tag,
 		 nb_interaction_compute_f_tag>
-      (NULL, param, cutoff, iindex, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, 1, NULL, NULL, NULL);
[…]

### 2014-10-22 force.kernel/test.kernels/include/nb_interaction_acc_128s.h

@@ -141,21 +141,22 @@ template <>
 inline void
 load_data_s3_a1
 <nb_interaction_accelteration_128s_tag> (const typename nb_interaction_accelteration_128s_tag::ValueType * __restrict__ dof,
-					    const int & iidx,
-					    typename nb_interaction_accelteration_128s_tag::DataType * x,
-					    typename nb_interaction_accelteration_128s_tag::DataType * y,
-					    typename nb_interaction_accelteration_128s_tag::DataType * z)
+					 const int & iidx,
+					 typename nb_interaction_accelteration_128s_tag::DataType * x,
+					 typename nb_interaction_accelteration_128s_tag::DataType * y,
+					 typename nb_interaction_accelteration_128s_tag::DataType * z)
 {
   const float * __restrict__ p0 (dof+3*iidx);
   
   __m128 t1, t2;
 
   t1 = _mm_loadl_pi(_mm_setzero_ps(), (__m64 *)p0);
-  t2 = _mm_load_ss(dof+2);
+  t2 = _mm_load_ss(p0+2);
 
   *x = _mm_shuffle_ps(t1, t1, _MM_SHUFFLE(0, 0, 0, 0));
   *y = _mm_shuffle_ps(t1, t1, _MM_SHUFFLE(1, 1, 1, 1));
   *z = _mm_shuffle_ps(t2, t2, _MM_SHUFFLE(0, 0, 0, 0));
+
 }
 
 template <>
@@ -217,7 +218,7 @@ load_data_s2_afull
 
 template <>
 inline void
-update_data_s3_afull
+decrease_data_s3_afull
 <nb_interaction_accelteration_128s_tag> (typename nb_interaction_accelteration_128s_tag::ValueType * __restrict__ dof,
 					    const typename nb_interaction_accelteration_128s_tag::IndexType iidx,
 					    typename nb_interaction_accelteration_128s_tag::DataType x,
@@ -256,6 +257,40 @@ update_data_s3_afull
   t4          = _mm_sub_ps(t4, t10);
   _mm_store_ss(p3, t4);
   _mm_storeh_pi((__m64 *)(p3+1), t4);
+}
+
+template <>
+inline void
+increase_data_s3_a1
+<nb_interaction_accelteration_128s_tag> (typename nb_interaction_accelteration_128s_tag::ValueType * __restrict__ dof_,
[…]

### 2014-10-22 force.kernel/test.kernels/include/nb_interaction_operators.h

@@ -48,11 +48,20 @@ load_data_s3_afull (const typename Acceleration::ValueType * __restrict__ dof,
 
 template <typename Acceleration>
 inline void
-update_data_s3_afull (typename Acceleration::ValueType * __restrict__ dof,
-		      const typename Acceleration::IndexType input,
-		      typename Acceleration::DataType x,
-		      typename Acceleration::DataType y,
-		      typename Acceleration::DataType z);
+decrease_data_s3_afull (typename Acceleration::ValueType * __restrict__ dof,
+			const typename Acceleration::IndexType input,
+			typename Acceleration::DataType x,
+			typename Acceleration::DataType y,
+			typename Acceleration::DataType z);
+
+template <typename Acceleration>
+inline void
+increase_data_s3_a1 (typename Acceleration::ValueType * __restrict__ dof,
+		     typename Acceleration::ValueType * __restrict__ shift,
+		     const int &input,
+		     typename Acceleration::DataType x,
+		     typename Acceleration::DataType y,
+		     typename Acceleration::DataType z);
 
 
 template<typename Acceleration>

### 2014-10-22 force.kernel/test.kernels/src/Stopwatch.cpp
add missing files

@@ -1,0 +1,30 @@
+#include "Stopwatch.h"
+#include <iostream>
+
+
+Stopwatch::Stopwatch ()
+    : HZi (1./HZ)
+{
+}
+
+// int main(int argc, char * argv[])
+// {
+//   Stopwatch sw;
+//   double a = 1000;
+//   double b = 19;
+//   double c;
+//   sw.start();
+//   for (double i = 0; i < 1e8; i = i + 1.) c = a * b;
+//   sw.stop();  
+//   std::cout << "user time " << sw.user() << std::endl;
+//   std::cout << "system time " << sw.system() << std::endl;
+//   std::cout << "real time " << sw.real() << std::endl;
+
+// //   sw.start();
+//   for (double i = 0; i < 1e8; i = i + 1.) c = a * b;
+//   sw.stop();  
+//   std::cout << "user time " << sw.user() << std::endl;
+//   std::cout << "system time " << sw.system() << std::endl;
+//   std::cout << "real time " << sw.real() << std::endl;
+  
+// }

### 2014-10-23 force.kernel/test.kernels/app/explicit.cpp
no output

@@ -101,9 +101,9 @@ int main(int argc, char * argv[])
   
   mywatch.stop();
 
-  for (int ii = 0; ii < n0; ++ii){
-    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  }
+  // for (int ii = 0; ii < n0; ++ii){
+  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  // }
 
   printf ("syste: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
   return 0;

### 2014-10-23 force.kernel/test.kernels/app/main.cpp

@@ -65,9 +65,9 @@ int main(int argc, char * argv[])
       (NULL, param, cutoff, n0, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, 1, force, force_shift, NULL);
   mywatch.stop();
   
-  for (int ii = 0; ii < n0; ++ii){
-    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  }
+  // for (int ii = 0; ii < n0; ++ii){
+  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  // }
   
   printf ("syste: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
 

### 2014-10-23 force.kernel/test.kernels/app/explicit.cpp
add energy computing mode, add code for phantom neighbors

@@ -16,14 +16,13 @@ using namespace std;
 const int MDDIM = 3;
 typedef float ValueType;
 
-#include "nb_interaction_lj.h"
 #include "RandomGenerator.h"
 #include "Stopwatch.h"
 
 int main(int argc, char * argv[])
 {
-  int n0 = 10000;
-  int n1 = 4*10000;
+  int n0 = 4;
+  int n1 = 2;
   ValueType cutoff[1] = {5.0};
   ValueType param [4] = {0.};
   param[0] = 24;
@@ -41,10 +40,14 @@ int main(int argc, char * argv[])
     force[ii] = force_shift[ii] = 0;
   }
 
-  int * neighbor_index = (int *) malloc (sizeof(int) * n1);
+  int * neighbor_index = (int *) malloc (sizeof(int) * (n1 + 256));
   for (int ii = 0; ii < n1; ++ii){
     neighbor_index[ii] = int(RandomGenerator_MT19937::genrand_real2() * n0);
   }
+  for (int ii = n1; ii < n1+256; ++ii){
+    neighbor_index[ii] = -1;
+  }
+  
   int * neighbor_index_data = (int *) malloc (sizeof(int) * n0 * 2);
   for (int ii = 0; ii < n0 * 2; ii+=2){
     neighbor_index_data[ii+0] = 0;
@@ -101,11 +104,11 @@ int main(int argc, char * argv[])
   
   mywatch.stop();
 
-  // for (int ii = 0; ii < n0; ++ii){
-  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  // }
+  for (int ii = 0; ii < n0; ++ii){
+    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  }
 
-  printf ("syste: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
+  printf ("system: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
   return 0;
 }
 

### 2014-10-23 force.kernel/test.kernels/app/main.cpp

@@ -24,8 +24,8 @@ typedef float ValueType;
 
 int main(int argc, char * argv[])
 {
-  int n0 = 10000;
-  int n1 = 4*10000;
+  int n0 = 4;
+  int n1 = 2;
   ValueType cutoff[1] = {5.0};
   ValueType param [4] = {0.};
   param[0] = 24;
@@ -42,10 +42,14 @@ int main(int argc, char * argv[])
   for (int ii = 0; ii < n0 * MDDIM; ++ii){
     force[ii] = force_shift[ii] = 0;
   }
-  int * neighbor_index = (int *) malloc (sizeof(int) * n1);
+  int * neighbor_index = (int *) malloc (sizeof(int) * (n1 + 256));
   for (int ii = 0; ii < n1; ++ii){
     neighbor_index[ii] = int(RandomGenerator_MT19937::genrand_real2() * n0);
   }
+  for (int ii = n1; ii < n1+256; ++ii){
+    neighbor_index[ii] = -1;
+  }
+
   int * neighbor_index_data = (int *) malloc (sizeof(int) * n0 * 2);
   for (int ii = 0; ii < n0 * 2; ii+=2){
     neighbor_index_data[ii+0] = 0;
@@ -60,16 +64,16 @@ int main(int argc, char * argv[])
 		 nb_interaction_geometric_none_tag,
 		 nb_interaction_accelteration_128s_tag,
 		 nb_interaction_electrostatic_null_tag,
-		 nb_interaction_vanderWaals_cutoff_tag,
-		 nb_interaction_compute_f_tag>
+		 nb_interaction_vanderWaals_full_tag,
+		 nb_interaction_compute_energy_no_tag>
       (NULL, param, cutoff, n0, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, 1, force, force_shift, NULL);
   mywatch.stop();
   
-  // for (int ii = 0; ii < n0; ++ii){
-  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  // }
+  for (int ii = 0; ii < n0; ++ii){
+    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  }
   
-  printf ("syste: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
+  printf ("system: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
 
   free (coord);
   free (neighbor_index);

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc.h

@@ -18,4 +18,6 @@ struct nb_interaction_accelteration_avx_128_s_tag
 struct nb_interaction_accelteration_avx_256_s_tag {} ;
 
 
+
+
 #endif

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc_128s.h

@@ -42,6 +42,35 @@ copy_index<nb_interaction_accelteration_128s_tag> (const int & start_idx,
 
 template<>
 inline void
+copy_index_capped <nb_interaction_accelteration_128s_tag> (const int & start_idx,
+							   const int * nlist_data,
+							   typename nb_interaction_accelteration_128s_tag::IndexType * idx)
+{
+  (*idx).x = nlist_data[start_idx+0];
+  (*idx).y = (nlist_data[start_idx+1] < 0) ? nlist_data[start_idx] : nlist_data[start_idx+1] ;
+  (*idx).z = (nlist_data[start_idx+2] < 0) ? nlist_data[start_idx] : nlist_data[start_idx+2] ;
+  (*idx).w = (nlist_data[start_idx+3] < 0) ? nlist_data[start_idx] : nlist_data[start_idx+3] ;
+}
+
+template<>
+inline nb_interaction_accelteration_128s_tag::DataType
+cal_mask <nb_interaction_accelteration_128s_tag> (const int & start_idx,
+						  const int * nlist_data)
+{
+  return (nb_interaction_accelteration_128s_tag::DataType) (
+      _mm_cmplt_epi32(_mm_loadu_si128((const __m128i *)(nlist_data+start_idx)),_mm_setzero_si128()));
+}
+
+template<>
+inline nb_interaction_accelteration_128s_tag::DataType
+apply_mask <nb_interaction_accelteration_128s_tag> (const nb_interaction_accelteration_128s_tag::DataType & mask,
+						    const nb_interaction_accelteration_128s_tag::DataType & a)
+{
+  return _mm_andnot_ps(mask, a);
+}
+
+template<>
+inline void
 index_table_trans<nb_interaction_accelteration_128s_tag> (const typename nb_interaction_accelteration_128s_tag::IndexType * in,
 							  const int * table,
 							  typename nb_interaction_accelteration_128s_tag::IndexType * out)
@@ -220,10 +249,10 @@ template <>
 inline void
 decrease_data_s3_afull
 <nb_interaction_accelteration_128s_tag> (typename nb_interaction_accelteration_128s_tag::ValueType * __restrict__ dof,
-					    const typename nb_interaction_accelteration_128s_tag::IndexType iidx,
-					    typename nb_interaction_accelteration_128s_tag::DataType x,
-					    typename nb_interaction_accelteration_128s_tag::DataType y,
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_lj.h

@@ -1,51 +1,0 @@
-#ifndef __nb_interaction_lj_h_wanghan__
-#define __nb_interaction_lj_h_wanghan__
-
-#include "nb_interaction_acc.h"
-#include "nb_interaction_vdw.h"
-
-namespace LennardJones6_12{
-  typedef enum paramIndex {
-    epsilon		,
-    sigma		,
-    nparam
-  } paramIndex_t;
-}
-
-template <typename Acceleration>
-class VanderWaals_Interaction <Acceleration, nb_interaction_vanderWaals_cutoff_tag>
-{
-  typedef enum paramIndex {
-    epsilon		,
-    sigma		,
-    nparam
-  } paramIndex_t;
-  
-  static typename Acceleration::DataType one_over_12;
-  static typename Acceleration::DataType one_over_6;
-public:
-  inline typename Acceleration::DataType
-  fscale (const typename Acceleration::DataType & rinvsq,
-	  const typename Acceleration::DataType & c6,
-	  const typename Acceleration::DataType & c12);
-}
-    ;
-
-template<typename Acceleration>
-inline typename Acceleration::DataType
-VanderWaals_Interaction<Acceleration, nb_interaction_vanderWaals_cutoff_tag>::
-fscale (const typename Acceleration::DataType & rinvsq,
-	const typename Acceleration::DataType & c6,
-	const typename Acceleration::DataType & c12)
-{
-  typename Acceleration::DataType rinv6, vvdw6, vvdw12;
-  
-  rinv6  = mul<Acceleration>(mul<Acceleration>(rinvsq, rinvsq), rinvsq);
-  vvdw6  = mul<Acceleration>(c6, rinv6);
-  vvdw12 = mul<Acceleration>(c12, mul<Acceleration>(rinv6, rinv6));
-  return  mul<Acceleration>(sub<Acceleration>(vvdw12, vvdw6), rinvsq);
-}
-
-#endif
-
-

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_operators.h

@@ -14,6 +14,22 @@ copy_index (const int & start_idx,
 
 template<typename Acceleration>
 inline void
+copy_index_capped (const int & start_idx,
+		   const int * nlist_data,
+		   typename Acceleration::IndexType * idx);
+
+template<typename Acceleration>
+inline typename Acceleration::DataType
+cal_mask (const int & start_idx,
+	  const int * nlist_data);
+
+template<typename Acceleration>
+inline typename Acceleration::DataType
+apply_mask (const typename Acceleration::DataType & mask,
+	    const typename Acceleration::DataType & a);
+
+template<typename Acceleration>
+inline void
 index_table_trans (const typename Acceleration::IndexType * in,
 		   const int * table,
 		   typename Acceleration::IndexType * out);

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_vdw.h

@@ -2,18 +2,22 @@
 #define __nb_interaction_vdw_h_wanghan__
 
 struct nb_interaction_vanderWaals_null_tag	{} ;
-struct nb_interaction_vanderWaals_cutoff_tag	{} ;
+struct nb_interaction_vanderWaals_full_tag	{} ;
 struct nb_interaction_vanderWaals_shift_tag	{} ;
 struct nb_interaction_vanderWaals_pme_tag	{} ;
 
-template <typename Acceleration, typename VanderWaalsType>
+template <typename Acceleration,
+	  typename VanderWaalsType,
+	  typename ComputeMode>
 class VanderWaals_Interaction
 {
 public:
-  inline typename Acceleration::DataType
-  fscale (const typename Acceleration::DataType & rinvsq,
-	  const typename Acceleration::DataType & c6,
-	  const typename Acceleration::DataType & c12);  
+  inline void
+  force_energy (const typename Acceleration::DataType & rinv2,
+		const typename Acceleration::DataType & c6,
+		const typename Acceleration::DataType & c12,
+		typename Acceleration::DataType * fscale,
+		typename Acceleration::DataType * energy);
 };
 
 #endif

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_vdw_cutoff.h

@@ -1,0 +1,155 @@
+#ifndef __nb_interaction_vdw_cutoff_h_wanghan__
+#define __nb_interaction_vdw_cutoff_h_wanghan__
+
+#include "nb_interaction_acc.h"
+#include "nb_interaction_vdw.h"
+#include "nb_interaction_compute.h"
+
+namespace LennardJones6_12{
+  typedef enum paramIndex {
+    epsilon		,
+    sigma		,
+    nparam
+  } paramIndex_t;
+}
+
+template <typename Acceleration,
+	  typename ComputeMode>
+class VanderWaals_Interaction <Acceleration,
+			       nb_interaction_vanderWaals_full_tag,
+			       ComputeMode>
+{
+  typename Acceleration::DataType one_over_12;
+  typename Acceleration::DataType one_over_6;
+  inline void
+  cal_energy (const typename Acceleration::DataType & vvdw6,
+	      const typename Acceleration::DataType & vvdw12,
+	      typename Acceleration::DataType * energy,
+	      nb_interaction_compute_energy_no_tag);
+  inline void
+  cal_energy (const typename Acceleration::DataType & vvdw6,
+	      const typename Acceleration::DataType & vvdw12,
+	      typename Acceleration::DataType * energy,
+	      nb_interaction_compute_energy_yes_tag);	  
+public:
+  inline void
+  force_energy (const typename Acceleration::DataType & rinv2,
+		const typename Acceleration::DataType & c6,
+		const typename Acceleration::DataType & c12,
+		typename Acceleration::DataType * fscale,
+		typename Acceleration::DataType * energy);
+  inline void
+  foo ();
+}
+    ;
+
+template<typename Acceleration,
+	 typename ComputeMode>
+inline void
+VanderWaals_Interaction<Acceleration,
+			nb_interaction_vanderWaals_full_tag,
+			ComputeMode>::
+force_energy (const typename Acceleration::DataType & rinv2,
+	      const typename Acceleration::DataType & c6,
+	      const typename Acceleration::DataType & c12,
+	      typename Acceleration::DataType * fscale,
+	      typename Acceleration::DataType * energy)
+{
+  typename Acceleration::DataType rinv6, vvdw6, vvdw12;
+  
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_interactions.h

@@ -2,7 +2,7 @@
 #define __nb_interactions_h_wanghan__
 
 #include "nb_auxiliary.h"
-#include "nb_interaction_lj.h"
+#include "nb_interaction_vdw.h"
 #include "nb_interaction_acc_128s.h"
 
 // accelteration options:
@@ -15,11 +15,6 @@ struct nb_interaction_electrostatic_null_tag	{} ;
 struct nb_interaction_electrostatic_rf_tag	{} ;
 struct nb_interaction_electrostatic_pme_tag	{} ;
 struct nb_interaction_electrostatic_zm_tag	{} ;
-
-struct nb_interaction_compute_f_tag		{} ;
-struct nb_interaction_compute_fe_tag		{} ;
-struct nb_interaction_compute_fev_tag		{} ;
-struct nb_interaction_compute_fv_tag		{} ;
 
 template <int MDDIM, typename ValueType>
 inline void
@@ -37,7 +32,7 @@ nb_pair_force_lj_scale (const ValueType *		vdwParam,
 			const ValueType &		dist2,
 			ValueType &			fscale,
 			nb_interaction_accelteration_none_tag,
-			nb_interaction_vanderWaals_cutoff_tag)
+			nb_interaction_vanderWaals_full_tag)
 {
   ValueType ri2 = 1./dist2;
   ValueType sri2 = vdwParam[LennardJones6_12::sigma] * vdwParam[LennardJones6_12::sigma] * ri2;
@@ -73,8 +68,8 @@ nb_pair_force_impl_nocut (const ValueType *		eleParam,
 			  nb_interaction_geometric_none_tag,
 			  nb_interaction_accelteration_none_tag,
 			  nb_interaction_electrostatic_null_tag,
-			  nb_interaction_vanderWaals_cutoff_tag,
-			  nb_interaction_compute_f_tag)
+			  nb_interaction_vanderWaals_full_tag,
+			  nb_interaction_compute_energy_no_tag)
 {
   ValueType ri2 = 1./dist2;
   ValueType sri2 = vdwParam[LennardJones6_12::sigma] * vdwParam[LennardJones6_12::sigma] * ri2;

### 2014-10-23 force.kernel/test.kernels/include/nb_kernels.h

@@ -2,7 +2,7 @@
 #define __nb_kernels_h_wanghan__
 
 #include "nb_interaction_acc_128s.h"
-#include "nb_interaction_lj.h"
+#include "nb_interaction_vdw_cutoff.h"
 // #include "nb_interactions.h"
 
 template <int MDDIM,
@@ -25,36 +25,41 @@ nb_pair_force (const ValueType *		eleParam_,
 	       const int			nvdw,
 	       ValueType *			force,
 	       ValueType *			force_shift,
-	       ValueType *			energy)
+	       ValueType *			total_energy)
 {
   // nb_pair_force_impl <MDDIM, ValueType,
   // 		      ElectrostaticType,
   // 		      VanderWaalsType,
   // 		      ComputeMode>
   //     (eleParam, vdwParam, cutoff, idx0, idx1, dof, charge, force, energy, fshift, Geometric(), Acceleration());
-  VanderWaals_Interaction <Acceleration, VanderWaalsType> vdw_inter;
+  VanderWaals_Interaction <Acceleration, VanderWaalsType, ComputeMode> vdw_inter;
   
   const typename Acceleration::ValueType * dof,*vdwParam;
   dof = static_cast <const typename Acceleration::ValueType *> (dof_);
   // eleParam = static_cast <const typename Acceleration::ValueType *> (eleParam_);
   vdwParam = static_cast <const typename Acceleration::ValueType *> (vdwParam_);
-  
-  typename Acceleration::DataType cix, ciy, ciz;
-  typename Acceleration::DataType fix, fiy, fiz;
+
+  typename Acceleration::DataType fscale, energy;
+  energy = fscale = init<Acceleration>();
 
   for (int iindex = 0; iindex < ni; ++iindex){
+    typename Acceleration::DataType cix, ciy, ciz;
     load_data_s3_a1<Acceleration> (dof, iindex, &cix, &ciy, &ciz);
-
     cix = sub<Acceleration> (cix, init<Acceleration>(2.0));
     ciy = sub<Acceleration> (ciy, init<Acceleration>(2.0));
     ciz = sub<Acceleration> (ciz, init<Acceleration>(2.0));
+
+    typename Acceleration::DataType fix, fiy, fiz;
     fix = init<Acceleration>();
     fiy = init<Acceleration>();
     fiz = init<Acceleration>();
 
     int vdw_ishift = vdwtype[iindex] * nvdw * 2;
 
[…]

### 2014-10-23 force.kernel/test.kernels/src/nb_interaction_lj.cpp

@@ -1,14 +1,0 @@
-#include "nb_interaction_vdw.h"
-#include "nb_interaction_lj.h"
-#include "nb_interaction_acc.h"
-
-template <>
-typename nb_interaction_accelteration_128s_tag::DataType
-VanderWaals_Interaction<nb_interaction_accelteration_128s_tag, nb_interaction_vanderWaals_cutoff_tag>::one_over_12 =
-    init<nb_interaction_accelteration_128s_tag> (nb_interaction_accelteration_128s_tag::ValueType(1./12.));
-
-template <>
-typename nb_interaction_accelteration_128s_tag::DataType
-VanderWaals_Interaction<nb_interaction_accelteration_128s_tag, nb_interaction_vanderWaals_cutoff_tag>::one_over_6 =
-    init<nb_interaction_accelteration_128s_tag> (nb_interaction_accelteration_128s_tag::ValueType(1./6.));
-

### 2014-10-23 force.kernel/test.kernels/app/explicit.cpp
clean up the operators' interface

@@ -21,8 +21,8 @@ typedef float ValueType;
 
 int main(int argc, char * argv[])
 {
-  int n0 = 4;
-  int n1 = 2;
+  int n0 = 10000;
+  int n1 = 39999;
   ValueType cutoff[1] = {5.0};
   ValueType param [4] = {0.};
   param[0] = 24;
@@ -104,9 +104,9 @@ int main(int argc, char * argv[])
   
   mywatch.stop();
 
-  for (int ii = 0; ii < n0; ++ii){
-    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  }
+  // for (int ii = 0; ii < n0; ++ii){
+  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  // }
 
   printf ("system: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
   return 0;

### 2014-10-23 force.kernel/test.kernels/app/main.cpp

@@ -24,8 +24,8 @@ typedef float ValueType;
 
 int main(int argc, char * argv[])
 {
-  int n0 = 4;
-  int n1 = 2;
+  int n0 = 10000;
+  int n1 = 39999;
   ValueType cutoff[1] = {5.0};
   ValueType param [4] = {0.};
   param[0] = 24;
@@ -69,9 +69,9 @@ int main(int argc, char * argv[])
       (NULL, param, cutoff, n0, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, 1, force, force_shift, NULL);
   mywatch.stop();
   
-  for (int ii = 0; ii < n0; ++ii){
-    printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
-  }
+  // for (int ii = 0; ii < n0; ++ii){
+  //   printf ("%f %f %f\n", force[0+3*ii], force[1+3*ii], force[2+3*ii]);
+  // }
   
   printf ("system: %f  user: %f  real: %f\n", mywatch.system(), mywatch.user(), mywatch.real());
 

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc.h

@@ -1,6 +1,8 @@
 #ifndef __nb_interaction_acc_h_wanghan__
 #define __nb_interaction_acc_h_wanghan__
 
+#include "nb_interaction_operators.h"
+
 struct nb_interaction_accelteration_none_tag	{} ;
 struct nb_interaction_accelteration_128s_tag ;
 struct nb_interaction_accelteration_128d_tag	{} ;

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc_128s.h

@@ -15,22 +15,9 @@ public:
 }
     ;
 
-// template<>
-// inline typename nb_interaction_accelteration_128s_tag::DataType
-// init <float, nb_interaction_accelteration_128s_tag> (const float & a)
-// {
-//   return _mm_set1_ps (a);
-// }
-// template<>
-// inline void 
-// copy_index <nb_interaction_accelteration_128s_tag> (const int & input,
-// 						    typename nb_interaction_accelteration_128s_tag::IndexType * idx)
-// {
-// }
-
 template<>
 inline void
-copy_index<nb_interaction_accelteration_128s_tag> (const int & start_idx,
+copy_index<nb_interaction_accelteration_128s_tag> (const int   start_idx,
 						   const int * nlist_data,
 						   typename nb_interaction_accelteration_128s_tag::IndexType * idx)
 {
@@ -42,7 +29,7 @@ copy_index<nb_interaction_accelteration_128s_tag> (const int & start_idx,
 
 template<>
 inline void
-copy_index_capped <nb_interaction_accelteration_128s_tag> (const int & start_idx,
+copy_index_capped <nb_interaction_accelteration_128s_tag> (const int   start_idx,
 							   const int * nlist_data,
 							   typename nb_interaction_accelteration_128s_tag::IndexType * idx)
 {
@@ -54,7 +41,7 @@ copy_index_capped <nb_interaction_accelteration_128s_tag> (const int & start_idx
 
 template<>
 inline nb_interaction_accelteration_128s_tag::DataType
-cal_mask <nb_interaction_accelteration_128s_tag> (const int & start_idx,
+cal_mask <nb_interaction_accelteration_128s_tag> (const int   start_idx,
 						  const int * nlist_data)
 {
   return (nb_interaction_accelteration_128s_tag::DataType) (
@@ -63,8 +50,8 @@ cal_mask <nb_interaction_accelteration_128s_tag> (const int & start_idx,
 
 template<>
 inline nb_interaction_accelteration_128s_tag::DataType
-apply_mask <nb_interaction_accelteration_128s_tag> (const nb_interaction_accelteration_128s_tag::DataType & mask,
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_operators.h

@@ -3,30 +3,30 @@
 
 template<typename Acceleration>
 inline void
-get (typename Acceleration::DataType in,
+get (const typename Acceleration::DataType in,
      typename Acceleration::ValueType * out);		// print the content of a for debug
 
 template<typename Acceleration>
 inline void
-copy_index (const int & start_idx,
+copy_index (const int   start_idx,
 	    const int * nlist_data,
 	    typename Acceleration::IndexType * idx);
 
 template<typename Acceleration>
 inline void
-copy_index_capped (const int & start_idx,
+copy_index_capped (const int   start_idx,
 		   const int * nlist_data,
 		   typename Acceleration::IndexType * idx);
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-cal_mask (const int & start_idx,
+cal_mask (const int   start_idx,
 	  const int * nlist_data);
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-apply_mask (const typename Acceleration::DataType & mask,
-	    const typename Acceleration::DataType & a);
+apply_mask (const typename Acceleration::DataType mask,
+	    const typename Acceleration::DataType a);
 
 template<typename Acceleration>
 inline void
@@ -37,7 +37,7 @@ index_table_trans (const typename Acceleration::IndexType * in,
 template<typename Acceleration>
 inline void
 index_increase (typename Acceleration::IndexType * out,
-		const int & inc);
+		const int inc);
 
 template <typename Acceleration>
 inline void
@@ -49,7 +49,7 @@ load_data_s2_afull (const typename Acceleration::ValueType * __restrict__ dof,
 template <typename Acceleration>
 inline void
 load_data_s3_a1 (const typename Acceleration::ValueType * __restrict__ dof,
-		 const int & idx,
+		 const int idx,
 		 typename Acceleration::DataType * x,
 		 typename Acceleration::DataType * y,
 		 typename Acceleration::DataType * z);
@@ -74,7 +74,7 @@ template <typename Acceleration>
 inline void
 increase_data_s3_a1 (typename Acceleration::ValueType * __restrict__ dof,
 		     typename Acceleration::ValueType * __restrict__ shift,
-		     const int &input,
+		     const int input,
 		     typename Acceleration::DataType x,
 		     typename Acceleration::DataType y,
 		     typename Acceleration::DataType z);
@@ -82,7 +82,7 @@ increase_data_s3_a1 (typename Acceleration::ValueType * __restrict__ dof,
 
 template<typename Acceleration>
[…]

### 2014-10-23 force.kernel/test.kernels/app/explicit.cpp
fix bug in lj parameter reading, default implementation of operators in float or double.

@@ -27,6 +27,7 @@ int main(int argc, char * argv[])
   ValueType param [4] = {0.};
   param[0] = 24;
   param[1] = 48;
+  int nvdw = 1;
 
   ValueType * coord = (ValueType *) malloc (sizeof(ValueType) * MDDIM * n0);
   int * vdwtype = (int *) malloc (sizeof(ValueType) * MDDIM * n0);
@@ -65,6 +66,7 @@ int main(int argc, char * argv[])
     dof0[1] = coord[iindex*3+1]	-2;
     dof0[2] = coord[iindex*3+2]	-2;
     ValueType tmpf [MDDIM] = {0.};
+    int vdw_ishift = vdwtype[iindex] * nvdw;
     
     for (int jj = neighbor_index_data[iindex*2]; jj < neighbor_index_data[iindex*2+1]; ++jj){
       int jindex = neighbor_index[jj];
@@ -80,8 +82,9 @@ int main(int argc, char * argv[])
       ValueType ri2 = 1./dist2;
       ValueType sri2 = ri2;
       ValueType sri6 = sri2*sri2*sri2;
-      ValueType scalor = (param[1] * (sri6*sri6) - param[0] * sri6) * ri2;
-      
+      int ljparam_idx  = vdwtype[jindex] + vdw_ishift;
+      ValueType scalor = (param[ljparam_idx*2+1] * (sri6*sri6) - param[ljparam_idx*2] * sri6) * ri2;
+
       // force0[0] = scalor * diff[0];
       // force0[1] = scalor * diff[1];
       // force0[2] = scalor * diff[2];

### 2014-10-23 force.kernel/test.kernels/app/main.cpp

@@ -30,6 +30,7 @@ int main(int argc, char * argv[])
   ValueType param [4] = {0.};
   param[0] = 24;
   param[1] = 48;
+  int nvdw = 1;
 
   ValueType * coord = (ValueType *) malloc (sizeof(ValueType) * MDDIM * n0);
   int * vdwtype = (int *) malloc (sizeof(ValueType) * MDDIM * n0);
@@ -62,11 +63,11 @@ int main(int argc, char * argv[])
   nb_pair_force <3,
 		 float,
 		 nb_interaction_geometric_none_tag,
-		 nb_interaction_accelteration_128s_tag,
+		 nb_interaction_accelteration_none_s_tag,
 		 nb_interaction_electrostatic_null_tag,
 		 nb_interaction_vanderWaals_full_tag,
 		 nb_interaction_compute_energy_no_tag>
-      (NULL, param, cutoff, n0, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, 1, force, force_shift, NULL);
+      (NULL, param, cutoff, n0, neighbor_index_data, neighbor_index, coord, NULL, vdwtype, nvdw, force, force_shift, NULL);
   mywatch.stop();
   
   // for (int ii = 0; ii < n0; ++ii){
@@ -80,6 +81,7 @@ int main(int argc, char * argv[])
   free (neighbor_index_data);
   free (force_shift);
   free (force);
+  free (vdwtype);
 
   return 0;
 }

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc.h

@@ -3,12 +3,14 @@
 
 #include "nb_interaction_operators.h"
 
-struct nb_interaction_accelteration_none_tag	{} ;
-struct nb_interaction_accelteration_128s_tag ;
+struct nb_interaction_accelteration_none_s_tag	;
+struct nb_interaction_accelteration_none_d_tag	{} ;
+struct nb_interaction_accelteration_128s_tag	;
 struct nb_interaction_accelteration_128d_tag	{} ;
 struct nb_interaction_accelteration_256s_tag	{} ;
 struct nb_interaction_accelteration_256d_tag	{} ;
 
+#include "nb_interaction_acc_none_s.h"
 #include "nb_interaction_acc_128s.h"
 
 struct nb_interaction_accelteration_sse2_s_tag

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc_128s.h

@@ -58,14 +58,14 @@ apply_mask <nb_interaction_accelteration_128s_tag> (const nb_interaction_accelte
 
 template<>
 inline void
-index_table_trans<nb_interaction_accelteration_128s_tag> (const typename nb_interaction_accelteration_128s_tag::IndexType * in,
+index_table_trans<nb_interaction_accelteration_128s_tag> (const typename nb_interaction_accelteration_128s_tag::IndexType in,
 							  const int * table,
 							  typename nb_interaction_accelteration_128s_tag::IndexType * out)
 {
-  out->x = table[in->x];
-  out->y = table[in->y];
-  out->z = table[in->z];
-  out->w = table[in->w];
+  out->x = table[in.x];
+  out->y = table[in.y];
+  out->z = table[in.z];
+  out->w = table[in.w];
 }
 
 template<>
@@ -179,10 +179,10 @@ template <>
 inline void
 load_data_s3_afull
 <nb_interaction_accelteration_128s_tag> (const typename nb_interaction_accelteration_128s_tag::ValueType * __restrict__ dof,
-					    const typename nb_interaction_accelteration_128s_tag::IndexType iidx,
-					    typename nb_interaction_accelteration_128s_tag::DataType * x,
-					    typename nb_interaction_accelteration_128s_tag::DataType * y,
-					    typename nb_interaction_accelteration_128s_tag::DataType * z)
+					 const typename nb_interaction_accelteration_128s_tag::IndexType iidx,
+					 typename nb_interaction_accelteration_128s_tag::DataType * x,
+					 typename nb_interaction_accelteration_128s_tag::DataType * y,
+					 typename nb_interaction_accelteration_128s_tag::DataType * z)
 {
   const float * __restrict__ p0 (dof+3*iidx.x);
   const float * __restrict__ p1 (dof+3*iidx.y);

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_operators.h

@@ -30,7 +30,7 @@ apply_mask (const typename Acceleration::DataType mask,
 
 template<typename Acceleration>
 inline void
-index_table_trans (const typename Acceleration::IndexType * in,
+index_table_trans (const typename Acceleration::IndexType in,
 		   const int * table,
 		   typename Acceleration::IndexType * out);
 
@@ -82,11 +82,11 @@ increase_data_s3_a1 (typename Acceleration::ValueType * __restrict__ dof,
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-init (const typename Acceleration::ValueType a);				// return all elements of a
+init (const typename Acceleration::ValueType a);			// return all elements of a
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-init (void);									// return 0
+init (void);								// return 0
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
@@ -111,11 +111,210 @@ rsq (const typename Acceleration::DataType x,
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-invsqrt (const typename Acceleration::DataType a);				// 1/sqrt(a)
+invsqrt (const typename Acceleration::DataType a);			// 1/sqrt(a)
 
 template<typename Acceleration>
 inline typename Acceleration::DataType
-sq (const typename Acceleration::DataType a);					// a*a
+sq (const typename Acceleration::DataType a);				// a*a
+
+
+////////////////////////////////////////////////////////////////////////////////////////////////////
+// default implementation of the operators for a single float or double
+////////////////////////////////////////////////////////////////////////////////////////////////////
+
+template<typename Acceleration>
+inline void
+get (const typename Acceleration::DataType in,
+     typename Acceleration::ValueType * out)
+{
+  *out = static_cast<typename Acceleration::ValueType> (in);
+}
+
+template<typename Acceleration>
+inline void
+copy_index (const int   start_idx,
+	    const int * nlist_data,
+	    typename Acceleration::IndexType * idx)
+{
+  *idx = nlist_data[start_idx];
+}
+
+template<typename Acceleration>
+inline void
+copy_index_capped (const int   start_idx,
+		   const int * nlist_data,
+		   typename Acceleration::IndexType * idx)
+{
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_interactions.h

@@ -16,126 +16,126 @@ struct nb_interaction_electrostatic_rf_tag	{} ;
 struct nb_interaction_electrostatic_pme_tag	{} ;
 struct nb_interaction_electrostatic_zm_tag	{} ;
 
-template <int MDDIM, typename ValueType>
-inline void
-nb_pair_force_lj_scale (const ValueType *		vdwParam,
-			const ValueType &		dist2,
-			ValueType &			fscale,
-			nb_interaction_accelteration_none_tag,
-			nb_interaction_vanderWaals_null_tag)
-{
-}
+// template <int MDDIM, typename ValueType>
+// inline void
+// nb_pair_force_lj_scale (const ValueType *		vdwParam,
+// 			const ValueType &		dist2,
+// 			ValueType &			fscale,
+// 			nb_interaction_accelteration_none_tag,
+// 			nb_interaction_vanderWaals_null_tag)
+// {
+// }
 
-template <int MDDIM, typename ValueType>
-inline void
-nb_pair_force_lj_scale (const ValueType *		vdwParam,
-			const ValueType &		dist2,
-			ValueType &			fscale,
-			nb_interaction_accelteration_none_tag,
-			nb_interaction_vanderWaals_full_tag)
-{
-  ValueType ri2 = 1./dist2;
-  ValueType sri2 = vdwParam[LennardJones6_12::sigma] * vdwParam[LennardJones6_12::sigma] * ri2;
-  ValueType sri6 = sri2*sri2*sri2;
-  fscale += 24 * vdwParam[LennardJones6_12::epsilon] * (ValueType(2) * (sri6*sri6) - sri6) * ri2;
-}
+// template <int MDDIM, typename ValueType>
+// inline void
+// nb_pair_force_lj_scale (const ValueType *		vdwParam,
+// 			const ValueType &		dist2,
+// 			ValueType &			fscale,
+// 			nb_interaction_accelteration_none_tag,
+// 			nb_interaction_vanderWaals_full_tag)
+// {
+//   ValueType ri2 = 1./dist2;
+//   ValueType sri2 = vdwParam[LennardJones6_12::sigma] * vdwParam[LennardJones6_12::sigma] * ri2;
+//   ValueType sri6 = sri2*sri2*sri2;
+//   fscale += 24 * vdwParam[LennardJones6_12::epsilon] * (ValueType(2) * (sri6*sri6) - sri6) * ri2;
+// }
 
-template <int MDDIM, typename ValueType>
-inline void
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_kernels.h

@@ -54,7 +54,7 @@ nb_pair_force (const ValueType *		eleParam_,
     fiy = init<Acceleration>();
     fiz = init<Acceleration>();
 
-    int vdw_ishift = vdwtype[iindex] * nvdw * 2;
+    int vdw_ishift = vdwtype[iindex] * nvdw;
 
     int jj;
     for (jj = neighbor_index_data[iindex*2];
@@ -78,14 +78,16 @@ nb_pair_force (const ValueType *		eleParam_,
       rinv = invsqrt<Acceleration>(r2);
       rinv2 = mul<Acceleration>(rinv, rinv);
 
-      typename Acceleration::DataType c6, c12;
-      typename Acceleration::IndexType param_index;
-      index_table_trans<Acceleration> (&jindex, vdwtype, &param_index);
-      index_increase<Acceleration> (&param_index, vdw_ishift);
+      {
+	typename Acceleration::DataType c6, c12;
+	typename Acceleration::IndexType param_index;
+	index_table_trans<Acceleration> (jindex, vdwtype, &param_index);
+	index_increase<Acceleration> (&param_index, vdw_ishift);
     
-      load_data_s2_afull<Acceleration> (vdwParam, param_index, &c6, &c12);
+	load_data_s2_afull<Acceleration> (vdwParam, param_index, &c6, &c12);
     
-      vdw_inter.force_energy (rinv2, c6, c12, &fscale, &energy);
+	vdw_inter.force_energy (rinv2, c6, c12, &fscale, &energy);
+      }
     
       typename Acceleration::DataType tfx, tfy, tfz;
       tfx = mul<Acceleration> (fscale, diffx);
@@ -128,29 +130,23 @@ nb_pair_force (const ValueType *		eleParam_,
       rinv = invsqrt<Acceleration>(r2);
       rinv2 = mul<Acceleration>(rinv, rinv);
 
-      typename Acceleration::DataType c6, c12;
-      typename Acceleration::IndexType param_index;
-      index_table_trans<Acceleration> (&jindex, vdwtype, &param_index);
-      index_increase<Acceleration> (&param_index, vdw_ishift);
+      {
+	typename Acceleration::DataType c6, c12;
+	typename Acceleration::IndexType param_index;
+	index_table_trans<Acceleration> (jindex, vdwtype, &param_index);
+	index_increase<Acceleration> (&param_index, vdw_ishift);
     
[…]

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_acc_none_s.h
add missing files

@@ -1,0 +1,17 @@
+#ifndef __nb_interaction_acc_none_s_h_wanghan__
+#define __nb_interaction_acc_none_s_h_wanghan__
+
+#include "nb_interaction_operators.h"
+
+struct nb_interaction_accelteration_none_s_tag	{
+public:
+  typedef float		ValueType;
+  typedef float		DataType;
+  typedef int		IndexType;
+  static const int	index_stride = 1;
+}
+    ;
+
+#endif
+
+

### 2014-10-23 force.kernel/test.kernels/include/nb_interaction_compute.h

@@ -1,0 +1,7 @@
+#ifndef __nb_interaction_compute_h_wanghan__
+#define __nb_interaction_compute_h_wanghan__
+
+struct nb_interaction_compute_energy_no_tag	{} ;
+struct nb_interaction_compute_energy_yes_tag	{} ;
+
+#endif

### 2014-10-23 force.kernel/test.kernels/app/explicit.cpp
backup

@@ -78,6 +78,8 @@ int main(int argc, char * argv[])
       diff[1] = dof0[1] - dof1[1];
       diff[2] = dof0[2] - dof1[2];
       ValueType dist2 = diff[0] * diff[0] + diff[1] * diff[1] + diff[2] * diff[2];
+      // ValueType rinv = 1.f/sqrt(dist2);
+      // ValueType ri2 = rinv * rinv;
       // if (dist2 > cutoff[0] * cutoff[0]) continue;
       ValueType ri2 = 1./dist2;
       ValueType sri2 = ri2;
